### 2011-02-02 text/data_survey.tex
initial import text and data first experiment

\documentclass[fleqn,reqno,10pt,draft]{article}

%========================================
% Packages
%========================================

\usepackage[]{helpers/mypackages}

\bibliography{MyRefGlobal}

%\usepackage[garamond]{mathdesign}

%========================================
% Theorem Environments
%========================================

\usepackage{helpers/myenvironments}

%========================================
% Commands
%========================================

\usepackage{helpers/mycommands}

%========================================
% Page Layout
%========================================
% \renewcommand{\baselinestretch}{1.1} % multiplies vertical distance between lines in a paragraph
% \setlength{\parskip}{1ex plus 0.4ex minus 0.1ex}
% \addtolength{\voffset}{-1.7cm} \addtolength{\hoffset}{-1.5cm}
% \addtolength{\textwidth}{3.1cm} \addtolength{\textheight}{2.3cm}
% \addtolength{\voffset}{-1cm} \addtolength{\hoffset}{-0.5cm}
% \addtolength{\textwidth}{1cm} \addtolength{\textheight}{2cm}
% \setlength{\parindent}{0cm} % set paragraph indentation

%========================================
% More Layout
%========================================

% Itemize
\renewcommand{\labelitemi}{\large{$\mathbf{\cdot}$}}    % itemize symbols
\renewcommand{\labelitemii}{\large{$\mathbf{\cdot}$}}
\renewcommand{\labelitemiii}{\large{$\mathbf{\cdot}$}}
\renewcommand{\labelitemiv}{\large{$\mathbf{\cdot}$}}

% Description
\renewcommand{\descriptionlabel}[1]{\hspace\labelsep\textsc{#1}}

% Figure Captions
\usepackage{caption} % use corresponding myfiguresize!
\setlength{\captionmargin}{20pt}
\renewcommand{\captionfont}{\small}
\setlength{\belowcaptionskip}{7pt} % standard is 0pt

% Equationnumbering
%\numberwithin{equation}{section}

% sectioning
% \usepackage{sectsty}
% \chapterfont{\rmfamily\mdseries\Large\raggedleft}
% \sectionfont{\rmfamily\mdseries\large\nohang}
% \subsectionfont{\rmfamily\mdseries\normalsize\nohang}
% \subsubsectionfont{\rmfamily\mdseries\normalsize\itshape\nohang}
% \paragraphfont{\rmfamily\mdseries\normalsize\textsc}

% for indentation of section headings:
%\sectionfont{\hspace*{-2.3em}\rmfamily\mdseries\bfseries\large\nohang\raggedright}

%========================================
% Special for this Document
%========================================

\newcommand{\lit}{\ensuremath{\text{\textsc{lit}}}}
\newcommand{\glb}{\ensuremath{\text{\textsc{glb}}}}
\newcommand{\loc}{\ensuremath{\text{\textsc{loc}}}}

%========================================
% Document
%========================================

\title{Scalar Items in Embedded Positions}

\author{Michael Franke}
\date{\today}

\begin{document}

\maketitle

\section{Motivation}

\begin{itemize}
\item we are interested in studying potential global/local
  implicatures for sentences of the forms:
  \begin{exe}
    \ex 
      \begin{xlist}
        \ex All of the $X$'s are related to some of the $Y$'s.
        \ex Exactly one of the $X$'s is related to some of the $Y$'s.
        \ex Exactly one of the $Y$'s is related to all of the $Y$'s.
      \end{xlist}
  \end{exe}
\end{itemize}

\subsection{Global Implicatures}
\label{sec:global-implicatures}

\begin{itemize}
\item a \textsc{global implicature} of a sentence is derived by
  replacing one scalar item with its scale mates and negating the
  resulting sentence:
  \begin{exe}
    \ex \label{bsp:All_Some-Global} All of the $X$'s are related to some of the $Y$'s.
      \begin{xlist}
      \ex All of the $X$'s are related to some of the $Y$'s and
        \dots 
       \ex \dots it's
        not the case that all of the $X$'s are related to all of the $Y$'s.
      \end{xlist}
    \ex \label{bsp:Exactly_1_Some-Global} Exactly one of the $X$'s is related to some of the $Y$'s.
      \begin{xlist}
        \ex Exactly one of the $X$'s is related to some of the $Y$'s
          and \dots 
        \ex  \dots it's not the case that exactly one of the $X$'s is
          related to all of the $Y$'s.
      \end{xlist}
    \ex \label{bsp:Exactly_1_All-Global} Exactly one of the $Y$'s is related to all of the $Y$'s.
      \begin{xlist}
        \ex Exactly one of the $X$'s is related to all of the $Y$'s
          and \dots 
        \ex  \dots it's not the case that exactly one of the $X$'s is
          related to some of the $Y$'s.
      \end{xlist}
  \end{exe}
\item the global implicatures in (\ref{bsp:All_Some-Global}) and
  (\ref{bsp:Exactly_1_Some-Global}) are attested by all current formal
  theories of quantity implicature
\item we are interested in whether this prediction is borne out;
  previous experimentation supports this
\item we are also interested in whether we find support for the global
  implicature in (\ref{bsp:Exactly_1_All-Global}), which some theories
  predict
  \citep[e.g.][]{Sauerland2004:Scalar-Implicat,Fox2007:Free-Choice-and}
  and others don't \citep{HornDivisionofLabor1984};\draftnote{need to
    check in detail who predicts what} this case has not been
  investigated yet
\end{itemize}

\subsection{Local Implicatures}
\label{sec:local-implicatures}

\begin{itemize}
\item a \textsc{local implicature} of a sentence is derived by
  inserting into any appropriate scope site an exhaustifity operator
  akin to the workings of \emph{only},\draftnote{there is some due
    variation in formulation of this kind of approach}
\item all global implicatures are local implicatures, but additionally
  for our target sentences we may derive:
  \begin{exe}
    \ex \label{bsp:All-some-local} All of the $X$'s are related to some of the $Y$'s.
      \begin{xlist}
      \ex All of the $X$'s are related to some but not all of the $Y$'s.
      \end{xlist}
    \ex \label{bsp:Exactly-1-some-local} Exactly 1 of the $X$'s is related to some of the $Y$'s.
      \begin{xlist}
      \ex Exactly 1 of the $X$'s is related to some but not all of the $Y$'s.
      \end{xlist}
  \end{exe}
\item we are interested in whether these local implicatures are
  attested; previous studies have presented diverging evidence for
  this: \citet{GeurtsPouscoulous2009:Embedded-Implic} provide evidence
  \emph{against}; \citet{ChemlaSpector2010:Experimental-Ev} provide evidence
  \emph{for} these inferences
\end{itemize}

\section{Material}
\label{sec:material}

\begin{itemize}
\item we apply a truth-value judgement task, under the supposition
  that implicatures, when drawn, inform truth-judgements
\item we speak of a possible ``reading'' of a sentence: whether a
  global and/or local implicature is drawn
  \begin{itemize}
  \item literal reading: literally true \hfill (\lit)
  \item global reading: global implicature true \hfill (\glb)
  \item local reading: local implicature true \hfill (\loc)
  \end{itemize}
\item we present each of the three sentences with enough pictures to
  distinguish any possible reading
\item since there may be entailment relations between these
  ``readings'', the space of possibilities is rather restricted\\
  (e.g., obviously, the global reading always entails the literal reading)
\end{itemize}

\subsection{Case: ``All of the $X$'s are related to some of the $Y$'s.''}
\label{sec:case:-all-some}

\begin{itemize}
\item entailment relations in this case are: $\loc
  \Rightarrow \glb \Rightarrow \lit$
\item we can thus distinguish four cases:
  \begin{center}
    \begin{tabular}{lccc}
      \toprule
      & \textsc{lit} & \textsc{glb} & \textsc{loc} \\ \midrule
      Case 1 & 1 & 1 & 1 \\
      Case 2 & 1 & 1 & 0 \\
      Case 3 & 1 & 0 & 0 \\
      Case 4 & 0 & 0 & 0 \\ \bottomrule
    \end{tabular}
  \end{center}
\end{itemize}

\subsubsection{Pictures}
\label{sec:pictures}

\begin{itemize}

\item these cases can be tested for with the following
  diagrams:
  \begin{itemize}
  \item Case 1 (true-true-true):

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-4);

      \end{tikzpicture}
    \end{center}

  \item Case 2 (true-true-false):

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-1);

        \path [draw=green,->] (X-2) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-3);

        \path [draw=green,->] (X-2) -> (Y-4);

        \path [draw=red,->] (X-3) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-4);

      \end{tikzpicture}

    \end{center}
    \item Case 3 (true-false-false):

\begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=blue,->] (X-1) -> (Y-3);

        \path [draw=blue,->] (X-1) -> (Y-4);

        \path [draw=green,->] (X-2) -> (Y-1);

        \path [draw=green,->] (X-2) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-3);

        \path [draw=green,->] (X-2) -> (Y-4);

        \path [draw=red,->] (X-3) -> (Y-1);

        \path [draw=red,->] (X-3) -> (Y-2);

        \path [draw=red,->] (X-3) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-4);

      \end{tikzpicture}

    \end{center}

    \item Case 4 (false-false-false):

\begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=red,->] (X-3) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-4);

      \end{tikzpicture}

    \end{center}

  \end{itemize}
\end{itemize}

\subsubsection{Sentence Items}
\label{sec:sentence-items}

\begin{exe}
  \ex
    \begin{xlist}
    \ex Für jeden dieser Anwälte gilt: er vertritt einige dieser
      Angeklagten.
    \ex Für jedes dieser Kinder gilt: es mag einige dieser
      Speisen.
    \ex Für jeden dieser Kritiker gilt: er lobte einige dieser
      Aufführungen.
    \ex Für jede dieser Tennisspielerinnen gilt: sie hat schon
      einige dieser Turniere gewonnen.
    \ex Für jede dieser Künstlerinnen gilt: sie stellt in einigen
      dieser Museen aus.
    \ex Für jeden dieser Jungen gilt: er ist mit einigen dieser
      Mädchen befreundet.
    \ex Für jeden dieser Fußballfans gilt: er hat einige dieser
      Spiele gesehen.
    \ex Für jeden dieser Touristen gilt: er hat bereits einige dieser
      Länder bereist.
    \ex Für jeden dieser Bergsteiger gilt: er hat bereits einige dieser
      Gipfel erklommen.
    \ex Für jeden dieser Musikliebhaber gilt: er mag einige
      dieser Komponisten.
    \ex Für jeden dieser Schauspieler gilt: er hat bereits mit einigen dieser
      Regisseure zusammengearbeitet.
    \end{xlist}
\end{exe}

\subsection{Case: ``Exactly one of the $X$'s is related to some of the
  $Y$'s.''}
\label{sec:case:-exactly1-some}

\begin{itemize}
\item entailment relations in this case are:
  \begin{enumerate}[(i)]
  \item $\glb \Rightarrow \lit$
  \item $\glb \Rightarrow \loc$
  \item $\loc \Rightarrow \neg \lit$
  \end{enumerate}
\item so we distinguish the following four cases:
\begin{center}
    \begin{tabular}{lccc}
      \toprule
      & \textsc{lit} & \textsc{glb} & \textsc{loc} \\ \midrule
      Case 1 & 1 & 1 & 1 \\
      Case 2 & 0 & 0 & 1 \\
      Case 3 & 1 & 0 & 0 \\
      Case 4 & 0 & 0 & 0 \\ \bottomrule
    \end{tabular}
  \end{center}

\end{itemize}

\subsubsection{Pictures}
\label{sec:pictures}

\begin{itemize}

\item these cases can be tested for with the following
  diagrams:
  \begin{itemize}
  \item Case 1 (true-true-true):

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

      \end{tikzpicture}
    \end{center}
  \item Case 2 (false-false-true):

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=blue,->] (X-1) -> (Y-3);

        \path [draw=blue,->] (X-1) -> (Y-4);

        \path [draw=green,->] (X-2) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-3);

        \path [draw=green,->] (X-2) -> (Y-4);

        \path [draw=red,->] (X-3) -> (Y-1);

        \path [draw=red,->] (X-3) -> (Y-2);

        \path [draw=red,->] (X-3) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-4);

      \end{tikzpicture}
    \end{center}
  \item Case 3 (true-false-false):

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=green,->] (X-2) -> (Y-1);

        \path [draw=green,->] (X-2) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-3);

        \path [draw=green,->] (X-2) -> (Y-4);

      \end{tikzpicture}
    \end{center}
  \item Case 3 (false-false-false):

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=red,->] (X-3) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-4);

      \end{tikzpicture}
    \end{center}

  \end{itemize}
\end{itemize}

\subsubsection{Sentence Items}
\label{sec:sentence-items}

\begin{exe}
  \ex
    \begin{xlist}
    \ex Für genau einen dieser Anwälte gilt: er vertritt einige dieser
      Angeklagten.
    \ex Für genau eines dieser Kinder gilt: es mag einige dieser
      Speisen.
    \ex Für genau einen dieser Kritiker gilt: er lobte einige dieser
      Aufführungen.
    \ex Für genau eine dieser Tennisspielerinnen gilt: sie hat schon
      einige dieser Turniere gewonnen.
    \ex Für genau eine dieser Künstlerinnen gilt: sie stellt in einigen
      dieser Museen aus.
    \ex Für genau einen dieser Jungen gilt: er ist mit einigen dieser
      Mädchen befreundet.
    \ex Für genau einen dieser Fußballfans gilt: er hat einige dieser
      Spiele gesehen.
    \ex Für genau einen dieser Touristen gilt: er hat bereits einige dieser
      Länder bereist.
    \ex Für genau einen dieser Bergsteiger gilt: er hat bereits einige dieser
      Gipfel erklommen.
    \ex Für genau einen dieser Musikliebhaber gilt: er mag einige
      dieser Komponisten.
    \ex Für genau einen dieser Schauspieler gilt: er hat bereits mit einigen dieser
      Regisseure zusammengearbeitet.
    \end{xlist}
\end{exe}

\subsection{Case: ``Exactly one of the $X$'s is related to all of the
  $Y$'s.''}
\label{sec:case:-exactly1-all}

\begin{itemize}
\item entailment relations in this case are trivial: $\glb \Rightarrow \lit$
\item so we distinguish the following three cases:
\begin{center}
    \begin{tabular}{lcc}
      \toprule
      & \textsc{lit} & \textsc{glb} \\ \midrule
      Case 1 & 1 & 1  \\
      Case 2 & 1 & 0  \\
      Case 3 & 0 & 0  \\ \bottomrule
    \end{tabular}
  \end{center}
\end{itemize}

\subsubsection{Pictures}
\label{sec:pictures}

\begin{itemize}
\item these cases can be tested for with the following
  diagrams:
  \begin{itemize}
  \item Case 1 (true-true):

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-1);

        \path [draw=green,->] (X-2) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-3);

        \path [draw=green,->] (X-2) -> (Y-4);

      \end{tikzpicture}
    \end{center}
  \item Case 2 (true-false):

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=green,->] (X-2) -> (Y-1);

        \path [draw=green,->] (X-2) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-3);

        \path [draw=green,->] (X-2) -> (Y-4);

      \end{tikzpicture}
    \end{center}
  \item Case 3 (false-false):

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

      \end{tikzpicture}
    \end{center}
  \item Case 4 (false-false):\draftnote{we wanted to use two false
      conditions here, to fill the data set with four pictures for
      each sentence}

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=blue,->] (X-1) -> (Y-3);

        \path [draw=blue,->] (X-1) -> (Y-4);

        \path [draw=green,->] (X-2) -> (Y-1);

        \path [draw=green,->] (X-2) -> (Y-2);

        \path [draw=green,->] (X-2) -> (Y-3);

        \path [draw=green,->] (X-2) -> (Y-4);

        \path [draw=red,->] (X-3) -> (Y-1);

        \path [draw=red,->] (X-3) -> (Y-2);

        \path [draw=red,->] (X-3) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-4);

      \end{tikzpicture}
    \end{center}

  \end{itemize}
\end{itemize}

\subsubsection{Sentence Items}
\label{sec:sentence-items}

\begin{exe}
  \ex
    \begin{xlist}
    \ex Für genau einen dieser Anwälte gilt: er vertritt jeden
      dieser Angeklagten.
    \ex Für genau eines dieser Kinder gilt: es mag jede dieser
      Speisen.
    \ex Für genau einen dieser Kritiker gilt: er lobte jede dieser
      Aufführungen.
    \ex Für genau eine dieser Tennisspielerinnen gilt: sie hat schon
      jedes dieser Turniere gewonnen.
    \ex Für genau eine dieser Künstlerinnen gilt: sie stellt in jedem
      dieser Museen aus.
    \ex Für genau einen dieser Jungen gilt: er ist mit jedem dieser
      Mädchen befreundet.
    \ex Für genau einen dieser Fußballfans gilt: er hat jedes dieser
      Spiele gesehen.
    \ex Für genau einen dieser Touristen gilt: er hat bereits jedes dieser
      Länder bereist.
    \ex Für genau einen dieser Bergsteiger gilt: er hat bereits jeden dieser
      Gipfel erklommen.
    \ex Für genau einen dieser Musikliebhaber gilt: er mag jeden
      dieser Komponisten.
    \ex Für genau einen dieser Schauspieler gilt: er hat bereits mit jeden dieser
      Regisseure zusammengearbeitet.
    \end{xlist}
\end{exe}

\newpage

\section{Thoughts on Cumulative Readings}
\label{sec:thoughts-cumul-read}

\begin{itemize}
\item there may be a problem in our design from cumulative readings of (\ref{bsp:All_Some-Global})
\item under a cumulative reading, a sentence like
  (\ref{bsp:All_Some-Global}) means that the group of $X$'s \emph{as a
  whole} is connected to some of the $Y$'s
\item there are three relevant possible (disjoint) state distinctions
  for this reading:
  \begin{itemize}
  \item false-condition: group of $X$'s is connected to none of the $Y$'s; no
    arrows whatsoever
  \item literally-true-condition: group of $X$' is connected to all of
    the $Y$'s
  \item implicature-condition: group of $X$' is connected to
    some-but-not-all of the 
    $Y$'s
  \end{itemize}
\item the potential problem is that subjects' \emph{true}/\emph{false}
  judgements could be based on these cumulative readings (with/without
  implicature) and thus obscure whether they apply local or global readings
\item in particular, subjects who answer \emph{false} in cases 2 and 3
  might do so based on the cumulative reading with implicature, so
  that we might not know whether these judgements reflect on the
  potential implicatures of the non-cumulative readings
\item there is no way we can present a picture that could illicit
  judgements that would let us differentiate between cumulative and
  non-cumulative readings in cases 2 and 3
\item \emph{but} we can assess whether cumulative readings are
  available in two ways:
  \begin{itemize}
  \item under a cumulative reading case 1 (as depicted above) should
    also be judged \emph{false}
  \item moreover, we should change pictures for case 4 to:

    \begin{center}
      \begin{tikzpicture}[node distance = 1.3cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance =
        3cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=red,->] (X-3) -> (Y-2);

        \path [draw=red,->] (X-3) -> (Y-3);

      \end{tikzpicture}

    \end{center}

    Subjects who apply a cumulative reading should judge this
    \emph{true}
  \end{itemize}
\item as far as I can see, this is the best we can do: we have control
  conditions (cases 1 and 4) that would detect cumulative
  readings; but when they do we simply cannot use pictures like these
  to test cases 3 and 4 (if we wanted that, we'd need different visual
  material, unfortunately)
\item or am I wrong?
\item finally, if cumulative readings are possible for ``all of the
  $X$'s'' in (\ref{bsp:All_Some-Global}), so should they be in
  (\ref{bsp:Exactly_1_All-Global}), shouldn't they?
\item but here, too, we would see this in subjects responding
  \emph{true} in case 3 (as above) for this case\draftnote{careful: I
    mean the \emph{first} false-false picture; the previous text
    contained two times ``case 3'', a typo!}
\end{itemize}

\end{document}

### 2011-02-25 aux/material_exp2/sentences.tex
material 2nd experiment first draft

\documentclass[fleqn,reqno,10pt]{article}

%========================================
% Packages
%========================================

\usepackage[]{mypackages}

\bibliography{MyRefGlobal}

%\usepackage[garamond]{mathdesign}

%========================================
% Theorem Environments
%========================================

\usepackage{myenvironments}

%========================================
% Commands
%========================================

\usepackage{mycommands}

%========================================
% Page Layout
%========================================
% \renewcommand{\baselinestretch}{1.1} % multiplies vertical distance between lines in a paragraph
% \setlength{\parskip}{1ex plus 0.4ex minus 0.1ex}
% \addtolength{\voffset}{-1.7cm} \addtolength{\hoffset}{-1.5cm}
% \addtolength{\textwidth}{3.1cm} \addtolength{\textheight}{2.3cm}
% \addtolength{\voffset}{-1cm} \addtolength{\hoffset}{-0.5cm}
% \addtolength{\textwidth}{1cm} \addtolength{\textheight}{2cm}
% \setlength{\parindent}{0cm} % set paragraph indentation

%========================================
% More Layout
%========================================

% Itemize
\renewcommand{\labelitemi}{\large{$\mathbf{\cdot}$}}    % itemize symbols
\renewcommand{\labelitemii}{\large{$\mathbf{\cdot}$}}
\renewcommand{\labelitemiii}{\large{$\mathbf{\cdot}$}}
\renewcommand{\labelitemiv}{\large{$\mathbf{\cdot}$}}

% Description
\renewcommand{\descriptionlabel}[1]{\hspace\labelsep\textsc{#1}}

% Figure Captions
\usepackage{caption} % use corresponding myfiguresize!
\setlength{\captionmargin}{20pt}
\renewcommand{\captionfont}{\small}
\setlength{\belowcaptionskip}{7pt} % standard is 0pt

% Equationnumbering
%\numberwithin{equation}{section}

% sectioning
\usepackage{sectsty}
\chapterfont{\rmfamily\mdseries\Large\raggedleft}
\sectionfont{\rmfamily\mdseries\large\nohang\centering}
\subsectionfont{\rmfamily\mdseries\normalsize\nohang\centering}
\subsubsectionfont{\rmfamily\mdseries\normalsize\itshape\nohang\centering}
\paragraphfont{\rmfamily\mdseries\normalsize\textsc}

% for indentation of section headings:
%\sectionfont{\hspace*{-2.3em}\rmfamily\mdseries\bfseries\large\nohang\raggedright}

%========================================
% Document
%========================================

\title{Sentences for use in Experiment 2}

\date{February 25, 2011 }

\begin{document}

\maketitle

\section{Target Sentences}

\begin{itemize}
\item target sentences have a scalar item embedded under a quantifier
  \begin{itemize}
  \item embedding quantifiers:
    \begin{enumerate}
    \item definite article \attrib{(for baseline)}
    \item ``einige'' \attrib{(upward monotonic)}
    \item ``alle'' \attrib{(upward monotonic)}
    \item ``genau ein'' \attrib{(non-monotonic)}
    \end{enumerate}
  \item two scalar items in embedded position:
    \begin{enumerate}
    \item ``einige''
    \item ``oder''
    \end{enumerate}
  \end{itemize}
  \begin{exe}
  \ex \label{bsp:target1} Der \dots ist mit einigen seiner \dots
    verbunden. \attrib{($\iota\exists$)}
  \ex Einige der \dots sind  mit einigen ihrer \dots
    verbunden. \attrib{($\exists\exists$)}
  \ex Alle der \dots sind  mit einigen ihrer \dots verbunden. \attrib{($\forall\exists$)}
  \ex Genau einer der \dots ist  mit einigen seiner \dots verbunden. \attrib{($!\exists\exists$)}
  \ex Der \dots ist mit seinem \dots oder \dots verbunden. \attrib{($\iota\vee$)}
  \ex Einige der \dots sind  mit ihrem \dots oder \dots verbunden. \attrib{($\exists\vee$)}
  \ex Alle der \dots sind  mit ihrem \dots oder \dots verbunden. \attrib{($\forall\vee$)}
  \ex Genau einer der \dots ist  mit seinem \dots oder \dots verbunden. \attrib{($!\exists\vee$)}
  \end{exe}
\item each target sentence should occur in four (or three?) versions,
  e.g.:
  \begin{exe}
  \exr{bsp:target1} Der \dots ist mit einigen seiner \dots
    verbunden. \attrib{($\iota\exists$)}
    \begin{xlist}
    \ex Der \dots ist mit einigen seiner \dots
      verbunden. \attrib{(flat)}
    \ex Der \dots ist mit \emph{einigen} seiner \dots
      verbunden. \attrib{(stress)}
    \ex Der \dots ist nur mit einigen seiner \dots
      verbunden. \attrib{(only, flat)}
    \ex Der \dots ist nur mit \emph{einigen} seiner \dots
      verbunden. \attrib{(only, stress)}
    \end{xlist}
  \end{exe}

\end{itemize}

\section{Controls \& Fillers}

\begin{itemize}
\item to check if \acros{vp}\ understand ``incremental information
  evaluation'' in general
\end{itemize}

\medskip

\begin{exe}
  \ex Genau zwei der \dots sind mit mindestens einem der \dots verbunden.
  \ex Mindestens zwei der \dots sind mit mindestens eimem der \dots verbunden.
\end{exe}

\begin{itemize}
\item to check if \acros{vp}\ behave consistently with genuinely
  ambiguous sentences
  \begin{itemize}
  \item potential problem: disambiguation by intonation
  \end{itemize}
\end{itemize}

\medskip

\begin{exe}
  \ex There are triangles and squares that are connected with all of
    their circles.
  \ex There are blue triangles and squares.
\end{exe}

\section{Fillers}

\begin{exe}
  \ex Alle Quadrate sind rechts von ihrem Stern.
  \ex Der Stern ist links neben dem Quadrat.
  \ex Alle blauen Sterne sind unverbunden.
  \ex Genau ein Stern ist zwischen seinem dem Quadrat und seinem
    Dreieck. 
\end{exe}

% \printbibliography[heading=bibintoc]

\end{document}

### 2011-02-25 aux/material_exp2/sentences.tex
material 2nd experiment updated after meeting

@@
     \begin{enumerate}
-    \item definite article \attrib{(for baseline)}
-    \item ``einige'' \attrib{(upward monotonic)}
     \item ``alle'' \attrib{(upward monotonic)}
@@
   \begin{exe}
-  \ex \label{bsp:target1} Der \dots ist mit einigen seiner \dots
-    verbunden. \attrib{($\iota\exists$)}
-  \ex Einige der \dots sind  mit einigen ihrer \dots
-    verbunden. \attrib{($\exists\exists$)}
-  \ex Alle der \dots sind  mit einigen ihrer \dots verbunden. \attrib{($\forall\exists$)}
+  \ex \label{bsp:target1} Alle der \dots sind  mit einigen ihrer \dots
+    verbunden. \attrib{($\forall\exists$)}
   \ex Genau einer der \dots ist  mit einigen seiner \dots verbunden. \attrib{($!\exists\exists$)}
-  \ex Der \dots ist mit seinem \dots oder \dots verbunden. \attrib{($\iota\vee$)}
-  \ex Einige der \dots sind  mit ihrem \dots oder \dots verbunden. \attrib{($\exists\vee$)}
   \ex Alle der \dots sind  mit ihrem \dots oder \dots verbunden. \attrib{($\forall\vee$)}
@@
   \end{exe}
-\item each target sentence should occur in four (or three?) versions,
-  e.g.:
+\item each target sentence should occur in three versions, e.g.:
   \begin{exe}
-  \exr{bsp:target1} Der \dots ist mit einigen seiner \dots
-    verbunden. \attrib{($\iota\exists$)}
+    \exr{bsp:target1} Alle der \dots sind mit einigen ihrer \dots
+    verbunden. \attrib{($\forall\exists$)}
     \begin{xlist}
-    \ex Der \dots ist mit einigen seiner \dots
+    \ex  Alle der \dots sind mit einigen ihrer \dots
       verbunden. \attrib{(flat)}
-    \ex Der \dots ist mit \emph{einigen} seiner \dots
+    \ex Alle der \dots sind mit \emph{einigen} ihrer \dots
       verbunden. \attrib{(stress)}
-    \ex Der \dots ist nur mit einigen seiner \dots
-      verbunden. \attrib{(only, flat)}
-    \ex Der \dots ist nur mit \emph{einigen} seiner \dots
-      verbunden. \attrib{(only, stress)}
+    \ex Alle der \dots sind nur mit \emph{einigen} ihrer \dots
+      verbunden. \attrib{(only + stress)}
     \end{xlist}
   \end{exe}
-
+\item we test for 3 possible readings of each target sentence
 \end{itemize}

### 2011-02-28 aux/material_exp2/sentences.tex
import python scripts

@@
 
-%\usepackage[garamond]{mathdesign}
+\usepackage[]{mathdesign}
+\usepackage{MnSymbol}
+\usepackage{ulsy}
+\usepackage{wasysym}
+\usepackage{ascii}
+\usepackage{marvosym}
+\usepackage{pifont}
+\usepackage{phaistos}
+\usepackage{epsdice}
+\usepackage{skak}
 
@@
 
-\usepackage{mycommands}
+\usepackage{mycommand_local}
 
@@
 
+\newpage
+
+\appendix
+
+\section{Target Sentences}
+\label{sec:target-sentences}
+
+\subsection{$\forall\exists$}
+\label{sec:forallexists}
+
+\begin{exe}
+  \ex
+    \begin{xlist}
+      \ex Alle der Häkchen ($\checkmark$) sind mit einigen ihrer Kreise verbunden.
+      \ex Alle der Kreuze ($\maltese$) sind mit einigen ihrer Vierecke
+        verbunden.
+      \ex Alle der Sternchen ($\bigstar$) sind mit einigen ihrer
+        Dreiecke verbunden.
+      \ex Alle der Dreiecke ($\filledmedtriangleup$) sind mit einigen ihrer
+        Kreise verbunden.
+      \ex Alle der Punkte ($\medbullet$) sind mit einigen ihrer
+        Vierecke verbunden.
+      \ex Alle der Pfeile ($\text{\ding{220}}$) sind mit einigen ihrer
+        Dreiecke verbunden.
+      \ex Alle der Punkte ($\filledmedsquare$) sind mit einigen ihrer
+        Vierecke verbunden.
+      \ex Alle der Pentagramme ($\pentagram$) sind mit einigen ihrer
+        Kreise verbunden.
+      \ex Alle der Blitze ($\text{\blitze}$) sind mit einigen ihrer
+        Dreiecke verbunden.
+      \ex Alle der Fragezeichen ($\text{?}$) sind mit einigen ihrer
+        Dreiecke verbunden.
+      \ex Alle der Herzchen ($\varheartsuit$) sind mit einigen ihrer
+        Kreise verbunden.
+      \ex Alle der Picksymbole ($\spadesuit$) sind mit einigen ihrer
+        Kreise verbunden.
+    \end{xlist}
+\end{exe}
+
+\subsection{$!\exists\exists$}
+
+\begin{exe}
+\ex
+  \begin{xlist}
+  \ex Genau eine der Ellipsen ($\partialvartoiint$) ist mit einigen ihrer
+    Vierecke verbunden.     
+  \ex Genau einer der Monde ($\leftmoon$) ist mit einigen seiner
+    Vierecke verbunden.
+    \ex Genau eines der Notenzeichen ($\text{\SO}$) ist mit einigen seiner
+    Vierecke verbunden.
+    \ex Genau einer der Smileys ($\text{\SOH}$) ist mit einigen seiner
+    Vierecke verbunden.
+    \ex Genau eine der Sonnen ($\text{\SI}$) ist mit einigen seiner
+    Vierecke verbunden.
+    \ex Genau eines der Karos ($\text{\EOT}$) ist mit einigen seiner
+    Vierecke verbunden.
+    \ex Genau eines der Telefone ($\text{\Telefon}$) ist mit einigen seiner
+    Vierecke verbunden.
+    \ex Briefe (\Letter)
+    \ex Handys (\Mobilefone)
+    \ex Gefahrsymbole (\Biohazard)
+    \ex Stoppschilder (\Stopsign)
+    \ex Scheren (\Rightscissors)
+  \end{xlist}
+
+\end{exe}
+
+\subsection{$\forall\vee$}
+
+\begin{exe}
+\ex
+  \begin{xlist}
+    \ex Bleistifte (\ding{46})
+    \ex Davidsterne (\davidsstar)
+    \ex Eiskristalle (\ding{100})
+    \ex Blumen (\ding{96})
+    \ex Davidsterne (\davidsstar)
+    \ex Eiskristalle (\ding{100})
+    \ex Blumen (\ding{96})
+    \ex Fünfecke (\pentagon)
+    \ex Flugzeuge (\ding{40})
+    \ex Balken (\ding{121})
+    \ex Halbkreis (\ding{119})
+    \ex Taube (\PHdove)
+  \end{xlist}
+\end{exe}
+
+\subsection{$!\exists\vee$}
+
+\begin{exe}
+\ex
+  \begin{xlist}
+  \ex Punker (\PHplumedHead)
+  \ex Fisch (\PHtunny)
+  \ex Männchen (\PHchild)
+  \ex Äste (\PHplaneTree)
+  \ex Böcke (\PHram)
+  \ex Blätter (\textleaf)
+  \ex Uhren (\clock)
+  \ex Glocken (\bell)
+  \ex Fußbälle (\Football)
+  \ex Fahrräder (\Bicycle)
+  \ex Kaffetassen (\Coffeecup)
+  \ex Fabriken (\Industry)
+  \end{xlist}
+\end{exe}
+
+\subsection{Controls}
+
+\begin{exe}
+\ex
+  \begin{xlist}
+  \ex Bügeleisen (\IroningIII)
+  \ex Yingyangsymbole (\Yinyang)
+  \ex Fledermäuse (\Bat)
+  \ex Anarchiesymbole (\CircledA)
+  \ex Würfel (\epsdice{5})
+  \ex Springer (\symknight)
+  \ex Türme (\symrook)
+  \end{xlist}
+\end{exe}
+
+\subsection{Filler}
+
 % \printbibliography[heading=bibintoc]

### 2011-02-28 aux/material_exp2/make_basic.py

@@ -1,0 +1,113 @@
+from subprocess import *
+
+# define variable string elements
+
+colors = ["blue","red", "orange","brown","black"]
+plabels = ["\\Diamond", "\\Box", "\\alpha", "\\omega","\\mathrm{A}"]
+clabels = ["\\Box", "\\alpha", "\\omega"]
+
+# define text blocks
+
+file_header = """
+\\documentclass{article}
+
+\\usepackage[palatino]{mypackages}\\usepackage{mycommands}
+
+\\usepackage{verbatim}
+\\usepackage[active,tightpage]{preview}
+\\PreviewEnvironment{tikzpicture}
+\\setlength\\PreviewBorder{20pt}
+
+\\usetikzlibrary{shapes.geometric}
+\pgfdeclarelayer{foreground}
+\pgfsetlayers{background,main,foreground}
+
+\\begin{document}
+"""
+
+tikzheader = """\\begin{tikzpicture}[rounded corners,node distance = 3cm]
+
+    \\tikzset{ctype/.style={circle,thick,minimum
+      width=14mm},
+      htype/.style={},
+      ptype/.style={circle,draw=black!70,fill=blue!50,thick,minimum
+      width=8mm},
+      arrow/.style={-,very thick}}\n"""
+
+def powerset(seq):
+    if len(seq) > 0:
+        head = powerset(seq[:-1])
+        return head + [item + [seq[-1]] for item in head]
+    else:
+        return [[]]
+
+def make_periphery(hidden=False, connections = []):
+
+    directions = ["above left of = c0", "above of = c0", "above right of = c0",\
+                  "below right of = c0", "below of = c0", "below left of = c0"]
+
+    periphery = ""
+
+    for i in range(6):
+        periphery += "\\node [ptype, %s]  (p%s)   {};\n\n" % (directions[i],i)
+
+    for connection in connections:
+        periphery += '\\draw [arrow] (c0) to (p%s);\n\n' % str(connection)
+
+    if not hidden:
+        return periphery
+    else:
+        return periphery + """
+        
+         \\node at (0,-1.7) [semicircle,shape border rotate
+          =180,draw=black!70,fill=green!80, minimum size = 4cm]  {};
+    
+        """
+
+tikzbackground = """\\begin{pgfonlayer}{background}
+      \\node at (0,0) [circle,draw=black!70,fill=green!20,minimum size = 8.5cm] {};
+    \\end{pgfonlayer}"""
+
+def make_center(clabel=''):
[…]

### 2011-02-28 aux/material_exp2/make_labelled.py

@@ -1,0 +1,114 @@
+from subprocess import *
+
+# define variable string elements
+
+colors = ["blue","red", "orange","brown","black"]
+plabels = ["\\mathrm{A}", "\\mathrm{B}", "\\mathrm{C}", "\\mathrm{D}", "\\mathrm{E}", "\\mathrm{F}"]
+clabels = ["\\Box", "\\alpha", "\\omega"]
+
+# define text blocks
+
+file_header = """
+\\documentclass{article}
+
+\\usepackage[palatino]{mypackages}\\usepackage{mycommands}
+
+\\usepackage{verbatim}
+\\usepackage[active,tightpage]{preview}
+\\PreviewEnvironment{tikzpicture}
+\\setlength\\PreviewBorder{20pt}
+
+\\usetikzlibrary{shapes.geometric}
+\pgfdeclarelayer{foreground}
+\pgfsetlayers{background,main,foreground}
+
+\\begin{document}
+"""
+
+tikzheader = """\\begin{tikzpicture}[rounded corners,node distance = 3cm]
+
+    \\tikzset{ctype/.style={circle,thick,minimum
+      width=14mm},
+      htype/.style={},
+      ptype/.style={circle,draw=black!70,fill=blue!50,thick,minimum
+      width=8mm},
+      arrow/.style={-,very thick}}\n"""
+
+def powerset(seq):
+    if len(seq) > 0:
+        head = powerset(seq[:-1])
+        return head + [item + [seq[-1]] for item in head]
+    else:
+        return [[]]
+
+def make_periphery(hidden=False, nodes = [], connections = [],plabels=[]):
+
+    directions = ["above left of = c0", "above of = c0", "above right of = c0",\
+                  "below right of = c0", "below of = c0", "below left of = c0"]
+
+    periphery = ""
+
+    for i in nodes:
+        periphery += "\\node [ptype, %s]  (p%s)   {$%s$};\n\n" % (directions[i],i,plabels[i])
+
+    for connection in connections:
+        periphery += '\\draw [arrow] (c0) to (p%s);\n\n' % str(connection)
+
+    if not hidden:
+        return periphery
+    else:
+        return periphery + """
+        
+         \\node at (0,-1.7) [semicircle,shape border rotate
+          =180,draw=black!70,fill=green!80, minimum size = 4cm]  {};
+    
+        """
+
+tikzbackground = """\\begin{pgfonlayer}{background}
[…]

### 2011-02-28 aux/material_exp2/sentences.tex
target sentences and distractors for exp2

@@
 % sectioning
-\usepackage{sectsty}
-\chapterfont{\rmfamily\mdseries\Large\raggedleft}
-\sectionfont{\rmfamily\mdseries\large\nohang\centering}
-\subsectionfont{\rmfamily\mdseries\normalsize\nohang\centering}
-\subsubsectionfont{\rmfamily\mdseries\normalsize\itshape\nohang\centering}
-\paragraphfont{\rmfamily\mdseries\normalsize\textsc}
+% \usepackage{sectsty}
+% \chapterfont{\rmfamily\mdseries\Large\raggedleft}
+% \sectionfont{\rmfamily\mdseries\large\nohang\centering}
+% \subsectionfont{\rmfamily\mdseries\normalsize\nohang\centering}
+% \subsubsectionfont{\rmfamily\mdseries\normalsize\itshape\nohang\centering}
+% \paragraphfont{\rmfamily\mdseries\normalsize\textsc}
 
@@
     \begin{xlist}
+      \ex Alle der SYMBOLE sind mit einigen ihrer FORM verbunden.
+      \ex Alle der SYMBOLE sind mit \emph{einigen} ihrer FORM
+        verbunden.
+      \ex Alle der SYMBOLE sind nur mit \emph{einigen} ihrer FORM
+        verbunden.
+    \end{xlist}
+\end{exe}
+
+\begin{exe}
+  \ex
+    \begin{xlist}
       \ex Alle der Häkchen ($\checkmark$) sind mit einigen ihrer Kreise verbunden.
@@
 \begin{exe}
+\ex (base-line)
+  \begin{xlist}
+  \ex Das SYMBOL ist mit einigen seiner FORM verbunden.
+  \ex Das SYMBOL ist mit seinem SYMBOL2 oder SYMBOL3 verbunden.
+  \end{xlist}
+\ex (control for task)
+  \begin{xlist}
+  \ex Genau zwei der SYMBOLE 1 sind mit SYMBOL2 und SYMBOL3 verbunden.
+  \ex Genau zwei der SYMBOLE 1 sind mit allen ihrer FORM verbunden.
+  \end{xlist}
+\ex (ambige Sätze)
+  \begin{xlist}
+    \ex Es gibt blaue Dreiecke und Vierecke.
+    \ex Es gibt Dreiecke und Vierecke, die mit allen ihren FORMEN
+      verbunden sind.
+  \end{xlist}
+\end{exe}
+
+\subsection{Distractors}
+
+\begin{exe}
+  \ex
+    \begin{xlist}
+    \ex Wenn ein SYMBOL1 mit einem SYMBOL2 verbunden ist, dann ist
+      es auch mit einem SYMBOL3 verbunden.
+    \ex Alle SYMBOLE1 sind mit allen SYMBOLEN2 verbunden.
+    \ex Nur alle \emph{SYMBOLE1} sind mit allen SYMBOLEN2 verbunden.
+    \ex Alle SYMBOLE1 sind mit allen ihrer FORM verbunden.
+    \ex Nur alle \emph{SYMBOLE1} sind mit allen ihrer FORM verbunden.
+    \ex Kein SYMBOL ist mit nur einem SYMBOL2 verbunden.
+    \ex Alle FORMEN, die mit einem SYMBOL verbunden sind, sind FARBE.
+    \ex Nur SYMBOL1 und SYMBOL2 sind mit allen ihren FORMEN
+      verbunden.
+    \ex Nur SYMBOL1 und SYMBOL2 sind mit genau zwei ihrer FORMEN
+      verbunden.
+    \ex Nur alle \emph{FARBE} Sterne sind nicht mit ihren FORMEN
+      verbunden.
+    \ex Alle blauen \emph{SYMBOL} sind mit all ihren FORMEN
+      verbunden.
+    \ex Das SYMBOL1 ist nicht nur mit SYMBOL2 verbunden.
+    \ex Das SYMBOL1 hat \emph{keine} Verbindung.
+    \ex Wenn ein SYMBOL1 nur \emph{eine} Verbindung hat, dann ist es
+      nur mit seinem SYMBOL2 verbunden.
+    \ex Genau ein unverbundenes SYMBOL ist FARBE.
+    \ex Nur wenn ein SYMBOL FARBE ist, dann ist es mit allen seinen
+      FORMEN verbunden.
+    \ex Kein FARBE SYMBOL ist nur mit genau zwei seiner FORMEN
+      verbunden.
+    \ex Nur unverbundene SYMBOLE sind FARBE.
+    \ex Nur genau ein SYMBOL ist FARBE und unverbunden.
+    \ex Es gibt FARBE SYMBOLE, die mit nur genau einer ihrer FORM
+      verbunden ist.
+    \ex Kein SYMBOL ist nur mit SYMBOL1 oder SYMBOL2 verbunden.
+    \ex Kein \emph{SYMBOL}, das unverbunden ist, ist FARBE.
+    \end{xlist}
+\end{exe}
+
+\subsection{Extra Symbols}
+
+\begin{exe}
 \ex
@@
 
-\subsection{Filler}
-
 % \printbibliography[heading=bibintoc]

### 2011-03-01 aux/material_exp2/make_labelled.py
small changes in scripts

@@ -3,7 +3,8 @@ from subprocess import *
 # define variable string elements
 
 colors = ["blue","red", "orange","brown","black"]
-plabels = ["\\mathrm{A}", "\\mathrm{B}", "\\mathrm{C}", "\\mathrm{D}", "\\mathrm{E}", "\\mathrm{F}"]
+plabels = ["\\mathrm{A}", "\\mathrm{B}", "\\mathrm{C}",\
+           "\\mathrm{D}", "\\mathrm{E}", "\\mathrm{F}"]
 clabels = ["\\Box", "\\alpha", "\\omega"]
 
 # define text blocks

### 2011-03-01 aux/material_exp2/make_basic.py
scripts anpassen

@@ -1,10 +1,28 @@
 from subprocess import *
+import os
+import itertools
+
 
 # define variable string elements
 
-colors = ["blue","red", "orange","brown","black"]
-plabels = ["\\Diamond", "\\Box", "\\alpha", "\\omega","\\mathrm{A}"]
-clabels = ["\\Box", "\\alpha", "\\omega"]
+colors = ["blue","red", "yellow","green"]
+color_names = ["Blau","Rot", "Gelb","Gruen"]
+
+#colors = ["blue","red"]
+#color_names = ["Blau","Rot"]
+
+#plabels = ["\\text{\\SI}","\\leftmoon","\\text{\\blitze}","\\varheartsuit","\\text{\\ding{96}}","\\text{\epsdice{5}}"]
+#plabel_names = ["Sonne", "Mond","Blitz","Herz", "Blume","Wuerfel"]
+
+plabels = ["\\text{\\SI}","\\leftmoon","\\text{\\blitze}","\\varheartsuit"]
+plabel_names = ["Sonne", "Mond","Blitz","Herz"]
+
+#clabels = ["\\text{\\Letter}","\\text{\\Rightscissors}","\\text{\\ding{46}}","\\star","\\text{\\bell}","\\text{\\clock}"]
+#clabel_names = ["Brief","Schere", "Stifte","Sterne","Glocken","Uhren"]
+
+clabels = ["\\text{\\Letter}","\\text{\\Rightscissors}"]
+clabel_names = ["Brief","Schere"]
+
 
 # define text blocks
 
@@ -12,6 +30,17 @@ file_header = """
 \\documentclass{article}
 
 \\usepackage[palatino]{mypackages}\\usepackage{mycommands}
+
+\\usepackage[]{mathdesign}
+\\usepackage{MnSymbol}
+\\usepackage{ulsy}
+\\usepackage{wasysym}
+\\usepackage{ascii}
+\\usepackage{marvosym}
+\\usepackage{pifont}
+\\usepackage{phaistos}
+\\usepackage{epsdice}
+\\usepackage{skak}
 
 \\usepackage{verbatim}
 \\usepackage[active,tightpage]{preview}
@@ -25,14 +54,16 @@ file_header = """
 \\begin{document}
 """
 
-tikzheader = """\\begin{tikzpicture}[rounded corners,node distance = 3cm]
+def make_tikzheader(color):
+    return """\\begin{tikzpicture}[rounded corners,node distance = 3cm]
 
[…]

### 2011-03-01 aux/material_exp2/make_labelled.py

@@ -2,10 +2,23 @@ from subprocess import *
 
 # define variable string elements
 
-colors = ["blue","red", "orange","brown","black"]
-plabels = ["\\mathrm{A}", "\\mathrm{B}", "\\mathrm{C}",\
-           "\\mathrm{D}", "\\mathrm{E}", "\\mathrm{F}"]
-clabels = ["\\Box", "\\alpha", "\\omega"]
+#colors = ["blue","red", "yellow","green"]
+#color_names = ["Blau","Rot", "Gelb","Gruen"]
+
+colors = ["blue","red"]
+color_names = ["Blau","Rot"]
+
+#plabels = ["\\text{\\SI}","\\leftmoon","\\text{\\blitze}","\\varheartsuit","\\text{\\ding{96}}","\\text{\epsdice{5}}"]
+#plabel_names = ["Sonne", "Mond","Blitz","Herz", "Blume","Wuerfel"]
+
+plabels = ["\\text{\\SI}","\\leftmoon","\\text{\\blitze}","\\varheartsuit"]
+plabel_names = ["Sonne", "Mond","Blitz","Herz"]
+
+#clabels = ["\\text{\\Letter}","\\text{\\Rightscissors}","\\text{\\ding{46}}","\\star","\\text{\\bell}","\\text{\\clock}"]
+#clabel_names = ["Brief","Schere", "Stifte","Sterne","Glocken","Uhren"]
+
+clabels = ["\\text{\\Letter}","\\text{\\Rightscissors}"]
+clabel_names = ["Brief","Schere"]
 
 # define text blocks
 

### 2011-03-02 aux/material_exp2/make_basic.py
Exp2 Picture scripts

@@ -6,7 +6,7 @@ import itertools
 # define variable string elements
 
 colors = ["blue","red", "yellow","green"]
-color_names = ["Blau","Rot", "Gelb","Gruen"]
+color_names = ["B","R", "Y","G"]
 
 #colors = ["blue","red"]
 #color_names = ["Blau","Rot"]
@@ -72,7 +72,7 @@ def powerset(seq):
     else:
         return [[]]
 
-def make_periphery(hidden=False, labeled = False, connections = [],plabels=[],color_list=[]):
+def make_periphery(hidden=False, labeled = False, connections = [],labels=[],color_list=[]):
 
     if labeled:
         directions = ["above left of = c0", "above right of = c0",\
@@ -84,10 +84,9 @@ def make_periphery(hidden=False, labeled = False, connections = [],plabels=[],co
     periphery = "\\begin{pgfonlayer}{foreground}\n\n"
 
     if labeled:
-        print color_list
         for i in range(4):
             periphery += "\\node [p4type, ,draw=black!70,fill=%s!50,%s]\
-              (p%s)   {\\Huge{$%s$}};\n\n" % (color_list[i],directions[i],i,plabels[i])
+              (p%s)   {\\Huge{$%s$}};\n\n" % (colors[color_list[i]],directions[i],i,plabels[labels[i]])
     else:
         for i in range(6):
             periphery += "\\node [ptype, %s]  (p%s)   {};\n\n" % (directions[i],i)
@@ -149,31 +148,44 @@ file_footer = "\\end{document}"
 #        call(["pdflatex", file_name+".tex"])
 #        #call(["open", "-a", "Skim", file_name+".pdf"])
 
-# Generate Labeled 
 
-out_string = file_header
-for color_permutation in itertools.permutations(colors):
-    for j,clabel in enumerate(clabels):
-        pset6 = powerset(range(4))
-        pset3 = powerset(range(2))
-        for connections in pset6:
-            out_string += make_tikzheader("green") + tikzbackground + make_center(clabel)
-            out_string += make_periphery(hidden=False,labeled=True,\
-                                         connections=connections,plabels=plabels,color_list=color_permutation)
-            out_string += tikzbackground + tikzfooter
-        for connections in pset3:
-            out_string += make_tikzheader("green") + tikzbackground + make_center(clabel)
-            out_string += make_periphery(hidden=True,labeled=True,\
-                                         connections=connections,plabels=plabels,color_list=color_permutation)
[…]

### 2011-03-02 aux/material_exp2/make_basic.py
security commit

@@ -11,17 +11,22 @@ color_names = ["B","R", "Y","G"]
 #colors = ["blue","red"]
 #color_names = ["Blau","Rot"]
 
-#plabels = ["\\text{\\SI}","\\leftmoon","\\text{\\blitze}","\\varheartsuit","\\text{\\ding{96}}","\\text{\epsdice{5}}"]
-#plabel_names = ["Sonne", "Mond","Blitz","Herz", "Blume","Wuerfel"]
+plabels = ["\\text{\\SI}","\\leftmoon","\\text{\\blitze}","\\varheartsuit","\\text{\\ding{96}}","\\text{\epsdice{5}}"]
+plabel_names = ["Sonne", "Mond","Blitz","Herz", "Blume","Wuerfel"]
 
-plabels = ["\\text{\\SI}","\\leftmoon","\\text{\\blitze}","\\varheartsuit"]
-plabel_names = ["Sonne", "Mond","Blitz","Herz"]
+#plabels = ["\\text{\\SI}","\\leftmoon","\\text{\\blitze}","\\varheartsuit"]
+#plabel_names = ["Sonne", "Mond","Blitz","Herz"]
 
-#clabels = ["\\text{\\Letter}","\\text{\\Rightscissors}","\\text{\\ding{46}}","\\star","\\text{\\bell}","\\text{\\clock}"]
-#clabel_names = ["Brief","Schere", "Stifte","Sterne","Glocken","Uhren"]
+clabels = ["\\text{\\Letter}","\\text{\\Rightscissors}","\\text{\\ding{46}}","\\star","\\text{\\bell}","\\text{\\clock}"]
+clabel_names = ["Brief","Schere", "Stifte","Sterne","Glocken","Uhren"]
 
-clabels = ["\\text{\\Letter}","\\text{\\Rightscissors}"]
-clabel_names = ["Brief","Schere"]
+#clabels = ["\\text{\\Letter}","\\text{\\Rightscissors}"]
+#clabel_names = ["Brief","Schere"]
+
+shapes = ["circle","regular polygon, regular polygon sides=4",\
+          "regular polygon, regular polygon sides=3",\
+          "regular polygon, regular polygon sides=5"]
+shape_names = ["Kreise", "Vierecke", "Dreiecke", "Fuenfecke"]
 
 
 # define text blocks
@@ -54,16 +59,15 @@ file_header = """
 \\begin{document}
 """
 
-def make_tikzheader(color):
+def make_tikzheader():
[…]

### 2011-03-07 text/exp1.tex

\documentclass[a4paper,10pt]{article}

\usepackage{t1enc}
\usepackage{linguex}
\usepackage{harvard}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage{eurosym}

%opening
\title{Exp1}
\author{Fabian Schlotterbeck}

\begin{document}

\maketitle

\section{Introduction}
The present experiment was a picture verification experiment. It served two purposes. Firstly, we wanted to see whether the findings of \citeasnoun{Chemlatoappear} could be replicated using a different method. In particular, we collected truth value judgments about set diagrams instead of acceptability ratings and also included distractor items in order to keep participants from developing strategies. Secondly, we tested another type of linguistic construction which has not yet been investigated experimentally. These were constructions  like \Next containing {\it every} embeded under the non-monotone operator {\it exactly one}. The scalar item {\it every} is the utmost item in its scale. There has been a debate about whether constructions like these should give rise to global scalar implicatures like in \NNext \citeaffixed{}{see}.

\ex. \a.[]   Exactly one student was parsised by all the teachers.

\ex. \a.[$\rightsquigarrow$] It is not true that exactly one student was praised by some teachers.

\subsection{Procedure}
The present experiment was part of a dual task experiment employing picture verification and a sternberg task \cite{Sternberg1966}. In addition to the picture verification task participants had to solve a memory task in some trials. In the {\it high load} condition participants had to remember six letters while performing the picture verification. In the {\it low load} condition they had to remember one letter and in the {\it no load} condition they didn't have to remember anything while they were performing the picture verification. In the {\it memory only} conditions they only had to perform a memory task (ie. remember one or six letters) but no picture verification. All the critical items of the present experiment were presented in the {\it no load} condition. Only distractor items were presented in one of the dual task conditions.

In each trial participants were first asked to indicate readiness by pressing a button. In the {\it no load} condition, after they had pressed the button an  asterisk was flashed on the screen six times within $7.2s$. Then a sentence and a picture were presented simultaneously. Within $12s$ participants had to judge whether the sentence was true with respect to the picture. They indicated their judgment by pressing one of two buttons. After they had provided their judgment the next trial started automatically. If they did not respond within twelve seconds, the next trial was started. Judgments and reaction times were logged.

In the {\it low load} and {\it high load} condition a trial looked similar to a trial in the {\it no load} condition except for two things. Firstly, in the dual task conditions instead of asterisks letters were flashed on the screen. Secondly, after finishing the picture verification task a question appeared on the screen probing for a letter. Participants had to indicate by pressing a button whether they thought the letter had been present in the array from the beginning of the trial.

Except for one thing, the {\it memory only} trials were identical to the dual task trials. In {\it memory only} trials the picture verification part was replaced with a blank screen. That is, in the middle of such trials the screen stayed blank for $5s$.

The experiment started with a practise session consisting of $25$ trials devided into three blocks (1st block: memory task only, ten trials; 2nd block: picture verification only, five trials; 3rd block: dual task, ten trials). Then one list consisting of 249 trials devided into three blocks was presented. An experimental session took about 75 minutes. During the whole experiment no feedback was provided to the participants.

\subsection{Materials}

There were three sentence conditions. An example of each sentence condition is given in \ref{ex:AE}$-$\ref{ex:EA}. We will refer to the sentence type in \ref{ex:AE} as the $\forall \exists$ type of sentence. Such sentences contained the determiner {\it einige} (some) embedded under {\it jeder} (every). Sentences like the one in \ref{ex:EE}  contained {\it einige} embedded under {\it genau ein} (exactly one), they will be referred to as $\exists ! \exists$ sentences. Finally, sentences like in \ref{ex:EA}  containig {\it jeder} embedded under {\it genau ein} will be referred to as $\exists ! \forall$.  Within every one sentence the two quantificational determiners were separated by a clause boundary as to enforce linear scope readings. We constructed 48 experimental items, so  48 sentences of each type were constructed yielding a total of 144 sentences.

Because of the logical relations between the different readings of the sentences in \ref{ex:AE}$-$\ref{ex:EA}, it was not possible to construct all types of disambiguating diagrams one might wish to test. However, testing some of the possible sentence-picture combinations can already provide crucial information about the status of global and local implicatures of embedded scalar items. Below we will introduce the picture materials for each sentence condition in turn. Every sentence was paired with diagrams of four types. In total, this yielded twelve conditions and 576 pictures. The conditions were distributed over twelve lists accordding to a latin square design ensuring that in each list every item was only present in one condition. In addition to the target sentences, 201 (?) distractors were included in each list. Of these, $n$ were {\it memory only} trials. One third (?) of them was presented in the {\it no load} condition, another third (?) in the {\it low load} and $n$ in the {\it high load} condition. The picture verification of {\it n} of the distractor items was intended to yield a "yes true" response, $n$ were false.
\small
\exg. \label{ex:AE}F{\"u}r jeden dieser Umweltsch{\"u}tzer gilt: er  boykottierte einige dieser Gro{\ss}konzerne.\\
For each of\ these environmentalists holds: he boycotted some of\ these conglomerates.\\
 Each of\ these environmentalists boycotted some of\ these conglomerates.\\

\exg. \label{ex:EE}F{\"u}r genau einen dieser Umweltsch{\"u}tzer gilt: er bykottierte einige dieser Gro{\ss}konzerne.\\
For exactly one of\ these environmentalists holds: he boycotted some of\ these conglomerates.\\
 Exactly one of\ these environmentalists boycotted some of\ these conglomerates.\\

\exg. \label{ex:EA}F{\"u}r genau einen dieser Umweltsch{\"u}tzer gilt: er bykottierte jeden dieser Gro{\ss}konzerne.\\
For exactly one of\ these environmentalists holds: he boycotted each of\ these conglomerates.\\
Exactly one of\ these environmentalists boycotted eachl of\ these conglomerates.\\

\normalsize

\subsubsection{Diagrams for $\forall \exists$ sentences}

The $\forall \exists$ sentences were paired with diagrams like those in Figure \ref{fig:AE}. Figure \ref{fig:AE-LITGLBLOC} is compatible with the global implicature, the local implicature and the literal meaning of \ref{ex:AE}. Using the terminology of \citename{Chemlatoappear} we will refer to such diagrams as {\it strong} diagrams. In contrast to {\it strong} diagrams, Figure \ref{fig:AE-LITGLB} is not compatible with the local implicature ({\it weak} diagrams) and Figure \ref{fig:AE-LIT} is only compatible with the literal meaning of the sentence ({\it literal} diagrams). Finally, Figure \ref{fig:AE-false} is not compatible with the sentence at all ({\it false} diagrams).  These four conditions constitute a replication of \citeasnoun[Experiment 1]{Chemlatoappear}.

\begin{figure}[ht]
\centering
\subfigure[{\it strong}: compatible with global, local and literal interpretation]{
\includegraphics[width=3.8cm]{./pictures/Umweltschuetzer01.eps}
\label{fig:AE-LITGLBLOC}
}
\subfigure[{\it weak}: compatible with global, literal but not with local interpretation]{
\includegraphics[width=3.8cm]{./pictures/Umweltschuetzer02.eps}
\label{fig:AE-LITGLB}
}
\subfigure[{\it literal}: Only compatible with the literal meaning]{
\includegraphics[width=3.8cm]{./pictures/Umweltschuetzer03.eps}
\label{fig:AE-LIT}
}
\subfigure[{\it false}: Not compatible with the sentence at all]{
\includegraphics[width=3.8cm]{./pictures/Umweltschuetzer04.eps}
\label{fig:AE-false}
}
\caption[Optional caption for list of figures]{Diagrams for $\forall \exists$ sentences}
\label{fig:AE}
\end{figure}

\subsubsection{Diagrams for $\exists! \exists$ sentences}

The $\exists! \exists$ sentences were paired with digrams like those in Figure \ref{fig:EE}. The diagram in Figure \ref{fig:EE-LITGLBLOC} is compatible with all three interpretations.  We use \possessivecite{Chemlatoappear} term {\it all} to refer to such diagrams. Figure\ref{fig:EE-LOC} is only compatible with the local interpretation ({\it local} diagrams) and Figure \ref{fig:EE-LIT} is only compatible with the literal interpretation ({\it literal} diagrams). Figure \ref{fig:EE-false} is plainly false with respect to the sentence in \ref{ex:EE} ({\it false} diagrams). These four conditions replicate  \citeasnoun[Experiment 2]{Chemlatoappear}.

\begin{figure}[ht]
\centering
\subfigure[{\it all}: compatible with global, local and literal interpretation]{
\includegraphics[width=4cm]{./pictures/Umweltschuetzer05.eps}
\label{fig:EE-LITGLBLOC}
}
\subfigure[{\it local}: compatible with local interpretation only]{
\includegraphics[width=4cm]{./pictures/Umweltschuetzer06.eps}
\label{fig:EE-LOC}
}
\subfigure[{\it literal}: compatible with literal interpretation only]{
\includegraphics[width=4cm]{./pictures/Umweltschuetzer07.eps}
\label{fig:EE-LIT}
}
\subfigure[{\it all}: not compatible at all]{
\includegraphics[width=4cm]{./pictures/Umweltschuetzer08.eps}
\label{fig:EE-false}
}
\caption[Optional caption for list of figures]{Diagrams for $\exists! \exists$ sentences}
\label{fig:EE}
\end{figure}

\subsubsection{Diagrams for $\exists! \forall$ sentences}

The $\exists! \forall$ sentences were paired with digrams like those in Figure \ref{fig:EA}. Figure \ref{fig:EA-LIT} is only true under the literal reading ({\it literal} diagrams) while  Figure \ref{fig:EA-LITGLB} is only true with respect to the global implicature ({\it global} diagrams), denying the weaker scalar alternative containig {\it einige} (some). Diagrams like those in Figures \ref{fig:EA-FALSE1} and \ref{fig:EA-FALSE2} were not compatible with the $\exists! \forall$ sentences. Figure \ref{fig:EA-FALSE1} is incompatible because there are too few connections. Figure \ref{fig:EA-FALSE2} is incompatible because there are too many connections. We used two types of incompatible pictures only because of thechnical reasons.

\begin{figure}[ht]
\centering
\subfigure[compatible with literal meaning and global implicature]{
\includegraphics[width=4cm]{./pictures/Umweltschuetzer09.eps}
\label{fig:EA-LIT}
}
\subfigure[compatible with literal interpretation only]{
\includegraphics[width=4cm]{./pictures/Umweltschuetzer10.eps}
\label{fig:EA-LITGLB}
}
\subfigure[false because of insufficient connections]{
\includegraphics[width=4cm]{./pictures/Umweltschuetzer11.eps}
\label{fig:EA-FALSE1}
}
\subfigure[false because of to many connections]{
\includegraphics[width=4cm]{./pictures/Umweltschuetzer12.eps}
\label{fig:EA-FALSE2}
}
\caption[Optional caption for list of figures]{Diagrams for $\exists! \forall$ sentences}
\label{fig:EA}
\end{figure}

\subsection{Participants}
60 native German speakers (40 female, mean age: $24$, ranging between $20$ and $40$) from the University of T{\"u}bingen participated in the study. Participants were na\"ive to the purpose of the study. They were paid \euro{10} compensation.

\subsection{Hypotheses and Predictions}
Since most of the present experiment replicates the study of \citeasnoun{Chemlatoappear}, the major hypotheses and predictions can be found therein. We will shortly summarize the main points here. In monotone increasing environments local implicatures do generally imply global implicatures, but not reversely.  In these cases the distinction between local and global accounts is rather subtle. It is hard to test the existence of locally drawn implicatures in upward entailing contexts empirically \citeaffixed{Chemlatoappear,Geurts2009}{see, however,}. The same applies to the existence of global implicatures in upward entailing contexts. Generally, if one reading implies another one and both are rated equally, nothing can be concluded since the sentences may just be ambiguous.

If we do find evidence for the existence of global scalar implicatures, this does at least provide evidence that strict locality is not enough. This is because when applied to sentences containing embedded scalar items, local accounts are not able to generate global implicatures. If implicature computation was strictly local, global implicatures should not be drawn.

The heterogenity of global accounts is another complicating factor.  Global accounts differ with respect to the readings they assume to be possible in upward entailing environments. Some global accounts \citeaffixed{}{eg.} posit global strategies that produce readings equivalent to eg. the local implicature of $\forall \exists$ sentences. Other more restricted global accounts do not manage to generate any of the local readings. Therefore, it is not possible to decide between globality and locality by testing scalar items in upward entailing contexts. Even clear evidence for so called local readings does only discard some global accounts, but not globality in general.

In non-monotone contexts implication from local to global readings does not hold. Furthermore, no global account can generate any of the local readings in such contexts. Therefore, as \citename{Chemlatoappear} point out, non-monotone contexts are a good test case. If local implicatures are detected in such environments, strict globality is clearly insufficient.

Yet another distinction within the global accounts can be drawn on the basis of sentences like \ref{ex:EA} which have not been investigated experimentally thus far. Replacing {\it jeder} (every) in \ref{ex:EA} with any other item from its scale does not yield a sentence that entails the original one. Therefore, most theories do not consider this substitution an alternative to be negated by implicature. Some global accounts do, however, allow for such implicatures. Luckily, for sentences like \ref{ex:EA}  global readings do not imply literal readings. Therefore acceptance of global readings of such sentences would have straightforward theorectical implications. We will now spell out the predictions for each sentence condition in some detail.

\subsubsection{Predictions for $\exists! \forall$ sentences}
Local accounts let us predict that {\it strong} diagrams are accepted more often than {\it literal} ones.  Furthermore, they do not predict any difference between acceptance of {\it literal} and {\it weak} diagrams. Global accounts, on the other hand, predict that {\it  weak} diagrams are accepted more often than {\it literal} diagrams. At least more restricted global accounts do not predict any difference between {\it strong} and {\it weak} diagrams.

\subsubsection{Predictions for $\exists! \forall$ sentences}
Global accounts predict that {\it all} diagrams are rated better than {\it literal} diagrams. They cannot explain more acceptance of {\it local} diagrams than of {\it false} diagrams. Local accounts predict both {\it all} and {\it local} diagrams to be rated better than {\it litaral} and false {\it diagrams}.

\subsubsection{Predictions for $\exists! \forall$ sentences}
Some global accounts would predict {\it global} pictures to be rated better than {\it literal} pictures. Other global accounts do not predict any difference. Since the literal reading is true in both types of diagrams, they should be rated better than {\it false1} and {\it false2}.

\subsection{Results}

Overall participants were able to solve the task. In the distractor items the picture verification was done accurately in $88\%$ ($sd: 33\%$) of the cases. All participants were above $70\%$ and significantly better than chance. On average it took participants $4989ms$ ($sd:2176ms$) to come up with their answer in the filler trials. We will now consider results for the three sentence conditions in turn.

\subsubsection{Results for $\exists! \forall$ sentences}
The judgment pattern we obtained for $\exists! \forall$ sentences is depicted in Figure \ref{fig:EABars}. The {\it strong} diagrams were judged to be true in $90\%$ of the cases, {\it weak} diagrams received "yes" judgments in $79\%$ , {\it literal} diagrams in  $72\%$  and {\it false} in $0.9\%$.  A logit mixed effects model with binomial link function containing a fixed effect of {\it diagram} as well as random effects of items and participants revealed a clear effect of {\it diagram}. In particular {\it false}, {\it literal} and {\it weak} diagrams all received fewer "yes" judgments than {\it strong} diargams (all $p<.001$).  Another logit mixed effects model only modelling data for {\it literal} and {\it weak} diagrams also revealed an reliable effect of {\it diagram} (p<.05). Finally, a model only considering  {\it false} and {\it literal} diagrams also revealed a significant effect of {\it diagram} (p<.001).

\begin{figure}[ht]
\centering
\subfigure[$\forall\exists$ sentences]{
\includegraphics[width=3.92cm]{../data/JudgmentsAllSomeBars.eps}
\label{fig:EABars}
}
\subfigure[$\exists! \exists$ sentences]{
\includegraphics[width=3.5cm]{../data/JudgmentsExactlySomeBars.eps}
\label{fig:EEBars}
}
\caption[Optional caption for list of figures]{Mean judgments}
\label{fig:Bars}
\end{figure}

\subsubsection{Results for $\exists! \exists$ sentences}
The response pattern for $\exists! \exists$ sentences is presented in Figure \ref{fig:EEBars}. Unsurprisingly, these sentences were accepted as truthfull description of {\it false} diagrams in only $0.8\%$ of all cases. The {\it local} diagrams received  "yes" responses in $20\%$, {\it literal} in $71\%$ and {\it all} in $93\%$ of the time. A logit mixed effects model with {\it diagram} as fixed effect as well as item and participant as random effects revealed a signficant effect of {\it diagram}. The {\it all}, {\it literal} and {\it local} diagrams were all accepted more often than the {\it false} diagram (all $p<.001$). A simpler model only considering {\it local} and {\it literal} diagrams reveald a reliable effect of {\it diagram} (p<.001) as did a model only considering {\it literal} and {\it all} diagrams (p<.001).

\subsubsection{Tendency for acceptance of diagrams compatible with local readings}
Participants who accepted {\it local} diagrams together with $\exists! \exists$ sentences also on average made a greater difference between {\it strong} and {\it weak} diagrams when they were judging $\forall \exists$ sentences. This is reflected in a significant positive correlation between these two variables. The first variable is the proportion of "yes" responses per participant to the {\it local} diagrams in the $\exists! \exists$ sentences. The second one is the difference per participant between the proportion of "yes" responses to {\it strong} and {\it weak} diagrams in the $\exists! \exists$ sentences. This correlation ($p<.001$) is visualized in Figure \ref{fig:cor}.

\begin{figure}[t]
\begin{center}
\includegraphics[width=3.92cm]{../data/KorrelationScatterPlot.eps}
\end{center}
\label{fig:cor}
\caption{Correlation}
\end{figure}

\bibliographystyle{harvard}
\bibliography{ESI}
\end{document}

### 2011-03-10 aux/material_exp2/make_basic.py
make label changes

@@ -60,7 +60,7 @@ file_header = """
 """
 
 def make_tikzheader():
-    return """\\begin{tikzpicture}[rounded corners,node distance = 3cm]
+    return """\\begin{tikzpicture}[node distance = 3cm]
 
     \\tikzset{ctype/.style={circle,thick,minimum
       width=18mm},
@@ -131,27 +131,27 @@ file_footer = "\\end{document}"
 ### Generate Unlabelled ###
 ###########################
 
-for s,shape in enumerate(shapes):
-    for c,color in enumerate(colors):    
-        for j,clabel in enumerate(clabels):
-            out_string = file_header
-            pset6 = powerset(range(6))
-            pset3 = powerset(range(3))
-            for connections in pset6:
-                out_string += make_tikzheader() + tikzbackground + make_center(clabel)
-                out_string += make_periphery(hidden=False,connections=connections,shape=shape)
-                out_string += tikzbackground + tikzfooter
-            for connections in pset3:
-                out_string += make_tikzheader() + tikzbackground + make_center(clabel)
-                out_string += make_periphery(hidden=True,connections=connections,shape=shape)
-                out_string += tikzbackground + tikzfooter
-            out_string += file_footer
-            file_dir = os.path.join(os.path.dirname(__file__), 'Pics','Unlabeled')
-            file_name = os.path.join(file_dir, clabel_names[j] + "-" + shape_names[s] + "-" +color_names[c])
-            f = open(file_name+'.tex','w')
-            f.write(out_string)
-            f.close()
-            os.chdir(file_dir)
+#for s,shape in enumerate(shapes):
+#    for c,color in enumerate(colors):    
+#        for j,clabel in enumerate(clabels):
+#            out_string = file_header
+#            pset6 = powerset(range(6))
+#            pset3 = powerset(range(3))
+#            for connections in pset6:
+#                out_string += make_tikzheader() + tikzbackground + make_center(clabel)
+#                out_string += make_periphery(hidden=False,connections=connections,shape=shape,color=color)
+#                out_string += tikzbackground + tikzfooter
+#            for connections in pset3:
+#                out_string += make_tikzheader() + tikzbackground + make_center(clabel)
+#                out_string += make_periphery(hidden=True,connections=connections,shape=shape,color=color)
+#                out_string += tikzbackground + tikzfooter
+#            out_string += file_footer
+#            file_dir = os.path.join(os.path.dirname(__file__), 'Pics','Unlabeled')
[…]

### 2011-03-22 aux/material_exp2/Pics/Sequences/Alle-Einige/seguence.tex

\documentclass{article}

\usepackage[palatino]{mypackages}\usepackage{mycommands}

\usepackage{verbatim}
\usepackage[active,tightpage]{preview}
\PreviewEnvironment{tikzpicture}
\setlength\PreviewBorder{5pt}

\begin{document}

\begin{tikzpicture}[rounded corners]

  \node at (6,18) {\Huge{Alle der Briefe sind mit einigen ihrer Kreise verbunden.}};

  \node at (0,0) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (12,0) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (12,12) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (0,12) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (0,-6)
  {\Huge{Wahr}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (6,-6)
  {\Huge{Falsch}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (12,-6) {\Huge{Mehr Info}};

\end{tikzpicture}

\begin{tikzpicture}[rounded corners]

  \node at (6,18) {\Huge{Alle der Briefe sind mit einigen ihrer Kreise verbunden.}};

  \node at (0,0) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (12,0) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (12,12) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (0,12) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (0,-6)
  {\Huge{Wahr}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (6,-6)
  {\Huge{Falsch}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (12,-6) {\Huge{Mehr Info}};

\end{tikzpicture}

\begin{tikzpicture}[rounded corners]

  \node at (6,18) {\Huge{Alle der Briefe sind mit einigen ihrer Kreise verbunden.}};

  \node at (0,0) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (12,0) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (12,12) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (0,12) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (0,-6)
  {\Huge{Wahr}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (6,-6)
  {\Huge{Falsch}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (12,-6) {\Huge{Mehr Info}};

\end{tikzpicture}

\begin{tikzpicture}[rounded corners]

  \node at (6,18) {\Huge{Alle der Briefe sind mit einigen ihrer Kreise verbunden.}};

  \node at (0,0) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (12,0) {\includegraphics{56_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (12,12) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (0,12) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (0,-6)
  {\Huge{Wahr}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (6,-6)
  {\Huge{Falsch}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (12,-6) {\Huge{Mehr Info}};

\end{tikzpicture}

\begin{tikzpicture}[rounded corners]

  \node at (6,18) {\Huge{Alle der Briefe sind mit einigen ihrer Kreise verbunden.}};

  \node at (0,0) {\includegraphics{64_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (12,0) {\includegraphics{56_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (12,12) {\includegraphics{24_pdfsam_Brief-Kreise-Blau.pdf}};

  \node at (0,12) {\includegraphics{8_pdfsam_Brief-Kreise-Blau.pdf}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (0,-6)
  {\Huge{Wahr}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (6,-6)
  {\Huge{Falsch}};

  \node[draw=black!80,fill=blue!30,ultra thick] at (12,-6) {\Huge{Mehr Info}};

\end{tikzpicture}

\end{document}

### 2011-03-22 aux/material_exp2/Pics/Sequences/GenauEin-Einige/seguence.tex

--- 2011-03-22 aux/material_exp2/Pics/Sequences/Alle-Einige/seguence.tex
@@
 
-  \node at (6,18) {\Huge{Alle der Briefe sind mit einigen ihrer Kreise verbunden.}};
+  \node at (6,18) {\Huge{Genau einer der Briefe ist mit einigen seiner Kreise verbunden.}};
 
@@
 
-  \node at (6,18) {\Huge{Alle der Briefe sind mit einigen ihrer Kreise verbunden.}};
+  \node at (6,18) {\Huge{Genau einer der Briefe ist mit einigen seiner Kreise verbunden.}};
 
-  \node at (0,0) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (0,0) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};
 
-  \node at (12,0) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (12,0) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};
 
-  \node at (12,12) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (12,12) {\includegraphics{64_pdfsam_Brief-Kreise-Blau.pdf}};
 
-  \node at (0,12) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (0,12) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};
 
@@
 
-  \node at (6,18) {\Huge{Alle der Briefe sind mit einigen ihrer Kreise verbunden.}};
+  \node at (6,18) {\Huge{Genau einer der Briefe ist mit einigen seiner Kreise verbunden.}};
 
-  \node at (0,0) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (0,0) {\includegraphics{31_pdfsam_Brief-Kreise-Blau.pdf}};
 
-  \node at (12,0) {\includegraphics{56_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (12,0) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};
 
-  \node at (12,12) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (12,12) {\includegraphics{64_pdfsam_Brief-Kreise-Blau.pdf}};
 
-  \node at (0,12) {\includegraphics{72_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (0,12) {\includegraphics{105_pdfsam_Brief-Kreise-Blau.pdf}};
 
@@
 
-  \node at (6,18) {\Huge{Alle der Briefe sind mit einigen ihrer Kreise verbunden.}};
+  \node at (6,18) {\Huge{Genau einer der Briefe ist mit einigen seiner Kreise verbunden.}};
 
-  \node at (0,0) {\includegraphics{64_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (0,0) {\includegraphics{31_pdfsam_Brief-Kreise-Blau.pdf}};
 
-  \node at (12,0) {\includegraphics{56_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (12,0) {\includegraphics{64_pdfsam_Brief-Kreise-Blau.pdf}};
 
-  \node at (12,12) {\includegraphics{24_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (12,12) {\includegraphics{64_pdfsam_Brief-Kreise-Blau.pdf}};
 
-  \node at (0,12) {\includegraphics{8_pdfsam_Brief-Kreise-Blau.pdf}};
+  \node at (0,12) {\includegraphics{64_pdfsam_Brief-Kreise-Blau.pdf}};
 

### 2011-07-18 text/EXC_textbox/EXC_textbox.tex
EXC textbox

\documentclass[fleqn,reqno,10pt]{article}

%========================================
% Packages
%========================================

\usepackage[]{mypackages}

%\usepackage[natbib=true,style=authoryear-comp,backend=bibtex,doi=false,url=false]{biblatex}

\bibliography{MyRefGlobal}

%\usepackage[garamond]{mathdesign}

%========================================
% Theorem Environments
%========================================

\usepackage{myenvironments}

%========================================
% Commands
%========================================

\usepackage{mycommands}
%========================================
% Page Layout
%========================================
% \renewcommand{\baselinestretch}{1.1} % multiplies vertical distance between lines in a paragraph
% \setlength{\parskip}{1ex plus 0.4ex minus 0.1ex}
% \addtolength{\voffset}{-1.7cm} \addtolength{\hoffset}{-1.5cm}
% \addtolength{\textwidth}{3.1cm} \addtolength{\textheight}{2.3cm}
% \addtolength{\voffset}{-1cm} \addtolength{\hoffset}{-0.5cm}
% \addtolength{\textwidth}{1cm} \addtolength{\textheight}{2cm}
% \setlength{\parindent}{0cm} % set paragraph indentation

%========================================
% More Layout
%========================================

% Itemize
\renewcommand{\labelitemi}{\large{$\mathbf{\cdot}$}}    % itemize symbols
\renewcommand{\labelitemii}{\large{$\mathbf{\cdot}$}}
\renewcommand{\labelitemiii}{\large{$\mathbf{\cdot}$}}
\renewcommand{\labelitemiv}{\large{$\mathbf{\cdot}$}}

% Description
\renewcommand{\descriptionlabel}[1]{\hspace\labelsep\textsc{#1}}

% Figure Captions
\usepackage{caption} % use corresponding myfiguresize!
\setlength{\captionmargin}{20pt}
\renewcommand{\captionfont}{\small}
\setlength{\belowcaptionskip}{7pt} % standard is 0pt

% Equationnumbering
%\numberwithin{equation}{section}

% sectioning
\usepackage{sectsty}
\chapterfont{\rmfamily\mdseries\Large\raggedleft}
\sectionfont{\rmfamily\mdseries\large\nohang\centering}
\subsectionfont{\rmfamily\mdseries\normalsize\nohang\centering}
\subsubsectionfont{\rmfamily\mdseries\normalsize\itshape\nohang\centering}
\paragraphfont{\rmfamily\mdseries\normalsize\textsc}

% for indentation of section headings:
%\sectionfont{\hspace*{-2.3em}\rmfamily\mdseries\bfseries\large\nohang\raggedright}

%========================================
% Document
%========================================

\title{Processing of Scalar Items in Embedded Positions}

\author{Petra Augurzky, Michael Franke \& Fabian Schlotterbeck}
\date{}

\begin{document}

\maketitle

\textbf{Scalar implicatures} are inferences such as from
(\ref{bsp:SI_Kiki_Target}) to (\ref{bsp:SI_Kiki_Implicature}). These
inference hinge on comparing what the speaker \emph{actually} said
with what she \emph{could have said}. Roughly speaking, since the
determiner ``all'' is a salient alternative to the determiner ``some''
that was used in (\ref{bsp:SI_Kiki_Target}), the inference in
(\ref{bsp:SI_Kiki_Implicature}) is licensed.

\noindent \begin{minipage}{0.5\linewidth}
  \begin{exe}
  \ex  \label{bsp:SI_Kiki_Target} Some of my friends are
    bald.
  \end{exe}
\end{minipage}
\begin{minipage}{0.5\linewidth}
  \begin{exe}
  \ex  \label{bsp:SI_Kiki_Implicature} Not all of my friends are
    bald.
  \end{exe}
\end{minipage}

\noindent Recently there has been renewed interest in the question
what inferences arise from utterances where scalar items like ``some''
occur in embedded position
\citep[cf.][]{Cohen1971:Some-Remarks-on,Landman1998:Plurals-and-Max,Chierchia:2004_ScalarImplicatures,Magri2009:A-Theory-of-Ind}. For
example, a sentence like (\ref{bsp:AllSome}a) could get a \textbf{global
enrichment} as in (\ref{bsp:AllSome_Implicature_Global}) by comparing it to the whole alternative utterance in
(\ref{bsp:AllSome}b), or it could be strengthened to a reading as in
(\ref{bsp:AllSome}c) where the scalar item ``some'' gets a \textbf{local
enrichment} in the scope of another logical operator. 
\noindent \begin{minipage}{0.4\linewidth}
\begin{exe}
\ex \label{bsp:AllSome} All of the students read
\end{exe}
\end{minipage}
\begin{minipage}{0.3\linewidth}
  a. some of the books.
\end{minipage}
\begin{minipage}{0.3\linewidth}
  b. all of the books.
\end{minipage}
\noindent \begin{minipage}{0.4\linewidth}
 $ $ 
\end{minipage}
\begin{minipage}{0.6\linewidth}
  c. some but not all of the books.
\end{minipage}
\begin{minipage}{1.0\linewidth}
  \begin{exe}
  \ex \label{bsp:AllSome_Implicature_Global} All read some and some did
    not read all. 
  \end{exe}
\end{minipage}

\noindent Empirical evidence on the availability of either global and
local enrichments in relevant constructions is sparse and, where it
exists, not unanimous
\citep{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}.
The reason is that global and local enrichments are not locally
independent and therefore standard picture verification tasks run into
difficulties because we cannot keep the properties of the visual
stimuli constant across to-be-compared conditions. In cooperation
between the \acro{sfb} and the \acro{sfs}, we therefore designed an
amended picture verification task where subjects had to sequentially
unveil visual information if necessary for a truth-value judgement. We
also studied \textbf{the effects of prosody on pragmatic enrichments}
and found that global enrichments are hardly attested, while local
enrichments occur seldom with neutral prosody, but more frequent if an
embedded scalar items is intonationally marked. In future work we
intend to extend the developed paradigm beyond embedding quantifiers
``all'' and ``exactly one'' to other quantifiers and also modal
expressions and to probe more deeply into the effect prosody on
pragmatic interpretation.

\printbibliography[heading=bibintoc]

\end{document}

### 2012-05-21 text/paper/paper.tex
paper initial import

\documentclass[fleqn,reqno,10pt]{article}

\usepackage{myarticlestyledefault}

\title{Scalar Items in Embedded Position: {A}nother Experimental Approach}
\author{Fabian Schlotterbeck, Michael Franke and Petra Augurzky}
\date{}

\begin{document}
\maketitle

\begin{abstract}
  \dots make concrete \dots
\end{abstract}

\svnInfo $Id: paper.tex 205 2012-04-29 16:26:54Z micha $

\printbibliography[heading=bibintoc]

\end{document}

### 2012-05-21 text/paper/paper.tex
paper initial import
paper messing with svnInfo
paper svnInfo fiddling
paper sec com

@@
 \usepackage{myarticlestyledefault}
+
+\usepackage{mypackages}
+\usepackage{mycommands}
+\usepackage{myenvironments}
+
+\usepackage[]{svninfo}
+
+\newcommand{\lit}{\acro{lit}}
+\newcommand{\glb}{\acro{glb}}
+\newcommand{\loc}{\acro{loc}}
+
+\newcommand{\as}{\acro{as}}
+\renewcommand{\es}{\acro{es}}
+\renewcommand{\AE}{\as}
+\newcommand{\GE}{\es}
+
+\newcommand{\lc}{\acro{lc}}
+\newcommand{\ec}{\acro{ec}}
+
+\DefineNamedColor{named}{mycol}{cmyk}{0.6,0.6,0,0}
+\DefineNamedColor{named}{mygray}{cmyk}{0.05,0.05,0.05,0.05}
+\DefineNamedColor{named}{mygraylight}{cmyk}{0.017,0.017,0.017,0.017}
+
+\newcommand{\mymark}[1]{{\color{mycol}{#1}}}
 
@@
 
-\svnInfo $Id: paper.tex 205 2012-04-29 16:26:54Z micha $
+\svnInfo $Id$
+
+\section{Introduction}
+\label{sec:introduction}
+
+This paper deals with the interpretation of two types of
+sentences, exemplified by:
+
+\begin{exe}
+\ex \label{bsp:AE}
+  \mymark{All} of the students read \mymark{some} of the
+  papers. \hfill (\AE)
+\ex \label{bsp:GE} 
+  \mymark{Exactly one} of the students read \mymark{some} of the
+  papers. \hfill (\GE)
+\end{exe}
+
+\noindent In \as-sentences a scalar item \emph{some} takes scope under
+a universal quantifier \emph{all}. In \es-sentences a scalar item
+\emph{some} takes scope under a non-monotonic quantifier \emph{exactly
+  one}. Scalar \emph{some} is usually assumed to receive a semantic
+interpretation similar to logical $\exists$, so that the expression
+\emph{Some boys cried.} is literally true in a situation where all
+boys cried. But it is also known to invite upper-bounding inferences
+in plain utterances:
+
+\begin{exe}
+  \ex \label{bsp:Plain-SI}
+    \begin{xlist}
+      \ex \label{bsp:Plain-SI-Target} Hans solved some of the problems.
+      \ex \label{bsp:Plain-SI-Implicature} $\implicates$ Hans solved some but not all of the problems.
+    \end{xlist}
+\end{exe}
+
+\noindent The classical explanation of this inference, following the
+pioneering work of \citet{Grice1975:Logic-and-Conve}, has it that
+(\ref{bsp:Plain-SI-Implicature}) is a pragmatic inference, a so-called
+\emph{quantity implicature}, derived by an abductive inference as the
+best explanation of why am informed, knowledgable and cooperative
+speaker has uttered (\ref{bsp:Plain-SI-Target}) when she could also
+have uttered the semantically stronger and relevant:\dn{redo labels of
+  examples}
+
+\begin{exe}
+  \exr{bsp:Plain-SI}
+    \begin{xlist}
+      \exi{c.} \label{bsp:Plain-SI-Alternative} Hans solved all of the problems.
+    \end{xlist}
+\end{exe}
+
+\noindent If this upper-bounding inference would occur often and
+systematically enough, then it may well be that also embedded
+occurrences of \emph{some} get enriched, in some fashion or other, to
+contribute \emph{in situ} the enriched meaning \emph{some but not
+  all}. Indeed, even \citeauthor{Grice1975:Logic-and-Conve} envisaged
+this possibility when he wrote: ``It may not be impossible for what
+starts life, so to speak, as a conversational implicature to become
+conventionalized'' \citep[p.58]{Grice1975:Logic-and-Conve}. But then
+there are at least three relevant candidate readings for \as- and
+\es-sentences: (i) a \emph{literal reading} like in
+(\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where \emph{some}
+has only its literal meaning as in; (ii) a \emph{global reading} like
+in (\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where, according
+to the Gricean intuition, we compare utterances of (\ref{bsp:AE}) or
+(\ref{bsp:GE}) with utterances of the corresponding sentences
+(\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
+\emph{some} is replaced by \emph{all}; and also (iii) a \emph{local
+  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
+\emph{some} is read to mean \emph{some but not all} in the scope of
+the embedding quantifier.
+
+% DIRTY!!!
+\setcounter{exx}{0}
+
+\begin{exe}
+
+  \ex \mymark{All} of the students read {\mymark{some}} of the
+  papers.
+
+  \begin{xlist}
+  \ex \label{bsp:AE-Literal} \mymark{All} of the students read
+    {\mymark{some and maybe all}} of the papers. \hfill (\as-\lit)
+  \ex \label{bsp:AE-Global}
+    \mymark{All} of the students read \mymark{some} 
+    and  \hfill (\as-\glb)\\
+    \mymark{not all} of the students read \mymark{all} of the papers.
+  \ex \label{bsp:AE-Local}
+    \mymark{All} of the students read {\mymark{some  but not all}} of the
+    papers. \hfill (\as-\loc)
+  \end{xlist}
+
+\ex \mymark{Exactly one} of the students read {\mymark{some}} of the
+  papers.
+
+  \begin{xlist}
+  \ex \label{bsp:GE-Literal} \mymark{Exactly one} of the students read
+    {\mymark{some and maybe all}} of the papers. \hfill (\es-\lit)
+  \ex \label{bsp:GE-Global}
+    \mymark{Exactly one} of the students read \mymark{some} 
+    and  \hfill (\es-\glb)\\
+    \mymark{not all} of the students read \mymark{all} of the papers.
+  \ex \label{bsp:GE-Local}
+    \mymark{Exactly one} of the students read {\mymark{some  but not all}} of the
+    papers. \hfill (\es-\loc)
+  \end{xlist}
+
+\ex \label{bsp:AE-Alternative} \mymark{All} of the students read
+  {\mymark{all}} of the papers.
+
+\ex \label{bsp:GE-Alternative} \mymark{Exactly one} of the students
+  read {\mymark{all}} of the papers.
+
+\end{exe}
+
+\bigskip
+
+\section{Get to know your readings}
+\label{sec:get-know-your}
+
+\section{Theories and predictions}
+\label{sec:theories-predictions}
+
+\section{Previous studies}
+\label{sec:previous-studies}
 

### 2012-05-21 text/paper/paper.tex
paper sec com

@@
 there are at least three relevant candidate readings for \as- and
-\es-sentences: (i) a \emph{literal reading} like in
+\es-sentences (see Section~\ref{sec:get-know-your} for more detail and
+some helpful illustrations): (i) a \emph{literal reading} like in
 (\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where \emph{some}
@@
 
+The main question we are interested in here is which of these three
+conceivable readings is available to subjects na\"{i}ve to all
+pragmatic theory. We are moreover interested in the more refined
+question which of the available readings na\"{i}ve subjects prefer.
+
+Addressing these issues empirically is highly relevant because they
+lie at the heart of the current debate of the exact location and
+nature of the interface between semantics and pragmatics. In rough
+approximation, there are three camps ---more or less fiercely---
+involved in this border war. (We will give a more detailed description
+of the various theoretical positions below in
+Section~\ref{sec:theories-predictions}.) Firstly, there are
+\emph{pragmatic traditionalists} who seek to conserve the spirit of
+\citeauthor{Grice1975:Logic-and-Conve}'s
+(\citeyear{Grice1975:Logic-and-Conve}) original ideas as much as
+possible
+\citep[e.g.][]{Spector2006:Scalar-Implicat,Sauerland2004:Scalar-Implicat,Russell2006:Against-Grammat,vanRooijSchulz:ExhaustiveInterpretation,Geurts2010:Quantity-Implic,Franke2011:Quantity-Implic}.
+Traditionalists
+happily acknowledge the existence of global readings, but might
+consider local readings either unavailable or a beast distinct from
+scalar implicatures. Opposed to that is the camp of \emph{lexical
+  conventionalists}
+\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}
+who maintain a double lexical meaning for scalar \emph{some}, one as
+in logical semantics, and one with the enriched meaning \emph{some but
+  not all}. As the latter is considered a default, lexical
+conventionalism has no problem accounting for local readings, and in
+fact would consider these the preferred readings. Thirdly and finally,
+there is also the ever more powerful camp of \emph{grammaticalists}
+who defend that the distribution of upper-bounded readings of
+\emph{some} is best explained by postulating a silent operator, akin
+to the meaning of the particle \emph{only} \citep{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Sauerland2012:The-Computation}.
+This operator may be
+applied in compositional semantics also in the scope of other logical
+operators, so as to account for, e.g., local readings of \as- and
+\es-sentences.
+
 \bigskip

### 2012-05-21 text/paper/paper.tex
K2 paper sec com

--- 2012-05-21 text/paper/paper.tex
@@
 This paper deals with the interpretation of two types of
-sentences, exemplified by:
+sentences, namely:
 
@@
   one}. Scalar \emph{some} is usually assumed to receive a semantic
-interpretation similar to logical $\exists$, so that the expression
-\emph{Some boys cried.} is literally true in a situation where all
+interpretation similar to logical $\exists$, so that the sentence
+\emph{Some boys cried} is literally true in a situation where all
 boys cried. But it is also known to invite upper-bounding inferences
@@
 occurrences of \emph{some} get enriched, in some fashion or other, to
-contribute \emph{in situ} the enriched meaning \emph{some but not
-  all}. Indeed, even \citeauthor{Grice1975:Logic-and-Conve} envisaged
-this possibility when he wrote: ``It may not be impossible for what
-starts life, so to speak, as a conversational implicature to become
-conventionalized'' \citep[p.58]{Grice1975:Logic-and-Conve}. But then
-there are at least three relevant candidate readings for \as- and
-\es-sentences: (i) a \emph{literal reading} like in
-(\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where \emph{some}
-has only its literal meaning as in; (ii) a \emph{global reading} like
-in (\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where, according
-to the Gricean intuition, we compare utterances of (\ref{bsp:AE}) or
-(\ref{bsp:GE}) with utterances of the corresponding sentences
+contribute the enriched meaning \emph{some but not all} also under the
+scope of other logical operators. Indeed, even
+\citeauthor{Grice1975:Logic-and-Conve} envisaged this possibility when
+he wrote: ``It may not be impossible for what starts life, so to
+speak, as a conversational implicature to become conventionalized''
+\citep[p.58]{Grice1975:Logic-and-Conve}. But then there are at least
+three relevant candidate readings for \as- and \es-sentences: (i) a
+\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
+(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
+(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
+(\ref{bsp:GE-Global}) where, according to the Gricean intuition, we
+enrich utterances of (\ref{bsp:AE}) and (\ref{bsp:GE}) with the
+negation of alternativ utterances of the corresponding sentences
 (\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
@@
 
+\noindent Section~\ref{sec:get-know-your} will discuss these reading
+in more detail and, by giving some helpful illustrations, make clear
+that these readings are all distinct but logically dependent
+on each other in interesting ways.
+
+The main question we are interested in here is which of these three
+conceivable readings is available to subjects na\"{i}ve to all
+pragmatic theory. We are moreover interested in the more refined
+question which of the available readings na\"{i}ve subjects prefer.
+
+Addressing these issues empirically is highly relevant because they
+lie at the heart of the current debate of the exact location and
+nature of the interface between semantics and pragmatics. There are
+three major camps which are ---more or less fiercely--- involved in
+this border war, all of which make different predictions about
+availability and preferences of readings. We will give a more detailed
+description of the various theoretical positions below in
+Section~\ref{sec:theories-predictions}, but on a first rough
+approximation the situation is the following. Firstly, there are
+\mymark{pragmatic traditionalists} who seek to conserve the spirit of
+\citeauthor{Grice1975:Logic-and-Conve}'s
+(\citeyear{Grice1975:Logic-and-Conve}) original ideas as much as
+possible
+\citep[e.g.][]{Spector2006:Scalar-Implicat,Sauerland2004:Scalar-Implicat,Russell2006:Against-Grammat,vanRooijSchulz:ExhaustiveInterpretation,Geurts2010:Quantity-Implic,Franke2011:Quantity-Implic}.
+Traditionalists
+happily acknowledge the existence of global readings, but might
+consider local readings either unavailable or a beast distinct from
+scalar implicatures. Opposed to that is the camp of \mymark{lexical
+  conventionalists}
+\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}
+who maintain that scalar \emph{some} is lexically ambiguous between
+the standard logical meaning \emph{some and maybe all} and the
+upper-bounded meaning \emph{some but not all}. As the latter is
+considered a default, lexical conventionalism has no problem
+accounting for local readings, and in fact would consider these the
+preferred readings. Thirdly and finally, there is the camp of
+\mymark{grammaticalists} who defend that the distribution of
+upper-bounded readings of \emph{some} is best explained by postulating
+a silent operator, akin to the meaning of the particle \emph{only}
+\citep{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Sauerland2012:The-Computation}. According
+to the grammatical view, this silent operator may be applied in
+compositional semantics also in the scope of other logical operators,
+but the availability of readings is constraint by the \emph{strongest
+  meaning hypothesis}
+\citep{DalrympleKanazawa1998:Reciprocal-Expr}. Details follow in
+Section~\ref{sec:theories-predictions}, but suffice it to just state
+already that grammaticalist theories predict that all three types of
+readings are available. Moreover, according to the grammatical view,
+the local reading is preferred for \as-sentences, while the global one
+is preferred for \es-sentences. (More precisely, but see
+Section~\ref{sec:theories-predictions}, depending on the variant of
+the strongest meaning hypothesis employed, either the global reading
+is predicted to be preferred for \es-sentences, or the global and the
+local reading are predicted to be equally preferred.)
+
 \bigskip

### 2012-05-21 text/paper/paper.tex
K2 paper sec com

@@
 \newcommand{\ec}{\acro{ec}}
+\newcommand{\LC}{\lc}
+\newcommand{\EC}{\ec}
 
@@
 the local reading is preferred for \as-sentences, while the global one
-is preferred for \es-sentences. (More precisely, but see
+is preferred for \es-sentences. (More precisely, as we will see
 Section~\ref{sec:theories-predictions}, depending on the variant of
@@
 local reading are predicted to be equally preferred.)
+
+Due to its theoretical significance, a number of previous studies have
+already probed into the availability of readings for \as- and
+\es-sentences
+\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. However,
+as we will argue in Section~\ref{sec:previous-studies}, results have
+not been as clear-cut as one might have hoped for. Even worse so,
+taken in conjunction, the empirical evidence is inconclusive as to
+whether local readings exist. We hypothesized that previous studies
+might be insufficiently informative because of the focus on (variants
+of) a picture-verification paradigm.\dn{relate to Bob van Tiel's
+  work}.  The problem is that in order to test the availability of
+different candidate meanings different pictures have to be presented,
+so that effects of pictorial complexity or stereotypicality could
+never be ruled out entirely. Moreover, previous studies have only
+accumulated limited evidence pertaining to the second question that
+may help decide between theoretical positions, namely which of the
+attested readings subjects prefer.
+
+In reaction to this situation, we therefore studied a different mode
+of visual presentation: subjects were presented with pictures that
+were partly covered and could incrementally be uncovered at the
+subjects' request; for each ((partially) covered) picture, subjects
+had to decide whether they could already give a truth-value judgement
+or needed more information.\dn{mention who else does this} This way we
+obtained behavioral data that is both indicative of the reading
+subjects assumed and independent of the complexity of the visual
+stimulus. At the same time, we hypothesized that the incremental
+nature of this task would shed light on the preferences over readings,
+because the temporal distribution of truth-value judgments would give
+away which reading subjects were waiting to evaluate, so to speak.
+
+To test whether our method is indeed suitable to detect interpretation
+preferences, we included ambiguous test items like
+(\ref{bsp:target-related-filler}) which are known to preferentially
+receive the late-closure reading in
+(\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
+attested early-closure reading (\ref{bsp:target-related-filler-EC}).
+
+    \begin{exe}
+      \ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
+        suns.
+        \begin{xlist}
+          \ex \label{bsp:target-related-filler-LC} The letter is connected with circles and squares; the latter
+            but not the former contain suns. \hfill (\LC)
+          \ex \label{bsp:target-related-filler-EC} The letter is connected with circles and squares; both
+            contain suns. \hfill (\EC)
+        \end{xlist}
+    \end{exe}
+
+ with syntactically ambiguous
+sentences whose interpretation preferences have been frequently
+attested empirically.\dn{insert references to literature on EC-LC
+  processing}
+
+ Moreover,
+since it is often argued (see Section~\ref{sec:theories-predictions})
+that intonational stress on an embedded scalar item can favor a local
+reading we presented sentence auditorily and manipulated stress
+accordingly. The design of our studies is detailed in Section XYZ.
+
+\begin{itemize}
+\item summarize results
+\end{itemize}
 

### 2012-05-21 text/paper/paper.tex
K2 paper sec com

@@
-\documentclass[fleqn,reqno,10pt]{article}
+\documentclass[fleqn,reqno,10pt,draft]{article}
 
@@
 because the temporal distribution of truth-value judgments would give
-away which reading subjects were waiting to evaluate, so to speak.
-
-To test whether our method is indeed suitable to detect interpretation
+away which reading subjects were waiting to evaluate, so to speak. To
+test whether our method is indeed suitable to detect interpretation
 preferences, we included ambiguous test items like
@@
 (\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
-attested early-closure reading (\ref{bsp:target-related-filler-EC}).
+attested early-closure reading
+(\ref{bsp:target-related-filler-EC}).\dn{insert references to
+  literature on EC-LC processing}
 
@@
 
- with syntactically ambiguous
-sentences whose interpretation preferences have been frequently
-attested empirically.\dn{insert references to literature on EC-LC
-  processing}
-
- Moreover,
-since it is often argued (see Section~\ref{sec:theories-predictions})
-that intonational stress on an embedded scalar item can favor a local
-reading we presented sentence auditorily and manipulated stress
-accordingly. The design of our studies is detailed in Section XYZ.
+\noindent Finally, since it is often argued (see
+Section~\ref{sec:theories-predictions}) that intonational stress on an
+embedded scalar item can favor a local reading we presented sentence
+auditorily and manipulated stress accordingly. The design of our
+studies is detailed in Section XYZ.
 

### 2012-06-20 text/paper/Critique.tex
paper put together

\documentclass[a4paper,10pt]{article}

\usepackage{t1enc}
\usepackage{linguex}
\usepackage{harvard}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usepackage{subfigure}
\usepackage{qtree}
%\usepackage{hyperref}

\bibliographystyle{diss}

%opening
\title{Critique of previous studies and motivation}
\author{}

\newtheorem{hypothese}{Hypothesis}
\newtheorem{Def}{Definition}
\newtheorem{Prop}{Proposition}
\newtheorem{Example}{Example}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Critique of previous studies and motivation}

Summing up, the mentioned studies have presented diverging evidence concerning the availability of local implicatures. Varoius problematic aspects of these studies have already been discussed elsewhere (C\&D, C\&S, van Tiel). Here, we want to point out two particular methodological problems that do impede their interpretation. However, we also want to make clear that these problems follow almost directly from the nature of the phenomenon under investigation and therefore seem nearly impossible to avoid.

Firstly,  a mapping between responses to be obtained in an experiment and readings of the sentences is problematic due to the logical dependencies between the relevant readings discussed in section \ref{xyz}. It is impossible to construct situations that clearly correspond to local readings of AS-sentences, since the local reading of such sentences implies their global and local readings. Every situation which is consitent with such a sentence under its local reading is also consitent with the other two readings. Therefore, we cannot test all the cases we might wish to. It would be especially desirable to test situations that are consitent with the local reading, but inconsitent with the global and literal reading of AS-sentences, in a picture verification task. In that case 'yes'-responses would unambiguously indicate local readings, whereas 'no'-responses would indicate their absence. However, since this is impossible we are left with suboptimal choices. In the experiment of Geurts situations that are inconsitent with local readings but consitent with the other two readings were tested. In that case 'no'-responses would be decisive~-- when compared to a suitable baseline. However, 'yes' responses were observed exclusively. These can be attributed to one of the other readings. Therefore, assuming a principle of charity (Davidson 2001) to be at play in picture verification tasks, the data of Geurts do not provide evidence against the existence of local readings.  In  the experiments of C\&S and C\&D on the other hand situations that are consitent with all three readings were tested. Here again 'yes'-judgments cannot be interpreted confidently because they can always be attributed to global or literal readings. Both C\&S and C\&D attempt to surpass this problem by interpreting relative preferences. This does, however, bring us to the second problem.

Preferences may be affectd by graphical properties of the picture materials. For example, verification complexity or typicality of the pictures with respect to the test sentences may differ between conditions and thereby induce certain preferences. In his careful critique van Tiel has eleborated on this point. Van Tiel points out that the relative preferences C\&S and C\&D interpret can be explained solely in terms of typicality, because the {\bf all}-pictures (see e.g. Figure \ref{xx}) are more typical instances of the sentence meaning than the competing pictures, irrespective of local implicatures.

To conclude, in order to decide about the availablity of local implicatures we would ideally like to test situations that can unambiguously be mapped to the different readings and do not differ in typcality or other crucial properties. Given the logical dependencies inherent to the relevant readings and the considerations concerning typicality presented by van Tiel this seems impossible to achieve. As we willl argue below we do, however, believe it is.

\bibliography{../../Literatur/tex/literatur}
\end{document}

### 2012-06-20 text/paper/ResultsK2.tex
paper put together

\documentclass[a4paper,10pt]{article}

\usepackage{t1enc}
\usepackage{linguex}
\usepackage{harvard}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usepackage{subfigure}
\usepackage{qtree}
%\usepackage{hyperref}

\bibliographystyle{diss}

%opening
\title{Results K2s}
\author{}

\newtheorem{hypothese}{Hypothesis}
\newtheorem{Def}{Definition}
\newtheorem{Prop}{Proposition}
\newtheorem{Example}{Example}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Results}
The judgments obtained for the four target conditions are depicted   in Figure \ref{fig:JudgmentsK2}.  We coded the judgments as {\it literal}, {\it global} or {\it local} if they were as expected under one of these readings and as {\it error} if not. The distribution of readings as coded by us is presented in Figure \ref{fig:ReadingsExp1}. Participants mostly gave judgments indicating literal or local readings. Judgments compatible with a global reading were seldomly obtained. In the All-Some conditions participants made hardly any errors, whereas the amount of errors was slightly greater in the Exactly-One-Some conditions.

\begin{figure}[h]
\centering
\subfigure[All-Some accented]{
\includegraphics[width=5cm]{graph_AE_AKZ.jpg}
\label{fig:ReadingsAE}
}
\subfigure[All-Some neutral]{
\includegraphics[width=5cm]{graph_AE_NTR.jpg}
\label{fig:ReadingsGE}
}
\subfigure[Exactly-One-Some accented]{
\includegraphics[width=5cm]{graph_GE_AKZ.jpg}
\label{fig:ReadingsAE}
}
\subfigure[Exactly-One-Some neutral]{
\includegraphics[width=5cm]{graph_GE_NTR.jpg}
\label{fig:ReadingsGE}
}

\caption[Optional caption for list of figures]{Judgments for the four target conditions in Experiment 1. Relative frequency of yes/no-judgments is plotted against the position within the trial. In the All-Some conditions there were seven positions. On the third position a yes-judgment corresponded to a literal reading, while on the fith position a yes-judgment corresponded to a global reading.  A no-judgment on the seventh position was only consistent with a local reading. The Exactly-One-Some conditions had five positions. No- judgments on positions two and three corresponded to global and literal readings, respectively. A yes-judgment on the last segment  corresponded to a local reading. }
\label{fig:JudgmentsK2}
\end{figure}

In the All-Some conditions  (see Figure \ref{fig:ReadingsAE}) judgments were consistent with literal readings in 65.0\% of the trials with neutral prosody and in 67.5\% of the trials with accented prosody. The number of global readings was very low, with 1.6\% of the neutral and 0.8\% of the accented trials. Judgments indicating local readings were given in 22.0\% of both the neutral and accented trials. In the Exactly-One-Some conditions (see Figure \ref{fig:ReadingsGE}) judgments consistent with literal readings were given in 47.2\% and 44.7\% of the trials with neutral and accented prosody, respectively. Global readings were observed in 0.8\% of the trials in both the neutral and the accented condition. Judgments indicating local readings were given in 22.8\% of the neutral and 27.6\% of the accented trials.

In order to test wether local readings exist we tested whether the number of local responses in each condition was higher than expected by chance. Local responses had to be given on the last position in each trial. If local readings didn't exist we would expect participants, who reached the last position (ie. who did not abort the trial prior to the last position) to give local judgments not more often than expected by chance. On the last position two responses were possible. One was compatible with a local reading the other was not. Therefore, we would expect 50\% local responses by chance. As it turns out  local responses were given significantly more often than 50\% in all target conditions (all Bonferoni corrected p<.05). Note that this finding cannot be explained by some kind of general response bias on the last position since local readings required a yes-judgment in the Exactly-One-Some conditions but a no-judgment in the All-Some conditions.

In order to test whether accentuation or the quantifier has an influence on the distribution of readings, log-liner models were computed (see Schepers 2003). The factors {\it Reading}, {\it Accentuation} and {\it Quantifier} were included in these models. Two variants of these models were computed.  In the first, the factor {\it Item} was added to the above mentioned. In the latter {\it Participants} was included as a factor. Inclusion of these two factors allowed us to test whether the distribution of readings was identical accros items and participants. We report log-likelihood ratio Chi-squares ($LRCS_1$ and $LRCS_2$), degrees of freedom ($df_1$, $df_2$) and significance levels ($p_1$ and $p_2$).

Unsurprisingly, there was an effect of reading ($LRCS_1=364.77, df_1 = 3, p_1<.001, LRCS_2=364.77, df_2 = 3, p_1<.001,$) because overall the readings were distributed inhomogeneously (sse Figure \ref{fig:ReadingsGE}). The quantifier had an influence on the distribution of readings as revealed by a reliable interaction of {\it Reading} and {\it Quantifier} ($LRCS_1=49.32, p_1<.01,LRCS_2=32.16, p_1<.01,$). Looking at the data  it seemed unlikely that the quantifier affected the amount of local readings. We suspected that this interaction was due to the higher number of errors and lower number of literal readings in the Exactly-One-Some conditions as compared with the All-Some conditions. A difference in the distribution of judgment types between participants was revealed by a reliable interaction of {\it Reading} and {\it Participant} ($LRCS_1=487.70, p_1<.01$). We were interested in whether this effect was due to some of the participants being more likely to choose literal readings than others. Finally, there was a three-way interaction of {\it Participants}, {\it Construction} and {\it Reading} ($LRCS_1, = 143.92, df_1 = 117, p_1<.05$) which could stem from to the fact that some participants were more prone than others to make errors in the Exactly-One-Some conditions.

In order to find out whether the interactions just reported affected the amount of local readings, the log-linear models were computed again with a different coding of the readings. Here,  we only considered the amount of local readings versus all other kinds of judgments. Judgments were coded as {\it local} and {\it other}. If the reported interactions affect the amount of local readings they should show up again. The  expected but irrelevant effect of {\it Reading} was again significant ($LRCS_1=134.55, df_1 = 1, p_1<.001, LRCS_2=144.64, df_2 = 1, p_1<.001,$). In addition, the interaction of {\it Participant} and {\it Reading} ($LRCS_1=487.70, p_1<.01$) as well as the three-way interaction of {\it Construction}, {\it Participant} and {\it Reading} ($LRCS_1=487.70, p_1<.01$) were significant. No other effects were significant. In particular, the interaction of {\it Construction} and {\it Reading} was not significant ($LRCS_1=2.10, p_1=.15,LRCS_2=.74, p_2=.39$).

The interaction of {\it Participant} and {\it Reading} shows that there are indeed varying preferences for local readings among German speakers. Further examination of the distribution of local readings revealed a clear pattern (see Figure \ref{fig:HistogramLocalReadingsK2}). In all four conditions, about  seven out of the 40 participants ($16\%$)  were consitently giving judgments that indicate local readings. Further, the relative frequency of local judgments per participant strongly correlated between all four conditions (all $r>.6, p<.001$). Appart from the localists about half of the participants (and 41.5\% of all participants) were consitently giving judgments that indicate literal readings. Only a minority of participants exhibited inconsistency. Reading preferences were  more clear-cut in the All-Some conditions than in the Exactly-One-Some conditions. The number of consitent litaralists was lower in the Exactly-One-Some (25.6\%) conditions as compared to the All-Some conditions (57.3\%). Also, the number of participants that showed inconsitency was higher in these conditions. However, the number of consistent localists did hardly differ between constructions.

The three way-interaction of {\it Participant}, {\it Construction} and {\it Reading} is due to the fact that for some participants preferences for local over other readings deviated between the two construction types. These deviations were, however, not systematic to any degree. How much local preferences deviated between the two contsruction types per participant is depicted in Figure \ref{}. Most participants had exactly the same preferences in the two constructions. However, a few had a stronger and a few others a weaker preference for local readings in the Exactly-One-Some than in the All-Some conditions. Since we did not find any sytematic patterns here, we speculate that the three-way interaction is due to the Exactly-One-Some construction beeing understood non-standardly by a few participants. This speculation is plausible given the higher number of errors in the Exactly-One-Some  as compared to the All-Some conditions.

The absence of the interaction between {\it Construction} and {\it Participant} indicates that the type of construction does not affect the amount of local readings. We assumed based on the observed distribution of judgments that the type of contsruction affected the amount of literal but not local and global readings. To further test this assumption, we also considered literal and global readings versus other judgments in separate analyses. Comparing global readings versus other judgments {\it Construction} and {\it Reading} were found to interact ($LRCS_1=42.80, df= 1, p<.001; LRCS_2=22.14, df= 1, p<.001$). Comparing global readings to other judgments no such interaction was obeserved ($LRCS_1=1.24, df= 1, p=.29, LRCS_1=.21, df= 1, p=.65$).

\begin{figure}[h]
\centering
\subfigure[All-Some Conditions]{
\includegraphics[width=5cm]{ReadingsAE.eps}
\label{fig:ReadingsAE}
}
\subfigure[Exactly-One-Some Conditions]{
\includegraphics[width=5cm]{ReadingsGE.eps}
\label{fig:ReadingsGE}
}
\caption[Optional caption for list of figures]{Judgments}
\label{fig:ReadingsExp1}
\end{figure}

\begin{figure}[h]
\centering
\subfigure[All-Some accented]{
\includegraphics[width=5cm]{histLocalReadingAE_AKZ.jpg}
\label{fig:ReadingsAE}
}
\subfigure[All-Some neutral]{
\includegraphics[width=5cm]{histLocalReadingAE_NTR.jpg}
\label{fig:ReadingsGE}
}
\subfigure[Exactly-One-Some accented]{
\includegraphics[width=5cm]{histLocalReadingGE_AKZ.jpg}
\label{fig:ReadingsAE}
}
\subfigure[Exactly-One-Some neutral]{
\includegraphics[width=5cm]{histLocalReadingGE_NTR.jpg}
\label{fig:ReadingsGE}
}
\label{fig:HistogramLocalReadingsK2}
\caption[Optional caption for list of figures]{Judgments for the four target conditions}
\end{figure}

\bibliography{../../Literatur/tex/literatur}
\end{document}

### 2012-06-21 text/paper/Design.tex
paper design added

\documentclass[a4paper,10pt]{article}

\usepackage{t1enc}
\usepackage{linguex}
\usepackage{harvard}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usepackage{subfigure}
\usepackage{qtree}
%\usepackage{hyperref}

\bibliographystyle{diss}

%opening
\title{Results K2 (Target Conditions)}
\author{}

\newtheorem{hypothese}{Hypothesis}
\newtheorem{Def}{Definition}
\newtheorem{Prop}{Proposition}
\newtheorem{Example}{Example}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Design}

\paragraph{General Idea:} In order to test whether local implicatures are possible, we seeked for a way to unambiguously map responses from a picture verification task to the alternative readings of AS- and ES-sentences. In addition, we wanted to minimize effects of any graphical differences between the picture materials. To achieve this we designed an experiment employing a modified version of picture verification, namely the incremental verification task (IVT, see Conroy). We will now describe the design step by step.

Consider the AS-sentence in \Next. With respect to figure \ref{fig:exseqAS3} the local reading is false, while the global and literal reading is true. Now, we made use of the following fact. If we cover up certain edges in the graph as in Figure \ref{fig:exseqAS2} the literal and global reading is still true, but the local reading is not decidable (assuming we haven't seen the whole graph, yet). By covering even a greater part of the graph, we can go one step further. In Figure \ref{fig:exseqAS1} the literal reading is true, while the local and global reading cannot be decided, yet. Now, consider the following task. Participants are asked to read sentence \Next and then uncover a graph step by step until they feel able to give a truth value judgment. In this task the participant has three options at each step: (1) demand more information (2) judge the sentence as true (3) judge the sentence as false. Presenting a sequence like Figure \ref{fig:exseqAS}, we obtain the desired mapping between judgments and readings. This mapping is illustrated in Figure \ref{fig:mappingAS}.

For the ES-sentences, the idea is similar. With respect to the sentence in \NNext we obtain an unambiguous mapping between truth values and readings with respect to the sequence in \ref{fig:exseqES}. This is illustrated in Figure \ref{fig:mappingES}. There are two differences to the previous case. Firstly, the order of readings that can be identified in the sequence differs. At the first step the global reading can be judged. Then the literal and, finally, the local reading can be judged. Secondly, the readings correspond to different truth values. Global and literal readings correspond to negative truth values, while local reading require positive judgments.

\exg. \label{ex:as}{\bf Jeder} Brief ist mit {\bf einigen} seiner Dreiecke verbunden.\\
Every Letter is with some its triangles connected.\\
Every letter is connected to some of its triangles.

\exg. \label{ex:es}{\bf Genau} eine Glocke ist mit {\bf einigen} ihrer Halbkreise verbunden.\\
Exactly one Letter is with some its semicircles connected.\\
Exactly one letter is connected to some of its semicircless.

\begin{figure}[ht]
	\centering
	\subfigure[Step 3]{ 
		\fbox{\includegraphics[width=3cm]{ae_7_v_l.pdf}}
	    \label{fig:exseqAS3}
	}
	\subfigure[Step 2]{
		\fbox{\includegraphics[width=3cm]{ae_5_v_l.pdf}}
	    \label{fig:exseqAS2}
	}
	\subfigure[Step 1]{ 
		\fbox{\includegraphics[width=3cm]{ae_3_v_l.pdf}}
	    \label{fig:exseqAS1}
	}
	\caption[]{Example sequence for AS-sentences}
	\label{fig:exseqAS}
\end{figure}

\begin{figure}[ht]
	\centering
	\subfigure[Step 3]{ 
		\fbox{\includegraphics[width=3cm]{ge_6_v_l.pdf}}
	    \label{fig:subfig1}
	}
	\subfigure[Step 2]{
		\fbox{\includegraphics[width=3cm]{ge_4_v_l.pdf}}
	    \label{fig:subfig2}
	}
	\subfigure[Step 1]{ 
		\fbox{\includegraphics[width=3cm]{ge_3_v_l.pdf}}
	    \label{fig:subfig1}
	}
	\caption[]{Example sequence for AS-sentences}
	\label{fig:exseqES}
\end{figure}

\begin{figure}[ht]
	\centering
	\subfigure[AS-Sentences]{ 
\begin{tabular}{cccc}
&more info&true&false\\
\hline
Step 1&?&literal&?\\
Step 2&?&global&?\\
Step 3&?&?&local\\
\hline
\end{tabular}

	    \label{fig:mappingAS}
	}
	\subfigure[ES-Sentences]{
\begin{tabular}{cccc}
&more info&true&false\\
\hline
Step 1&?&literal&?\\
Step 2&?&global&?\\
Step 3&?&?&local\\
\hline
\end{tabular}
	    \label{fig:mappingES}
	}
	\caption{Mapping from truth values to readings}
	\label{fig:subfigureExample}
	\end{figure}

In addition to the unambiguous mapping from readings to truth values, we think that the present design minimizes graphical effects because there is no comparison between different pictures. The distribution of responses found in previous studies could in part be explained by differences in typicality of the pictures with respect to the possible readings (see van Tiel). In the present case this kind of reasoning would have to be extended to the typicalilty of parts of pictures. On intuitive grounds, we take this kind of reasoning to be implausible. We will now shortly discuss how graphical properties might still affect judgments in the worst case. In the first step of the AS-condition local and global readings cannot be judged, yet. Therefore, graphical properties should not affect judgments if participants have one of these readings in mind. If participants have a literal reading in mind, the worst case scenario is that they refrain from judging the sentence as true at this point due to some, eg. atypical, graphical property of the picture. The situation is similar at the second step. The local reading is still not decidable. Therefore, graphical properties should not play a role if participants have a local reading in mind. A positive judgment might, however, be a delayed judgment of a literal reading. Again, the worst case scenario for our purpose is that participants refrain from answering because of graphical properties. At the last step the local reading requires a negative judgment. Now, we could obtain delayed negative responses from literal or global readings because the graph as a whole is, e.g., logically true but atypical with respect to these readings. These kinds of judgments would be indistinguishable from local responses. Note, however, that we have no reason to believe that typicality has large effects,  because, given the results from van Tiel, the picture as a whole is expected to be one of the more typical situations for AS-sentences. Still, we cannot exclude the possibility that graphical properties of the pictures might have the described effect. In the ES-conditions this type of effect is, however, entirely impossible since the  literal and global reading is plainly false given the initial parts as well as the whole graph. Summing up, in the worst case, which we consider implausible, graphical effects might lead to an enhanced number of local responses in the AS- as compared to the ES-condition. We have to keep this possibility in mind. We want to stress, however, that the design presented here improves on previous studies with respect to possible graphical effects.

\paragraph{Testing Effects of accentuation:} It has been claimed that local readings only emerge in the case of special accentuation of the the scalar item under consideration (REFERENCES). Further, it is generally assumed that the required type of accentuation is a pitch accent (REFS). To test for this possibility we decided to present the sentences  (eg., \LLast and \Last) auditively in two versions each. In the accented version a pitch accent was palced on {\it einige}. The second version had neutral prosody. If accentuation is the driving force for local readings, we would expect a higher proportion of local readings in the former than in the latter version of the sentences.

\paragraph{Controlling Response biases:} In order to control for response biases that are independent of the sentence meaning, but only depend on the experimental procedure or on the picture materials, we generated a set of control conditions. For all three readings in the AS- and ES-conditions we constructed one unambiguous control sentence requiring the same type of response at the same point in the sequence. We used sentences as in \Next and \NNext. Example \Next[a] requires the same response as the AS-sentence in \ref{ex:as} under its literal reading, \Next[b] corresponds to the AS-sentence under its global reading and \Next[c] corresponds to the local reading. With regard to the ES-sentences, controls like \NNext[a] correspond to the global reading, \NNext[b] to the literal and \NNext[c] to the local reading.  If, independently from sentence meaning, there was any bias to respond in a certain way at any point in the sequences this should affect the control sentences to the same degree as it affects the target conditions.

\ex. \ag. Alle W\"urfel sind mit mindestens drei ihrer Dreiecke verbunden.\\
All dice are with at-least three their triangles connected.\\
All dice are connected to at least three of their triangles. 
\bg. Mindestens ein Brief ist mit genau f\"unf seiner Quadrate verbunden.\\
At-least one letter is with exactly five his squares connected.\\
At least one letter is connected with exactly five of his squares. 
\bg. Jeder Brief ist mit mindestens vier seiner Quadrate verbunden.\\
Every letter is with at-least four his squares connected.\\
Every letter is connected to at least four of its squares.

\ex. \ag. Alle Glocken sind mit weniger als vier ihrer Halbkreise verbunden. \\
All bells are with fewer than four their semicircles connected.\\
All bells are connected with fewer than four of their semicircles.  
\bg. Alle Glocken sind mit allen ihren Halbkreisen verbunden.\\
All bells are with all their semicircles connected.\\
All bells are connected to all of their semicircles. 
\bg. Mindestens drei Glocken sind mit allen ihren Halbkreisen verbunden.\\
At-least three bells are with all  their semicircles connected.\\
At least three bells are connectd with all of their semicircles.

\paragraph{Controlling ambiguity resolution} In order to confidently interpret the results obtained in the described IVT experiment, we need to know certain facts about how participants deal with amiguous sentences in the IVT (disccussion of Conroy's study). To ivestigate this we used a second type of control conditions. In particular, we tested (1) whether the order in which readings can be judged affects preferences for ambiguous sentences and (2) whether prosodic information can, in principle, shift reading preferences in the present task. To this end, we used ambiguous sentences of the type in \Next. In the literature (REFS) two readings are reported for sentences of this kind. Under the first reading the PP {\it with suns} modifies the complete conjunction {\it circles and squares}. This reading is called the high-attachment reading. Under the second, low-attachment, reading the PP only modifies the second conjunct, {\it squares}. Generally, the late closure reading is preferred over the early closure reading for sentences like \Next (REFS). Concerning presentation order of readings, it is crucial for our purpose that dispreferd readings are in principle detectable regardless of their position in the sequence. To test this we combined sentences like \Next with two kinds of sequences. In the first kind of sequence a partly uncovered graph like in figure \ref{fig:exec1} preceeds a graph like in figure \ref{fig:exec2}. Here, the high-attachment reading can be judged first. Under this reading we would expect a "no"-judgment on \ref{fig:exec1}. Under the low-attachment reading we would, in contrast, expect a "yes"-response on \ref{fig:exec2}. The order of presentation is reversed in the second kind of sequence which included pictures like \ref{fig:exlc1} folllowed by pictures like \ref{fig:exlc2}. Here, the low-attachment reading can be judged first requiring a "yes"-response on \ref{fig:exlc1}. The high-attachment reading can only be judged later in the sequence. When we reach \ref{fig:exlc2} a "no"-response is expected under a high-attachment reading. If presentation order does affect preferences, we would expect preferences to differ between the two types of sequences.

\exg. Die Brief ist mit Kreisen und Vierecken mit Sonnen verbunden.\\
The letter is with circles and squares with suns connected.\\
The letter is connected with circles and squares with suns.

\begin{figure}[ht]
	\centering
	\subfigure[Step 1]{ 
		\fbox{\includegraphics[width=3cm]{ec_01_3.pdf}}
	    \label{fig:exec1}
	}
	\subfigure[Step 2]{
		\fbox{\includegraphics[width=3cm]{ec_01_5.pdf}}
	    \label{fig:exec2}
	}
	\caption[]{High-attachment first}
	\label{fig:exec}
\end{figure}

\begin{figure}[ht]
	\centering
	\subfigure[Step 1]{ 
		\fbox{\includegraphics[width=3cm]{lc_01_3.pdf}}
	    \label{fig:exlc1}
	}
	\subfigure[Step 2]{
		\fbox{\includegraphics[width=3cm]{lc_01_6.pdf}}
	    \label{fig:exlc2}
	}
	\caption[]{Low-attachment first}
	\label{fig:exec}
\end{figure}

Concerning prosodic information, we wanted to make sure that differences in prosody may generally lead to a shift in interpretation preferences in the ITV task. Sentences like \Last are well suited to test this assumption since it is well-known that their interpretational preferences are sensitive to prosody. The most natural way to pronounce a sentence like \Last includes a prosodic phrase boundary between {\it squares} and {\it with}. This intonation pattern strongly corresponds to the high-attachment reading. If, instead, a prosodic phrase boundary after {\it circles} is present, the acceptance of the low-attachment reading is boosted. To test whether prosodic information is taken into account in the IVT we presented both types of prosodic structures expecting the described boost in acceptance for the low-attachment reading. In addition, we also included a neutral version containing no phrase marking whatsoever. This should receive intermediate acceptance rates. Further, we also presented unambiguous sentences corresponding to the early closure reading. As in the case of the AS- and ES-sentences the unambiguous counterparts  served as a baseline to control for response biases that are independent of sentence meaning.

\bibliography{../../Literatur/tex/literatur}
\end{document}

### 2012-06-28 text/paper/paper.tex
K2 paper sec com
paper sec com

--- 2012-05-21 text/paper/paper.tex
@@
-\documentclass[fleqn,reqno,10pt]{article}
+\documentclass[fleqn,reqno,10pt,draft]{article}
 
-\usepackage{myarticlestyledefault}
+\usepackage[natbib=true,
+            style=authoryear-comp,
+            backend=bibtex,
+            sortcites=false,
+            maxnames=2,
+            doi=false,
+            url=false]{biblatex}
+% \bibliography{../helpers/MyRefGlobal}
+\bibliography{paper}
 
-\usepackage{mypackages}
-\usepackage{mycommands}
-\usepackage{myenvironments}
+\usepackage[final,            % override "draft" which means "no nothing"
+            colorlinks,       % rather than outlining them in boxes
+            linkcolor=gray,   % override truly awful colour choices
+            citecolor=gray,   %   (ditto)
+            urlcolor=gray,    %   (ditto)
+            plainpages=false, % to overcome complaints with multiple
+            pdfpagelabels,    % multiple page 1-s due to preface
+            hypertexnames=false % solves warning, but interferes with
+                                % index and \autoref apparently
+            ]{hyperref}
+
+\usepackage{amsmath}            % Formeln
+\usepackage{amsfonts}           % Fonts for Formulas
+\usepackage{amssymb}
+\usepackage[final]{graphicx}
+\usepackage{booktabs}
+\usepackage{enumerate}
+\usepackage{lipsum}
+\usepackage{txfonts} % for strict implication symbols
+\usepackage{soul}
+\usepackage{relsize} % provides command \relsize{+/-x} for relative
+                     % font size changes
+\usepackage[german,english]{babel}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc} 
+\usepackage{subfig}
+\usepackage{xypic}
+\usepackage{url}
+\usepackage{tikz}
+\usetikzlibrary{arrows,shapes,automata,backgrounds,petri,fit,decorations.pathmorphing}
+\usepackage{refcount}
+\usepackage{xspace} % for \xspace in definition of acronyms etc.
+\usepackage{attrib} % for right-aligned references at the end of
+                    % quotes; part of Frankenstein bundle, but 
+\renewcommand\PreTrib {}   % overwrite these commands, from attrib.sty
+\renewcommand\PostTrib {}  % to suppress additional brackets around
+                           % attributions
+
+\usepackage{pgfplots}
+
+\usepackage{../helpers/gb4e_micha}
+\usepackage{../helpers/proofing}
+
+\usepackage{../helpers/mycommands}
+% \usepackage{../helpers/myenvironments}
 
 \usepackage[]{svninfo}
+\usepackage{subfig}
+
+%%%% Additional Macros
 
@@
 \newcommand{\ec}{\acro{ec}}
+\newcommand{\LC}{\lc}
+\newcommand{\EC}{\ec}
 
-\DefineNamedColor{named}{mycol}{cmyk}{0.6,0.6,0,0}
-\DefineNamedColor{named}{mygray}{cmyk}{0.05,0.05,0.05,0.05}
-\DefineNamedColor{named}{mygraylight}{cmyk}{0.017,0.017,0.017,0.017}
+\newcommand{\exh}{\ensuremath{\mathrm{Exh}}}
+\newcommand{\alt}{\ensuremath{\mathrm{Alt}}}
 
-\newcommand{\mymark}[1]{{\color{mycol}{#1}}}
+%%%% Document
 
-\title{Scalar Items in Embedded Position: {A}nother Experimental Approach}
+\title{Scalar Items in Embedded Position: {A}n Experimental Revisit}
 \author{Fabian Schlotterbeck, Michael Franke and Petra Augurzky}
@@
 
+\tableofcontents
+
 \svnInfo $Id$
@@
 
-This paper deals with the interpretation of two types of
-sentences, namely:
-
-\begin{exe}
-\ex \label{bsp:AE}
-  \mymark{All} of the students read \mymark{some} of the
-  papers. \hfill (\AE)
-\ex \label{bsp:GE} 
-  \mymark{Exactly one} of the students read \mymark{some} of the
-  papers. \hfill (\GE)
-\end{exe}
-
-\noindent In \as-sentences a scalar item \emph{some} takes scope under
-a universal quantifier \emph{all}. In \es-sentences a scalar item
-\emph{some} takes scope under a non-monotonic quantifier \emph{exactly
-  one}. Scalar \emph{some} is usually assumed to receive a semantic
-interpretation similar to logical $\exists$, so that the sentence
-\emph{Some boys cried} is literally true in a situation where all
-boys cried. But it is also known to invite upper-bounding inferences
-in plain utterances:
+The existential quantifier \emph{some} is usually assumed to receive a
+semantic interpretation similar to logical $\exists$, so that the
+sentence \emph{Some boys cried} is literally true in a situation where
+all boys cried. But it is also usually considered to be a
+\mymark{scalar item} in that its use invites comparison with (at
+least) the semantically stronger universal quantifier \emph{all}
+\citep[c.f.][]{Horn1972:On-the-Semantic,Gazdar1979:Pragmatics:-Imp,AtlasLevinson1981}. This
+comparison can lead to an upper-bounding meaning enrichment, e.g.,
+when an utterance of (\ref{bsp:Plain-SI-Target}) is taken to invite
+the inference in (\ref{bsp:Plain-SI-Implicature}).
 
@@
     \begin{xlist}
-      \ex \label{bsp:Plain-SI-Target} Hans solved some of the problems.
-      \ex \label{bsp:Plain-SI-Implicature} $\implicates$ Hans solved some but not all of the problems.
+      \ex \label{bsp:Plain-SI-Target} Hans solved some of the
+        problems.
+      \ex \label{bsp:Plain-SI-Implicature} $\implicates$ Hans solved
+        some but not all of the problems.
+      \ex \label{bsp:Plain-SI-Alternative} Hans solved all of the problems.
     \end{xlist}
@@
 \noindent The classical explanation of this inference, following the
-pioneering work of \citet{Grice1975:Logic-and-Conve}, has it that
+pioneering work of \citet{Grice1975:Logic-and-Conve} \citep[see][for
+recent overview]{Geurts2010:Quantity-Implic}, is that
 (\ref{bsp:Plain-SI-Implicature}) is a pragmatic inference, a so-called
 \emph{quantity implicature}, derived by an abductive inference as the
-best explanation of why am informed, knowledgable and cooperative
-speaker has uttered (\ref{bsp:Plain-SI-Target}) when she could also
-have uttered the semantically stronger and relevant:\dn{redo labels of
-  examples}
+best explanation of why an informed, knowledgable and cooperative
+speakers have uttered (\ref{bsp:Plain-SI-Target}) when they could also
+have uttered the semantically stronger and relevant
+(\ref{bsp:Plain-SI-Alternative}).
+
+% If this upper-bounding inference would occur often and
+% systematically enough, then it may well be that also embedded
+% occurrences of \emph{some} get enriched, in some fashion or other, to
+% contribute the enriched meaning \emph{some but not all} also under the
+% scope of other logical operators.
+% Indeed, even
+% \citeauthor{Grice1975:Logic-and-Conve} envisaged this possibility when
+% he wrote: ``It may not be impossible for what starts life, so to
+% speak, as a conversational implicature to become conventionalized''
+% \citep[p.58]{Grice1975:Logic-and-Conve}.
+
+This paper deals with the interpretation of two types of sentences,
+where the scalar item \emph{some} occurs in the scope of other logical
+operators. In \as-sentences (short for \textsc{All-Some}) as in (\ref{bsp:AE})
+the scalar item \emph{some} is embedded under universal quantifier
+\emph{all}. In \es-sentences (short for \textsc{ExactlyOne-Some}) like (\ref{bsp:GE}) \emph{some} takes
+scope under the non-monotonic quantifier \emph{exactly
+  one}.\dn{explain what non-monotonic means?  here or later?}
+According to current pragmatic theory, there are at least three
+relevant candidate readings for \as- and \es-sentences: (i) a
+\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
+(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
+(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
+(\ref{bsp:GE-Global}) where, according to Gricean intuition, we enrich
+utterances of (\ref{bsp:AE}) and (\ref{bsp:GE}) with the negation of
+alternative utterances of the corresponding sentences
+(\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
+\emph{some} is replaced by \emph{all}; and also (iii) a \emph{local
+  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
+\emph{some} is interpreted as \emph{some but not all} in the scope of
+the embedding quantifier.
 
 \begin{exe}
-  \exr{bsp:Plain-SI}
+  \ex \label{bsp:AE} \mymark{All} of the students read {\mymark{some}} of the
+  papers. \hfill{(\as)}
+
   \begin{xlist}
-      \exi{c.} \label{bsp:Plain-SI-Alternative} Hans solved all of the problems.
+  \ex \label{bsp:AE-Literal} \mymark{All} of the students read
+    {\mymark{some and maybe all}} of the papers. \hfill (\as-\lit)
+  \ex \label{bsp:AE-Global}
+    \mymark{All} of the students read \mymark{some and maybe all} 
+    and  \hfill (\as-\glb)\\
+    it's not the case that \mymark{all} of the students read \mymark{all} of the papers.
+  \ex \label{bsp:AE-Local}
+    \mymark{All} of the students read {\mymark{some  but not all}} of the
+    papers. \hfill (\as-\loc)
   \end{xlist}
@@
 
-\noindent If this upper-bounding inference would occur often and
-systematically enough, then it may well be that also embedded
-occurrences of \emph{some} get enriched, in some fashion or other, to
-contribute the enriched meaning \emph{some but not all} also under the
-scope of other logical operators. Indeed, even
-\citeauthor{Grice1975:Logic-and-Conve} envisaged this possibility when
-he wrote: ``It may not be impossible for what starts life, so to
-speak, as a conversational implicature to become conventionalized''
-\citep[p.58]{Grice1975:Logic-and-Conve}. But then there are at least
-three relevant candidate readings for \as- and \es-sentences: (i) a
-\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
-(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
-(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
-(\ref{bsp:GE-Global}) where, according to the Gricean intuition, we
-enrich utterances of (\ref{bsp:AE}) and (\ref{bsp:GE}) with the
-negation of alternativ utterances of the corresponding sentences
-(\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
-\emph{some} is replaced by \emph{all}; and also (iii) a \emph{local
-  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
-\emph{some} is read to mean \emph{some but not all} in the scope of
-the embedding quantifier.
+\begin{exe}
+\ex  \label{bsp:GE} \mymark{Exactly one} of the students read {\mymark{some}} of the
+  papers. \hfill{(\es)}
 
-% DIRTY!!!
-\setcounter{exx}{0}
+  \begin{xlist}
+  \ex \label{bsp:GE-Literal} \mymark{Exactly one} of the students read
+    {\mymark{some and maybe all}} of the papers. \hfill (\es-\lit)
+  \ex \label{bsp:GE-Global}
+    \mymark{Exactly one} of the students read \mymark{some and maybe all} 
+    and  \hfill (\es-\glb)\\
+    it's not the case that \mymark{exactly one} of the students read \mymark{all} of the papers.
+  \ex \label{bsp:GE-Local}
+    \mymark{Exactly one} of the students read {\mymark{some  but not all}} of the
+    papers. \hfill (\es-\loc)
+  \end{xlist}
+\end{exe}
 
 \begin{exe}
+\ex \label{bsp:AE-Alternative} \mymark{All} of the students read
+  {\mymark{all}} of the papers.
+
+\ex \label{bsp:GE-Alternative} \mymark{Exactly one} of the students
+  read {\mymark{all}} of the papers.
+\end{exe}
+
+% Section~\ref{sec:get-know-your} will discuss these readings
+% in more detail, showing that all three readings of each sentence are
+% distinct but logically dependent on each other in interesting ways.
+
+\noindent Given this relative abundance of theoretically conceivable
+readings, two interlocked empirical questions arise:
+\begin{enumerate}[Q1:]
+\item which of these three
+conceivable readings are available to na\"{i}ve subjects; and
+\item which of the available readings are preferred.\fn{It may
+    ultimately be impossible to keep unavailability and strong
+    dispreference strictly apart. For our purposes this is not
+    important. Every time we speak of availability, the so-inclined
+    reader may think of non-negligible preference.}
+\end{enumerate}
+Addressing these questions empirically is relevant because they lie at
+the heart of the current debate about the exact location and nature of
+the interface between semantics and pragmatics. The controversy
+concerns the question to what extent the upper-bounding inference from
+\emph{some} to \emph{some but not all} is conventionalized within the
+compositional computation of semantic values. For that matter, it is
+particularly relevant to assess the availability and relative
+preference of local readings. (Section~\ref{sec:theories-predictions}
+will discuss the relevant theoretical positions and the significance
+of alleged local readings in more detail.)
+
+% Firstly, there are \mymark{pragmatic traditionalists} who seek to
+% conserve the spirit of \citeauthor{Grice1975:Logic-and-Conve}'s
+% (\citeyear{Grice1975:Logic-and-Conve}) original ideas as much as
+% possible
+% \citep[e.g.][]{Spector2006:Scalar-Implicat,Sauerland2004:Scalar-Implicat,Russell2006:Against-Grammat,vanRooijSchulz:ExhaustiveInterpretation,Geurts2010:Quantity-Implic,Franke2011:Quantity-Implic}.
+Traditionalists
+% acknowledge the existence of global readings, but might consider local
+% readings either unavailable or a beast distinct from scalar
+% implicatures. An often phrased intuition of the traditionalists is
+% that local readings, since they are special kinds of inferences,
+% require special intonation, in particular emphatic stress on the
+% scalar item.\dn{give references}
+
+% Opposed to that is the camp of \mymark{lexical conventionalists}
+% \citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}
+% who maintain that scalar \emph{some} is lexically ambiguous between
+% the standard logical meaning \emph{some and maybe all} and the
+% upper-bounded meaning \emph{some but not all}. As the latter is
+% considered a default, lexical conventionalism has no problem
+% accounting for local readings, and in fact would consider these the
+% preferred readings.
+
+% Thirdly and finally, there is the camp of \mymark{grammaticalists} who
+% defend that the distribution of upper-bounded readings of \emph{some}
+% is best explained by postulating a silent operator, akin to the
+% meaning of the particle \emph{only}
+% \citep{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}. According
+% to the grammatical view, this silent operator may be applied in
+% compositional semantics also in the scope of other logical operators,
+% but, so as not to overgenerate readings, the availability of readings
+% is constraint by the \emph{strongest meaning hypothesis}
+% \citep{DalrympleKanazawa1998:Reciprocal-Expr}. Grammaticalist theories
+% predict that all three types of readings are available. Moreover,
+% according to the grammatical view, the local reading is preferred for
+% \as-sentences, while the global one is preferred for
+% \es-sentences. (More precisely, as we will see
+% Section~\ref{sec:theories-predictions}, depending on the variant of
+% the strongest meaning hypothesis employed, either the global reading
+% is predicted to be preferred for \es-sentences, or the global and the
+% local reading are predicted to be equally preferred.)
+
+A number of empirical studies have already examined the availability
+of readings for \as- and \es-sentences
+\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. However,
+results have not been as clear-cut as one might have hoped for: for
+instance, the available empirical evidence is inconclusive as to
+whether local readings exist \citep[see also][for related
+discussion]{Tielvan-Tiel2012:Embedded-Scalar} and do not clearly
+address all preference relations between readings relevant to
+distinguish between theoretical positions. In the following we will
+argue that these heterogeneous results are partly due to the specific
+tasks used in previous studies, i.e., complexity differences in
+variants of the picture-verification paradigm.
+% We hypothesized that previous studies might be
+% insufficiently informative because of the focus on (variants of) a
+% picture-verification paradigm.\dn{relate to Bob van Tiel's work} The
+% problem is that in order to test the availability of different
+% candidate meanings different pictures have to be presented, so that
+% effects of pictorial complexity or stereotypicality could never be
+% ruled out entirely.
+Moreover, previous studies have only accumulated limited evidence
+pertaining to the second question that may help decide between
+theoretical positions, namely which of the attested readings subjects
+prefer. Finally, previous studies presented target sentences
+visually. But as it is often argued that intonational stress on an
+embedded scalar item can favor a local reading
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar},
+it seems important to present target sentences auditorily, so as to be
+able to control for effects of ``silent intonation'' that subjects may
+apply when reading a sentence (see Bader 1998, Fodor 2000)\dn{provide
+  references}.
+
+In reaction to this situation, we therefore presented sentence
+material auditorily and also employed a different kind of visual
+presentation of the pictorial material: subjects were presented with
+pictures that were initially covered and could incrementally be
+uncovered at the subjects' request; at each step of uncovering,
+subjects had to decide whether they could already give a truth-value
+judgement or needed more information (Comry ????)\dn{insert
+  references}. This way we obtained behavioral data that is both
+indicative of the reading subjects assumed and independent of the
+complexity of the visual stimulus. At the same time, we hypothesized
+that the incremental nature of this task would shed light on the
+preferences over readings, because the temporal distribution of
+truth-value judgments would give away which reading subjects were
+waiting to evaluate, so to speak. Adding to previous studies, we
+therefore made sure that our method is able to reveal information
+about preferential readings by including ambiguous test items like
+(\ref{bsp:target-related-filler}) which are known to preferentially
+receive the late-closure reading in
+(\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
+attested early-closure reading (\ref{bsp:target-related-filler-EC})
+(Frazier 1987 XYZ).\dn{insert proper references}
+\begin{exe}
+\ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
+  suns.
+  \begin{xlist}
+  \ex \label{bsp:target-related-filler-LC} The letter is connected
+    with squares with suns and circles. \hfill (\LC)
+  \ex \label{bsp:target-related-filler-EC} The letter is connected
+    with circles with suns and squares with suns. \hfill (\EC)
+  \end{xlist}
+\end{exe}
+
+% \begin{itemize}
+% \item Fabian wants to skip the following; Petra wants to enlarge on
+%   it; I give first my version, then Petra's
+%   \begin{itemize}
+%   \item To test whether our method is indeed suitable to detect
+%     interpretation preferences, we included ambiguous test items like
+%     (\ref{bsp:target-related-filler}) which are known to
+%     preferentially receive the late-closure reading in
+%     (\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
+%     attested early-closure reading
+%     (\ref{bsp:target-related-filler-EC}).\dn{insert references to
+%       literature on EC-LC processing}
+
+%     \begin{exe}
+%     \ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
+%       suns.
+%       \begin{xlist}
+%       \ex \label{bsp:target-related-filler-LC} The letter is connected
+%         with squares with suns and circles. \hfill (\LC)
+%       \ex \label{bsp:target-related-filler-EC} The letter is connected
+%         with circles with suns and squares with suns. \hfill (\EC)
+%       \end{xlist}
+%     \end{exe}
+%   \item To test whether our method is indeed suitable to detect
+%     interpretation preferences, we included ambiguous test items like
+%     (\ref{bsp:target-related-filler}) which have been repeatedly shown
+%     to exhibit preferences in previous studies. We thus included
+%     so-called \emph{late-closure structures} in which a propositional
+%     phrase can be either attached to the immediately preceding
+%     \acro{np} (the ``late-closure'' (\LC) reading as
+%     (\ref{bsp:target-related-filler-LC})), or to an
+%     \acro{np}-coordination (the ``early-closure'' (\EC) readins as in
+%     (\ref{bsp:target-related-filler-EC})). According to principles of
+%     structural simplicity, an advantage for the \LC-reading has been
+%     repeatedly demonstrated (Frazier 1987 XYZ).\dn{insert proper
+%       references}
+%     \begin{exe}
+%     \ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
+%       suns.
+%       \begin{xlist}
+%       \ex \label{bsp:target-related-filler-LC} The letter is connected
+%         with squares with suns and circles. \hfill (\LC)
+%       \ex \label{bsp:target-related-filler-EC} The letter is connected
+%         with circles with suns and squares with suns. \hfill (\EC)
+%       \end{xlist}
+%     \end{exe}
+%     By including these structures, we intended to control whether
+%     dispreferred readings in general were still available to our
+%     participants in the specific task used.
+
+% \end{itemize}
+% \end{itemize}
+
+% To test whether our method is indeed suitable to detect interpretation
+% preferences, we included ambiguous test items like
+% (\ref{bsp:target-related-filler}) which have been repeatedly shown to
+% exhibit preferences in previous studies.
+% \begin{exe}
+% \ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
+%   suns.
+%   \begin{xlist}
+%   \ex \label{bsp:target-related-filler-LC} The letter is connected
+%     with squares with suns and circles. \hfill (\LC)
+%   \ex \label{bsp:target-related-filler-EC} The letter is connected
+%     with circles with suns and squares with suns. \hfill (\EC)
+%   \end{xlist}
+% \end{exe}
+% Sentence (\ref{bsp:target-related-filler}) is an example of a
+% so-called \emph{late-closure structure} in which a propositional
+% phrase can be either attached to the immediately preceding \acro{np}
+% (the ``late-closure'' (\LC) reading as
+% (\ref{bsp:target-related-filler-LC})), or to an \acro{np}-coordination
+% (the ``early-closure'' (\EC) readins as in
+% (\ref{bsp:target-related-filler-EC})). According to principles of
+% structural simplicity, an advantage for the \LC-reading has been
+% repeatedly demonstrated (Frazier 1987 XYZ).\dn{insert proper
+%   references}
+
+\medskip
+
+\begin{itemize}
+\item summarize results
+\end{itemize}
+
+The paper is structured as follows. Section~\ref{sec:get-know-your}
+elaborates on the three kinds of relevant readings for our target
+sentences. Section~\ref{sec:theories-predictions} works out the
+different theoretical positions and their predictions about
+availability and preference. Section~\ref{sec:previous-studies} recaps
+the results of previous studies on this subject, arguing for the need
+of a more refined methodology. Section~\ref{sec:design} describes our
+experimental design. Section~\ref{sec:results} states our results,
+which we discuss in Section~\ref{sec:discussion}.\dn{rephrase
+  eventually}
+
+\section{Get to know your readings}
+\label{sec:get-know-your}
+
+Three readings are \emph{prima facie} conceivable for the \as- and
+\es-sentences in (\ref{bsp:AE}) and (\ref{bsp:GE}). These are
+logically dependent in intricate ways.
+
+\paragraph{\as-sentences.}
+
+An \as-sentence like (\ref{bsp:AE}), repeated below, has a literal
+reading (\lit) as in (\ref{bsp:AE-Literal}), a global reading (\glb) as in
+(\ref{bsp:AE-Global}) and a local reading (\loc) as in (\ref{bsp:AE-Local}).
+
+\begin{exer}{bsp:AE}
 
@@
   \begin{xlist}
-  \ex \label{bsp:AE-Literal} \mymark{All} of the students read
+  \ex \mymark{All} of the students read
     {\mymark{some and maybe all}} of the papers. \hfill (\as-\lit)
-  \ex \label{bsp:AE-Global}
-    \mymark{All} of the students read \mymark{some} 
+  \ex
+    \mymark{All} of the students read \mymark{some and maybe all} 
     and  \hfill (\as-\glb)\\
-    \mymark{not all} of the students read \mymark{all} of the papers.
-  \ex \label{bsp:AE-Local}
+    it's not the case that \mymark{all} of the students read \mymark{all} of the papers.
+  \ex
     \mymark{All} of the students read {\mymark{some  but not all}} of the
@@
   \end{xlist}
+\end{exer}
 
+\noindent These readings stand in a strict entailment relation: the
+local reading asymmetrically entails the global reading, which
+asymmetrically entails the literal reading:
+\begin{exe}
+  \ex \label{bsp:Entailments-AS} \loc $\subset$ \glb $\subset$ \lit
+\end{exe}
+\glb entails \lit because, in general, global readings are defined as
+the conjunction of the literal reading and the negated
+(relevant/feasible) alternative(s) of the to-be-interpreted
+utterance. This entailment is asymmetric, because the information that
+not all of the students read all of the papers is not entailed by the
+literal reading. To see that \loc $\subset$ \glb, notice that the case
+where all of the students read some but not all of the papers is a
+special case of the case where all of the students read some (and
+maybe all), while not all of the students read all of the papers.
+
+Given these entailment relations, there are four kinds of situations,
+the names for which we borrow from
+\citet{ChemlaSpector2010:Experimental-Ev}, that we can distinguish
+based on different truth values for our candidate readings. These are
+given in Table~\ref{fig:situations-AE}.
+%
+\begin{table}
+  \centering
+  \subfloat[][\as-sentences]{
+  \label{fig:situations-AE}
+    \begin{tabular}{lccc}
+    \toprule
+    situation    & \multicolumn{3}{c}{truth value} 
+  \\ 
+  \cmidrule(r){2-4}
+     & \lit & \glb & \loc \\ \midrule
+    false   & 0 & 0 & 0 \\
+    literal & 1 & 0 & 0 \\
+    weak    & 1 & 1 & 0 \\
+    strong  & 1 & 1 & 1 \\ \bottomrule
+  \end{tabular}
+} \qquad \qquad
+  \subfloat[][\es-sentences]{
+  \label{fig:situations-GS}
+  \begin{tabular}{lccc}
+    \toprule
+    situation    & \multicolumn{3}{c}{truth value} 
+  \\ 
+  \cmidrule(r){2-4}
+    & \textsc{lit} & \textsc{glb} & \textsc{loc} \\ \midrule
+    false   & 0 & 0 & 0 \\
+    literal & 1 & 0 & 0 \\
+    local   & 0 & 0 & 1 \\
+    all     & 1 & 1 & 1 \\ \bottomrule
+  \end{tabular}
+}
+\caption{Possible truth-value distributions for readings of \as- and \es-sentences}
+\label{tab:situations}
+\end{table}
+%
+Examples of these kinds of situations are given in
+Figure~\ref{fig:AS-distinguishing-pics}, where the dots on the right
+of each diagram represent students, the dots on the left represent
+papers and an arrow from a student to a paper indicates that the
+student read the paper.\dn{improve graphics} Notice that other
+arrangements of arrows might equally well serve as examples for the
+various situations.
+
+\begin{figure}[]
+  \centering
+
+\subfloat[fig:false][false]{
+  \label{fig:false-AE}
+
+\begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & false \\
+            \glb & false \\
+            \loc & false 
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=blue,->] (X-1) -> (Y-1);
+
+        \path [draw=blue,->] (X-1) -> (Y-2);
+
+        \path [draw=red,->] (X-3) -> (Y-3);
+
+        \path [draw=red,->] (X-3) -> (Y-4);
+
+      \end{tikzpicture}
+
+}
+\subfloat[fig:literal][literal]{
+  \label{fig:literal-AE}
+
+  \begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & true \\
+            \glb & false \\
+            \loc & false 
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=blue,->] (X-1) -> (Y-1);
+
+        \path [draw=blue,->] (X-1) -> (Y-2);
+
+        \path [draw=blue,->] (X-1) -> (Y-3);
+
+        \path [draw=blue,->] (X-1) -> (Y-4);
+
+        \path [draw=black,->] (X-2) -> (Y-1);
+
+        \path [draw=black,->] (X-2) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-3);
+
+        \path [draw=black,->] (X-2) -> (Y-4);
+
+        \path [draw=red,->] (X-3) -> (Y-1);
+
+        \path [draw=red,->] (X-3) -> (Y-2);
+
+        \path [draw=red,->] (X-3) -> (Y-3);
+
+        \path [draw=red,->] (X-3) -> (Y-4);
+
+      \end{tikzpicture}
+
+}
+\subfloat[fig:weak][weak]{
+  \label{fig:weak}
+
+\begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & true \\
+            \glb & true \\
+            \loc & false 
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=blue,->] (X-1) -> (Y-1);
+
+        \path [draw=blue,->] (X-1) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-1);
+
+        \path [draw=black,->] (X-2) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-3);
+
+        \path [draw=black,->] (X-2) -> (Y-4);
+
+        \path [draw=red,->] (X-3) -> (Y-3);
+
+        \path [draw=red,->] (X-3) -> (Y-4);
+
+      \end{tikzpicture}
+
+}
+\subfloat[fig:strong][strong]{
+  \label{fig:strong}
+
+\begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & true \\
+            \glb & true \\
+            \loc & true 
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=blue,->] (X-1) -> (Y-1);
+
+        \path [draw=blue,->] (X-1) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-3);
+
+        \path [draw=red,->] (X-3) -> (Y-3);
+
+        \path [draw=red,->] (X-3) -> (Y-4);
+
+      \end{tikzpicture}
+
+}
+
+  \caption{Distinguishing scenarious for \as-sentences}
+  \label{fig:AS-distinguishing-pics}
+\end{figure}
+
+\paragraph{\es-sentences.}
+
+The situation for \es-sentences like (\ref{bsp:GE}) is similar but a
+little more complicated because the embedding quantifier is
+non-monotonic. Again, we consider a literal reading as in
+(\ref{bsp:GE-Literal}), repeated below, a global reading as in
+(\ref{bsp:GE-Global}) and a local reading as in (\ref{bsp:GE-Local}).
+
+\begin{exer}{bsp:GE}
 \ex \mymark{Exactly one} of the students read {\mymark{some}} of the
@@
   \begin{xlist}
-  \ex \label{bsp:GE-Literal} \mymark{Exactly one} of the students read
+  \ex \mymark{Exactly one} of the students read
     {\mymark{some and maybe all}} of the papers. \hfill (\es-\lit)
-  \ex \label{bsp:GE-Global}
-    \mymark{Exactly one} of the students read \mymark{some} 
+  \ex 
+    \mymark{Exactly one} of the students read \mymark{some and maybe all} 
     and  \hfill (\es-\glb)\\
-    \mymark{not all} of the students read \mymark{all} of the papers.
-  \ex \label{bsp:GE-Local}
+    it's not the case that \mymark{exactly one} of the students read \mymark{all} of the papers.
+  \ex 
     \mymark{Exactly one} of the students read {\mymark{some  but not all}} of the
@@
   \end{xlist}
+\end{exer}
 
-\ex \label{bsp:AE-Alternative} \mymark{All} of the students read
-  {\mymark{all}} of the papers.
+\noindent Entailment relations in this case are non-linear:
+\begin{exe}
+  \ex \label{bsp:Entailments-GE}       \lit\ $\supset$ \glb\ $\color{mycol}{\subset}$ \loc 
+    % \hspace{1cm} and \hspace{1cm}  \lit\ $\not \supset$ \loc
+\end{exe}
+By definition of global readings $\glb$ entails $\lit$. This
+entailment is asymmetric because the extra information that it is not
+the case that exactly one student read all of the papers is not
+entailed by the literal reading (\ref{bsp:GE-Literal}). However,
+unlike for \as-sentences, \loc is not stronger than \glb, but
+asymmetrically entailed by the latter. To see this, notice that the
+global reading is equivalent to:
 
-\ex \label{bsp:GE-Alternative} \mymark{Exactly one} of the students
-  read {\mymark{all}} of the papers.
-
+\begin{exe}
+  \exp{bsp:GE-Global} \mymark{Exactly one} of the students read \mymark{some but not
+    all} and \\
+  \mymark{everybody else} read \mymark{none} of the papers.
 \end{exe}
 
-\noindent Section~\ref{sec:get-know-your} will discuss these reading
-in more detail and, by giving some helpful illustrations, make clear
-that these readings are all distinct but logically dependent
-on each other in interesting ways.
+\noindent Finally, \loc and \lit are logically independent: all
+possible combinations of truth-values for \loc and \lit are possible.
 
-The main question we are interested in here is which of these three
-conceivable readings is available to subjects na\"{i}ve to all
-pragmatic theory. We are moreover interested in the more refined
-question which of the available readings na\"{i}ve subjects prefer.
+Given these entailment relations, there are again four different
+situations corresponding to the four possible distributions of truth
+values for candidate readings. These are given in
+Table~\ref{fig:situations-GS} and named following
+\citet{ChemlaSpector2010:Experimental-Ev}. Examples for each situation
+are given in Figure~\ref{fig:ES-distinguishing-pics}.
 
-Addressing these issues empirically is highly relevant because they
-lie at the heart of the current debate of the exact location and
-nature of the interface between semantics and pragmatics. There are
-three major camps which are ---more or less fiercely--- involved in
-this border war, all of which make different predictions about
-availability and preferences of readings. We will give a more detailed
-description of the various theoretical positions below in
-Section~\ref{sec:theories-predictions}, but on a first rough
-approximation the situation is the following. Firstly, there are
-\mymark{pragmatic traditionalists} who seek to conserve the spirit of
-\citeauthor{Grice1975:Logic-and-Conve}'s
-(\citeyear{Grice1975:Logic-and-Conve}) original ideas as much as
-possible
-\citep[e.g.][]{Spector2006:Scalar-Implicat,Sauerland2004:Scalar-Implicat,Russell2006:Against-Grammat,vanRooijSchulz:ExhaustiveInterpretation,Geurts2010:Quantity-Implic,Franke2011:Quantity-Implic}.
-Traditionalists
-happily acknowledge the existence of global readings, but might
-consider local readings either unavailable or a beast distinct from
-scalar implicatures. Opposed to that is the camp of \mymark{lexical
-  conventionalists}
-\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}
-who maintain that scalar \emph{some} is lexically ambiguous between
-the standard logical meaning \emph{some and maybe all} and the
-upper-bounded meaning \emph{some but not all}. As the latter is
-considered a default, lexical conventionalism has no problem
-accounting for local readings, and in fact would consider these the
-preferred readings. Thirdly and finally, there is the camp of
-\mymark{grammaticalists} who defend that the distribution of
-upper-bounded readings of \emph{some} is best explained by postulating
-a silent operator, akin to the meaning of the particle \emph{only}
-\citep{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Sauerland2012:The-Computation}. According
-to the grammatical view, this silent operator may be applied in
-compositional semantics also in the scope of other logical operators,
-but the availability of readings is constraint by the \emph{strongest
-  meaning hypothesis}
-\citep{DalrympleKanazawa1998:Reciprocal-Expr}. Details follow in
-Section~\ref{sec:theories-predictions}, but suffice it to just state
-already that grammaticalist theories predict that all three types of
-readings are available. Moreover, according to the grammatical view,
-the local reading is preferred for \as-sentences, while the global one
-is preferred for \es-sentences. (More precisely, but see
-Section~\ref{sec:theories-predictions}, depending on the variant of
-the strongest meaning hypothesis employed, either the global reading
-is predicted to be preferred for \es-sentences, or the global and the
-local reading are predicted to be equally preferred.)
+\begin{figure}[]
+  \centering
 
-\bigskip
+\subfloat[fig:false][false]{
+  \label{fig:false-GE}
 
-\section{Get to know your readings}
-\label{sec:get-know-your}
+  \begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & false \\
+            \glb & false \\
+            \loc & false 
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=blue,->] (X-1) -> (Y-1);
+
+        \path [draw=blue,->] (X-1) -> (Y-2);
+
+        \path [draw=red,->] (X-3) -> (Y-3);
+
+        \path [draw=red,->] (X-3) -> (Y-4);
+
+      \end{tikzpicture}
+
+}
+\subfloat[fig:literal][literal]{
+  \label{fig:literal-GE}
+
+      \begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & true \\
+            \glb & false \\
+            \loc & false 
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=black,->] (X-2) -> (Y-1);
+
+        \path [draw=black,->] (X-2) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-3);
+
+        \path [draw=black,->] (X-2) -> (Y-4);
+
+      \end{tikzpicture}
+
+}
+\subfloat[fig:local][local]{
+  \label{fig:local}
+
+            \begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & false \\
+            \glb & false \\
+            \loc & true 
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=blue,->] (X-1) -> (Y-1);
+
+        \path [draw=blue,->] (X-1) -> (Y-2);
+
+        \path [draw=blue,->] (X-1) -> (Y-3);
+
+        \path [draw=blue,->] (X-1) -> (Y-4);
+
+        \path [draw=black,->] (X-2) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-3);
+
+        \path [draw=black,->] (X-2) -> (Y-4);
+
+        \path [draw=red,->] (X-3) -> (Y-1);
+
+        \path [draw=red,->] (X-3) -> (Y-2);
+
+        \path [draw=red,->] (X-3) -> (Y-3);
+
+        \path [draw=red,->] (X-3) -> (Y-4);
+
+      \end{tikzpicture}
+
+}
+\subfloat[fig:all][all]{
+  \label{fig:all}
+
+      \begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & true \\
+            \glb & true \\
+            \loc & true 
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=blue,->] (X-1) -> (Y-1);
+
+        \path [draw=blue,->] (X-1) -> (Y-2);
+
+      \end{tikzpicture}
+
+}
+
+  \caption{Distinguishing scenarious for \es-sentences}
+  \label{fig:ES-distinguishing-pics}
+
+\end{figure}
 
@@
 
+We consider three main theoretical positions which make different
+predictions about the readings of \as- and \es-sentences
+\citep[c.f.][for
+overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation}. We
+will refer to these here as \mymark{traditionalism},
+\mymark{conventionalism} and \mymark{grammaticalism} and treat each
+one in turn. Since there is some leeway in assessing the predictions
+for some of these positions (depending on which of several reasonable
+additional assumptions we should adopt), we will distinguish different
+varieties of each position. For convenience, the predictions of each
+(variety of each) position are also summarized in
+Table~\ref{tab:predictions} at the end of this section.\dn{micha says:
+I'll leave all the varieties in here until we know which ones we need
+and which ones we don't need}
+
+\subsection{Traditionalism}
+\label{sec:traditionalism}
+
+We refer to traditionalism as traditionalism because of its
+conservative stance towards Grice's original theory of conversational
+implicatures \citep{Grice1975:Logic-and-Conve}. Many author's have
+defended traditionalist positions in this sense. Of the more recent
+literature, we would consider as traditionalist, among others,
+contributions by \citet{Spector2006:Scalar-Implicat},
+\citet{Sauerland2004:Scalar-Implicat},
+\citet{Russell2006:Against-Grammat},
+\citet{vanRooijSchulz:ExhaustiveInterpretation},
+\citet{Geurts2010:Quantity-Implic} or
+\citet{Franke2011:Quantity-Implic}.
+
+According to Grice, conversational implicatures, of which quantity
+implicatures are a special case, are to be thought of as
+rationalizations of speaker behavior. Central in this reasoning is the
+assumption that the speaker's behavior is efficient (if not optimal)
+and goal-oriented. Usually, the assumed goal of conversation is the
+cooperative exchange of helpful information from the speaker to the
+hearer.
+
+Consequently, the \mymark{Gricean recipe}
+\citep[c.f.][]{Geurts2010:Quantity-Implic} for deriving a simple
+scalar inference like that in (\ref{bsp:Plain-SI-Implicature}) from an
+utterance of (\ref{bsp:Plain-SI-Target}) is as follows: if the issue
+whether Hans solved only some or all of the problems is relevant, then
+a cooperative and knowledgable speaker would utter
+(\ref{bsp:Plain-SI-Alternative}) if in a position to do so; hence, one
+of the most natural explanations of why such a speaker has not uttered
+(\ref{bsp:Plain-SI-Alternative}), but only (\ref{bsp:Plain-SI-Target})
+is that she is uncertain of whether (\ref{bsp:Plain-SI-Alternative})
+is true; but on the assumption that she is knowledgeable (competent,
+opinionated, informed \dots) it follows that
+(\ref{bsp:Plain-SI-Implicature}) should in fact be true.\fn{We are
+  glossing here somewhat swiftly over the more nuanced details of the
+  derivation of implicatures targeting the speaker's epistemic state
+  \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit},
+  as this is not crucially relevant for the issues we are interested
+  in here.}\textsuperscript{,}\dn{do we need to enlarge on epistemic
+  implicatures?}
+
+\begin{exer}{bsp:Plain-SI}
+  \ex 
+    \begin{xlist}
+      \ex \label{bsp:Plain-SI-Target} Hans solved \mymark{some} of the problems.
+      \ex \label{bsp:Plain-SI-Implicature} $\implicates$ Hans solved
+        \mymark{some but not all} of the problems.
+      \ex  \label{bsp:Plain-SI-Alternative}  Hans solved \mymark{all} of the problems.
+    \end{xlist}
+\end{exer}
+
+The Gricean recipe applies also to \as- and \es-sentences and derives
+the global reading in a straightforward way. Consequently,
+traditionalism predicts that both literal and global readings are
+available: literal readings, because these form the starting point of
+pragmatic reasoning; global readings because these may be arrived at
+by the Gricean recipe.
+
+Which of these readings, if any, does traditionalism predict to be
+preferred? This depends on whether the auxiliary assumptions necessary
+to derive global readings by the Gricean recipe are plausibly met in
+the particular case of utterance of \as- and \es-sentences. These
+auxiliary assumptions include relevance of the extra information
+provided in the global reading, mutual awareness that the stronger
+alternative has been a speaker option, the speaker's competence about
+the issue, etc. Normally, traditionalist accounts would assume that
+these extra assumptions are met. In that case, traditionalism would
+predict that the global readings should be preferred over the literal
+readings. On the other hand, it might also be hypothesized that, for
+example, a competence assumption is harder to justify for \as- and
+\es-sentences in general than for simpler sentences such as
+(\ref{bsp:Plain-SI}), because of the additional quantificational
+element: it might be less clear that the speaker knows exactly how
+many students solved how many problems, than that the speaker knows
+exactly how many problems, e.g., Hans solved. In that case, or if any
+other assumption of the Gricean recipe cannot be maintained,
+traditionalism would predict that the literal reading would be
+preferred over the global one. But that means that there are at least
+two varieties of traditionalism that, depending on which additional
+assumptions we would make, yield slightly different predictions:
+\mymark{the strong variety of traditionalism} maintains that the
+auxiliary assumptions of the Gricean recipe hold
+usually/strongly/unless-completely-intenable and therefore predicts
+that global readings are preferred over the literal ones; \mymark{the
+  weak variety of traditionalism} holds that the auxiliary assumptions
+are more fragile and predicts that literal readings are preferred over
+the global ones.\fn{We mention for clarity that although weak
+  traditionalism does not predict the global reading to be preferred,
+  it might still predict an \emph{epistemically weak implicature},
+  similar to the global reading, that the speaker is uncertain whether
+  the stronger alternative is true. Whether it does predict that
+  depends on which auxiliary assumption are assumed to be met and
+  which are not.}\dn{acknowledge comment by Philippe Schlenker
+  here;possibly expand}
+
+Does traditionalism also predict local readings to be available?  The
+answer is slightly different for \as- and the \es-sentences. For
+\es-sentences, traditionalism does not predict that a local reading is
+available, at least not as a quantity implicature
+\citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. This
+is because traditionalism assumes that quantity implicatures are
+pragmatic enrichments of the literal meaning of an utterance, obtained
+by conjoining the literal meaning with a suitable set of negated
+alternatives. But since the literal and the local reading of
+\es-sentences are logically independent, there is no way that local
+readings can be derived in a traditionalist manner as a quantity
+implicature: if $X$ and $Y$ are logically independent propositions,
+then there is no proposition $Z$ such that $X$ would be equivalent to
+$Y \wedge \neg Z$. Traditionalism often does concede that (something
+like) local readings can occur if scalar items are marked with
+\emph{special intonation}, albeit then as a signal of a different
+pragmatic process
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic}. We
+will come back to this issue in Section~\ref{sec:role-intonation}.
+
+On the other hand, as for \as-sentences, there is a traditionalist way
+of deriving the local reading, namely by assuming that not only
+(\ref{bsp:AE-Alternative}) is an alternative to (\ref{bsp:AE}), but
+also the sentence in (\ref{bsp:AE-Alternatives-Extended}).
+
+\begin{exer}{bsp:AE}
+  \ex \mymark{All} of the students solved \mymark{some} of the problems.
+\end{exer}
+
+\begin{exer}{bsp:AE-Alternative}
+  \ex \mymark{All} of the students solved \mymark{all} of the problems.
+\end{exer}
+
+\begin{exe}
+\ex \label{bsp:AE-Alternatives-Extended} \mymark{Some} of the students solved \mymark{all} of the problems.
+\end{exe}
+
+\noindent Clearly, if we conjoin a literal reading of (\ref{bsp:AE})
+with the negation of (\ref{bsp:AE-Alternatives-Extended}) we obtain
+exactly the local reading. (Notice that the negation of
+(\ref{bsp:AE-Alternatives-Extended}) entails the negation of
+(\ref{bsp:AE-Alternative}), so it makes no difference (not) to add it
+in this case.) Consequently, traditionalism does predict that the
+local reading of \as-sentences is available if
+(\ref{bsp:AE-Alternatives-Extended}) is an available alternative. We
+should therefore introduce another distinction: \mymark{restricted
+  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
+not available and therefore predicts that the local reading for
+\as-sentences is not available; in contrast, \mymark{unrestricted
+  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
+available and so is the local reading.
+
+Still, even unrestricted traditionalism would not predict that the
+local reading is preferred over the global reading. This is because
+the derivation of the local reading via
+(\ref{bsp:AE-Alternatives-Extended}) hinges on yet another auxiliary
+assumption, namely the availability of the alternative in
+(\ref{bsp:AE-Alternatives-Extended}), which seems much less obvious
+and therefore presumably is less readily available than the
+alternative in (\ref{bsp:AE-Alternative}). Consequently, we derive the
+following predictions about preferences for unrestricted
+traditionalism: weak unrestricted traditionalism prefers the literal
+over the global over the local reading, while strong unrestricted
+traditionalism prefers the global over the local over the literal
+reading (see also Table~\ref{tab:predictions}).
+
+\subsection{Conventionalism}
+\label{sec:conventionalism}
+
+Lexical conventionalism is a position that has been defended for
+instance by \citet{LevinsonPresumptiveMeanings2000} and
+\citet{Chierchia:2004_ScalarImplicatures}.\fn{See also
+  \citet{Sauerland2012:The-Computation} who argues quite favorably for
+  a pragmatically informed conventionalism, although eventually
+  dismissing it in favor of grammaticalism.} The general idea is that
+if the upper-bounding inference from \emph{some} to \emph{some but not
+  all} occurs frequently, then it would be inefficient to execute the
+Gricean reasoning that traditionalists propose over and over
+again. Conventionalism therefore assumes that scalar inferences have
+become routinized, hard-wired, so much so that there are two lexical
+entries for a scalar item like \emph{some}, one with meaning
+\emph{some and maybe all} and one with the meaning \emph{some but not
+  all}. \citet{LevinsonPresumptiveMeanings2000} proposed that the
+latter is the preferred default meaning, a position which we will
+refer to as \mymark{defaultism}.\fn{Levinson's defaultism has strong
+  empirical evidence against it, because several processing studies
+  show that the computation of scalar inferences appears to be time-
+  and effort-consuming, when they \emph{do} arise, not when they
+  \emph{don't}, as defaultism would have it
+  \citep[c.f.][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
+  there is also competing evidence that scalar inferences are
+  immediate, low-level processes
+  \citep{GrodnerKlein2010:Some-and-Possib}.}\dn{Petra says: empirical
+  stuff in footnote irrelevant; I agree, let's move it to discussion
+  section} For completeness sake, we will call the opposite view that
+the literal meanings are \emph{ceteris paribus} preferred
+\mymark{literalism}\dn{better name?}. We are not aware that anyone has
+defended this option, but we will come back to this later on.\dn{where
+  exactly}
+
+Both varieties of conventionalism make interesting predictions about
+available readings for \as- and \es-sentences. Unaided,
+conventionalism does not predict that global readings are
+available. The lexically stored upper-bound for scalar \emph{some}
+only allows to derive literal and local readings. Moreover, defaultism
+predicts that local readings are preferred over literal ones. Contrary
+to that, our dummy position of literalism predicts that literal
+readings are preferred over local ones.\dn{Petra says that his is too
+  short; suggests skipping the whole section; I'm not sure; could do
+  that too; anyway, it must be mentioned because conventionalism turns
+  out to be one of the best predictors of our data;}
+
+\subsection{Grammaticalism}
+\label{sec:grammaticalism}
+
+The third and final kind of theoretical position we consider is
+\mymark{grammaticalism}. Recently, a lot of evidence based on
+intuitive judgements and more theoretical considerations has been
+discussed in favor of this position
+\citep[c.f.][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}. % When
+% it comes to the predictions of available readings of \as- and
+% \es-sentences, grammaticalism appears like the conjunction of
+% traditionalism and conventionalism. But conceptually speaking,
+% grammaticalism goes down a road of its own.
+Grammaticalism approaches quantity implicatures by postulating a
+silent operator that can be variably applied during compositional
+computation of a sentence's truth-value
+\citep{Chierchia2006:Broaden-Your-Vi}, if necessary multiple times
+\citep{Fox2007:Free-Choice-and}. This silent operator is variably
+referred to as $\mathrm{O}(\cdot)$ or $\exh(\cdot)$, because it is
+assumed to be similar in effect to the meaning of particle \emph{only}
+or of the mechanism of \emph{exhaustive interpretation}
+\citep{GroenendijkStokhofThesis1984,Stechowvon-StechowZimmermann1984:Term-Answers-an,Rooijvan-RooijSchulz2013:Exhaustive-Inte,vanRooijSchulz:ExhaustiveInterpretation,Fox2007:Free-Choice-and}. For
+our purposes, it is enough to note that $\exh(\cdot)$ is a
+poly-typed function that enriches an expression $X$, which crucially
+need not be a full proposition, based on a set, $\alt(X)$, of
+(suitable, relevant) alternatives to $X$ that yields an enriched
+meaning of the form:\fn{More sophisticated formulations of exhaustive
+  interpretation have been proposed
+  \citep[e.g.][]{Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}
+  but this simple formulation is sufficient for the purposes of this
+  paper. Also, we gloss here over non-trivial details in the way this
+  operation is to be specified exactly within a compositional
+  semantics \citep[c.f.][]{Chierchia2006:Broaden-Your-Vi}.}
+\begin{exe}
+  \ex \label{bsp:Exh-Def} $\exh(X,\alt(X)) = X \bigwedge_{A \in
+      \alt(X)} \neg A$.
+\end{exe}
+
+As this operator can apply at various scope sites, the grammatical
+approach predicts that all three readings of \as- and \es-sentences
+are available: literal readings arise if no exhaustification operator
+is applied; global readings arise if the exhaustification operator
+takes sentence-wide scope as in (\ref{Grammar-Global}); and local
+readings arise if the exhaustification operator takes scope under the
+respective quantifiers as in (\ref{Grammar-Local}).
+
+\begin{exe}
+  \ex \label{Grammar-Global}
+    \begin{xlist}
+      \ex \label{Grammar-Global-AE} \mymark{$\exh$}(\mymark{All} of the students solved
+        \mymark{some} of the problems).
+      \ex \label{Grammar-Global-GE} \mymark{$\exh$}(\mymark{Exactly one} of the students solved
+        \mymark{some} of the problems).
+    \end{xlist}
+\end{exe}
+
+\begin{exe}
+  \ex \label{Grammar-Local}
+    \begin{xlist}
+      \ex \label{Grammar-Local-AE} \mymark{All} of the students \mymark{$\exh$}(solved
+        \mymark{some} of the problems).
+      \ex \label{Grammar-Local-GE} \mymark{Exactly one} of the
+        students \mymark{$\exh$}( solved
+        \mymark{some} of the problems).
+    \end{xlist}
+\end{exe}
+
+The grammatical approach, as described so far, is rather flexible in
+that it makes many readings available. It is so flexible, in fact,
+that it must be constrained in some way or other to shield the
+approach against overgeneration. The easiest examples where this is
+crucial are occurrences of scalar items in downward-entailing
+environments, such as in:
+
+\begin{exe}
+\ex \label{bsp:Overgenereation-target} It's \mymark{not} the case that
+  Hans solve \mymark{some} of the problems.
+\end{exe}
+
+\noindent An assertion of (\ref{bsp:Overgeneration-continued})
+normally would be taken to convey
+(\ref{bsp:Overgenereation-implicature-attested}), not the disjunctive
+meaning in (\ref{bsp:Overgenereation-implicature-UNattested}).
+
+\begin{exe}
+\ex 
+  \begin{xlist}
+  \ex \label{bsp:Overgenereation-implicature-attested} Hans solves \mymark{none} of the problems.
+  \ex \label{bsp:Overgenereation-implicature-UNattested} Hans solved
+    \mymark{none or all} of the problems 
+  \end{xlist}
+\end{exe}
+
+\noindent The latter, however, is a reading that grammaticalism
+predicts to be available by letting the $\exh(\cdot)$-operator take
+scope under negation, as in:
+
+\begin{exe}
+\ex It's not the case that Hans solved \mymark{$\exh$}(\mymark{some} of the problems)
+\end{exe}
+
+\noindent Indeed, this reading is not unattested, for witness a
+continuation of (\ref{bsp:Overgenereation-target}) as in:
+\begin{exe}
+\ex \label{bsp:Overgeneration-continued} It's \mymark{not} the case that Hans
+  solve \mymark{\emph{some}} of the problems. He solved
+  \mymark{\emph{all}} of them.
+\end{exe}
+
+\noindent But this reading seems to be marked, in that it requires
+exceptional contextual circumstances and a non-standard intonational
+stress.
+
+To account for the markedness of certain examples, grammaticalism is
+therefore aided by a principle that specifies which readings are to be
+preferred if several readings are generated by optional applications
+of $\exh(\cdot)$ in the compositional computation of semantic
+values. The principle that grammaticalists adhere to
+\citep[c.f.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}
+is the \mymark{strongest meaning hypothesis} of
+\citet{DalrympleKanazawa1998:Reciprocal-Expr}. Roughly speaking, if a
+given sentence has several conceivable readings, the strongest meaning
+hypothesis selects for the strongest of
+these. \citet{ChierchiaFox2008:The-Grammatical} discuss two concrete
+variants of the strongest meaning hypothesis. Towards a definition
+that is just precise enough for our current purposes, fix a sentence
+with propositional content $S$ with candidate readings $C(S)$, where
+$C(S)$ contains $S$ and all readings derivable from inserting
+$\exh(\cdot)$ at suitable scope sites.\fn{Strictly speaking, we should
+  compare \emph{parses} of sentences with $\exh(\cdot)$ at various
+  scope sites with respect to the readings that these parses give rise
+  to \citep[c.f.][]{ChierchiaFox2008:The-Grammatical}, but we may
+  ignore this detail here for ease of exposition.}  Then define
+\emph{ceteris paribus} preferences among members of $X,Y \in C(S)$ as
+either:
+\begin{exe}
+\ex \label{bsp:SMH-Total} 
+  $X >_w Y$ iff $X \subset Y$ 
+  \attrib{\citep[(104)]{ChierchiaFox2008:The-Grammatical}}
+\end{exe}
+or:
+\begin{exe}
+\ex \label{bsp:SMH-Partial}  $X >_s Y$ iff $X \subset Y$ and $X$ and
+  $Y$ are readings obtained from applications of $\exh(\cdot)$ at
+  exactly the same scope sites, except for one.
+  \attrib{\citep[(105)]{ChierchiaFox2008:The-Grammatical}} 
+\end{exe}
+Since $X >_s Y$ entails $X >_w Y$, we will speak of \mymark{weak
+  grammaticalism} and \mymark{strong grammaticalism}, depending on
+whether (\ref{bsp:SMH-Total}) or (\ref{bsp:SMH-Partial}) is used.
+
+These two varieties of grammaticalism give rise to different
+predictions about preferred readings. The preference for readings that
+weak grammaticalism predicts mirrors the entailment relations in
+(\ref{bsp:Entailments-AS}) and (\ref{bsp:Entailments-GE}): for
+\as-sentences weak grammaticalism predicts that local readings are
+preferred over global readings which in turn are preferred over
+literal readings; for \es-sentences strong grammaticalism predicts
+that global readings are most preferred, while literal and local
+readings are not ranked with respect to preference. Strong
+grammaticalism, on the other hand, predicts that both \as- and
+\es-sentences preferably get either a local or a global reading rather
+than a literal reading. But strong grammaticalism does not rank these
+former two with respect to each other because they differ in more than
+one application of the $\exh(\cdot)$ operator.
+
+\medskip
+
+Taking stock, traditionalism, conventionalism and grammaticalism
+predict different patterns of availability and preference for \as- and
+\es-sentences. Most notably, traditionalism does not predict local
+readings for \es-sentences to be available, while conventionalism does
+not predict any global readings to be available. Grammaticalism
+predicts that all readings are available, but, given the strongest
+meaning hypothesis, also comes with a clear indication of preference:
+literal meanings are dispreferred. All predictions are summarized in
+Table~\ref{tab:predictions}.
+
+\begin{table}[t]
+  \centering
+  \begin{tabular}{lcc}
+    & \multicolumn{2}{c}{preference \& availability}
+    \\ \cmidrule(r){2-3}
+    theoretical position
+    & \as
+    & \es
+    \\ \midrule
+    traditionalism
+    \\
+    \ \ weak restricted 
+    & \lit > \glb 
+    & \lit > \glb
+    \\
+    \ \ weak unrestricted
+    & \lit > \glb > \loc 
+    & \lit > \glb
+    \\
+    \ \ strong restricted
+    & \glb > \lit 
+    & \glb > \lit
+    \\
+    \ \ strong unrestricted
+    & \glb > \loc > \lit 
+    & \glb > \lit
+    \\
+    conventionalism
+    \\
+    \ \ defaultism
+    & \loc >  \lit 
+    & \loc >  \lit
+    \\
+    \ \ literalism
+    & \lit >  \loc 
+    & \lit >  \loc
+    \\
+    grammaticalism
+    \\
+    \ \ weak
+    & \loc > \glb > \lit 
+    & \glb > \lit, \loc
+    \\
+    \ \ strong
+    & \glb, \loc > \lit 
+    & \glb, \loc >  \lit
+    \\
+  \end{tabular}
+  \caption{Predictions of the relevant theoretical positions. Listed
+    are the predicted preference relations. If a reading is not
+    listed, it is predicted to be unavailable.}
+  \label{tab:predictions}
+\end{table}
+
+% \begin{table}[t]
+%   \centering
+%   \begin{tabular}{lcccccc}
+%     & \multicolumn{4}{c}{availability} 
+%     & \multicolumn{2}{c}{preference}
+%     \\ \cmidrule(r){2-5}  \cmidrule(r){6-7}
+%     theoretical position
+%     & \as-\glb
+%     & \as-\loc
+%     & \es-\glb
+%     & \es-\loc
+%     & \as
+%     & \es
+%     \\ \midrule
+%     traditionalism
+%     \\
+%     \ \ weak restricted 
+%     & $\checkmark$
+%     & $-$
+%     & $\checkmark$
+%     & $-$
+%     & \lit > \glb 
+%     & \lit > \glb
+%     \\
+%     \ \ weak unrestricted
+%     & $\checkmark$
+%     & $\checkmark$
+%     & $\checkmark$
+%     & $-$
+%     & \lit > \glb > \loc 
+%     & \lit > \glb
+%     \\
+%     \ \ strong restricted
+%     & $\checkmark$
+%     & $-$
+%     & $\checkmark$
+%     & $-$
+%     & \glb > \lit 
+%     & \glb > \lit
+%     \\
+%     \ \ strong unrestricted
+%     & $\checkmark$
+%     & $\checkmark$
+%     & $\checkmark$
+%     & $-$
+%     & \glb > \loc > \lit 
+%     & \glb > \lit
+%     \\
+%     conventionalism
+%     \\
+%     \ \ defaultism
+%     & $-$
+%     & $\checkmark$
+%     & $-$
+%     & $\checkmark$
+%     & \loc >  \lit 
+%     & \loc >  \lit
+%     \\
+%     \ \ literalism
+%     & $-$
+%     & $\checkmark$
+%     & $-$
+%     & $\checkmark$
+%     & \lit >  \loc 
+%     & \lit >  \loc
+%     \\
+%     grammaticalism
+%     \\
+%     \ \ weak
+%     & $\checkmark$
+%     & $\checkmark$
+%     & $\checkmark$
+%     & $\checkmark$
+%     & \loc > \glb > \lit 
+%     & \glb > \lit, \loc
+%     \\
+%     \ \ strong
+%     & $\checkmark$
+%     & $\checkmark$
+%     & $\checkmark$
+%     & $\checkmark$
+%     & \glb, \loc > \lit 
+%     & \glb, \loc >  \lit
+%     \\
+%   \end{tabular}
+%   \caption{Predictions of the relevant theoretical positions}
+%   \label{tab:predictions}
+% \end{table}
+
 \section{Previous studies}
 \label{sec:previous-studies}
+
+In order to disentangle the divergent predictions of these opposing
+theoretical positions, a number of empirical studies have been carried
+out. In this section, we will focus on the influential studies by
+\citet{GeurtsPouscoulous2009:Embedded-Implic},
+\citet{CliftonDube2010:Embedded-Implic} and
+\citet{ChemlaSpector2010:Experimental-Ev}. Unfortunately, as we argue
+here, the conjoined evidence from all of these studies is inconclusive
+as to the availability and preference of relevant readings.
+
+\subsection{\citet{GeurtsPouscoulous2009:Embedded-Implic}}
+\label{sec:Geurts-and-Pouscoulous}
+
+\citet{GeurtsPouscoulous2009:Embedded-Implic} conducted a
+picture-verification task to find out whether local readings of \as-
+and \es-sentences are available.\fn{Actually,
+  \citet{GeurtsPouscoulous2009:Embedded-Implic} did not use
+  \es-sentences, but sentences where scalar \emph{some} was embedded
+  under non-monotonic quantifier \emph{exactly two} (with appropriate
+  pictures, of course). This case is a little more complex, but we
+  will gloss over this here, treating their data, as if it was obtained
+  for \es-sentences.} The critical conditions of their study presented
+subjects with pictures like those in Figure~\ref{fig:weak} and
+\ref{fig:local} where the local reading gets a different truth-value
+from the literal and the global reading. In particular, for
+\as-sentences the local reading is false for the critical picture in
+Figure~\ref{fig:weak} whereas the literal and global readings are
+true; for \es-sentences the local reading is true for the critical
+picture in Figure~\ref{fig:local}, whereas the literal and global
+readings are false.\dn{Petra wants more detail in the description of
+  this study; I'm not sure that this is needed...?}
+
+The results of \citeauthor{GeurtsPouscoulous2009:Embedded-Implic} were
+strikingly unambiguous: there were \emph{no} responses indicative of a
+local reading; \emph{all} of the subjects judged \as-sentences true in
+a situation like in Figure~\ref{fig:weak} and \emph{all} of the
+subjects judged \es-sentences false in situations like
+\ref{fig:local}.
+
+These results were criticized on theoretical grounds (e.g.,
+\citet{Sauerland2010:Embedded-Implic}, but see
+\citet{Ippolito2010:Embedded-Implic} for supporting evidence), as well
+as based on empirical observations
+\citep{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. In
+the following, we will review these empirical studies in some detail,
+as they constitute an important background for our own experiment. We
+will first consider a comment by
+\citet{CliftonDube2010:Embedded-Implic}, which explicitly
+distinguishes between the availability of a reading and its
+preference.
+
+\subsection{\citet{CliftonDube2010:Embedded-Implic}}
+\label{sec:clifton-dube}
+
+In a reply to \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s
+study \citeauthor{CliftonDube2010:Embedded-Implic} raised the question
+whether the use of a picture-verification paradigm might have been
+infelicitous for testing the availability of strong readings, at least
+in the case of \as-sentences. Asking whether a sentence fits a picture
+might have created a bias for accepting sentences also on a weaker and
+probably dispreferred reading. Clifton and Dube's study was therefore
+aimed at finding out about a potential preference relation between
+local and literal readings. To this end, Clifton and Dube developed a
+picture-choice task where subjects were presented with an AS-sentence
+and a pair of pictures, hence introducing the option to choose between
+different alternatives. Subjects were asked to ``indicate which shape
+is best described by the sentence'' and could choose either picture,
+or options `both' and `neither.' There were two versions of this
+experiment, differing in which kind of picture pairs were presented on
+critical trials. In version 1, the picture pair consisted of the weak
+and strong situations in Figures~\ref{fig:weak} and
+\ref{fig:strong}. The response percentages observed by
+\citeauthor{CliftonDube2010:Embedded-Implic} were:
+
+\begin{center}
+  \begin{tabular}{cccc}
+    weak & strong & both & neither
+    \\ \midrule 
+ 3 & 39 & 57 & 1 
+  \end{tabular}
+\end{center}
+
+\noindent That the majority answer is ``both'' could be taken as
+evidence that the literal reading is the preferred one. But the almost
+40\% of choices for the strong situation, so
+\citeauthor{CliftonDube2010:Embedded-Implic} argue, might be
+indicative of the availability of the local reading. In version 2 of
+the experiment, the picture pair consisted of the literal and weak
+situations in Figures~\ref{fig:literal-AE} and \ref{fig:weak}. In this
+case, response percentages were:
+
+\begin{center}
+  \begin{tabular}{cccc}
+    weak & literal & both & neither
+    \\ \midrule 
+    28 & 6 & 50 & 17 
+  \end{tabular}
+\end{center}
+
+\noindent Again the majority response ``both'' might speak for a
+preference for the literal reading, but, as
+\citeauthor{CliftonDube2010:Embedded-Implic} propose, the 17\% of
+``neither'' answers in this case again suggest that the local reading
+is available. Taken together,
+\citeauthor{CliftonDube2010:Embedded-Implic} take these results to
+contradict \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s
+findings. Local readings are, after all, attested if subjects are
+given a choice as to which situation they consider most fitting for an
+\as-sentence.
+
+Taken together, the results by Clifton and Dube demonstrate that
+participant' choices for \as-readings might be strongly affected by
+the specific experimental paradigm used. If task demands are only
+felicitous for a literal reading, the \emph{absence} of choices of
+local readings cannot be accounted for by assuming an inavailability
+of these readings \emph{per se}.\dn{micha does not understand this
+  sentence} However, at present it is less clear whether these results
+can also be generalized to further situations. For instance, subjects
+rejected the \es-sentences in Geurts and Poscoulous' original study,
+despite the fact that they could have accepted it based on the local
+reading. It is thus necessary to test both universal and non-monotonic
+quantifiers within the same experiment using a task that offers
+alternatives. Additionally, it would be informative to also probe into
+the availability and the relative preference of global readings. The
+study of \citet{ChemlaSpector2010:Experimental-Ev} did both of that.
+
+\subsection{\citet{ChemlaSpector2010:Experimental-Ev}}
+\label{sec:Chemla-Spector}
+
+\citet{ChemlaSpector2010:Experimental-Ev} also took issue with
+\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s design, arguing
+that, firstly, the pictorial material used in
+\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s study was unduly
+difficult; that, secondly, these pictures also may have failed to make
+the local reading sufficiently relevant; and that, thirdly, the
+restriction to a categorial choice (whether the sentence fits the
+picture of not) may induce a bias against non-preferred readings in
+cases where candidate readings stand in entailment relations
+\citep[c.f.][for this latter
+criticism]{Sauerland2010:Embedded-Implic}. To meet these potential
+problems, \citet{ChemlaSpector2010:Experimental-Ev} presented subjects
+with pictorial material like that in Figure~\ref{fig:Chemla-Spector},
+which was assumed to be easier to assess and better at highlighting
+the relevance of the local readings. Additionally, subjects were
+asked, not for categorial judgements, but for graded judgements:
+subjects could freely click on a scale, as shown in
+Figure~\ref{fig:Chemla-Spector}, to indicate how much they considered
+a picture fitting for a given sentence \citep[c.f.][for more on this
+method]{Chemla2009:Presuppositions}.
+
+\begin{figure}[t]
+  \centering
+      \includegraphics[scale=0.35]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
+      \includegraphics[scale=0.35]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
+        \caption{Example of critical trial for \as-condition by
+          \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
+          (\citeyear{ChemlaSpector2010:Experimental-Ev})}
+  \label{fig:Chemla-Spector}
+\end{figure}
+
+Albeit in a different format, the pictures used by
+\citeauthor{ChemlaSpector2010:Experimental-Ev} were all different
+instantiation of the situation types in
+Figures~\ref{fig:AS-distinguishing-pics} and
+\ref{fig:ES-distinguishing-pics}. The results reported in this study
+are averaged clicking positions, as shown in
+Figure~\ref{fig:Chemla-Spector-Results}.
+%
+\begin{figure}
+  \centering
+  \subfloat[][\as-condition]{
+    \label{fig:CS-Results-as}
+        \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
+  }
+  \subfloat[test][\es-condition]{
+    \label{fig:CS-Results-es}
+    \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
+  }
+  \caption{Results from
+    \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
+    (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
+  \label{fig:Chemla-Spector-Results}
+\end{figure}
+%
+According to \citeauthor{ChemlaSpector2010:Experimental-Ev}, the
+crucial piece of evidence for the availability of local readings for
+\as-sentences was that these sentences yielded higher graded
+acceptability scores for the strong situation than for the weak
+situation (although these differ only with respect to the truth value
+of the local reading). In a similar way, evidence for the availability
+of the local reading for \es-sentences comes from the difference
+between the local and the literal situation. Strikingly, in the latter
+case, the \es-sentences received an average of 73\% acceptability in
+the local situation although the literal and global readings are false
+in this case.
+
+\subsection{Critique}
+\label{sec:critique}
+
+Summing up, the mentioned studies have presented diverging evidence
+concerning the availability of local readings. Varoius problematic
+aspects of these studies have already been discussed elsewhere
+\citep[e.g.][]{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,Tielvan-Tiel2012:Embedded-Scalar}. Here,
+we want to point out two particular methodological problems that do
+impede their interpretation. However, we also want to make clear that
+these problems follow almost directly from the nature of the
+phenomenon under investigation and therefore seem nearly impossible to
+avoid.
+
+Firstly, a mapping between responses in a picture-verification task
+and readings of the relevant sentences is problematic due to the
+logical dependencies between the relevant readings discussed in
+Section~\ref{sec:get-know-your}. Let us consider \as-sentences in the
+following because these have been addressed by all three
+aforementioned studies. (Similar arguments apply to \es-sentences.) It
+is impossible to construct situations that clearly correspond to local
+readings of \as-sentences, since the local reading of such sentences
+implies their global and local readings. Every situation which is
+consistent with such a sentence under its local reading is also
+consistent with the other two readings. Therefore, we cannot test
+directly and independently all the cases we might wish to using a
+simple picture-verification paradigm. It would be especially desirable
+to test situations that are consistent with the local reading, but
+inconsistent with the global and literal reading. In that case
+\emph{yes}-responses would unambiguously indicate availability of
+local readings. However, since this is impossible we are left with
+suboptimal choices. In the experiment of
+\citet{GeurtsPouscoulous2009:Embedded-Implic} situations that are
+inconsistent with local readings but consistent with the other two
+readings were tested. In that case \emph{no}-responses would be decisive~--
+when compared to a suitable baseline. However, \emph{yes}-responses were
+observed exclusively. These can be attributed to one of the other
+readings. Therefore, assuming a principle of charity
+\citep{Davidson1973:Radical-Interpr} to be at play in picture
+verification tasks, the data of Geurts do not provide evidence against
+the existence of local readings.  In the experiments of C\&S and C\&D
+on the other hand situations that are consistent with all three
+readings were tested. Here again 'yes'-judgments cannot be interpreted
+confidently because they can always be attributed to global or literal
+readings. Both C\&S and C\&D attempt to surpass this problem by
+interpreting relative preferences. This does, however, bring us to the
+second problem.
+
+Preferences may be affectd by graphical properties of the picture
+materials. For example, verification complexity or typicality of the
+pictures with respect to the test sentences may differ between
+conditions and thereby induce certain preferences. In his careful
+critique van Tiel has eleborated on this point. Van Tiel points out
+that the relative preferences C\&S and C\&D interpret can be explained
+solely in terms of typicality, because the `strong'-situation (see
+e.g.~Figure~\ref{fig:strong}) are more typical instances of the
+sentence meaning than the competing pictures, irrespective of local
+implicatures.
+
+To conclude, in order to decide about the availablity of local
+implicatures we would ideally like to test situations that can
+unambiguously be mapped to the different readings and do not differ in
+typcality or other crucial properties. Given the logical dependencies
+inherent to the relevant readings and the considerations concerning
+typicality presented by van Tiel this seems impossible to achieve. As
+we willl argue below we do, however, believe it is.
+
+\subsection{To-Be-Included Here}
+\label{sec:whats-missing}
+
+\begin{itemize}
+\item establish independence (as much as possible) of pictorial
+  complexity/stereotypicality and assessment of reading
+  \begin{itemize}
+  \item not desirable to raise the level of relevance of local
+    readings, because we want to test the base-line / default (cite
+    Geurts / van Tiel)
+  \item unclear what graded truth-value judgements measure exactly
+    (re-read \citet{Chemla2009:Presuppositions} if needed)
+  \item cannot separate judgements about sentences from judgements
+    about pictures (van Tiel)
+  \item unclear whether design assesses preferences of readings or
+    targets pictorial complexity / typicality (van Tiel)
+  \end{itemize}
+\item provide a benchmark from which to deduce preference relations
+\item control for intonational pattern (present auditorily)
+  \begin{itemize}
+  \item intonational effects discussed by
+    \citet{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic},
+    \citep[c.f.][]{ChemlaSpector2010:Experimental-Ev}
+  \item mention \citet{SchwarzClifton2008:Strengthening-o} (re-read,
+    check for newer version)
+  \end{itemize}
+\item different languages
+\end{itemize}
+
+\section{An Incremental Verification Task}
+\label{sec:exp}
+
+\subsection{Design}
+\label{sec:design}
+
+\paragraph{General Idea.} In order to test the availability and
+preferences of different readings of \as- and \es-sentences, we were
+looking for a way to unambiguously map responses from a picture
+verification task to specific readings. We were particularly
+interested in the question whether local readings would be observed at
+all, but we were also interested in obtaining information about the
+relative preferences of the relevant readings. In addition, we wanted
+to minimize effects of any graphical differences between the picture
+materials. To achieve this we designed an experiment employing a
+modified version of picture verification, namely the
+\mymark{incremental verification task} (\acro{ivt}, see Conroy
+???)\dn{reference}. The general idea is that subjects are to judge
+sentence material based on pictures that do not necessarily contain
+all the information necessary to judge a certain reading true or
+false. In that case, participants can demand that more information is
+revealed. Participants are instructed to make a truth-value judgement
+as soon as they are able to.\dn{need to mention somewhere that trial
+  ends with each TV judgement}
+
+\paragraph{The Target Conditions.} More concretely, our study
+presented participants with pictures, like those in
+Figures~\ref{fig:InitialPicture}, \ref{fig:exseqAS} or
+\ref{fig:exseqES}, depicting a set of four identical central elements
+(e.g., letters), which could be connected to surrounding elements
+(e.g., triangles). Initially, any potential connections between
+central and surrounding elements were covered by dark gray color (see
+Figure~\ref{fig:InitialPicture}).
+%
+\begin{figure}
+  \centering
+      \fbox{\includegraphics[width=5cm]{../pictures/paper/ae_01_1.pdf}}
+      \caption{Initial picture presented to participants where all
+        possible connections from each letter to its surrounding
+        triangles are covered.}
+  \label{fig:InitialPicture}
+\end{figure}
+%
+Sentences to be judged were in German (see (\ref{ex:as}) and
+(\ref{ex:es}) below) and presented auditorily, and participants were
+asked to listen to a given sentence and then uncover the potential
+links step by step until they felt able to give a truth value
+judgment. Three options were available for participants at each step:
+(i), demand more information, (ii), judge the sentence as true, and
+(iii), judge the sentence as false. Importantly, each of the three
+potentially available readings corresponded to a specific step in the
+uncovering process where the truth value of that reading (and only of
+that reading) could be assessed for the first time. The location in
+the sequence and the corresponding truth-value judgement differed
+between \as- and \es-sentences, as described presently. (This is,
+again, because of the logical dependencies between readings.)
+
+Consider the \as-sentence in (\ref{ex:as}).
+\begin{exe}
+\ex \gll \mymark{Alle} diese Briefe sind mit \mymark{einigen} ihrer Dreiecke
+  verbunden.\label{ex:as}\\
+All these letters are with some their triangles connected.\\
+\trans All of these letters are connected to some of their triangles.
+\end{exe}
+Figure~\ref{fig:exseqAS} shows the three corresponding critical
+positions for this sentence in the order of the uncovering
+process. First, the situation in Figure~\ref{fig:exseqAS1} becomes
+available, which is true under a literal reading, while the local and
+global readings cannot be evaluated yet. Second, in
+Figure~\ref{fig:exseqAS2}, the literal reading is still true, but now
+the global reading can be additionally confirmed by a \emph{true}
+response, as all the connections of one of the letters are now
+uncovered, and it is now visible that one of the letters is not
+connected to all of its triangles. Finally, decisions concerning the
+local reading are possible as soon as all connections have been
+uncovered. In this case, the critical position shown in
+Figure~\ref{fig:exseqAS3} is incompatible with a local reading: One of
+the central elements is linked to all of its surrounding elements,
+thus yielding to \emph{false} answers if participants indeed adopted
+the local reading. Note that associating the final position with
+\emph{false} answers allows us to exclude both literal and global
+readings, which correspond to a \emph{true} answer at this
+position. In sum, \emph{true} or \emph{false} answers on particular
+positions in the incrementally revealed picture sequence can be mapped
+uniquely to candidate reading. All other \emph{true} or \emph{false}
+answer were counted as errors. The mapping between responses and
+readings is summarized in Table~\ref{tab:mappingAS}.
+
+\begin{figure}[ht]
+	\centering
+	\subfloat[][Step 1]{ 
+		\fbox{\includegraphics[width=3.5cm]{../pictures/paper/ae_3_v_l.pdf}}
+	    \label{fig:exseqAS1}
+	}
+	\subfloat[][Step 2]{
+		\fbox{\includegraphics[width=3.5cm]{../pictures/paper/ae_5_v_l.pdf}}
+	    \label{fig:exseqAS2}
+	}
+	\subfloat[][Step 3]{ 
+		\fbox{\includegraphics[width=3.5cm]{../pictures/paper/ae_7_v_l.pdf}}
+	    \label{fig:exseqAS3}
+	}
+	\caption[]{Example sequence for \as-sentences}
+	\label{fig:exseqAS}
+\end{figure}
+
+\begin{table}[ht]
+	\centering
+	\subfloat[][\as-Sentences]{ 
+\begin{tabular}{cccc}
+&more info&true&false\\ \midrule
+Step 1&error&\lit&error\\
+Step 2&error&\glb&error\\
+Step 3&-&error&\loc
+\end{tabular}
+
+	    \label{tab:mappingAS}
+	} \qquad
+	\subfloat[][\es-Sentences]{
+\begin{tabular}{cccc}
+&more info&true&false\\ \midrule
+Step 1&error&error&\glb\\
+Step 2&error&error&\lit\\
+Step 3&-&\loc&error
+\end{tabular}
+	    \label{tab:mappingES}
+	}
+\caption{Mapping from response types to readings. Notice that on steps
+3 the option ``more info'' is not available because the whole picture
+has been revealed.}
+\label{tab:subfigureExample}
+\end{table}
+
+\es-sentences, due to the non-linear relationship of candidate
+readings described in Section~\ref{sec:get-know-your}, require a
+slightly different sequence of unfolding which yields a different
+order in which truth-value judgements can be made.
+%
+\begin{figure}[ht]
+	\centering
+	\subfloat[][Step 1]{ 
+		\fbox{\includegraphics[width=3cm]{../pictures/paper/ge_3_v_l.pdf}}
+	    \label{fig:subfig1}
+	}
+	\subfloat[][Step 2]{
+		\fbox{\includegraphics[width=3cm]{../pictures/paper/ge_4_v_l.pdf}}
+	    \label{fig:subfig2}
+	}
+	\subfloat[][Step 3]{ 
+		\fbox{\includegraphics[width=3cm]{../pictures/paper/ge_6_v_l.pdf}}
+	    \label{fig:subfig1}
+	}
+	\caption[]{Example sequence for \es-sentences}
+	\label{fig:exseqES}
+\end{figure}
+%
+For a sentence like (\ref{ex:es}) we obtain an unambiguous
+mapping between truth values and readings with respect to the sequence
+in \ref{fig:exseqES}.
+\begin{exe}
+\ex \label{ex:es} \gll \mymark{Genau} eine der Glocken ist mit
+  \mymark{einigen} ihrer Halbkreise verbunden.\\ 
+  Exactly one of-the bells is with some its semicircles connected.\\
+  \trans Exactly one letter is connected to some of its semicircless.
+\end{exe}
+At the first critical position shown in Figure~\ref{fig:subfig1}, the
+global reading corresponds to a \emph{false} response, as one of the
+bells is already linked to all of its semicircles. The literal reading
+becomes available in \ref{fig:subfig2}, corresponding to a
+\emph{false} response, as there are two bells that are connected to at
+least some of their surrounding elements. Finally, confirming
+\ref{fig:subfig1} by a \emph{true} response corresponds to the local
+reading, as one of the bells is linked to some but not all of its
+semicircles, while all of the other bells are linked to all of
+them. Note that again, global and literal readings differ from local
+readings with respect to their truth values. Mappings between
+responses and readings are summarized in Table \ref{tab:mappingES}.
+
+In addition to the unambiguous mapping from readings to truth values,
+the present design minimizes graphical effects because there is no
+comparison between different pictures
+\citep[c.f.][]{Tielvan-Tiel2012:Embedded-Scalar}. Moreover, we
+controlled for pictorial effects by introducing control conditions,
+which are described in the next section.\dn{Are we sure that this
+  paragraph needs to go here? this should be mentioned in the
+  motivation preceding this section and in the discussion at the end,
+  no?}
+
+\paragraph{Controls.} In order to make sure that subjects understood
+the task, i.e., gave truth-value judgements neither sooner not later
+than at the first possible position in a sequence, we included a set
+of control conditions. These also controlled for response biases that
+are independent of the sentence meaning, but only depend on the
+experimental procedure or on the picture materials. For each of the
+three readings in the \as- and \es-conditions, we constructed an
+unambiguous control sentence as in (\ref{bsp:controls-as}) and
+(\ref{bsp:controls-es}), requiring the same judgement at the identical
+position in the same sequence used for the respective targets. For
+instance, example (\ref{bsp:controls-as-1}) requires a
+\emph{true}-response analogous to the \as-sentence in (\ref{ex:as})
+under its literal reading, (\ref{bsp:controls-as-2}) corresponds to
+the \as-sentence under its global reading and
+(\ref{bsp:controls-as-3}) corresponds to its local reading. With
+regard to the \es-sentences, controls like (\ref{bsp:controls-es-1})
+correspond to the global reading, (\ref{bsp:controls-es-2}) to the
+literal and (\ref{bsp:controls-es-3}) to the local reading. If,
+independently of sentence meaning, there was any bias to respond in a
+certain way at any point in the sequences, this should affect control
+sentences to the same degree as it affects target conditions.
+
+\begin{exe}
+  \ex \label{bsp:controls-as}
+    \begin{xlist}
+\ex \label{bsp:controls-as-1} \gll Alle Briefe sind mit mindestens drei ihrer Dreiecke verbunden.\\
+  All letters are with at-least three their triangles connected.\\
+  \trans All letters are connected to at least three of their triangles.
+\ex \label{bsp:controls-as-2} \gll Mindestens ein Brief ist mit genau f\"unf seiner Dreiecke verbunden.\\
+  At-least one letter is with exactly five his triangles connected.\\
+  \trans At least one letter is connected with exactly five of its triangles.
+\ex \label{bsp:controls-as-3} \gll Jeder Brief ist mit mindestens vier seiner Dreiecke verbunden.\\
+  Every letter is with at-least four his triangles connected.\\
+  \trans Every letter is connected to at least four of its triangles.
+\end{xlist}
+\end{exe}
+
+\begin{exe}
+\ex \label{bsp:controls-es}
+  \begin{xlist}
+\ex \label{bsp:controls-es-1} \gll Alle Glocken sind mit weniger als
+  vier ihrer Halbkreise verbunden. \\ 
+All bells are with fewer than four their semicircles connected.\\
+\trans All bells are connected with fewer than four of their semicircles.  
+\ex \label{bsp:controls-es-2} \gll Alle Glocken sind mit allen ihren Halbkreisen verbunden.\\
+All bells are with all their semicircles connected.\\
+\trans All bells are connected to all of their semicircles. 
+\ex \label{bsp:controls-es-3} \gll Mindestens drei Glocken sind mit
+  allen ihren Halbkreisen verbunden.\\ 
+  At-least three bells are with all  their semicircles connected.\\
+  \trans At least three bells are connectd with all of their semicircles.
+\end{xlist}
+\end{exe}
+
+\paragraph{Controlling ambiguity resolution.} In order to control for
+artificial effects of presentation order on the availability of
+readings, we included a second type of control conditions. In
+particular, we tested (i), whether the order of given readings affects
+preferences for ambiguous sentences and (ii), whether prosodic
+information can, in principle, shift reading preferences in the
+present task. Note that for our target sentences, the logical
+entailment relations between readings always require local readings to
+be evaluated at the end of a sequence. It could thus in principle be
+possible that no subject ever reaches this point, because they gave
+truth-value judgements earlier, thereby ending the trial. In that case
+it would be unclear if these decisions have been affected by a general
+inavailability of local readings or by the fact that one of the
+earlier presented readings is the preferred one. By including globally
+ambiguous structures with a known preference over available readings,
+we thus intended to test whether participants in our task occasionally
+choose dispreferred readings, even if they were presented following
+preferred readings.
+
+We therefore included globally ambiguous \emph{late-closure
+  structures} as in (\ref{bsp:target-related}), which have been
+repeatedly shown to exhibit interpretive preferences.
+\begin{exe}
+\ex \gll Der Brief ist mit Kreisen und Vierecken mit Sonnen
+  verbunden. \label{bsp:target-related}\\
+The letter is with circles and squares with suns connected.\\
+The letter is connected with circles and squares with suns.
+\begin{xlist}
+  \ex \label{bsp:target-related-LC} The letter is connected with squares containing suns, and it is
+    also connected with circles. \hfill{(\lc)}
+  \ex \label{bsp:target-related-EC} The letter is connected with circles and squares, both of which
+    are containing suns.  \hfill{(\ec)} 
+\end{xlist}
+\end{exe}
+In late-closure sentences, a modifier can be attached to one of two
+preceding hosts. More specifically, in (\ref{bsp:target-related}), the
+prepositional phrase \emph{with suns} can be attached to the preceding
+noun \emph{squares}, resulting in the so-called \emph{late-closure} or
+\emph{low-attachment} reading ((\ref{bsp:target-related-LC}), see
+Frazier, 1987, for details)\dn{references}. Alternatively, the
+\acro{pp} can be attached to the whole conjoined \acro{np}
+\emph{circles and squares}, corresponding to the \emph{early-closure}
+or \emph{high-attachment} reading
+(\ref{bsp:target-related-EC}). Generally, the late-closure reading is
+preferred over the early closure reading for sentences comparable to
+those in (\ref{bsp:target-related}) (REFS)\dn{references}.
+
+For each sentence, two sequences were designed. In the first, the
+critical position associated with the dispreferred high-attachment
+reading preceded the critical position for the low-attachment
+reading. In this case, a partly covered graph as in
+Figure~\ref{fig:exec1} preceded a graph as in \ref{fig:exec2}.
+%
+\begin{figure}[ht]
+	\centering
+	\subfloat[][Step 1]{ 
+		\fbox{\includegraphics[width=5cm]{../pictures/paper/ec_01_3.pdf}}
+	    \label{fig:exec1}
+	}
+	\subfloat[][Step 2]{
+		\fbox{\includegraphics[width=5cm]{../pictures/paper/ec_01_5.pdf}}
+	    \label{fig:exec2}
+	}
+	\caption[]{Critical steps of a sequence for sentence
+          (\ref{bsp:target-related}) where
+          early-closure/high-attachment reading
+          (\ref{bsp:target-related-EC}) can be judged first.}
+	\label{fig:exec}
+\end{figure}
+%
+If
+participants adopted an early-closure reading as in
+(\ref{bsp:target-related-EC}), a \emph{false}-judgment would be
+expected at the position illustrated in \ref{fig:exec1}, as none of
+the circles connected to the letter contain any suns. Under the
+late-closure reading in (\ref{bsp:target-related-EC}), in contrast, a
+\emph{true}-response would be expected no sooner than in the step
+shown in Figure~\ref{fig:exec2}. The order of possible judgements is
+reversed in the second kind of sequence including pictures like
+\ref{fig:exlc1} followed by pictures like \ref{fig:exlc2}. Here, the
+late-closure reading in (\ref{bsp:target-related-LC}) can be judged
+first requiring a \emph{true}-response on \ref{fig:exlc1}. The
+early-closure reading in (\ref{bsp:target-related-EC}) can only be
+judged later in the sequence. When we reach \ref{fig:exlc2} a
+\emph{false}-response is expected under an
+early-closure/high-attachment reading.
+
+\begin{figure}[ht]
+	\centering
+	\subfloat[][Step 1]{ 
+		\fbox{\includegraphics[width=5cm]{../pictures/paper/lc_01_3.pdf}}
+	    \label{fig:exlc1}
+	}
+	\subfloat[][Step 2]{
+		\fbox{\includegraphics[width=5cm]{../pictures/paper/lc_01_6.pdf}}
+	    \label{fig:exlc2}
+	}
+	\caption[]{Critical steps of a sequence for sentence
+          (\ref{bsp:target-related}) where
+          late-closure/low-attachment reading
+          (\ref{bsp:target-related-LC}) can be judged first.}
+	\label{fig:exec}
+\end{figure}
+
+\paragraph{Testing Effects of accentuation.}\dn{These two paragraphs
+  still need a proper home; Petra opts for ``materials'' section.} It
+has been claimed that local readings only emerge in the case of
+special accentuation of the the scalar item under consideration
+(REFERENCES). Further, it is generally assumed that the required type
+of accentuation is a pitch accent (REFS). To test for this possibility
+we decided to present the sentences (eg., (\ref{ex:as}) and
+(\ref{ex:es})) auditorily in two versions each. In the accented
+version a pitch accent was placed on {\it einige}. The second version
+had neutral prosody. If accentuation is the driving force for local
+readings, we would expect a higher proportion of local readings in the
+former than in the latter version of the sentences.
+
+We also wished to make sure that differences in prosody may generally
+lead to a shift in interpretation preferences in the \acro{itv}
+task. Sentences like (\ref{bsp:target-related}) are well suited to
+test this assumption since it is well-known that their
+interpretational preferences are sensitive to prosody. If an utterance
+of (\ref{bsp:target-related}) includes a prosodic phrase boundary
+between {\it squares} and {\it with}, this intonational pattern
+strongly corresponds to the high-attachment reading. If, instead, a
+prosodic phrase boundary after {\it circles} is present, the
+acceptance of the low-attachment reading is boosted. To test whether
+prosodic information is taken into account in the \acro{itv} we
+presented both types of prosodic structures expecting the described
+boost in acceptance for the low-attachment reading. In addition, we
+also included a neutral version containing no phrase marking
+whatsoever. This should receive intermediate acceptance
+rates. Further, we also presented unambiguous sentences corresponding
+to the early-closure reading. As in the case of the \as- and
+\es-sentences the unambiguous counterparts served as a baseline to
+control for response biases that are independent of sentence meaning.
+
+\subsection{Procedure}
+\label{sec:procedure}
+
+\subsection{Materials}
+\label{sec:materials}
+
+A detailed description of our auditory material is found in
+Appendix~\ref{sec:audit-sent-mater}.
+
+\subsection{Participants}
+\label{sec:participants}
+
+41 native speakers of German took part in our study, none of which had
+any prior exposure to logic or formal semantics. We excluded 3
+subjects due to insufficient performance on controls ($\le 50\%$
+correct answers).
+
+\begin{itemize}
+\item possibly mention ages, backgrounds and sexes?
+\end{itemize}
+
+\subsection{Results}
+\label{sec:results}
+
+Performance on basic control conditions was high (92\% correct
+responses on average), indicating that subjects understood the task,
+giving truth-value judgements at the ``right'' moment in a sequence
+without being influenced in general by inessential features of the
+picture material or showing general response biases.
+
+The judgments obtained for the four target conditions are depicted in
+Figure \ref{fig:JudgmentsK2}.\dn{we should introduce the actual
+  sequences that we presented so that it is clear what it means to say
+\emph{true} or \emph{false} on some position or other}
+%
+\begin{figure}[]
+\centering
+\subfloat[][\as-accented]{
+\includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
+\label{fig:ReadingsAE}
+}
+\subfloat[][\as-neutral]{
+\includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
+\label{fig:ReadingsGE}
+}
+
+\subfloat[][\es-accented]{
+\includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
+\label{fig:ReadingsAE}
+}
+\subfloat[][\es-neutral]{
+\includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
+\label{fig:ReadingsGE}
+}
+
+\caption[Optional caption for list of figures]{Judgments for the four
+  target conditions in Experiment 1. Relative frequency of
+  yes/no-judgments is plotted against the position within the
+  trial. In the \as-conditions there were seven positions. On the
+  third position a yes-judgment corresponded to a literal reading,
+  while on the fith position a yes-judgment corresponded to a global
+  reading.  A no-judgment on the seventh position was only consistent
+  with a local reading. The \es-conditions had five
+  positions. No- judgments on positions two and three corresponded to
+  global and literal readings, respectively. A yes-judgment on the
+  last segment corresponded to a local reading. }
+\label{fig:JudgmentsK2}
+\end{figure}
+%
+We coded the judgments as {\it literal}, {\it global} or {\it local}
+if they were as expected under one of these readings and as {\it
+  error} if not. The distribution of readings as coded by us is
+presented in Figure~\ref{fig:JudgementPercentages}.
+%
+\begin{figure}[]
+\centering
+\subfloat[][\as-Conditions]{
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.5,
+                  enlarge y limits=0.25,
+                  legend style={at={(0.5,-0.15)}, anchor=north, legend columns=-1},
+        ylabel={\% of answers}, symbolic x
+        coords={ae-ntr,ae-acc}, xtick=data, nodes
+        near coords, nodes near coords align={vertical},x=65, bar width=3mm, ymin = 8 ]
+
+        \addplot coordinates {(ae-ntr,73) (ae-acc,70)};
+
+        \addplot coordinates {(ae-ntr,23) (ae-acc,22)};
+
+        \addplot coordinates {(ae-ntr,1) (ae-acc,2)};
+
+        \addplot coordinates {(ae-ntr,4) (ae-acc,6)};
+
+        % \addplot coordinates {(ae-ntr,83) (ae-acc,80) (ge-ntr,53)
+        % (ge-acc,56)};
+
+        % \addplot coordinates {(ae-ntr,26) (ae-acc,25) (ge-ntr,33)
+        % (ge-acc,26)};
+
+        % \addplot coordinates {(ae-ntr,1) (ae-acc,2) (ge-ntr,0)
+        % (ge-acc,1)};
+
+        % \addplot coordinates {(ae-ntr,4) (ae-acc,7) (ge-ntr,28)
+        % (ge-acc,31)};
+
+        \legend{literal, local, global, false}
+
+      \end{axis}
+
+    \end{tikzpicture}
+
+% \includegraphics[width=5cm]{../pictures/paper/ReadingsAE.pdf}
+\label{fig:JudgementPercentagesAE}
+}
+\subfloat[][\es-Conditions]{
+\begin{tikzpicture}[scale=0.8]
+
+  \begin{axis}[ybar, 
+               enlarge x limits=0.5,
+               enlarge y limits=0.25, 
+               legend style={at={(0.5,-0.15)},
+                 anchor=north,
+                 legend columns=-1}, 
+               ylabel={\% of answers}, 
+               symbolic x coords={ge-ntr,ge-acc}, 
+               xtick=data,
+               nodes near coords,
+               nodes near coords align={vertical},
+               x=65, bar width=3mm,
+               ymin = 8
+               ]
+
+    \addplot coordinates {(ge-ntr,47) (ge-acc,49)};
+
+    \addplot coordinates {(ge-ntr,29) (ge-acc,23)};
+
+    \addplot coordinates {(ge-ntr,0) (ge-acc,1)};
+
+    \addplot coordinates {(ge-ntr,25) (ge-acc,27)};
+
+    % \addplot coordinates {(ae-ntr,83) (ae-acc,80) (ge-ntr,53) (ge-acc,56)};
+
+    % \addplot coordinates {(ae-ntr,26) (ae-acc,25) (ge-ntr,33) (ge-acc,26)};
+
+    % \addplot coordinates {(ae-ntr,1) (ae-acc,2) (ge-ntr,0) (ge-acc,1)};
+
+    % \addplot coordinates {(ae-ntr,4) (ae-acc,7) (ge-ntr,28) (ge-acc,31)};
+
+    \legend{literal, local, global, false}
+
+  \end{axis}
+
+\end{tikzpicture}
+
+% \includegraphics[width=5cm]{../pictures/paper/ReadingsGE.pdf}
+\label{fig:JudgementPercentagesGE}
+}
+\caption[Optional caption for list of figures]{Judgments}
+\label{fig:JudgementPercentages}
+\end{figure}
+%
+Participants mostly gave judgments indicating literal or local
+readings. Judgments compatible with a global reading were seldom
+obtained. In the \as-conditions participants made hardly any errors,
+whereas the amount of errors was slightly greater in the
+\es-conditions.
+
+In the \as-conditions (see Figure~\ref{fig:JudgementPercentagesAE})
+judgments were consistent with literal readings in 65.0\% of the
+trials with neutral prosody and in 67.5\% of the trials with accented
+prosody.\dn{IMPORTANT: Figure contains different numbers (even if
+  rounded)! Fabian, did you exclude the 3 bad performers when you
+  obtained this data?} The number of global readings was very low,
+with 1.6\% of the neutral and 0.8\% of the accented trials
+(corresponding to a total of 3 answers across all trials). Judgments
+indicating local readings were given in 22.0\% of both the neutral and
+accented trials. In the \es-conditions (see
+Figure~\ref{fig:JudgementPercentagesGE}) judgments consistent with
+literal readings were given in 47.2\% and 44.7\% of the trials with
+neutral and accented prosody, respectively. Global readings were
+observed in 0.8\% of the trials in both the neutral and the accented
+condition. Judgments indicating local readings were given in 22.8\% of
+the neutral and 27.6\% of the accented trials.
+
+In order to test wether local readings exist we tested whether the
+number of local responses in each condition was higher than expected
+by chance. Local responses had to be given on the last position in
+each trial. If local readings didn't exist we would expect
+participants, who reached the last position (ie. who did not abort the
+trial prior to the last position) to give local judgments not more
+often than expected by chance. On the last position two responses were
+possible. One was compatible with a local reading the other was
+not. Therefore, we would expect 50\% local responses by chance. As it
+turns out local responses were given significantly more often than
+50\% in all target conditions (all Bonferoni corrected p<.05). Note
+that this finding cannot be explained by some kind of general response
+bias on the last position since local readings required a yes-judgment
+in the \es-conditions but a no-judgment in the \as-conditions.
+
+In order to test whether accentuation or the quantifier has an
+influence on the distribution of readings, log-liner models were
+computed (see Schepers 2003). The factors {\it Reading}, {\it
+  Accentuation} and {\it Quantifier} were included in these
+models. Two variants of these models were computed.  In the first, the
+factor {\it Item} was added to the above mentioned. In the latter {\it
+  Participants} was included as a factor. Inclusion of these two
+factors allowed us to test whether the distribution of readings was
+identical accros items and participants. We report log-likelihood
+ratio Chi-squares ($LRCS_1$ and $LRCS_2$), degrees of freedom ($df_1$,
+$df_2$) and significance levels ($p_1$ and $p_2$).
+
+Unsurprisingly, there was an effect of reading ($LRCS_1=364.77, df_1 =
+3, p_1<.001, LRCS_2=364.77, df_2 = 3, p_1<.001,$) because overall the
+readings were distributed inhomogeneously (sse Figure
+\ref{fig:ReadingsGE}). The quantifier had an influence on the
+distribution of readings as revealed by a reliable interaction of {\it
+  Reading} and {\it Quantifier} ($LRCS_1=49.32, p_1<.01,LRCS_2=32.16,
+p_1<.01,$). Looking at the data it seemed unlikely that the quantifier
+affected the amount of local readings. We suspected that this
+interaction was due to the higher number of errors and lower number of
+literal readings in the \es-conditions as compared with
+the \as-conditions. A difference in the distribution of judgment
+types between participants was revealed by a reliable interaction of
+{\it Reading} and {\it Participant} ($LRCS_1=487.70, p_1<.01$). We
+were interested in whether this effect was due to some of the
+participants being more likely to choose literal readings than
+others. Finally, there was a three-way interaction of {\it
+  Participants}, {\it Construction} and {\it Reading} ($LRCS_1, =
+143.92, df_1 = 117, p_1<.05$) which could stem from to the fact that
+some participants were more prone than others to make errors in the
+\es-conditions.
+
+In order to find out whether the interactions just reported affected
+the amount of local readings, the log-linear models were computed
+again with a different coding of the readings. Here, we only
+considered the amount of local readings versus all other kinds of
+judgments. Judgments were coded as {\it local} and {\it other}. If the
+reported interactions affect the amount of local readings they should
+show up again. The expected but irrelevant effect of {\it Reading} was
+again significant ($LRCS_1=134.55, df_1 = 1, p_1<.001, LRCS_2=144.64,
+df_2 = 1, p_1<.001,$). In addition, the interaction of {\it
+  Participant} and {\it Reading} ($LRCS_1=487.70, p_1<.01$) as well as
+the three-way interaction of {\it Construction}, {\it Participant} and
+{\it Reading} ($LRCS_1=487.70, p_1<.01$) were significant. No other
+effects were significant. In particular, the interaction of {\it
+  Construction} and {\it Reading} was not significant ($LRCS_1=2.10,
+p_1=.15,LRCS_2=.74, p_2=.39$).
+
+The interaction of {\it Participant} and {\it Reading} shows that
+there are indeed varying preferences for local readings among German
+speakers. Further examination of the distribution of local readings
+revealed a clear pattern (see Figure
+\ref{fig:HistogramLocalReadingsK2}). In all four conditions, about
+seven out of the 40 participants ($16\%$) were consistently giving
+judgments that indicate local readings. Further, the relative
+frequency of local judgments per participant strongly correlated
+between all four conditions (all $r>.6, p<.001$). Appart from the
+localists about half of the participants (and 41.5\% of all
+participants) were consistently giving judgments that indicate literal
+readings. Only a minority of participants exhibited
+inconsistency. Reading preferences were more clear-cut in the
+\as-conditions than in the \es-conditions. The number of consistent
+litaralists was lower in the \es-conditions (25.6\%) as compared to
+the \as-conditions (57.3\%). Also, the number of participants that
+showed inconsitency was higher in these conditions. However, the
+number of consistent localists did hardly differ between
+constructions.
+
+The three way-interaction of {\it Participant}, {\it Construction} and
+{\it Reading} is due to the fact that for some participants
+preferences for local over other readings deviated between the two
+construction types. These deviations were, however, not systematic to
+any degree. How much local preferences deviated between the two
+construction types per participant is depicted in Figure \ref{}. Most
+participants had exactly the same preferences in the two
+constructions. However, a few had a stronger and a few others a weaker
+preference for local readings in the \es- than in the
+\as-conditions. Since we did not find any systematic patterns
+here, we speculate that the three-way interaction is due to the
+\es-construction beeing understood non-standardly by a
+few participants. This speculation is plausible given the higher
+number of errors in the \es- as compared to the \as-conditions.
+
+The absence of the interaction between {\it Construction} and {\it
+  Participant} indicates that the type of construction does not affect
+the amount of local readings. We assumed based on the observed
+distribution of judgments that the type of contsruction affected the
+amount of literal but not local and global readings. To further test
+this assumption, we also considered literal and global readings versus
+other judgments in separate analyses. Comparing global readings versus
+other judgments {\it Construction} and {\it Reading} were found to
+interact ($LRCS_1=42.80, df= 1, p<.001; LRCS_2=22.14, df= 1,
+p<.001$). Comparing global readings to other judgments no such
+interaction was obeserved ($LRCS_1=1.24, df= 1, p=.29, LRCS_1=.21, df=
+1, p=.65$).
+
+\begin{figure}[h]
+\centering
+\subfloat[][\as-accented]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_AKZ.jpg}
+\label{fig:ReadingsAE}
+}
+\subfloat[][\as-neutral]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_NTR.jpg}
+\label{fig:ReadingsGE}
+}
+
+\subfloat[][\es-accented]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_AKZ.jpg}
+\label{fig:ReadingsAE}
+}
+\subfloat[][\es-neutral]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_NTR.jpg}
+\label{fig:ReadingsGE}
+}
+\label{fig:HistogramLocalReadingsK2}
+\caption[Optional caption for list of figures]{Judgments for the four target conditions}
+\end{figure}
+
+\subsection{Discussion}
+\label{sec:discussion}
+
+\subsubsection{Bits and Pieces}
+\label{sec:bits-pieces}
+
+\begin{itemize}
+\item The distribution of
+responses found in previous studies could in part be explained by
+differences in typicality of the pictures with respect to the possible
+readings (see van Tiel). In the present case this kind of reasoning
+would have to be extended to the typicalilty of parts of pictures. On
+intuitive grounds, we take this kind of reasoning to be
+implausible. We will now shortly discuss how graphical properties
+might still affect judgments in the worst case. In the first step of
+the \as-condition local and global readings cannot be judged,
+yet. Therefore, graphical properties should not affect judgments if
+participants have one of these readings in mind. If participants have
+a literal reading in mind, the worst case scenario is that they
+refrain from judging the sentence as true at this point due to some,
+eg. atypical, graphical property of the picture. The situation is
+similar at the second step. The local reading is still not
+decidable. Therefore, graphical properties should not play a role if
+participants have a local reading in mind. A positive judgment might,
+however, be a delayed judgment of a literal reading. Again, the worst
+case scenario for our purpose is that participants refrain from
+answering because of graphical properties. At the last step the local
+reading requires a negative judgment. Now, we could obtain delayed
+negative responses from literal or global readings because the graph
+as a whole is, e.g., logically true but atypical with respect to these
+readings. These kinds of judgments would be indistinguishable from
+local responses. Note, however, that we have no reason to believe that
+typicality has large effects, because, given the results from van
+Tiel, the picture as a whole is expected to be one of the more typical
+situations for \as-sentences. Still, we cannot exclude the possibility
+that graphical properties of the pictures might have the described
+effect. In the \es-conditions this type of effect is, however,
+entirely impossible since the literal and global reading is plainly
+false given the initial parts as well as the whole graph. Summing up,
+in the worst case, which we consider implausible, graphical effects
+might lead to an enhanced number of local responses in the \as- as
+compared to the \es-condition. We have to keep this possibility in
+mind. We want to stress, however, that the design presented here
+improves on previous studies with respect to possible graphical
+effects.
+\end{itemize}
+
+\section{Conclusions}
+\label{sec:conclusions}
+
+\appendix
+
+\section{The auditory sentence material}
+\label{sec:audit-sent-mater}
+
+A phonetically trained female native speaker of German was instructed
+to realize two prosodic versions of each target sentence, and four
+versions of the target-related fillers. In addition to these
+sentences, a set of unrelated fillers and neutral control structures
+was also recorded. For these constructions, the speaker was instructed
+to realize prosodic contours as neutral and natural as possible.
+
+For all target sentences (\as and \es), the determiner \emph{some} was
+produced with a contrastive pitch accent as well as with a neutral
+accent, respectively. Contrastive accents in German are realized by an
+H*L contour (XYZ)\dn{insert references}, thus employing a generally
+falling pattern. A set of 15 experimental items was recorded for each
+condition (\emph{accented} vs.~\emph{unaccented}), resulting in a
+total number of 60 target sentences.
+
+In contrast to the accent manipulation, target-related fillers
+differed with respect to prosodic phrasing. Prosodic phrase boundaries
+in German are realized by a rise in F0 as well as by a durational
+increase on the final part of the constituent preceding the boundary
+(prefinal lengthening) plus an optional pause (XYZ)\dn{references:
+  Vaissiere, 1983; Fery, 1993}. Boundaries for these filler sentences
+were either realized at the position separating the second \acro{pp}
+from the preceding material (\emph{late boundary}, corresponding to a
+high-attachment reading) or directly preceding the second conjunct in
+the first \acro{pp} (\emph{early boundary}, corresponding to a
+low-attachment reading). As the prosodic realization of the targets
+involved the comparison between an accented and a neutral variant, we
+also included a third version of target-related fillers, in which our
+speaker produced the sentences without any pronounced
+boundaries. Finally, an additional condition was recorded, using
+disambiguated sentences that were prosodically neutral (XYZ)\dn{proper
+  reference to explanation above}. For each prosodic variant, a set of
+30 items was read, yielding 150 target-related fillers. Together with
+30 unrelated fillers and 90 control sentences, a total number of 300
+sentences was recorded. The session was recorded in an acoustically
+shielded booth (44.1\,kHz sampling rate, 16 bit amplitude resolution).
+
+Before entering the judgment task, experimental items and
+target-related fillers were analyzed with respect to their acoustic
+properties. As both accented elements as well as prosodic boundaries
+were expected to differ with respect to their F0 and/or durational
+properties, we calculated durational values as well as difference
+values between minimal and maximal F0 for each word. As targets
+slightly differed with respect to the total number of words as well as
+with respect to certain lexical properties (i.e., \emph{seinen}
+vs.~\emph{ihren}, see above (XYZ)\dn{proper reference}), we considered
+the following analysis regions:
+
+\begin{exe}
+  \ex
+    \begin{xlist}
+      \ex $|_{\text{R}1}$~Alle  	\ $|_{\text{R}2}$~dieser 
+      \ $|_{\text{R}3}$~$\acro{np}_1$  
+      \ $|_{\text{R}4}$~sind  \ $|_{\text{R}5}$~mit  \
+      $|_{\text{R}6}$~einigen  \ $|_{\text{R}7}$~ihrer 
+       \ $|_{\text{R}8}$~{$\acro{np}_2$}  \ $|_{\text{R}9}$~verbunden.
+    \ex       $|_{\text{R}1}$~Genau einer  	\ $|_{\text{R}2}$~der 
+      \ $|_{\text{R}3}$~$\acro{np}_1$  
+      \ $|_{\text{R}4}$~ist  \ $|_{\text{R}5}$~mit  \
+      $|_{\text{R}6}$~einigen  \ $|_{\text{R}7}$~seiner 
+       \ $|_{\text{R}8}$~{$\acro{np}_2$}  \ $|_{\text{R}9}$~verbunden.
+    \end{xlist}
+    % \begin{tabbing}
+    %   $|_{\text{R}1}$ Genau einer \= 	\ $|_{\text{R}2}$ diese \=
+    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \= 
+    %   \ $|_{\text{R}4}$ sind \= \ $|_{\text{R}5}$ mit \= \
+    %   $|_{\text{R}6}$ einigen \= \ $|_{\text{R}7}$ seiner 
+    %   \= \ $|_{\text{R}8}$  \acro{np}$_2$ \= \ $|_{\text{R}9}$
+    %   verbunden. \kill
+    %   $|_{\text{R}1}$ Alle \> 	\ $|_{\text{R}2}$ dieser \>
+    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \> 
+    %   \ $|_{\text{R}4}$ sind \> \ $|_{\text{R}5}$ mit \> \
+    %   $|_{\text{R}6}$ einigen \> \ $|_{\text{R}7}$ ihrer 
+    %   \> \ $|_{\text{R}8}$  \acro{np}$_1$ \> \ $|_{\text{R}9}$
+    %   verbunden. \\
+    %   $|_{\text{R}1}$ Genau einer \> 	\ $|_{\text{R}2}$ der \>
+    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \> 
+    %   \ $|_{\text{R}4}$ ist \> \ $|_{\text{R}5}$ mit \> \
+    %   $|_{\text{R}6}$ einigen \> \ $|_{\text{R}7}$ seiner 
+    %   \> \ $|_{\text{R}8}$  \acro{np}$_1$ \> \ $|_{\text{R}9}$ verbunden.
+    % \end{tabbing}
+\end{exe}
+
+Note that differences between Regions 1, 2, 4 and 7 can be expected
+due to lexical differences between the \as and \es-conditions. As
+target-related fillers did not differ with respect to their lexical
+properties, we carried out word-by-word analyses for these
+conditions. Durational values included the respective word plus any
+following silent interval. Note that we did not include the
+disambiguated fillers in these analyses as they involved very
+different sentence types (i.e., constructions involving prepositional
+phrases vs.~relative clauses).
+
+\begin{exe}
+  \ex $|_{\text{R}1}$ \acro{D}  	\ $|_{\text{R}2}$ $\acro{np}_1$
+      \ $|_{\text{R}3}$ ist 
+      \ $|_{\text{R}4}$ mit  \ $|_{\text{R}5}$ $\acro{np}_2$   \
+      $|_{\text{R}6}$ und  \ $|_{\text{R}7}$ $\acro{np}_3$ 
+       \ $|_{\text{R}8}$  mit  \ $|_{\text{R}9}$ $\acro{np}_4$ \ $|_{\text{R}10}$~verbunden.
+\end{exe}
+
+For the durational analyses, constituents were automatically labeled
+by the \emph{Aligner} tool (XYZ),\dn{reference! Rapp, 1998} and the
+obtained values were manually corrected afterwards. For the targets,
+two-factorial \acros{anova} with the factors \acro{Quantifier} (all
+vs. exactly one) and \acro{Prosody} (accented vs.~unaccented) were
+carried out. For the target-related fillers, we carried out
+one-factorial \acros{anova} with the factor \acro{Prosody} (early
+boundary, late boundary, neutral prosody). F0 values were extracted by
+means of special Praat scripts
+(\url{http://www.fon.hum.uva.nl/praat/}). For the present analyses,
+differences between minimal and maximal F0 values for each region or
+word were calculated. Again, two-factorial \acros{anova} were carried
+out for statistical comparison of the fillers, and one-factorial
+\acros{anova} were carried out for target-related structures.
+
+\paragraph{Targets.} Table~\ref{tab:table-A} shows the durational values for each of
+the single regions in the sentence. Crucially, durational values of
+accented determiners were significantly increased as opposed to their
+non-accented counterparts. Overall, \acro{Quantifier} effects were
+observed, which might be attributed to the above-mentioned lexical
+differences, as well as to the fact that \es-structures generally
+contained fewer words, thus leading to a tendency of a durational
+decrease for each of the single words.
+
+Differences between maximal and minimal F0 values for each of the
+single words in the sentence are depicted in
+Table~\ref{tab:table-B}. As is descriptively evident, accented
+determiners showed a larger F0 range compared to unaccented versions,
+an effect which is confirmed by statistical analyses. An additional
+\acro{Quantifier}*\acro{Prosody} interaction indicates that these
+differences are even more pronounced in the \as-condition. Finally,
+comparable to the durational analyses, \acro{Quantifier} effects were
+observed when conditions exhibited lexical differences.
+
+Finally, differences between maximal and minimal F0 values for each of
+the single words in the sentence are given in
+Table~\ref{tab:table-D}. Again, the most reliable differences occur at
+the boundary regions.\dn{provide caption for table D}
+
+\begin{table}
+  \centering
+
+  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-A.png}
+
+  \caption{Durational values in ms for each of the single regions in the target sentences. Region 6 corresponds to \emph{einigen}.}
+  \label{tab:table-A}
+\end{table}
+
+\begin{table}
+  \centering
+
+  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-B.png}
+
+  \caption{Difference between minimal and maximal F0 values in Hz for
+    each of the single words in the target sentences. Region 6
+    corresponds to \emph{einigen}.} 
+  \label{tab:table-B}
+\end{table}
+
+\paragraph{Target-related fillers.} Table~\ref{tab:table-C} shows the
+durational values of each of the single words in the sentence. As is
+descriptively evident, the largest durational differences were
+realized at the boundary regions (i.e. Region 5 and Region
+7). Interestingly, small differences between conditions also yielded
+significance at other positions, suggesting that our speaker produced
+the different conditions very consistently (i.e., with little
+variance).
+
+\begin{table}
+  \centering
+
+  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-C.png}
+
+  \caption{Durational values in ms for each of the single regions in
+    the target-related fillers. Regions 5 and 7 correspond to the
+    nouns preceding the boundaries.}  
+  \label{tab:table-C}
+\end{table}
+
+\begin{table}
+  \centering
+
+  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-D.png}
+
+  \caption{???}  
+  \label{tab:table-D}
+\end{table}
 

### 2012-07-02 text/paper/paper.tex
paper just typos
paper added notes

@@
 
-  \caption{Distinguishing scenarious for \as-sentences}
+  \caption{Distinguishing scenarios for \as-sentences}
   \label{fig:AS-distinguishing-pics}
@@
 
-  \caption{Distinguishing scenarious for \es-sentences}
+  \caption{Distinguishing scenarios for \es-sentences}
   \label{fig:ES-distinguishing-pics}
@@
 
-\subsection{Critique}
+\subsection{Reflection}
 \label{sec:critique}
@@
 Summing up, the mentioned studies have presented diverging evidence
-concerning the availability of local readings. Varoius problematic
+concerning the availability of local readings. Various problematic
 aspects of these studies have already been discussed elsewhere
@@
 we willl argue below we do, however, believe it is.
+
+\bigskip
+
+We also tested examples like (\ref{bsp:EA}), which are the ``global
+alternatives'' to \es-sentences, with a universal quantifier where
+\es-sentences have scalar \emph{some}.
+\begin{exe}
+\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es mag \mymark{jede} dieser
+  Speisen. \label{bsp:EA}\\
+  For exactly one {of these} children {it holds} it likes all {of
+    these} dishes.\\
+  For exactly one of these children it holds that it likes all of these dishes.
+\end{exe}
+Sentence like (\ref{bsp:EA}) are literally true in both of the
+situations given in Figure~\ref{fig:EA-distinguishing-pics}, but these
+situations differ in the truth value of the corresponding
+\es-sentence. Interestingly, we found a difference in acceptability,
+but a curious one. The sentence was judged \emph{true} in 90.34\% of
+the cases for the situation in Figure~\ref{fig:global-EA} and in
+98.34\% in situation \ref{fig:literal-EA}. The observed difference is
+significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$). That is a
+curious finding, because, from the point of view of implicature
+calculation, the only thing that could plausibly explain this
+acceptability difference is the presence of a global implicature,
+resulting from the negation of the corresponding \es-sentence. But
+such a putative global implicature would be true in the
+situation~\ref{fig:global-EA}, but false in the
+situation~\ref{fig:literal-EA}. Consequently, the observed difference
+in acceptability cannot be explained simply in terms of the hypothesis
+of \citet{ChemlaSpector2010:Experimental-Ev} that acceptability is
+proportional to the number of available true readings: if a putative
+global reading is at stake, the acceptability pattern should be
+reversed; if no such global reading is at stake, then the
+acceptability difference cannot be explained.
+
+\begin{figure}[]
+  \centering
+
+\subfloat[fig:global][global]{
+  \label{fig:global-EA}
+
+  \begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & true \\
+            \glb & true
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=blue,->] (X-1) -> (Y-1);
+
+        \path [draw=blue,->] (X-1) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-1);
+
+        \path [draw=black,->] (X-2) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-3);
+
+        \path [draw=black,->] (X-2) -> (Y-4);
+
+      \end{tikzpicture}
+
+} \qquad \qquad
+\subfloat[fig:literal][literal]{
+  \label{fig:literal-EA}
+
+      \begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & true \\
+            \glb & false
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=black,->] (X-2) -> (Y-1);
+
+        \path [draw=black,->] (X-2) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-3);
+
+        \path [draw=black,->] (X-2) -> (Y-4);
+
+      \end{tikzpicture}
+
+}
+
+  \caption{Distinguishing scenarios for sentence XYZ}
+  \label{fig:EA-distinguishing-pics}
+
+\end{figure}
 

### 2012-07-02 text/paper/paper.tex
paper added notes

@@
 which was assumed to be easier to assess and better at highlighting
-the relevance of the local readings. Additionally, subjects were
-asked, not for categorial judgements, but for graded judgements:
+the relevance of the local readings. Albeit in a different format, the
+pictures used by \citeauthor{ChemlaSpector2010:Experimental-Ev} were
+all different instantiation of the situation types in
+Figures~\ref{fig:AS-distinguishing-pics} and
+\ref{fig:ES-distinguishing-pics}. Additionally, subjects were asked,
+not for categorial judgements, but for \mymark{graded judgements}:
 subjects could freely click on a scale, as shown in
@@
 
-Albeit in a different format, the pictures used by
-\citeauthor{ChemlaSpector2010:Experimental-Ev} were all different
-instantiation of the situation types in
-Figures~\ref{fig:AS-distinguishing-pics} and
-\ref{fig:ES-distinguishing-pics}. The results reported in this study
-are averaged clicking positions, as shown in
-Figure~\ref{fig:Chemla-Spector-Results}.
+\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the
+degree to which a sentence was rated acceptable is proportional to the
+number of available true readings. Observed averaged clicking
+positions are shown in Figure~\ref{fig:Chemla-Spector-Results}.
 %
@@
 
-We also tested examples like (\ref{bsp:EA}), which are the ``global
+\begin{center}
+  \textbf{Micha's notes:}
+\end{center}
+
+\begin{itemize}
+\item K1:
+  \begin{itemize}
+  \item tried to replicate
+    \citet{GeurtsPouscoulous2009:Embedded-Implic}'s study
+  \item but tested all conditions
+  \item used German cleft-sentences (possibly problematic)
+  \item some evidence for subjective patterns in answers
+  \end{itemize}
+\item We also tested examples like (\ref{bsp:EA}), which are the ``global
 alternatives'' to \es-sentences, with a universal quantifier where
@@
 \begin{exe}
-\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es mag \mymark{jede} dieser
-  Speisen. \label{bsp:EA}\\
+\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es
+  mag \mymark{jede} dieser Speisen. \label{bsp:EA}\\
   For exactly one {of these} children {it holds} it likes all {of
@@
 acceptability difference cannot be explained.
+\end{itemize}
 

### 2012-07-03 text/paper/paper.tex
paper reworked motivation section, more typicality

@@
             colorlinks,       % rather than outlining them in boxes
-            linkcolor=gray,   % override truly awful colour choices
+            linkcolor=gray,   % override truly awful color choices
             citecolor=gray,   %   (ditto)
@@
                            % attributions
-
+\usepackage{eurosym}
 \usepackage{pgfplots}
@@
 crucial piece of evidence for the availability of local readings for
-\as-sentences was that these sentences yielded higher graded
+\as-sentences is that these sentences yielded higher graded
 acceptability scores for the strong situation than for the weak
@@
 
-\subsection{Reflection}
-\label{sec:critique}
-
-Summing up, the mentioned studies have presented diverging evidence
-concerning the availability of local readings. Various problematic
-aspects of these studies have already been discussed elsewhere
-\citep[e.g.][]{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,Tielvan-Tiel2012:Embedded-Scalar}. Here,
-we want to point out two particular methodological problems that do
-impede their interpretation. However, we also want to make clear that
-these problems follow almost directly from the nature of the
-phenomenon under investigation and therefore seem nearly impossible to
-avoid.
-
-Firstly, a mapping between responses in a picture-verification task
-and readings of the relevant sentences is problematic due to the
-logical dependencies between the relevant readings discussed in
-Section~\ref{sec:get-know-your}. Let us consider \as-sentences in the
-following because these have been addressed by all three
-aforementioned studies. (Similar arguments apply to \es-sentences.) It
-is impossible to construct situations that clearly correspond to local
-readings of \as-sentences, since the local reading of such sentences
-implies their global and local readings. Every situation which is
-consistent with such a sentence under its local reading is also
-consistent with the other two readings. Therefore, we cannot test
-directly and independently all the cases we might wish to using a
-simple picture-verification paradigm. It would be especially desirable
-to test situations that are consistent with the local reading, but
-inconsistent with the global and literal reading. In that case
-\emph{yes}-responses would unambiguously indicate availability of
-local readings. However, since this is impossible we are left with
-suboptimal choices. In the experiment of
-\citet{GeurtsPouscoulous2009:Embedded-Implic} situations that are
-inconsistent with local readings but consistent with the other two
-readings were tested. In that case \emph{no}-responses would be decisive~--
-when compared to a suitable baseline. However, \emph{yes}-responses were
-observed exclusively. These can be attributed to one of the other
-readings. Therefore, assuming a principle of charity
-\citep{Davidson1973:Radical-Interpr} to be at play in picture
-verification tasks, the data of Geurts do not provide evidence against
-the existence of local readings.  In the experiments of C\&S and C\&D
-on the other hand situations that are consistent with all three
-readings were tested. Here again 'yes'-judgments cannot be interpreted
-confidently because they can always be attributed to global or literal
-readings. Both C\&S and C\&D attempt to surpass this problem by
-interpreting relative preferences. This does, however, bring us to the
-second problem.
-
-Preferences may be affectd by graphical properties of the picture
-materials. For example, verification complexity or typicality of the
-pictures with respect to the test sentences may differ between
-conditions and thereby induce certain preferences. In his careful
-critique van Tiel has eleborated on this point. Van Tiel points out
-that the relative preferences C\&S and C\&D interpret can be explained
-solely in terms of typicality, because the `strong'-situation (see
-e.g.~Figure~\ref{fig:strong}) are more typical instances of the
-sentence meaning than the competing pictures, irrespective of local
-implicatures.
-
-To conclude, in order to decide about the availablity of local
-implicatures we would ideally like to test situations that can
-unambiguously be mapped to the different readings and do not differ in
-typcality or other crucial properties. Given the logical dependencies
-inherent to the relevant readings and the considerations concerning
-typicality presented by van Tiel this seems impossible to achieve. As
-we willl argue below we do, however, believe it is.
-
-\bigskip
-
+\subsection{Reflection: Categorical Judgements \& Typicality}
+\label{sec:local-read-categ}
+
+Summing up so far, three previous studies have presented different
+pieces of evidence concerning putative local readings. G\&P's results
+suggest that local readings are not available, because they do not
+affect a categorical truth-value judgments in a picture-verification
+task. On the other hand, C\&D's and C\&S's design was suggested to be
+sensitive enough to reveal effects of local readings: either by a
+choice of the situation that better befits a given sentence (C\&D), or
+by a graded truth-value judgment (C\&S).
+
+To account for all of the available data in conjunction, it could be
+hypothesized along with C\&D and C\&S that local readings are
+available, but so dispreferred they do not affect simple
+\emph{categorical} truth-value judgements. This, however, does not
+seem to be the case, as revealed by a pilot study of ourselves. We
+tried to replicate G\&P's results, using a simple categorial
+truth-value judgement task on pictures that were exactly like those in
+Figures \ref{fig:AS-distinguishing-pics} and
+\ref{fig:ES-distinguishing-pics}. Test sentences were German
+cleft-constructions as in (\ref{bsp:AS-K1}) and
+(\ref{bsp:ES-K1}).\fn{We concede that these cleft-constructions might
+  unduly emphasize potential local readings, but that is not
+  essential, because the main issue we are trying to address here is
+  whether putative local readings \emph{could} affect categorical
+  truth-value judgements.}
+\begin{exe}
+\ex \gll F\"{u}r \mymark{jedes} dieser Kinder gilt: es
+  mag \mymark{einige} dieser Speisen. \label{bsp:AS-K1}\\
+  For every {of these} children {it holds} it likes some {of
+    these} dishes.\\
+  For all of these children it holds that it likes some of these dishes.
+\end{exe}
+\begin{exe}
+\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es
+  mag \mymark{einige} dieser Speisen. \label{bsp:ES-K1}\\
+  For exactly one {of these} children {it holds} it likes some {of
+    these} dishes.\\
+  For exactly one of these children it holds that it likes some of these dishes.
+\end{exe}
+60 native German speakers (40 female, mean age: $24$, ranging between
+$20$ and $40$) participated in this pilot. Participants were na\"ive
+to the purpose of the study and were paid \euro{10}
+compensation.\dn{We should expand on the method in an appendix}
+
+Mean acceptance rates for our target
+sentences were (see also Figure~\ref{fig:Bars-K1}):
 \begin{center}
-  \textbf{Micha's notes:}
+  \begin{tabular}{ccccccccc}
+    \multicolumn{4}{c}{\as-sentences} &&
+    \multicolumn{4}{c}{\es-sentences}     \\ \cmidrule(r){1-4} \cmidrule(r){6-9}
+    false & literal & weak & strong && false & local & literal & all
+    \\ \midrule 
+    .9 & 72 & 79 & 90 && .8 & 20 & 71 & 93 
+  \end{tabular}
 \end{center}
-
-\begin{itemize}
-\item K1:
-  \begin{itemize}
-  \item tried to replicate
-    \citet{GeurtsPouscoulous2009:Embedded-Implic}'s study
-  \item but tested all conditions
-  \item used German cleft-sentences (possibly problematic)
-  \item some evidence for subjective patterns in answers
-  \end{itemize}
-\item We also tested examples like (\ref{bsp:EA}), which are the ``global
-alternatives'' to \es-sentences, with a universal quantifier where
-\es-sentences have scalar \emph{some}.
+Two observations are of interest here. Firstly, unlike G\&P, we
+observed \emph{false}-judgements in the \as-weak condition, as well as
+\emph{true}-judgements in the \es-local condition. Secondly, the
+observed difference between the \as-weak and the \as-strong
+conditions, on the one had, and the \es-false and the \es-local
+condition, on the other hand, both reached significance.\dn{spell out
+  in appendix}
+
+\begin{figure}[]
+\centering
+\subfloat[\as-sentences]{
+\includegraphics[width=5.5cm]{../pictures/paper/JudgmentsAllSomeBars.pdf}
+\label{fig:EABars}
+}
+\subfloat[\es-sentences]{
+\includegraphics[width=5cm]{../pictures/paper/JudgmentsExactlySomeBars.pdf}
+\label{fig:EEBars}
+}
+\caption{Means of \emph{true}-judgments in our pilot study}
+\label{fig:Bars-K1}
+\end{figure}
+
+The perhaps most obvious explanation for these observed patterns is
+that local readings \emph{are} available and \emph{can} have an effect
+even on categorical truth-value judgements. However, we believe that
+this interpretation of the data is problematic for reasons already
+addressed also by \citet{ChemlaSpector2010:Experimental-Ev} and, more
+recently, \citet{Tielvan-Tiel2012:Embedded-Scalar}. The problem is
+that the present variants of truth-value judgment tasks all run risk
+of conflating evidence about the availability or preference of
+readings with properties of the pictorial material that are
+independent of the reading to be assessed. This problem affects all of
+the studies covered above, to some degree or other, because it follows
+almost directly from the nature of the phenomenon under investigation
+and therefore seems nearly impossible to avoid.
+
+To illustrate the potential conflation, consider a sentence like
+(\ref{bsp:EA}), which is a ``global alternatives'' to an \es-sentence,
+with a universal quantifier where an \es-sentence has scalar
+\emph{some}.
 \begin{exe}
@@
 situations differ in the truth value of the corresponding
-\es-sentence. Interestingly, we found a difference in acceptability,
+\es-sentence. Our pilot study revealed a difference in acceptability,
 but a curious one. The sentence was judged \emph{true} in 90.34\% of
@@
 98.34\% in situation \ref{fig:literal-EA}. The observed difference is
-significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$). That is a
+significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$). This is a
 curious finding, because, from the point of view of implicature
@@
 of \citet{ChemlaSpector2010:Experimental-Ev} that acceptability is
-proportional to the number of available true readings: if a putative
-global reading is at stake, the acceptability pattern should be
-reversed; if no such global reading is at stake, then the
-acceptability difference cannot be explained.
+proportional to the number of available true readings. Rather some
+feature of the pictorial material that is independent of the putative
+readings under scrutiny does affect truth-value judgements, even
+categorical ones.
+
+\citet{ChemlaSpector2010:Experimental-Ev} acknowledge the possibility
+that the \emph{typicality} of a picture may affect graded truth-value
+judgements. Stronger still, they show that graded judgments of
+\as-sentences differ significantly for different instantiations of the
+conditions in \ref{fig:AS-distinguishing-pics}, that differ in the
+amount of connections, but not so that they would alter the assignment
+of truth-values to candidate
+readings. \citeauthor{ChemlaSpector2010:Experimental-Ev} suggest that
+typicality of the pictorial material can account for these
+differences, but submit that this does not explain away the effect of
+the local reading. This is disputed by
+\citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates that all of
+\citeauthor{CliftonDube2010:Embedded-Implic}'s and
+\citeauthor{ChemlaSpector2010:Experimental-Ev}'s data on \as-sentences
+can be explained as typicality effects, dispensing the need to appeal
+to any influence of local readings. We are sympathetic towards
+\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
+reinterpretation of the data, but note, as
+\citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
+typicality-based explanation does not extend to \es-sentences in an
+obvious way\fn{For similar reasons, appeal to typicality cannot
+  explain, as far as we can see, the
+  preference for the situation in Figure~\ref{fig:literal-EA} over
+  that in Figure\ref{fig:global-EA} given a sentence like
+  (\ref{bsp:EA}).} and that it also does not explain why we observed putative
+effects of typicality also in categorical judgements in our pilot.
+
+\bigskip
+
+To conclude, in order to decide about the availablity of local
+implicatures we would ideally like to test situations that can
+unambiguously be mapped to the different readings and do not differ in
+typicality or other crucial properties. Given the logical dependencies
+inherent to the relevant readings and the considerations concerning
+typicality presented by van Tiel this seems impossible to achieve. As
+we willl argue below we do, however, believe it is.
+
+\begin{itemize}
+\item what's needed
+  \begin{itemize}
+  \item evidence about all preferences
+  \item factor out picture-complexity
+  \item preferably categorical judgements
+  \item intonation
+  \end{itemize}
+
+\end{itemize}
+
+\bigskip
+
+\begin{center}
+  \textbf{Micha's notes:}
+\end{center}
+
+\begin{itemize}
+\item K1:
+  \begin{itemize}
+  \item tried to replicate
+    \citet{GeurtsPouscoulous2009:Embedded-Implic}'s study
+  \item but tested all conditions
+  \item used German cleft-sentences (possibly problematic)
+  \item some evidence for subjective patterns in answers
+  \end{itemize}
+\item Thirdly, we observed that a tendency that participants
+who rejected \as-sentences in the literal situation where more prone
+to also accept \es-sentences in the local condition.\dn{spell out
+  in appendix} This suggests that there might be participants who are
+more likely to be influenced by local readings than others.
 \end{itemize}

### 2012-07-04 text/paper/paper.tex
paper micha version on critique of previous studies and motivation of our own

@@
 pictures used by \citeauthor{ChemlaSpector2010:Experimental-Ev} were
-all different instantiation of the situation types in
+instantiations of the situation types in
 Figures~\ref{fig:AS-distinguishing-pics} and
@@
   \centering
-      \includegraphics[scale=0.35]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
-      \includegraphics[scale=0.35]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
-        \caption{Example of critical trial for \as-condition by
-          \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
-          (\citeyear{ChemlaSpector2010:Experimental-Ev})}
+
+  \subfloat[][Example of the \as-weak condition of
+  \citet{ChemlaSpector2010:Experimental-Ev}]{
       \label{fig:Chemla-Spector}
-\end{figure}
-
-\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the
-degree to which a sentence was rated acceptable is proportional to the
-number of available true readings. Observed averaged clicking
-positions are shown in Figure~\ref{fig:Chemla-Spector-Results}.
-%
-\begin{figure}
-  \centering
-  \subfloat[][\as-condition]{
+  \begin{minipage}{0.45\linewidth}
+    \begin{center}
+      \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
+      \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
+    \end{center}
+
+  \end{minipage}
+    }
+   \begin{minipage}{6cm}
+     \subfloat[][Results \as-condition]{
     \label{fig:CS-Results-as}
@@
   }
-  \subfloat[test][\es-condition]{
+
+  \subfloat[test][Results \es-condition]{
     \label{fig:CS-Results-es}
@@
   }  
-  \caption{Results from
+   \end{minipage}
+        \caption{Example trial and results of
           \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
-    (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
-  \label{fig:Chemla-Spector-Results}
+          (\citeyear{ChemlaSpector2010:Experimental-Ev}) study.}
 \end{figure}
+
+% \begin{figure}[t]
+%   \centering
+%       \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
+%       \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
+%         \caption{Example of critical trial for \as-condition by
+%           \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
+%           (\citeyear{ChemlaSpector2010:Experimental-Ev})}
+%   \label{fig:Chemla-Spector}
+% \end{figure}
+
+\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the
+degree to which a sentence is rated acceptable is proportional to the
+number of available true readings. Observed averaged clicking
+positions are shown in Figures~\ref{fig:CS-Results-as} and
+\ref{fig:CS-Results-es}.
+%
+% \begin{figure}
+%   \centering
+%   \subfloat[][\as-condition]{
+%     \label{fig:CS-Results-as}
+%         \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
+%   }
+%   \subfloat[test][\es-condition]{
+%     \label{fig:CS-Results-es}
+%     \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
+%   }
+%   \caption{Results from
+%     \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
+%     (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
+%   \label{fig:Chemla-Spector-Results}
+% \end{figure}
 %
@@
 of the local reading for \es-sentences comes from the difference
-between the local and the literal situation. Strikingly, in the latter
-case, the \es-sentences received an average of 73\% acceptability in
-the local situation although the literal and global readings are false
-in this case.
+between the local and the literal situation. Strikingly, \es-sentences
+received an average 73\% degree of acceptability in the local
+situation although the literal and global readings are false in this
+case.
 
@@
 Summing up so far, three previous studies have presented different
-pieces of evidence concerning putative local readings. G\&P's results
+pieces of evidence concerning putative local
+readings. \citeauthor{ChemlaSpector2010:Experimental-Ev}'s results
 suggest that local readings are not available, because they do not
 affect a categorical truth-value judgments in a picture-verification
-task. On the other hand, C\&D's and C\&S's design was suggested to be
-sensitive enough to reveal effects of local readings: either by a
-choice of the situation that better befits a given sentence (C\&D), or
-by a graded truth-value judgment (C\&S).
-
-To account for all of the available data in conjunction, it could be
-hypothesized along with C\&D and C\&S that local readings are
-available, but so dispreferred they do not affect simple
-\emph{categorical} truth-value judgements. This, however, does not
-seem to be the case, as revealed by a pilot study of ourselves. We
-tried to replicate G\&P's results, using a simple categorial
-truth-value judgement task on pictures that were exactly like those in
-Figures \ref{fig:AS-distinguishing-pics} and
-\ref{fig:ES-distinguishing-pics}. Test sentences were German
+task. On the other hand,
+\citeauthor{CliftonDube2010:Embedded-Implic}'s and
+\citeauthor{ChemlaSpector2010:Experimental-Ev}'s design was suggested
+to be sensitive enough to reveal effects of local readings: either by
+a choice of the situation that better befits a given sentence
+(\citeauthor{CliftonDube2010:Embedded-Implic}), or by a graded
+truth-value judgment (\citeauthor{ChemlaSpector2010:Experimental-Ev}).
+
+To account for all of these observations, it could be hypothesized
+along with \citeauthor{CliftonDube2010:Embedded-Implic} and
+\citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
+available, but so dispreferred that they do not affect simple
+\emph{categorical} truth-value judgements. It could then furthermore
+be argued, in line with traditionalism, that the reason why local
+readings do not affect categorical judgements is because they are not
+(strongly) truth-relevant speaker-intended meaning enrichments after
+all, so that no case can be made for lexicalism or grammaticalism
+\citep[c.f.][for arguments along these lines]{Tielvan-Tiel2012:Embedded-Scalar}.
+
+Either position is cast into doubt by a pilot study of
+ourselves.\dn{We should expand on the method in an appendix} We tried
+to replicate \citeauthor{ChemlaSpector2010:Experimental-Ev}'s results,
+using a simple categorial truth-value judgement task on pictures that
+were exactly like those in Figures \ref{fig:AS-distinguishing-pics}
+and \ref{fig:ES-distinguishing-pics}. Test sentences were German
 cleft-constructions as in (\ref{bsp:AS-K1}) and
@@
 \end{exe}
-60 native German speakers (40 female, mean age: $24$, ranging between
-$20$ and $40$) participated in this pilot. Participants were na\"ive
-to the purpose of the study and were paid \euro{10}
-compensation.\dn{We should expand on the method in an appendix}
-
-Mean acceptance rates for our target
-sentences were (see also Figure~\ref{fig:Bars-K1}):
+Mean acceptance rates of 60 native German speakers for our target
+sentences were:
 \begin{center}
@@
 \end{center}
-Two observations are of interest here. Firstly, unlike G\&P, we
-observed \emph{false}-judgements in the \as-weak condition, as well as
-\emph{true}-judgements in the \es-local condition. Secondly, the
-observed difference between the \as-weak and the \as-strong
-conditions, on the one had, and the \es-false and the \es-local
-condition, on the other hand, both reached significance.\dn{spell out
-  in appendix}
-
-\begin{figure}[]
-\centering
-\subfloat[\as-sentences]{
-\includegraphics[width=5.5cm]{../pictures/paper/JudgmentsAllSomeBars.pdf}
-\label{fig:EABars}
-}
-\subfloat[\es-sentences]{
-\includegraphics[width=5cm]{../pictures/paper/JudgmentsExactlySomeBars.pdf}
-\label{fig:EEBars}
-}
-\caption{Means of \emph{true}-judgments in our pilot study}
-\label{fig:Bars-K1}
-\end{figure}
-
-The perhaps most obvious explanation for these observed patterns is
-that local readings \emph{are} available and \emph{can} have an effect
-even on categorical truth-value judgements. However, we believe that
-this interpretation of the data is problematic for reasons already
-addressed also by \citet{ChemlaSpector2010:Experimental-Ev} and, more
-recently, \citet{Tielvan-Tiel2012:Embedded-Scalar}. The problem is
-that the present variants of truth-value judgment tasks all run risk
-of conflating evidence about the availability or preference of
-readings with properties of the pictorial material that are
-independent of the reading to be assessed. This problem affects all of
-the studies covered above, to some degree or other, because it follows
-almost directly from the nature of the phenomenon under investigation
-and therefore seems nearly impossible to avoid.
+Two observations are of interest here. Firstly, we observed 21\%
+\emph{false}-judgements in the \as-weak condition, as well as 20\%
+\emph{true}-judgements in the \es-local condition, contrary to the 0\%
+in each case observed by
+\citet{GeurtsPouscoulous2009:Embedded-Implic}. Secondly, the observed
+difference between the \as-weak and the \as-strong conditions, on the
+one had, and the \es-false and the \es-local condition, on the other
+hand, both reached significance.\dn{spell out in appendix}
+
+% \begin{figure}[]
+% \centering
+% \subfloat[\as-sentences]{
+% \includegraphics[width=5.5cm]{../pictures/paper/JudgmentsAllSomeBars.pdf}
+% \label{fig:EABars}
+% }
+% \subfloat[\es-sentences]{
+% \includegraphics[width=5cm]{../pictures/paper/JudgmentsExactlySomeBars.pdf}
+% \label{fig:EEBars}
+% }
+% \caption{Means of \emph{true}-judgments in our pilot study}
+% \label{fig:Bars-K1}
+% \end{figure}
+
+These observed patterns suggest that local readings \emph{are}
+available and \emph{can} have an effect even on categorical
+truth-value judgements. However, this interpretation of the data is
+problematic for reasons already addressed also by
+\citet{ChemlaSpector2010:Experimental-Ev} and, more recently,
+\citet{Tielvan-Tiel2012:Embedded-Scalar}. The problem is that the
+present variants of truth-value judgment tasks all run risk of
+conflating evidence about the availability or preference of readings
+with properties of the pictorial material that are independent of the
+reading to be assessed. This problem affects all of the studies
+covered above, to some degree or other, because it follows almost
+directly from the nature of the phenomenon under investigation and
+therefore seems nearly impossible to avoid.
 
 To illustrate the potential conflation, consider a sentence like
-(\ref{bsp:EA}), which is a ``global alternatives'' to an \es-sentence,
+(\ref{bsp:EA}), which is a ``global alternative'' to an \es-sentence,
 with a universal quantifier where an \es-sentence has scalar
@@
 \end{exe}
-Sentence like (\ref{bsp:EA}) are literally true in both of the
-situations given in Figure~\ref{fig:EA-distinguishing-pics}, but these
+Sentences like (\ref{bsp:EA}) are literally true in both of the
+situations in Figure~\ref{fig:EA-distinguishing-pics}, but these
 situations differ in the truth value of the corresponding
-\es-sentence. Our pilot study revealed a difference in acceptability,
-but a curious one. The sentence was judged \emph{true} in 90.34\% of
+\es-sentence.
+%
+\begin{figure}[]
+  \centering
+
+\subfloat[fig:global][global]{
+  \label{fig:global-EA}
+
+  \begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & true \\
+            \glb & true
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=blue,->] (X-1) -> (Y-1);
+
+        \path [draw=blue,->] (X-1) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-1);
+
+        \path [draw=black,->] (X-2) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-3);
+
+        \path [draw=black,->] (X-2) -> (Y-4);
+
+      \end{tikzpicture}
+
+} \qquad \qquad
+\subfloat[fig:literal][literal]{
+  \label{fig:literal-EA}
+
+      \begin{tikzpicture}[node distance = 1cm]
+        % Nodes
+
+        \node (X-1) {$\Large{\bullet}$};
+
+        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
+
+        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
+
+        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
+
+        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
+
+        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
+
+        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
+
+        % table added from here
+
+        \node (X-4) [below of = X-3, node distance = 2cm] {};
+
+        \node (table) [right of = X-4] {
+          \begin{tabular}{ll}
+            \lit & true \\
+            \glb & false
+          \end{tabular}};
+
+        % Arrows
+
+        \path [draw=black,->] (X-2) -> (Y-1);
+
+        \path [draw=black,->] (X-2) -> (Y-2);
+
+        \path [draw=black,->] (X-2) -> (Y-3);
+
+        \path [draw=black,->] (X-2) -> (Y-4);
+
+      \end{tikzpicture}
+
+}
+
+\caption{Distinguishing scenarios for sentence(\ref{bsp:EA})}
+  \label{fig:EA-distinguishing-pics}
+
+\end{figure}
+%
+Our pilot study revealed a difference in acceptability,
+but a curious one. The sentence was judged \emph{true} in 90.3\% of
 the cases for the situation in Figure~\ref{fig:global-EA} and in
-98.34\% in situation \ref{fig:literal-EA}. The observed difference is
+98.3\% in situation \ref{fig:literal-EA}. The observed difference is
 significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$). This is a
@@
 acceptability difference is the presence of a global implicature,
-resulting from the negation of the corresponding \es-sentence. But
-such a putative global implicature would be true in the
+resulting from the negation of the corresponding
+\es-sentence.\fn{Notice that (\ref{bsp:EA}) is the alternative to the
+  corresponding \es-sentence needed for computing the putative global
+  implicature. But these sentences are logically independent. So, it
+  may be that the corresponding \es-sentence is an alternative also to
+  sentences like (\ref{bsp:EA}). It may also be that being an
+  alternative is not a symmetric notion. Be that as it may, our
+  argument does not hinge on whether (\ref{bsp:EA}) does or does not
+  actually have a global implicature of the alleged kind.} But such a
+putative global implicature would be true in the
 situation~\ref{fig:global-EA}, but false in the
@@
 \as-sentences differ significantly for different instantiations of the
-conditions in \ref{fig:AS-distinguishing-pics}, that differ in the
-amount of connections, but not so that they would alter the assignment
-of truth-values to candidate
-readings. \citeauthor{ChemlaSpector2010:Experimental-Ev} suggest that
-typicality of the pictorial material can account for these
-differences, but submit that this does not explain away the effect of
-the local reading. This is disputed by
+conditions in \ref{fig:AS-distinguishing-pics}, that vary in the
+amount of connections without changing the assignment of truth values
+to candidate readings. \citeauthor{ChemlaSpector2010:Experimental-Ev}
+suggest that typicality of the pictorial material can account for
+these differences, but submit that this does not explain away the
+effect of the local reading. This is disputed by
 \citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates that all of
@@
 obvious way\fn{For similar reasons, appeal to typicality cannot
-  explain, as far as we can see, the
-  preference for the situation in Figure~\ref{fig:literal-EA} over
-  that in Figure\ref{fig:global-EA} given a sentence like
-  (\ref{bsp:EA}).} and that it also does not explain why we observed putative
-effects of typicality also in categorical judgements in our pilot.
-
-\bigskip
-
-To conclude, in order to decide about the availablity of local
-implicatures we would ideally like to test situations that can
-unambiguously be mapped to the different readings and do not differ in
-typicality or other crucial properties. Given the logical dependencies
-inherent to the relevant readings and the considerations concerning
-typicality presented by van Tiel this seems impossible to achieve. As
-we willl argue below we do, however, believe it is.
-
-\begin{itemize}
-\item what's needed
-  \begin{itemize}
-  \item evidence about all preferences
-  \item factor out picture-complexity
-  \item preferably categorical judgements
-  \item intonation
-  \end{itemize}
-
-\end{itemize}
-
-\bigskip
-
-\begin{center}
-  \textbf{Micha's notes:}
-\end{center}
-
-\begin{itemize}
-\item K1:
-  \begin{itemize}
-  \item tried to replicate
-    \citet{GeurtsPouscoulous2009:Embedded-Implic}'s study
-  \item but tested all conditions
-  \item used German cleft-sentences (possibly problematic)
-  \item some evidence for subjective patterns in answers
-  \end{itemize}
-\item Thirdly, we observed that a tendency that participants
-who rejected \as-sentences in the literal situation where more prone
-to also accept \es-sentences in the local condition.\dn{spell out
-  in appendix} This suggests that there might be participants who are
-more likely to be influenced by local readings than others.
-\end{itemize}
-
-\begin{figure}[]
-  \centering
-
-\subfloat[fig:global][global]{
-  \label{fig:global-EA}
-
-  \begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & true \\
-            \glb & true
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=blue,->] (X-1) -> (Y-1);
-
-        \path [draw=blue,->] (X-1) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-1);
-
-        \path [draw=black,->] (X-2) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-3);
-
-        \path [draw=black,->] (X-2) -> (Y-4);
-
-      \end{tikzpicture}
-
-} \qquad \qquad
-\subfloat[fig:literal][literal]{
-  \label{fig:literal-EA}
-
-      \begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & true \\
-            \glb & false
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=black,->] (X-2) -> (Y-1);
-
-        \path [draw=black,->] (X-2) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-3);
-
-        \path [draw=black,->] (X-2) -> (Y-4);
-
-      \end{tikzpicture}
-
-}
-
-  \caption{Distinguishing scenarios for sentence XYZ}
-  \label{fig:EA-distinguishing-pics}
-
-\end{figure}
-
-\subsection{To-Be-Included Here}
-\label{sec:whats-missing}
-
-\begin{itemize}
-\item establish independence (as much as possible) of pictorial
-  complexity/stereotypicality and assessment of reading
-  \begin{itemize}
-  \item not desirable to raise the level of relevance of local
-    readings, because we want to test the base-line / default (cite
-    Geurts / van Tiel)
-  \item unclear what graded truth-value judgements measure exactly
-    (re-read \citet{Chemla2009:Presuppositions} if needed)
-  \item cannot separate judgements about sentences from judgements
-    about pictures (van Tiel)
-  \item unclear whether design assesses preferences of readings or
-    targets pictorial complexity / typicality (van Tiel)
-  \end{itemize}
-\item provide a benchmark from which to deduce preference relations
-\item control for intonational pattern (present auditorily)
-  \begin{itemize}
-  \item intonational effects discussed by
-    \citet{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic},
-    \citep[c.f.][]{ChemlaSpector2010:Experimental-Ev}
-  \item mention \citet{SchwarzClifton2008:Strengthening-o} (re-read,
-    check for newer version)
-  \end{itemize}
-\item different languages
-\end{itemize}
+  explain, as far as we can see, the preference for the situation in
+  Figure~\ref{fig:literal-EA} over that in Figure\ref{fig:global-EA}
+  given a sentence like (\ref{bsp:EA}).} and that it also does not
+explain why we observed putative effects of typicality also in
+categorical judgements in our pilot.
+
+To conclude, the confounding effects of pictorial complexity and/or
+typicality are real and affect even categorical judgements. The
+available evidence about availability, preference and nature of local
+readings is therefore still inconclusive. What is needed to complement
+the picture is data from a design that elicits categorical judgements
+that are as independent as possible of possibly conflating properties
+of the pictorial material. Given the logical dependencies of the
+relevant readings of \as- and \es-sentences this seems almost
+impossible to achieve. As we will argue below we do, however, believe
+it is.
+
+On top of this, we would like to obtain more further information about
+the relative preferences among all putative readings, so as to be able
+to decide between theoretical positions, as outlined in
+Section~\ref{sec:theories-predictions}. Neither of the previous
+studies gives us that, either because they simply have not
+investigated all the relevant comparisons
+(\citet{GeurtsPouscoulous2009:Embedded-Implic},
+\citet{CliftonDube2010:Embedded-Implic}), or because they cannot safely
+derive the required cardinal information for danger of conflating
+preferences for readings with preferences for pictures
+(\citet{ChemlaSpector2010:Experimental-Ev}, our pilot study).
+
+Another desideratum for a further empirical testing is that a study
+aimed at revealing information about availability and preferences of
+readings be accompanied by a suitable comparable investigation into a
+phenomenon which is know to allow for several readings with a given
+known preferences structure. This way and only this way can a proper
+baseline be established to guide the interpretation of the observed
+data.
+
+Moreover, a final omission of previous studies is that they did not
+control for possible conflating effects of ``silent intonation''
+(XYZ)\dn{references}. Even traditionalism maintains that local
+readings are attested, but requiring a contrastive stress on the
+scalar item
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}. Variation
+in the interpretation of target sentences therefore could be caused by
+subjects imposing different intonational patterns on the visually
+presented target sentences. Ideally, we should therefore present
+sentences auditorily and address directly the frequently voiced
+hypothesis that local readings are triggered by contrastive
+stress.\dn{relate to \citet{SchwarzClifton2008:Strengthening-o} and
+  others?}
+
+The following section presents a study designed to meet all of these
+desiderata.
 

### 2012-07-07 text/paper/paper.tex
paper motivation section rewrite sec com

@@
 pieces of evidence concerning putative local
-readings. \citeauthor{ChemlaSpector2010:Experimental-Ev}'s results
+readings. \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s results
 suggest that local readings are not available, because they do not
@@
 (\citeauthor{CliftonDube2010:Embedded-Implic}), or by a graded
-truth-value judgment (\citeauthor{ChemlaSpector2010:Experimental-Ev}).
-
-To account for all of these observations, it could be hypothesized
-along with \citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
-available, but so dispreferred that they do not affect simple
-\emph{categorical} truth-value judgements. It could then furthermore
-be argued, in line with traditionalism, that the reason why local
-readings do not affect categorical judgements is because they are not
-(strongly) truth-relevant speaker-intended meaning enrichments after
-all, so that no case can be made for lexicalism or grammaticalism
-\citep[c.f.][for arguments along these lines]{Tielvan-Tiel2012:Embedded-Scalar}.
-
-Either position is cast into doubt by a pilot study of
-ourselves.\dn{We should expand on the method in an appendix} We tried
-to replicate \citeauthor{ChemlaSpector2010:Experimental-Ev}'s results,
-using a simple categorial truth-value judgement task on pictures that
-were exactly like those in Figures \ref{fig:AS-distinguishing-pics}
-and \ref{fig:ES-distinguishing-pics}. Test sentences were German
-cleft-constructions as in (\ref{bsp:AS-K1}) and
-(\ref{bsp:ES-K1}).\fn{We concede that these cleft-constructions might
-  unduly emphasize potential local readings, but that is not
-  essential, because the main issue we are trying to address here is
-  whether putative local readings \emph{could} affect categorical
-  truth-value judgements.}
+truth-value judgment
+(\citeauthor{ChemlaSpector2010:Experimental-Ev}).
+
+The data made available by all of these three studies, if taken in
+conjunction, can be interpreted in several ways. Here are the two most
+obvious candidates that have been suggested in the literature.
+Firstly, conventionalists or grammaticalists could maintain that the
+latter two studies refute traditionalism because they show that local
+readings are available, despite the fact that they do not affect
+simple \mymark{categorical truth-value judgements}. This is
+essentially the interpretation favored by
+\citet{CliftonDube2010:Embedded-Implic}, as well as
+\citet{ChemlaSpector2010:Experimental-Ev}. In contrast,
+traditionalists could rebut this position by arguing that the very
+reason why local readings do not affect categorical judgements is
+because they are not truth-relevant speaker-intended meaning
+enrichments after all. The traditionalist, who would like to argue in
+this way, would then have to provide an alternative explanation for
+the effects attributed to the availability of local readings in the
+latter two studies. One such explanation, at least for the data
+concerning \as-sentences, has recently been suggested by
+\citet{Tielvan-Tiel2012:Embedded-Scalar}, who argues that the effects
+of putative local readings in the latter mentioned studies are due to
+\mymark{typicality effects}.\fn{Yet another possible interpretation
+  could be given by literalism which admits to local readings but
+  considers them dispreffered to literal readings. This position
+  explains the tendentious effects reported in the latter two studies
+  \emph{and} explains why local readings do not show in categorical
+  judgements: literal readings are simply preferred, so that local
+  readings only figure in tendentious choices, but not in categorical
+  ones. We will come back to this position eventually.}
+
+The main point we would like to make in this section is that neither
+interpretation is fully satisfactory because the situation is even
+more complicated than suggested so far. Therefore, further empirical
+testing is required, but should be carefully designed so as to
+circumnavigate, as far as possible, the delicate methodological
+pitfalls the subject matter so unkindly provides.
+
+In outline our position, which we will elaborate on in the following,
+is this. On the one hand, we believe with
+\citet{ChemlaSpector2010:Experimental-Ev} and
+\citet{Tielvan-Tiel2012:Embedded-Scalar} that properties of the
+pictorial material can affect subjects' judgements. We concede,
+following \citet{Tielvan-Tiel2012:Embedded-Scalar}, that a notion of
+typicality may partly be responsible. But we also submit, in line with
+\citet{ChemlaSpector2010:Experimental-Ev}, that typicality might not
+be all of the story. On the other hand, we present suggestive evidence
+based on a pilot study of ourselves (to be addressed presently) that
+even categorical judgements \emph{can} be affected by pictorial
+properties. We conclude that further empirical evidence is needed and
+that a follow-up study should meet the following requirements: (i) it
+should be a categorical truth-value judgement task after all because
+only that way the traditionalist claim that any observed effects are
+not truth-relevant can be suitably addressed\dn{@Fabian: would a
+  reference fit here to the book(?) that discusses why true/false
+  judgements are best?} and (ii) it must make sure to minimize any
+putative effects of the pictorial material as much as possible.
+
+In support of this position, we would like to briefly discuss the
+results of a small pilot study of ourselves.\fn{A word of
+  motivation. We report the results of this pilot mainly for
+  expository reasons. A better argument that categorical judgements
+  can be indicative of local readings is given by our main
+  experiment. But in order to motivate the readers that they should be
+  interested in this experiment, we feel it is helpful to discuss the
+  mildly suggestive, but ultimately inconclusive evidence of this
+  pilot. Additionally, introducing the pilot also serves another
+  purpose, namely the discussion of the results for sentences like
+  (\ref{bsp:EA}). These help introduce in a tangible way how seemingly
+  innocuous properties of the pictorial material can influence
+  subjects' truth-value judgements, and why typicality might not be
+  the whole explanation for these pictorial effects.} Our pilot tried
+to replicate \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s
+results, using a simple categorical truth-value judgement task on
+pictures that were exactly like those in Figures
+\ref{fig:AS-distinguishing-pics} and
+\ref{fig:ES-distinguishing-pics}.\dn{We should expand on the method in
+  an appendix} Test sentences were German cleft-constructions as in
+(\ref{bsp:AS-K1}) and (\ref{bsp:ES-K1}).\fn{We concede that these
+  cleft-constructions might unduly emphasize potential local readings,
+  perhaps because they induces a quotative reading. (We are grateful
+  to Philippe Schlenker for raising this latter possibility.) But that
+  is not essential, because the main issue we are trying to address
+  here is whether putative local readings \emph{could} affect
+  categorical truth-value judgements.}
 \begin{exe}
@@
 \begin{center}
-  \begin{tabular}{ccccccccc}
-    \multicolumn{4}{c}{\as-sentences} &&
-    \multicolumn{4}{c}{\es-sentences}     \\ \cmidrule(r){1-4} \cmidrule(r){6-9}
-    false & literal & weak & strong && false & local & literal & all
+  \begin{tabular}{cccc}
+    \multicolumn{4}{c}{\as-sentences}     \\ \cmidrule(r){1-4}
+    false & literal & weak & strong 
     \\ \midrule 
-    .9 & 72 & 79 & 90 && .8 & 20 & 71 & 93 
+    .9 & 72 & 79 & 90 
+  \end{tabular}
+  \qquad
+  \begin{tabular}{cccc}
+    \multicolumn{4}{c}{\es-sentences}    \\ \cmidrule(r){1-4} 
+    false & local & literal & all
+    \\ \midrule 
+    .8 & 20 & 71 & 93 
   \end{tabular}
 \end{center}
+% \begin{center}
+%   \begin{tabular}{ccccccccc}
+%     \multicolumn{4}{c}{\as-sentences} &&
+%     \multicolumn{4}{c}{\es-sentences}     \\ \cmidrule(r){1-4} \cmidrule(r){6-9}
+%     false & literal & weak & strong && false & local & literal & all
+%     \\ \midrule 
+%     .9 & 72 & 79 & 90 && .8 & 20 & 71 & 93 
+%   \end{tabular}
+% \end{center}
 Two observations are of interest here. Firstly, we observed 21\%
@@
 one had, and the \es-false and the \es-local condition, on the other
-hand, both reached significance.\dn{spell out in appendix}
+hand, both reached significance.\dn{spell out in appendix} This
+suggests that local readings \emph{are} available and \emph{can} have
+an effect even on categorical truth-value judgements.
 
@@
 
-These observed patterns suggest that local readings \emph{are}
-available and \emph{can} have an effect even on categorical
-truth-value judgements. However, this interpretation of the data is
-problematic for reasons already addressed also by
+However, the interpretation of data from judgement tasks is generally
+problematic for reasons already addressed by
 \citet{ChemlaSpector2010:Experimental-Ev} and, more recently,
@@
       \end{tikzpicture}
-
 }
@@
 %
-Our pilot study revealed a difference in acceptability,
-but a curious one. The sentence was judged \emph{true} in 90.3\% of
-the cases for the situation in Figure~\ref{fig:global-EA} and in
-98.3\% in situation \ref{fig:literal-EA}. The observed difference is
-significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$). This is a
-curious finding, because, from the point of view of implicature
-calculation, the only thing that could plausibly explain this
-acceptability difference is the presence of a global implicature,
-resulting from the negation of the corresponding
-\es-sentence.\fn{Notice that (\ref{bsp:EA}) is the alternative to the
-  corresponding \es-sentence needed for computing the putative global
-  implicature. But these sentences are logically independent. So, it
-  may be that the corresponding \es-sentence is an alternative also to
-  sentences like (\ref{bsp:EA}). It may also be that being an
-  alternative is not a symmetric notion. Be that as it may, our
-  argument does not hinge on whether (\ref{bsp:EA}) does or does not
-  actually have a global implicature of the alleged kind.} But such a
-putative global implicature would be true in the
-situation~\ref{fig:global-EA}, but false in the
-situation~\ref{fig:literal-EA}. Consequently, the observed difference
-in acceptability cannot be explained simply in terms of the hypothesis
-of \citet{ChemlaSpector2010:Experimental-Ev} that acceptability is
-proportional to the number of available true readings. Rather some
-feature of the pictorial material that is independent of the putative
-readings under scrutiny does affect truth-value judgements, even
-categorical ones.
+Our pilot study revealed a difference in acceptability, but a curious
+one. The sentence was judged \emph{true} in 90.3\% of the cases for
+the situation in Figure~\ref{fig:global-EA} and in 98.3\% in situation
+\ref{fig:literal-EA}. The observed difference is significant ($t =
+-3.8259$, $df = 322.375$, $p < 0.001$). This is a curious finding,
+because, from the point of view of implicature calculation, the only
+thing that could plausibly explain this acceptability difference is
+the presence of a global implicature, resulting from the negation of
+the corresponding \es-sentence.\fn{Notice that (\ref{bsp:EA}) is the
+  alternative to the corresponding \es-sentence needed for computing
+  the putative global implicature of that \es-sentence. But since
+  these sentences are logically independent, it may be assumed that
+  the corresponding \es-sentence is an alternative also to sentences
+  like (\ref{bsp:EA}). It may also be that \emph{being-an-alternative}
+  is not a symmetric notion. Be that as it may, our argument does not
+  hinge on whether (\ref{bsp:EA}) does or does not actually have a
+  global implicature of the alleged kind.} But such a putative global
+implicature would be true in the situation~\ref{fig:global-EA}, but
+false in the situation~\ref{fig:literal-EA}. Consequently, the
+observed difference in acceptability cannot be explained simply in
+terms of the hypothesis of \citet{ChemlaSpector2010:Experimental-Ev}
+that acceptability is proportional to the number of available true
+readings. Rather some feature of the pictorial material that is
+independent of the putative readings under scrutiny does affect
+truth-value judgements, even categorical ones.
 
@@
   explain, as far as we can see, the preference for the situation in
-  Figure~\ref{fig:literal-EA} over that in Figure\ref{fig:global-EA}
+  Figure~\ref{fig:literal-EA} over that in Figure~\ref{fig:global-EA}
   given a sentence like (\ref{bsp:EA}).} and that it also does not
 explain why we observed putative effects of typicality also in
-categorical judgements in our pilot.
+categorical truth-value judgements in our pilot.
 
 To conclude, the confounding effects of pictorial complexity and/or
-typicality are real and affect even categorical judgements. The
-available evidence about availability, preference and nature of local
-readings is therefore still inconclusive. What is needed to complement
-the picture is data from a design that elicits categorical judgements
-that are as independent as possible of possibly conflating properties
-of the pictorial material. Given the logical dependencies of the
-relevant readings of \as- and \es-sentences this seems almost
-impossible to achieve. As we will argue below we do, however, believe
-it is.
-
-On top of this, we would like to obtain more further information about
+typicality are real and affect even categorical truth-value
+judgements. The available evidence about availability, preference and
+nature of local readings is therefore still inconclusive. What is
+needed to complement the picture is data from a design that elicits
+categorical truth-value judgements that are as independent as possible
+of possibly conflating properties of the pictorial material. Given the
+logical dependencies of the relevant readings of \as- and
+\es-sentences this seems almost impossible to achieve. As we will
+argue below we do, however, believe it is.
+
+On top of this, we would like to obtain further information about
 the relative preferences among all putative readings, so as to be able

### 2012-07-07 text/paper/paper.tex
paper motivation section rewrite

@@
 
-On top of this, we would like to obtain further information about
-the relative preferences among all putative readings, so as to be able
-to decide between theoretical positions, as outlined in
+On top of this, we would like to obtain further information about the
+relative preferences among all putative readings, so as to be able to
+decide between theoretical positions, as outlined in
 Section~\ref{sec:theories-predictions}. Neither of the previous
@@
 (\citet{GeurtsPouscoulous2009:Embedded-Implic},
-\citet{CliftonDube2010:Embedded-Implic}), or because they cannot safely
-derive the required cardinal information for danger of conflating
-preferences for readings with preferences for pictures
+\citet{CliftonDube2010:Embedded-Implic}), or because they run risk of
+conflating preferences for readings with preferences for pictures
 (\citet{ChemlaSpector2010:Experimental-Ev}, our pilot study).
 
-Another desideratum for a further empirical testing is that a study
-aimed at revealing information about availability and preferences of
-readings be accompanied by a suitable comparable investigation into a
-phenomenon which is know to allow for several readings with a given
-known preferences structure. This way and only this way can a proper
-baseline be established to guide the interpretation of the observed
-data.
-
-Moreover, a final omission of previous studies is that they did not
+% Another desideratum for a further empirical testing is that a study
+% aimed at revealing information about availability and preferences of
+% readings be accompanied by a suitable comparable investigation into a
+% phenomenon which is know to allow for several readings with a given
+% known preferences structure. This way and only this way can a proper
+% baseline be established to guide the interpretation of the observed
+% data.
+
+Another potential shortcoming of previous studies is that they did not
 control for possible conflating effects of ``silent intonation''
@@
 effects.
+\item Strictly speaking, directly comparing the results of all
+  relevant empirical studies is not feasible for a number of
+  reasons. Firstly, all of the previous studies were conducted in
+  different languages. \citet{GeurtsPouscoulous2009:Embedded-Implic}
+  tested Dutch material, \citet{CliftonDube2010:Embedded-Implic}
+  English, \citet{ChemlaSpector2010:Experimental-Ev} French, and we
+  tested German material. Although quantity implicatures are usually
+  considered a universal phenomenon, derived from general principles
+  of efficient language use and/or organization, it might nonetheless
+  be that different languages show slightly different patterns of
+  data, because there might be relevant differences in the set of
+  available quantifiers.\dn{spell out?} Secondly, we must be careful
+  to compare studies directly, because of methodological concerns. For
+  instance, not only the pictorial material might influence judgement
+  patterns, also the filler material might. If the fillers used are
+  all very clear to elicit a \emph{true}- or \emph{false}-judgement,
+  then subtle meaning differences in the target conditions might more
+  easily be smothered. On the other hand, if the filler material is
+  also subtly ambiguous, potential meaning differences in the target
+  material could be accented. In other words, it might be that the
+  filler material, as it were, could influence the \mymark{standard of
+    precision} for applicability of the predicates \emph{true} and
+  \emph{false}. (Indeed, we believe that, when it comes to subjects'
+  responses in psycholinguistic experiments, \emph{truth-of-a-sentence} is a
+  vague notion.\dn{reference!})
 \end{itemize}

### 2012-07-20 text/paper/paper.tex

@@
 
-Summing up so far, three previous studies have presented different
-pieces of evidence concerning putative local
-readings. \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s results
-suggest that local readings are not available, because they do not
-affect a categorical truth-value judgments in a picture-verification
-task. On the other hand,
-\citeauthor{CliftonDube2010:Embedded-Implic}'s and
-\citeauthor{ChemlaSpector2010:Experimental-Ev}'s design was suggested
-to be sensitive enough to reveal effects of local readings: either by
-a choice of the situation that better befits a given sentence
-(\citeauthor{CliftonDube2010:Embedded-Implic}), or by a graded
-truth-value judgment
-(\citeauthor{ChemlaSpector2010:Experimental-Ev}).
-
-The data made available by all of these three studies, if taken in
-conjunction, can be interpreted in several ways. Here are the two most
-obvious candidates that have been suggested in the literature.
-Firstly, conventionalists or grammaticalists could maintain that the
-latter two studies refute traditionalism because they show that local
-readings are available, despite the fact that they do not affect
-simple \mymark{categorical truth-value judgements}. This is
-essentially the interpretation favored by
-\citet{CliftonDube2010:Embedded-Implic}, as well as
-\citet{ChemlaSpector2010:Experimental-Ev}. In contrast,
-traditionalists could rebut this position by arguing that the very
-reason why local readings do not affect categorical judgements is
-because they are not truth-relevant speaker-intended meaning
-enrichments after all. The traditionalist, who would like to argue in
-this way, would then have to provide an alternative explanation for
-the effects attributed to the availability of local readings in the
-latter two studies. One such explanation, at least for the data
-concerning \as-sentences, has recently been suggested by
-\citet{Tielvan-Tiel2012:Embedded-Scalar}, who argues that the effects
-of putative local readings in the latter mentioned studies are due to
-\mymark{typicality effects}.\fn{Yet another possible interpretation
-  could be given by literalism which admits to local readings but
-  considers them dispreffered to literal readings. This position
-  explains the tendentious effects reported in the latter two studies
-  \emph{and} explains why local readings do not show in categorical
-  judgements: literal readings are simply preferred, so that local
-  readings only figure in tendentious choices, but not in categorical
-  ones. We will come back to this position eventually.}
+Summing up so far, three previous studies have presented diverging
+pieces of evidence concerning the status of putative local
+readings. \citet{GeurtsPouscoulous2009:Embedded-Implic} did not observe any truth value judgments that would indicate
+local readings. On the basis of this finding they argue that these readings are simply not available. On the other
+hand, C\&D and C\&S argue that the findings of G\&P may be due to a bias in their experimental design and
+employed different methods intended to be sensitive enough to reveal effects of local readings: either by
+a choice of the situation that better befits a given sentence (\citeauthor{CliftonDube2010:Embedded-Implic}), or by a graded
+truth-value judgment (\citeauthor{ChemlaSpector2010:Experimental-Ev}). Both studies found evidence in support of local readings.
+
+To account for all of these observations, it could be hypothesized
+along with \citeauthor{CliftonDube2010:Embedded-Implic} and
+\citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
+available, but so dispreferred that they do not affect
+\emph{categorical} truth-value judgements (See, however, \citet{Crain1998} for arguments in favour of truth value judgments
+as a means of detecting highly dispreferred readings).
+It could then furthermore be argued, in line with traditionalism, that the reason why local
+readings do not affect categorical judgements is because they are not
+(strongly) truth-relevant speaker-intended meaning enrichments after
+all, so that no case can be made for lexicalism or grammaticalism
+\citep[c.f.][for arguments along these lines]{Tielvan-Tiel2012:Embedded-Scalar}.
 
@@
 
-However, the interpretation of data from judgement tasks is generally
-problematic for reasons already addressed by
-\citet{ChemlaSpector2010:Experimental-Ev} and, more recently,
-\citet{Tielvan-Tiel2012:Embedded-Scalar}. The problem is that the
-present variants of truth-value judgment tasks all run risk of
-conflating evidence about the availability or preference of readings
-with properties of the pictorial material that are independent of the
-reading to be assessed. This problem affects all of the studies
-covered above, to some degree or other, because it follows almost
-directly from the nature of the phenomenon under investigation and
-therefore seems nearly impossible to avoid.
+These observed patterns suggest that local readings \emph{are}
+available and \emph{can} have an effect even on categorical
+truth-value judgements.
 

### 2012-07-20 text/paper/paper1.tex

--- 2012-07-07 text/paper/paper.tex
@@
 \newcommand{\GE}{\es}
+\newcommand{\ea}{\acro{ea}}
 
@@
 
-\svnInfo $Id$
+\svnInfo $Id: paper.tex 102 2012-07-04 10:19:59Z michael.franke $
 
@@
 
-Summing up so far, three previous studies have presented different
-pieces of evidence concerning putative local
-readings. \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s results
-suggest that local readings are not available, because they do not
-affect a categorical truth-value judgments in a picture-verification
-task. On the other hand,
-\citeauthor{CliftonDube2010:Embedded-Implic}'s and
-\citeauthor{ChemlaSpector2010:Experimental-Ev}'s design was suggested
-to be sensitive enough to reveal effects of local readings: either by
-a choice of the situation that better befits a given sentence
-(\citeauthor{CliftonDube2010:Embedded-Implic}), or by a graded
-truth-value judgment
-(\citeauthor{ChemlaSpector2010:Experimental-Ev}).
-
-The data made available by all of these three studies, if taken in
-conjunction, can be interpreted in several ways. Here are the two most
-obvious candidates that have been suggested in the literature.
-Firstly, conventionalists or grammaticalists could maintain that the
-latter two studies refute traditionalism because they show that local
-readings are available, despite the fact that they do not affect
-simple \mymark{categorical truth-value judgements}. This is
-essentially the interpretation favored by
-\citet{CliftonDube2010:Embedded-Implic}, as well as
-\citet{ChemlaSpector2010:Experimental-Ev}. In contrast,
-traditionalists could rebut this position by arguing that the very
-reason why local readings do not affect categorical judgements is
-because they are not truth-relevant speaker-intended meaning
-enrichments after all. The traditionalist, who would like to argue in
-this way, would then have to provide an alternative explanation for
-the effects attributed to the availability of local readings in the
-latter two studies. One such explanation, at least for the data
-concerning \as-sentences, has recently been suggested by
-\citet{Tielvan-Tiel2012:Embedded-Scalar}, who argues that the effects
-of putative local readings in the latter mentioned studies are due to
-\mymark{typicality effects}.\fn{Yet another possible interpretation
-  could be given by literalism which admits to local readings but
-  considers them dispreffered to literal readings. This position
-  explains the tendentious effects reported in the latter two studies
-  \emph{and} explains why local readings do not show in categorical
-  judgements: literal readings are simply preferred, so that local
-  readings only figure in tendentious choices, but not in categorical
-  ones. We will come back to this position eventually.}
-
-The main point we would like to make in this section is that neither
-interpretation is fully satisfactory because the situation is even
-more complicated than suggested so far. Therefore, further empirical
-testing is required, but should be carefully designed so as to
-circumnavigate, as far as possible, the delicate methodological
-pitfalls the subject matter so unkindly provides.
-
-In outline our position, which we will elaborate on in the following,
-is this. On the one hand, we believe with
-\citet{ChemlaSpector2010:Experimental-Ev} and
-\citet{Tielvan-Tiel2012:Embedded-Scalar} that properties of the
-pictorial material can affect subjects' judgements. We concede,
-following \citet{Tielvan-Tiel2012:Embedded-Scalar}, that a notion of
-typicality may partly be responsible. But we also submit, in line with
-\citet{ChemlaSpector2010:Experimental-Ev}, that typicality might not
-be all of the story. On the other hand, we present suggestive evidence
-based on a pilot study of ourselves (to be addressed presently) that
-even categorical judgements \emph{can} be affected by pictorial
-properties. We conclude that further empirical evidence is needed and
-that a follow-up study should meet the following requirements: (i) it
-should be a categorical truth-value judgement task after all because
-only that way the traditionalist claim that any observed effects are
-not truth-relevant can be suitably addressed\dn{@Fabian: would a
-  reference fit here to the book(?) that discusses why true/false
-  judgements are best?} and (ii) it must make sure to minimize any
-putative effects of the pictorial material as much as possible.
-
-In support of this position, we would like to briefly discuss the
-results of a small pilot study of ourselves.\fn{A word of
-  motivation. We report the results of this pilot mainly for
-  expository reasons. A better argument that categorical judgements
-  can be indicative of local readings is given by our main
-  experiment. But in order to motivate the readers that they should be
-  interested in this experiment, we feel it is helpful to discuss the
-  mildly suggestive, but ultimately inconclusive evidence of this
-  pilot. Additionally, introducing the pilot also serves another
-  purpose, namely the discussion of the results for sentences like
-  (\ref{bsp:EA}). These help introduce in a tangible way how seemingly
-  innocuous properties of the pictorial material can influence
-  subjects' truth-value judgements, and why typicality might not be
-  the whole explanation for these pictorial effects.} Our pilot tried
-to replicate \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s
-results, using a simple categorical truth-value judgement task on
-pictures that were exactly like those in Figures
-\ref{fig:AS-distinguishing-pics} and
-\ref{fig:ES-distinguishing-pics}.\dn{We should expand on the method in
-  an appendix} Test sentences were German cleft-constructions as in
-(\ref{bsp:AS-K1}) and (\ref{bsp:ES-K1}).\fn{We concede that these
-  cleft-constructions might unduly emphasize potential local readings,
-  perhaps because they induces a quotative reading. (We are grateful
-  to Philippe Schlenker for raising this latter possibility.) But that
-  is not essential, because the main issue we are trying to address
-  here is whether putative local readings \emph{could} affect
-  categorical truth-value judgements.}
+Summing up so far, three previous studies have presented diverging
+pieces of evidence concerning the status of putative local
+readings. In their picture verification experiment, \citet{GeurtsPouscoulous2009:Embedded-Implic} did not observe any truth value judgments that would indicate
+local readings. On the basis of this finding they argue that these readings are simply not available. On the other
+hand,  \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} argue that the findings of  \citeauthor{GeurtsPouscoulous2009:Embedded-Implic} may be due to a bias in their experimental design and
+employed different methods intended to be sensitive enough to reveal effects of local readings: either by
+a choice of the situation that better befits a given sentence (\citeauthor{CliftonDube2010:Embedded-Implic}), or by a graded
+truth-value judgment (\citeauthor{ChemlaSpector2010:Experimental-Ev}). Both studies found evidence in support of local readings.
+To account for the diverging results we could draw a distinction between \emph{categorical} truth-value
+judgments and other more sensitive measures. Firstly, it could be hypothesized
+along with \citeauthor{CliftonDube2010:Embedded-Implic} and
+\citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
+available, but so dispreferred that they do not affect
+\emph{categorical} truth-value judgements (See, however, \citet{Crain1998} for arguments in favour of truth value judgments
+as a means of detecting highly dispreferred readings).
+Secondly it could also be argued, in line with traditionalism, that the apparent difference in
+sensitivity of the different judgment types can be explained by the stipulation that
+the results reported by \citeauthor{CliftonDube2010:Embedded-Implic}
+and \citeauthor{ChemlaSpector2010:Experimental-Ev} reflect something other than
+(strongly) truth-relevant speaker-intended meaning enrichments after all, so that no case
+can be made for lexicalism or grammaticalism on the basis of these data \citep[c.f.][for arguments along these lines]{Tielvan-Tiel2012:Embedded-Scalar}.
+
+Note, however, that the type of judgment  is not the only crucial difference between the methods of \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} on the one hand and  \citet{GeurtsPouscoulous2009:Embedded-Implic} on the other.
+For example these studies  also differed with respect to the types of situations that were shown to the participants during the course of the experiment.
+The presence or absence of competing situations may have led to skewed distributions of judgments for situations like in Figure \ref{fig:weak}.
+Such effects might emerge simply because the type of sentence-picture combinations shown during the experiment affects the standard of judgment but could~-- maybe more elegantly~-- also be explained by findings from \citet{Raffray2010} suggesting that exposing participants to models may prime corresponding logical forms and thereby shift reading preferences.
+Taking these possibilities into account, it remains unclear whether the effects reported by  \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} would also show up using ordinary picture verification, in the first place.
+
+Be this as it may, we cannot ascribe the effects reported by  \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} to the availability of local readings with certainty.
+\citet{ChemlaSpector2010:Experimental-Ev} themeselves acknowledge
+the possibility that the \emph{typicality} of a picture with respect to some meaning may affect graded truth-value
+judgements. Strengthening this possibility, they show that graded judgments of
+\as-sentences differ significantly for different instantiations of the
+conditions in \ref{fig:AS-distinguishing-pics}, that vary in the
+amount of connections without changing the assignment of truth values
+to candidate readings. \citeauthor{ChemlaSpector2010:Experimental-Ev}
+suggest that typicality of the pictorial material can account for
+these differences, but submit that this does not explain away the
+high acceptance of pictures like Figure \ref{fig:weak}. The latter point is disputed by
+\citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates that a huge chunk of variance in the data of
+\citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} on
+\as-sentences can be explained as typicality effects, dispensing the need to appeal
+to the distribution of different readings. \citet{Tielvan-Tiel2012:Embedded-Scalar} elicited what he calls the typicality
+structures associated with the quantifiers {\it all} and {\it some} and predicted the judgments of \as-sentences obtained by C\&S based
+on these data. Thereby, he obtained an excelent model fit. We are sympathetic towards
+\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
+reinterpretation of the data, but note, as
+\citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
+typicality-based explanation does not extend to \es-sentences in an
+obvious way\fn{For similar reasons, appeal to typicality cannot
+  explain, as far as we can see, the preference for the situation in
+  Figure~\ref{fig:literal-EA} over that in Figure\ref{fig:global-EA}
+  given a sentence like (\ref{bsp:EA}).}.
+
+To conclude, although considerable progress has been made in understanding which factors
+have to be controlled for in order to asses the status of loacl readings, the evidence about availability,
+preference and nature of local readings is still inconclusive. What is needed to complement
+the picture are data that are sensitive enough to detect local readings even if they
+are strongly dispreferred and are as independent as possible of possibly conflating properties
+of the pictorial material. Given the logical dependencies of the
+relevant readings of \as- and \es-sentences this seems almost
+impossible to achieve. As we will argue below we do, however, believe it is.
+
+On top of this, it would be desirable to obtain further information about
+the relative preferences among all putative readings, so as to be able
+to decide between theoretical positions, as outlined in
+Section~\ref{sec:theories-predictions}. Neither of the previous
+studies gives us that, either because they simply have not
+investigated all the relevant comparisons
+(\citet{GeurtsPouscoulous2009:Embedded-Implic},
+\citet{CliftonDube2010:Embedded-Implic}), or because they cannot safely
+derive the required cardinal information for danger of conflating
+preferences for readings with preferences for pictures
+(\citet{ChemlaSpector2010:Experimental-Ev}, our pilot study).
+
+Moreover, a final omission of previous studies is that they did not
+control for possible conflating effects of ``silent intonation''
+(XYZ)\dn{references}. Even traditionalism maintains that local
+readings are attested, but requiring a contrastive stress on the
+scalar item
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}. Variation
+in the interpretation of target sentences therefore could be caused by
+subjects imposing different intonational patterns on the visually
+presented target sentences. Ideally, we should therefore present
+sentences auditorily and address directly the frequently voiced
+hypothesis that local readings are triggered by contrastive
+stress.\dn{relate to \citet{SchwarzClifton2008:Strengthening-o} and
+  others?}
+
+\section{Pilot Study}
+To start off, we conducted  a pilot study  investigating whether the diverging evidence reviewed above can be explained by considerations on how sensitive the different kinds of measures are.
+This information was critical to our main experiment below.
+Because the main experiment employed categorial truth-value judgments out of methodological necessity, we wanted to test the sensitivity of this measure independently.
+In addition, the question is interesting in its own right since it has implications about the nature of the ambiguity at hand, namely whether it is due to truth-relevant meaning enrichment.
+
+In particular, we tested whether the critical effects \citet{ChemlaSpector2010:Experimental-Ev} found in their graded truth-value judgment task do also show up in a categorial truth value judgment task.
+In order to test this we simply replicated \citeauthor{ChemlaSpector2010:Experimental-Ev}'s experiment
+using a categorial truth-value judgment task.
+If, as has been suggested, categorial truth-value judgments are not sensitive enough to detect a difference of acceptance between situations like \ref{fig:weak} and \ref{fig:strong} given \as-sentences or between \ref{fig:local} and \ref{fig:all} given \es-sentences, these should be judged identical in a truth value judgment task.
+
+In addition to the conditions from  \citet{ChemlaSpector2010:Experimental-Ev} we also included another type of sentence.
+This type of sentence, \ea-sentences, contained the scalar item {\it all} embedded under {\it exactly one}.
+Here, a rather atypical kind of global implicature would be arrived at by replacing {\it all} with its weaker alternative {\it some}.
+We tested whether this kind of implicature is detectable using a truth-value judgment task.
+In the discussion of the present experiment we will, however, mainly focus on the replication of  \citet{ChemlaSpector2010:Experimental-Ev}.
+
+\subsection{Materials}
+Test sentences were German cleft-constructions as in (\ref{bsp:AS-K1})$-$(\ref{bsp:EA-K1}).
+Sentences like (\ref{bsp:AS-K1}) are \as-sentences, (\ref{bsp:ES-K1}) are \es- and  (\ref{bsp:EA-K1}) \ea-sentences.
+We decided to use cleft constructions in order to fix the relative scope of the quantifiers involved.
+This was ensured via clause-boundedness.
+In total, 48 experimental items were constructed in all three conditions yielding a total of 144 sentences.
+
 \begin{exe}
@@
   For exactly one of these children it holds that it likes some of these dishes.
+\ex \gll F{\"u}r \mymark{genau eines} dieser Kinder gilt: es mochte \mymark{jede} dieser Speisen.  \label{bsp:EA-K1}\\
+For exactly\ one of\ these children it\ holds: it likes some of\ these dishes.\\
+Exactly one of\ these children it holds that it likes some of\ these dishes.\\
 \end{exe}
-Mean acceptance rates of 60 native German speakers for our target
-sentences were:
+
+The sentences were paired with pictures like in Figures \ref{fig:AS-distinguishing-pics}, \ref{fig:ES-distinguishing-pics}, \label{fig:EA}.
+For \es- and \as-sentences  there were four types of situations just as in  the study of \citet{ChemlaSpector2010:Experimental-Ev}.
+Sentences in the \as-condition were paired with situations as in \ref{fig:literal-AE}, \ref{fig:false-AE}, \ref{fig:weak}, \ref{fig:strong}.
+Sentences in in the \es-condition were paired with \ref{fig:literal-GE},\ref{fig:literal-GE},\ref{fig:local} and \ref{fig:all}.
+The \ea-sentences were paired with pictures like in \ref{fig:EA}.
+Figure \ref{fig:EA-LIT} is only true under the literal reading ({\it literal} diagrams) while  Figure \ref{fig:EA-LITGLB} is also true with respect to the global implicature ({\it global} diagrams) denying the weaker scalar alternative containig {\it einige} (some).
+Diagrams like those in Figures \ref{fig:EA-FALSE1} and \ref{fig:EA-FALSE2} were not compatible with the \ea-sentences.
+Figure \ref{fig:EA-FALSE1} is incompatible because there are too few connections.
+Figure \ref{fig:EA-FALSE2} is incompatible because there are too many connections.
+We used two types of incompatible pictures only because of thechnical reasons.
+
+In total, this yielded twelve conditions and 576 pictures.
+The conditions were distributed over twelve lists according to a latin square design ensuring that in each list every item was only present in one condition.
+In addition, to the target sentences, 201 (?) distractors were included in each list.
+Of these $n$ were intended to yield a "yes true" response, $m$ were false.
+
+\begin{figure}[t]
+  \centering
+
+\begin{minipage}{6cm}
+     \subfloat[][literal]{
+    \label{fig:EA-LIT}
+        \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer09.eps}
+  }
+
+  \subfloat[test][global]{
+    \label{fig:EA-LITGLB}
+    \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer10.eps}
+  }  
+   \end{minipage}
+   \begin{minipage}{6cm}
+     \subfloat[][false1]{
+    \label{fig:EA-FALSE1}
+        \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer11.eps}
+  }
+
+  \subfloat[test][false2]{
+    \label{fig:EA-FALSE2}
+    \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer12.eps}
+  }  
+   \end{minipage}
+        \caption{}
+\label{fig:EA}
+\end{figure}
+
+\subsection{Procedure}
+The present pilot study was conducted as part of a dual task experiment employing picture verification and a sternberg task \cite{Sternberg1966}.
+In some trials participants had to solve a memory task in addition to the picture verification task.
+In the {\it high load} condition participants had to remember six letters while performing the picture verification.
+In the {\it low load} condition they had to remember one letter and in the {\it no load} condition they didn't have to remember anything while they were performing the picture verification.
+In the {\it memory only} conditions they only had to perform a memory task (i.e.
+remember one or six letters) but no picture verification.
+All the critical items of the present experiment were presented in the {\it no load} condition.
+Only distractor items were presented in one of the dual task conditions.
+
+In each trial participants were first asked to indicate readiness by pressing a button.
+In the {\it no load} condition, after they had pressed the button an  asterisk was flashed on the screen six times within $7.2s$.
+Then a sentence and a picture were presented simultaneously.
+Within $12s$ participants had to judge whether the sentence was true with respect to the picture.
+They indicated their judgment by pressing one of two buttons.
+After they had provided their judgment the next trial started automatically.
+If they did not respond within twelve seconds, the next trial was started.
+Judgments and reaction times were logged.\footnote{In the {\it low load} and {\it high load} condition a trial looked similar to a trial in the {\it no load} condition except for two things.
+Firstly, in the dual task conditions instead of asterisks letters were flashed on the screen.
+Secondly, after finishing the picture verification task a question appeared on the screen probing for a letter.
+Participants had to indicate by pressing a button whether they thought the letter had been present in the array from the beginning of the trial.
+Except for one difference, the {\it memory only} trials were identical to the dual task trials.
+In {\it memory only} trials the picture verification part was replaced with a blank screen.
+That is, in the middle of such trials the screen stayed blank for $5s$.
+}
+
+The experiment started with a practise session consisting of $25$ trials devided into three blocks (1st block: memory task only, ten trials; 2nd block: picture verification only, five trials; 3rd block: dual task, ten trials).
+Then one list consisting of 249 trials devided into three blocks was presented.
+An experimental session took about 75 minutes.
+During the whole experiment no feedback was provided to the participants.
+
+\subsection{Participants}
+60 native German speakers (40 female, mean age: $24$, ranging between $20$ and $40$) from the University of T{\"u}bingen participated in the study.
+Participants were na\"ive to the purpose of the study.
+They were paid \euro{10} compensation.
+
+\subsection{Results}
+Overall participants were able to solve the task.
+In the distractor items the picture verification was done accurately in $88\%$ ($sd: 33\%$) of the cases.
+All participants were above $70\%$ and significantly better than chance.
+On average it took participants $4989ms$ ($sd:2176ms$) to come up with their answer in the filler trials.
+We will now consider results for the three sentence conditions in turn.
+
+The mean judgments we obtained for \as-sentences are depicted in Figure \ref{fig:AEBars}.
+The {\it strong} diagrams were judged to be true in $90\%$ of the cases, {\it weak} diagrams received "yes" judgments in $79\%$ , {\it literal} diagrams in  $72\%$  and {\it false} in $0.9\%$ of the trials.
+A logit mixed effects model with binomial link function containing a fixed effect of {\it diagram} as well as random effects of items and participants revealed a clear effect of {\it diagram}.
+In particular {\it false}, {\it literal} and {\it weak} diagrams all received fewer "yes" judgments than {\it strong} diargams (all $p<.001$).
+Another logit mixed effects model only modelling data for {\it literal} and {\it weak} diagrams also revealed an reliable effect of {\it diagram} (p<.05).
+Finally, a model only considering  {\it false} and {\it literal} diagrams also revealed a significant effect of {\it diagram} (p<.001).
+
+\begin{figure}[t]
+  \centering
+
+     \subfloat[][\as]{
+    \label{fig:AEBars}
+        \includegraphics[width=5cm]{../pictures/JudgmentsAllSomeBars.eps}
+  }
+  \subfloat[test][\es]{
+    \label{fig:GEBars}
+    \includegraphics[width=5cm]{../pictures/JudgmentsExactlySomeBars.eps}
+  }
+
+        \caption{Mean judgments}
+\label{fig:BarsPilot}
+\label{fig:EA}
+\end{figure}
+
+The responses for \es-sentences are summarized in Figure \ref{fig:GEBars}.
+Unsurprisingly, these sentences were accepted as truthfull description of {\it false} diagrams in only $0.8\%$ of all cases.
+The {\it local} diagrams received  "yes" responses in $20\%$, {\it literal} in $71\%$ and {\it all} in $93\%$ of the time.
+A logit mixed effects model with {\it diagram} as fixed effect as well as item and participant as random effects revealed a signficant effect of {\it diagram}.
+The {\it all}, {\it literal} and {\it local} diagrams were all accepted more often than the {\it false} diagram (all $p<.001$).
+A simpler model only considering {\it local} and {\it literal} diagrams revealed a reliable effect of {\it diagram} (p<.001) as did a model only considering {\it literal} and {\it all} diagrams (p<.001).
+
+The mean responses for the \ea-sentences are shown in table \ref{}. The observed difference between the global and literal diagrams is
+significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$).
+
 \begin{center}
   \begin{tabular}{cccc}
-    \multicolumn{4}{c}{\as-sentences}     \\ \cmidrule(r){1-4}
-    false & literal & weak & strong 
+    \multicolumn{4}{c}{\as-sentences}  \\
+    \hline
+    literal & global & false1 & false2
     \\ \midrule 
-    .9 & 72 & 79 & 90 
-  \end{tabular}
-  \qquad
-  \begin{tabular}{cccc}
-    \multicolumn{4}{c}{\es-sentences}    \\ \cmidrule(r){1-4} 
-    false & local & literal & all
-    \\ \midrule 
-    .8 & 20 & 71 & 93 
+    98.3 & 90.3 & 7.1 & 3.3 
   \end{tabular}
 \end{center}
-% \begin{center}
-%   \begin{tabular}{ccccccccc}
-%     \multicolumn{4}{c}{\as-sentences} &&
-%     \multicolumn{4}{c}{\es-sentences}     \\ \cmidrule(r){1-4} \cmidrule(r){6-9}
-%     false & literal & weak & strong && false & local & literal & all
-%     \\ \midrule 
-%     .9 & 72 & 79 & 90 && .8 & 20 & 71 & 93 
-%   \end{tabular}
-% \end{center}
-Two observations are of interest here. Firstly, we observed 21\%
-\emph{false}-judgements in the \as-weak condition, as well as 20\%
-\emph{true}-judgements in the \es-local condition, contrary to the 0\%
-in each case observed by
-\citet{GeurtsPouscoulous2009:Embedded-Implic}. Secondly, the observed
-difference between the \as-weak and the \as-strong conditions, on the
-one had, and the \es-false and the \es-local condition, on the other
-hand, both reached significance.\dn{spell out in appendix} This
-suggests that local readings \emph{are} available and \emph{can} have
-an effect even on categorical truth-value judgements.
-
-% \begin{figure}[]
-% \centering
-% \subfloat[\as-sentences]{
-% \includegraphics[width=5.5cm]{../pictures/paper/JudgmentsAllSomeBars.pdf}
-% \label{fig:EABars}
-% }
-% \subfloat[\es-sentences]{
-% \includegraphics[width=5cm]{../pictures/paper/JudgmentsExactlySomeBars.pdf}
-% \label{fig:EEBars}
-% }
-% \caption{Means of \emph{true}-judgments in our pilot study}
-% \label{fig:Bars-K1}
-% \end{figure}
-
-However, the interpretation of data from judgement tasks is generally
-problematic for reasons already addressed by
-\citet{ChemlaSpector2010:Experimental-Ev} and, more recently,
-\citet{Tielvan-Tiel2012:Embedded-Scalar}. The problem is that the
-present variants of truth-value judgment tasks all run risk of
-conflating evidence about the availability or preference of readings
-with properties of the pictorial material that are independent of the
-reading to be assessed. This problem affects all of the studies
-covered above, to some degree or other, because it follows almost
-directly from the nature of the phenomenon under investigation and
-therefore seems nearly impossible to avoid.
-
-To illustrate the potential conflation, consider a sentence like
-(\ref{bsp:EA}), which is a ``global alternative'' to an \es-sentence,
-with a universal quantifier where an \es-sentence has scalar
-\emph{some}.
-\begin{exe}
-\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es
-  mag \mymark{jede} dieser Speisen. \label{bsp:EA}\\
-  For exactly one {of these} children {it holds} it likes all {of
-    these} dishes.\\
-  For exactly one of these children it holds that it likes all of these dishes.
-\end{exe}
-Sentences like (\ref{bsp:EA}) are literally true in both of the
-situations in Figure~\ref{fig:EA-distinguishing-pics}, but these
-situations differ in the truth value of the corresponding
-\es-sentence.
-%
-\begin{figure}[]
-  \centering
-
-\subfloat[fig:global][global]{
-  \label{fig:global-EA}
-
-  \begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & true \\
-            \glb & true
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=blue,->] (X-1) -> (Y-1);
-
-        \path [draw=blue,->] (X-1) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-1);
-
-        \path [draw=black,->] (X-2) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-3);
-
-        \path [draw=black,->] (X-2) -> (Y-4);
-
-      \end{tikzpicture}
-
-} \qquad \qquad
-\subfloat[fig:literal][literal]{
-  \label{fig:literal-EA}
-
-      \begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & true \\
-            \glb & false
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=black,->] (X-2) -> (Y-1);
-
-        \path [draw=black,->] (X-2) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-3);
-
-        \path [draw=black,->] (X-2) -> (Y-4);
-
-      \end{tikzpicture}
-}
-
-\caption{Distinguishing scenarios for sentence(\ref{bsp:EA})}
-  \label{fig:EA-distinguishing-pics}
-
-\end{figure}
-%
-Our pilot study revealed a difference in acceptability, but a curious
-one. The sentence was judged \emph{true} in 90.3\% of the cases for
-the situation in Figure~\ref{fig:global-EA} and in 98.3\% in situation
-\ref{fig:literal-EA}. The observed difference is significant ($t =
--3.8259$, $df = 322.375$, $p < 0.001$). This is a curious finding,
-because, from the point of view of implicature calculation, the only
-thing that could plausibly explain this acceptability difference is
-the presence of a global implicature, resulting from the negation of
-the corresponding \es-sentence.\fn{Notice that (\ref{bsp:EA}) is the
-  alternative to the corresponding \es-sentence needed for computing
-  the putative global implicature of that \es-sentence. But since
-  these sentences are logically independent, it may be assumed that
-  the corresponding \es-sentence is an alternative also to sentences
-  like (\ref{bsp:EA}). It may also be that \emph{being-an-alternative}
-  is not a symmetric notion. Be that as it may, our argument does not
-  hinge on whether (\ref{bsp:EA}) does or does not actually have a
-  global implicature of the alleged kind.} But such a putative global
-implicature would be true in the situation~\ref{fig:global-EA}, but
-false in the situation~\ref{fig:literal-EA}. Consequently, the
-observed difference in acceptability cannot be explained simply in
-terms of the hypothesis of \citet{ChemlaSpector2010:Experimental-Ev}
-that acceptability is proportional to the number of available true
-readings. Rather some feature of the pictorial material that is
-independent of the putative readings under scrutiny does affect
-truth-value judgements, even categorical ones.
-
-\citet{ChemlaSpector2010:Experimental-Ev} acknowledge the possibility
-that the \emph{typicality} of a picture may affect graded truth-value
-judgements. Stronger still, they show that graded judgments of
-\as-sentences differ significantly for different instantiations of the
-conditions in \ref{fig:AS-distinguishing-pics}, that vary in the
-amount of connections without changing the assignment of truth values
-to candidate readings. \citeauthor{ChemlaSpector2010:Experimental-Ev}
-suggest that typicality of the pictorial material can account for
-these differences, but submit that this does not explain away the
-effect of the local reading. This is disputed by
-\citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates that all of
-\citeauthor{CliftonDube2010:Embedded-Implic}'s and
-\citeauthor{ChemlaSpector2010:Experimental-Ev}'s data on \as-sentences
-can be explained as typicality effects, dispensing the need to appeal
-to any influence of local readings. We are sympathetic towards
-\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
-reinterpretation of the data, but note, as
-\citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
-typicality-based explanation does not extend to \es-sentences in an
-obvious way\fn{For similar reasons, appeal to typicality cannot
-  explain, as far as we can see, the preference for the situation in
-  Figure~\ref{fig:literal-EA} over that in Figure~\ref{fig:global-EA}
-  given a sentence like (\ref{bsp:EA}).} and that it also does not
-explain why we observed putative effects of typicality also in
-categorical truth-value judgements in our pilot.
-
-To conclude, the confounding effects of pictorial complexity and/or
-typicality are real and affect even categorical truth-value
-judgements. The available evidence about availability, preference and
-nature of local readings is therefore still inconclusive. What is
-needed to complement the picture is data from a design that elicits
-categorical truth-value judgements that are as independent as possible
-of possibly conflating properties of the pictorial material. Given the
-logical dependencies of the relevant readings of \as- and
-\es-sentences this seems almost impossible to achieve. As we will
-argue below we do, however, believe it is.
-
-On top of this, we would like to obtain further information about
-the relative preferences among all putative readings, so as to be able
-to decide between theoretical positions, as outlined in
-Section~\ref{sec:theories-predictions}. Neither of the previous
-studies gives us that, either because they simply have not
-investigated all the relevant comparisons
-(\citet{GeurtsPouscoulous2009:Embedded-Implic},
-\citet{CliftonDube2010:Embedded-Implic}), or because they cannot safely
-derive the required cardinal information for danger of conflating
-preferences for readings with preferences for pictures
-(\citet{ChemlaSpector2010:Experimental-Ev}, our pilot study).
-
-Another desideratum for a further empirical testing is that a study
-aimed at revealing information about availability and preferences of
-readings be accompanied by a suitable comparable investigation into a
-phenomenon which is know to allow for several readings with a given
-known preferences structure. This way and only this way can a proper
-baseline be established to guide the interpretation of the observed
-data.
-
-Moreover, a final omission of previous studies is that they did not
-control for possible conflating effects of ``silent intonation''
-(XYZ)\dn{references}. Even traditionalism maintains that local
-readings are attested, but requiring a contrastive stress on the
-scalar item
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}. Variation
-in the interpretation of target sentences therefore could be caused by
-subjects imposing different intonational patterns on the visually
-presented target sentences. Ideally, we should therefore present
-sentences auditorily and address directly the frequently voiced
-hypothesis that local readings are triggered by contrastive
-stress.\dn{relate to \citet{SchwarzClifton2008:Strengthening-o} and
-  others?}
-
-The following section presents a study designed to meet all of these
-desiderata.
+
+\subsection{Discussion}
+
+Concerning the \as- and \es-sentences the observed distribution of judgments were rather similar to the results from \citeauthor{ChemlaSpector2010:Experimental-Ev}.
+Qualitatively, the only notable difference lies in the rather low acceptance of situations like \ref{fig:literal-AE} in the present experiment as compared to \citeauthor{ChemlaSpector2010:Experimental-Ev}'s original study.
+Crucially, similar to the findings of \citeauthor{ChemlaSpector2010:Experimental-Ev}, we found that situation \ref{fig:strong} was more often accepted than situation \ref{fig:strong} and that situation \ref{fig:local} was accepted more often than situation \ref{fig:false-GE}.
+This suggests that local readings are available and are even detectable via categorial truth-value judgments.
+
+However, we have to be careful with our interpretation of the results.
+Since the picture materials differd drastically in the critical comparisons, we cannot exclude pictorial effects.
+As reviewed above  \citeauthor{Tielvan-Tiel2012:Embedded-Scalar} did even show that with regards to the \as-sentences the differences in acceptance reported by C\&S and therefore presumably also the replicated results presented here can be explained by typicality of the pictures with respect to the sentence meaning.
+
+That truth is not the only determining factor affecting truth-value judgments also becomes evident from the distribution of judgments we obtained for the \ea-sentences.
+The observed difference  between \ref{fig:EA-LIT} and \ref{fig:EA-LITGLB}  is a curious finding at first sight.
+Firstly, the literal reading is true in both situations.
+Secondly, from the point of view of implicature calculation, the only thing that could plausibly explain an acceptability difference between these two situations is the presence of a global implicature, resulting from the negation of the corresponding \es-sentence.\fn{Notice that (\ref{bsp:EA}) is the alternative to the corresponding \es-sentence needed for computing the putative global implicature.
+But these sentences are logically independent.
+So, it
+  may be that the corresponding \es-sentence is an alternative also to sentences like (\ref{bsp:EA}). It may also be that being an
+  alternative is not a symmetric notion. Be that as it may, our argument does not hinge on whether (\ref{bsp:EA}) does or does not
+  actually have a global implicature of the alleged kind.} However, this putative global implicature would be true in the
+situation \ref{fig:EA-LITGLB}, but false in the situation \ref{fig:EA-LIT}. Consequently, the observed difference
+in acceptability cannot be explained simply in terms of the hypothesis
+of \citet{ChemlaSpector2010:Experimental-Ev} that acceptability increases with  the number of available true readings.
+Rather this finding, just as  \citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s study, suggests that some
+feature of the pictorial material that is independent of the putative readings under scrutiny does affect truth-value judgements, even
+categorical ones.
+
+We conclude, that  effects of pictorial complexity and/or typicality are real and affect even categorial judgments.
+For this reason the following experiment was set up to investigate the availability of local readings while minimizing pictorial effects such as typicality or complexity.
 

### 2012-07-23 text/paper/paper1.tex

@@
 available, but so dispreferred that they do not affect
-\emph{categorical} truth-value judgements (See, however, \citet{Crain1998} for arguments in favour of truth value judgments
+\emph{categorical} truth-value judgments (See, however, \citet{Crain1998} for arguments in favour of truth value judgments
 as a means of detecting highly dispreferred readings).
@@
 the possibility that the \emph{typicality} of a picture with respect to some meaning may affect graded truth-value
-judgements. Strengthening this possibility, they show that graded judgments of
+judgments. Strengthening this possibility, they show that graded judgments of
 \as-sentences differ significantly for different instantiations of the
@@
 structures associated with the quantifiers {\it all} and {\it some} and predicted the judgments of \as-sentences obtained by C\&S based
-on these data. Thereby, he obtained an excelent model fit. We are sympathetic towards
+on these data. Thereby, he obtained an excellent model fit. We are sympathetic towards
 \citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
@@
 To conclude, although considerable progress has been made in understanding which factors
-have to be controlled for in order to asses the status of loacl readings, the evidence about availability,
+have to be controlled for in order to asses the status of local readings, the evidence about availability,
 preference and nature of local readings is still inconclusive. What is needed to complement
@@
 This information was critical to our main experiment below.
-Because the main experiment employed categorial truth-value judgments out of methodological necessity, we wanted to test the sensitivity of this measure independently.
+Because the main experiment employed categorical truth-value judgments out of methodological necessity, we wanted to test the sensitivity of this measure independently.
 In addition, the question is interesting in its own right since it has implications about the nature of the ambiguity at hand, namely whether it is due to truth-relevant meaning enrichment.
 
-In particular, we tested whether the critical effects \citet{ChemlaSpector2010:Experimental-Ev} found in their graded truth-value judgment task do also show up in a categorial truth value judgment task.
+In particular, we tested whether the critical effects \citet{ChemlaSpector2010:Experimental-Ev} found in their graded truth-value judgment task do also show up in a categorical truth value judgment task.
 In order to test this we simply replicated \citeauthor{ChemlaSpector2010:Experimental-Ev}'s experiment
-using a categorial truth-value judgment task.
-If, as has been suggested, categorial truth-value judgments are not sensitive enough to detect a difference of acceptance between situations like \ref{fig:weak} and \ref{fig:strong} given \as-sentences or between \ref{fig:local} and \ref{fig:all} given \es-sentences, these should be judged identical in a truth value judgment task.
+using a categorical truth-value judgment task.
+If, as has been suggested, categorical truth-value judgments are not sensitive enough to detect a difference of acceptance between situations like \ref{fig:weak} and \ref{fig:strong} given \as-sentences or between \ref{fig:local} and \ref{fig:all} given \es-sentences, these should be judged identical in a truth value judgment task.
 
@@
 The \ea-sentences were paired with pictures like in \ref{fig:EA}.
-Figure \ref{fig:EA-LIT} is only true under the literal reading ({\it literal} diagrams) while  Figure \ref{fig:EA-LITGLB} is also true with respect to the global implicature ({\it global} diagrams) denying the weaker scalar alternative containig {\it einige} (some).
+Figure \ref{fig:EA-LIT} is only true under the literal reading ({\it literal} diagrams) while  Figure \ref{fig:EA-LITGLB} is also true with respect to the global implicature ({\it global} diagrams) denying the weaker scalar alternative containing {\it einige} (some).
 Diagrams like those in Figures \ref{fig:EA-FALSE1} and \ref{fig:EA-FALSE2} were not compatible with the \ea-sentences.
@@
 Figure \ref{fig:EA-FALSE2} is incompatible because there are too many connections.
-We used two types of incompatible pictures only because of thechnical reasons.
+We used two types of incompatible pictures only because of technical reasons.
 
@@
 
-The experiment started with a practise session consisting of $25$ trials devided into three blocks (1st block: memory task only, ten trials; 2nd block: picture verification only, five trials; 3rd block: dual task, ten trials).
-Then one list consisting of 249 trials devided into three blocks was presented.
+The experiment started with a practice session consisting of $25$ trials divided into three blocks (1st block: memory task only, ten trials; 2nd block: picture verification only, five trials; 3rd block: dual task, ten trials).
+Then one list consisting of 249 trials divided into three blocks was presented.
 An experimental session took about 75 minutes.
@@
 A logit mixed effects model with binomial link function containing a fixed effect of {\it diagram} as well as random effects of items and participants revealed a clear effect of {\it diagram}.
-In particular {\it false}, {\it literal} and {\it weak} diagrams all received fewer "yes" judgments than {\it strong} diargams (all $p<.001$).
-Another logit mixed effects model only modelling data for {\it literal} and {\it weak} diagrams also revealed an reliable effect of {\it diagram} (p<.05).
+In particular {\it false}, {\it literal} and {\it weak} diagrams all received fewer "yes" judgments than {\it strong} diagrams (all $p<.001$).
+Another logit mixed effects model only modeling data for {\it literal} and {\it weak} diagrams also revealed an reliable effect of {\it diagram} (p<.05).
 Finally, a model only considering  {\it false} and {\it literal} diagrams also revealed a significant effect of {\it diagram} (p<.001).
@@
 The responses for \es-sentences are summarized in Figure \ref{fig:GEBars}.
-Unsurprisingly, these sentences were accepted as truthfull description of {\it false} diagrams in only $0.8\%$ of all cases.
+Unsurprisingly, these sentences were accepted as truthful description of {\it false} diagrams in only $0.8\%$ of all cases.
 The {\it local} diagrams received  "yes" responses in $20\%$, {\it literal} in $71\%$ and {\it all} in $93\%$ of the time.
-A logit mixed effects model with {\it diagram} as fixed effect as well as item and participant as random effects revealed a signficant effect of {\it diagram}.
+A logit mixed effects model with {\it diagram} as fixed effect as well as item and participant as random effects revealed a significant effect of {\it diagram}.
 The {\it all}, {\it literal} and {\it local} diagrams were all accepted more often than the {\it false} diagram (all $p<.001$).
@@
 Crucially, similar to the findings of \citeauthor{ChemlaSpector2010:Experimental-Ev}, we found that situation \ref{fig:strong} was more often accepted than situation \ref{fig:strong} and that situation \ref{fig:local} was accepted more often than situation \ref{fig:false-GE}.
-This suggests that local readings are available and are even detectable via categorial truth-value judgments.
+This suggests that local readings are available and are even detectable via categorical truth-value judgments.
 
@@
 Rather this finding, just as  \citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s study, suggests that some
-feature of the pictorial material that is independent of the putative readings under scrutiny does affect truth-value judgements, even
+feature of the pictorial material that is independent of the putative readings under scrutiny does affect truth-value judgments, even
 categorical ones.
 
-We conclude, that  effects of pictorial complexity and/or typicality are real and affect even categorial judgments.
+We conclude, that  effects of pictorial complexity and/or typicality are real and affect even categorical judgments.
 For this reason the following experiment was set up to investigate the availability of local readings while minimizing pictorial effects such as typicality or complexity.
@@
 false. In that case, participants can demand that more information is
-revealed. Participants are instructed to make a truth-value judgement
+revealed. Participants are instructed to make a truth-value judgment
 as soon as they are able to.\dn{need to mention somewhere that trial
-  ends with each TV judgement}
+  ends with each TV judgment}
 
@@
 that reading) could be assessed for the first time. The location in
-the sequence and the corresponding truth-value judgement differed
+the sequence and the corresponding truth-value judgment differed
 between \as- and \es-sentences, as described presently. (This is,
@@
 slightly different sequence of unfolding which yields a different
-order in which truth-value judgements can be made.
+order in which truth-value judgments can be made.
 %

### 2012-07-31 text/paper/paper1.tex
lala

@@
 particularly relevant to assess the availability and relative
-preference of local readings. (Section~\ref{sec:theories-predictions}
-will discuss the relevant theoretical positions and the significance
-of alleged local readings in more detail.)
+preference of local readings. %(Section~\ref{sec:theories-predictions}
+%will discuss the relevant theoretical positions and the significance
+%of alleged local readings in more detail.)
 
@@
 address all preference relations between readings relevant to
-distinguish between theoretical positions. In the following we will
-argue that these heterogeneous results are partly due to the specific
-tasks used in previous studies, i.e., complexity differences in
-variants of the picture-verification paradigm.
+distinguish between theoretical positions. In the following, we will
+argue that these heterogeneous results were partly due to the use of 
+standard procedures such as picture-verification paradigm, which might not 
+be sufficiently sensitive for the phenomenon under investigation,
+for instance, due to possible confounding effects of the pictures used.
+
 % We hypothesized that previous studies might be
@@
 material auditorily and also employed a different kind of visual
-presentation of the pictorial material: subjects were presented with
-pictures that were initially covered and could incrementally be
-uncovered at the subjects' request; at each step of uncovering,
-subjects had to decide whether they could already give a truth-value
-judgement or needed more information (Comry ????)\dn{insert
-  references}. This way we obtained behavioral data that is both
+presentation of the pictorial material.
+%: subjects were presented with
+%pictures that were initially covered and could incrementally be
+%uncovered at the subjects' request; at each step of uncovering,
+%subjects had to decide whether they could already give a truth-value
+%judgement or needed more information (Comry ????)\dn{insert
+%  references}. 
+This way we obtained behavioral data that is both
 indicative of the reading subjects assumed and independent of the
-complexity of the visual stimulus. At the same time, we hypothesized
-that the incremental nature of this task would shed light on the
-preferences over readings, because the temporal distribution of
-truth-value judgments would give away which reading subjects were
-waiting to evaluate, so to speak. Adding to previous studies, we
-therefore made sure that our method is able to reveal information
-about preferential readings by including ambiguous test items like
-(\ref{bsp:target-related-filler}) which are known to preferentially
-receive the late-closure reading in
-(\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
-attested early-closure reading (\ref{bsp:target-related-filler-EC})
-(Frazier 1987 XYZ).\dn{insert proper references}
-\begin{exe}
-\ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
-  suns.
-  \begin{xlist}
-  \ex \label{bsp:target-related-filler-LC} The letter is connected
-    with squares with suns and circles. \hfill (\LC)
-  \ex \label{bsp:target-related-filler-EC} The letter is connected
-    with circles with suns and squares with suns. \hfill (\EC)
-  \end{xlist}
-\end{exe}
+confounding pictorial effects. 
+%At the same time, we hypothesized
+%that the incremental nature of this task would shed light on the
+%preferences over readings, because the temporal distribution of
+%truth-value judgments would give away which reading subjects were
+%waiting to evaluate, so to speak. 
+Adding to previous studies, we made sure that our method is able 
+to reveal information about reading preferences by relating our 
+targets to strucutres that are known in the psycholinguistic 
+literature for exhibiting certain preferences.
+
+%including ambiguous ambiguous structures, 
+%which have been shown to exhibit certain preferences in previous
+
+% like
+%(\ref{bsp:target-related-filler}) which are known to preferentially
+%receive the late-closure reading in
+%(\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
+%attested early-closure reading (\ref{bsp:target-related-filler-EC})
+%(Frazier 1987 XYZ).\dn{insert proper references}
+%\begin{exe}
+%\ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
+%  suns.
+%  \begin{xlist}
+%  \ex \label{bsp:target-related-filler-LC} The letter is connected
+%    with squares with suns and circles. \hfill (\LC)
+%  \ex \label{bsp:target-related-filler-EC} The letter is connected
+%    with circles with suns and squares with suns. \hfill (\EC)
+%  \end{xlist}
+%\end{exe}
 
@@
 
-\begin{itemize}
-\item summarize results
-\end{itemize}
-
-The paper is structured as follows. Section~\ref{sec:get-know-your}
-elaborates on the three kinds of relevant readings for our target
-sentences. Section~\ref{sec:theories-predictions} works out the
-different theoretical positions and their predictions about
-availability and preference. Section~\ref{sec:previous-studies} recaps
-the results of previous studies on this subject, arguing for the need
-of a more refined methodology. Section~\ref{sec:design} describes our
-experimental design. Section~\ref{sec:results} states our results,
-which we discuss in Section~\ref{sec:discussion}.\dn{rephrase
-  eventually}
+%\begin{itemize}
+%\item summarize results
+%\end{itemize}
+
+%The paper is structured as follows. Section~\ref{sec:get-know-your}
+%elaborates on the three kinds of relevant readings for our target
+%sentences. Section~\ref{sec:theories-predictions} works out the
+%different theoretical positions and their predictions about
+%availability and preference. Section~\ref{sec:previous-studies} recaps
+%the results of previous studies on this subject, arguing for the need
+%of a more refined methodology. Section~\ref{sec:design} describes our
+%experimental design. Section~\ref{sec:results} states our results,
+%which we discuss in Section~\ref{sec:discussion}.\dn{rephrase
+%  eventually}
 
@@
 like) local readings can occur if scalar items are marked with
-\emph{special intonation}, albeit then as a signal of a different
+\emph{special accentuation}, albeit then as a signal of a different
 pragmatic process
@@
   will gloss over this here, treating their data, as if it was obtained
-  for \es-sentences.} The critical conditions of their study presented
-subjects with pictures like those in Figure~\ref{fig:weak} and
+  for \es-sentences.} Subjects were presented with pictures like 
+  those in Figure~\ref{fig:weak} and
 \ref{fig:local} where the local reading gets a different truth-value
-from the literal and the global reading. In particular, for
-\as-sentences the local reading is false for the critical picture in
+from the literal and the global reading. For
+\as-sentences, the local reading is false for the critical picture in
 Figure~\ref{fig:weak} whereas the literal and global readings are
@@
 
-\begin{figure}[t]
-  \centering
-
-\begin{minipage}{6cm}
-     \subfloat[][literal]{
-    \label{fig:EA-LIT}
-        \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer09.eps}
-  }
-
-  \subfloat[test][global]{
-    \label{fig:EA-LITGLB}
-    \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer10.eps}
-  }  
-   \end{minipage}
-   \begin{minipage}{6cm}
-     \subfloat[][false1]{
-    \label{fig:EA-FALSE1}
-        \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer11.eps}
-  }
-
-  \subfloat[test][false2]{
-    \label{fig:EA-FALSE2}
-    \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer12.eps}
-  }  
-   \end{minipage}
-        \caption{}
-\label{fig:EA}
-\end{figure}
+%\begin{figure}[t]
+%  \centering
+% 
+%\begin{minipage}{6cm}
+%     \subfloat[][literal]{
+%    \label{fig:EA-LIT}
+%        \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer09.eps}
+%  }
+%
+%  \subfloat[test][global]{
+%    \label{fig:EA-LITGLB}
+%    \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer10.eps}
+%  }  
+%   \end{minipage}
+%   \begin{minipage}{6cm}
+%     \subfloat[][false1]{
+%    \label{fig:EA-FALSE1}
+%        \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer11.eps}
+%  }
+%
+%  \subfloat[test][false2]{
+%    \label{fig:EA-FALSE2}
+%    \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer12.eps}
+%  }  
+%   \end{minipage}
+%        \caption{}
+%\label{fig:EA}
+%\end{figure}
 
@@
 
-\begin{figure}[t]
-  \centering
-
-     \subfloat[][\as]{
-    \label{fig:AEBars}
-        \includegraphics[width=5cm]{../pictures/JudgmentsAllSomeBars.eps}
-  }
-  \subfloat[test][\es]{
-    \label{fig:GEBars}
-    \includegraphics[width=5cm]{../pictures/JudgmentsExactlySomeBars.eps}
-  }
-
-        \caption{Mean judgments}
-\label{fig:BarsPilot}
-\label{fig:EA}
-\end{figure}
+%\begin{figure}[t]
+%  \centering
+% 
+%
+%     \subfloat[][\as]{
+%    \label{fig:AEBars}
+%        \includegraphics[width=5cm]{../pictures/JudgmentsAllSomeBars.eps}
+%  }
+%  \subfloat[test][\es]{
+%    \label{fig:GEBars}
+%    \includegraphics[width=5cm]{../pictures/JudgmentsExactlySomeBars.eps}
+%  }  
+%  
+%        \caption{Mean judgments}
+%\label{fig:BarsPilot}
+%\label{fig:EA}
+%\end{figure}
 
@@
 
-\paragraph{The Target Conditions.} More concretely, our study
+\paragraph{Target Conditions.} More concretely, our study
 presented participants with pictures, like those in
@@
 
-\paragraph{Controls.} In order to make sure that subjects understood
+\paragraph{Positional controls.} In order to make sure that subjects understood
 the task, i.e., gave truth-value judgements neither sooner not later
@@
 
-\paragraph{Controlling ambiguity resolution.} In order to control for
+\paragraph{Preference-related controls} In order to control for
 artificial effects of presentation order on the availability of
@@
 we thus intended to test whether participants in our task occasionally
-choose dispreferred readings, even if they were presented following
-preferred readings.
+choose dispreferred readings, even if they were presented subsequent 
+to preferred readings.
 
@@
 \end{xlist}
+
+\ex \gll Der Brief ist mit Kreisen, die Sonnen beinhalten und Vierecken
+  verbunden. \label{bsp:target-related2}\\
+The letter is with circles, which suns contain and squares connected.\\
+The letter is connected with circles containing suns, and with squares.
+
 \end{exe}
@@
 
+\paragraph{\as- and \es-sentences and positional controls}
+
+We constructed a set of 15 items for \as- and \es-sentences, respectively,
+analogous to the examples in ... and ..
+
+Sentences were introduced by a subject DP, including the quantifiers 
+{\it alle diese} ("all of these") or {\it genau einer der} ("exactly 
+one of these"), as well as the head noun which denoted different icons, 
+such as letters or bells. Subjects were followed by an auxiliary, and 
+a PP containing {\it einige}, a possessive pronoun, and a noun denoting 
+a geometrical object, e.g. a triangle or a square. Each sentence was recorded 
+with a stressed and an unstressed version of scalar "some" (see section xx 
+below). As described in section ..., three control sentences were created 
+for each experimental item, corresponding to the critical positions.
+
+Items were evenly distributed across 5 lists using a Latin square design.
+
+\paragraph{Preference-related controls}
+For controlling preferences, 28 ambiguous Late closure sentences and 28 
+of their disambiguated counterparts were constructed as described in Section ... 
+In these sentences, subject DPs were always denoting icons and were followed
+by an auxiliary. In the ambiguous sentences, the auxiliary was followed by two PPs.
+The first of these PPs consisted in a coordination of two geometrical 
+objects, whereas the second PP denoted an icon again. In contrast to these 
+sentences, the first part of the conjunct in the unambiguous sentences,was 
+modified by a relative clause.
+
+\paragraph{Acoustic properties}
+
+A phonetically trained female native speaker of German was instructed
+to realize two prosodic versions of each target sentence, and four
+versions of the target-related fillers. In addition to these
+sentences, a set of unrelated fillers and neutral control structures
+was also recorded. For these constructions, the speaker was instructed
+to realize prosodic contours as neutral and natural as possible.
+
+For all target sentences (\as and \es), the determiner \emph{some} was
+produced with a contrastive pitch accent as well as with a neutral
+accent, respectively. Contrastive accents in German are realized by an
+H*L contour (XYZ)\dn{insert references}, thus employing a generally
+falling pattern. A set of 15 experimental items was recorded for each
+condition (\emph{accented} vs.~\emph{unaccented}), resulting in a
+total number of 60 target sentences.
+
+In contrast to the accent manipulation, target-related fillers
+differed with respect to prosodic phrasing. Prosodic phrase boundaries
+in German are realized by a rise in F0 as well as by a durational
+increase on the final part of the constituent preceding the boundary
+(prefinal lengthening) plus an optional pause (XYZ)\dn{references:
+  Vaissiere, 1983; Fery, 1993}. Boundaries for these filler sentences
+were either realized at the position separating the second \acro{pp}
+from the preceding material (\emph{late boundary}, corresponding to a
+high-attachment reading) or directly preceding the second conjunct in
+the first \acro{pp} (\emph{early boundary}, corresponding to a
+low-attachment reading). As the prosodic realization of the targets
+involved the comparison between an accented and a neutral variant, we
+also included a third version of target-related fillers, in which our
+speaker produced the sentences without any pronounced
+boundaries. Finally, an additional condition was recorded, using
+disambiguated sentences that were prosodically neutral (XYZ)\dn{proper
+  reference to explanation above}. For each prosodic variant, a set of
+30 items was read, yielding 150 target-related fillers. Together with
+30 unrelated fillers and 90 control sentences, a total number of 300
+sentences was recorded. The session was recorded in an acoustically
+shielded booth (44.1\,kHz sampling rate, 16 bit amplitude resolution).
+
+Before entering the judgment task, experimental items and
+target-related fillers were analyzed with respect to their acoustic
+properties. As both accented elements as well as prosodic boundaries
+were expected to differ with respect to their F0 and/or durational
+properties, we calculated durational values as well as difference
+values between minimal and maximal F0 for each word. As targets
+slightly differed with respect to the total number of words as well as
+with respect to certain lexical properties (i.e., \emph{seinen}
+vs.~\emph{ihren}, see above (XYZ)\dn{proper reference}), we considered
+the following analysis regions:
+
+\begin{exe}
+  \ex
+    \begin{xlist}
+      \ex $|_{\text{R}1}$~Alle  	\ $|_{\text{R}2}$~dieser 
+      \ $|_{\text{R}3}$~$\acro{np}_1$  
+      \ $|_{\text{R}4}$~sind  \ $|_{\text{R}5}$~mit  \
+      $|_{\text{R}6}$~einigen  \ $|_{\text{R}7}$~ihrer 
+       \ $|_{\text{R}8}$~{$\acro{np}_2$}  \ $|_{\text{R}9}$~verbunden.
+    \ex       $|_{\text{R}1}$~Genau einer  	\ $|_{\text{R}2}$~der 
+      \ $|_{\text{R}3}$~$\acro{np}_1$  
+      \ $|_{\text{R}4}$~ist  \ $|_{\text{R}5}$~mit  \
+      $|_{\text{R}6}$~einigen  \ $|_{\text{R}7}$~seiner 
+       \ $|_{\text{R}8}$~{$\acro{np}_2$}  \ $|_{\text{R}9}$~verbunden.
+    \end{xlist}
+    % \begin{tabbing}
+    %   $|_{\text{R}1}$ Genau einer \= 	\ $|_{\text{R}2}$ diese \=
+    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \= 
+    %   \ $|_{\text{R}4}$ sind \= \ $|_{\text{R}5}$ mit \= \
+    %   $|_{\text{R}6}$ einigen \= \ $|_{\text{R}7}$ seiner 
+    %   \= \ $|_{\text{R}8}$  \acro{np}$_2$ \= \ $|_{\text{R}9}$
+    %   verbunden. \kill
+    %   $|_{\text{R}1}$ Alle \> 	\ $|_{\text{R}2}$ dieser \>
+    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \> 
+    %   \ $|_{\text{R}4}$ sind \> \ $|_{\text{R}5}$ mit \> \
+    %   $|_{\text{R}6}$ einigen \> \ $|_{\text{R}7}$ ihrer 
+    %   \> \ $|_{\text{R}8}$  \acro{np}$_1$ \> \ $|_{\text{R}9}$
+    %   verbunden. \\
+    %   $|_{\text{R}1}$ Genau einer \> 	\ $|_{\text{R}2}$ der \>
+    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \> 
+    %   \ $|_{\text{R}4}$ ist \> \ $|_{\text{R}5}$ mit \> \
+    %   $|_{\text{R}6}$ einigen \> \ $|_{\text{R}7}$ seiner 
+    %   \> \ $|_{\text{R}8}$  \acro{np}$_1$ \> \ $|_{\text{R}9}$ verbunden.
+    % \end{tabbing}
+\end{exe}
+
+Note that differences between Regions 1, 2, 4 and 7 can be expected
+due to lexical differences between the \as and \es-conditions. As
+target-related fillers did not differ with respect to their lexical
+properties, we carried out word-by-word analyses for these
+conditions. Durational values included the respective word plus any
+following silent interval. Note that we did not include the
+disambiguated fillers in these analyses as they involved very
+different sentence types (i.e., constructions involving prepositional
+phrases vs.~relative clauses).
+
+\begin{exe}
+  \ex $|_{\text{R}1}$ \acro{D}  	\ $|_{\text{R}2}$ $\acro{np}_1$
+      \ $|_{\text{R}3}$ ist 
+      \ $|_{\text{R}4}$ mit  \ $|_{\text{R}5}$ $\acro{np}_2$   \
+      $|_{\text{R}6}$ und  \ $|_{\text{R}7}$ $\acro{np}_3$ 
+       \ $|_{\text{R}8}$  mit  \ $|_{\text{R}9}$ $\acro{np}_4$ \ $|_{\text{R}10}$~verbunden.
+\end{exe}
+
+For the durational analyses, constituents were automatically labeled
+by the \emph{Aligner} tool (XYZ),\dn{reference! Rapp, 1998} and the
+obtained values were manually corrected afterwards. For the targets,
+two-factorial \acros{anova} with the factors \acro{Quantifier} (all
+vs. exactly one) and \acro{Prosody} (accented vs.~unaccented) were
+carried out. For the target-related fillers, we carried out
+one-factorial \acros{anova} with the factor \acro{Prosody} (early
+boundary, late boundary, neutral prosody). F0 values were extracted by
+means of special Praat scripts
+(\url{http://www.fon.hum.uva.nl/praat/}). For the present analyses,
+differences between minimal and maximal F0 values for each region or
+word were calculated. Again, two-factorial \acros{anova} were carried
+out for statistical comparison of the fillers, and one-factorial
+\acros{anova} were carried out for target-related structures.
+
 A detailed description of our auditory material is found in
 Appendix~\ref{sec:audit-sent-mater}.
+
+In sum, our speaker reliably produced (i) differences in accent realization for the target sentences and (ii) different boundary realizations for the target- related fillers.
+Whereas accented elements clearly differed from their unac-
+cented counterpart by showing an increase in duration and F0 range, prosodic
+boundaries for our target-related fillers were realized by pre-final lengthening
+(i.e. an increase in F0 and duration at the position preceding the boundary).
 
@@
 
-A phonetically trained female native speaker of German was instructed
-to realize two prosodic versions of each target sentence, and four
-versions of the target-related fillers. In addition to these
-sentences, a set of unrelated fillers and neutral control structures
-was also recorded. For these constructions, the speaker was instructed
-to realize prosodic contours as neutral and natural as possible.
-
-For all target sentences (\as and \es), the determiner \emph{some} was
-produced with a contrastive pitch accent as well as with a neutral
-accent, respectively. Contrastive accents in German are realized by an
-H*L contour (XYZ)\dn{insert references}, thus employing a generally
-falling pattern. A set of 15 experimental items was recorded for each
-condition (\emph{accented} vs.~\emph{unaccented}), resulting in a
-total number of 60 target sentences.
-
-In contrast to the accent manipulation, target-related fillers
-differed with respect to prosodic phrasing. Prosodic phrase boundaries
-in German are realized by a rise in F0 as well as by a durational
-increase on the final part of the constituent preceding the boundary
-(prefinal lengthening) plus an optional pause (XYZ)\dn{references:
-  Vaissiere, 1983; Fery, 1993}. Boundaries for these filler sentences
-were either realized at the position separating the second \acro{pp}
-from the preceding material (\emph{late boundary}, corresponding to a
-high-attachment reading) or directly preceding the second conjunct in
-the first \acro{pp} (\emph{early boundary}, corresponding to a
-low-attachment reading). As the prosodic realization of the targets
-involved the comparison between an accented and a neutral variant, we
-also included a third version of target-related fillers, in which our
-speaker produced the sentences without any pronounced
-boundaries. Finally, an additional condition was recorded, using
-disambiguated sentences that were prosodically neutral (XYZ)\dn{proper
-  reference to explanation above}. For each prosodic variant, a set of
-30 items was read, yielding 150 target-related fillers. Together with
-30 unrelated fillers and 90 control sentences, a total number of 300
-sentences was recorded. The session was recorded in an acoustically
-shielded booth (44.1\,kHz sampling rate, 16 bit amplitude resolution).
-
-Before entering the judgment task, experimental items and
-target-related fillers were analyzed with respect to their acoustic
-properties. As both accented elements as well as prosodic boundaries
-were expected to differ with respect to their F0 and/or durational
-properties, we calculated durational values as well as difference
-values between minimal and maximal F0 for each word. As targets
-slightly differed with respect to the total number of words as well as
-with respect to certain lexical properties (i.e., \emph{seinen}
-vs.~\emph{ihren}, see above (XYZ)\dn{proper reference}), we considered
-the following analysis regions:
-
-\begin{exe}
-  \ex
-    \begin{xlist}
-      \ex $|_{\text{R}1}$~Alle  	\ $|_{\text{R}2}$~dieser 
-      \ $|_{\text{R}3}$~$\acro{np}_1$  
-      \ $|_{\text{R}4}$~sind  \ $|_{\text{R}5}$~mit  \
-      $|_{\text{R}6}$~einigen  \ $|_{\text{R}7}$~ihrer 
-       \ $|_{\text{R}8}$~{$\acro{np}_2$}  \ $|_{\text{R}9}$~verbunden.
-    \ex       $|_{\text{R}1}$~Genau einer  	\ $|_{\text{R}2}$~der 
-      \ $|_{\text{R}3}$~$\acro{np}_1$  
-      \ $|_{\text{R}4}$~ist  \ $|_{\text{R}5}$~mit  \
-      $|_{\text{R}6}$~einigen  \ $|_{\text{R}7}$~seiner 
-       \ $|_{\text{R}8}$~{$\acro{np}_2$}  \ $|_{\text{R}9}$~verbunden.
-    \end{xlist}
-    % \begin{tabbing}
-    %   $|_{\text{R}1}$ Genau einer \= 	\ $|_{\text{R}2}$ diese \=
-    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \= 
-    %   \ $|_{\text{R}4}$ sind \= \ $|_{\text{R}5}$ mit \= \
-    %   $|_{\text{R}6}$ einigen \= \ $|_{\text{R}7}$ seiner 
-    %   \= \ $|_{\text{R}8}$  \acro{np}$_2$ \= \ $|_{\text{R}9}$
-    %   verbunden. \kill
-    %   $|_{\text{R}1}$ Alle \> 	\ $|_{\text{R}2}$ dieser \>
-    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \> 
-    %   \ $|_{\text{R}4}$ sind \> \ $|_{\text{R}5}$ mit \> \
-    %   $|_{\text{R}6}$ einigen \> \ $|_{\text{R}7}$ ihrer 
-    %   \> \ $|_{\text{R}8}$  \acro{np}$_1$ \> \ $|_{\text{R}9}$
-    %   verbunden. \\
-    %   $|_{\text{R}1}$ Genau einer \> 	\ $|_{\text{R}2}$ der \>
-    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \> 
-    %   \ $|_{\text{R}4}$ ist \> \ $|_{\text{R}5}$ mit \> \
-    %   $|_{\text{R}6}$ einigen \> \ $|_{\text{R}7}$ seiner 
-    %   \> \ $|_{\text{R}8}$  \acro{np}$_1$ \> \ $|_{\text{R}9}$ verbunden.
-    % \end{tabbing}
-\end{exe}
-
-Note that differences between Regions 1, 2, 4 and 7 can be expected
-due to lexical differences between the \as and \es-conditions. As
-target-related fillers did not differ with respect to their lexical
-properties, we carried out word-by-word analyses for these
-conditions. Durational values included the respective word plus any
-following silent interval. Note that we did not include the
-disambiguated fillers in these analyses as they involved very
-different sentence types (i.e., constructions involving prepositional
-phrases vs.~relative clauses).
-
-\begin{exe}
-  \ex $|_{\text{R}1}$ \acro{D}  	\ $|_{\text{R}2}$ $\acro{np}_1$
-      \ $|_{\text{R}3}$ ist 
-      \ $|_{\text{R}4}$ mit  \ $|_{\text{R}5}$ $\acro{np}_2$   \
-      $|_{\text{R}6}$ und  \ $|_{\text{R}7}$ $\acro{np}_3$ 
-       \ $|_{\text{R}8}$  mit  \ $|_{\text{R}9}$ $\acro{np}_4$ \ $|_{\text{R}10}$~verbunden.
-\end{exe}
-
-For the durational analyses, constituents were automatically labeled
-by the \emph{Aligner} tool (XYZ),\dn{reference! Rapp, 1998} and the
-obtained values were manually corrected afterwards. For the targets,
-two-factorial \acros{anova} with the factors \acro{Quantifier} (all
-vs. exactly one) and \acro{Prosody} (accented vs.~unaccented) were
-carried out. For the target-related fillers, we carried out
-one-factorial \acros{anova} with the factor \acro{Prosody} (early
-boundary, late boundary, neutral prosody). F0 values were extracted by
-means of special Praat scripts
-(\url{http://www.fon.hum.uva.nl/praat/}). For the present analyses,
-differences between minimal and maximal F0 values for each region or
-word were calculated. Again, two-factorial \acros{anova} were carried
-out for statistical comparison of the fillers, and one-factorial
-\acros{anova} were carried out for target-related structures.
-
 \paragraph{Targets.} Table~\ref{tab:table-A} shows the durational values for each of

### 2012-07-31 text/paper/paper1.tex
Kleinere Änderungen an 'Materials'

@@
 
-\paragraph{\as- and \es-sentences and positional controls}
+\paragraph{Target sentences and positional controls}
 
 We constructed a set of 15 items for \as- and \es-sentences, respectively,
-analogous to the examples in ... and ..
-
-Sentences were introduced by a subject DP, including the quantifiers 
+analogous to the examples in \ref{ex:as} and \ref{ex:es}. Sentences were
+introduced by a subject {\small \acro{DP}}, including the quantifiers 
 {\it alle diese} ("all of these") or {\it genau einer der} ("exactly 
@@
 such as letters or bells. Subjects were followed by an auxiliary, and 
-a PP containing {\it einige}, a possessive pronoun, and a noun denoting 
-a geometrical object, e.g. a triangle or a square. Each sentence was recorded 
-with a stressed and an unstressed version of scalar "some" (see section xx 
-below). As described in section ..., three control sentences were created 
-for each experimental item, corresponding to the critical positions.
-
-Items were evenly distributed across 5 lists using a Latin square design.
-
-\paragraph{Preference-related controls}
+a {\small \acro{PP}} containing {\it einige}, a possessive pronoun, and a noun denoting 
+a geometrical object, e.g. {\it einigen seiner Dreiecke/Quadrate} ("some of its triangles/squares").
+The last word was the main verb {\it verbunden} ("connected"). Each sentence was recorded 
+in a stressed and an unstressed version of scalar {\it einige} (see section xx 
+below). As described above, three control sentences were created 
+for each experimental item, corresponding to the critical positions
+in the course of uncovering the accompanying sequences (see below).
+The positional controls were recorded with neutral prosody.  Items
+were evenly distributed across 5 lists using a Latin square design.
+
+\paragraph{Preference-related control sentences}
 For controlling preferences, 28 ambiguous Late closure sentences and 28 
-of their disambiguated counterparts were constructed as described in Section ... 
-In these sentences, subject DPs were always denoting icons and were followed
-by an auxiliary. In the ambiguous sentences, the auxiliary was followed by two PPs.
-The first of these PPs consisted in a coordination of two geometrical 
-objects, whereas the second PP denoted an icon again. In contrast to these 
-sentences, the first part of the conjunct in the unambiguous sentences,was 
+of their disambiguated counterparts were constructed as described  above.
+In these sentences, subject {\small \acro{DP}}s were always denoting icons and were followed
+by an auxiliary. In the ambiguous sentences, the auxiliary was followed by two {\it mit}-{\small \acro{PP}}s.
+The first of these {\small \acro{PP}}s consisted in a coordination of two nouns denoting geometrical 
+objects, whereas the second PP denoted icons. In contrast to these 
+sentences, the unambiguous sentences contained only one PP with a conjunction the first part of which was 
 modified by a relative clause.
@@
 A phonetically trained female native speaker of German was instructed
-to realize two prosodic versions of each target sentence, and four
-versions of the target-related fillers. In addition to these
-sentences, a set of unrelated fillers and neutral control structures
-was also recorded. For these constructions, the speaker was instructed
+to realize two prosodic versions of each target sentence, and three
+versions of the ambiguous preference-related controls. In addition to these
+sentences, the unambiguous preference-related controls, the positional controls
+and a set of unrelated fillers were also recorded. For these constructions, the speaker was instructed
 to realize prosodic contours as neutral and natural as possible.
 
-For all target sentences (\as and \es), the determiner \emph{some} was
+For all target sentences (\as and \es), the determiner \emph{einige} was
 produced with a contrastive pitch accent as well as with a neutral
-accent, respectively. Contrastive accents in German are realized by an
+accent. Contrastive accents in German are realized by an
 H*L contour (XYZ)\dn{insert references}, thus employing a generally
 falling pattern. A set of 15 experimental items was recorded for each
-condition (\emph{accented} vs.~\emph{unaccented}), resulting in a
+condition (\as vs. \es, \emph{accented} vs.~\emph{unaccented}), resulting in a
 total number of 60 target sentences.
 
-In contrast to the accent manipulation, target-related fillers
+In contrast to the accent manipulation, the ambiguous preference-related controls
 differed with respect to prosodic phrasing. Prosodic phrase boundaries
@@
 (prefinal lengthening) plus an optional pause (XYZ)\dn{references:
-  Vaissiere, 1983; Fery, 1993}. Boundaries for these filler sentences
-were either realized at the position separating the second \acro{pp}
+  Vaissiere, 1983; Fery, 1993}. Boundaries for these control sentences
+were either realized at the position separating the second {\small \acro{PP}}
 from the preceding material (\emph{late boundary}, corresponding to a
 high-attachment reading) or directly preceding the second conjunct in
-the first \acro{pp} (\emph{early boundary}, corresponding to a
+the first {\small \acro{PP}} (\emph{early boundary}, corresponding to a
 low-attachment reading). As the prosodic realization of the targets
 involved the comparison between an accented and a neutral variant, we
-also included a third version of target-related fillers, in which our
+also included a third version of the ambiguous preference related controls, in which our
 speaker produced the sentences without any pronounced
-boundaries. Finally, an additional condition was recorded, using
-disambiguated sentences that were prosodically neutral (XYZ)\dn{proper
-  reference to explanation above}. For each prosodic variant, a set of
-30 items was read, yielding 150 target-related fillers. Together with
-30 unrelated fillers and 90 control sentences, a total number of 300
-sentences was recorded. The session was recorded in an acoustically
+boundaries. For each prosodic variant, a set of
+30 items was read, yielding 90 target-related fillers.
+
+Altogether a total number of 300 sentences consisting of 60 target sentences, 90 ambiguous preference-related controls, 30 unambiguous preference-related controls, 90 positional control sentences and 30 unrelated fillers was recorded.
+The session was recorded in an acoustically
 shielded booth (44.1\,kHz sampling rate, 16 bit amplitude resolution).
@@
 Before entering the judgment task, experimental items and
-target-related fillers were analyzed with respect to their acoustic
+preference-related fillers were analyzed with respect to their acoustic
 properties. As both accented elements as well as prosodic boundaries
@@
 differences between minimal and maximal F0 values for each region or
-word were calculated. Again, two-factorial \acros{anova} were carried
-out for statistical comparison of the fillers, and one-factorial
-\acros{anova} were carried out for target-related structures.
-
-A detailed description of our auditory material is found in
+word were calculated. Again, two-factorial \acros{anova}s were carried
+out for statistical comparison of the target sentences, and one-factorial
+\acros{anova}s were carried out for preference-related controls.
+
+The details of these analyses are found in
 Appendix~\ref{sec:audit-sent-mater}.
-
-In sum, our speaker reliably produced (i) differences in accent realization for the target sentences and (ii) different boundary realizations for the target- related fillers.
-Whereas accented elements clearly differed from their unac-
-cented counterpart by showing an increase in duration and F0 range, prosodic
-boundaries for our target-related fillers were realized by pre-final lengthening
+In sum, our speaker reliably produced (i) differences in accent realization for the target sentences and (ii) the expected boundary realizations for the preference-related controls.
+Whereas accented elements clearly differed from their unaccented counterpart by showing an increase in duration and F0 range, prosodic boundaries for our target-related fillers were realized by pre-final lengthening
 (i.e. an increase in F0 and duration at the position preceding the boundary).

### 2012-08-01 text/paper/paper1.tex
smallish changes

@@
 whether local readings exist \citep[see also][for related
-discussion]{Tielvan-Tiel2012:Embedded-Scalar} and do not clearly
-address all preference relations between readings relevant to
+discussion]{Tielvan-Tiel2012:Embedded-Scalar}, and previous studies 
+did not explicitly address all preference relations between readings relevant to
 distinguish between theoretical positions. In the following, we will
@@
 In reaction to this situation, we therefore presented sentence
-material auditorily and also employed a different kind of visual
+materials auditorily and also employed a different kind of visual
 presentation of the pictorial material.
@@
 picture-verification task to find out whether local readings of \as-
-and \es-sentences are available.\fn{Actually,
-  \citet{GeurtsPouscoulous2009:Embedded-Implic} did not use
+and \es-sentences are available.\fn{We will focus here on a subset 
+of the conditions tested by
+  \citet{GeurtsPouscoulous2009:Embedded-Implic}. Moreover, note that these authors did not use
   \es-sentences, but sentences where scalar \emph{some} was embedded
@@
 
-\noindent Again the majority response ``both'' might speak for a
+\noindent Again, the majority response ``both'' might speak for a
 preference for the literal reading, but, as
@@
 Taken together, the results by Clifton and Dube demonstrate that
-participant' choices for \as-readings might be strongly affected by
+participants' choices for \as-readings might be strongly affected by
 the specific experimental paradigm used. If task demands are only
@@
 rejected the \es-sentences in Geurts and Poscoulous' original study,
-despite the fact that they could have accepted it based on the local
+despite the fact that they could have accepted them based on the local
 reading. It is thus necessary to test both universal and non-monotonic
@@
 readings. In their picture verification experiment, \citet{GeurtsPouscoulous2009:Embedded-Implic} did not observe any truth value judgments that would indicate
-local readings. On the basis of this finding they argue that these readings are simply not available. On the other
+local readings. On the basis of their results, they argue that these readings are simply not available. On the other
 hand,  \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} argue that the findings of  \citeauthor{GeurtsPouscoulous2009:Embedded-Implic} may be due to a bias in their experimental design and
@@
 
-Be this as it may, we cannot ascribe the effects reported by  \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} to the availability of local readings with certainty.
+For these reasons, we cannot ascribe the effects reported by  \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} to the availability of local readings with certainty.
 \citet{ChemlaSpector2010:Experimental-Ev} themeselves acknowledge
@@
 
-Moreover, a final omission of previous studies is that they did not
-control for possible conflating effects of ``silent intonation''
-(XYZ)\dn{references}. Even traditionalism maintains that local
-readings are attested, but requiring a contrastive stress on the
-scalar item
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}. Variation
-in the interpretation of target sentences therefore could be caused by
-subjects imposing different intonational patterns on the visually
-presented target sentences. Ideally, we should therefore present
-sentences auditorily and address directly the frequently voiced
-hypothesis that local readings are triggered by contrastive
+Finally, the above-mentioned studies did not control for possible 
+conflating effects of ``silent prosody''. A growing number of experiments
+suggests that numerous factors might influence accent placement and
+prosodic phrasing even while reading, amongst them default accentuation,
+constituent length, rhythmic phenomena, and individual variation
+(Augurzky, 2008; Bader, 1998; Fodor, 2000, 2001; Kentner, 2012, Steinhauer et.
+al., 2001, see also the discussion in Frazier, 2009)\dn{references}.
+
+As it has been suggested in the theoretical literature that the availability
+of a local reading might hinge on the realization of contrastive stress on the
+scalar item, 
+%Even traditionalism maintains that local
+%readings are attested, but requiring a contrastive stress on the
+%scalar item
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}, it is necessary to
+control for potential variation due to potential differences in silent accent placement.
+We therefore presented sentences auditorily and addressed the frequently proposed claim 
+that local readings are triggered by contrastive
 stress.\dn{relate to \citet{SchwarzClifton2008:Strengthening-o} and
@@
 
-\paragraph{Preference-related controls} In order to control for
+\paragraph{Preference-related controls.} In order to control for
 artificial effects of presentation order on the availability of

### 2012-08-01 text/paper/paper1.tex
smallish changes 2

@@
 Finally, the above-mentioned studies did not control for possible 
-conflating effects of ``silent prosody''. A growing number of experiments
+conflating effects of ``silent prosody''. A growing number of evidence
 suggests that numerous factors might influence accent placement and
@@
 \paragraph{General Idea.} In order to test the availability and
-preferences of different readings of \as- and \es-sentences, we were
-looking for a way to unambiguously map responses from a picture
+preferences of different readings of \as- and \es-sentences in German, 
+we were looking for a way to unambiguously map responses from a picture
 verification task to specific readings. We were particularly
 interested in the question whether local readings would be observed at
-all, but we were also interested in obtaining information about the
-relative preferences of the relevant readings. In addition, we wanted
-to minimize effects of any graphical differences between the picture
-materials. To achieve this we designed an experiment employing a
+all, and whether their presence or absence would be modulated by
+a contrastive accent on the scalar item. Moreover, we were  
+interested in obtaining information about the relative preferences 
+of the different readings. In addition, we wanted
+to minimize effects of graphical differences between the picture
+materials. To achieve this, we designed an experiment employing a
 modified version of picture verification, namely the
 \mymark{incremental verification task} (\acro{ivt}, see Conroy
-???)\dn{reference}. The general idea is that subjects are to judge
+???)\dn{reference}. The general idea is that subjects are requested to judge
 sentence material based on pictures that do not necessarily contain
@@
 
-\paragraph{Target Conditions.} More concretely, our study
-presented participants with pictures, like those in
-Figures~\ref{fig:InitialPicture}, \ref{fig:exseqAS} or
-\ref{fig:exseqES}, depicting a set of four identical central elements
+\paragraph{Target Conditions.} In the present study, participants were 
+presented pictures
+%, like those in
+%Figures~\ref{fig:InitialPicture}, \ref{fig:exseqAS} or
+%\ref{fig:exseqES}, 
+depicting a set of four identical central elements
 (e.g., letters), which could be connected to surrounding elements
@@
 %
-Sentences to be judged were in German (see (\ref{ex:as}) and
-(\ref{ex:es}) below) and presented auditorily, and participants were
+Sentences to be judged 
+%were in German (see (\ref{ex:as}) and (\ref{ex:es}) below) and 
+were presented auditorily, and participants were
 asked to listen to a given sentence and then uncover the potential
@@
 uncovering process where the truth value of that reading (and only of
-that reading) could be assessed for the first time. The location in
-the sequence and the corresponding truth-value judgment differed
-between \as- and \es-sentences, as described presently. (This is,
-again, because of the logical dependencies between readings.)
+that reading) could be assessed for the first time, which we will
+refer to as {\it critical position}. The location in the sequence and 
+the corresponding truth-value judgment differed between \as- and 
+\es-sentences, as described presently. (This is, again, because of the 
+logical dependencies between readings.)
 
@@
 we thus intended to test whether participants in our task occasionally
-choose dispreferred readings, even if they were presented subsequent 
-to preferred readings.
+choose dispreferred readings, even if they were available only at a critical
+position following the preferred readings.
 

### 2012-08-01 text/paper/paper.tex
bibtex test

@@
 able to control for effects of ``silent intonation'' that subjects may
-apply when reading a sentence (see Bader 1998, Fodor 2000)\dn{provide
+apply when reading a sentence (see Bader 1998, Fodor, 2000)\dn{provide
   references}.

### 2012-08-01 text/paper/paper1.tex
bibtex test

@@
 able to control for effects of ``silent intonation'' that subjects may
-apply when reading a sentence (see Bader 1998, Fodor 2000)\dn{provide
+apply when reading a sentence see Bader 1998, \citep{Fodor1998:Learning}
+\dn{provide
   references}.

### 2012-08-02 text/paper/paper1.tex
materials modification

@@
 a {\small \acro{PP}} containing {\it einige}, a possessive pronoun, and a noun denoting 
-a geometrical object, e.g. {\it einigen seiner Dreiecke/Quadrate} ("some of its triangles/squares").
-The last word was the main verb {\it verbunden} ("connected"). Each sentence was recorded 
-in a stressed and an unstressed version of scalar {\it einige} (see section xx 
-below). As described above, three control sentences were created 
+a geometrical object, e.g. {\it einigen seiner Dreiecke/Quadrate} ("some of its triangles/squares"). The possessive pronoun was used in order to fix relative 
+quantifier scope to surface scope, thus ensuring that {\it einige} has 
+embedded status. The last word was the main verb {\it verbunden} ("connected"). 
+Each sentence was recorded  in a stressed and an unstressed version of scalar 
+{\it einige} (see section xx  below). As described above, three control sentences were created 
 for each experimental item, corresponding to the critical positions
@@
 (i.e. an increase in F0 and duration at the position preceding the boundary).
+
+\paragraph{Pictures.}
+The visual sequences accompanying each sentence consisted of pictures comparable to those illustrated in Figure \ref{fig:InitialPicture}.
+In each picture, four alternative sub-scenarios were presented, in which an icon was surrounded by six geometrical shapes.
+Depending on the sentence material, shapes and icons differed across sentence types and conditions.
+For example, in our target conditions, 4 identical icons were surrounded by geometrical shapes that were all of the same type, whereas various iconds and surrounding elements were used in each sequence of the preference-related control structures.
+As described in section xx, grey colour initially covered the links between icons and shapes.
+As the connections were to be uncovered step by step, different pictures were designed corresponding to different stages in the uncovering process.
+Note that the single conditions impose distinct requirements on sequences.
+For instance, inherent entailment relations between \as-sentences and \es-sentences lead to different critical positions at which participants can make their judgments.
+We will therefore describe the sequences for each condition separately.
+
+For \as-sentences, as well as for the corresponding positional control sentences described in Section \ref{sec:design}, we designed a set of seven pictures for each trial.
+In each sequence, the critical position associated with the literal meaning was presented at the third step, the position associated with the global meaning was shown at the fifth step, and the local reading was presented at the final step (see Figure \ref{fig:exseqAS} for an illustration of the critical positions).
+Pictures that were interspersed between these positions served as spillover-pictures.
+These were used in order to control for potentially delayed judgments and they additionally served as distractor items.
+
+Sequences in the \es conditions (and their respective positional controls) consisted of a set of five pictures with the following critical positions.
+The critical positions as illustrated in Figure \ref{fig:exseqES} are associated with the second picture (global reading), the third picture (literal reading), as well as with the final picture (local reading).
+
+For the preference-related controls, we used two types of sequences.
+First, a sequence in which the crirical position for the (preferred) Late Closure reading was presented preceding the critical position for the Early Closure reading ({\it LC sequence}), and second, a sequence in which the readings were presented in reversed order ({\it EC sequence}.
+In the LC sequences, seven pictures were presented, with the LC reading given at the third picture, aand the EC reading at the sixth picture.
+EC sequences consisted of five pictures, in which the critical positions were realized at the third picture (EC reading) and at the fifth picture (LC reading).
+
+Finally, we added pictures compatible with unrelated fillers with critical position at random uncovering stages.
+
+\paragraph{Lists.}
+Experimental items and preference-related fillers were evenly distributed across lists.
+For the \as- and \es-sentences together with their respective controls, five lists were used employing a Latin square design.
+Picture sentence-pairs for the preference-related controls were spread across eight lists.
+Each target list was combined with each list from the preference-related controls, thus yielding to a total of forty lists.
+The thirty unrelated filler items were included in each of these resulting lists.
 

### 2012-08-03 text/paper/paper1.tex
beginning of prosody part revision

@@
 prefer. Finally, previous studies presented target sentences
-visually. But as it is often argued that intonational stress on an
+visually. But as it is often argued that focal stress on an
 embedded scalar item can favor a local reading
@@
 it seems important to present target sentences auditorily, so as to be
-able to control for effects of ``silent intonation'' that subjects may
+able to control for effects of ``silent prosody'' that subjects may
 apply when reading a sentence see Bader 1998, \citep{Fodor1998:Learning}
@@
 indicative of the reading subjects assumed and independent of the
-confounding pictorial effects. 
+potential pictorial and prosodic confounds. 
 %At the same time, we hypothesized
@@
 
-\paragraph{Testing Effects of accentuation.}\dn{These two paragraphs
-  still need a proper home; Petra opts for ``materials'' section.} It
-has been claimed that local readings only emerge in the case of
-special accentuation of the the scalar item under consideration
-(REFERENCES). Further, it is generally assumed that the required type
-of accentuation is a pitch accent (REFS). To test for this possibility
-we decided to present the sentences (eg., (\ref{ex:as}) and
-(\ref{ex:es})) auditorily in two versions each. In the accented
-version a pitch accent was placed on {\it einige}. The second version
-had neutral prosody. If accentuation is the driving force for local
-readings, we would expect a higher proportion of local readings in the
-former than in the latter version of the sentences.
+\paragraph{Testing Effects of prosody.}\dn{These two paragraphs
+  still need a proper home; Petra opts for ``materials'' section.}
+
+The availability of local readings has often been claimed to be
+affected by the presence or absence of a focal accent on the scalar
+item. By contrastively accenting the scalar, potential alternatives
+are highlighted, resulting in more implicatures being computed.
+Some approaches have even claimed that local readings exclusively 
+emerge when the scalar item is accented and are otherwise generally
+unavailable (Refs).
+
+Though there seems to be general consensus about these potential 
+prosodic effects, empirical evidence for this assumption 
+is still scarce. One notable exception comes from a pilot study 
+by Frazier, in which participants were instructed to read embedded
+and non-embedded versions of English ae sentences, in which some was either
+capitalized or non-capitalized. Prior to the experiment, participants 
+were told that capitalizing corresponded to contrastive stress.
+Interestingly, strengthened interpretations occurred rather often 
+in the embedded sentences in this task (59 \%), but were 
+not affected by capitalizing. ...
+Another study relevant for the present consideration comes from Schwarz et al., 
+examining the effects of contrastive accentuation of "or" in non-embedded sentences 
+like {\it Mary will invite Fred or/OR Sam to barbecue}. After listening to these 
+sentences, participants were presented two alternative readings ({\it 1. She will 
+invite Fred or Sam or possibly both}, or {\it 2. She will invite Fred or Sam but 
+not both}).
+
+%  It
+%has been claimed that local readings only emerge in the case of
+%special accentuation of the the scalar item under consideration
+%(REFERENCES). Further, it is generally assumed that the required type
+%of accentuation is a pitch accent (REFS). To test for this possibility
+%we decided to present the sentences (eg., (\ref{ex:as}) and
+%(\ref{ex:es})) auditorily in two versions each. In the accented
+%version a pitch accent was placed on {\it einige}. The second version
+%had neutral prosody. If accentuation is the driving force for local
+%readings, we would expect a higher proportion of local readings in the
+%former than in the latter version of the sentences.
 

### 2012-08-05 text/paper/paper1.tex
paper1 general stuff, typos, layout, minor in whole document

@@
 \begin{abstract}
-  \dots make concrete \dots
+  \begin{itemize}
+  \item What is needed to complement the picture is data from a
+    verification experiment that is as independent as possible of
+    potentially conflating properties of the pictorial material and
+    that is nonetheless sensitive enough to detect local readings even
+    if they are dispreferred.
+  \end{itemize}
+
 \end{abstract}
@@
 \emph{quantity implicature}, derived by an abductive inference as the
-best explanation of why an informed, knowledgable and cooperative
-speakers have uttered (\ref{bsp:Plain-SI-Target}) when they could also
-have uttered the semantically stronger and relevant
+best explanation of why informed, knowledgable and cooperative
+speakers would utter (\ref{bsp:Plain-SI-Target}) when they could also
+utter the semantically stronger and relevant
 (\ref{bsp:Plain-SI-Alternative}).
@@
 \begin{enumerate}[Q1:]
-\item which of these three
-conceivable readings are available to na\"{i}ve subjects; and
+\item which of these readings are available to na\"{i}ve subjects; and
 \item which of the available readings are preferred.\fn{It may
@@
 for instance, due to possible confounding effects of the pictures used.
-
 % We hypothesized that previous studies might be
@@
 %waiting to evaluate, so to speak. 
-Adding to previous studies, we made sure that our method is able 
-to reveal information about reading preferences by relating our 
-targets to strucutres that are known in the psycholinguistic 
-literature for exhibiting certain preferences.
+Adding to previous studies, we made sure that our method is able to
+reveal information about reading preferences by relating our targets
+to ambiguous sentences with a well-known preference on available
+readings.
 
@@
 one in turn. Since there is some leeway in assessing the predictions
-for some of these positions (depending on which of several reasonable
+for each of these positions (depending on which of several reasonable
 additional assumptions we should adopt), we will distinguish different
-varieties of each position. For convenience, the predictions of each
-(variety of each) position are also summarized in
-Table~\ref{tab:predictions} at the end of this section.\dn{micha says:
-I'll leave all the varieties in here until we know which ones we need
-and which ones we don't need}
+varieties of each. For convenience, the predictions of each (variety
+of each) position are also summarized in Table~\ref{tab:predictions}
+at the end of this section.\dn{micha says: I'll leave all the
+  varieties in here until we know which ones we need and which ones we
+  don't need}
 
@@
 these extra assumptions are met. In that case, traditionalism would
-predict that the global readings should be preferred over the literal
+predict that global readings should be preferred over literal
 readings. On the other hand, it might also be hypothesized that, for
@@
 usually/strongly/unless-completely-intenable and therefore predicts
-that global readings are preferred over the literal ones; \mymark{the
-  weak variety of traditionalism} holds that the auxiliary assumptions
-are more fragile and predicts that literal readings are preferred over
-the global ones.\fn{We mention for clarity that although weak
+that global readings are preferred over literal ones; \mymark{the weak
+  variety of traditionalism} holds that the auxiliary assumptions are
+more fragile and predicts that literal readings are preferred over the
+global ones.\fn{We mention for clarity that although weak
   traditionalism does not predict the global reading to be preferred,
@@
   the stronger alternative is true. Whether it does predict that
-  depends on which auxiliary assumption are assumed to be met and
+  depends on which auxiliary assumptions are assumed to be met and
   which are not.}\dn{acknowledge comment by Philippe Schlenker
@@
 \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic}. We
-will come back to this issue in Section~\ref{sec:role-intonation}.
+will come back to this issue in Section~\ref{sec:local-read-categ}.
 
@@
 the literal meanings are \emph{ceteris paribus} preferred
-\mymark{literalism}\dn{better name?}. We are not aware that anyone has
-defended this option, but we will come back to this later on.\dn{where
-  exactly}
+\mymark{literalism}. We are not aware that anyone has defended this
+option, but it pays to include this option, because, as we will see
+later on, this possible position is the best direct explanation of our
+experimental data.
 
@@
 to that, our dummy position of literalism predicts that literal
-readings are preferred over local ones.\dn{Petra says that his is too
-  short; suggests skipping the whole section; I'm not sure; could do
-  that too; anyway, it must be mentioned because conventionalism turns
-  out to be one of the best predictors of our data;}
+readings are preferred over local ones.
 
@@
 poly-typed function that enriches an expression $X$, which crucially
-need not be a full proposition, based on a set, $\alt(X)$, of
+need not be a full proposition, based on a set $\alt(X)$ of
 (suitable, relevant) alternatives to $X$ that yields an enriched
@@
 these. \citet{ChierchiaFox2008:The-Grammatical} discuss two concrete
-variants of the strongest meaning hypothesis. Towards a definition
-that is just precise enough for our current purposes, fix a sentence
-with propositional content $S$ with candidate readings $C(S)$, where
-$C(S)$ contains $S$ and all readings derivable from inserting
-$\exh(\cdot)$ at suitable scope sites.\fn{Strictly speaking, we should
-  compare \emph{parses} of sentences with $\exh(\cdot)$ at various
-  scope sites with respect to the readings that these parses give rise
-  to \citep[c.f.][]{ChierchiaFox2008:The-Grammatical}, but we may
-  ignore this detail here for ease of exposition.}  Then define
-\emph{ceteris paribus} preferences among members of $X,Y \in C(S)$ as
-either:
+variants of the strongest meaning hypothesis: fix a sentence with
+propositional content $S$ with candidate readings $C(S)$, where $C(S)$
+contains $S$ and all readings derivable from inserting $\exh(\cdot)$
+at suitable scope sites;\fn{Strictly speaking, we should compare
+  \emph{parses} of sentences with $\exh(\cdot)$ at various scope sites
+  with respect to the readings that these parses give rise to
+  \citep[c.f.][]{ChierchiaFox2008:The-Grammatical}, but we may ignore
+  this detail here for ease of exposition.} then define \emph{ceteris
+  paribus} preferences among members of $X,Y \in C(S)$ as either
 \begin{exe}
 \ex \label{bsp:SMH-Total} 
-  $X >_w Y$ iff $X \subset Y$ 
+  $X$ is preferred to $Y$ iff $X \subset Y$ 
   \attrib{\citep[(104)]{ChierchiaFox2008:The-Grammatical}}
 \end{exe}
-or:
+or
 \begin{exe}
-\ex \label{bsp:SMH-Partial}  $X >_s Y$ iff $X \subset Y$ and $X$ and
-  $Y$ are readings obtained from applications of $\exh(\cdot)$ at
-  exactly the same scope sites, except for one.
-  \attrib{\citep[(105)]{ChierchiaFox2008:The-Grammatical}} 
+\ex \label{bsp:SMH-Partial}  $X$ is preferred to $Y$ iff $X \subset Y$
+  and $X$ and $Y$ are readings obtained from applications of
+  $\exh(\cdot)$ at exactly the same scope sites, except for
+  one. \attrib{\citep[(105)]{ChierchiaFox2008:The-Grammatical}} 
 \end{exe}
-Since $X >_s Y$ entails $X >_w Y$, we will speak of \mymark{weak
-  grammaticalism} and \mymark{strong grammaticalism}, depending on
-whether (\ref{bsp:SMH-Total}) or (\ref{bsp:SMH-Partial}) is used.
+Since the former is entailed by the latter, we will speak of
+\mymark{weak grammaticalism} and \mymark{strong grammaticalism},
+depending on whether (\ref{bsp:SMH-Total}) or (\ref{bsp:SMH-Partial})
+is used.
 
@@
 40\% of choices for the strong situation, so
-\citeauthor{CliftonDube2010:Embedded-Implic} argue, might be
-indicative of the availability of the local reading. In version 2 of
-the experiment, the picture pair consisted of the literal and weak
-situations in Figures~\ref{fig:literal-AE} and \ref{fig:weak}. In this
-case, response percentages were:
+\citeauthor{CliftonDube2010:Embedded-Implic} argue, is indicative of
+the availability of the local reading. In version 2 of the experiment,
+the picture pair consisted of the literal and weak situations in
+Figures~\ref{fig:literal-AE} and \ref{fig:weak}. In this case,
+response percentages were:
 
@@
 
-Taken together, the results by Clifton and Dube demonstrate that
+The diverging results of
+\citeauthor{GeurtsPouscoulous2009:Embedded-Implic} and
+\citeauthor{CliftonDube2010:Embedded-Implic} demonstrate that
 participants' choices for \as-readings might be strongly affected by
@@
 felicitous for a literal reading, the \emph{absence} of choices of
-local readings cannot be accounted for by assuming an inavailability
+local readings cannot be accounted for by assuming an unavailability
 of these readings \emph{per se}.\dn{micha does not understand this
@@
 reading. It is thus necessary to test both universal and non-monotonic
-quantifiers within the same experiment using a task that offers
-alternatives. Additionally, it would be informative to also probe into
-the availability and the relative preference of global readings. The
-study of \citet{ChemlaSpector2010:Experimental-Ev} did both of that.
+quantifiers within the same experiment. Additionally, it would be
+informative to also probe into the availability of global
+readings. The study of \citet{ChemlaSpector2010:Experimental-Ev} did
+both of that.
 
@@
 situation (although these differ only with respect to the truth value
-of the local reading). In a similar way, evidence for the availability
+of the local reading). Evidence for the availability
 of the local reading for \es-sentences comes from the difference
@@
 pieces of evidence concerning the status of putative local
-readings. In their picture verification experiment, \citet{GeurtsPouscoulous2009:Embedded-Implic} did not observe any truth value judgments that would indicate
-local readings. On the basis of their results, they argue that these readings are simply not available. On the other
-hand,  \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} argue that the findings of  \citeauthor{GeurtsPouscoulous2009:Embedded-Implic} may be due to a bias in their experimental design and
-employed different methods intended to be sensitive enough to reveal effects of local readings: either by
-a choice of the situation that better befits a given sentence (\citeauthor{CliftonDube2010:Embedded-Implic}), or by a graded
-truth-value judgment (\citeauthor{ChemlaSpector2010:Experimental-Ev}). Both studies found evidence in support of local readings.
-To account for the diverging results we could draw a distinction between \emph{categorical} truth-value
-judgments and other more sensitive measures. Firstly, it could be hypothesized
-along with \citeauthor{CliftonDube2010:Embedded-Implic} and
+readings. In their picture verification experiment
+\citet{GeurtsPouscoulous2009:Embedded-Implic} did not observe any
+truth value judgments that would indicate local readings. On the basis
+of this observation, they argue that these readings are simply not
+available. On the other hand,
+\citeauthor{CliftonDube2010:Embedded-Implic} and
+\citeauthor{ChemlaSpector2010:Experimental-Ev} argue that the findings
+of \citeauthor{GeurtsPouscoulous2009:Embedded-Implic} may be due to a
+bias in their experimental design and employed different methods
+intended to be sensitive enough to reveal effects of local readings:
+either by a choice of the situation that better befits a given
+sentence (\citeauthor{CliftonDube2010:Embedded-Implic}), or by a
+graded truth-value judgment
+(\citeauthor{ChemlaSpector2010:Experimental-Ev}). Both studies found
+putative evidence in support of local readings.
+
+To account for the diverging results we could draw a distinction
+between \emph{categorical} truth-value judgments and other more
+sensitive measures. Firstly, it could be hypothesized along with
+\citeauthor{CliftonDube2010:Embedded-Implic} and
 \citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
-available, but so dispreferred that they do not affect
-\emph{categorical} truth-value judgments (See, however, \citet{Crain1998} for arguments in favour of truth value judgments
-as a means of detecting highly dispreferred readings).
-Secondly it could also be argued, in line with traditionalism, that the apparent difference in
-sensitivity of the different judgment types can be explained by the stipulation that
+available, but so dispreferred that they do not affect categorical
+truth-value judgments (see, however, \citet{Crain1998} for arguments
+in favour of truth-value judgments as a means of detecting highly
+dispreferred readings).  Secondly it could also be argued, in line
+with traditionalism, that the apparent difference in sensitivity of
+the different judgment types can be explained by the stipulation that
 the results reported by \citeauthor{CliftonDube2010:Embedded-Implic}
-and \citeauthor{ChemlaSpector2010:Experimental-Ev} reflect something other than
-(strongly) truth-relevant speaker-intended meaning enrichments after all, so that no case
-can be made for lexicalism or grammaticalism on the basis of these data \citep[c.f.][for arguments along these lines]{Tielvan-Tiel2012:Embedded-Scalar}.
-
-Note, however, that the type of judgment  is not the only crucial difference between the methods of \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} on the one hand and  \citet{GeurtsPouscoulous2009:Embedded-Implic} on the other.
-For example these studies  also differed with respect to the types of situations that were shown to the participants during the course of the experiment.
-The presence or absence of competing situations may have led to skewed distributions of judgments for situations like in Figure \ref{fig:weak}.
-Such effects might emerge simply because the type of sentence-picture combinations shown during the experiment affects the standard of judgment but could~-- maybe more elegantly~-- also be explained by findings from \citet{Raffray2010} suggesting that exposing participants to models may prime corresponding logical forms and thereby shift reading preferences.
-Taking these possibilities into account, it remains unclear whether the effects reported by  \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} would also show up using ordinary picture verification, in the first place.
-
-For these reasons, we cannot ascribe the effects reported by  \citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} to the availability of local readings with certainty.
-\citet{ChemlaSpector2010:Experimental-Ev} themeselves acknowledge
-the possibility that the \emph{typicality} of a picture with respect to some meaning may affect graded truth-value
-judgments. Strengthening this possibility, they show that graded judgments of
-\as-sentences differ significantly for different instantiations of the
-conditions in \ref{fig:AS-distinguishing-pics}, that vary in the
-amount of connections without changing the assignment of truth values
-to candidate readings. \citeauthor{ChemlaSpector2010:Experimental-Ev}
+and \citeauthor{ChemlaSpector2010:Experimental-Ev} reflect something
+other than (strongly) truth-relevant speaker-intended meaning
+enrichments after all, so that no case can be made for lexicalism or
+grammaticalism on the basis of these data \citep[c.f.][for arguments
+along these lines]{Tielvan-Tiel2012:Embedded-Scalar}.
+
+Note, however, that the type of judgment is not the only crucial
+difference between the methods of
+\citeauthor{CliftonDube2010:Embedded-Implic} and
+\citeauthor{ChemlaSpector2010:Experimental-Ev} on the one hand and
+\citet{GeurtsPouscoulous2009:Embedded-Implic} on the other. These
+studies also differed with respect to the \emph{types} of situations
+(as distinguished in Figures~\ref{fig:AS-distinguishing-pics}
+and~\ref{fig:ES-distinguishing-pics}) that were shown to the
+participants during the course of the experiment. The presence or
+absence of competing situations may have led to skewed distributions
+of judgments for situations like in Figure \ref{fig:weak}. Such
+effects might emerge simply because the type of sentence-picture
+combinations shown during the experiment affects the standard of
+judgment but could~-- maybe more elegantly~-- also be explained by
+findings from \citet{Raffray2010} suggesting that exposing
+participants to models may prime corresponding logical forms and
+thereby shift reading preferences. Taking these possibilities into
+account, it remains unclear whether the effects reported by
+\citeauthor{CliftonDube2010:Embedded-Implic} and
+\citeauthor{ChemlaSpector2010:Experimental-Ev} would also show up
+using ordinary picture verification, in the first place.
+
+For these reasons, we cannot ascribe the effects reported by
+\citeauthor{CliftonDube2010:Embedded-Implic} and
+\citeauthor{ChemlaSpector2010:Experimental-Ev} to the availability of
+local readings with
+certainty. \citet{ChemlaSpector2010:Experimental-Ev} themselves
+acknowledge the possibility that the \emph{typicality} of a picture
+with respect to some meaning may affect graded truth-value
+judgments. Strengthening this possibility, they show that graded
+judgments of \as-sentences differ significantly for different
+instantiations of the situation types from
+Figure~\ref{fig:AS-distinguishing-pics}, that vary in the amount of
+connections without changing the assignment of truth values to
+candidate readings. \citeauthor{ChemlaSpector2010:Experimental-Ev}
 suggest that typicality of the pictorial material can account for
-these differences, but submit that this does not explain away the
-high acceptance of pictures like Figure \ref{fig:weak}. The latter point is disputed by
-\citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates that a huge chunk of variance in the data of
-\citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} on
-\as-sentences can be explained as typicality effects, dispensing the need to appeal
-to the distribution of different readings. \citet{Tielvan-Tiel2012:Embedded-Scalar} elicited what he calls the typicality
-structures associated with the quantifiers {\it all} and {\it some} and predicted the judgments of \as-sentences obtained by C\&S based
-on these data. Thereby, he obtained an excellent model fit. We are sympathetic towards
-\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
-reinterpretation of the data, but note, as
+these differences, but submit that this does not explain away the high
+acceptance of pictures like Figure \ref{fig:weak}. The latter point is
+disputed by \citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates
+that a huge chunk of variance in the data of
+\citeauthor{CliftonDube2010:Embedded-Implic} and
+\citeauthor{ChemlaSpector2010:Experimental-Ev} on \as-sentences can be
+explained as typicality effects, dispensing the need to appeal to the
+distribution of different
+readings. \citet{Tielvan-Tiel2012:Embedded-Scalar} elicited what he
+calls the typicality structures associated with the quantifiers {\it
+  all} and {\it some} and predicted the judgments of \as-sentences
+obtained by \citeauthor{ChemlaSpector2010:Experimental-Ev} based on
+these data. Thereby, he obtained an excellent model fit. We are
+sympathetic towards \citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s
+innovative line of reinterpretation of the data, but note, as
 \citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
 typicality-based explanation does not extend to \es-sentences in an
-obvious way\fn{For similar reasons, appeal to typicality cannot
-  explain, as far as we can see, the preference for the situation in
-  Figure~\ref{fig:literal-EA} over that in Figure\ref{fig:global-EA}
-  given a sentence like (\ref{bsp:EA}).}.
-
-To conclude, although considerable progress has been made in understanding which factors
-have to be controlled for in order to asses the status of local readings, the evidence about availability,
-preference and nature of local readings is still inconclusive. What is needed to complement
-the picture are data that are sensitive enough to detect local readings even if they
-are strongly dispreferred and are as independent as possible of possibly conflating properties
-of the pictorial material. Given the logical dependencies of the
-relevant readings of \as- and \es-sentences this seems almost
-impossible to achieve. As we will argue below we do, however, believe it is.
-
-On top of this, it would be desirable to obtain further information about
-the relative preferences among all putative readings, so as to be able
-to decide between theoretical positions, as outlined in
+obvious way.
+  % \fn{For similar reasons, appeal to typicality cannot
+  % explain, as far as we can see, the preference for the situation in
+  % Figure~\ref{fig:literal-EA} over that in Figure\ref{fig:global-EA}
+  % given a sentence like (\ref{bsp:EA}).}
+
+To conclude, although considerable progress has been made in
+understanding which factors have to be controlled for in order to
+asses the status of local readings, the evidence about availability,
+preference and nature of local readings is still inconclusive. What is
+needed to complement the picture is data that is as independent as
+possible of potentially conflating properties of the pictorial
+material and that is nonetheless sensitive enough to detect local
+readings even if they are dispreferred. Given the logical dependencies
+of the relevant readings this seems almost impossible to achieve. As
+we will argue below we do, however, believe it is.
+
+On top of this, it would be desirable to obtain further information
+about the relative preferences among all putative readings, so as to
+be able to decide between theoretical positions, as outlined in
 Section~\ref{sec:theories-predictions}. Neither of the previous
@@
 (\citet{GeurtsPouscoulous2009:Embedded-Implic},
-\citet{CliftonDube2010:Embedded-Implic}), or because they cannot safely
-derive the required cardinal information for danger of conflating
+\citet{CliftonDube2010:Embedded-Implic}), or because they cannot
+safely derive the required information for danger of conflating
 preferences for readings with preferences for pictures
-(\citet{ChemlaSpector2010:Experimental-Ev}, our pilot study).
+(\citet{ChemlaSpector2010:Experimental-Ev}).
 
@@
 suggests that numerous factors might influence accent placement and
-prosodic phrasing even while reading, amongst them default accentuation,
-constituent length, rhythmic phenomena, and individual variation
-(Augurzky, 2008; Bader, 1998; Fodor, 2000, 2001; Kentner, 2012, Steinhauer et.
-al., 2001, see also the discussion in Frazier, 2009)\dn{references}.
-
-As it has been suggested in the theoretical literature that the availability
-of a local reading might hinge on the realization of contrastive stress on the
-scalar item, 
+prosodic phrasing even while reading, amongst them default
+accentuation, constituent length, rhythmic phenomena, and individual
+variation (Augurzky, 2008; Bader, 1998; Fodor, 2000, 2001; Kentner,
+2012, Steinhauer et.  al., 2001, see also the discussion in Frazier,
+2009).\dn{references} As it has been suggested in the theoretical
+literature that the availability of a local reading might hinge on the
+realization of contrastive stress on the scalar item,
 %Even traditionalism maintains that local
@@
 
-In each trial participants were first asked to indicate readiness by pressing a button.
-In the {\it no load} condition, after they had pressed the button an  asterisk was flashed on the screen six times within $7.2s$.
-Then a sentence and a picture were presented simultaneously.
-Within $12s$ participants had to judge whether the sentence was true with respect to the picture.
-They indicated their judgment by pressing one of two buttons.
-After they had provided their judgment the next trial started automatically.
-If they did not respond within twelve seconds, the next trial was started.
-Judgments and reaction times were logged.\footnote{In the {\it low load} and {\it high load} condition a trial looked similar to a trial in the {\it no load} condition except for two things.
-Firstly, in the dual task conditions instead of asterisks letters were flashed on the screen.
-Secondly, after finishing the picture verification task a question appeared on the screen probing for a letter.
-Participants had to indicate by pressing a button whether they thought the letter had been present in the array from the beginning of the trial.
-Except for one difference, the {\it memory only} trials were identical to the dual task trials.
-In {\it memory only} trials the picture verification part was replaced with a blank screen.
-That is, in the middle of such trials the screen stayed blank for $5s$.
-}
+In each trial participants were first asked to indicate readiness by
+pressing a button. In the {\it no load} condition, after they had
+pressed the button an asterisk was flashed on the screen six times
+within $7.2s$. Then a sentence and a picture were presented
+simultaneously. Within $12s$ participants had to judge whether the
+sentence was true with respect to the picture. They indicated their
+judgment by pressing one of two buttons. After they had provided their
+judgment the next trial started automatically. If they did not respond
+within twelve seconds, the next trial was started. Judgments and
+reaction times were logged.\footnote{In the {\it low load} and {\it
+    high load} condition a trial looked similar to a trial in the {\it
+    no load} condition except for two things. Firstly, in the dual
+  task conditions instead of asterisks letters were flashed on the
+  screen. Secondly, after finishing the picture verification task a
+  question appeared on the screen probing for a letter. Participants
+  had to indicate by pressing a button whether they thought the letter
+  had been present in the array from the beginning of the
+  trial. Except for one difference, the {\it memory only} trials were
+  identical to the dual task trials. In {\it memory only} trials the
+  picture verification part was replaced with a blank screen. That is,
+  in the middle of such trials the screen stayed blank for $5s$. }
 
@@
 &more info&true&false\\ \midrule
-Step 1&error&\lit&error\\
-Step 2&error&\glb&error\\
-Step 3&-&error&\loc
+Step 1&-&\lit&error\\
+Step 2&-&\glb&error\\
+Step 3&n.a.&error&\loc
 \end{tabular}
@@
 &more info&true&false\\ \midrule
-Step 1&error&error&\glb\\
-Step 2&error&error&\lit\\
-Step 3&-&\loc&error
+Step 1&-&error&\glb\\
+Step 2&-&error&\lit\\
+Step 3&n.a.&\loc&error
 \end{tabular}
@@
   Exactly one of-the bells is with some its semicircles connected.\\
-  \trans Exactly one letter is connected to some of its semicircless.
+  \trans Exactly one bell is connected to some of its semicircless.
 \end{exe}
@@
 bells is already linked to all of its semicircles. The literal reading
-becomes available in \ref{fig:subfig2}, corresponding to a
+can be evaluated in Figure~\ref{fig:subfig2}, where it would trigger a
 \emph{false} response, as there are two bells that are connected to at
@@
 
-In addition to the unambiguous mapping from readings to truth values,
-the present design minimizes graphical effects because there is no
-comparison between different pictures
-\citep[c.f.][]{Tielvan-Tiel2012:Embedded-Scalar}. Moreover, we
-controlled for pictorial effects by introducing control conditions,
-which are described in the next section.\dn{Are we sure that this
-  paragraph needs to go here? this should be mentioned in the
-  motivation preceding this section and in the discussion at the end,
-  no?}
-
-\paragraph{Positional controls.} In order to make sure that subjects understood
-the task, i.e., gave truth-value judgements neither sooner not later
-than at the first possible position in a sequence, we included a set
-of control conditions. These also controlled for response biases that
-are independent of the sentence meaning, but only depend on the
-experimental procedure or on the picture materials. For each of the
-three readings in the \as- and \es-conditions, we constructed an
-unambiguous control sentence as in (\ref{bsp:controls-as}) and
-(\ref{bsp:controls-es}), requiring the same judgement at the identical
-position in the same sequence used for the respective targets. For
-instance, example (\ref{bsp:controls-as-1}) requires a
-\emph{true}-response analogous to the \as-sentence in (\ref{ex:as})
-under its literal reading, (\ref{bsp:controls-as-2}) corresponds to
-the \as-sentence under its global reading and
-(\ref{bsp:controls-as-3}) corresponds to its local reading. With
-regard to the \es-sentences, controls like (\ref{bsp:controls-es-1})
-correspond to the global reading, (\ref{bsp:controls-es-2}) to the
-literal and (\ref{bsp:controls-es-3}) to the local reading. If,
-independently of sentence meaning, there was any bias to respond in a
-certain way at any point in the sequences, this should affect control
-sentences to the same degree as it affects target conditions.
+\paragraph{Positional controls.} In order to make sure that subjects
+understood the task, i.e., gave truth-value judgements neither sooner
+not later than at the first possible position in a sequence, we
+included a set of control conditions. These also controlled for
+response biases that are independent of the sentence meaning, but only
+depend on the experimental procedure or on the picture materials. For
+each of the three readings in the \as- and \es-conditions, we
+constructed an unambiguous control sentence as in
+(\ref{bsp:controls-as}) and (\ref{bsp:controls-es}), requiring the
+same judgement at the identical position in the same sequence used for
+the respective targets. For instance, example
+(\ref{bsp:controls-as-1}) requires a \emph{true}-response analogous to
+the \as-sentence in (\ref{ex:as}) under its literal reading,
+(\ref{bsp:controls-as-2}) corresponds to the \as-sentence under its
+global reading and (\ref{bsp:controls-as-3}) corresponds to its local
+reading. With regard to the \es-sentences, controls like
+(\ref{bsp:controls-es-1}) correspond to the global reading,
+(\ref{bsp:controls-es-2}) to the literal and (\ref{bsp:controls-es-3})
+to the local reading. If, independently of sentence meaning, there was
+any bias to respond in a certain way at any point in the sequences,
+such as to preferably unravel the whole picture, this should affect
+control sentences to the same degree as it affects target conditions.
 
@@
 For each sentence, two sequences were designed. In the first, the
-critical position associated with the dispreferred high-attachment
-reading preceded the critical position for the low-attachment
-reading. In this case, a partly covered graph as in
-Figure~\ref{fig:exec1} preceded a graph as in \ref{fig:exec2}.
+critical position associated with the dispreferred early-closure
+reading preceded the critical position for the preferred late-closure
+reading. In this case, a partly covered picture as in
+Figure~\ref{fig:exec1} preceded a picture as in \ref{fig:exec2}.
 %
@@
 	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=5cm]{../pictures/paper/ec_01_3.pdf}}
+		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/ec_01_3.pdf}}
 	    \label{fig:exec1}
@@
 	\subfloat[][Step 2]{
-		\fbox{\includegraphics[width=5cm]{../pictures/paper/ec_01_5.pdf}}
+		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/ec_01_5.pdf}}
 	    \label{fig:exec2}
@@
 	\caption[]{Critical steps of a sequence for sentence
-          (\ref{bsp:target-related}) where
-          early-closure/high-attachment reading
+          (\ref{bsp:target-related}) where the early-closure reading
           (\ref{bsp:target-related-EC}) can be judged first.}
@@
 %
-If
-participants adopted an early-closure reading as in
+If participants adopted an early-closure reading as in
 (\ref{bsp:target-related-EC}), a \emph{false}-judgment would be
@@
 	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=5cm]{../pictures/paper/lc_01_3.pdf}}
+		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/lc_01_3.pdf}}
 	    \label{fig:exlc1}
@@
 	\subfloat[][Step 2]{
-		\fbox{\includegraphics[width=5cm]{../pictures/paper/lc_01_6.pdf}}
+		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/lc_01_6.pdf}}
 	    \label{fig:exlc2}
@@
 	\caption[]{Critical steps of a sequence for sentence
-          (\ref{bsp:target-related}) where
-          late-closure/low-attachment reading
+          (\ref{bsp:target-related}) where the late-closure reading
           (\ref{bsp:target-related-LC}) can be judged first.}
@@
 
-We constructed a set of 15 items for \as- and \es-sentences, respectively,
-analogous to the examples in \ref{ex:as} and \ref{ex:es}. Sentences were
-introduced by a subject {\small \acro{DP}}, including the quantifiers 
-{\it alle diese} ("all of these") or {\it genau einer der} ("exactly 
-one of these"), as well as the head noun which denoted different icons, 
-such as letters or bells. Subjects were followed by an auxiliary, and 
-a {\small \acro{PP}} containing {\it einige}, a possessive pronoun, and a noun denoting 
-a geometrical object, e.g. {\it einigen seiner Dreiecke/Quadrate} ("some of its triangles/squares"). The possessive pronoun was used in order to fix relative 
-quantifier scope to surface scope, thus ensuring that {\it einige} has 
-embedded status. The last word was the main verb {\it verbunden} ("connected"). 
-Each sentence was recorded  in a stressed and an unstressed version of scalar 
-{\it einige} (see section xx  below). As described above, three control sentences were created 
-for each experimental item, corresponding to the critical positions
-in the course of uncovering the accompanying sequences (see below).
-The positional controls were recorded with neutral prosody.  Items
-were evenly distributed across 5 lists using a Latin square design.
+We constructed a set of 15 items for \as- and \es-sentences,
+respectively, analogous to the examples in \ref{ex:as} and
+\ref{ex:es}. Sentences were introduced by a subject {\small
+  \acro{DP}}, including the quantifiers {\it alle diese} ("all of
+these") or {\it genau eine(r) der} ("exactly one of these"), as well
+as the head noun which denoted different icons, such as letters or
+bells. Subjects were followed by an auxiliary, and a {\small
+  \acro{PP}} containing {\it einige}, a possessive pronoun, and a noun
+denoting a geometrical object, e.g. {\it einigen seiner
+  Dreiecke/Quadrate} ("some of its triangles/squares"). The possessive
+pronoun was used in order to fix relative quantifier scope to surface
+scope, thus ensuring that {\it einige} has embedded status. The last
+word was the main verb {\it verbunden} ("connected").  Each sentence
+was recorded in a stressed and an unstressed version of scalar {\it
+  einige} (see section xx below). As described above, three control
+sentences were created for each experimental item, corresponding to
+the critical positions in the course of uncovering the accompanying
+sequences (see below).  The positional controls were recorded with
+neutral prosody.  Items were evenly distributed across 5 lists using a
+Latin square design.
 
 \paragraph{Preference-related control sentences}
-For controlling preferences, 28 ambiguous Late closure sentences and 28 
-of their disambiguated counterparts were constructed as described  above.
-In these sentences, subject {\small \acro{DP}}s were always denoting icons and were followed
-by an auxiliary. In the ambiguous sentences, the auxiliary was followed by two {\it mit}-{\small \acro{PP}}s.
-The first of these {\small \acro{PP}}s consisted in a coordination of two nouns denoting geometrical 
-objects, whereas the second PP denoted icons. In contrast to these 
-sentences, the unambiguous sentences contained only one PP with a conjunction the first part of which was 
+For controlling preferences, 28 sentences that were ambiguous between
+a late-closure and an early-closure reading, as well as 28 of their
+disambiguated counterparts were constructed as described above. In
+these sentences, subject {\small \acro{DP}}s were always denoting
+icons and were followed by an auxiliary. In the ambiguous sentences,
+the auxiliary was followed by two {\it mit}-{\small \acro{PP}}s.  The
+first of these {\small \acro{PP}}s consisted in a coordination of two
+nouns denoting geometrical objects, whereas the second PP denoted
+icons. In contrast to these sentences, the unambiguous sentences
+contained only one PP with a conjunction the first part of which was
 modified by a relative clause.
@@
 falling pattern. A set of 15 experimental items was recorded for each
-condition (\as vs. \es, \emph{accented} vs.~\emph{unaccented}), resulting in a
+condition (\as vs.~\es, \emph{accented} vs.~\emph{unaccented}), resulting in a
 total number of 60 target sentences.
@@
 boundaries. For each prosodic variant, a set of
-30 items was read, yielding 90 target-related fillers.
+30 items was read, yielding 90 preference-related fillers.
 
@@
 due to lexical differences between the \as and \es-conditions. As
-target-related fillers did not differ with respect to their lexical
+preference-related fillers did not differ with respect to their lexical
 properties, we carried out word-by-word analyses for these
@@
 vs. exactly one) and \acro{Prosody} (accented vs.~unaccented) were
-carried out. For the target-related fillers, we carried out
+carried out. For the preference-related fillers, we carried out
 one-factorial \acros{anova} with the factor \acro{Prosody} (early
@@
 The details of these analyses are found in
-Appendix~\ref{sec:audit-sent-mater}.
-In sum, our speaker reliably produced (i) differences in accent realization for the target sentences and (ii) the expected boundary realizations for the preference-related controls.
-Whereas accented elements clearly differed from their unaccented counterpart by showing an increase in duration and F0 range, prosodic boundaries for our target-related fillers were realized by pre-final lengthening
-(i.e. an increase in F0 and duration at the position preceding the boundary).
+Appendix~\ref{sec:audit-sent-mater}. In sum, our speaker reliably
+produced (i) differences in accent realization for the target
+sentences and (ii) the expected boundary realizations for the
+preference-related controls. Whereas accented elements clearly
+differed from their unaccented counterpart by showing an increase in
+duration and F0 range, prosodic boundaries for our preference-related
+fillers were realized by pre-final lengthening (i.e. an increase in F0
+and duration at the position preceding the boundary).
 
 \paragraph{Pictures.}
-The visual sequences accompanying each sentence consisted of pictures comparable to those illustrated in Figure \ref{fig:InitialPicture}.
-In each picture, four alternative sub-scenarios were presented, in which an icon was surrounded by six geometrical shapes.
-Depending on the sentence material, shapes and icons differed across sentence types and conditions.
-For example, in our target conditions, 4 identical icons were surrounded by geometrical shapes that were all of the same type, whereas various iconds and surrounding elements were used in each sequence of the preference-related control structures.
-As described in section xx, grey colour initially covered the links between icons and shapes.
-As the connections were to be uncovered step by step, different pictures were designed corresponding to different stages in the uncovering process.
-Note that the single conditions impose distinct requirements on sequences.
-For instance, inherent entailment relations between \as-sentences and \es-sentences lead to different critical positions at which participants can make their judgments.
-We will therefore describe the sequences for each condition separately.
-
-For \as-sentences, as well as for the corresponding positional control sentences described in Section \ref{sec:design}, we designed a set of seven pictures for each trial.
-In each sequence, the critical position associated with the literal meaning was presented at the third step, the position associated with the global meaning was shown at the fifth step, and the local reading was presented at the final step (see Figure \ref{fig:exseqAS} for an illustration of the critical positions).
-Pictures that were interspersed between these positions served as spillover-pictures.
-These were used in order to control for potentially delayed judgments and they additionally served as distractor items.
-
-Sequences in the \es conditions (and their respective positional controls) consisted of a set of five pictures with the following critical positions.
-The critical positions as illustrated in Figure \ref{fig:exseqES} are associated with the second picture (global reading), the third picture (literal reading), as well as with the final picture (local reading).
-
-For the preference-related controls, we used two types of sequences.
-First, a sequence in which the crirical position for the (preferred) Late Closure reading was presented preceding the critical position for the Early Closure reading ({\it LC sequence}), and second, a sequence in which the readings were presented in reversed order ({\it EC sequence}.
-In the LC sequences, seven pictures were presented, with the LC reading given at the third picture, aand the EC reading at the sixth picture.
-EC sequences consisted of five pictures, in which the critical positions were realized at the third picture (EC reading) and at the fifth picture (LC reading).
-
-Finally, we added pictures compatible with unrelated fillers with critical position at random uncovering stages.
+The visual sequences accompanying each sentence consisted of pictures
+comparable to those illustrated in Figure \ref{fig:InitialPicture}. In
+each picture, four alternative sub-scenarios were presented, in which
+an icon was surrounded by six geometrical shapes. Depending on the
+sentence material, shapes and icons differed across sentence types and
+conditions. For example, in our target conditions, 4 identical icons
+were surrounded by geometrical shapes that were all of the same type,
+whereas various icons and surrounding elements were used in each
+sequence of the preference-related control structures. As described in
+section xx, grey colour initially covered the links between icons and
+shapes. As the connections were to be uncovered step by step,
+different pictures were designed corresponding to different stages in
+the uncovering process. Note that the single conditions impose
+distinct requirements on sequences. For instance, inherent entailment
+relations between \as-sentences and \es-sentences lead to different
+critical positions at which participants can make their judgments. We
+will therefore describe the sequences for each condition separately.
+
+For \as-sentences, as well as for the corresponding positional control
+sentences described in Section \ref{sec:design}, we designed a set of
+seven pictures for each trial. In each sequence, the critical position
+associated with the literal meaning was presented at the third step,
+the position associated with the global meaning was shown at the fifth
+step, and the local reading was presented at the final step (see
+Figure \ref{fig:exseqAS} for an illustration of the critical
+positions). Pictures that were interspersed between these positions
+served as spillover-pictures. These were used in order to control for
+potentially delayed judgments and they additionally served as
+distractor items.
+
+Sequences in the \es conditions (and their respective positional
+controls) consisted of a set of five pictures with the following
+critical positions. The critical positions as illustrated in Figure
+\ref{fig:exseqES} are associated with the second picture (global
+reading), the third picture (literal reading), as well as with the
+final picture (local reading).
+
+For the preference-related controls, we used two types of
+sequences. First, a sequence in which the crirical position for the
+(preferred) Late Closure reading was presented preceding the critical
+position for the Early Closure reading ({\it LC sequence}), and
+second, a sequence in which the readings were presented in reversed
+order ({\it EC sequence}. In the LC sequences, seven pictures were
+presented, with the LC reading given at the third picture, and the EC
+reading at the sixth picture. EC sequences consisted of five pictures,
+in which the critical positions were realized at the third picture (EC
+reading) and at the fifth picture (LC reading).
+
+Finally, we added pictures compatible with unrelated fillers with
+critical position at random uncovering stages, including cases where
+no uncovering was needed for a truth-value judgement.
 
 \paragraph{Lists.}
-Experimental items and preference-related fillers were evenly distributed across lists.
-For the \as- and \es-sentences together with their respective controls, five lists were used employing a Latin square design.
-Picture sentence-pairs for the preference-related controls were spread across eight lists.
-Each target list was combined with each list from the preference-related controls, thus yielding to a total of forty lists.
-The thirty unrelated filler items were included in each of these resulting lists.
+Experimental items and preference-related fillers were evenly
+distributed across lists. For the \as- and \es-sentences together with
+their respective controls, five lists were used employing a Latin
+square design. Picture sentence-pairs for the preference-related
+controls were spread across eight lists. Each target list was combined
+with each list from the preference-related controls, thus yielding to
+a total of forty lists. The thirty unrelated filler items were
+included in each of these resulting lists.
 
@@
   target conditions in Experiment 1. Relative frequency of
-  yes/no-judgments is plotted against the position within the
-  trial. In the \as-conditions there were seven positions. On the
-  third position a yes-judgment corresponded to a literal reading,
-  while on the fith position a yes-judgment corresponded to a global
-  reading.  A no-judgment on the seventh position was only consistent
-  with a local reading. The \es-conditions had five
-  positions. No- judgments on positions two and three corresponded to
-  global and literal readings, respectively. A yes-judgment on the
-  last segment corresponded to a local reading. }
+  \emph{yes}/\emph{no} judgments is plotted against the position
+  within the trial. In the \as-conditions there were seven
+  positions. On the third position a \emph{yes} judgment corresponded
+  to a literal reading, while on the fith position a \emph{yes}
+  judgment corresponded to a global reading.  A \emph{no} judgment on
+  the seventh position was only consistent with a local reading. The
+  \es-conditions had five positions. \emph{No} judgments on positions
+  two and three corresponded to global and literal readings,
+  respectively. A \emph{yes} judgment on the last segment corresponded
+  to a local reading.}
 \label{fig:JudgmentsK2}
@@
 if they were as expected under one of these readings and as {\it
-  error} if not. The distribution of readings as coded by us is
-presented in Figure~\ref{fig:JudgementPercentages}.
+  error} if not. The distribution of readings thus coded is presented
+in Figure~\ref{fig:JudgementPercentages}.
 %
@@
 \centering
-\subfloat[][\as-Conditions]{
+\subfloat[][\as-condition]{
 \begin{tikzpicture}[scale=0.8]
@@
         ylabel={\% of answers}, symbolic x
-        coords={ae-ntr,ae-acc}, xtick=data, nodes
-        near coords, nodes near coords align={vertical},x=65, bar width=3mm, ymin = 8 ]
-
-        \addplot coordinates {(ae-ntr,73) (ae-acc,70)};
-
-        \addplot coordinates {(ae-ntr,23) (ae-acc,22)};
-
-        \addplot coordinates {(ae-ntr,1) (ae-acc,2)};
-
-        \addplot coordinates {(ae-ntr,4) (ae-acc,6)};
+        coords={neutral,accented}, xtick=data, nodes
+        near coords, nodes near coords align={vertical},x=65, bar
+        width=3mm, ymin = 8, ymax = 73 ]
+
+        \addplot coordinates {(neutral,73) (accented,70)};
+
+        \addplot coordinates {(neutral,23) (accented,22)};
+
+        \addplot coordinates {(neutral,1) (accented,2)};
+
+        \addplot coordinates {(neutral,4) (accented,6)};
 
@@
 
-        \legend{literal, local, global, false}
+        \legend{literal, local, global, error}
 
@@
 }
-\subfloat[][\es-Conditions]{
+\subfloat[][\es-condition]{
 \begin{tikzpicture}[scale=0.8]
@@
                ylabel={\% of answers}, 
-               symbolic x coords={ge-ntr,ge-acc}, 
+               symbolic x coords={neutral,accented}, 
                xtick=data,
@@
                x=65, bar width=3mm,
-               ymin = 8
+               ymin = 8, ymax = 73
                ]
 
-    \addplot coordinates {(ge-ntr,47) (ge-acc,49)};
-
-    \addplot coordinates {(ge-ntr,29) (ge-acc,23)};
-
-    \addplot coordinates {(ge-ntr,0) (ge-acc,1)};
-
-    \addplot coordinates {(ge-ntr,25) (ge-acc,27)};
+    \addplot coordinates {(neutral,47) (accented,49)};
+
+    \addplot coordinates {(neutral,29) (accented,23)};
+
+    \addplot coordinates {(neutral,0) (accented,1)};
+
+    \addplot coordinates {(neutral,25) (accented,27)};
 
@@
 
-    \legend{literal, local, global, false}
+    \legend{literal, local, global, error}
 
@@
 }
-\caption[Optional caption for list of figures]{Judgments}
+\caption[Optional caption for list of figures]{Response type
+  frequencies for target conditions}
 \label{fig:JudgementPercentages}
@@
 obtained. In the \as-conditions participants made hardly any errors,
-whereas the amount of errors was slightly greater in the
+whereas the amount of errors was considerably larger in the
 \es-conditions.
@@
 literal readings were given in 47.2\% and 44.7\% of the trials with
-neutral and accented prosody, respectively. Global readings were
+neutral and accented prosody respectively. Global readings were
 observed in 0.8\% of the trials in both the neutral and the accented
@@
 
-Unsurprisingly, there was an effect of reading ($LRCS_1=364.77, df_1 =
-3, p_1<.001, LRCS_2=364.77, df_2 = 3, p_1<.001,$) because overall the
-readings were distributed inhomogeneously (sse Figure
+Unsurprisingly, there was an effect of \emph{Reading} ($LRCS_1=364.77,
+df_1 = 3, p_1<.001, LRCS_2=364.77, df_2 = 3, p_1<.001,$) because
+overall the readings were distributed inhomogeneously (see Figure
 \ref{fig:ReadingsGE}). The quantifier had an influence on the
@@
 interaction was due to the higher number of errors and lower number of
-literal readings in the \es-conditions as compared with
-the \as-conditions. A difference in the distribution of judgment
-types between participants was revealed by a reliable interaction of
-{\it Reading} and {\it Participant} ($LRCS_1=487.70, p_1<.01$). We
-were interested in whether this effect was due to some of the
-participants being more likely to choose literal readings than
-others. Finally, there was a three-way interaction of {\it
-  Participants}, {\it Construction} and {\it Reading} ($LRCS_1, =
-143.92, df_1 = 117, p_1<.05$) which could stem from to the fact that
-some participants were more prone than others to make errors in the
-\es-conditions.
+literal readings in the \es-conditions as compared with the
+\as-conditions. A difference in the distribution of judgment types
+between participants was revealed by a reliable interaction of {\it
+  Reading} and {\it Participant} ($LRCS_1=487.70, p_1<.01$). We were
+interested in whether this effect was due to some of the participants
+being more likely to choose literal readings than others. Finally,
+there was a three-way interaction of {\it Participants}, {\it
+  Construction} and {\it Reading} ($LRCS_1, = 143.92, df_1 = 117,
+p_1<.05$) which could stem from to the fact that some participants
+were more prone than others to make errors in the \es-conditions.
 
@@
 there are indeed varying preferences for local readings among German
-speakers. Further examination of the distribution of local readings
-revealed a clear pattern (see Figure
-\ref{fig:HistogramLocalReadingsK2}). In all four conditions, about
-seven out of the 40 participants ($16\%$) were consistently giving
-judgments that indicate local readings. Further, the relative
-frequency of local judgments per participant strongly correlated
-between all four conditions (all $r>.6, p<.001$). Appart from the
-localists about half of the participants (and 41.5\% of all
+speakers (see Table~\ref{table:answer-types-as}).
+%
+\begin{table}[t]
+  \centering
+      \begin{tabular}{lccc}
+      & \multicolumn{3}{c}{\es} \\ \cmidrule(r){2-4}
+      \as & literalist & localist & incons. \\ \midrule
+      literalist   & 19 & 2 & 6\\
+      localist     &  0 & 7 & 0 \\
+      incons. &  2 & 1 & 1\\
+    \end{tabular}
+    \caption{Contingency table showing the number of occurrences of
+      \emph{response types} in the \as- and \es-conditions with
+      neutral intonation. \emph{Literalists} are subjects who gave
+      responses that were classified as either a literal response or
+      an error; \emph{localist} are subjects who gave responses
+      that were classified as either a 
+      local response or an error. Subjects who gave at least two
+      responses from different categories (literal, global, local) are
+      classified as \emph{inconsistent}. (No subject's responses where
+      errors exclusively and there where no \emph{globalists}, as
+      defined in parallel fashion.)}
+    \label{table:answer-types-as}
+\end{table}
+%
+Further examination of the distribution of local readings revealed a
+clear pattern (see Figure \ref{fig:HistogramLocalReadingsK2}). In all
+four conditions, about seven out of the 40 participants ($16\%$) were
+consistently giving judgments that indicate local readings.\dn{please
+  check numbers; this cannot be true!?} Further,
+the relative frequency of local judgments per participant strongly
+correlated between all four conditions (all $r>.6, p<.001$). Appart
+from the localists about half of the participants (and 41.5\% of all
 participants) were consistently giving judgments that indicate literal
@@
 \as-conditions than in the \es-conditions. The number of consistent
-litaralists was lower in the \es-conditions (25.6\%) as compared to
+literalists was lower in the \es-conditions (25.6\%) as compared to
 the \as-conditions (57.3\%). Also, the number of participants that
-showed inconsitency was higher in these conditions. However, the
+showed inconsistency was higher in these conditions. However, the
 number of consistent localists did hardly differ between
 constructions.
+
+\begin{figure}[h]
+\centering
+\subfloat[][\as-accented]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_AKZ.jpg}
+\label{fig:ReadingsAE}
+}
+\subfloat[][\as-neutral]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_NTR.jpg}
+\label{fig:ReadingsGE}
+}
+
+\subfloat[][\es-accented]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_AKZ.jpg}
+\label{fig:ReadingsAE}
+}
+\subfloat[][\es-neutral]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_NTR.jpg}
+\label{fig:ReadingsGE}
+}
+\label{fig:HistogramLocalReadingsK2}
+\caption[]{Judgments for the four target conditions}
+\end{figure}
 
@@
 1, p=.65$).
-
-\begin{figure}[h]
-\centering
-\subfloat[][\as-accented]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_AKZ.jpg}
-\label{fig:ReadingsAE}
-}
-\subfloat[][\as-neutral]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_NTR.jpg}
-\label{fig:ReadingsGE}
-}
-
-\subfloat[][\es-accented]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_AKZ.jpg}
-\label{fig:ReadingsAE}
-}
-\subfloat[][\es-neutral]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_NTR.jpg}
-\label{fig:ReadingsGE}
-}
-\label{fig:HistogramLocalReadingsK2}
-\caption[Optional caption for list of figures]{Judgments for the four target conditions}
-\end{figure}
 
@@
 
-\paragraph{Target-related fillers.} Table~\ref{tab:table-C} shows the
+\paragraph{Preference-related fillers.} Table~\ref{tab:table-C} shows the
 durational values of each of the single words in the sentence. As is
@@
   \caption{Durational values in ms for each of the single regions in
-    the target-related fillers. Regions 5 and 7 correspond to the
+    the preference-related fillers. Regions 5 and 7 correspond to the
     nouns preceding the boundaries.}  

### 2012-08-05 text/paper/paper1.tex
start on discussion section

@@
                  legend columns=-1}, 
-               ylabel={\% of answers}, 
+               % ylabel={\% of answers}, 
                symbolic x coords={neutral,accented}, 
@@
 consistently giving judgments that indicate local readings.\dn{please
-  check numbers; this cannot be true!?} Further,
-the relative frequency of local judgments per participant strongly
-correlated between all four conditions (all $r>.6, p<.001$). Appart
-from the localists about half of the participants (and 41.5\% of all
-participants) were consistently giving judgments that indicate literal
-readings. Only a minority of participants exhibited
-inconsistency. Reading preferences were more clear-cut in the
-\as-conditions than in the \es-conditions. The number of consistent
-literalists was lower in the \es-conditions (25.6\%) as compared to
-the \as-conditions (57.3\%). Also, the number of participants that
-showed inconsistency was higher in these conditions. However, the
-number of consistent localists did hardly differ between
-constructions.
+  check numbers; this cannot be true!? not accross all four
+  conditions} Further, the relative frequency of local judgments per
+participant strongly correlated between all four conditions (all
+$r>.6, p<.001$). Appart from the localists about half of the
+participants (and 41.5\% of all participants) were consistently giving
+judgments that indicate literal readings. Only a minority of
+participants exhibited inconsistency. Reading preferences were more
+clear-cut in the \as-conditions than in the \es-conditions. The number
+of consistent literalists was lower in the \es-conditions (25.6\%) as
+compared to the \as-conditions (57.3\%). Also, the number of
+participants that showed inconsistency was higher in these
+conditions. However, the number of consistent localists did hardly
+differ between constructions.
 
@@
 
+\paragraph{Preference-related controls}
+
+\begin{itemize}
+\item see Figure~\ref{fig:response-type-freque-TRF}
+\end{itemize}
+
+\begin{figure}[t]
+  \centering
+  \subfloat[][\LC-condition]{
+        \begin{tikzpicture}[scale=0.8]
+
+  \begin{axis}[ybar, 
+               enlarge x limits=0.5,
+               enlarge y limits=0.25, 
+               legend style={at={(0.5,-0.15)},
+                 anchor=north,
+                 legend columns=-1}, 
+               ylabel={\% of answers}, 
+               symbolic x coords={neutral,LC-pref,EC-pref}, 
+               xtick=data,
+               nodes near coords,
+               nodes near coords align={vertical},
+               x = 45, 
+               bar width = 3mm,
+               ymin = 8
+               ]
+
+    \addplot coordinates {(neutral, 69) (LC-pref, 77) (EC-pref, 52)};
+
+    \addplot coordinates {(neutral, 24) (LC-pref, 12) (EC-pref, 30)};
+
+    \addplot coordinates {(neutral, 7) (LC-pref, 11) (EC-pref, 19)};
+
+    % \addplot coordinates {(l-ntr, 93) (l-l, 101) (l-e, 70) (e-ntr, 85)
+    %   (e-l, 100) (e-e, 75)};
+
+    % \addplot coordinates {(l-ntr, 33) (l-l, 16) (l-e, 40) (e-ntr, 34)
+    %   (e-l, 16) (e-e, 43)};
+
+    % \addplot coordinates {(l-ntr, 9) (l-l, 14) (l-e, 25) (e-ntr, 16)
+    %   (e-l, 15) (e-e, 17)};
+
+    \legend{LC, EC, error}
+
+  \end{axis}
+
+\end{tikzpicture}
+  }
+  \subfloat[][\ec-condition]{
+    \begin{tikzpicture}[scale=0.8]
+
+  \begin{axis}[ybar, 
+               enlarge x limits=0.5, 
+               enlarge y limits=0.25, 
+               legend style={at={(0.5,-0.15)},
+                 anchor=north,
+                 legend columns=-1}, 
+               % ylabel={\% of answers}, 
+               symbolic x coords={neutral,LC-pref,EC-pref}, 
+               xtick=data,
+               nodes near coords,
+               nodes near coords align={vertical},
+               x = 45, 
+               bar width = 3mm,
+               ymin = 8
+               ]
+
+    \addplot coordinates {(neutral, 63)
+      (LC-pref, 76) (EC-pref, 56)};
+
+    \addplot coordinates {(neutral, 25)
+      (LC-pref, 12) (EC-pref, 32)};
+
+    \addplot coordinates {(neutral, 12)
+      (LC-pref, 11) (EC-pref, 13)};
+
+    % \addplot coordinates {(l-ntr, 93) (l-l, 101) (l-e, 70) (e-ntr, 85)
+    %   (e-l, 100) (e-e, 75)};
+
+    % \addplot coordinates {(l-ntr, 33) (l-l, 16) (l-e, 40) (e-ntr, 34)
+    %   (e-l, 16) (e-e, 43)};
+
+    % \addplot coordinates {(l-ntr, 9) (l-l, 14) (l-e, 25) (e-ntr, 16)
+    %   (e-l, 15) (e-e, 17)};
+
+    \legend{LC, EC, error}
+
+  \end{axis}
+
+\end{tikzpicture}
+}
+  \caption{Response type frequences for preference-related controls}
+  \label{fig:response-type-freque-TRF}
+\end{figure}
+
 \subsection{Discussion}
 \label{sec:discussion}
+
+\newcommand{\ivt}{\acro{ivt}}
+
+High scores of success in our general control condition clearly
+indicate that participants understood the incremental verification
+task and were in general able to give judgements at the earliest
+possible point in a picture sequence. Results obtained for the
+preference-related target conditions moreover show that our design is
+able to detect multiple readings and preferences on these. Crucially,
+the amount of response types for \lc- and \ec-readings reflected the
+known preference for the former, irrespective of the order in which
+each reading could first be judged in a given sequence. Given this,
+the best and most straightforward explanation of the observed response
+type frequencies in our target condition is the hypothesis that the
+actual preferences among readings for both \as- and \es-sentences
+alike are:
+\begin{exe}
+  \ex \label{bsp:observed-preferences} \lit \ > \ \loc \ \ ( > \glb)
+\end{exe}
+where it is unclear whether the global readings are entirely
+unavailable or simply severely dispreferred. Crucially, our data does
+attest local readings, albeit that they are not preferred across the
+board but preferred, as it seems, only by a small, but substantial
+number of consistent localists.
+
+On the face of it, there is a very clear winner among the stylized
+candidate theories that we introduced in
+Section~\ref{sec:theories-predictions}. Assuming that global readings
+are not available at all, the preference pattern in
+(\ref{bsp:observed-preferences}) is exactly what \emph{literalism}
+would predict. Remember that literalism was the conventionalist
+position which posited a lexical ambiguity of scalar \emph{some} with
+a preference for the semantically weaker meaning \emph{some and maybe
+  all} over the upper-bounded reading \emph{some but not all}.
 

### 2012-08-06 text/paper/paper1.tex
discussion section sec com

@@
 preferred over global readings which in turn are preferred over
-literal readings; for \es-sentences strong grammaticalism predicts
-that global readings are most preferred, while literal and local
-readings are not ranked with respect to preference. Strong
-grammaticalism, on the other hand, predicts that both \as- and
-\es-sentences preferably get either a local or a global reading rather
-than a literal reading. But strong grammaticalism does not rank these
-former two with respect to each other because they differ in more than
-one application of the $\exh(\cdot)$ operator.
+literal readings; for \es-sentences weak grammaticalism predicts that
+global readings are most preferred, while literal and local readings
+are not ranked with respect to preference. Strong grammaticalism, on
+the other hand, predicts that \as-sentences preferably get either a
+local or a global reading rather than a literal reading, but does not
+rank these former two with respect to each other because they differ
+in more than one application of the $\exh(\cdot)$ operator. For
+\es-sentences, then, strong grammaticalism does not predict \emph{any}
+preference relations between candidate readings at all.
 
@@
     & \glb, \loc > \lit 
-    & \glb, \loc >  \lit
+    & \glb, \loc , \lit
     \\
@@
 possible point in a picture sequence. Results obtained for the
-preference-related target conditions moreover show that our design is
-able to detect multiple readings and preferences on these. Crucially,
-the amount of response types for \lc- and \ec-readings reflected the
-known preference for the former, irrespective of the order in which
+preference-related controls moreover show that our design is able to
+detect multiple readings and preferences among these. Crucially, the
+amount of response types for \lc- and \ec-readings reflected the known
+preference for the former, \emph{irrespective} of the order in which
 each reading could first be judged in a given sequence. Given this,
-the best and most straightforward explanation of the observed response
-type frequencies in our target condition is the hypothesis that the
-actual preferences among readings for both \as- and \es-sentences
-alike are:
+the best and most straightforward explanation of the observed data is
+the hypothesis that the actual preferences among readings for both
+\as- and \es-sentences alike are:
 \begin{exe}
@@
 number of consistent localists.
+
+This is bad news for both traditionalism and grammaticalism, as no
+version of either would predict the pattern in
+(\ref{bsp:observed-preferences}). The main problem is that
+traditionalism, if left on its own, fails to predict local readings,
+while grammaticalism, when it relies on the strongest meaning
+hypothesis, fails to predict the preference order altogether. What are
+the problems exactly? Could either position be aided by innocuous
+auxiliary assumptions to be compatible with
+(\ref{bsp:observed-preferences})?
+
+It is not a major obstacle for traditionalism to predict that global
+readings are available. The weak variety of traditionalism holds that
+the extra assumptions needed to derive global readings are not
+standardly available, and so traditionalism is compatible with a lack
+of observed global readings. Alternatively, traditionalists could
+argue that the task's rather high processing demands lead to a
+suppression of global implicature readings, in line with the findings
+of \citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
+load negatively affects the number of scalar implicature responses in
+sentence verification tasks. Unfortunately, to the extent that global
+readings are explained away, traditionalism also looses the
+possibility of accounting for local readings of \as-sentences in its
+unrestricted variety.\fn{Remember that what we called unrestricted
+  traditionalism can account for local readings of \as-sentences by
+  assuming that a sentence of the form \emph{Some of the $X$ are
+    related to some of the $Y$} is a feasible alternative.} This is
+because unrestricted traditionalism explains local and global readings
+of \as-sentences in essentially the same manner. On top of that,
+traditionalism cannot explain local readings for \es-sentences at
+all. In sum, traditionalism alone cannot explain
+(\ref{bsp:observed-preferences}), but needs an additional explanation
+of local readings for \emph{both} \as- \emph{and} \es-sentences.
+
+Grammaticalism, on the other hand, fails to predict the preference
+relation in (\ref{bsp:observed-preferences}), because these strictly
+contradict the strongest meaning hypothesis in either of its suggested
+varieties.
+
+\bigskip
 

### 2012-08-06 text/paper/paper1.tex
discussion section sec com

@@
 sentence verification tasks. Unfortunately, to the extent that global
-readings are explained away, traditionalism also looses the
-possibility of accounting for local readings of \as-sentences in its
-unrestricted variety.\fn{Remember that what we called unrestricted
-  traditionalism can account for local readings of \as-sentences by
-  assuming that a sentence of the form \emph{Some of the $X$ are
-    related to some of the $Y$} is a feasible alternative.} This is
-because unrestricted traditionalism explains local and global readings
-of \as-sentences in essentially the same manner. On top of that,
-traditionalism cannot explain local readings for \es-sentences at
-all. In sum, traditionalism alone cannot explain
-(\ref{bsp:observed-preferences}), but needs an additional explanation
-of local readings for \emph{both} \as- \emph{and} \es-sentences.
+readings are explained away as dispreferred or unavailable,
+traditionalism also looses the possibility of accounting for local
+readings of \as-sentences in its unrestricted variety.\fn{Remember
+  that what we called unrestricted traditionalism can account for
+  local readings of \as-sentences by assuming that a sentence of the
+  form \emph{Some of the $X$ are related to some of the $Y$} is a
+  feasible alternative.} This is because unrestricted traditionalism
+explains local and global readings of \as-sentences in essentially the
+same manner. On top of that, traditionalism cannot explain local
+readings for \es-sentences at all. In sum, traditionalism alone cannot
+explain (\ref{bsp:observed-preferences}), but needs an additional
+explanation of local readings for \emph{both} \as- \emph{and}
+\es-sentences.
 
@@
 relation in (\ref{bsp:observed-preferences}), because these strictly
-contradict the strongest meaning hypothesis in either of its suggested
-varieties.
+contradict the strongest meaning hypothesis in either of the two
+varieties suggested by \citet{ChierchiaFox2008:The-Grammatical}. This
+shows most clearly in the fact that both versions of the strongest
+meaning hypothesis predict that local readings of \as-sentences are
+preferred over literal ones. The problem, therefore, seems to be the
+selection of readings by the strongest meaning hypothesis. In fact, if
+(\ref{bsp:observed-preferences}) is the actual preference over
+readings, then the strongest meaning hypothesis is also conceptually
+on the wrong track, because no account that merely looks at the
+logical strengths of readings can plausibly predict the preference
+pattern in (\ref{bsp:observed-preferences}) for both \as- and
+\es-sentences at the same time. (Try, if you please!) Turning away
+from comparisons of logical strength, a selection criterion that
+produces (\ref{bsp:observed-preferences}) is ready at hand: if we
+assume that each insertion of $\exh(\cdot)$ operator is \emph{costly}
+anti-proportional to the depth of its embedding, then we derive a
+preference of literal readings over local ones over global ones. But
+whether such an economy principle is sound and in line with further
+empirical data is an interesting matter of further investigation. What
+it does not explain in any case, is why some subjects in our study
+gave local responses \emph{consistently}, while others did not. In
+sum, in as far as grammaticalism depends on the strongest meaning
+hypothesis, its predictive success is equally thin as that of
+traditionalism.
 

### 2012-08-07 text/paper/paper1.tex
discussion sec com

@@
 where it is unclear whether the global readings are entirely
-unavailable or simply severely dispreferred. Crucially, our data does
-attest local readings, albeit that they are not preferred across the
-board but preferred, as it seems, only by a small, but substantial
-number of consistent localists.
+unavailable or simply severely dispreferred. Crucially, our data
+attests local readings independently of a stress accent on the
+embedded scalar item, albeit that local readings are not preferred to
+literal readings and given, as it seems, only by a small, but
+substantial number of consistent localists.
 
@@
 while grammaticalism, when it relies on the strongest meaning
-hypothesis, fails to predict the preference order altogether. What are
-the problems exactly? Could either position be aided by innocuous
-auxiliary assumptions to be compatible with
-(\ref{bsp:observed-preferences})?
-
-It is not a major obstacle for traditionalism to predict that global
-readings are available. The weak variety of traditionalism holds that
-the extra assumptions needed to derive global readings are not
-standardly available, and so traditionalism is compatible with a lack
-of observed global readings. Alternatively, traditionalists could
-argue that the task's rather high processing demands lead to a
-suppression of global implicature readings, in line with the findings
-of \citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
-load negatively affects the number of scalar implicature responses in
-sentence verification tasks. Unfortunately, to the extent that global
-readings are explained away as dispreferred or unavailable,
-traditionalism also looses the possibility of accounting for local
-readings of \as-sentences in its unrestricted variety.\fn{Remember
-  that what we called unrestricted traditionalism can account for
-  local readings of \as-sentences by assuming that a sentence of the
-  form \emph{Some of the $X$ are related to some of the $Y$} is a
-  feasible alternative.} This is because unrestricted traditionalism
-explains local and global readings of \as-sentences in essentially the
-same manner. On top of that, traditionalism cannot explain local
-readings for \es-sentences at all. In sum, traditionalism alone cannot
-explain (\ref{bsp:observed-preferences}), but needs an additional
-explanation of local readings for \emph{both} \as- \emph{and}
-\es-sentences.
+hypothesis, fails to predict the right preference order. Let's look
+more closely at each position in turn.
+
+As for traditionalism, it is not a major obstacle for this position to
+predict that global readings are available. The weak variety of
+traditionalism holds that the extra assumptions needed to derive
+global readings are not standardly available, and so traditionalism is
+compatible with a lack of observed global readings. Alternatively,
+traditionalists could argue that the task's rather high processing
+demands lead to a suppression of global readings, in line with the
+findings of \citet{NeysDe-NeysSchaeken2007:When-People-Are} that
+working memory load negatively affects the number of scalar
+implicature responses in sentence verification tasks. Unfortunately,
+to the extent that global readings are explained away as dispreferred
+or unavailable, traditionalism also looses the possibility of
+accounting for local readings of \as-sentences in its unrestricted
+variety.\fn{Remember that what we called unrestricted traditionalism
+  can account for local readings of \as-sentences by assuming that a
+  sentence of the form \emph{Some of the $X$ are related to some of
+    the $Y$} is a feasible alternative.} This is because unrestricted
+traditionalism explains local and global readings of \as-sentences in
+essentially the same manner. On top of that, traditionalism cannot
+explain local readings for \es-sentences. Since our design presented
+sentence material auditorily, the traditionalist cannot resort to
+effects of silent intonation to explain these local readings
+away. Local readings showed on the neutral accentuation case as
+well. Notice that it is not a problem for this argument that the local
+responses were not emphasized with a contrastive stress on the
+embedded scalar. In sum, traditionalism alone cannot explain
+(\ref{bsp:observed-preferences}), but needs an additional explanation
+of local readings for \emph{both} \as- \emph{and} \es-sentences.
 
@@
 pattern in (\ref{bsp:observed-preferences}) for both \as- and
-\es-sentences at the same time. (Try, if you please!) Turning away
-from comparisons of logical strength, a selection criterion that
-produces (\ref{bsp:observed-preferences}) is ready at hand: if we
-assume that each insertion of $\exh(\cdot)$ operator is \emph{costly}
-anti-proportional to the depth of its embedding, then we derive a
-preference of literal readings over local ones over global ones. But
-whether such an economy principle is sound and in line with further
-empirical data is an interesting matter of further investigation. What
-it does not explain in any case, is why some subjects in our study
-gave local responses \emph{consistently}, while others did not. In
-sum, in as far as grammaticalism depends on the strongest meaning
-hypothesis, its predictive success is equally thin as that of
-traditionalism.
-
-\bigskip
-
-On the face of it, there is a very clear winner among the stylized
-candidate theories that we introduced in
-Section~\ref{sec:theories-predictions}. Assuming that global readings
-are not available at all, the preference pattern in
-(\ref{bsp:observed-preferences}) is exactly what \emph{literalism}
-would predict. Remember that literalism was the conventionalist
-position which posited a lexical ambiguity of scalar \emph{some} with
-a preference for the semantically weaker meaning \emph{some and maybe
-  all} over the upper-bounded reading \emph{some but not all}.
+\es-sentences at the same time. (Try, if you please!)
+
+It may seem as if grammaticalism is better suited to cope with the
+data than traditionalism, because traditionalism cannot cope with
+local readings for principled reasons while the only thing that
+grammaticalism got wrong is the selection criterion over preferred
+readings, i.e., it mistakenly put all its coin on the strongest
+meaning hypothesis. Turning away from comparisons of logical strength,
+a \emph{prima facie} plausible selection criterion that produces
+(\ref{bsp:observed-preferences}) is ready at hand: if we assume that
+each insertion of $\exh(\cdot)$ operator is \emph{costly}
+anti-proportional to the depth of its embedding under other logical
+operators, then we derive a preference of literal readings over local
+ones over global ones. Whether such an \emph{economy principle} is
+sound and in line with further empirical data would then be an
+interesting matter of further investigation. On the entirely
+speculative supposition that it did turn out to be a good predictor,
+grammaticalism would be saved in a straightforward way. But is this an
+argument for grammaticalism contra traditionalism? No it clearly is
+not. The crucial point is that grammaticalism needs a selection
+criterion, for without one it is not a predictive theory at all, and
+that the only one that has been seriously proposed fails to predict
+the observed data. That grammaticalism can do with many such selection
+criteria is not, as such, an argument in its favor over
+traditionalism. The case remains that both theories fail on the
+observed data.
+
+There is a variation of an existing theory of scalar implicature that
+does explain the preference ordering (\ref{bsp:observed-preferences})
+in a completely straightforward manner. The theory of interest is
+\emph{conventionalism} (also sometimes called \emph{lexicalism})
+\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}.
+The general idea is that if the upper-bounding inference from
+\emph{some} to \emph{some but not all} occurs frequently, then it
+would be inefficient to execute the Gricean reasoning that
+traditionalists propose over and over again. Conventionalism therefore
+assumes that scalar inferences have become routinized, hard-wired, so
+much so that there are two lexical entries for a scalar item like
+\emph{some}, one with logical meaning \emph{some and maybe all} and
+one with the upper-bounded meaning \emph{some but not
+  all}. \citet{LevinsonPresumptiveMeanings2000} proposed that the
+latter is the preferred default meaning and has therefore ofttimes be
+addressed as \mymark{defaultism}. Unfortunately, defaultism has strong
+empirical evidence against it, because several processing studies show
+that the computation of scalar inferences appears to be time- and
+effort-consuming, when they \emph{do} arise, not when they
+\emph{don't}, as defaultism would have it
+\citep[c.f.][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
+there is also competing evidence that scalar inferences are available
+in immediate, low-level processes, such as the resolution of
+referential expressions in a visual-world paradigm
+\citep{GrodnerKlein2010:Some-and-Possib}. For our purposes, it is
+interesting to note that the preference relation in
+(\ref{bsp:observed-preferences}) is predicted by the dual of
+defaultism, call it \emph{literalism}, which posits a lexical
+ambiguity but predicts that the logical meanings are \emph{ceteris
+  paribus} preferred over the upper-bounded meanings.
+
+Unfortunately, there are problems with conventionalism that seem to
+require that it be backed up by traditionalism
+\citep[e.g.][]{Sauerland2012:The-Computation}.\fn{\citet{Sauerland2012:The-Computation}
+  eventually dismisses even conventionalism backed up by
+  traditionalism in favor of grammaticalism based on cases of
+  so-called \emph{intermediate implicatures}, where what seems to be
+  necessary is the insertion of an exhaustivity operator in
+  intermediate scope position \citep[see][for
+  details]{Sauerland2012:The-Computation}. Appreciation of such
+  intermediate implicatures requires more argumentation, involving a
+  discussion of \emph{Hurford's constraint}
+  \citep[c.f.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2009:Hurfords-Constr,ChierchiaFox2008:The-Grammatical}.}
+For instance, conventionalism cannot account for \emph{indirect
+  implicatures}, such as the inference from
+(\ref{bsp:indirect-SI-Target}) to (\ref{bsp:indirect-SI-Inference})
+which cannot be explained by positing a lexical ambiguity for
+\emph{all}.
+
+\begin{exe}
+  \ex \label{bsp:indirect-SI}
+    \begin{xlist}
+      \ex \label{bsp:indirect-SI-Target} Hans did not solve all of the problems.
+      \ex \label{bsp:indirect-SI-Inference} Hans solved some of the problems.
+    \end{xlist}
+\end{exe}
+
+\noindent In the context of the present study, this would then be good
+news for traditionalism, because a combined
+traditionalism+conventionalism would predict the observed data
+well. The combined position would even be able to explain something
+that grammaticalism cannot make sense of as easily, namely the
+observation that there were rather consistent localists among the
+participants of our study. The combined tradionalism+conventionalism
+could explain this by the assumption that some (lazy?, smart?)
+speakers have made a conventionalized upper-bounding meaning entry for
+scalar \emph{some} while others keep computing things on the
+fly. It is not clear how grammaticalism can account for the
+intra-subjective consistency.
+
+In sum, if the interpretation of our data as suggested here is correct
+(we will argue presently that it is), then both traditionalism and
+grammaticalism are in need of revision. Traditionalism must explain
+the availability of local readings, grammaticalism must revise its
+selection criterion among readings.
 
@@
 
+\begin{itemize}
+\item future research: isolate consistent localists to probe into \emph{processing}
+\end{itemize}
+
 \appendix

### 2012-08-07 text/paper/paper1.tex
discussion sec com

@@
 
-\subsection{Discussion}
-\label{sec:discussion}
-
-\newcommand{\ivt}{\acro{ivt}}
+\subsection{Interpretation}
+\label{sec:interpretation}
 
@@
 
-In sum, if the interpretation of our data as suggested here is correct
-(we will argue presently that it is), then both traditionalism and
-grammaticalism are in need of revision. Traditionalism must explain
-the availability of local readings, grammaticalism must revise its
-selection criterion among readings.
+In sum, if the interpretation of our data as suggested here is
+correct, then both traditionalism and grammaticalism are in need of
+revision. Traditionalism must explain the availability of local
+readings, grammaticalism must revise its selection criterion among
+readings. In the remainder of this section we would like to discuss
+whether this interpretation of our data is feasible.
+
+\subsection{Discussion}
+\label{sec:discussion}
+
+Several worries and objections are conceivable that might cast doubt
+on the previous interpretation of our experimental data. In the
+following we would like to address some of these that we consider most
+pressing. Eventually, however, we conclude that the main point raised
+above remains valid: neither traditionalism, nor grammaticalism
+explains the observations even under alternative interpretations of the
+data.
+
+\newcommand{\ivt}{\acro{ivt}}
+
+There are many ways in which it could be questioned whether our design
+really reliably indicates the preference relation in
+(\ref{bsp:observed-preferences}) among readings of our target
+sentences. A first potential worry from that class that can be
+dismissed rather quickly is that the incremental verification task
+(\ivt) might simply select for the weakest possible reading. This idea
+might be grounded in the observation that the preferred \lc-readings
+of our target-related controls entail the dispreferred
+\ec-readings. It could thus be argued that the difference in responses
+for preference-related controls are due to the entailment properties,
+not the known preference relation over \lc- and \ec-readings. But this
+does not explain why the distribution of responses in the target
+conditions are obviously not governed by logical strength. In fact, it
+is a very noteworthy point that although entailment relations among
+readings differ between \as- and \es-sentences, the observed response
+pattern does not. (This is what is at the heart of the problem for a
+grammaticalism that relies on the strongest meaning hypothesis.)
+
+But maybe, a similar kind of objection goes, it is not feasible to
+actually compare results from the preference-related controls to
+results from our target conditions, because the kind of ``ambiguity''
+is of a different kind. In the former we have a case of syntactic
+ambiguity, in the latter a small number of competing pragmatic
+enrichments. The former is a case of perceived ambiguity (some of our
+subjects reported this in the
+\emph{Nachbefragungsbogen}\dn{English?}), the latter arguably is
+not \citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps
+even if the distribution of responses is indicative of the known
+preference patterns in preference-related controls, this would not
+necessarily mean that the distribution of responses in target
+conditions is indicative of preference relations.
+
+There are two kinds of reply to this objection (and others like
+it). The first kind of reply starts with a concession. It is true that
+we cannot conclude with certainty that our data implies that
+(\ref{bsp:observed-preferences}) is the actual preference relation
+among candidate readings of our target sentences. But we do not have
+to either. Maybe in fact, the observed distribution has nothing to do
+with preferences over readings. It does not matter. The main point is
+that neither traditionalism nor grammaticalism predicts the observed
+distribution of responses. The second kind of reply is fatalistic but
+stubborn. If we assume that the \ivt is incapable of indicating
+preferences among readings for pragmatically unspecified, then it
+should at least be able to indicate availability of readings, should
+it not? And if we deny the observed response patterns the power to
+indicate preference, what should the information about availability of
+readings be that we may safely infer from it? It should be that local
+readings are available and that global readings are not. But that is
+again bad news for both traditionalism and grammaticalism. The former
+cannot explain the substantial number of local responses, the latter
+doesn't explain the absence of global responses.
+
+\begin{itemize}
+\item different kinds of ``multiple readings'': syntactic ambiguity
+  vs.~pragmatic xxx
+\item typicality after all
+\end{itemize}
 

### 2012-08-07 text/paper/paper1.tex
discussion and conventionalism removed

@@
 \newcommand{\alt}{\ensuremath{\mathrm{Alt}}}
+
+\newcommand{\ivt}{\acro{ivt}}
 
@@
 
-We consider three main theoretical positions which make different
+We consider two main theoretical positions which make different
 predictions about the readings of \as- and \es-sentences
@@
 overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation}. We
-will refer to these here as \mymark{traditionalism},
-\mymark{conventionalism} and \mymark{grammaticalism} and treat each
-one in turn. Since there is some leeway in assessing the predictions
-for each of these positions (depending on which of several reasonable
-additional assumptions we should adopt), we will distinguish different
-varieties of each. For convenience, the predictions of each (variety
-of each) position are also summarized in Table~\ref{tab:predictions}
-at the end of this section.\dn{micha says: I'll leave all the
-  varieties in here until we know which ones we need and which ones we
-  don't need}
+will refer to these here as \mymark{traditionalism} and
+\mymark{grammaticalism} and treat each one in turn. Since there is
+some leeway in assessing the predictions for each (depending on which
+of several reasonable additional assumptions we should adopt), we will
+distinguish different varieties of both. For convenience, the
+predictions of each (variety of each) position are also summarized in
+Table~\ref{tab:predictions} at the end of this section.
 
@@
 
-\subsection{Conventionalism}
-\label{sec:conventionalism}
-
-Lexical conventionalism is a position that has been defended for
-instance by \citet{LevinsonPresumptiveMeanings2000} and
-\citet{Chierchia:2004_ScalarImplicatures}.\fn{See also
-  \citet{Sauerland2012:The-Computation} who argues quite favorably for
-  a pragmatically informed conventionalism, although eventually
-  dismissing it in favor of grammaticalism.} The general idea is that
-if the upper-bounding inference from \emph{some} to \emph{some but not
-  all} occurs frequently, then it would be inefficient to execute the
-Gricean reasoning that traditionalists propose over and over
-again. Conventionalism therefore assumes that scalar inferences have
-become routinized, hard-wired, so much so that there are two lexical
-entries for a scalar item like \emph{some}, one with meaning
-\emph{some and maybe all} and one with the meaning \emph{some but not
-  all}. \citet{LevinsonPresumptiveMeanings2000} proposed that the
-latter is the preferred default meaning, a position which we will
-refer to as \mymark{defaultism}.\fn{Levinson's defaultism has strong
-  empirical evidence against it, because several processing studies
-  show that the computation of scalar inferences appears to be time-
-  and effort-consuming, when they \emph{do} arise, not when they
-  \emph{don't}, as defaultism would have it
-  \citep[c.f.][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
-  there is also competing evidence that scalar inferences are
-  immediate, low-level processes
-  \citep{GrodnerKlein2010:Some-and-Possib}.}\dn{Petra says: empirical
-  stuff in footnote irrelevant; I agree, let's move it to discussion
-  section} For completeness sake, we will call the opposite view that
-the literal meanings are \emph{ceteris paribus} preferred
-\mymark{literalism}. We are not aware that anyone has defended this
-option, but it pays to include this option, because, as we will see
-later on, this possible position is the best direct explanation of our
-experimental data.
-
-Both varieties of conventionalism make interesting predictions about
-available readings for \as- and \es-sentences. Unaided,
-conventionalism does not predict that global readings are
-available. The lexically stored upper-bound for scalar \emph{some}
-only allows to derive literal and local readings. Moreover, defaultism
-predicts that local readings are preferred over literal ones. Contrary
-to that, our dummy position of literalism predicts that literal
-readings are preferred over local ones.
-
 \subsection{Grammaticalism}
@@
     \\
-    \ \ weak restricted 
+    \ \ \ \ weak restricted 
     & \lit > \glb 
@@
     \\
-    \ \ weak unrestricted
+    \ \ \ \ weak unrestricted
     & \lit > \glb > \loc 
@@
     \\
-    \ \ strong restricted
+    \ \ \ \ strong restricted
     & \glb > \lit 
@@
     \\
-    \ \ strong unrestricted
+    \ \ \ \ strong unrestricted
     & \glb > \loc > \lit 
@@
     \\
-    conventionalism
-    \\
-    \ \ defaultism
-    & \loc >  \lit 
-    & \loc >  \lit
-    \\
-    \ \ literalism
-    & \lit >  \loc 
-    & \lit >  \loc
-    \\
+    % conventionalism
+    % \\
+    % \ \ defaultism
+    % & \loc >  \lit 
+    % & \loc >  \lit
+    % \\
+    % \ \ literalism
+    % & \lit >  \loc 
+    % & \lit >  \loc
+    % \\
     grammaticalism
     \\
-    \ \ weak
+    \ \ \ \ weak
     & \loc > \glb > \lit 
@@
     \\
-    \ \ strong
+    \ \ \ \ strong
     & \glb, \loc > \lit 
@@
 \emph{some} to \emph{some but not all} occurs frequently, then it
-would be inefficient to execute the Gricean reasoning that
-traditionalists propose over and over again. Conventionalism therefore
+would be inefficient to execute over and over again the Gricean
+reasoning that traditionalists propose. Conventionalism therefore
 assumes that scalar inferences have become routinized, hard-wired, so
@@
   all}. \citet{LevinsonPresumptiveMeanings2000} proposed that the
-latter is the preferred default meaning and has therefore ofttimes be
-addressed as \mymark{defaultism}. Unfortunately, defaultism has strong
-empirical evidence against it, because several processing studies show
-that the computation of scalar inferences appears to be time- and
-effort-consuming, when they \emph{do} arise, not when they
-\emph{don't}, as defaultism would have it
+latter is the preferred default meaning, a position which has
+therefore ofttimes be addressed as \mymark{defaultism}. Unfortunately,
+defaultism has strong empirical evidence against it, because several
+processing studies show that the computation of scalar inferences
+appears to be time- and effort-consuming, when they \emph{do} arise,
+not when they \emph{don't}, as defaultism would have it
 \citep[c.f.][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
@@
 
-Unfortunately, there are problems with conventionalism that seem to
-require that it be backed up by traditionalism
+Unfortunately, there are problems with conventionalism, no matter
+which lexical reading is assumed to be preferred, that seem to require
+that it be backed up by traditionalism
 \citep[e.g.][]{Sauerland2012:The-Computation}.\fn{\citet{Sauerland2012:The-Computation}
@@
 speakers have made a conventionalized upper-bounding meaning entry for
-scalar \emph{some} while others keep computing things on the
-fly. It is not clear how grammaticalism can account for the
-intra-subjective consistency.
+scalar \emph{some} while others keep computing things on the fly. It
+is not clear how grammaticalism can account for the intra-subjective
+consistency. Still, this is not an argument \emph{for} traditionalism,
+because the point remains that traditionalism as such fails to predict
+the observed data.
 
@@
 data.
-
-\newcommand{\ivt}{\acro{ivt}}
 
@@
 \begin{itemize}
-\item different kinds of ``multiple readings'': syntactic ambiguity
-  vs.~pragmatic xxx
+\item pictures overemphasize contrast some/all
+\item subjects tricked into local responses because they are at the end
+  \begin{itemize}
+  \item would only show availability after all
+  \end{itemize}
 \item typicality after all

### 2012-08-28 text/paper/paper1.tex
changes in paper1

@@
 able to control for effects of ``silent prosody'' that subjects may
-apply when reading a sentence see Bader 1998, \citep{Fodor1998:Learning}
+apply when reading a sentence see Bader 1998, \citep{Fodor98}
 \dn{provide
@@
 accentuation, constituent length, rhythmic phenomena, and individual
-variation (Augurzky, 2008; Bader, 1998; Fodor, 2000, 2001; Kentner,
+variation (Augurzky, 2008; Bader, 1998; Fodor98, 2000, 2001; Kentner,
 2012, Steinhauer et.  al., 2001, see also the discussion in Frazier,
@@
 \end{exe}
-In late-closure sentences, a modifier can be attached to one of two
-preceding hosts. More specifically, in (\ref{bsp:target-related}), the
+In late-closure sentences, a modifier such as a relative clause or a 
+prepositional phrase can be attached to one of two
+preceding hosts. For instance, in (\ref{bsp:target-related}), the
 prepositional phrase \emph{with suns} can be attached to the preceding
 noun \emph{squares}, resulting in the so-called \emph{late-closure} or
-\emph{low-attachment} reading ((\ref{bsp:target-related-LC}), see
-Frazier, 1987, for details)\dn{references}. Alternatively, the
-\acro{pp} can be attached to the whole conjoined \acro{np}
+\emph{low-attachment} reading ((\ref{bsp:target-related-LC}). Alternatively, 
+the \acro{pp} can be attached to the whole conjoined \acro{np}
 \emph{circles and squares}, corresponding to the \emph{early-closure}
-or \emph{high-attachment} reading
-(\ref{bsp:target-related-EC}). Generally, the late-closure reading is
-preferred over the early closure reading for sentences comparable to
-those in (\ref{bsp:target-related}) (REFS)\dn{references}.
-
-For each sentence, two sequences were designed. In the first, the
+or \emph{high-attachment} reading (\ref{bsp:target-related-EC}).
+Late-closure readings have been observed to be preferred over the early 
+closure reading for sentences comparable to those in (\ref{bsp:target-related})
+\citep[e.g.][]{Frazier87,Frazier82}.
+
+For each sentence, two sequences were designed. In the first one, the
 critical position associated with the dispreferred early-closure
@@
 \paragraph{Testing Effects of prosody.}\dn{These two paragraphs
-  still need a proper home; Petra opts for ``materials'' section.}
+  still need a proper home; Petra opts for ``materials'' section.
+  - Petra's comment: wenn wir's wie jetzt etwas ausführlicher diskutieren, 
+  kann's auch gerne hier bleiben}
 
@@
 item. By contrastively accenting the scalar, potential alternatives
-are highlighted, resulting in more implicatures being computed.
-Some approaches have even claimed that local readings exclusively 
+are highlighted, resulting in more implicatures being computed. Some 
+approaches have even claimed that local readings exclusively 
 emerge when the scalar item is accented and are otherwise generally
-unavailable (Refs).
+unavailable \citep[e.g.][]{Horn2006:The-Border-Wars,
+Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,
+Tielvan-Tiel2012:Embedded-Scalar}.
 
@@
 is still scarce. One notable exception comes from a pilot study 
-by Frazier, in which participants were instructed to read embedded
-and non-embedded versions of English ae sentences, in which some was either
-capitalized or non-capitalized. Prior to the experiment, participants 
-were told that capitalizing corresponded to contrastive stress.
-Interestingly, strengthened interpretations occurred rather often 
-in the embedded sentences in this task (59 \%), but were 
-not affected by capitalizing. ...
-Another study relevant for the present consideration comes from Schwarz et al., 
-examining the effects of contrastive accentuation of "or" in non-embedded sentences 
-like {\it Mary will invite Fred or/OR Sam to barbecue}. After listening to these 
-sentences, participants were presented two alternative readings ({\it 1. She will 
-invite Fred or Sam or possibly both}, or {\it 2. She will invite Fred or Sam but 
-not both}).
-
-%  It
-%has been claimed that local readings only emerge in the case of
-%special accentuation of the the scalar item under consideration
-%(REFERENCES). Further, it is generally assumed that the required type
-%of accentuation is a pitch accent (REFS). To test for this possibility
-%we decided to present the sentences (eg., (\ref{ex:as}) and
-%(\ref{ex:es})) auditorily in two versions each. In the accented
-%version a pitch accent was placed on {\it einige}. The second version
-%had neutral prosody. If accentuation is the driving force for local
-%readings, we would expect a higher proportion of local readings in the
-%former than in the latter version of the sentences.
-
-We also wished to make sure that differences in prosody may generally
-lead to a shift in interpretation preferences in the \acro{itv}
-task. Sentences like (\ref{bsp:target-related}) are well suited to
-test this assumption since it is well-known that their
-interpretational preferences are sensitive to prosody. If an utterance
-of (\ref{bsp:target-related}) includes a prosodic phrase boundary
-between {\it squares} and {\it with}, this intonational pattern
-strongly corresponds to the high-attachment reading. If, instead, a
-prosodic phrase boundary after {\it circles} is present, the
-acceptance of the low-attachment reading is boosted. To test whether
-prosodic information is taken into account in the \acro{itv} we
-presented both types of prosodic structures expecting the described
-boost in acceptance for the low-attachment reading. In addition, we
-also included a neutral version containing no phrase marking
-whatsoever. This should receive intermediate acceptance
-rates. Further, we also presented unambiguous sentences corresponding
-to the early-closure reading. As in the case of the \as- and
-\es-sentences the unambiguous counterparts served as a baseline to
+reported in \citet{Frazier08}, in which participants were 
+instructed to read embedded and non-embedded versions of English 
+\as-sentences. In the embedded sentences (e.g. {\it All of the students 
+wrote some of the official memos}), {\it some} was either capitalized 
+or non-capitalized. Prior to the experiment, 
+participants were informed that capitalizing corresponded to contrastive 
+stress. The task consisted in a forced-choice questionnaire with two
+given alternatives (such as {\it All of the students wrote some but 
+not all of the official memos}  vs. {\it All of the students wrote at 
+least some of the official memos}). Interestingly, strengthened  
+interpretations occurred rather often across all sentences in this task 
+(59 \%), but were not affected by capitalizing. \fn{Note that, 
+unfortunately, the authors do not provide percentages for the embedded 
+conditions alone, but only the means across sentence types.} The authors 
+conclude that accentuation did not affect their silent reading data, 
+but raise the possibility that prosodic effects may have been present 
+at least in a subset of the items (see footnote 1 in \citet{Frazier08}, 
+p. 330).
+
+Another study relevant for the present considerations comes from 
+\citet{SchwarzClifton2008:Strengthening-o}, examining the effects of 
+contrastive accentuation of "or" in non-embedded sentences like {\it 
+Mary will invite Fred or/OR Sam to barbecue}. After listening to these 
+sentences, participants were presented two alternative readings 
+({\it 1. She will invite Fred or Sam or possibly both}, or {\it 2. 
+She will invite Fred or Sam but not both}). Contratry to the silent-prosodic 
+effects reported in the pilot experiment by Frazier and colleagues, the 
+authors found a significant impact of overtly realized contrastive accents 
+on implicature processing: Besides a general advantage for non-strengthened 
+readings, focal accents significantly increased the strengthened interpretation 
+(from 16.4 \% to 28.6 \%). These results are compatible with the "focus 
+strengthening hypothesis" proposed by the authors.
+
+To sum up so far, though an effect of contrastive accentuation has been 
+claimed tobe essential for triggering local implicatures, experimental evidence 
+is currently mixed, suggesting potential effects of presentation mode (visual vs. 
+auditory), item-specific characteristics, as well as the specific construction 
+under investigation (e.g. embedded cases vs. non-embedded cases such as in 
+\citet{SchwarzClifton2008:Strengthening-o}).
+
+Whereas contrastive accents are usually assumed to be realized by a special 
+contour in English (i.e. L+H*, see \citet{Pierrehumbert90}), 
+the exact phonological classification of contrast in German is still under 
+debate \citep[see][]{Uhmann91,Fery93,Grabe98,Toepel06, Sudhoff10}. 
+These approaches have in common that from an acoustic perceptive, prosodic 
+prominence of contrastively accented constituents is realized by
+
+\begin{enumerate}[1:]
+\item a higher higher f0 maximum or a higher pitch range (difference 
+between minimal and maximal f0 values), and
+\item a longer duration of the accented element as opposed to its 
+non-accented counterpart
+\end{enumerate}
+
+We therefore recorded sentences by a trained speaker familiar with the 
+concept of contrastive focus and instructed her to produce contrast as 
+described in 1 and 2. Both \as-sentences and \es-sentences
+were recorded in two versions each. In the accented version, a pitch 
+accent was placed on {\it einige}. The second version had neutral prosody. 
+If accentuation is the driving force for local readings, we would expect 
+a higher proportion of local readings in the former than in the latter 
+version of the sentences.
+
+Preference-related controls also differed prosodically. Modifier attachment 
+ambiguities comparable to the examples in (\ref{bsp:target-related}) and 
+(\ref{bsp:target-related2}) have been shown to be sensitive to differences 
+in prosodic phrasing. Though there has been discussion as to whether 
+speakers reliably \textit{produce} disambiguating cues in such constructions 
+\citep[e.g.][]{Allbritton96,Kraljik05, Snedeker03, Schafer00}, overt prosodic 
+boundaries are generally acknowledged to guide interpretive processes of Late 
+Closure sentences in \textit{comprehension} \citep[e.g.][]{Steinhauer99, Augurzky06}. 
+Specifically, it has been shown that prosodically separating a modifier from 
+the directly preceding material supports an early closure reading, whereas 
+separating the two potential attachment sites is supportive of a late closure 
+reading. Thus, a phrase boundary between {\it squares} and {\it with} in
+(\ref{bsp:target-related}) corresponds to a high-attachment reading, whereas
+a prosodic phrase boundary following {\it circles} corresponds to a low-attachment
+reading.
+
+To test whether prosodic information is taken into account in the \acro{itv} task, we
+presented sentences in both of these prosodic variants. In addition, in order to test 
+prosody-independent preferences, we also included a neutral version without any 
+pronounced boundary. Further, we also presented 
+unambiguous sentences corresponding to the early-closure reading. As in the case 
+of the \as- and \es-sentences, the unambiguous counterparts served as a baseline to
 control for response biases that are independent of sentence meaning.
@@
 was recorded in a stressed and an unstressed version of scalar {\it
-  einige} (see section xx below). As described above, three control
+  einige}. As described above, three control
 sentences were created for each experimental item, corresponding to
 the critical positions in the course of uncovering the accompanying
-sequences (see below).  The positional controls were recorded with
+sequences.  The positional controls were recorded with
 neutral prosody.  Items were evenly distributed across 5 lists using a
@@
 \paragraph{Acoustic properties}
-
 A phonetically trained female native speaker of German was instructed
@@
 produced with a contrastive pitch accent as well as with a neutral
-accent. Contrastive accents in German are realized by an
-H*L contour (XYZ)\dn{insert references}, thus employing a generally
-falling pattern. A set of 15 experimental items was recorded for each
-condition (\as vs.~\es, \emph{accented} vs.~\emph{unaccented}), resulting in a
-total number of 60 target sentences.
+accent. Contrastive accents in German are realized by an increase in f0 (range)
+as well as by a longer duration (see {sec:design} above). A set of 15 
+experimental items was recorded for each condition (\as vs.~\es, \emph{accented} 
+vs.~\emph{unaccented}), resulting in a total number of 60 target sentences.
 
@@
 increase on the final part of the constituent preceding the boundary
-(prefinal lengthening) plus an optional pause (XYZ)\dn{references:
-  Vaissiere, 1983; Fery, 1993}. Boundaries for these control sentences
-were either realized at the position separating the second {\small \acro{PP}}
+(prefinal lengthening) plus an optional pause \citep[e.g.][]{Vaissiere83,Fery93}.
+Boundaries for these control sentences were either realized at the position 
+separating the second {\small \acro{PP}}
 from the preceding material (\emph{late boundary}, corresponding to a
@@
 with respect to certain lexical properties (i.e., \emph{seinen}
-vs.~\emph{ihren}, see above (XYZ)\dn{proper reference}), we considered
-the following analysis regions:
+vs.~\emph{ihren}, we considered the following analysis regions:
 
@@
     \begin{xlist}
-      \ex $|_{\text{R}1}$~Alle  	\ $|_{\text{R}2}$~dieser 
+      \ex $|_{\text{R}1}$~Alle  	\ $|_{\text{R}2}$~diese 
       \ $|_{\text{R}3}$~$\acro{np}_1$  
@@
 For the durational analyses, constituents were automatically labeled
-by the \emph{Aligner} tool (XYZ),\dn{reference! Rapp, 1998} and the
+by the \emph{Aligner} tool \citet{Rapp98},and the
 obtained values were manually corrected afterwards. For the targets,
@@
 differences between minimal and maximal F0 values for each region or
-word were calculated. Again, two-factorial \acros{anova}s were carried
+word were calculated. Again, two-factorial \acros{anova} were carried
 out for statistical comparison of the target sentences, and one-factorial
-\acros{anova}s were carried out for preference-related controls.
+\acros{anova} were carried out for preference-related controls.
 
 The details of these analyses are found in
-Appendix~\ref{sec:audit-sent-mater}. In sum, our speaker reliably
+Appendix~\ref{sec:audit-sent-mater}.
+\dn{Petras Kommentar: Vielleicht sollten wir hier jeweils 1 Figure für akzentuiert vs.
+nicht und boundary vs.
+nicht reinbringen.
+Fabian meint zurecht, dass man nicht einfach die Ergebnisse nur in den Appendix packen kann.
+Es wären dann halt 4 Figures, da wir ja f0 und duration ansehen, und wir würden nur die experimentell interessanten veranschaulichen und die Statistik dann im Appendix lassen - was meint Ihr?}
+
+In sum, our speaker reliably
 produced (i) differences in accent realization for the target

### 2012-08-28 text/paper/paper1.tex
refs etc.

@@
 accentuation, constituent length, rhythmic phenomena, and individual
-variation (Augurzky, 2008; Bader, 1998; Fodor98, 2000, 2001; Kentner,
-2012, Steinhauer et.  al., 2001, see also the discussion in Frazier,
-2009).\dn{references} As it has been suggested in the theoretical
+variation \citep[e.g.][]{Augurzky08,Bader98,Fodor98,Fodor02,Kentner12,
+Steinhauer01}. As it has been suggested in the theoretical
 literature that the availability of a local reading might hinge on the

### 2012-09-01 text/paper/paper2.tex
Petra changes new version paper2

--- 2012-08-28 text/paper/paper1.tex
@@
 
-High scores of success in our general control condition clearly
-indicate that participants understood the incremental verification
-task and were in general able to give judgements at the earliest
-possible point in a picture sequence. Results obtained for the
-preference-related controls moreover show that our design is able to
-detect multiple readings and preferences among these. Crucially, the
-amount of response types for \lc- and \ec-readings reflected the known
-preference for the former, \emph{irrespective} of the order in which
-each reading could first be judged in a given sequence. Given this,
-the best and most straightforward explanation of the observed data is
-the hypothesis that the actual preferences among readings for both
-\as- and \es-sentences alike are:
+High scores of success clearly indicate that participants understood 
+the incremental verification task and were in general able to give 
+judgements at the earliest possible point in a picture sequence. 
+Moreover, results obtained for the preference-related controls  
+show that our design is able to detect multiple readings and preferences 
+among these. Crucially, the amount of response types for \lc- and \ec-readings 
+reflected the known preference for the former, \emph{irrespective} of the 
+order in which each reading could first be judged in a given sequence. 
+Finally, prosodic effects were restricted to the preference-related 
+controls. As expected, the dispreferred \ec-reading was chosen 
+significantly more often when supported by prosodic phrasing. Interestingly, 
+contrastively accenting scalar \emph{some} had no effect on the observed 
+decisions in \as- and \es-sentences.
+
+Given the overall pattern of results, the most straightforward 
+explanation of the observed data is the hypothesis that the actual 
+preferences among readings for both \as- and \es-sentences alike are:
+
 \begin{exe}
@@
 \end{exe}
+
 where it is unclear whether the global readings are entirely
 unavailable or simply severely dispreferred. Crucially, our data
-attests local readings independently of a stress accent on the
-embedded scalar item, albeit that local readings are not preferred to
-literal readings and given, as it seems, only by a small, but
-substantial number of consistent localists.
-
-This is bad news for both traditionalism and grammaticalism, as no
-version of either would predict the pattern in
-(\ref{bsp:observed-preferences}). The main problem is that
-traditionalism, if left on its own, fails to predict local readings,
+attests local readings independent of prosody, albeit that local 
+readings are not preferred to literal readings and given, as it seems, 
+only by a small, but substantial number of consistent localists.
+
+These findings are hard to explain both by traditionalism and grammaticalism, 
+as no version of either would predict the pattern in (\ref{bsp:observed-preferences}). 
+Traditionalism, if left on its own, fails to predict local readings,
 while grammaticalism, when it relies on the strongest meaning
@@
 
-As for traditionalism, it is not a major obstacle for this position to
-predict that global readings are available. The weak variety of
-traditionalism holds that the extra assumptions needed to derive
-global readings are not standardly available, and so traditionalism is
-compatible with a lack of observed global readings. Alternatively,
-traditionalists could argue that the task's rather high processing
-demands lead to a suppression of global readings, in line with the
+For traditionalism, the absence of global readings \textit{per se} can be
+explained in a straightforward manner, for instance, by proposing
+that the extra assumptions needed to derive global readings are not 
+standardly available (as in the weak variety of traditionalism).
+Alternatively, traditionalists could argue that the task's rather high 
+processing demands lead to a suppression of global readings, in line with the
 findings of \citet{NeysDe-NeysSchaeken2007:When-People-Are} that
 working memory load negatively affects the number of scalar
-implicature responses in sentence verification tasks. Unfortunately,
-to the extent that global readings are explained away as dispreferred
-or unavailable, traditionalism also looses the possibility of
-accounting for local readings of \as-sentences in its unrestricted
-variety.\fn{Remember that what we called unrestricted traditionalism
+implicature responses in sentence verification tasks. However, it then remains 
+unclear why memory effects should be restricted to global readings.
+As a result, approaches like the unrestricted variety of traditionalism thereby 
+loose the possibility of accounting for local readings of \as-sentences.
+\fn{Remember that what we called unrestricted traditionalism
   can account for local readings of \as-sentences by assuming that a
@@
 essentially the same manner. On top of that, traditionalism cannot
-explain local readings for \es-sentences. Since our design presented
-sentence material auditorily, the traditionalist cannot resort to
-effects of silent intonation to explain these local readings
-away. Local readings showed on the neutral accentuation case as
-well. Notice that it is not a problem for this argument that the local
+explain local readings for \es-sentences. Finally, since our materials were 
+presented auditorily, we controlled for potential effects of silent
+prosody. Importantly, local readings were observed in the accented as well
+as in the unaccented condition, thus countering previous traditionalist
+suggestions that local readings are to be attributed to specific pragmatic 
+mechanisms.\dn{Petra: das habe ich hier so von der Intro übernommen. Sowohl
+dort als auch hier fände ich es interessant, kurz zu sehen, was für alternative
+pragmatische Mechanismen das sind - geht das in Kürze? Den nächsten Satz habe ich
+in Bezug zum vorhergehenden Absatz nicht verstanden}
+
+%showed on the neutral accentuation case as
+%well. 
+Notice that it is not a problem for this argument that the local
 responses were not emphasized with a contrastive stress on the
@@
 Grammaticalism, on the other hand, fails to predict the preference
-relation in (\ref{bsp:observed-preferences}), because these strictly
-contradict the strongest meaning hypothesis in either of the two
+relation in (\ref{bsp:observed-preferences}), because it strictly
+contradicts the strongest meaning hypothesis in either of the two
 varieties suggested by \citet{ChierchiaFox2008:The-Grammatical}. This
@@
 
-It may seem as if grammaticalism is better suited to cope with the
-data than traditionalism, because traditionalism cannot cope with
-local readings for principled reasons while the only thing that
-grammaticalism got wrong is the selection criterion over preferred
-readings, i.e., it mistakenly put all its coin on the strongest
+Summing up so far, the existing versions of traditionalism and grammaticalism
+cannot explain the present results. Of the two approaches, grammaticalism 
+seems better suited to account for the observed effects. Whereas 
+traditionalism cannot cope with local readings for principled reasons, 
+the only thing that grammaticalism would have to change is the 
+selection criterion over preferred readings, i.e. to reconsider the strongest
 meaning hypothesis. Turning away from comparisons of logical strength,
@@
 sound and in line with further empirical data would then be an
-interesting matter of further investigation. On the entirely
-speculative supposition that it did turn out to be a good predictor,
-grammaticalism would be saved in a straightforward way. But is this an
-argument for grammaticalism contra traditionalism? No it clearly is
-not. The crucial point is that grammaticalism needs a selection
-criterion, for without one it is not a predictive theory at all, and
-that the only one that has been seriously proposed fails to predict
-the observed data. That grammaticalism can do with many such selection
-criteria is not, as such, an argument in its favor over
-traditionalism. The case remains that both theories fail on the
-observed data.
-
-There is a variation of an existing theory of scalar implicature that
-does explain the preference ordering (\ref{bsp:observed-preferences})
-in a completely straightforward manner. The theory of interest is
-\emph{conventionalism} (also sometimes called \emph{lexicalism})
+interesting matter of further investigation. 
+%On the entirely
+%speculative supposition that it did turn out to be a good predictor,
+%grammaticalism would be saved in a straightforward way. 
+%But is this an argument for grammaticalism contra traditionalism? No 
+%it clearly is not.
+
+%In order to be a predictive theory, grammaticalism thus needs a selection
+%criterion, for without one it is not a predictive theory at all, and
+%that the only one that has been seriously proposed fails to predict
+%the observed data. That grammaticalism can do with many such selection
+%criteria is not, as such, an argument in its favor over
+%traditionalism. The case remains that both theories fail on the
+%observed data.
+
+Interestingly, an alternative theory of scalar implicature explains the 
+observed preference ordering (\ref{bsp:observed-preferences})
+in a completely straightforward manner. 
+\emph{Conventionalism} (also sometimes called \emph{lexicalism})
 \citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}.
-The general idea is that if the upper-bounding inference from
-\emph{some} to \emph{some but not all} occurs frequently, then it
+proposes that if the upper-bounding inference from
+\emph{some} to \emph{some but not all} occurs frequently, it
 would be inefficient to execute over and over again the Gricean
@@
 because the point remains that traditionalism as such fails to predict
-the observed data.
+the observed data.\dn{Petra: dieser Absatz scheint mir sehr wichtig und gut - 
+wäre es möglich, hier noch etwas ausführlicher drüber zu schreiben?}
 
@@
 
-Several worries and objections are conceivable that might cast doubt
-on the previous interpretation of our experimental data. In the
-following we would like to address some of these that we consider most
-pressing. Eventually, however, we conclude that the main point raised
+%Several worries and objections are conceivable that might cast doubt
+%on the previous interpretation of our experimental data.
+
+In the following, we would like to address potential alternative
+explanations for the present results. We will argue that besides
+these interpretation variants, the main point raised
 above remains valid: neither traditionalism, nor grammaticalism
-explains the observations even under alternative interpretations of the
-data.
-
-There are many ways in which it could be questioned whether our design
-really reliably indicates the preference relation in
-(\ref{bsp:observed-preferences}) among readings of our target
-sentences. A first potential worry from that class that can be
-dismissed rather quickly is that the incremental verification task
+is able to account for the present pattern of results.
+
+%some of these that we consider most
+%pressing. Eventually, however, we conclude that the main point raised
+%above remains valid: neither traditionalism, nor grammaticalism
+%explains the observations even under alternative interpretations of the
+%data.
+
+First, it could be questioned whether our design reliably 
+indicates the preference relation in (\ref{bsp:observed-preferences}) 
+among readings of our target sentences. Thus, the incremental verification task
 (\ivt) might simply select for the weakest possible reading. This idea
-might be grounded in the observation that the preferred \lc-readings
+can be grounded in the observation that the preferred \lc-readings
 of our target-related controls entail the dispreferred
@@
 for preference-related controls are due to the entailment properties,
-not the known preference relation over \lc- and \ec-readings. But this
+not the known preference relation over \lc- and \ec-readings. However, this
 does not explain why the distribution of responses in the target
@@
 grammaticalism that relies on the strongest meaning hypothesis.)
+\dn{Petra: ich glaub, den Punkt verstehe ich nicht ganz - sollte man hier
+auch die Prosodie erwähnen? Phrasierung wirkt sich ja nicht auf entailment
+relations aus, sondern wird normalerweise dem Syntax-Prosodie-Interface
+zugeschrieben}
 
@@
 results from our target conditions, because the kind of ``ambiguity''
-is of a different kind. In the former we have a case of syntactic
+is of a different kind. In the former we have a syntactic
 ambiguity, in the latter a small number of competing pragmatic
 enrichments. The former is a case of perceived ambiguity (some of our
-subjects reported this in the
-\emph{Nachbefragungsbogen}\dn{English?}), the latter arguably is
+subjects reported this in a \emph{Nachbefragungsbogen}\dn{English?}), 
+the latter arguably is
 not \citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps

### 2012-10-31 text/paper/paper2.tex
changes result section

@@
 
-41 native speakers of German took part in our study, none of which had
-any prior exposure to logic or formal semantics. We excluded 3
+Forty native speakers of German took part in our study, none of which had
+any prior exposure to logic or formal semantics. We excluded three
 subjects due to insufficient performance on controls ($\le 50\%$
@@
 
-Performance on basic control conditions was high (92\% correct
+\paragraph{Target conditions and positional controls}
+Performance on positional controls was high (92\% correct
 responses on average), indicating that subjects understood the task,
@@
 
+Participants' judgments are depicted in Figures \ref{Fig:EC_judgments} and 
+\ref{Fig:LC_judgments}. Judgments were coded as \ec, \lc if they were as expected
+under one of these readings, and "other" if they were not. The distributions 
+of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{../pictures/graph_ec.pdf}
+\caption{Judgments for prefence-related controls (EC sequence). Relative frequencies
+of {\it yes/no} judgments is plotted against the position within the
+trial. Each {\it EC sequences} consisted of five pictures, in which the
+critical positions for a reading were the third position ("false" corresponded
+to an \ec reading) and the fifth position ("true" corresponded to an \lc reading)}
+\label{Fig:EC_judgments}
+\end{figure}
+
+%\clearpage
+
+\begin{figure}
+\includegraphics[width=\textwidth]{../pictures/graph_lc.pdf}
+\caption{Judgments for prefence-related controls (LC sequence). Relative frequencies
+of {\it yes/no} judgments is plotted against the position within the
+trial. Each {\it LC sequences} consisted of seven pictures, in which the
+critical positions for a reading were the third position ("true" corresponded
+to an \lc reading) and the sixth position ("false" corresponded to an \ec reading)}
+\label{Fig:LC_judgments}.
+\end{figure}
+
+\begin{figure}
+
+\includegraphics[width=\textwidth]{../pictures/graph_lc.pdf}
+
+\end{figure}
+
 \begin{itemize}

### 2012-11-04 text/paper/paper2.tex
Descriptive results: tfs.

@@
 Participants' judgments are depicted in Figures \ref{Fig:EC_judgments} and 
-\ref{Fig:LC_judgments}. Judgments were coded as \ec, \lc if they were as expected
-under one of these readings, and "other" if they were not. The distributions 
-of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}
+\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they were as expected
+under one of these readings, and as "other" if they were not. The distributions 
+of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}. 
+Overall, participants mainly gave answers corresponding to the \lc-reading. Moreover,
+the preference for this reading was constrained by prosody. When prosody supported 
+a dispreferred \ec-reading, the number of \lc-decisions was decreased. The number 
+of erroneous answers did not differ between the single conditions. Finally, the
+availability of readings within a sequence did not yield any significant effects.
+
+In both \lc- and \ec-sequences, the number of \lc-answers was highest when this reading
+was supported by prosodic phrasing (i.e. 77\%  and 76\% , respectively), and a bit lower
+with neutral prosody (69\%  and 63\% ). This clearcut advantage decreased when prosodic
+phrasing supported the \ec-reading (52\%  vs. 56\% ).
+
+In order to test statistically whether prosodic phrasing and the sequential ordering 
+had an effect on the number of \lc choices, log-linear models with the factors
+{\it Reading}, {\it Prosody}, {\it Sequence}, {\it Item}, and {\it Participant} were included.
+
+An effect of {\it Reading} reflects that overall, readings were distributed inhomogeneously
+($LRCS = 539.04, p < .001$). As revealed by an interaction between {\it Prosody} and
+{\it Reading}, prosodic phrasing had an influence upon the distribution of readings 
+($LRCS = 50.42, p < .001$). Finally, an interaction between {\it Participant} and {\it Reading}
+shows that readings were distributed unevenly amongst participants ($LRCS = 345.22, p < .001$)
 
@@
 
-\begin{itemize}
-\item see Figure~\ref{fig:response-type-freque-TRF}
-\end{itemize}
+%\begin{itemize}
+%\item see Figure~\ref{fig:response-type-freque-TRF}
+%\end{itemize}
 

### 2012-11-08 text/paper/paper2.tex
small changes results parts

@@
 Participants mostly gave judgments indicating literal or local
-readings. Judgments compatible with a global reading were seldom
-obtained. In the \as-conditions participants made hardly any errors,
-whereas the amount of errors was considerably larger in the
-\es-conditions.
-
-In the \as-conditions (see Figure~\ref{fig:JudgementPercentagesAE})
+readings. Judgments compatible with a global reading were seldomly
+obtained. In the \as-conditions (see Figure~\ref{fig:JudgementPercentagesAE}),
 judgments were consistent with literal readings in 65.0\% of the
@@
   rounded)! Fabian, did you exclude the 3 bad performers when you
-  obtained this data?} The number of global readings was very low,
-with 1.6\% of the neutral and 0.8\% of the accented trials
-(corresponding to a total of 3 answers across all trials). Judgments
-indicating local readings were given in 22.0\% of both the neutral and
-accented trials. In the \es-conditions (see
-Figure~\ref{fig:JudgementPercentagesGE}) judgments consistent with
-literal readings were given in 47.2\% and 44.7\% of the trials with
-neutral and accented prosody respectively. Global readings were
+  obtained this data?} Judgments indicating local readings were given 
+  in 22.0\% of both the neutral and accented trials. Global readings 
+occurred in 1.6\% of the neutral and 0.8\% of the accented trials
+(corresponding to a total of 3 answers across all trials).  
+In the \es-conditions (see Figure~\ref{fig:JudgementPercentagesGE}) 
+judgments consistent with literal readings were given in 47.2\% and 
+44.7\% of the trials with neutral and accented prosody, respectively. 
+Judgments indicating local readings were given in 22.8\% of
+the neutral and 27.6\% of the accented trials. Global readings were
 observed in 0.8\% of the trials in both the neutral and the accented
-condition. Judgments indicating local readings were given in 22.8\% of
-the neutral and 27.6\% of the accented trials.
-
-In order to test wether local readings exist we tested whether the
+condition. 
+As for the number of erroneous decisions, a discrepancy between 
+\as-conditions and \es-conditions was observed: In the former, 
+participants made hardly any errors, while in the latter, the amount 
+of errors was considerably larger.
+
+In order to test wether local readings occurred reliably, we tested whether the
 number of local responses in each condition was higher than expected
@@
 of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}. 
-Overall, participants mainly gave answers corresponding to the \lc-reading. Moreover,
-the preference for this reading was constrained by prosody. When prosody supported 
-a dispreferred \ec-reading, the number of \lc-decisions was decreased. The number 
+Overall, participants mainly gave answers corresponding to the \lc-reading (65\%). 
+Moreover, the preference for this reading was constrained by prosody. When prosody 
+supported a dispreferred \ec-reading, the number of \lc-decisions was decreased. In both 
+\lc- and \ec-sequences, the number of \lc-answers was highest when this reading
+was supported by prosodic phrasing (i.e. 77\%  and 76\%, respectively), and a bit lower
+with neutral prosody (69\%  and 63\%). This clearcut advantage decreased when prosodic
+phrasing supported the \ec-reading (52\%  vs. 56\%). The number 
 of erroneous answers did not differ between the single conditions. Finally, the
@@
 
-In both \lc- and \ec-sequences, the number of \lc-answers was highest when this reading
-was supported by prosodic phrasing (i.e. 77\%  and 76\% , respectively), and a bit lower
-with neutral prosody (69\%  and 63\% ). This clearcut advantage decreased when prosodic
-phrasing supported the \ec-reading (52\%  vs. 56\% ).
-
-In order to test statistically whether prosodic phrasing and the sequential ordering 
+In order to test statistically whether prosodic phrasing and sequential ordering 
 had an effect on the number of \lc choices, log-linear models with the factors

### 2012-11-26 text/paper/paper2.tex
results/discussion - changes

@@
 
+In the following, we will report the results for targets and positional
+controls separately. After providing the descriptive results, we present
+statistical analyses, which were carried out in the following manner.
+We computed log-liner models (see Scheepers 2003) in two variants (by 
+item and by participant). In the first, the factor {\it Item} was 
+included, and in the second analysis, the factor {\it Participants} 
+was included. Inclusion of these two factors allowed us to test whether 
+the distribution of participants' choices was identical accros items and 
+participants. We report log-likelihood ratio Chi-squares ($LRCS_1$ 
+and $LRCS_2$), degrees of freedom ($df_1$, $df_2$) and significance 
+levels ($p_1$ and $p_2$). The relevant experimental
+factors are provided in the specific subsections below.
+
 \paragraph{Target conditions and positional controls}
@@
 In order to test whether accentuation or the quantifier has an
-influence on the distribution of readings, log-liner models were
-computed (see Schepers 2003). The factors {\it Reading}, {\it
-  Accentuation} and {\it Quantifier} were included in these
-models. Two variants of these models were computed.  In the first, the
-factor {\it Item} was added to the above mentioned. In the latter {\it
-  Participants} was included as a factor. Inclusion of these two
-factors allowed us to test whether the distribution of readings was
-identical accros items and participants. We report log-likelihood
-ratio Chi-squares ($LRCS_1$ and $LRCS_2$), degrees of freedom ($df_1$,
-$df_2$) and significance levels ($p_1$ and $p_2$).
+influence on the distribution of readings, log-liner models 
+including the factors {\it Reading}, {\it Accentuation} and 
+{\it Quantifier}.
 
@@
 Overall, participants mainly gave answers corresponding to the \lc-reading (65\%). 
-Moreover, the preference for this reading was constrained by prosody. When prosody 
-supported a dispreferred \ec-reading, the number of \lc-decisions was decreased. In both 
-\lc- and \ec-sequences, the number of \lc-answers was highest when this reading
-was supported by prosodic phrasing (i.e. 77\%  and 76\%, respectively), and a bit lower
-with neutral prosody (69\%  and 63\%). This clearcut advantage decreased when prosodic
-phrasing supported the \ec-reading (52\%  vs. 56\%). The number 
+Moreover, this pattern was constrained by prosody. When prosody 
+supported a dispreferred \ec-reading, the number of \ec-decisions were increased.
+
+In both \lc- and \ec-sequences, the number of \ec-answers was highest when this reading
+was supported by prosodic phrasing (i.e. 30\%  and 32\%, respectively), and a bit lower
+with neutral prosody (24\%  and 25\%). When prosodic phrasing supported the \lc-reading,
+the number of \ec choices was lowest (12\% in both sequences). The number 
 of erroneous answers did not differ between the single conditions. Finally, the
@@
 In order to test statistically whether prosodic phrasing and sequential ordering 
-had an effect on the number of \lc choices, log-linear models with the factors
-{\it Reading}, {\it Prosody}, {\it Sequence}, {\it Item}, and {\it Participant} were included.
+had an effect on the number of \ec-choices, we contrasted the number of \ec-choices
+with non-\ec -choices (i.e. \lc-answers and erroneous responses together), calculating
+log-linear model analyses with the factors {\it Reading}, {\it Prosody}, and 
+{\it Sequence}.
 
 An effect of {\it Reading} reflects that overall, readings were distributed inhomogeneously
-($LRCS = 539.04, p < .001$). As revealed by an interaction between {\it Prosody} and
+($LRCS_1 = 252.8, df_1 =1, p_1 < .001$; $LRCS_2 = 252.8, df_2 =1, p_2 < 001$). 
+As revealed by an interaction between {\it Prosody} and
 {\it Reading}, prosodic phrasing had an influence upon the distribution of readings 
-($LRCS = 50.42, p < .001$). Finally, an interaction between {\it Participant} and {\it Reading}
-shows that readings were distributed unevenly amongst participants ($LRCS = 345.22, p < .001$)
+($LRCS_1 = 38.4, df_1 =2, p_1 < 001$; $LRCS_2 = 26.1, df_2 =2, p_2 < .001$).
+
+In the analysis by participant, an interaction between {\it Participant} and {\it Reading}
+indicates that reading preferences differed between participants ($LRCS_1 = 376.6,df_1 =37,  
+p_1 < .001$).
+
+In the analysis by items, a three-way interaction between {\it Item}, {\it Prosody} and 
+{\it Reading} was observed ($LRCS_2 = 88.3, df_1 =54, p_2 < .01$). As this effect was 
+unexpected, we carried out additional descriptive analyses (crosstables) in order to examine whether
+the interaction might have been caused by specific items. When excluding the four items with
+the highest deviation from expected frequencies (Residuals > 2.4 in at least one cell), 
+the interaction was no longer significant ($p_2 = .18$).
 
@@
 
-\subsection{Interpretation}
+\subsection{Discussion}
 \label{sec:interpretation}
@@
 order in which each reading could first be judged in a given sequence.
-Finally, prosodic effects were restricted to the preference-related 
-controls. As expected, the dispreferred \ec-reading was chosen 
+Finally, the incremental verification task was generally sensitive
+to prosody. However, prosodic effects were restricted to the preference-related 
+controls. As expected, in these conditions, the dispreferred \ec-reading was chosen 
 significantly more often when supported by prosodic phrasing. Interestingly, 
 contrastively accenting scalar \emph{some} had no effect on the observed 
-decisions in \as- and \es-sentences.
+decisions in the target conditions. Crucially, local readings occurred in both
+\as- and \es-sentences, independently of prosody. Finally, closer examination of 
+the participants' decisions revealed two groups: participants in the first
+group consistently gave answers corresponding to local readings, whereas participants
+in the second group consistently showed a literal interpretation.
 
@@
 
-\subsection{Discussion}
+\subsection{General Discussion}
 \label{sec:discussion}

### 2013-01-20 text/paper/paper2.tex
layout and graphics

@@
 \usepackage{subfig}
+
+% \usepackage{geometry}
+% \linespread{1.2}
 
@@
 
-We conclude, that  effects of pictorial complexity and/or typicality are real and affect even categorical judgments.
+We conclude that  effects of pictorial complexity and/or typicality are real and affect even categorical judgments.
 For this reason the following experiment was set up to investigate the availability of local readings while minimizing pictorial effects such as typicality or complexity.
@@
 \centering
-\subfloat[][\as-accented]{
-\includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
-\label{fig:ReadingsAE}
-}
 \subfloat[][\as-neutral]{
-\includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
-\label{fig:ReadingsGE}
-}
-
-\subfloat[][\es-accented]{
-\includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
-\label{fig:ReadingsAE}
+% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.1,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
+                  ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,0) (2,0) (3,72) (4,1) (5,1) (6,0) (7,3)};
+
+        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,0) (6,0) (7,23)};
+
+        \legend{yes, no}
+
+      \end{axis}
+\end{tikzpicture}
+\label{fig:ReadingsAS-ntr}
 }
 \subfloat[][\es-neutral]{
-\includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
-\label{fig:ReadingsGE}
+% \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.2,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
+                  % ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,1) (2,4) (3,3) (4,0) (5,30)};
+
+        \addplot coordinates {(1,14) (2,0) (3,48) (4,2) (5,0)};
+
+        \legend{yes, no}
+
+      \end{axis}
+
+\end{tikzpicture}
+\label{fig:ReadingsES-ntr}
 }
 
-\caption[Optional caption for list of figures]{Judgments for the four
-  target conditions in Experiment 1. Relative frequency of
-  \emph{yes}/\emph{no} judgments is plotted against the position
-  within the trial. In the \as-conditions there were seven
-  positions. On the third position a \emph{yes} judgment corresponded
-  to a literal reading, while on the fith position a \emph{yes}
-  judgment corresponded to a global reading.  A \emph{no} judgment on
-  the seventh position was only consistent with a local reading. The
-  \es-conditions had five positions. \emph{No} judgments on positions
-  two and three corresponded to global and literal readings,
-  respectively. A \emph{yes} judgment on the last segment corresponded
-  to a local reading.}
+\subfloat[][\as-accented]{
+% \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.1,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
+                  ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,0) (2,1) (3,69) (4,1) (5,2) (6,0) (7,4)};
+
+        \addplot coordinates {(1,0) (2,0) (3,1) (4,0) (5,0) (6,0) (7,23)};
+
+        \legend{yes, no}
+
+      \end{axis}
+
+\end{tikzpicture}
+\label{fig:ReadingsAS-acc}
+}
+\subfloat[][\es-accented]{
+% \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.2,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
+                  % ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,0) (2,11) (3,9) (4,1) (5,23)};
+
+        \addplot coordinates {(1,0) (2,1) (3,50) (4,4) (5,1)};
+
+        \legend{yes, no}
+
+      \end{axis}
+
+\end{tikzpicture}
+\label{fig:ReadingsES-acc}
+}
+
+\caption{Positional judgments for the four target conditions. The
+  plots show rounded percentages of \emph{yes}/\emph{no} judgments
+  against the position within the trial. In the \as-conditions there
+  were seven positions. On the third position a \emph{yes} judgment
+  corresponded to a literal reading, while on the fifth position a
+  \emph{yes} judgment corresponded to a global reading.  A \emph{no}
+  judgment on the seventh position was only consistent with a local
+  reading. The \es-conditions had five positions. \emph{No} judgments
+  on positions two and three corresponded to global and literal
+  readings, respectively. A \emph{yes} judgment on the last segment
+  corresponded to a local reading.}
 \label{fig:JudgmentsK2}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../pictures/graph_ec.pdf}
+\includegraphics[width=\textwidth]{../pictures/paper/graph_ec.pdf}
 \caption{Judgments for prefence-related controls (EC sequence). Relative frequencies
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../pictures/graph_lc.pdf}
+\includegraphics[width=\textwidth]{../pictures/paper/graph_lc.pdf}
 \caption{Judgments for prefence-related controls (LC sequence). Relative frequencies
@@
 
-\begin{figure}
-
-\includegraphics[width=\textwidth]{../pictures/graph_lc.pdf}
-
-\end{figure}
+% \begin{figure}
+% \includegraphics[width=\textwidth]{../pictures/graph_lc.pdf}
+% \end{figure}
 

### 2013-01-21 text/paper/paper3.tex
paper3 - third version before (almost) final

--- 2013-01-20 text/paper/paper2.tex
@@
 where the scalar item \emph{some} occurs in the scope of other logical
-operators. In \as-sentences (short for \textsc{All-Some}) as in (\ref{bsp:AE})
-the scalar item \emph{some} is embedded under universal quantifier
-\emph{all}. In \es-sentences (short for \textsc{ExactlyOne-Some}) like (\ref{bsp:GE}) \emph{some} takes
-scope under the non-monotonic quantifier \emph{exactly
-  one}.\dn{explain what non-monotonic means?  here or later?}
+operators. In \as-sentences (short for \textit{all \dots some \dots})
+as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded under
+universal quantifier \emph{all}. In \es-sentences (short for
+\textit{exactly one \dots some \dots}) like (\ref{bsp:GE}) \emph{some}
+takes scope under the non-monotonic quantifier \emph{exactly one}.
 According to current pragmatic theory, there are at least three

### 2013-01-21 text/paper/paper3.tex
paper3 - intro rewritten and added - pilot strudy removed

@@
 where the scalar item \emph{some} occurs in the scope of other logical
-operators. In \as-sentences (short for \textit{all \dots some \dots})
+operators. In \as-sentences (mnemonic for \textit{all \dots some \dots})
 as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded under
-universal quantifier \emph{all}. In \es-sentences (short for
+universal quantifier \emph{all}. In \es-sentences (mnemonic for
 \textit{exactly one \dots some \dots}) like (\ref{bsp:GE}) \emph{some}
@@
 the interface between semantics and pragmatics. The controversy
-concerns the question to what extent the upper-bounding inference from
-\emph{some} to \emph{some but not all} is conventionalized within the
-compositional computation of semantic values. For that matter, it is
-particularly relevant to assess the availability and relative
-preference of local readings. %(Section~\ref{sec:theories-predictions}
+concerns the question under which circumstances and to what extent the
+upper-bounding inference from \emph{some} to \emph{some but not all}
+can occur within the compositional computation of semantic values. Two
+opposing theoretical positions can be distinguished here:
+\emph{traditionalism} holds in particular that local readings should
+not be readily attested unless marked by special intonation;
+\emph{grammaticalism} holds that local readings are available and
+indeed preferred. To distinguish between these opposing positions, it
+is particularly relevant to assess the availability and relative
+preference of local readings for \as- and
+\es-sentences. %(Section~\ref{sec:theories-predictions}
 %will discuss the relevant theoretical positions and the significance
@@
 
-A number of empirical studies have already examined the availability
-of readings for \as- and \es-sentences
-\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. However,
-results have not been as clear-cut as one might have hoped for: for
-instance, the available empirical evidence is inconclusive as to
-whether local readings exist \citep[see also][for related
-discussion]{Tielvan-Tiel2012:Embedded-Scalar}, and previous studies 
-did not explicitly address all preference relations between readings relevant to
-distinguish between theoretical positions. In the following, we will
-argue that these heterogeneous results were partly due to the use of 
-standard procedures such as picture-verification paradigm, which might not 
-be sufficiently sensitive for the phenomenon under investigation,
-for instance, due to possible confounding effects of the pictures used.
-% We hypothesized that previous studies might be
-% insufficiently informative because of the focus on (variants of) a
-% picture-verification paradigm.\dn{relate to Bob van Tiel's work} The
-% problem is that in order to test the availability of different
-% candidate meanings different pictures have to be presented, so that
-% effects of pictorial complexity or stereotypicality could never be
-% ruled out entirely.
-Moreover, previous studies have only accumulated limited evidence
-pertaining to the second question that may help decide between
-theoretical positions, namely which of the attested readings subjects
-prefer. Finally, previous studies presented target sentences
-visually. But as it is often argued that focal stress on an
-embedded scalar item can favor a local reading
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar},
-it seems important to present target sentences auditorily, so as to be
-able to control for effects of ``silent prosody'' that subjects may
-apply when reading a sentence see Bader 1998, \citep{Fodor98}
-\dn{provide
-  references}.
-
-In reaction to this situation, we therefore presented sentence
-materials auditorily and also employed a different kind of visual
-presentation of the pictorial material.
-%: subjects were presented with
-%pictures that were initially covered and could incrementally be
-%uncovered at the subjects' request; at each step of uncovering,
-%subjects had to decide whether they could already give a truth-value
-%judgement or needed more information (Comry ????)\dn{insert
-%  references}. 
-This way we obtained behavioral data that is both
-indicative of the reading subjects assumed and independent of the
-potential pictorial and prosodic confounds. 
-%At the same time, we hypothesized
-%that the incremental nature of this task would shed light on the
-%preferences over readings, because the temporal distribution of
-%truth-value judgments would give away which reading subjects were
-%waiting to evaluate, so to speak. 
-Adding to previous studies, we made sure that our method is able to
-reveal information about reading preferences by relating our targets
-to ambiguous sentences with a well-known preference on available
+A number of empirical studies have already targeted this issue
+\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. Unfortunately,
+results from these studies do not provide as clear-cut evidence for or
+against either of the two rivaling positions as one would hope
+for. This is due to a number of reasons, the most important of which
+are the following. Firstly, previous studies have only accumulated
+limited evidence pertaining to the preference relations between
+putative readings of both types of sentences. Secondly, as
+\citet{Tielvan-Tiel2012:Embedded-Scalar} and
+\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue, the putative
+evidence for the availability of local readings of \as-sentences
+suggested by studies of \citet{CliftonDube2010:Embedded-Implic} and
+\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounds
+with what van Tiel and Geurts call \emph{typicality effects}. Finally,
+and most importantly, previous studies presented target sentences
+visually. This is highly problematic, because traditionalists admit to
+the availability of local readings as long as it is intonationally
+marked
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}.
+We
+will address this extant position as the \emph{intonational markedness
+  hypothesis}. But if intonation plays a role, it is absolutely vital
+to present target sentences auditorily, so as to be able to control
+for effects of ``silent prosody'' that subjects may apply when reading
+a sentence \citep[see][]{Bader98,Fodor98}.
+
+This paper therefore presents results form an experimental study
+designed to deal with the above mentioned problems. We presented
+sentence material auditorily and explicitly manipulated intonational
+stress on embedded scalar items so as to explicitly so as to test the
+intonational markedness hypothesis. To cater for potential pictorial
+confounds, such as from typicality
+\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi},
+we employed an \emph{incremental verification task} in which parts of
+a to-be-evaluated picture were hidden and only revealed piece-wise at
+the participants' request until they felt able to give a binary
+truth-value judgement (SEE CONROY ????). This way we obtained
+categorical behavioral data that is both indicative of the reading
+subjects assumed and independent of any potential pictorial
+confounds. We also made sure that our method is able to reveal
+information about reading preferences by including a control condition
+with ambiguous sentences with a well-known preference on available
 readings.
 
-%including ambiguous ambiguous structures, 
-%which have been shown to exhibit certain preferences in previous
-
-% like
-%(\ref{bsp:target-related-filler}) which are known to preferentially
-%receive the late-closure reading in
-%(\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
-%attested early-closure reading (\ref{bsp:target-related-filler-EC})
-%(Frazier 1987 XYZ).\dn{insert proper references}
-%\begin{exe}
-%\ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
-%  suns.
-%  \begin{xlist}
-%  \ex \label{bsp:target-related-filler-LC} The letter is connected
-%    with squares with suns and circles. \hfill (\LC)
-%  \ex \label{bsp:target-related-filler-EC} The letter is connected
-%    with circles with suns and squares with suns. \hfill (\EC)
-%  \end{xlist}
-%\end{exe}
-
-% \begin{itemize}
-% \item Fabian wants to skip the following; Petra wants to enlarge on
-%   it; I give first my version, then Petra's
-%   \begin{itemize}
-%   \item To test whether our method is indeed suitable to detect
-%     interpretation preferences, we included ambiguous test items like
-%     (\ref{bsp:target-related-filler}) which are known to
-%     preferentially receive the late-closure reading in
-%     (\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
-%     attested early-closure reading
-%     (\ref{bsp:target-related-filler-EC}).\dn{insert references to
-%       literature on EC-LC processing}
-
-%     \begin{exe}
-%     \ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
-%       suns.
-%       \begin{xlist}
-%       \ex \label{bsp:target-related-filler-LC} The letter is connected
-%         with squares with suns and circles. \hfill (\LC)
-%       \ex \label{bsp:target-related-filler-EC} The letter is connected
-%         with circles with suns and squares with suns. \hfill (\EC)
-%       \end{xlist}
-%     \end{exe}
-%   \item To test whether our method is indeed suitable to detect
-%     interpretation preferences, we included ambiguous test items like
-%     (\ref{bsp:target-related-filler}) which have been repeatedly shown
-%     to exhibit preferences in previous studies. We thus included
-%     so-called \emph{late-closure structures} in which a propositional
-%     phrase can be either attached to the immediately preceding
-%     \acro{np} (the ``late-closure'' (\LC) reading as
-%     (\ref{bsp:target-related-filler-LC})), or to an
-%     \acro{np}-coordination (the ``early-closure'' (\EC) readins as in
-%     (\ref{bsp:target-related-filler-EC})). According to principles of
-%     structural simplicity, an advantage for the \LC-reading has been
-%     repeatedly demonstrated (Frazier 1987 XYZ).\dn{insert proper
-%       references}
-%     \begin{exe}
-%     \ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
-%       suns.
-%       \begin{xlist}
-%       \ex \label{bsp:target-related-filler-LC} The letter is connected
-%         with squares with suns and circles. \hfill (\LC)
-%       \ex \label{bsp:target-related-filler-EC} The letter is connected
-%         with circles with suns and squares with suns. \hfill (\EC)
-%       \end{xlist}
-%     \end{exe}
-%     By including these structures, we intended to control whether
-%     dispreferred readings in general were still available to our
-%     participants in the specific task used.
-
-% \end{itemize}
-% \end{itemize}
-
-% To test whether our method is indeed suitable to detect interpretation
-% preferences, we included ambiguous test items like
-% (\ref{bsp:target-related-filler}) which have been repeatedly shown to
-% exhibit preferences in previous studies.
-% \begin{exe}
-% \ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
-%   suns.
-%   \begin{xlist}
-%   \ex \label{bsp:target-related-filler-LC} The letter is connected
-%     with squares with suns and circles. \hfill (\LC)
-%   \ex \label{bsp:target-related-filler-EC} The letter is connected
-%     with circles with suns and squares with suns. \hfill (\EC)
-%   \end{xlist}
-% \end{exe}
-% Sentence (\ref{bsp:target-related-filler}) is an example of a
-% so-called \emph{late-closure structure} in which a propositional
-% phrase can be either attached to the immediately preceding \acro{np}
-% (the ``late-closure'' (\LC) reading as
-% (\ref{bsp:target-related-filler-LC})), or to an \acro{np}-coordination
-% (the ``early-closure'' (\EC) readins as in
-% (\ref{bsp:target-related-filler-EC})). According to principles of
-% structural simplicity, an advantage for the \LC-reading has been
-% repeatedly demonstrated (Frazier 1987 XYZ).\dn{insert proper
-%   references}
-
-\medskip
-
-%\begin{itemize}
-%\item summarize results
-%\end{itemize}
-
-%The paper is structured as follows. Section~\ref{sec:get-know-your}
-%elaborates on the three kinds of relevant readings for our target
-%sentences. Section~\ref{sec:theories-predictions} works out the
-%different theoretical positions and their predictions about
-%availability and preference. Section~\ref{sec:previous-studies} recaps
-%the results of previous studies on this subject, arguing for the need
-%of a more refined methodology. Section~\ref{sec:design} describes our
-%experimental design. Section~\ref{sec:results} states our results,
-%which we discuss in Section~\ref{sec:discussion}.\dn{rephrase
-%  eventually}
+The data obtained by this method contradicts both traditionalism and
+grammaticalism. Contrary to traditionalism and the intonational
+markedness hypothesis, we found evidence for local readings for both
+kinds of critical sentences, irrespective of intonational stress. Even
+the intonational markedness hypothesis on its own is contradicted by
+our data: stress on embedded scalar items did not lead to an increase
+in answers suggesting a local reading. But also grammaticalism is
+incongruent with the observed pattern in our data.  Grammaticalism
+predicts local readings to be the preferred readings, but we found no
+evidence for that. More strongly even, the preference order among
+putative readings suggested by our data cannot even in principle be
+explained by the general kind of second-order selection criterion that
+is currently favored by grammaticalists, namely by comparison of
+logical strength of putative readings
+\citep[e.g.][]{ChierchiaFox2008:The-Grammatical}. In sum, our data
+sheds doubt on both traditionalism and grammaticalism in their
+currently most common forms. We conclude the paper by some speculation
+about how either position might be amended in the light of our data.
+
+The paper is structured as follows. Section~\ref{sec:get-know-your}
+elaborates on the three kinds of relevant readings for our target
+sentences. Section~\ref{sec:theories-predictions} works out the
+predictions of traditionalism and grammaticalism about availability
+and preference of readings of our target sentences. The intonational
+markedness hypothesis, which is frequently relied on to back-up
+traditionalism, is elaborated on in
+Section~\ref{sec:inton-mark-hypoth}, together with a concise
+assessment of the sparse empirical data on the effects of intonation
+on the interpretation of (embedded) scalar
+items. Section~\ref{sec:previous-studies} recaps the results of
+previous related studies, pointing out the most important necessary
+amendments that motivated out own design. Section~\ref{sec:exp}
+eventually 
+describes our experimental design and continues to state, analyze and interpret the
+results we obtained. We defend our design and the interpretation of
+the results based on it in Section~\ref{sec:conclusions}.
 
@@
 
+\section{The Intonational Markedness Hypothesis}
+\label{sec:inton-mark-hypoth}
+
+\dots bla bla bla \dots
+
 \section{Previous studies}
@@
   others?}
-
-\section{Pilot Study}
-To start off, we conducted  a pilot study  investigating whether the diverging evidence reviewed above can be explained by considerations on how sensitive the different kinds of measures are.
-This information was critical to our main experiment below.
-Because the main experiment employed categorical truth-value judgments out of methodological necessity, we wanted to test the sensitivity of this measure independently.
-In addition, the question is interesting in its own right since it has implications about the nature of the ambiguity at hand, namely whether it is due to truth-relevant meaning enrichment.
-
-In particular, we tested whether the critical effects \citet{ChemlaSpector2010:Experimental-Ev} found in their graded truth-value judgment task do also show up in a categorical truth value judgment task.
-In order to test this we simply replicated \citeauthor{ChemlaSpector2010:Experimental-Ev}'s experiment
-using a categorical truth-value judgment task.
-If, as has been suggested, categorical truth-value judgments are not sensitive enough to detect a difference of acceptance between situations like \ref{fig:weak} and \ref{fig:strong} given \as-sentences or between \ref{fig:local} and \ref{fig:all} given \es-sentences, these should be judged identical in a truth value judgment task.
-
-In addition to the conditions from  \citet{ChemlaSpector2010:Experimental-Ev} we also included another type of sentence.
-This type of sentence, \ea-sentences, contained the scalar item {\it all} embedded under {\it exactly one}.
-Here, a rather atypical kind of global implicature would be arrived at by replacing {\it all} with its weaker alternative {\it some}.
-We tested whether this kind of implicature is detectable using a truth-value judgment task.
-In the discussion of the present experiment we will, however, mainly focus on the replication of  \citet{ChemlaSpector2010:Experimental-Ev}.
-
-\subsection{Materials}
-Test sentences were German cleft-constructions as in (\ref{bsp:AS-K1})$-$(\ref{bsp:EA-K1}).
-Sentences like (\ref{bsp:AS-K1}) are \as-sentences, (\ref{bsp:ES-K1}) are \es- and  (\ref{bsp:EA-K1}) \ea-sentences.
-We decided to use cleft constructions in order to fix the relative scope of the quantifiers involved.
-This was ensured via clause-boundedness.
-In total, 48 experimental items were constructed in all three conditions yielding a total of 144 sentences.
-
-\begin{exe}
-\ex \gll F\"{u}r \mymark{jedes} dieser Kinder gilt: es
-  mag \mymark{einige} dieser Speisen. \label{bsp:AS-K1}\\
-  For every {of these} children {it holds} it likes some {of
-    these} dishes.\\
-  For all of these children it holds that it likes some of these dishes.
-\end{exe}
-\begin{exe}
-\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es
-  mag \mymark{einige} dieser Speisen. \label{bsp:ES-K1}\\
-  For exactly one {of these} children {it holds} it likes some {of
-    these} dishes.\\
-  For exactly one of these children it holds that it likes some of these dishes.
-\ex \gll F{\"u}r \mymark{genau eines} dieser Kinder gilt: es mochte \mymark{jede} dieser Speisen.  \label{bsp:EA-K1}\\
-For exactly\ one of\ these children it\ holds: it likes some of\ these dishes.\\
-Exactly one of\ these children it holds that it likes some of\ these dishes.\\
-\end{exe}
-
-The sentences were paired with pictures like in Figures \ref{fig:AS-distinguishing-pics}, \ref{fig:ES-distinguishing-pics}, \label{fig:EA}.
-For \es- and \as-sentences  there were four types of situations just as in  the study of \citet{ChemlaSpector2010:Experimental-Ev}.
-Sentences in the \as-condition were paired with situations as in \ref{fig:literal-AE}, \ref{fig:false-AE}, \ref{fig:weak}, \ref{fig:strong}.
-Sentences in in the \es-condition were paired with \ref{fig:literal-GE},\ref{fig:literal-GE},\ref{fig:local} and \ref{fig:all}.
-The \ea-sentences were paired with pictures like in \ref{fig:EA}.
-Figure \ref{fig:EA-LIT} is only true under the literal reading ({\it literal} diagrams) while  Figure \ref{fig:EA-LITGLB} is also true with respect to the global implicature ({\it global} diagrams) denying the weaker scalar alternative containing {\it einige} (some).
-Diagrams like those in Figures \ref{fig:EA-FALSE1} and \ref{fig:EA-FALSE2} were not compatible with the \ea-sentences.
-Figure \ref{fig:EA-FALSE1} is incompatible because there are too few connections.
-Figure \ref{fig:EA-FALSE2} is incompatible because there are too many connections.
-We used two types of incompatible pictures only because of technical reasons.
-
-In total, this yielded twelve conditions and 576 pictures.
-The conditions were distributed over twelve lists according to a latin square design ensuring that in each list every item was only present in one condition.
-In addition, to the target sentences, 201 (?) distractors were included in each list.
-Of these $n$ were intended to yield a "yes true" response, $m$ were false.
-
-%\begin{figure}[t]
-%  \centering
-% 
-%\begin{minipage}{6cm}
-%     \subfloat[][literal]{
-%    \label{fig:EA-LIT}
-%        \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer09.eps}
-%  }
-%
-%  \subfloat[test][global]{
-%    \label{fig:EA-LITGLB}
-%    \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer10.eps}
-%  }  
-%   \end{minipage}
-%   \begin{minipage}{6cm}
-%     \subfloat[][false1]{
-%    \label{fig:EA-FALSE1}
-%        \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer11.eps}
-%  }
-%
-%  \subfloat[test][false2]{
-%    \label{fig:EA-FALSE2}
-%    \includegraphics[width=5.5cm]{../pictures/Umweltschuetzer12.eps}
-%  }  
-%   \end{minipage}
-%        \caption{}
-%\label{fig:EA}
-%\end{figure}
-
-\subsection{Procedure}
-The present pilot study was conducted as part of a dual task experiment employing picture verification and a sternberg task \cite{Sternberg1966}.
-In some trials participants had to solve a memory task in addition to the picture verification task.
-In the {\it high load} condition participants had to remember six letters while performing the picture verification.
-In the {\it low load} condition they had to remember one letter and in the {\it no load} condition they didn't have to remember anything while they were performing the picture verification.
-In the {\it memory only} conditions they only had to perform a memory task (i.e.
-remember one or six letters) but no picture verification.
-All the critical items of the present experiment were presented in the {\it no load} condition.
-Only distractor items were presented in one of the dual task conditions.
-
-In each trial participants were first asked to indicate readiness by
-pressing a button. In the {\it no load} condition, after they had
-pressed the button an asterisk was flashed on the screen six times
-within $7.2s$. Then a sentence and a picture were presented
-simultaneously. Within $12s$ participants had to judge whether the
-sentence was true with respect to the picture. They indicated their
-judgment by pressing one of two buttons. After they had provided their
-judgment the next trial started automatically. If they did not respond
-within twelve seconds, the next trial was started. Judgments and
-reaction times were logged.\footnote{In the {\it low load} and {\it
-    high load} condition a trial looked similar to a trial in the {\it
-    no load} condition except for two things. Firstly, in the dual
-  task conditions instead of asterisks letters were flashed on the
-  screen. Secondly, after finishing the picture verification task a
-  question appeared on the screen probing for a letter. Participants
-  had to indicate by pressing a button whether they thought the letter
-  had been present in the array from the beginning of the
-  trial. Except for one difference, the {\it memory only} trials were
-  identical to the dual task trials. In {\it memory only} trials the
-  picture verification part was replaced with a blank screen. That is,
-  in the middle of such trials the screen stayed blank for $5s$. }
-
-The experiment started with a practice session consisting of $25$ trials divided into three blocks (1st block: memory task only, ten trials; 2nd block: picture verification only, five trials; 3rd block: dual task, ten trials).
-Then one list consisting of 249 trials divided into three blocks was presented.
-An experimental session took about 75 minutes.
-During the whole experiment no feedback was provided to the participants.
-
-\subsection{Participants}
-60 native German speakers (40 female, mean age: $24$, ranging between $20$ and $40$) from the University of T{\"u}bingen participated in the study.
-Participants were na\"ive to the purpose of the study.
-They were paid \euro{10} compensation.
-
-\subsection{Results}
-Overall participants were able to solve the task.
-In the distractor items the picture verification was done accurately in $88\%$ ($sd: 33\%$) of the cases.
-All participants were above $70\%$ and significantly better than chance.
-On average it took participants $4989ms$ ($sd:2176ms$) to come up with their answer in the filler trials.
-We will now consider results for the three sentence conditions in turn.
-
-The mean judgments we obtained for \as-sentences are depicted in Figure \ref{fig:AEBars}.
-The {\it strong} diagrams were judged to be true in $90\%$ of the cases, {\it weak} diagrams received "yes" judgments in $79\%$ , {\it literal} diagrams in  $72\%$  and {\it false} in $0.9\%$ of the trials.
-A logit mixed effects model with binomial link function containing a fixed effect of {\it diagram} as well as random effects of items and participants revealed a clear effect of {\it diagram}.
-In particular {\it false}, {\it literal} and {\it weak} diagrams all received fewer "yes" judgments than {\it strong} diagrams (all $p<.001$).
-Another logit mixed effects model only modeling data for {\it literal} and {\it weak} diagrams also revealed an reliable effect of {\it diagram} (p<.05).
-Finally, a model only considering  {\it false} and {\it literal} diagrams also revealed a significant effect of {\it diagram} (p<.001).
-
-%\begin{figure}[t]
-%  \centering
-% 
-%
-%     \subfloat[][\as]{
-%    \label{fig:AEBars}
-%        \includegraphics[width=5cm]{../pictures/JudgmentsAllSomeBars.eps}
-%  }
-%  \subfloat[test][\es]{
-%    \label{fig:GEBars}
-%    \includegraphics[width=5cm]{../pictures/JudgmentsExactlySomeBars.eps}
-%  }  
-%  
-%        \caption{Mean judgments}
-%\label{fig:BarsPilot}
-%\label{fig:EA}
-%\end{figure}
-
-The responses for \es-sentences are summarized in Figure \ref{fig:GEBars}.
-Unsurprisingly, these sentences were accepted as truthful description of {\it false} diagrams in only $0.8\%$ of all cases.
-The {\it local} diagrams received  "yes" responses in $20\%$, {\it literal} in $71\%$ and {\it all} in $93\%$ of the time.
-A logit mixed effects model with {\it diagram} as fixed effect as well as item and participant as random effects revealed a significant effect of {\it diagram}.
-The {\it all}, {\it literal} and {\it local} diagrams were all accepted more often than the {\it false} diagram (all $p<.001$).
-A simpler model only considering {\it local} and {\it literal} diagrams revealed a reliable effect of {\it diagram} (p<.001) as did a model only considering {\it literal} and {\it all} diagrams (p<.001).
-
-The mean responses for the \ea-sentences are shown in table \ref{}. The observed difference between the global and literal diagrams is
-significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$).
-
-\begin{center}
-  \begin{tabular}{cccc}
-    \multicolumn{4}{c}{\as-sentences}  \\
-    \hline
-    literal & global & false1 & false2
-    \\ \midrule 
-    98.3 & 90.3 & 7.1 & 3.3 
-  \end{tabular}
-\end{center}
-
-\subsection{Discussion}
-
-Concerning the \as- and \es-sentences the observed distribution of judgments were rather similar to the results from \citeauthor{ChemlaSpector2010:Experimental-Ev}.
-Qualitatively, the only notable difference lies in the rather low acceptance of situations like \ref{fig:literal-AE} in the present experiment as compared to \citeauthor{ChemlaSpector2010:Experimental-Ev}'s original study.
-Crucially, similar to the findings of \citeauthor{ChemlaSpector2010:Experimental-Ev}, we found that situation \ref{fig:strong} was more often accepted than situation \ref{fig:strong} and that situation \ref{fig:local} was accepted more often than situation \ref{fig:false-GE}.
-This suggests that local readings are available and are even detectable via categorical truth-value judgments.
-
-However, we have to be careful with our interpretation of the results.
-Since the picture materials differd drastically in the critical comparisons, we cannot exclude pictorial effects.
-As reviewed above  \citeauthor{Tielvan-Tiel2012:Embedded-Scalar} did even show that with regards to the \as-sentences the differences in acceptance reported by C\&S and therefore presumably also the replicated results presented here can be explained by typicality of the pictures with respect to the sentence meaning.
-
-That truth is not the only determining factor affecting truth-value judgments also becomes evident from the distribution of judgments we obtained for the \ea-sentences.
-The observed difference  between \ref{fig:EA-LIT} and \ref{fig:EA-LITGLB}  is a curious finding at first sight.
-Firstly, the literal reading is true in both situations.
-Secondly, from the point of view of implicature calculation, the only thing that could plausibly explain an acceptability difference between these two situations is the presence of a global implicature, resulting from the negation of the corresponding \es-sentence.\fn{Notice that (\ref{bsp:EA}) is the alternative to the corresponding \es-sentence needed for computing the putative global implicature.
-But these sentences are logically independent.
-So, it
-  may be that the corresponding \es-sentence is an alternative also to sentences like (\ref{bsp:EA}). It may also be that being an
-  alternative is not a symmetric notion. Be that as it may, our argument does not hinge on whether (\ref{bsp:EA}) does or does not
-  actually have a global implicature of the alleged kind.} However, this putative global implicature would be true in the
-situation \ref{fig:EA-LITGLB}, but false in the situation \ref{fig:EA-LIT}. Consequently, the observed difference
-in acceptability cannot be explained simply in terms of the hypothesis
-of \citet{ChemlaSpector2010:Experimental-Ev} that acceptability increases with  the number of available true readings.
-Rather this finding, just as  \citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s study, suggests that some
-feature of the pictorial material that is independent of the putative readings under scrutiny does affect truth-value judgments, even
-categorical ones.
-
-We conclude that  effects of pictorial complexity and/or typicality are real and affect even categorical judgments.
-For this reason the following experiment was set up to investigate the availability of local readings while minimizing pictorial effects such as typicality or complexity.
 

### 2013-01-21 text/paper/paper3.tex
paper3 - sec com

@@
 where all of the students read some but not all of the papers is a
-special case of the case where all of the students read some (and
-maybe all), while not all of the students read all of the papers.
+special case of the set of situations where all of the students read
+some (and maybe all), while not all of the students read all of the
+papers.
 
@@
 papers and an arrow from a student to a paper indicates that the
-student read the paper.\dn{improve graphics} Notice that other
-arrangements of arrows might equally well serve as examples for the
-various situations.
+student read the paper. Notice that other arrangements of arrows might
+equally well serve as examples for the various situations.
 
@@
 
-We consider two main theoretical positions which make different
+There are two main theoretical positions which make different
 predictions about the readings of \as- and \es-sentences
@@
 and goal-oriented. Usually, the assumed goal of conversation is the
-cooperative exchange of helpful information from the speaker to the
-hearer.
+cooperative exchange of relevant information from speaker to hearer.
 
@@
 \es-sentences in general than for simpler sentences such as
-(\ref{bsp:Plain-SI}), because of the additional quantificational
-element: it might be less clear that the speaker knows exactly how
-many students solved how many problems, than that the speaker knows
-exactly how many problems, e.g., Hans solved. In that case, or if any
-other assumption of the Gricean recipe cannot be maintained,
-traditionalism would predict that the literal reading would be
-preferred over the global one. But that means that there are at least
-two varieties of traditionalism that, depending on which additional
-assumptions we would make, yield slightly different predictions:
-\mymark{the strong variety of traditionalism} maintains that the
-auxiliary assumptions of the Gricean recipe hold
+(\ref{bsp:Plain-SI}): it might be less clear that the speaker knows
+exactly how many students solved how many problems, than that the
+speaker knows exactly how many problems, e.g., Hans solved. In that
+case, or if any other assumption of the Gricean recipe cannot be
+maintained, traditionalism would predict that the literal reading
+would be preferred over the global one. But that means that there are
+at least two varieties of traditionalism that, depending on which
+additional assumptions we would make, yield slightly different
+predictions: \mymark{the strong variety of traditionalism} maintains
+that the auxiliary assumptions of the Gricean recipe hold
 usually/strongly/unless-completely-intenable and therefore predicts
@@
   depends on which auxiliary assumptions are assumed to be met and
-  which are not.}\dn{acknowledge comment by Philippe Schlenker
-  here;possibly expand}
+  which are not.}
 
@@
 then there is no proposition $Z$ such that $X$ would be equivalent to
-$Y \wedge \neg Z$. Traditionalism often does concede that (something
-like) local readings can occur if scalar items are marked with
-\emph{special accentuation}, albeit then as a signal of a different
-pragmatic process
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic}. We
-will come back to this issue in Section~\ref{sec:local-read-categ}.
+$Y \wedge \neg Z$.
 
@@
 
-\dots bla bla bla \dots
+\begin{itemize}
+\item Traditionalism often does concede that (something like) local
+  readings can occur if scalar items are marked with \emph{special
+    accentuation}, albeit then as a signal of a different pragmatic
+  process
+  \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic}. We
+  will come back to this issue in Section~\ref{sec:local-read-categ}.
+\end{itemize}
 
@@
 modified version of picture verification, namely the
-\mymark{incremental verification task} (\acro{ivt}, see Conroy
-???)\dn{reference}. The general idea is that subjects are requested to judge
+\mymark{incremental verification task} (\acro{ivt}, SEE CONROY
+????). The general idea is that subjects are requested to judge
 sentence material based on pictures that do not necessarily contain

### 2013-01-21 text/paper/paper3.tex
paper3 - sec com

@@
 Does traditionalism also predict local readings to be available? The
-answer is slightly different for \as- and the \es-sentences. For
-\es-sentences, traditionalism does not predict that a local reading is
-available, at least not as a quantity implicature
+answer is slightly different for \as- and the \es-sentences.\fn{Some
+  traditionalists concede that (something like) local readings can
+  occur for both kinds of sentences if scalar items are marked with
+  special accentuation, albeit then as a signal of a different
+  pragmatic process
+  \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic}. We
+  will address this addition to traditionalism in more detail in
+  Section~\ref{sec:inton-mark-hypoth}.} For \es-sentences,
+traditionalism does not predict that a local reading is available, at
+least not as a quantity implicature
 \citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. This
@@
 
-The third and final kind of theoretical position we consider is
+The other currently prominent theoretical position is
 \mymark{grammaticalism}. Recently, a lot of evidence based on
@@
 that it must be constrained in some way or other to shield the
-approach against overgeneration. The easiest examples where this is
-crucial are occurrences of scalar items in downward-entailing
-environments, such as in:
-
-\begin{exe}
-\ex \label{bsp:Overgenereation-target} It's \mymark{not} the case that
-  Hans solve \mymark{some} of the problems.
-\end{exe}
-
-\noindent An assertion of (\ref{bsp:Overgeneration-continued})
-normally would be taken to convey
-(\ref{bsp:Overgenereation-implicature-attested}), not the disjunctive
-meaning in (\ref{bsp:Overgenereation-implicature-UNattested}).
-
-\begin{exe}
-\ex 
-  \begin{xlist}
-  \ex \label{bsp:Overgenereation-implicature-attested} Hans solves \mymark{none} of the problems.
-  \ex \label{bsp:Overgenereation-implicature-UNattested} Hans solved
-    \mymark{none or all} of the problems 
-  \end{xlist}
-\end{exe}
-
-\noindent The latter, however, is a reading that grammaticalism
-predicts to be available by letting the $\exh(\cdot)$-operator take
-scope under negation, as in:
-
-\begin{exe}
-\ex It's not the case that Hans solved \mymark{$\exh$}(\mymark{some} of the problems)
-\end{exe}
-
-\noindent Indeed, this reading is not unattested, for witness a
-continuation of (\ref{bsp:Overgenereation-target}) as in:
-\begin{exe}
-\ex \label{bsp:Overgeneration-continued} It's \mymark{not} the case that Hans
-  solve \mymark{\emph{some}} of the problems. He solved
-  \mymark{\emph{all}} of them.
-\end{exe}
-
-\noindent But this reading seems to be marked, in that it requires
-exceptional contextual circumstances and a non-standard intonational
-stress.
-
-To account for the markedness of certain examples, grammaticalism is
-therefore aided by a principle that specifies which readings are to be
-preferred if several readings are generated by optional applications
-of $\exh(\cdot)$ in the compositional computation of semantic
-values. The principle that grammaticalists adhere to
+approach against overgeneration. Grammaticalism is therefore aided by
+a principle that specifies which readings are to be preferred if
+several readings are generated by optional applications of
+$\exh(\cdot)$ in the compositional computation of semantic values. The
+principle that grammaticalists adhere to
 \citep[c.f.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}
@@
 
-\begin{itemize}
-\item Traditionalism often does concede that (something like) local
-  readings can occur if scalar items are marked with \emph{special
-    accentuation}, albeit then as a signal of a different pragmatic
-  process
-  \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic}. We
-  will come back to this issue in Section~\ref{sec:local-read-categ}.
-\end{itemize}
+Although traditionalism does not of itself predict local readings to
+be available, many authors who adhere to a traditionalist position
+acknowledge that local readings are available if and only if the
+embedded scalar item is intonationally marked by contrastive stress
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Scalar-expressi}. This
+is taken to be continuous with other cases where pragmatic enrichments
+can take scope under logical operators if and only if the relevant
+focal accent is present (\ref{bsp:Stress}).
+
+\begin{exe}
+\ex \label{bsp:Stress} This coffee is not \textsc{hot}, it's \textsc{HOT}.
+\end{exe}
+
+\noindent The
+intonational markedness hypothesis, as we will call it here, is then
+an addition to the traditionalist's explanation of scalar implicatures
+along the lines of the Gricean recipe. The crucial point is that under
+this extra assumption, local readings are a marked phenomenon. If
+supplemented with the intonational markedness hypothesis,
+traditionalists would therefore predict that local readings are
+available for \as- and \es-sentences, but only if intonationally
+marked by contrastive stress; since this reading is marked, presumably
+it would still be predicted to be dispreferred even if available.
+
+Though there seems to be general consensus about such potential
+prosodic effects, empirical evidence for this assumption is still
+scarce. One notable exception comes from a pilot study reported in
+\citet{Frazier08}, in which participants were instructed to read
+embedded and non-embedded versions of English \as-sentences. In the
+embedded sentences (e.g. {\it All of the students wrote some of the
+  official memos}), {\it some} was either capitalized or
+non-capitalized. Prior to the experiment, participants were informed
+that capitalizing corresponded to contrastive stress. The task
+consisted in a forced-choice questionnaire with two given alternatives
+(such as {\it All of the students wrote some but not all of the
+  official memos} vs. {\it All of the students wrote at least some of
+  the official memos}). Interestingly, strengthened interpretations
+occurred rather often across all sentences in this task (59 \%), but
+were not affected by capitalizing.\fn{Note that, unfortunately, the
+  authors do not provide percentages for the embedded conditions
+  alone, but only the means across sentence types.}
+\citeauthor{Frazier08} concludes that accentuation did not affect
+their silent reading data, but raises the possibility that prosodic
+effects may have been present at least in a subset of the items (see
+footnote~1 in \citet{Frazier08}, p.~330).
+
+Another study relevant for the present considerations comes from
+\citet{SchwarzClifton2008:Strengthening-o}, examining the effects of
+contrastive accentuation of "or" in non-embedded sentences like {\it
+  Mary will invite Fred or/OR Sam to barbecue}. After listening to
+these sentences, participants were presented two alternative readings
+({\it 1. She will invite Fred or Sam or possibly both}, or {\it 2.
+  She will invite Fred or Sam but not both}). Contratry to the
+silent-prosodic effects reported in the pilot experiment by Frazier
+and colleagues, the authors found a significant impact of overtly
+realized contrastive accents on implicature processing: Besides a
+general advantage for non-strengthened readings, focal accents
+significantly increased the strengthened interpretation (from 16.4 \%
+to 28.6 \%). These results are compatible with the "focus
+strengthening hypothesis" proposed by the authors.
+
+To sum up so far, though an effect of contrastive accentuation has
+been claimed tobe essential for triggering local implicatures,
+experimental evidence is currently mixed, suggesting potential effects
+of presentation mode (visual vs.~auditory), item-specific
+characteristics, as well as the specific construction under
+investigation (e.g., embedded cases vs.~non-embedded cases such as in
+\citet{SchwarzClifton2008:Strengthening-o}). It is for these reasons
+that an experimental investigation into the availability of readings
+of \as- and \es-sentences should present sentential material
+auditorily and explicitly address the intonational markedness
+hypothesis.
 
@@
 
-In order to disentangle the divergent predictions of these opposing
-theoretical positions, a number of empirical studies have been carried
-out. In this section, we will focus on the influential studies by
+In order to test the divergent predictions of the relevant theoretical
+positions, a number of empirical studies have been carried out. In
+this section, we will focus on the influential studies by
 \citet{GeurtsPouscoulous2009:Embedded-Implic},
@@
 picture-verification task to find out whether local readings of \as-
-and \es-sentences are available.\fn{We will focus here on a subset 
-of the conditions tested by
-  \citet{GeurtsPouscoulous2009:Embedded-Implic}. Moreover, note that these authors did not use
-  \es-sentences, but sentences where scalar \emph{some} was embedded
-  under non-monotonic quantifier \emph{exactly two} (with appropriate
-  pictures, of course). This case is a little more complex, but we
-  will gloss over this here, treating their data, as if it was obtained
-  for \es-sentences.} Subjects were presented with pictures like 
-  those in Figure~\ref{fig:weak} and
+and \es-sentences are available.\fn{We will focus here on a subset of
+  the conditions tested by
+  \citet{GeurtsPouscoulous2009:Embedded-Implic}. Actually, these
+  authors did not use \es-sentences, but sentences where scalar
+  \emph{some} was embedded under non-monotonic quantifier
+  \emph{exactly two} (with appropriate pictures, of course). This case
+  is a little more complex, but we will gloss over this here, treating
+  their data, as if it was obtained for \es-sentences.} Subjects were
+presented with pictures like those in Figure~\ref{fig:weak} and
 \ref{fig:local} where the local reading gets a different truth-value
-from the literal and the global reading. For
-\as-sentences, the local reading is false for the critical picture in
-Figure~\ref{fig:weak} whereas the literal and global readings are
-true; for \es-sentences the local reading is true for the critical
-picture in Figure~\ref{fig:local}, whereas the literal and global
-readings are false.\dn{Petra wants more detail in the description of
-  this study; I'm not sure that this is needed...?}
+than the literal and the global reading. For \as-sentences, the local
+reading is false for the critical picture in Figure~\ref{fig:weak}
+whereas the literal and global readings are true; for \es-sentences
+the local reading is true for the critical picture in
+Figure~\ref{fig:local}, whereas the literal and global readings are
+false.
 
@@
 \citet{Sauerland2010:Embedded-Implic}, but see
-\citet{Ippolito2010:Embedded-Implic} for supporting evidence), as well
-as based on empirical observations
+\citet{Ippolito2010:Embedded-Implic} for support), as well as based on
+empirical observations
 \citep{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. In
@@
 \citeauthor{GeurtsPouscoulous2009:Embedded-Implic} and
-\citeauthor{CliftonDube2010:Embedded-Implic} demonstrate that
-participants' choices for \as-readings might be strongly affected by
-the specific experimental paradigm used. If task demands are only
-felicitous for a literal reading, the \emph{absence} of choices of
-local readings cannot be accounted for by assuming an unavailability
-of these readings \emph{per se}.\dn{micha does not understand this
-  sentence} However, at present it is less clear whether these results
-can also be generalized to further situations. For instance, subjects
-rejected the \es-sentences in Geurts and Poscoulous' original study,
-despite the fact that they could have accepted them based on the local
-reading. It is thus necessary to test both universal and non-monotonic
-quantifiers within the same experiment. Additionally, it would be
-informative to also probe into the availability of global
-readings. The study of \citet{ChemlaSpector2010:Experimental-Ev} did
-both of that.
+\citeauthor{CliftonDube2010:Embedded-Implic} seem to indicate that
+participants' choices for readings of \as-sentences might be affected
+by the specific experimental paradigm used \citep[but see][for
+critique of the latter
+design]{GeurtsTielvan-Tiel2013:Scalar-expressi}. Unfortunately,
+\citet{CliftonDube2010:Embedded-Implic} did not test both universal
+and non-monotonic quantifiers within the same
+experiment. Additionally, it would be informative to also probe into
+the availability of global readings. The study of
+\citet{ChemlaSpector2010:Experimental-Ev} did both of that.
 
@@
 \ref{fig:ES-distinguishing-pics}. Additionally, subjects were asked,
-not for categorial judgements, but for \mymark{graded judgements}:
+not for categorial judgements, but for \textit{graded judgements}:
 subjects could freely click on a scale, as shown in
@@
 \citet{GeurtsPouscoulous2009:Embedded-Implic} did not observe any
-truth value judgments that would indicate local readings. On the basis
+truth value-judgments that would indicate local readings. On the basis
 of this observation, they argue that these readings are simply not
@@
 between \emph{categorical} truth-value judgments and other more
-sensitive measures. Firstly, it could be hypothesized along with
+sensitive measures. If we do so, it could be hypothesized along with
 \citeauthor{CliftonDube2010:Embedded-Implic} and
@@
 in favour of truth-value judgments as a means of detecting highly
-dispreferred readings).  Secondly it could also be argued, in line
-with traditionalism, that the apparent difference in sensitivity of
-the different judgment types can be explained by the stipulation that
-the results reported by \citeauthor{CliftonDube2010:Embedded-Implic}
-and \citeauthor{ChemlaSpector2010:Experimental-Ev} reflect something
-other than (strongly) truth-relevant speaker-intended meaning
-enrichments after all, so that no case can be made for lexicalism or
+dispreferred readings).  It could then also be argued, in line with
+traditionalism, that the apparent difference in sensitivity of the
+different judgment types can be explained by the stipulation that the
+results reported by \citeauthor{CliftonDube2010:Embedded-Implic} and
+\citeauthor{ChemlaSpector2010:Experimental-Ev} reflect something other
+than (strongly) truth-relevant speaker-intended meaning enrichments
+after all, so that no case can be made for lexicalism or
 grammaticalism on the basis of these data \citep[c.f.][for arguments
-along these lines]{Tielvan-Tiel2012:Embedded-Scalar}.
+along these
+lines]{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}. To
+circumvent this issue, a method for probing into the readings
+for \as- and \es-sentences would therefore ideally evoke categorical
+truth-value judgements: if evidence for local readings can also be
+found using categorical truth-value judgements, it cannot be discarded
+as a secondary non-truth-conditional effect.
 
@@
 combinations shown during the experiment affects the standard of
-judgment but could~-- maybe more elegantly~-- also be explained by
+judgment but could also --maybe even more elegantly-- be explained by
 findings from \citet{Raffray2010} suggesting that exposing
@@
 \citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} would also show up
+\citeauthor{ChemlaSpector2010:Experimental-Ev} would not also show up
 using ordinary picture verification, in the first place.
@@
 explained as typicality effects, dispensing the need to appeal to the
-distribution of different
-readings. \citet{Tielvan-Tiel2012:Embedded-Scalar} elicited what he
-calls the typicality structures associated with the quantifiers {\it
-  all} and {\it some} and predicted the judgments of \as-sentences
-obtained by \citeauthor{ChemlaSpector2010:Experimental-Ev} based on
-these data. Thereby, he obtained an excellent model fit. We are
-sympathetic towards \citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s
-innovative line of reinterpretation of the data, but note, as
+distribution of different readings. In support of this idea,
+\citet{Tielvan-Tiel2012:Embedded-Scalar} elicited what he calls the
+typicality structures associated with the quantifiers {\it all} and
+{\it some} \citep[as done also by][]{DegenTanenhaus2011:Making-Inferenc} and predicted the judgments of \as-sentences obtained by
+\citeauthor{ChemlaSpector2010:Experimental-Ev} based on these
+data. Thereby, he obtained an excellent model fit.
+
+We are generally sympathetic towards
+\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
+reinterpretation of the data, but note, as
 \citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
 typicality-based explanation does not extend to \es-sentences in an
-obvious way.
-  % \fn{For similar reasons, appeal to typicality cannot
-  % explain, as far as we can see, the preference for the situation in
-  % Figure~\ref{fig:literal-EA} over that in Figure\ref{fig:global-EA}
-  % given a sentence like (\ref{bsp:EA}).}
+obvious way. Moreover, typicality itself is not a satisfactory
+primitive in a putative explanation of the pragmatic use of
+quantifiers. Plausibly, the reason why quantifier \emph{some} is more
+typical for some set sizes than others is at least dependent on, if not
+entirely derived from, its contrast with other conceivable
+alternatives, e.g., numerals within the subitizing range, as well as
+\emph{few}, \emph{most} or \emph{many}
+\citep[c.f.][]{DegenTanenhaus2012:Processing-Scal}. For these reasons,
+we believe that typicality and other pictorial effects need to be
+taken seriously in the experimental design, but do not give a
+satisfactory account of the observed variation all by themselves.
 
@@
 readings even if they are dispreferred. Given the logical dependencies
-of the relevant readings this seems almost impossible to achieve. As
-we will argue below we do, however, believe it is.
+of the relevant readings this is difficult, but, as we will argue
+below, not impossible.
 
@@
 variation \citep[e.g.][]{Augurzky08,Bader98,Fodor98,Fodor02,Kentner12,
-Steinhauer01}. As it has been suggested in the theoretical
-literature that the availability of a local reading might hinge on the
-realization of contrastive stress on the scalar item,
-%Even traditionalism maintains that local
-%readings are attested, but requiring a contrastive stress on the
-%scalar item
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}, it is necessary to
-control for potential variation due to potential differences in silent accent placement.
-We therefore presented sentences auditorily and addressed the frequently proposed claim 
-that local readings are triggered by contrastive
-stress.\dn{relate to \citet{SchwarzClifton2008:Strengthening-o} and
-  others?}
+  Steinhauer01}. If we adopt the intonational markedness hypothesis
+described in Section~\ref{sec:inton-mark-hypoth}, as many
+traditionalists do, we predict that the availability of a local
+reading hinges on the realization of contrastive stress on the scalar
+item
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}.
+But if intonation can have this role, it is necessary to control for
+this potential variation due to potential differences in silent accent
+placement. Ideally, therefore, we should present sentences auditorily
+and test the intonational markedness hypothesis explicitly by
+manipulating contrastive stress systematically.
 
@@
 
-\paragraph{Testing Effects of prosody.}\dn{These two paragraphs
-  still need a proper home; Petra opts for ``materials'' section.
-  - Petra's comment: wenn wir's wie jetzt etwas ausführlicher diskutieren, 
-  kann's auch gerne hier bleiben}
-
-The availability of local readings has often been claimed to be
-affected by the presence or absence of a focal accent on the scalar
-item. By contrastively accenting the scalar, potential alternatives
-are highlighted, resulting in more implicatures being computed. Some 
-approaches have even claimed that local readings exclusively 
-emerge when the scalar item is accented and are otherwise generally
-unavailable \citep[e.g.][]{Horn2006:The-Border-Wars,
-Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,
-Tielvan-Tiel2012:Embedded-Scalar}.
-
-Though there seems to be general consensus about these potential 
-prosodic effects, empirical evidence for this assumption 
-is still scarce. One notable exception comes from a pilot study 
-reported in \citet{Frazier08}, in which participants were 
-instructed to read embedded and non-embedded versions of English 
-\as-sentences. In the embedded sentences (e.g. {\it All of the students 
-wrote some of the official memos}), {\it some} was either capitalized 
-or non-capitalized. Prior to the experiment, 
-participants were informed that capitalizing corresponded to contrastive 
-stress. The task consisted in a forced-choice questionnaire with two
-given alternatives (such as {\it All of the students wrote some but 
-not all of the official memos}  vs. {\it All of the students wrote at 
-least some of the official memos}). Interestingly, strengthened  
-interpretations occurred rather often across all sentences in this task 
-(59 \%), but were not affected by capitalizing. \fn{Note that, 
-unfortunately, the authors do not provide percentages for the embedded 
-conditions alone, but only the means across sentence types.} The authors 
-conclude that accentuation did not affect their silent reading data, 
-but raise the possibility that prosodic effects may have been present 
-at least in a subset of the items (see footnote 1 in \citet{Frazier08}, 
-p. 330).
-
-Another study relevant for the present considerations comes from 
-\citet{SchwarzClifton2008:Strengthening-o}, examining the effects of 
-contrastive accentuation of "or" in non-embedded sentences like {\it 
-Mary will invite Fred or/OR Sam to barbecue}. After listening to these 
-sentences, participants were presented two alternative readings 
-({\it 1. She will invite Fred or Sam or possibly both}, or {\it 2. 
-She will invite Fred or Sam but not both}). Contratry to the silent-prosodic 
-effects reported in the pilot experiment by Frazier and colleagues, the 
-authors found a significant impact of overtly realized contrastive accents 
-on implicature processing: Besides a general advantage for non-strengthened 
-readings, focal accents significantly increased the strengthened interpretation 
-(from 16.4 \% to 28.6 \%). These results are compatible with the "focus 
-strengthening hypothesis" proposed by the authors.
-
-To sum up so far, though an effect of contrastive accentuation has been 
-claimed tobe essential for triggering local implicatures, experimental evidence 
-is currently mixed, suggesting potential effects of presentation mode (visual vs. 
-auditory), item-specific characteristics, as well as the specific construction 
-under investigation (e.g. embedded cases vs. non-embedded cases such as in 
-\citet{SchwarzClifton2008:Strengthening-o}).
-
-Whereas contrastive accents are usually assumed to be realized by a special 
-contour in English (i.e. L+H*, see \citet{Pierrehumbert90}), 
-the exact phonological classification of contrast in German is still under 
-debate \citep[see][]{Uhmann91,Fery93,Grabe98,Toepel06, Sudhoff10}. 
-These approaches have in common that from an acoustic perceptive, prosodic 
+\paragraph{Testing Effects of prosody.} Whereas contrastive accents
+are usually assumed to be realized by a special contour in English
+(i.e. L+H*, see \citet{Pierrehumbert90}), the exact phonological
+classification of contrast in German is still under debate
+\citep[see][]{Uhmann91,Fery93,Grabe98,Toepel06, Sudhoff10}.  These
+approaches have in common that from an acoustic perceptive, prosodic
 prominence of contrastively accented constituents is realized by

### 2013-01-21 text/paper/paper3.tex
paper3 - up to general discussion

@@
 of the different readings. In addition, we wanted
-to minimize effects of graphical differences between the picture
-materials. To achieve this, we designed an experiment employing a
+to minimize all effects of alleged typicality of pictures. To achieve this, we designed an experiment employing a
 modified version of picture verification, namely the
@@
 all the information necessary to judge a certain reading true or
-false. In that case, participants can demand that more information is
+false. In that case, participants can demand that more information be
 revealed. Participants are instructed to make a truth-value judgment
-as soon as they are able to.\dn{need to mention somewhere that trial
-  ends with each TV judgment}
+as soon as they are able to. When they do, the trial ends.
 
 \paragraph{Target Conditions.} In the present study, participants were
-presented pictures
-%, like those in
-%Figures~\ref{fig:InitialPicture}, \ref{fig:exseqAS} or
-%\ref{fig:exseqES}, 
-depicting a set of four identical central elements
-(e.g., letters), which could be connected to surrounding elements
-(e.g., triangles). Initially, any potential connections between
-central and surrounding elements were covered by dark gray color (see
-Figure~\ref{fig:InitialPicture}).
+presented with pictures depicting a set of four identical central
+elements (e.g., letters), which could be connected to surrounding
+elements (e.g., triangles). Initially, any potential connections
+between central and surrounding elements were covered by dark gray
+color (see Figure~\ref{fig:InitialPicture}).
 %
@@
 %were in German (see (\ref{ex:as}) and (\ref{ex:es}) below) and 
-were presented auditorily, and participants were
-asked to listen to a given sentence and then uncover the potential
-links step by step until they felt able to give a truth value
-judgment. Three options were available for participants at each step:
-(i), demand more information, (ii), judge the sentence as true, and
-(iii), judge the sentence as false. Importantly, each of the three
-potentially available readings corresponded to a specific step in the
-uncovering process where the truth value of that reading (and only of
-that reading) could be assessed for the first time, which we will
-refer to as {\it critical position}. The location in the sequence and 
-the corresponding truth-value judgment differed between \as- and 
-\es-sentences, as described presently. (This is, again, because of the 
-logical dependencies between readings.)
-
-Consider the \as-sentence in (\ref{ex:as}).
+were presented auditorily, and participants were asked to listen to a
+given sentence and then uncover the potential links step by step until
+they felt able to give a truth value judgment. Three options were
+available for participants at each step: (i) demand more information,
+(ii) judge the sentence as true, and (iii) judge the sentence as
+false. Trials ended with a truth-value judgement, and a judgement was
+required to end the trial when all connections had been
+revealed. Importantly, each of the three potentially available
+readings corresponded to a specific step in the uncovering process
+where the truth value of that reading (and only of that reading) could
+be assessed for the first time. We refer to this step in the sequence
+as the {\it critical position} of a given reading. The critical
+position and the corresponding truth-value judgment differed between
+\as- and \es-sentences, as described presently. (This is, partly,
+because of the logical dependencies between readings, and, partly,
+also to rule out positional biases.)
+
+Consider the German \as-sentence in (\ref{ex:as}), included in our study.
 \begin{exe}
@@
 bells is already linked to all of its semicircles. The literal reading
-can be evaluated in Figure~\ref{fig:subfig2}, where it would trigger a
-\emph{false} response, as there are two bells that are connected to at
-least some of their surrounding elements. Finally, confirming
-\ref{fig:subfig1} by a \emph{true} response corresponds to the local
-reading, as one of the bells is linked to some but not all of its
-semicircles, while all of the other bells are linked to all of
-them. Note that again, global and literal readings differ from local
-readings with respect to their truth values. Mappings between
-responses and readings are summarized in Table \ref{tab:mappingES}.
+can be evaluated at the critical position shown in
+Figure~\ref{fig:subfig2}, where it would trigger a \emph{false}
+response, as there are two bells that are connected to at least some
+of their surrounding elements. Finally, confirming \ref{fig:subfig1}
+by a \emph{true} response corresponds to the local reading, as one of
+the bells is linked to some but not all of its semicircles, while all
+of the other bells are linked to all of them. Note that again, global
+and literal readings differ from local readings with respect to their
+truth values. Mappings between responses and readings are summarized
+in Table \ref{tab:mappingES}.
 
@@
 included a set of control conditions. These also controlled for
-response biases that are independent of the sentence meaning, but only
-depend on the experimental procedure or on the picture materials. For
-each of the three readings in the \as- and \es-conditions, we
-constructed an unambiguous control sentence as in
+response biases. For each of the three readings in the \as- and
+\es-conditions, we constructed an unambiguous control sentence as in
 (\ref{bsp:controls-as}) and (\ref{bsp:controls-es}), requiring the
@@
 
-\paragraph{Preference-related controls.} In order to control for
-artificial effects of presentation order on the availability of
-readings, we included a second type of control conditions. In
-particular, we tested (i), whether the order of given readings affects
-preferences for ambiguous sentences and (ii), whether prosodic
+\paragraph{Preference-related controls.} In order to test whether the
+order of critical positions for different readings within a sequence
+had an influence on responses, we included a second type of control
+conditions. These conditions also controlled whether prosodic
 information can, in principle, shift reading preferences in the
@@
 it would be unclear if these decisions have been affected by a general
-inavailability of local readings or by the fact that one of the
+unavailability of local readings or by the fact that one of the
 earlier presented readings is the preferred one. By including globally
@@
 we thus intended to test whether participants in our task occasionally
-choose dispreferred readings, even if they were available only at a critical
-position following the preferred readings.
+choose dispreferred readings, even if they were available only at a
+critical position following the preferred readings.
 
@@
 In late-closure sentences, a modifier such as a relative clause or a
-prepositional phrase can be attached to one of two
-preceding hosts. For instance, in (\ref{bsp:target-related}), the
-prepositional phrase \emph{with suns} can be attached to the preceding
-noun \emph{squares}, resulting in the so-called \emph{late-closure} or
-\emph{low-attachment} reading ((\ref{bsp:target-related-LC}). Alternatively, 
-the \acro{pp} can be attached to the whole conjoined \acro{np}
-\emph{circles and squares}, corresponding to the \emph{early-closure}
-or \emph{high-attachment} reading (\ref{bsp:target-related-EC}).
-Late-closure readings have been observed to be preferred over the early 
-closure reading for sentences comparable to those in (\ref{bsp:target-related})
+prepositional phrase can be attached to one of two preceding
+hosts. For instance, in (\ref{bsp:target-related}), the prepositional
+phrase \emph{with suns} can be attached to the preceding noun
+\emph{squares}, resulting in the so-called \emph{late-closure} or
+\emph{low-attachment} reading
+((\ref{bsp:target-related-LC}). Alternatively, the \acro{pp} can be
+attached to the whole conjoined \acro{np} \emph{circles and squares},
+corresponding to the \emph{early-closure} or \emph{high-attachment}
+reading (\ref{bsp:target-related-EC}).  Late-closure readings have
+been observed to be preferred over the early-closure reading for
+sentences comparable to those in (\ref{bsp:target-related})
 \citep[e.g.][]{Frazier87,Frazier82}.
@@
 the circles connected to the letter contain any suns. Under the
-late-closure reading in (\ref{bsp:target-related-EC}), in contrast, a
+late-closure reading in (\ref{bsp:target-related-LC}), in contrast, a
 \emph{true}-response would be expected no sooner than in the step
@@
 
-\begin{enumerate}[1:]
-\item a higher higher f0 maximum or a higher pitch range (difference 
-between minimal and maximal f0 values), and
+\begin{enumerate}[(i)]
+\item a higher F0 maximum or a higher pitch range (difference 
+between minimal and maximal F0 values), and
 \item a longer duration of the accented element as opposed to its 
-non-accented counterpart
+non-accented counterpart.
 \end{enumerate}
 
-We therefore recorded sentences by a trained speaker familiar with the 
-concept of contrastive focus and instructed her to produce contrast as 
-described in 1 and 2. Both \as-sentences and \es-sentences
-were recorded in two versions each. In the accented version, a pitch 
-accent was placed on {\it einige}. The second version had neutral prosody. 
-If accentuation is the driving force for local readings, we would expect 
-a higher proportion of local readings in the former than in the latter 
-version of the sentences.
-
-Preference-related controls also differed prosodically. Modifier attachment 
-ambiguities comparable to the examples in (\ref{bsp:target-related}) and 
-(\ref{bsp:target-related2}) have been shown to be sensitive to differences 
-in prosodic phrasing. Though there has been discussion as to whether 
-speakers reliably \textit{produce} disambiguating cues in such constructions 
-\citep[e.g.][]{Allbritton96,Kraljik05, Snedeker03, Schafer00}, overt prosodic 
-boundaries are generally acknowledged to guide interpretive processes of Late 
-Closure sentences in \textit{comprehension} \citep[e.g.][]{Steinhauer99, Augurzky06}. 
-Specifically, it has been shown that prosodically separating a modifier from 
-the directly preceding material supports an early closure reading, whereas 
-separating the two potential attachment sites is supportive of a late closure 
-reading. Thus, a phrase boundary between {\it squares} and {\it with} in
-(\ref{bsp:target-related}) corresponds to a high-attachment reading, whereas
-a prosodic phrase boundary following {\it circles} corresponds to a low-attachment
-reading.
-
-To test whether prosodic information is taken into account in the \acro{itv} task, we
-presented sentences in both of these prosodic variants. In addition, in order to test 
-prosody-independent preferences, we also included a neutral version without any 
-pronounced boundary. Further, we also presented 
-unambiguous sentences corresponding to the early-closure reading. As in the case 
-of the \as- and \es-sentences, the unambiguous counterparts served as a baseline to
-control for response biases that are independent of sentence meaning.
+\noindent We therefore recorded sentences by a trained speaker
+familiar with the concept of contrastive focus and instructed her to
+produce contrast as described in 1 and 2. Both \as-sentences and
+\es-sentences were recorded in two versions each. In the accented
+version, a pitch accent was placed on {\it einige}. The second version
+had neutral prosody.  If accentuation is the driving force for local
+readings, we would expect a higher proportion of local readings in the
+former than in the latter version of the sentences.
+
+Preference-related controls also differed prosodically. Modifier
+attachment ambiguities comparable to the examples in
+(\ref{bsp:target-related}) and (\ref{bsp:target-related2}) have been
+shown to be sensitive to differences in prosodic phrasing. Though
+there has been discussion as to whether speakers reliably
+\textit{produce} disambiguating cues in such constructions
+\citep[e.g.][]{Allbritton96,Kraljik05, Snedeker03, Schafer00}, overt
+prosodic boundaries are generally acknowledged to guide interpretive
+processes of late-closure sentences in \textit{comprehension}
+\citep[e.g.][]{Steinhauer99, Augurzky06}.  Specifically, it has been
+shown that prosodically separating a modifier from the directly
+preceding material supports an early-closure reading, whereas
+separating the two potential attachment sites is supportive of a late
+closure reading. Thus, a phrase boundary between {\it squares} and
+{\it with} in (\ref{bsp:target-related}) corresponds to a
+high-attachment reading, whereas a prosodic phrase boundary following
+{\it circles} corresponds to a low-attachment reading.
+
+To test whether prosodic information is taken into account in our
+task, we presented sentences in both of these prosodic variants. In
+addition, in order to test prosody-independent preferences, we also
+included a neutral version without any pronounced boundary. Further,
+we also presented unambiguous sentences corresponding to the
+early-closure reading. As in the case of the \as- and \es-sentences,
+the unambiguous counterparts served as a baseline to control for
+response biases that are independent of sentence meaning.
 
@@
 
-We constructed a set of 15 items for \as- and \es-sentences,
+We constructed a set of 15 items for German \as- and \es-sentences,
 respectively, analogous to the examples in \ref{ex:as} and
@@
 produced with a contrastive pitch accent as well as with a neutral
-accent. Contrastive accents in German are realized by an increase in f0 (range)
-as well as by a longer duration (see {sec:design} above). A set of 15 
+accent. Contrastive accents in German are realized by an increase in F0 (range)
+as well as by a longer duration (see Section~\ref{sec:design} above). A set of 15 
 experimental items was recorded for each condition (\as vs.~\es, \emph{accented} 
@@
 
-Note that differences between Regions 1, 2, 4 and 7 can be expected
+\noindent Note that differences between Regions 1, 2, 4 and 7 can be expected
 due to lexical differences between the \as and \es-conditions. As
@@
 conditions. Durational values included the respective word plus any
-following silent interval. Note that we did not include the
+following silent interval. We did not include the
 disambiguated fillers in these analyses as they involved very
@@
 For the durational analyses, constituents were automatically labeled
-by the \emph{Aligner} tool \citet{Rapp98},and the
+by the \emph{Aligner} tool \citep{Rapp98}, and the
 obtained values were manually corrected afterwards. For the targets,
-two-factorial \acros{anova} with the factors \acro{Quantifier} (all
-vs. exactly one) and \acro{Prosody} (accented vs.~unaccented) were
+two-factorial \acros{anova} with the factors \acro{Quantifier} (\emph{all}
+vs.~\emph{exactly one}) and \acro{Prosody} (accented vs.~unaccented) were
 carried out. For the preference-related fillers, we carried out
@@
 The details of these analyses are found in
-Appendix~\ref{sec:audit-sent-mater}.
-\dn{Petras Kommentar: Vielleicht sollten wir hier jeweils 1 Figure für akzentuiert vs.
-nicht und boundary vs.
-nicht reinbringen.
-Fabian meint zurecht, dass man nicht einfach die Ergebnisse nur in den Appendix packen kann.
-Es wären dann halt 4 Figures, da wir ja f0 und duration ansehen, und wir würden nur die experimentell interessanten veranschaulichen und die Statistik dann im Appendix lassen - was meint Ihr?}
+Appendix~\ref{sec:audit-sent-mater}. \dn{Petras Kommentar: Vielleicht
+  sollten wir hier jeweils 1 Figure für akzentuiert vs. nicht und
+  boundary vs. nicht reinbringen. Fabian meint zurecht, dass man nicht
+  einfach die Ergebnisse nur in den Appendix packen kann. Es wären
+  dann halt 4 Figures, da wir ja F0 und duration ansehen, und wir
+  würden nur die experimentell interessanten veranschaulichen und die
+  Statistik dann im Appendix lassen - was meint Ihr? --- Micha sagt ``Ja!''}
 
@@
 duration and F0 range, prosodic boundaries for our preference-related
-fillers were realized by pre-final lengthening (i.e. an increase in F0
+fillers were realized by pre-final lengthening (i.e., an increase in F0
 and duration at the position preceding the boundary).
@@
 sequences. First, a sequence in which the crirical position for the
-(preferred) Late Closure reading was presented preceding the critical
-position for the Early Closure reading ({\it LC sequence}), and
+(preferred) late-closure reading was presented preceding the critical
+position for the early-closure reading ({\it LC sequence}), and
 second, a sequence in which the readings were presented in reversed
@@
 
-In the following, we will report the results for targets and positional
-controls separately. After providing the descriptive results, we present
-statistical analyses, which were carried out in the following manner.
-We computed log-liner models (see Scheepers 2003) in two variants (by 
-item and by participant). In the first, the factor {\it Item} was 
-included, and in the second analysis, the factor {\it Participants} 
-was included. Inclusion of these two factors allowed us to test whether 
-the distribution of participants' choices was identical accros items and 
-participants. We report log-likelihood ratio Chi-squares ($LRCS_1$ 
-and $LRCS_2$), degrees of freedom ($df_1$, $df_2$) and significance 
-levels ($p_1$ and $p_2$). The relevant experimental
-factors are provided in the specific subsections below.
+In the following, we will report the results for targets and
+preference-related controls separately. After providing the
+descriptive results, we present statistical analyses, which were
+carried out in the following manner.  We computed log-linear models
+(see SCHEEPERS 2003 ????) in two variants (by item and by participant). In
+the first, the factor {\it Item} was included, and in the second
+analysis, the factor {\it Participants} was included. Inclusion of
+these two factors allowed us to test whether the distribution of
+participants' choices was identical accros items and participants. We
+report log-likelihood ratio Chi-squares ($LRCS_1$ and $LRCS_2$),
+degrees of freedom ($df_1$, $df_2$) and significance levels ($p_1$ and
+$p_2$). The relevant experimental factors are provided in the specific
+subsections below.
 
 \paragraph{Target conditions and positional controls}
-Performance on positional controls was high (92\% correct
-responses on average), indicating that subjects understood the task,
-giving truth-value judgements at the ``right'' moment in a sequence
-without being influenced in general by inessential features of the
-picture material or showing general response biases.
+Performance on positional controls was high (92\% correct responses on
+average), indicating that subjects understood the task, giving
+truth-value judgements at the right moment in a sequence without being
+influenced in general by inessential features of the picture material
+or showing general response biases.
 
@@
                   legend style={at={(0.5,-0.15)}, anchor=north, legend columns=-1},
-        ylabel={\% of answers}, symbolic x
+        ylabel={\% of answers (rounded)}, symbolic x
         coords={neutral,accented}, xtick=data, nodes
@@
 that this finding cannot be explained by some kind of general response
-bias on the last position since local readings required a yes-judgment
-in the \es-conditions but a no-judgment in the \as-conditions.
-
-In order to test whether accentuation or the quantifier has an
-influence on the distribution of readings, log-liner models 
+bias on the last position since local readings required a \emph{yes} judgment
+in the \es-conditions but a \emph{no} judgment in the \as-conditions.
+
+In order to test whether accentuation or the quantifier had an
+influence on the distribution of readings, log-linear models 
 including the factors {\it Reading}, {\it Accentuation} and 
@@
   Construction} and {\it Reading} ($LRCS_1, = 143.92, df_1 = 117,
-p_1<.05$) which could stem from to the fact that some participants
-were more prone than others to make errors in the \es-conditions.
+p_1<.05$) which could stem from the fact that some participants were
+more prone than others to make errors in the \es-conditions.
 
@@
 Further examination of the distribution of local readings revealed a
-clear pattern (see Figure \ref{fig:HistogramLocalReadingsK2}). In all
-four conditions, about seven out of the 40 participants ($16\%$) were
-consistently giving judgments that indicate local readings.\dn{please
-  check numbers; this cannot be true!? not accross all four
-  conditions} Further, the relative frequency of local judgments per
-participant strongly correlated between all four conditions (all
-$r>.6, p<.001$). Appart from the localists about half of the
-participants (and 41.5\% of all participants) were consistently giving
-judgments that indicate literal readings. Only a minority of
-participants exhibited inconsistency. Reading preferences were more
-clear-cut in the \as-conditions than in the \es-conditions. The number
-of consistent literalists was lower in the \es-conditions (25.6\%) as
-compared to the \as-conditions (57.3\%). Also, the number of
-participants that showed inconsistency was higher in these
-conditions. However, the number of consistent localists did hardly
-differ between constructions.
+clear pattern (see Figure \ref{fig:HistogramLocalReadingsK2}). The
+relative frequency of local judgments per participant strongly
+correlated between all four conditions (all $r>.6, p<.001$). Appart
+from the localists about half of the participants (and 41.5\% of all
+participants) were consistently giving judgments that indicate literal
+readings. Only a minority of participants exhibited
+inconsistency. Reading preferences were more clear-cut in the
+\as-conditions than in the \es-conditions. The number of consistent
+literalists was lower in the \es-conditions (25.6\%) as compared to
+the \as-conditions (57.3\%). Also, the number of participants that
+showed inconsistency was higher in these conditions. However, the
+number of consistent localists did hardly differ between
+constructions.
 
@@
   Participant} indicates that the type of construction does not affect
-the amount of local readings. We assumed based on the observed
-distribution of judgments that the type of contsruction affected the
+the amount of local readings. We assumed, based on the observed
+distribution of judgments, that the type of contsruction affected the
 amount of literal but not local and global readings. To further test
 this assumption, we also considered literal and global readings versus
-other judgments in separate analyses. Comparing global readings versus
+other judgments in separate analyses. Comparing global\dn{do you mean LITERAL?} readings versus
 other judgments {\it Construction} and {\it Reading} were found to
@@
 
-Participants' judgments are depicted in Figures \ref{Fig:EC_judgments} and 
-\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they were as expected
-under one of these readings, and as "other" if they were not. The distributions 
-of readings thus coded is illustrated in Figure \ref{fig:response-type-freque-TRF}. 
-Overall, participants mainly gave answers corresponding to the \lc-reading (65\%). 
+Participants' judgments are depicted in Figures \ref{Fig:EC_judgments}
+and \ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if
+they were as expected under one of these readings, and as "other" if
+they were not. The distributions of readings thus coded is illustrated
+in Figure \ref{fig:response-type-freque-TRF}.  Overall, participants
+mainly gave answers corresponding to the \lc-reading (65\%).
 Moreover, this pattern was constrained by prosody. When prosody
-supported a dispreferred \ec-reading, the number of \ec-decisions were increased.
-
-In both \lc- and \ec-sequences, the number of \ec-answers was highest when this reading
-was supported by prosodic phrasing (i.e. 30\%  and 32\%, respectively), and a bit lower
-with neutral prosody (24\%  and 25\%). When prosodic phrasing supported the \lc-reading,
-the number of \ec choices was lowest (12\% in both sequences). The number 
-of erroneous answers did not differ between the single conditions. Finally, the
-availability of readings within a sequence did not yield any significant effects.
-
-In order to test statistically whether prosodic phrasing and sequential ordering 
-had an effect on the number of \ec-choices, we contrasted the number of \ec-choices
-with non-\ec -choices (i.e. \lc-answers and erroneous responses together), calculating
-log-linear model analyses with the factors {\it Reading}, {\it Prosody}, and 
-{\it Sequence}.
+supported a dispreferred \ec-reading, the number of \ec-decisions were
+increased and vice versa.
+
+In both \lc- and \ec-sequences, the number of \ec-answers was highest
+when this reading was supported by prosodic phrasing (30\% and
+32\%, respectively), and a bit lower with neutral prosody (24\% and
+25\%). When prosodic phrasing supported the \lc-reading, the number of
+\ec choices was lowest (12\% in both sequences). The number of
+erroneous answers did not differ between the single
+conditions. Finally, the availability of readings within a sequence
+did not yield any significant effects.
+
+In order to test statistically whether prosodic phrasing and
+sequential ordering had an effect on the number of \ec-choices, we
+contrasted the number of \ec-choices with non-\ec -choices (i.e.,
+\lc-answers and erroneous responses together), calculating log-linear
+model analyses with the factors {\it Reading}, {\it Prosody}, and {\it
+  Sequence}.
 
@@
                  legend columns=-1}, 
-               ylabel={\% of answers}, 
+               ylabel={\% of answers (rounded)}, 
                symbolic x coords={neutral,LC-pref,EC-pref}, 
@@
 
-\subsection{Discussion}
+\subsection{Summary \& Interpretation}
 \label{sec:interpretation}
@@
 
-where it is unclear whether the global readings are entirely
+\noindent where it is unclear whether the global readings are entirely
 unavailable or simply severely dispreferred. Crucially, our data
@@
 
-For traditionalism, the absence of global readings \textit{per se} can be
-explained in a straightforward manner, for instance, by proposing
-that the extra assumptions needed to derive global readings are not 
-standardly available (as in the weak variety of traditionalism).
-Alternatively, traditionalists could argue that the task's rather high 
-processing demands lead to a suppression of global readings, in line with the
-findings of \citet{NeysDe-NeysSchaeken2007:When-People-Are} that
-working memory load negatively affects the number of scalar
-implicature responses in sentence verification tasks. However, it then remains 
-unclear why memory effects should be restricted to global readings.
-As a result, approaches like the unrestricted variety of traditionalism thereby 
-loose the possibility of accounting for local readings of \as-sentences.
-\fn{Remember that what we called unrestricted traditionalism
-  can account for local readings of \as-sentences by assuming that a
-  sentence of the form \emph{Some of the $X$ are related to some of
-    the $Y$} is a feasible alternative.} This is because unrestricted
-traditionalism explains local and global readings of \as-sentences in
-essentially the same manner. On top of that, traditionalism cannot
-explain local readings for \es-sentences. Finally, since our materials were 
-presented auditorily, we controlled for potential effects of silent
-prosody. Importantly, local readings were observed in the accented as well
-as in the unaccented condition, thus countering previous traditionalist
-suggestions that local readings are to be attributed to specific pragmatic 
-mechanisms.\dn{Petra: das habe ich hier so von der Intro übernommen. Sowohl
-dort als auch hier fände ich es interessant, kurz zu sehen, was für alternative
-pragmatische Mechanismen das sind - geht das in Kürze? Den nächsten Satz habe ich
-in Bezug zum vorhergehenden Absatz nicht verstanden}
-
-%showed on the neutral accentuation case as
-%well. 
-Notice that it is not a problem for this argument that the local
-responses were not emphasized with a contrastive stress on the
-embedded scalar. In sum, traditionalism alone cannot explain
-(\ref{bsp:observed-preferences}), but needs an additional explanation
-of local readings for \emph{both} \as- \emph{and} \es-sentences.
+For traditionalism, the absence of global readings \textit{per se} can
+be explained, for instance, by proposing that the extra assumptions
+needed to derive global readings are not standardly available (as in
+the weak variety of traditionalism).  Alternatively, traditionalists
+could argue that the task's rather high processing demands lead to a
+suppression of global readings, in line with the findings of
+\citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
+load negatively affects the number of scalar implicature responses in
+sentence verification tasks. However, it then remains unclear why
+memory effects should be restricted to global readings.  As a result,
+approaches like the unrestricted variety of traditionalism thereby
+loose the possibility of accounting for local readings of
+\as-sentences.\fn{Remember that unrestricted traditionalism, as we
+  called it, can account for local readings of \as-sentences by
+  assuming that a sentence of the form \emph{Some of the $X$ are
+    related to some of the $Y$} is a feasible alternative.} This is
+because unrestricted traditionalism explains local and global readings
+of \as-sentences in essentially the same manner. On top of that,
+traditionalism cannot explain local readings for
+\es-sentences. Resorting to the intonational markedness hypothesis
+does not help improve predictions of traditionalism. The latter would
+predict an increase in local readings in the accented conditions, and
+maybe even an absence of local readings in the unaccented
+conditions. Neither was observed. Local readings were observed in the
+accented as well as in the unaccented condition, thus countering
+previous traditionalist suggestions that local readings are to be
+attributed to specific pragmatic mechanisms. In sum, traditionalism
+alone cannot explain (\ref{bsp:observed-preferences}), but needs an
+additional explanation of local readings for \emph{both} \as-
+\emph{and} \es-sentences.
 
@@
 
-Summing up so far, the existing versions of traditionalism and grammaticalism
-cannot explain the present results. Of the two approaches, grammaticalism 
-seems better suited to account for the observed effects. Whereas 
-traditionalism cannot cope with local readings for principled reasons, 
-the only thing that grammaticalism would have to change is the 
-selection criterion over preferred readings, i.e. to reconsider the strongest
-meaning hypothesis. Turning away from comparisons of logical strength,
-a \emph{prima facie} plausible selection criterion that produces
+Summing up so far, the existing versions of traditionalism and
+grammaticalism cannot explain the present results. Of the two
+approaches, grammaticalism seems better suited to account for the
+observed effects. Whereas traditionalism cannot cope with local
+readings (of unaccented sentences), the only thing that grammaticalism
+would have to change is the selection criterion over preferred
+readings, i.e., to reconsider the strongest meaning
+hypothesis. Turning away from comparisons of logical strength, a
+\emph{prima facie} plausible selection criterion that produces
 (\ref{bsp:observed-preferences}) is ready at hand: if we assume that
-each insertion of $\exh(\cdot)$ operator is \emph{costly}
+each insertion of the $\exh(\cdot)$ operator is \emph{costly}
 anti-proportional to the depth of its embedding under other logical
@@
 interesting matter of further investigation.
-%On the entirely
-%speculative supposition that it did turn out to be a good predictor,
-%grammaticalism would be saved in a straightforward way. 
-%But is this an argument for grammaticalism contra traditionalism? No 
-%it clearly is not.
-
-%In order to be a predictive theory, grammaticalism thus needs a selection
-%criterion, for without one it is not a predictive theory at all, and
-%that the only one that has been seriously proposed fails to predict
-%the observed data. That grammaticalism can do with many such selection
-%criteria is not, as such, an argument in its favor over
-%traditionalism. The case remains that both theories fail on the
-%observed data.
-
-Interestingly, an alternative theory of scalar implicature explains the 
-observed preference ordering (\ref{bsp:observed-preferences})
-in a completely straightforward manner. 
-\emph{Conventionalism} (also sometimes called \emph{lexicalism})
-\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}.
-proposes that if the upper-bounding inference from
-\emph{some} to \emph{some but not all} occurs frequently, it
-would be inefficient to execute over and over again the Gricean
-reasoning that traditionalists propose. Conventionalism therefore
-assumes that scalar inferences have become routinized, hard-wired, so
-much so that there are two lexical entries for a scalar item like
-\emph{some}, one with logical meaning \emph{some and maybe all} and
-one with the upper-bounded meaning \emph{some but not
+
+Interestingly, an alternative theory of scalar implicature explains
+the observed preference ordering (\ref{bsp:observed-preferences}) in a
+completely straightforward manner.  \emph{Conventionalism} (also
+sometimes called \emph{lexicalism}) proposes that if the
+upper-bounding inference from \emph{some} to \emph{some but not all}
+occurs frequently, it would be inefficient to execute over and over
+again the Gricean reasoning that traditionalists propose
+\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}. Conventionalism
+therefore assumes that scalar inferences have become routinized,
+hard-wired, so much so that there are two lexical entries for a scalar
+item like \emph{some}, one with logical meaning \emph{some and maybe
+  all} and one with the upper-bounded meaning \emph{some but not
   all}. \citet{LevinsonPresumptiveMeanings2000} proposed that the
@@
 processing studies show that the computation of scalar inferences
-appears to be time- and effort-consuming, when they \emph{do} arise,
-not when they \emph{don't}, as defaultism would have it
+appears to be time- and effort-consuming, when they do arise,
+not when they do not
 \citep[c.f.][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
@@
   discussion of \emph{Hurford's constraint}
-  \citep[c.f.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2009:Hurfords-Constr,ChierchiaFox2008:The-Grammatical}.}
+  \citep[c.f.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2009:Hurfords-Constr,ChierchiaFox2008:The-Grammatical},
+so we skip this here.}
 For instance, conventionalism cannot account for \emph{indirect
@@
 because the point remains that traditionalism as such fails to predict
-the observed data.\dn{Petra: dieser Absatz scheint mir sehr wichtig und gut - 
-wäre es möglich, hier noch etwas ausführlicher drüber zu schreiben?}
+the observed data.
 

### 2013-01-21 text/paper/paper3.tex
paper3 - general discussion fixed

@@
 
-%Several worries and objections are conceivable that might cast doubt
-%on the previous interpretation of our experimental data.
-
-In the following, we would like to address potential alternative
-explanations for the present results. We will argue that besides
-these interpretation variants, the main point raised
-above remains valid: neither traditionalism, nor grammaticalism
-is able to account for the present pattern of results.
-
-%some of these that we consider most
-%pressing. Eventually, however, we conclude that the main point raised
-%above remains valid: neither traditionalism, nor grammaticalism
-%explains the observations even under alternative interpretations of the
-%data.
-
-First, it could be questioned whether our design reliably 
+There are a number of conceivable objections to our interpretation of
+the presented results. We will consider the most pressing ones in the
+following and conclude that the main point raised above remains valid:
+neither traditionalism, nor grammaticalism is able to account for the
+present pattern of results.
+
+To begin with, it could be questioned whether our design reliably
 indicates the preference relation in (\ref{bsp:observed-preferences})
-among readings of our target sentences. Thus, the incremental verification task
-(\ivt) might simply select for the weakest possible reading. This idea
-can be grounded in the observation that the preferred \lc-readings
-of our target-related controls entail the dispreferred
-\ec-readings. It could thus be argued that the difference in responses
-for preference-related controls are due to the entailment properties,
-not the known preference relation over \lc- and \ec-readings. However, this
-does not explain why the distribution of responses in the target
-conditions are obviously not governed by logical strength. In fact, it
-is a very noteworthy point that although entailment relations among
-readings differ between \as- and \es-sentences, the observed response
-pattern does not. (This is what is at the heart of the problem for a
-grammaticalism that relies on the strongest meaning hypothesis.)
-\dn{Petra: ich glaub, den Punkt verstehe ich nicht ganz - sollte man hier
-auch die Prosodie erwähnen? Phrasierung wirkt sich ja nicht auf entailment
-relations aus, sondern wird normalerweise dem Syntax-Prosodie-Interface
-zugeschrieben}
-
-But maybe, a similar kind of objection goes, it is not feasible to
-actually compare results from the preference-related controls to
-results from our target conditions, because the kind of ``ambiguity''
-is of a different kind. In the former we have a syntactic
-ambiguity, in the latter a small number of competing pragmatic
+among readings of our target sentences. After all, our incremental
+verification task might simply select for the weakest possible
+reading. This idea can be grounded in the observation that the
+preferred \lc-readings of our target-related controls entail the
+dispreferred \ec-readings. It could thus be argued that the difference
+in responses for preference-related controls are due to the entailment
+properties, not the known preference relation over \lc- and
+\ec-readings. However, this does not explain why the distribution of
+responses in the target conditions are obviously not governed by
+logical strength. In fact, it is a very noteworthy point that although
+entailment relations among readings differ between \as- and
+\es-sentences, the observed response pattern does not. (This is what
+is at the heart of the problem for a grammaticalism that relies on the
+strongest meaning hypothesis.)
+
+A related objection would be that maybe it is not feasible to actually
+compare results from the preference-related controls to results from
+our target conditions, because the source of different readings is
+fundamentally different. In the former we have a syntactic ambiguity,
+in the latter a small number of competing putative pragmatic
 enrichments. The former is a case of perceived ambiguity (some of our
-subjects reported this in a \emph{Nachbefragungsbogen}\dn{English?}), 
-the latter arguably is
-not \citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps
-even if the distribution of responses is indicative of the known
-preference patterns in preference-related controls, this would not
-necessarily mean that the distribution of responses in target
-conditions is indicative of preference relations.
+subjects reported this), the latter arguably is not
+\citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
+if the distribution of responses is indicative of the known preference
+patterns in preference-related controls, this would not necessarily
+mean that the distribution of responses in target conditions is
+indicative of preference relations.
 
 There are two kinds of reply to this objection (and others like
-it). The first kind of reply starts with a concession. It is true that
-we cannot conclude with certainty that our data implies that
-(\ref{bsp:observed-preferences}) is the actual preference relation
-among candidate readings of our target sentences. But we do not have
-to either. Maybe in fact, the observed distribution has nothing to do
-with preferences over readings. It does not matter. The main point is
-that neither traditionalism nor grammaticalism predicts the observed
-distribution of responses. The second kind of reply is fatalistic but
-stubborn. If we assume that the \ivt is incapable of indicating
-preferences among readings for pragmatically unspecified, then it
-should at least be able to indicate availability of readings, should
-it not? And if we deny the observed response patterns the power to
-indicate preference, what should the information about availability of
-readings be that we may safely infer from it? It should be that local
-readings are available and that global readings are not. But that is
-again bad news for both traditionalism and grammaticalism. The former
-cannot explain the substantial number of local responses, the latter
-doesn't explain the absence of global responses.
-
-\begin{itemize}
-\item pictures overemphasize contrast some/all
-\item subjects tricked into local responses because they are at the end
-  \begin{itemize}
-  \item would only show availability after all
-  \end{itemize}
-\item typicality after all
-\end{itemize}
-
-\subsubsection{Bits and Pieces}
-\label{sec:bits-pieces}
-
-\begin{itemize}
-\item The distribution of
-responses found in previous studies could in part be explained by
-differences in typicality of the pictures with respect to the possible
-readings (see van Tiel). In the present case this kind of reasoning
-would have to be extended to the typicalilty of parts of pictures. On
-intuitive grounds, we take this kind of reasoning to be
-implausible. We will now shortly discuss how graphical properties
-might still affect judgments in the worst case. In the first step of
-the \as-condition local and global readings cannot be judged,
-yet. Therefore, graphical properties should not affect judgments if
-participants have one of these readings in mind. If participants have
-a literal reading in mind, the worst case scenario is that they
-refrain from judging the sentence as true at this point due to some,
-eg. atypical, graphical property of the picture. The situation is
-similar at the second step. The local reading is still not
-decidable. Therefore, graphical properties should not play a role if
-participants have a local reading in mind. A positive judgment might,
-however, be a delayed judgment of a literal reading. Again, the worst
-case scenario for our purpose is that participants refrain from
-answering because of graphical properties. At the last step the local
-reading requires a negative judgment. Now, we could obtain delayed
-negative responses from literal or global readings because the graph
-as a whole is, e.g., logically true but atypical with respect to these
-readings. These kinds of judgments would be indistinguishable from
-local responses. Note, however, that we have no reason to believe that
-typicality has large effects, because, given the results from van
-Tiel, the picture as a whole is expected to be one of the more typical
-situations for \as-sentences. Still, we cannot exclude the possibility
-that graphical properties of the pictures might have the described
-effect. In the \es-conditions this type of effect is, however,
-entirely impossible since the literal and global reading is plainly
-false given the initial parts as well as the whole graph. Summing up,
-in the worst case, which we consider implausible, graphical effects
-might lead to an enhanced number of local responses in the \as- as
-compared to the \es-condition. We have to keep this possibility in
-mind. We want to stress, however, that the design presented here
-improves on previous studies with respect to possible graphical
-effects.
-\end{itemize}
+it). Firstly, it is true that we cannot conclude with certainty that
+our data implies that (\ref{bsp:observed-preferences}) is the actual
+preference relation among candidate readings of our target
+sentences. But that does not matter. Even if the observed distribution
+has nothing to do with preferences over readings, the main point
+remains that neither traditionalism nor grammaticalism predicts the
+observed distribution of responses. Secondly, even if we assume that
+the incremental verification task is incapable of indicating
+preferences among pragmatic readings of the relevant kind, then it
+should at least be able to indicate availability of readings. So if
+we deny the observed response patterns the power to indicate
+preference, what should the information about availability of readings
+be that we may safely infer from it? It should be that local readings
+are available and that global readings are not. But that is again not
+predicted by either traditionalism or grammaticalism. The former cannot
+explain the substantial number of local responses, the latter doesn't
+explain the absence of global responses.
+
+A third objection could be that pictures in our tasks may unduly
+overemphasize the contrast between cases where items are connected
+with all or merely some but not all of their surrounding shapes. This
+is essentially the line of argument pursued by
+\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} against the data
+reported by \citet{ChemlaSpector2010:Experimental-Ev} in support of
+local readings of
+\es-sentences. \citeauthor{GeurtsTielvan-Tiel2013:Scalar-expressi}
+show that the strength of agreement to an \es-sentence on a 7-point
+Likert-scale depends on a visual contrast between, on the one hand,
+one element connected to some but not all of its surrounding shapes,
+and, on the other hand, a variable number of elements connected to all
+of their surrounding shapes. When two universally connected elements
+are present, the mean rate of agreement is higher than when only one
+is present. So, maybe our displays similarly provoked local readings
+because of an overemphasized visual contrast.
+
+This cannot be a plausible explanation for the number of local
+responses we found in our study. Although it is true that the critical
+position for judging the local reading is a picture with a high visual
+contrast in the above sense (see Figure~\ref{fig:exseqES}), a purely
+contrast-based explanation of the local responses in our data is not
+feasible for two reasons. The first is that visual contrast does not
+explain how subjects ever even got past the second critical position
+where the sentence can be judged false under its literal reading. At
+this position there is a visual contrast of the alleged kind but it is
+as small as possible. So something must have motivated subjects
+already at this position to continue unraveling, given that they were
+generally able of exiting at the earliest possible location. A second
+argument that casts doubt on a contrast-based explanation is that our
+study elicited categorical truth-value judgements. Unlike in
+\citeauthor{ChemlaSpector2010:Experimental-Ev}'s
+(\citeyear{ChemlaSpector2010:Experimental-Ev}) and
+\citeauthor{GeurtsTielvan-Tiel2013:Scalar-expressi}'s
+(\citeyear{GeurtsTielvan-Tiel2013:Scalar-expressi}) experiments, we
+did not record degrees of agreement with a statement. But it is hardly
+plausible that the visual contrast in a picture like in
+\ref{fig:subfig1} alone is enough to overrule a truth-value judgment
+so as to contradict the semantic meaning (even when there is no
+intonational markedness to support such a
+reinterpretation). Ultimately, however, even if the local answers in
+our study are contrast effects, the verdict remains that neither
+traditionalism can not account for that piece of the data unless aided
+by yet another auxiliary and grammaticalism cannot explain why it is
+relatively dispreferred.
+
+A fourth major conceivable objection maintains that we cannot rule out
+that the way we realized the intonational markedness in the accented
+conditions was not the right kind of intonational
+markedness. Therefore the intonational markedness hypothesis that
+links an increase in local readings to intonation might not be
+falsified by our results. Although true, this still does not help
+vindicate traditionalism, for even without marked intonation local
+readings were available.
+
+Finally, we should address the obvious worry that maybe our results
+could have been the product of typicality after all. Remember that
+\citet{Tielvan-Tiel2012:Embedded-Scalar} and
+\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue that the
+distribution of responses to \as-sentences found in previous studies
+could in part be explained by differences in typicality of the
+pictures with respect to the possible readings. In the present case
+this kind of reasoning would have to be extended to either cover the
+typicality of parts of pictures or to figure in subjects' expectations
+of pictorial typicality given their uncertainty. On intuitive grounds,
+we take either extension to be far-fetched and implausible. But even
+if this line of explanation can be plausibly extended to incrementally
+revealed picture verification, this does not as such save the day for
+traditionalism or grammaticalism, for the same reasons as given above.
+
+% Still, graphical properties might affect judgments in the worst
+% case. In the first step of the \as-condition local and global readings
+% cannot be judged, yet. Therefore, graphical properties should not
+% affect judgments if participants have one of these readings in
+% mind. If participants have a literal reading in mind, the worst case
+% scenario is that they refrain from judging the sentence as true at
+% this point due to some, say, atypical, graphical property of the
+% picture. The situation is similar at the second step. The local
+% reading is still not decidable. Therefore, graphical properties should
+% not play a role if participants have a local reading in mind. A
+% positive judgment might, however, be a delayed judgment of a literal
+% reading. Again, the worst case scenario for our purpose is that
+% participants refrain from answering because of graphical
+% properties. At the last step the local reading requires a negative
+% judgment. Now, we could obtain delayed negative responses from literal
+% or global readings because the graph as a whole is, e.g., logically
+% true but atypical with respect to these readings. These kinds of
+% judgments would be indistinguishable from local responses. Note,
+% however, that we have no reason to believe that typicality has large
+% effects, because, given the results from van Tiel, the picture as a
+% whole is expected to be one of the more typical situations for
+% \as-sentences. Still, we cannot exclude the possibility that graphical
+% properties of the pictures might have the described effect. In the
+% \es-conditions this type of effect is, however, entirely impossible
+% since the literal and global reading is plainly false given the
+% initial parts as well as the whole graph. Summing up, in the worst
+% case, which we consider implausible, graphical effects might lead to
+% an enhanced number of local responses in the \as- as compared to the
+% \es-condition. We have to keep this possibility in mind. We want to
+% stress, however, that the design presented here improves on previous
+% studies with respect to possible graphical effects.
 
@@
 \item future research: isolate consistent localists to probe into \emph{processing}
+\item production study
 \end{itemize}

### 2013-01-22 text/paper/paper3.tex
paper 3 - reworked up to discussion, conclusion missing

@@
 \begin{abstract}
-  \begin{itemize}
-  \item What is needed to complement the picture is data from a
-    verification experiment that is as independent as possible of
-    potentially conflating properties of the pictorial material and
-    that is nonetheless sensitive enough to detect local readings even
-    if they are dispreferred.
-  \end{itemize}
-
+  Scalar item \emph{some} is widely assumed to readily undergo a
+  pragmatic meaning enrichment to \emph{some but not all} if it occurs
+  in matrix position. The question under which circumstances this
+  meaning enrichment can take place in embedded position is an
+  important one to decide the delineation between semantics and
+  pragmatics, and therefore currently under renewed debate. % Some claim
+  % that it requires marked intonation for the relevant pragmatic
+  % enrichment to occur in embedded position; others allow for it more
+  % freely.
+  We present a novel experimental paradigm to test whether so-called
+  local readings are available with or without prosodic markedness. On
+  top of adding prosodic manipulation, our experimental design was
+  catered to a number of methodological difficulties that were
+  identified for previous studies, such as the possibility of
+  confounds of pictorial properties. The data obtained refutes both a
+  traditional Gricean view of scalar implicature calculation, as well
+  as the more recent grammatical approach.
 \end{abstract}
@@
 
+Although strictly speaking not a part of a Gricean theory of scalar
+implicature calculation, traditionalists frequently concede that local
+readings are in principle available, albeit not as a standard scalar
+implicature, but as a different pragmatic process triggered by
+prosodic markedness. We examine this \emph{intonational markedness
+  hypothesis} separately in Section~\ref{sec:inton-mark-hypoth},
+alongside a brief revision of the relevant experimental data.
+
 \subsection{Traditionalism}
@@
   as this is not crucially relevant for the issues we are interested
-  in here.}\textsuperscript{,}\dn{do we need to enlarge on epistemic
-  implicatures?}
+  in here.}
 
@@
 
-Taking stock, traditionalism, conventionalism and grammaticalism
-predict different patterns of availability and preference for \as- and
+Taking stock, traditionalism and grammaticalism predict different
+patterns of availability and preference for \as- and
 \es-sentences. Most notably, traditionalism does not predict local
-readings for \es-sentences to be available, while conventionalism does
-not predict any global readings to be available. Grammaticalism
-predicts that all readings are available, but, given the strongest
-meaning hypothesis, also comes with a clear indication of preference:
-literal meanings are dispreferred. All predictions are summarized in
+readings for \es-sentences to be available. Grammaticalism predicts
+that all readings are available, but, given the strongest meaning
+hypothesis, also comes with a clear indication of preference: literal
+meanings are dispreferred. All predictions are summarized in
 Table~\ref{tab:predictions}.
@@
 
-\section{The Intonational Markedness Hypothesis}
+\subsection{The Intonational Markedness Hypothesis}
 \label{sec:inton-mark-hypoth}
@@
 be available, many authors who adhere to a traditionalist position
-acknowledge that local readings are available if and only if the
+maintain that local readings are available if and only if the
 embedded scalar item is intonationally marked by contrastive stress
@@
 \begin{exe}
-\ex \label{bsp:Stress} This coffee is not \textsc{hot}, it's \textsc{HOT}.
+\ex \label{bsp:Stress} This chili is not \textsc{spicy}, it's \textsc{SPICY}.
 \end{exe}
 
-\noindent The
-intonational markedness hypothesis, as we will call it here, is then
-an addition to the traditionalist's explanation of scalar implicatures
-along the lines of the Gricean recipe. The crucial point is that under
-this extra assumption, local readings are a marked phenomenon. If
-supplemented with the intonational markedness hypothesis,
-traditionalists would therefore predict that local readings are
-available for \as- and \es-sentences, but only if intonationally
-marked by contrastive stress; since this reading is marked, presumably
-it would still be predicted to be dispreferred even if available.
+\noindent The \emph{intonational markedness hypothesis}, as we will
+call it here, is then an addition to the traditionalist's explanatory
+repertoire. The crucial point is that under this extra assumption,
+local readings are a marked phenomenon, and not the product of the
+same process as run-of-the-mill scalar implicatures associated with
+scalar items in matrix position. If supplemented with the intonational
+markedness hypothesis, traditionalists would therefore predict that
+local readings are available for \as- and \es-sentences, but only if
+intonationally marked by contrastive stress; since this reading is
+marked, presumably it would still be predicted to be dispreferred even
+if available.
 
@@
 obvious way. Moreover, typicality itself is not a satisfactory
-primitive in a putative explanation of the pragmatic use of
+primitive in a putative explanation of the use of
 quantifiers. Plausibly, the reason why quantifier \emph{some} is more
-typical for some set sizes than others is at least dependent on, if not
-entirely derived from, its contrast with other conceivable
+typical for some set sizes than others is at least dependent on, if
+not entirely derived from, its contrast with other conceivable
 alternatives, e.g., numerals within the subitizing range, as well as
@@
 had an influence on responses, we included a second type of control
-conditions. These conditions also controlled whether prosodic
-information can, in principle, shift reading preferences in the
-present task. Note that for our target sentences, the logical
-entailment relations between readings always require local readings to
-be evaluated at the end of a sequence. It could thus in principle be
-possible that no subject ever reaches this point, because they gave
-truth-value judgements earlier, thereby ending the trial. In that case
-it would be unclear if these decisions have been affected by a general
-unavailability of local readings or by the fact that one of the
-earlier presented readings is the preferred one. By including globally
-ambiguous structures with a known preference over available readings,
-we thus intended to test whether participants in our task occasionally
-choose dispreferred readings, even if they were available only at a
-critical position following the preferred readings.
+conditions. Secondly, these controls served as a test whether the
+incremental verification task could possibly detect at least ordinal
+preference relations among multiple candidate readings. Finally, these
+conditions also controlled whether prosodic information can, in
+principle, shift answer patterns in the present task. Note that for
+our target sentences, the logical entailment relations between
+readings always require local readings to be evaluated at the end of a
+sequence. It could thus in principle be possible that no subject ever
+reaches this point, because they gave truth-value judgements earlier,
+thereby ending the trial. In that case it would be unclear if these
+decisions have been affected by a general unavailability of local
+readings or by the fact that one of the earlier presented readings is
+the preferred one. By including globally ambiguous structures with a
+known preference over available readings, we thus intended to test
+whether participants in our task occasionally choose dispreferred
+readings, even if they were available only at a critical position
+following the preferred readings.
 
@@
 
-\paragraph{Target conditions and positional controls}
+\paragraph{Target conditions and positional controls.}
 Performance on positional controls was high (92\% correct responses on
@@
 The judgments obtained for the four target conditions are depicted in
-Figure \ref{fig:JudgmentsK2}.\dn{we should introduce the actual
-  sequences that we presented so that it is clear what it means to say
-\emph{true} or \emph{false} on some position or other}
+Figure \ref{fig:JudgmentsK2}.
 %
@@
 Further examination of the distribution of local readings revealed a
-clear pattern (see Figure \ref{fig:HistogramLocalReadingsK2}). The
+clear pattern (see Figure~\ref{fig:HistogramLocalReadingsK2}). The
 relative frequency of local judgments per participant strongly
 correlated between all four conditions (all $r>.6, p<.001$). Appart
-from the localists about half of the participants (and 41.5\% of all
-participants) were consistently giving judgments that indicate literal
-readings. Only a minority of participants exhibited
-inconsistency. Reading preferences were more clear-cut in the
-\as-conditions than in the \es-conditions. The number of consistent
-literalists was lower in the \es-conditions (25.6\%) as compared to
-the \as-conditions (57.3\%). Also, the number of participants that
-showed inconsistency was higher in these conditions. However, the
-number of consistent localists did hardly differ between
-constructions.
+from the localists about half of the participants (41.5\% of all
+participants)\dn{is this ``about half''?} were consistently giving
+judgments that indicate literal readings. Only a minority of
+participants exhibited inconsistency. Reading preferences were more
+clear-cut in the \as-conditions than in the \es-conditions. The number
+of consistent literalists was lower in the \es-conditions (25.6\%) as
+compared to the \as-conditions (57.3\%). Also, the number of
+participants that showed inconsistency was higher in these
+conditions. However, the number of consistent localists did hardly
+differ between constructions.
 
@@
 }
+\caption[]{Judgments for the four target conditions}
 \label{fig:HistogramLocalReadingsK2}
-\caption[]{Judgments for the four target conditions}
 \end{figure}
@@
 any degree. How much local preferences deviated between the two
-construction types per participant is depicted in Figure \ref{}. Most
+construction types per participant is depicted in Figure
+\ref{}.\dn{INCLUDE RELEVANT GRAPH!} Most
 participants had exactly the same preferences in the two
@@
 
-\paragraph{Preference-related controls}
-
-Participants' judgments are depicted in Figures \ref{Fig:EC_judgments}
-and \ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if
-they were as expected under one of these readings, and as "other" if
-they were not. The distributions of readings thus coded is illustrated
-in Figure \ref{fig:response-type-freque-TRF}.  Overall, participants
+\paragraph{Preference-related controls.} Participants' judgments are
+depicted in Figures \ref{Fig:EC_judgments} and
+\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they
+were as expected under one of these readings, and as "other" if they
+were not. The distributions of readings thus coded is illustrated in
+Figure \ref{fig:response-type-freque-TRF}.  Overall, participants
 mainly gave answers corresponding to the \lc-reading (65\%).
@@
 critical positions for a reading were the third position ("true" corresponded
-to an \lc reading) and the sixth position ("false" corresponded to an \ec reading)}
-\label{Fig:LC_judgments}.
+to an \lc reading) and the sixth position ("false" corresponded to an \ec reading).}
+\label{Fig:LC_judgments}
 \end{figure}
@@
   \begin{axis}[ybar, 
-               enlarge x limits=0.5,
+               enlarge x limits=0.45,
                enlarge y limits=0.25, 
@@
   \begin{axis}[ybar, 
-               enlarge x limits=0.5, 
+               enlarge x limits=0.45, 
                enlarge y limits=0.25, 
@@
 
-\subsection{Summary \& Interpretation}
-\label{sec:interpretation}
-
-High scores of success clearly indicate that participants understood 
-the incremental verification task and were in general able to give 
-judgements at the earliest possible point in a picture sequence. 
-Moreover, results obtained for the preference-related controls  
-show that our design is able to detect multiple readings and preferences 
-among these. Crucially, the amount of response types for \lc- and \ec-readings 
-reflected the known preference for the former, \emph{irrespective} of the 
-order in which each reading could first be judged in a given sequence.
-Finally, the incremental verification task was generally sensitive
-to prosody. However, prosodic effects were restricted to the preference-related 
-controls. As expected, in these conditions, the dispreferred \ec-reading was chosen 
-significantly more often when supported by prosodic phrasing. Interestingly, 
-contrastively accenting scalar \emph{some} had no effect on the observed 
-decisions in the target conditions. Crucially, local readings occurred in both
-\as- and \es-sentences, independently of prosody. Finally, closer examination of 
-the participants' decisions revealed two groups: participants in the first
-group consistently gave answers corresponding to local readings, whereas participants
-in the second group consistently showed a literal interpretation.
+\subsection{Discussion}
+\label{sec:discussion-1}
+
+\paragraph{Summary \& Interpretation.} High scores of success clearly
+indicate that participants understood the incremental verification
+task and were in general able to give judgements at the earliest
+possible point in a picture sequence.  Moreover, results obtained for
+the preference-related controls show that our design is able to detect
+multiple readings and preferences among these. Crucially, the amount
+of response types for \lc- and \ec-readings reflected the known
+preference for the former, \emph{irrespective} of the order in which
+each reading could first be judged in a given sequence.  Finally, the
+incremental verification task was generally sensitive to
+prosody. However, prosodic effects were restricted to the
+preference-related controls. As expected, in these conditions, the
+dispreferred \ec-reading was chosen significantly more often when
+supported by prosodic phrasing. Interestingly, contrastively accenting
+scalar \emph{some} had no effect on the observed decisions in the
+target conditions. Crucially, local readings occurred in both \as- and
+\es-sentences, independently of prosody. Finally, closer examination
+of the participants' decisions revealed two groups: participants in
+the first group consistently gave answers corresponding to local
+readings, whereas participants in the second group consistently showed
+a literal interpretation.
 
@@
 
-\subsection{General Discussion}
-\label{sec:discussion}
-
-There are a number of conceivable objections to our interpretation of
-the presented results. We will consider the most pressing ones in the
-following and conclude that the main point raised above remains valid:
-neither traditionalism, nor grammaticalism is able to account for the
-present pattern of results.
+\paragraph{Some Potential Objections.} There are a number of
+conceivable objections to our interpretation of the presented
+results. We will consider the most pressing ones in the following and
+conclude that the main point raised above remains valid: neither
+traditionalism, nor grammaticalism is able to account for the present
+pattern of results.
 
@@
 
-There are two kinds of reply to this objection (and others like
-it). Firstly, it is true that we cannot conclude with certainty that
-our data implies that (\ref{bsp:observed-preferences}) is the actual
-preference relation among candidate readings of our target
-sentences. But that does not matter. Even if the observed distribution
-has nothing to do with preferences over readings, the main point
-remains that neither traditionalism nor grammaticalism predicts the
-observed distribution of responses. Secondly, even if we assume that
-the incremental verification task is incapable of indicating
-preferences among pragmatic readings of the relevant kind, then it
-should at least be able to indicate availability of readings. So if
-we deny the observed response patterns the power to indicate
-preference, what should the information about availability of readings
-be that we may safely infer from it? It should be that local readings
-are available and that global readings are not. But that is again not
-predicted by either traditionalism or grammaticalism. The former cannot
-explain the substantial number of local responses, the latter doesn't
-explain the absence of global responses.
+Although we cannot rule out that the incremental verification task
+detects preferences among multiple readings only for some sources of
+variability in readings and not others, it is by no means clear why it
+should not. The burden of argument is on the sceptic. But even if we
+assume that the incremental verification task is incapable of reliably
+indicating preferences among candidate pragmatic enrichments of the
+relevant kind, then it should at least be able to indicate
+availability of readings. So if we deny the observed response patterns
+the power to indicate preference, what should the information about
+availability of readings be that we may safely infer from it? It
+should be that local readings are available and that global readings
+are not. But that is not predicted by either traditionalism or
+grammaticalism. The former cannot explain the substantial number of
+local responses, the latter doesn't explain the absence of global
+responses.
 

### 2013-01-22 text/paper/paper3.tex
acoustics part

@@
 involved the comparison between an accented and a neutral variant, we
-also included a third version of the ambiguous preference related controls, in which our
+also included a third version of the ambiguous preference-related controls, in which our
 speaker produced the sentences without any pronounced
@@
 
-The details of these analyses are found in
-Appendix~\ref{sec:audit-sent-mater}. \dn{Petras Kommentar: Vielleicht
-  sollten wir hier jeweils 1 Figure für akzentuiert vs. nicht und
-  boundary vs. nicht reinbringen. Fabian meint zurecht, dass man nicht
-  einfach die Ergebnisse nur in den Appendix packen kann. Es wären
-  dann halt 4 Figures, da wir ja F0 und duration ansehen, und wir
-  würden nur die experimentell interessanten veranschaulichen und die
-  Statistik dann im Appendix lassen - was meint Ihr? --- Micha sagt ``Ja!''}
+\paragraph{Targets.} 
+Differences between maximal and minimal F0 values for each of the
+single words in the sentence are depicted in
+Figure~\ref{fig:minmax_targets}. As expected, accented
+determiners showed a larger F0 range compared to unaccented versions,
+an effect which was confirmed by statistical analyses (effects on
+the determiner: \acro{Prosody}: \emph{F}=94.8; \emph{p}<.001); 
+Interaction of \acro{Quantifier} and \acro{Prosody}: \emph{F}=13.7; 
+\emph{p}<.01). The observed interaction indicates that these differences
+are even more pronounced in the \as-condition.
+
+\begin{figure}[ht]
+	\centering
+	\subfloat[][\as-sentences]{ 
+		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_ae.png}}
+	    \label{fig:minmax_ae}
+	}
+	\subfloat[][\es-sentences]{
+		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_ge.png}}
+	    \label{fig:minmax_ge}
+	}
+	\caption[]{Differences between minimal and maximal F0 values (in Hz) for 
+	the single regions for \as-sentences (a) and \es-sentences (b).}
+	\label{fig:minmax_targets}
+\end{figure}
+
+Figure~\ref{fig:duration_targets} shows the durational values 
+for each of the single regions in the sentence. 
+Though descriptively small, the duration of accented determiners 
+was significantly increased as opposed to their non-accented counterparts 
+(effects on
+the determiner: \acro{Quantifier}: \emph{F}=31.4; \emph{p}<.001;
+\acro{Prosody}: \emph{F}=23.8; \emph{p}<.001).
+
+\begin{figure}[ht]
+	\centering
+	\subfloat[][\as-sentences]{ 
+		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_ae.png}}
+	    \label{fig:duration_ae}
+	}
+	\subfloat[][\es-sentences]{
+		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_ge.png}}
+	    \label{fig:duration_ge}
+	}
+	\caption[]{Durational values (in ms) for 
+	the single regions for \as-sentences (a) and \es-sentences (b).}
+	\label{fig:duration_targets}
+\end{figure}
+
+A list of the statistical results of each sentential region is provided in 
+Appendix~\ref{sec:audit-sent-mater} (F0 values: Table~\ref{tab:table-B};
+durational values: Table~\ref{tab:table-A})
+
+\paragraph{Preference-related fillers.} 
+Differences between maximal and minimal F0 values for each of the
+single words in the sentence as well as durational values are depicted in
+Figure~\ref{fig:acoustics_fi}. As is
+evident, the largest durational and F0 differences were
+realized at the boundary regions (i.e. Region 5 and Region
+7).
+
+\begin{figure}[ht]
+	\centering
+	\subfloat[][F0 values]{ 
+		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_fi.png}}
+	    \label{fig:acoustics_fi}
+	}
+	\subfloat[][duration]{
+		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_fi.png}}
+	    \label{fig:duration_fi}
+	}
+	\caption[]{Differences between minimal and maximal F0 values (in Hz) (a) as well
+	as durational values (in ms)(b) for 
+	the single regions  .}
+	\label{fig:acoustics_fi}
+\end{figure}
+
+Statistical analyses for F0 on Region 5 reveal that all prosodic realizations
+(neutral vs. (\emph{early boundary} vs. (\emph{late boundary}) differ significantly
+from each other (effect of \acro{Prosody}: \emph{F}=129.3; \emph{p}<.001; all
+single comparisons \emph{p}<.001). On Region 7, F0 analyses again show a main
+effect of \acro{Prosody}: \emph{F}=132.5; \emph{p}<.001. However, the comparison
+between neutral prosody and a \emph{late boundary} did not reach significance 
+(\emph{p}>.2). Finally, durational analyses on reveal that all prosodic realizations
+(neutral vs. (\emph{early boundary} vs. (\emph{late boundary}) differ significantly
+from each other (Region 5: effect of \acro{Prosody}: \emph{F}=819.5; \emph{p}<.001; all
+single comparisons \emph{p}<.001; Region 7: effect of \acro{Prosody}: \emph{F}=1920.3; 
+\emph{p}<.001; all single comparisons \emph{p}<.001.)
+
+A list of the statistical results of each sentential region is provided in 
+Appendix~\ref{sec:audit-sent-mater} (F0 values: Table~\ref{tab:table-D};
+durational values: Table~\ref{tab:table-C})
+
+%\dn{Petras Kommentar: Vielleicht
+%  sollten wir hier jeweils 1 Figure für akzentuiert vs. nicht und
+%  boundary vs. nicht reinbringen. Fabian meint zurecht, dass man nicht
+%  einfach die Ergebnisse nur in den Appendix packen kann. Es wären
+%  dann halt 4 Figures, da wir ja F0 und duration ansehen, und wir
+%  würden nur die experimentell interessanten veranschaulichen und die
+%  Statistik dann im Appendix lassen - was meint Ihr? --- Micha sagt ``Ja!''}
 
@@
 any prior exposure to logic or formal semantics. We excluded three
-subjects due to insufficient performance on controls ($\le 50\%$
+participants due to insufficient performance on controls ($\le 50\%$
 correct answers).
@@
 
-\paragraph{Targets.} Table~\ref{tab:table-A} shows the durational values for each of
-the single regions in the sentence. Crucially, durational values of
-accented determiners were significantly increased as opposed to their
-non-accented counterparts. Overall, \acro{Quantifier} effects were
-observed, which might be attributed to the above-mentioned lexical
-differences, as well as to the fact that \es-structures generally
-contained fewer words, thus leading to a tendency of a durational
-decrease for each of the single words.
-
-Differences between maximal and minimal F0 values for each of the
-single words in the sentence are depicted in
-Table~\ref{tab:table-B}. As is descriptively evident, accented
-determiners showed a larger F0 range compared to unaccented versions,
-an effect which is confirmed by statistical analyses. An additional
-\acro{Quantifier}*\acro{Prosody} interaction indicates that these
-differences are even more pronounced in the \as-condition. Finally,
-comparable to the durational analyses, \acro{Quantifier} effects were
-observed when conditions exhibited lexical differences.
-
-Finally, differences between maximal and minimal F0 values for each of
-the single words in the sentence are given in
-Table~\ref{tab:table-D}. Again, the most reliable differences occur at
-the boundary regions.\dn{provide caption for table D}
-
 \begin{table}
@@
 
+  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-B.png}
+
+  \caption{Difference between minimal and maximal F0 values in Hz for
+    each of the single words in the target sentences. Region 6
+    corresponds to the determiner \emph{einigen}.} 
+  \label{tab:table-B}
+\end{table}
+
+\begin{table}
+  \centering
+
   \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-A.png}
 
-  \caption{Durational values in ms for each of the single regions in the target sentences. Region 6 corresponds to \emph{einigen}.}
+  \caption{Durational values in ms for each of the single regions in the target sentences. 
+  Region 6 corresponds to the determiner \emph{einigen}.}
   \label{tab:table-A}
@@
 
-  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-B.png}
-
-  \caption{Difference between minimal and maximal F0 values in Hz for
-    each of the single words in the target sentences. Region 6
-    corresponds to \emph{einigen}.} 
-  \label{tab:table-B}
+  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-D.png}
+
+  \caption{Difference between minimal and maximal F0 values in Hz  
+  for each of the single regions in
+    the preference-related fillers. Regions 5 and 7 correspond to the
+    nouns preceding the boundaries.}  
+  \label{tab:table-D}
 \end{table}
-
-\paragraph{Preference-related fillers.} Table~\ref{tab:table-C} shows the
-durational values of each of the single words in the sentence. As is
-descriptively evident, the largest durational differences were
-realized at the boundary regions (i.e. Region 5 and Region
-7). Interestingly, small differences between conditions also yielded
-significance at other positions, suggesting that our speaker produced
-the different conditions very consistently (i.e., with little
-variance).
 
@@
 
-\begin{table}
-  \centering
-
-  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-D.png}
-
-  \caption{???}  
-  \label{tab:table-D}
-\end{table}
+%\paragraph{Targets.} Table~\ref{tab:table-A} shows the durational values for each of
+%the single regions in the sentence. Crucially, durational values of
+%accented determiners were significantly increased as opposed to their
+%non-accented counterparts. Overall, \acro{Quantifier} effects were
+%observed, which might be attributed to the above-mentioned lexical
+%differences, as well as to the fact that \es-structures generally
+%contained fewer words, thus leading to a tendency of a durational
+%decrease for each of the single words.
+%
+%Differences between maximal and minimal F0 values for each of the
+%single words in the sentence are depicted in
+%Table~\ref{tab:table-B}. As is descriptively evident, accented
+%determiners showed a larger F0 range compared to unaccented versions,
+%an effect which is confirmed by statistical analyses. An additional
+%\acro{Quantifier}*\acro{Prosody} interaction indicates that these
+%differences are even more pronounced in the \as-condition. Finally,
+%comparable to the durational analyses, \acro{Quantifier} effects were
+%observed when conditions exhibited lexical differences.
+%
+%Finally, differences between maximal and minimal F0 values for each of
+%the single words in the sentence are given in
+%Table~\ref{tab:table-D}. Again, the most reliable differences occur at
+%the boundary regions.\dn{provide caption for table D}
+
+%\paragraph{Preference-related fillers.} Table~\ref{tab:table-C} shows the
+%durational values of each of the single words in the sentence. As is
+%descriptively evident, the largest durational differences were
+%realized at the boundary regions (i.e. Region 5 and Region
+%7). Interestingly, small differences between conditions also yielded
+%significance at other positions, suggesting that our speaker produced
+%the different conditions very consistently (i.e., with little
+%variance).
 

### 2013-01-22 text/paper/paper3.tex
polished plots and fixed table order in appendix

@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{../pictures/paper/graph_ec.pdf}
-\caption{Judgments for prefence-related controls (EC sequence). Relative frequencies
-of {\it yes/no} judgments is plotted against the position within the
-trial. Each {\it EC sequences} consisted of five pictures, in which the
-critical positions for a reading were the third position ("false" corresponded
-to an \ec reading) and the fifth position ("true" corresponded to an \lc reading)}
+\begin{figure}[]
+\centering
+\subfloat[][neutral accentuation]{
+% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.2,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
+                  ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,64)};
+
+        \addplot coordinates {(1,4) (2,2) (3,26) (4,1) (5,5)};
+
+        \legend{yes, no}
+
+      \end{axis}
+\end{tikzpicture}
+% \label{fig:ReadingsAS-ntr}
+}
+\subfloat[][prosody cues \lc-reading]{
+% \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.2,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
+                  % ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,76)};
+
+        \addplot coordinates {(1,4) (2,0) (3,13) (4,2) (5,5)};
+
+        % \legend{yes, no}
+
+      \end{axis}
+
+\end{tikzpicture}
+\label{fig:ReadingsES-ntr}
+}
+
+\subfloat[][prosody cues \ec-reading]{
+% \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.2,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
+                  ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,56)};
+
+        \addplot coordinates {(1,2) (2,1) (3,33) (4,2) (5,6)};
+
+        % \legend{yes, no}
+
+      \end{axis}
+
+\end{tikzpicture}
+% \label{fig:ReadingsAS-acc}
+}
+\subfloat[][unambiguous \lc-reading]{
+% \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.2,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
+                  % ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,1) (2,0) (3,0) (4,1) (5,86)};
+
+        \addplot coordinates {(1,6) (2,0) (3,5) (4,0) (5,2)};
+
+        % \legend{yes, no}
+
+      \end{axis}
+
+\end{tikzpicture}
+% \label{fig:ReadingsES-acc}
+}
+% \includegraphics[width=\textwidth]{../pictures/paper/graph_ec.pdf}
+\caption{Judgments for preference-related controls (EC
+  sequence). Rounded percentages of {\it yes/no} judgments are plotted
+  against the position within the trial. Each EC sequence consisted of
+  five pictures, in which the critical positions for a reading were
+  the third position (\emph{no} corresponded to an \ec reading) and
+  the fifth position (\emph{yes} corresponded to an \lc reading).}
 \label{Fig:EC_judgments}
@@
 
-%\clearpage
-
-\begin{figure}
-\includegraphics[width=\textwidth]{../pictures/paper/graph_lc.pdf}
-\caption{Judgments for prefence-related controls (LC sequence). Relative frequencies
-of {\it yes/no} judgments is plotted against the position within the
-trial. Each {\it LC sequences} consisted of seven pictures, in which the
-critical positions for a reading were the third position ("true" corresponded
-to an \lc reading) and the sixth position ("false" corresponded to an \ec reading).}
+\begin{figure}[]
+\centering
+\subfloat[][neutral accentuation]{
+% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.1,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
+                  ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,0) (2,0) (3,68) (4,0) (5,0) (6,1) (7,0)};
+
+        \addplot coordinates {(1,0) (2,0) (3,5) (4,0) (5,0) (6,25) (7,2)};
+
+        \legend{yes, no}
+
+      \end{axis}
+\end{tikzpicture}
+% \label{fig:ReadingsAS-ntr}
+}
+\subfloat[][prosody cues \lc-reading]{
+% \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.1,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
+                  % ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,0) (2,0) (3,79) (4,1) (5,1) (6,2) (7,1)};
+
+        \addplot coordinates {(1,0) (2,1) (3,3) (4,0) (5,0) (6,13) (7,0)};
+
+        % \legend{yes, no}
+
+      \end{axis}
+
+\end{tikzpicture}
+% \label{fig:ReadingsES-ntr}
+}
+
+\subfloat[][prosody cues \ec-reading]{
+% \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.1,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
+                  ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,0) (2,0) (3,51) (4,2) (5,1) (6,4) (7,0)};
+
+        \addplot coordinates {(1,2) (2,0) (3,8) (4,1) (5,0) (6,30) (7,2)};
+
+        % \legend{yes, no}
+
+      \end{axis}
+
+\end{tikzpicture}
+% \label{fig:ReadingsAS-acc}
+}
+\subfloat[][unambiguous \lc-reading]{
+% \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
+\begin{tikzpicture}[scale=0.8]
+
+      \begin{axis}[ybar, 
+                  enlarge x limits=0.1,
+                  enlarge y limits=0.1,
+                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
+                  % ylabel={\% of answers (rounded)}, 
+                  % xlabel={position}, 
+                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
+                  xtick=data, 
+                  nodes near coords,
+                  nodes near coords align={vertical}, 
+                  x=20, y=1,
+                  ymin = 0, ymax = 100,
+                  bar width=2mm
+        ]
+
+        \addplot coordinates {(1,0) (2,0) (3,88) (4,2) (5,0) (6,5) (7,0)};
+
+        \addplot coordinates {(1,1) (2,0) (3,1) (4,0) (5,0) (6,3) (7,0)};
+
+        % \legend{yes, no}
+
+      \end{axis}
+
+\end{tikzpicture}
+% \label{fig:ReadingsES-acc}
+}
+% \includegraphics[width=\textwidth]{../pictures/paper/graph_lc.pdf}
+\caption{Judgments for preference-related controls (LC
+  sequence). Rounded percentages of {\it yes/no} judgments are plotted
+  against the position within the trial. Each LC sequence consisted of
+  seven pictures, in which the critical positions for a reading were
+  the third position (\emph{yes} corresponded to an \lc reading) and the
+  sixth position (\emph{no} corresponded to an \ec reading).}
 \label{Fig:LC_judgments}
@@
 
+\newpage
+
 \appendix
@@
 
-\begin{table}
+\begin{table}[!hp]
   \centering
@@
 
+\newpage
+
 \printbibliography[heading=bibintoc]

### 2013-01-23 text/paper/paper3.tex
conclusions sec com

@@
 
-\title{Scalar Items in Embedded Position: {A}n Experimental Revisit}
-\author{Fabian Schlotterbeck, Michael Franke and Petra Augurzky}
-\date{}
+\title{Embedded Scalars: {A}n Experimental Revisit} \author{Fabian
+  Schlotterbeck, Michael Franke and Petra Augurzky} \date{}
 
@@
 \begin{abstract}
-  Scalar item \emph{some} is widely assumed to readily undergo a
-  pragmatic meaning enrichment to \emph{some but not all} if it occurs
-  in matrix position. The question under which circumstances this
-  meaning enrichment can take place in embedded position is an
-  important one to decide the delineation between semantics and
-  pragmatics, and therefore currently under renewed debate. % Some claim
+  Scalar item \emph{some} is widely assumed to undergo, given relevant
+  preconditions, a pragmatic meaning enrichment to \emph{some but not
+    all} if it occurs in matrix position. The question under which
+  circumstances this meaning enrichment can take place in embedded
+  position plays an important role in deciding how to delineate
+  semantics and pragmatics. % Some claim
   % that it requires marked intonation for the relevant pragmatic
@@
   % freely.
-  We present a novel experimental paradigm to test whether so-called
-  local readings are available with or without prosodic markedness. On
-  top of adding prosodic manipulation, our experimental design was
-  catered to a number of methodological difficulties that were
-  identified for previous studies, such as the possibility of
-  confounds of pictorial properties. The data obtained refutes both a
-  traditional Gricean view of scalar implicature calculation, as well
-  as the more recent grammatical approach.
+  We present a novel experimental paradigm to test whether the
+  relevant pragmatic enrichment is available in embedded positions
+  with or without prosodic markedness. On top of adding prosodic
+  manipulation, our experimental design was catered to a number of
+  methodological difficulties that were identified for previous
+  related studies. The data obtained refutes both a traditional
+  Gricean view of scalar implicature calculation, as well as the more
+  recent grammatical approach.
 \end{abstract}
@@
 items. Section~\ref{sec:previous-studies} recaps the results of
-previous related studies, pointing out the most important necessary
-amendments that motivated out own design. Section~\ref{sec:exp}
-eventually 
-describes our experimental design and continues to state, analyze and interpret the
-results we obtained. We defend our design and the interpretation of
-the results based on it in Section~\ref{sec:conclusions}.
+related experimental studies, pointing out the most important
+necessary amendments that motivated out own
+design. Section~\ref{sec:exp} eventually describes our experimental
+design and continues to state, analyze and interpret the results we
+obtained.
 
@@
 distribution of responses to \as-sentences found in previous studies
-could in part be explained by differences in typicality of the
-pictures with respect to the possible readings. In the present case
-this kind of reasoning would have to be extended to either cover the
+could be explained by differences in typicality, given an
+\as-sentence, of the pictures used by
+\citet{CliftonDube2010:Embedded-Implic}, as well as
+\citet{ChemlaSpector2010:Experimental-Ev}. In the present case this
+kind of reasoning would have to be extended to either cover the
 typicality of parts of pictures or to figure in subjects' expectations
@@
 revealed picture verification, this does not as such save the day for
-traditionalism or grammaticalism, for the same reasons as given above.
+traditionalism or grammaticalism, because, as argued above, typicality
+would likely still not predict the change in categorical truth-value
+judgement that we found in our experiment.
 
@@
 
+\paragraph{Future Directions.} The data obtained from our experiment
+raises a number of interesting questions for future research. Firstly,
+we found a surprisingly strong tendency of subjects to give literal or
+local answers rather consistently. This seems to be related to what
+has been reported in a number of previous studies on unembedded
+\emph{some}, where a tendency was found as well in subjects to either
+consistently interpret \emph{some} `semantically' as \emph{some and
+  possibly all} or to consistently interpret it `pragmatically' as
+\emph{some and not all}
+\citep[e.g.][]{NoveckPosada2003:Characterizing-,BottNoveck2004:Some-Utterances,DegenTanenhaus2012:Processing-Scal}. This
+inter-subjective consistency has not been paid due attention to in
+previous studies on embedded scalar items. It would be interesting to
+test whether there is any indication of a correlation between, on the
+one hand, subjects' tendencies to give literal vs.~local answers for
+embedded occurrences of \emph{some} and, on the other hand, subjects'
+tendencies to interpret unembedded \emph{some} semantically or
+pragmatically. If such a correlation exists, it would point towards
+the possibility that different subjects may even have different
+lexical representations of \emph{some} or possibly employ different
+processes of interpreting it. If so, this would severely mix up the
+theoretical landscape and should also be taken into account in any
+further study on the processing of scalar items.
+
 \section{Conclusions}

### 2013-01-23 text/paper/paper3.tex
conclusions and future outlook

@@
 
-These findings are hard to explain both by traditionalism and grammaticalism, 
-as no version of either would predict the pattern in (\ref{bsp:observed-preferences}). 
-Traditionalism, if left on its own, fails to predict local readings,
-while grammaticalism, when it relies on the strongest meaning
-hypothesis, fails to predict the right preference order. Let's look
-more closely at each position in turn.
+These findings are hard to explain both by traditionalism and
+grammaticalism, as no version of either would predict the pattern in
+(\ref{bsp:observed-preferences}).  Traditionalism, if left on its own,
+fails to predict local readings, while grammaticalism, when it relies
+on the strongest meaning hypothesis, fails to predict the right
+preference order and, more importantly, cannot explain the absence of
+answers indicative of a global reading. Let's look more closely at
+each position in turn.
 
@@
 previous traditionalist suggestions that local readings are to be
-attributed to specific pragmatic mechanisms. In sum, traditionalism
-alone cannot explain (\ref{bsp:observed-preferences}), but needs an
-additional explanation of local readings for \emph{both} \as-
-\emph{and} \es-sentences.
+attributed to specific pragmatic mechanisms. Other mechanisms might be
+hypothesized as the source of local readings (and we will look at some
+obvious candidates below), but that does not as such save
+traditionalism. Traditionalism alone, as well as traditionalism
+supplemented with the intonational markedness hypothesis, cannot
+explain (\ref{bsp:observed-preferences}), but needs an additional
+explanation of local readings for \emph{both} \as- \emph{and}
+\es-sentences.
 
 Grammaticalism, on the other hand, fails to predict the preference
-relation in (\ref{bsp:observed-preferences}), because it strictly
-contradicts the strongest meaning hypothesis in either of the two
-varieties suggested by \citet{ChierchiaFox2008:The-Grammatical}. This
-shows most clearly in the fact that both versions of the strongest
-meaning hypothesis predict that local readings of \as-sentences are
-preferred over literal ones. The problem, therefore, seems to be the
-selection of readings by the strongest meaning hypothesis. In fact, if
+relation in (\ref{bsp:observed-preferences}), in particular the
+absence of answers indicative of global readings. This is because
+(\ref{bsp:observed-preferences}) strictly contradicts the strongest
+meaning hypothesis in either of the two varieties suggested by
+\citet{ChierchiaFox2008:The-Grammatical}. This shows most clearly in
+the fact that both versions of the strongest meaning hypothesis
+predict that local readings of \as-sentences are preferred over
+literal ones. The problem, therefore, seems to be the selection of
+readings by the strongest meaning hypothesis. In fact, if
 (\ref{bsp:observed-preferences}) is the actual preference over
@@
 
-Summing up so far, the existing versions of traditionalism and
-grammaticalism cannot explain the present results. Of the two
-approaches, grammaticalism seems better suited to account for the
-observed effects. Whereas traditionalism cannot cope with local
-readings (of unaccented sentences), the only thing that grammaticalism
+Summing up so far, the existing versions of traditionalism, even if
+aided by the intonational markedness hypothesis, and grammaticalism
+cannot explain the present results. What would it take to amend either
+framework to make it fit the data we observed? Traditionalism would
+need to explain the possibility of local readings of intonationally
+unmarked sentences. To do so within a traditionalist framework seems
+impossible, so the most common approach is to explain putative
+evidence for local readings away as the result of some other
+phenomenon, such as typicality or contrast
+\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}. We
+argue below that neither explanation plausibly holds for the
+incremental verification task. On the other hand, what grammaticalism
 would have to change is the selection criterion over preferred
@@
 processing studies show that the computation of scalar inferences
-appears to be time- and effort-consuming, when they do arise,
-not when they do not
+appears to be time- and effort-consuming, when they do arise, not when
+they do not
 \citep[c.f.][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
@@
 (\ref{bsp:observed-preferences}) is predicted by the dual of
-defaultism, call it \emph{literalism}, which posits a lexical
-ambiguity but predicts that the logical meanings are \emph{ceteris
-  paribus} preferred over the upper-bounded meanings.
+defaultism, which has not been defended in the literature as far as we
+know, which posits a lexical ambiguity but predicts that the logical
+meanings are \emph{ceteris paribus} preferred over the upper-bounded
+meanings.
 
@@
 readings, grammaticalism must revise its selection criterion among
-readings. In the remainder of this section we would like to discuss
-whether this interpretation of our data is feasible.
+readings.
 
@@
 conceivable objections to our interpretation of the presented
-results. We will consider the most pressing ones in the following and
-conclude that the main point raised above remains valid: neither
-traditionalism, nor grammaticalism is able to account for the present
-pattern of results.
+results. We will consider the most pressing ones in the following.
 
@@
 detects preferences among multiple readings only for some sources of
-variability in readings and not others, it is by no means clear why it
-should not. The burden of argument is on the sceptic. But even if we
-assume that the incremental verification task is incapable of reliably
-indicating preferences among candidate pragmatic enrichments of the
-relevant kind, then it should at least be able to indicate
+variability in readings and not others, it is by no means clear why
+this should be so. The burden of argument is on the sceptic. But even
+if we assume that the incremental verification task is incapable of
+reliably indicating preferences among candidate pragmatic enrichments
+of the relevant kind, then it should at least be able to indicate
 availability of readings. So if we deny the observed response patterns
@@
 of their surrounding shapes. When two universally connected elements
-are present, the mean rate of agreement is higher than when only one
-is present. So, maybe our displays similarly provoked local readings
-because of an overemphasized visual contrast.
+are present, the mean rate of agreement with a suitable \es-sentence
+is higher than when only one is present. So, maybe our displays
+similarly provoked local readings because of an overemphasized visual
+contrast.
 
@@
 already at this position to continue unraveling, given that they were
-generally able of exiting at the earliest possible location. A second
+generally able of exiting at the earliest possible location, as
+evidence by ceiling success rates in our positional controls. A second
 argument that casts doubt on a contrast-based explanation is that our
@@
 plausible that the visual contrast in a picture like in
-\ref{fig:subfig1} alone is enough to overrule a truth-value judgment
-so as to contradict the semantic meaning (even when there is no
-intonational markedness to support such a
+Figure~\ref{fig:subfig1} alone is enough to overrule a truth-value
+judgment so as to contradict the semantic meaning (even when there is
+no intonational markedness to support such a
 reinterpretation). Ultimately, however, even if the local answers in
-our study are contrast effects, the verdict remains that neither
+our study are contrast effects, the verdict remains that
 traditionalism can not account for that piece of the data unless aided
@@
 
-A fourth major conceivable objection maintains that we cannot rule out
-that the way we realized the intonational markedness in the accented
-conditions was not the right kind of intonational
-markedness. Therefore the intonational markedness hypothesis that
-links an increase in local readings to intonation might not be
-falsified by our results. Although true, this still does not help
-vindicate traditionalism, for even without marked intonation local
-readings were available.
+% A fourth major conceivable objection maintains that we cannot rule out
+% that the way we realized the intonational markedness in the accented
+% conditions was not the right kind of intonational
+% markedness. Therefore the intonational markedness hypothesis that
+% links an increase in local readings to intonation might not be
+% falsified by our results. Although true, this still does not help
+% vindicate traditionalism, for even without marked intonation local
+% readings were available.
 
@@
 \citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue that the
-distribution of responses to \as-sentences found in previous studies
-could be explained by differences in typicality, given an
-\as-sentence, of the pictures used by
+distribution of responses to \as-sentences found by
 \citet{CliftonDube2010:Embedded-Implic}, as well as
-\citet{ChemlaSpector2010:Experimental-Ev}. In the present case this
-kind of reasoning would have to be extended to either cover the
+\citet{ChemlaSpector2010:Experimental-Ev} could be explained by
+differences in how typical representations for an \as-sentence the
+presented pictures were. To apply typicality-explanations to the
+incremental verification task, one would have to reason about the
 typicality of parts of pictures or to figure in subjects' expectations
-of pictorial typicality given their uncertainty. On intuitive grounds,
-we take either extension to be far-fetched and implausible. But even
-if this line of explanation can be plausibly extended to incrementally
+of pictorial typicality given their uncertainty about parts of the
+picture that they have not yet seen. On intuitive grounds, we take
+either extension to be far-fetched and implausible. But even if this
+line of explanation can be plausibly extended to incrementally
 revealed picture verification, this does not as such save the day for
 traditionalism or grammaticalism, because, as argued above, typicality
-would likely still not predict the change in categorical truth-value
-judgement that we found in our experiment.
+effects are arguably insufficient to explain the change in categorical
+truth-value judgement that we found in our experiment.
 
@@
 \paragraph{Future Directions.} The data obtained from our experiment
-raises a number of interesting questions for future research. Firstly,
-we found a surprisingly strong tendency of subjects to give literal or
-local answers rather consistently. This seems to be related to what
-has been reported in a number of previous studies on unembedded
-\emph{some}, where a tendency was found as well in subjects to either
-consistently interpret \emph{some} `semantically' as \emph{some and
-  possibly all} or to consistently interpret it `pragmatically' as
-\emph{some and not all}
+also raises a number of issues for future research. Firstly, we found
+a tendency of subjects to give literal or local answers rather
+consistently. This seems to be related to what has been reported in a
+number of previous studies on unembedded \emph{some}, where a tendency
+was found as well in subjects to either consistently interpret
+\emph{some} `semantically' as \emph{some and possibly all} or to
+consistently interpret it `pragmatically' as \emph{some and not all}
 \citep[e.g.][]{NoveckPosada2003:Characterizing-,BottNoveck2004:Some-Utterances,DegenTanenhaus2012:Processing-Scal}. This
-inter-subjective consistency has not been paid due attention to in
+inter-subjective consistency has not been paid any attention to in
 previous studies on embedded scalar items. It would be interesting to
@@
 
+Secondly, given the scarce literature on the topic, more research into
+the role of intonational markedness on pragmatic interpretation is
+clearly needed. Claims about the correlation of certain
+interpretations with certain patterns of intonation are frequently
+made in the theoretical literature, but only backed up by
+introspection and not made precise in their commitment to the exact
+kind of intonational pattern that is hypothesized to be relevant. The
+intonational markedness hypothesis, for instance, seems \emph{prima
+  facie} plausible, but we did not find any evidence for it in our
+experiment. This much is not yet any direct evidence against it
+either, because it is certainly possible that the contrastive accents
+we realized in our experiments, although the most plausible and in
+line with current theorizing about German contrast marking, was not
+the right kind of intonational markedness. This shows for one that
+claims about the putative effects of intonation and prosody must be
+more carefully phrased and filled with detail, but also points to
+further empirical research. The combination of production experiments
+the output of which is fed into a subsequent interpretation experiment
+comes to mind as a first natural continuation.
+
 \section{Conclusions}
@@
 
-\begin{itemize}
-\item future research: isolate consistent localists to probe into \emph{processing}
-\item production study
-\end{itemize}
+We tested experimentally the predictions of traditionalism and
+grammaticalism with respect to the availability of and preferences
+over three types of conceivable pragmatic readings of two types of
+sentences, in which scalar \emph{some} occurred in the scope of either
+a monotonic quantifier \emph{all} or the non-monotonic quantifier
+\emph{exactly one}. To avoid potential confounds of the pictorial
+material, such as through typicality or contrast
+\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi},
+we employed a novel experimental design, the incremental verification
+task, in which subjects were presented with partially covered pictures
+and asked to uncover the picture sequentially until they felt able to
+give a categorical truth-value judgements. Sentence material was
+presented auditorily and contrastive stress on embedded \emph{some}
+was manipulated so as to test the intonational markedness hypothesis,
+which is often used to supplement traditionalism. Both traditionalism
+and grammaticalism do not predict our data well.  Traditionalism fails
+to account for the non-negligible number of responses indicating local
+readings even for intonationally unmarked sentences. Grammaticalism
+fails to predict the absence of answers indicative of global readings
+and the relative abundance of answers indicative of literal readings.
 

### 2013-03-12 text/paper/paper3.tex

@@
 
-Summing up so far, three previous studies have presented diverging
+Summing up so far, three previous experimental studies have presented diverging
 pieces of evidence concerning the status of putative local
@@
 truth value-judgments that would indicate local readings. On the basis
-of this observation, they argue that these readings are simply not
+of this observation, they argue that these readings are not
 available. On the other hand,
@@
 of \citeauthor{GeurtsPouscoulous2009:Embedded-Implic} may be due to a
-bias in their experimental design and employed different methods
-intended to be sensitive enough to reveal effects of local readings:
-either by a choice of the situation that better befits a given
-sentence (\citeauthor{CliftonDube2010:Embedded-Implic}), or by a
-graded truth-value judgment
-(\citeauthor{ChemlaSpector2010:Experimental-Ev}). Both studies found
+bias in their experimental design. They employed different experimental methods
+intended to be sensitive enough to reveal local readings. In the experiment of \citeauthor{CliftonDube2010:Embedded-Implic}
+ participants had to choose the depicted situation that best fits a given
+sentence among a set of alternatives. In the experiment of \citeauthor{ChemlaSpector2010:Experimental-Ev}  participants
+had to provide graded truth-value judgments. Both studies found
 putative evidence in support of local readings.
 
-To account for the diverging results we could draw a distinction
-between \emph{categorical} truth-value judgments and other more
-sensitive measures. If we do so, it could be hypothesized along with
+How can we account for these diverging results? We can think of two possibilities.
+Firstly, we could draw a distinction between \emph{categorical} truth-value judgments
+and other more sensitive measures. It is possible, that truth value judgments are not sensitive enough
+to reveal local reading because they are a strongly dispreferred alternative or, alternatively,
+that a relatively large sample size is needed to detect local readings in truth value judgments (see, however, \citet{Crain1998} for arguments in favour of truth-value judgments as a means of detecting
+dispreferred readings). Secondly, we could explain the diverging results as
+an effect of the different experimental materials. The experiments of
 \citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
-available, but so dispreferred that they do not affect categorical
-truth-value judgments (see, however, \citet{Crain1998} for arguments
-in favour of truth-value judgments as a means of detecting highly
-dispreferred readings).  It could then also be argued, in line with
-traditionalism, that the apparent difference in sensitivity of the
+\citeauthor{ChemlaSpector2010:Experimental-Ev} on the one hand and
+\citet{GeurtsPouscoulous2009:Embedded-Implic} on the other used differed
+with respect to the \emph{types} of situations (as distinguished in Figures~\ref{fig:AS-distinguishing-pics}
+and~\ref{fig:ES-distinguishing-pics}) participants saw during the course
+of the experiment. The presence or absence of alternative situations may
+have led to skewed distributions of judgments and could, thereby, explain the diverging results.
+Skewed distributions may emerge simply because the type of sentence-picture
+combinations shown during an experiment affects the standard of
+judgment. Alternatively, presentation of  particular sentence-picture pairs might have
+primed corresponding logical forms and thereby shift reading preferences in future trials
+(see \citet{Raffray2010}).
+
+With respect to the first alternative, we could then hypothesize along with
+\citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
+available, but so dispreferred that they do not affect categorical truth-value judgments.
+On the other hand, it could then also be argued, in line with traditionalism, that the apparent difference in sensitivity of the
 different judgment types can be explained by the stipulation that the
@@
 along these
-lines]{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}. To
-circumvent this issue, a method for probing into the readings
-for \as- and \es-sentences would therefore ideally evoke categorical
-truth-value judgements: if evidence for local readings can also be
-found using categorical truth-value judgements, it cannot be discarded
-as a secondary non-truth-conditional effect.
-
-Note, however, that the type of judgment is not the only crucial
-difference between the methods of
-\citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} on the one hand and
-\citet{GeurtsPouscoulous2009:Embedded-Implic} on the other. These
-studies also differed with respect to the \emph{types} of situations
-(as distinguished in Figures~\ref{fig:AS-distinguishing-pics}
-and~\ref{fig:ES-distinguishing-pics}) that were shown to the
-participants during the course of the experiment. The presence or
-absence of competing situations may have led to skewed distributions
-of judgments for situations like in Figure \ref{fig:weak}. Such
-effects might emerge simply because the type of sentence-picture
-combinations shown during the experiment affects the standard of
-judgment but could also --maybe even more elegantly-- be explained by
-findings from \citet{Raffray2010} suggesting that exposing
-participants to models may prime corresponding logical forms and
-thereby shift reading preferences. Taking these possibilities into
-account, it remains unclear whether the effects reported by
-\citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} would not also show up
-using ordinary picture verification, in the first place.
-
-For these reasons, we cannot ascribe the effects reported by
+lines]{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}.
+
+Concerning the second possibility, we cannot ascribe the effects reported by
 \citeauthor{CliftonDube2010:Embedded-Implic} and
@@
 
-To conclude, although considerable progress has been made in
-understanding which factors have to be controlled for in order to
-asses the status of local readings, the evidence about availability,
-preference and nature of local readings is still inconclusive. What is
-needed to complement the picture is data that is as independent as
+To resolve these issues, we need to evoke categorical truth value judgments
+for \as- and \es-sentences in a way that is as independent as
 possible of potentially conflating properties of the pictorial
 material and that is nonetheless sensitive enough to detect local
-readings even if they are dispreferred. Given the logical dependencies
-of the relevant readings this is difficult, but, as we will argue
-below, not impossible.
+readings even if they are dispreferred.
 
@@
 \label{sec:procedure} 
+Each experimental trial proceeded as described above.
+The sentence was presented using active PC loud speakers and the picture materials were presented on a computer screen.
+Participants responded using the keyboard.
+By pressing one of four buttons  they could (1) listen to the sentence (up to three times), (2) request additional pictorial information and (3) respond "yes, fits" or (4) "no, does not fit".
+At the beginning of an experimental session participants received written instructions on their task.
+Then they completed an interactive training consisting with of 15 trials in which they were familiarized with the task.
+After the training the actual experiment started.
+Participants were tested individually in a silent room.
+Each session was divided into three blocks and participants were told they could take breaks between blocks.
+In total, an experimental session took about one hour.
+At the end of the session participants received 8 euros compensation.
 
@@
 \paragraph{Target conditions and positional controls.}
-Performance on positional controls was high (92\% correct responses on
-average), indicating that subjects understood the task, giving
-truth-value judgements at the right moment in a sequence without being
-influenced in general by inessential features of the picture material
-or showing general response biases.
+Performance on positional controls was overwhelmingly correct (92\% correct responses on
+average) indicating that participants understood the task and were able to give
+correct truth-value judgments at the adequate point in a sequence. 
+In general, they were not affected by inessential features of the picture materials
+or general response biases.
 
@@
 readings. Judgments compatible with a global reading were seldomly
-obtained. In the \as-conditions (see Figure~\ref{fig:JudgementPercentagesAE}),
+observed. In the \as-conditions (see Figure~\ref{fig:JudgementPercentagesAE}),
 judgments were consistent with literal readings in 65.0\% of the
@@
 
-In order to test wether local readings occurred reliably, we tested whether the
-number of local responses in each condition was higher than expected
-by chance. Local responses had to be given on the last position in
-each trial. If local readings didn't exist we would expect
-participants, who reached the last position (ie. who did not abort the
-trial prior to the last position) to give local judgments not more
-often than expected by chance. On the last position two responses were
-possible. One was compatible with a local reading the other was
-not. Therefore, we would expect 50\% local responses by chance. As it
-turns out local responses were given significantly more often than
-50\% in all target conditions (all Bonferoni corrected p<.05). Note
-that this finding cannot be explained by some kind of general response
-bias on the last position since local readings required a \emph{yes} judgment
-in the \es-conditions but a \emph{no} judgment in the \as-conditions.
-
-In order to test whether accentuation or the quantifier had an
-influence on the distribution of readings, log-linear models 
-including the factors {\it Reading}, {\it Accentuation} and 
-{\it Quantifier}.
-
-Unsurprisingly, there was an effect of \emph{Reading} ($LRCS_1=364.77,
-df_1 = 3, p_1<.001, LRCS_2=364.77, df_2 = 3, p_1<.001,$) because
-overall the readings were distributed inhomogeneously (see Figure
-\ref{fig:ReadingsGE}). The quantifier had an influence on the
-distribution of readings as revealed by a reliable interaction of {\it
-  Reading} and {\it Quantifier} ($LRCS_1=49.32, p_1<.01,LRCS_2=32.16,
-p_1<.01,$). Looking at the data it seemed unlikely that the quantifier
-affected the amount of local readings. We suspected that this
-interaction was due to the higher number of errors and lower number of
-literal readings in the \es-conditions as compared with the
-\as-conditions. A difference in the distribution of judgment types
-between participants was revealed by a reliable interaction of {\it
-  Reading} and {\it Participant} ($LRCS_1=487.70, p_1<.01$). We were
-interested in whether this effect was due to some of the participants
-being more likely to choose literal readings than others. Finally,
-there was a three-way interaction of {\it Participants}, {\it
-  Construction} and {\it Reading} ($LRCS_1, = 143.92, df_1 = 117,
-p_1<.05$) which could stem from the fact that some participants were
-more prone than others to make errors in the \es-conditions.
-
-In order to find out whether the interactions just reported affected
-the amount of local readings, the log-linear models were computed
-again with a different coding of the readings. Here, we only
-considered the amount of local readings versus all other kinds of
-judgments. Judgments were coded as {\it local} and {\it other}. If the
-reported interactions affect the amount of local readings they should
-show up again. The expected but irrelevant effect of {\it Reading} was
-again significant ($LRCS_1=134.55, df_1 = 1, p_1<.001, LRCS_2=144.64,
-df_2 = 1, p_1<.001,$). In addition, the interaction of {\it
-  Participant} and {\it Reading} ($LRCS_1=487.70, p_1<.01$) as well as
-the three-way interaction of {\it Construction}, {\it Participant} and
-{\it Reading} ($LRCS_1=487.70, p_1<.01$) were significant. No other
-effects were significant. In particular, the interaction of {\it
-  Construction} and {\it Reading} was not significant ($LRCS_1=2.10,
-p_1=.15,LRCS_2=.74, p_2=.39$).
-
-The interaction of {\it Participant} and {\it Reading} shows that
-there are indeed varying preferences for local readings among German
-speakers (see Table~\ref{table:answer-types-as}).
+Interestingly, there was considerable variation of response patterns within participants.
+The relative frequencies of local responses seemed to be distributed bimodally (see Figure \ref{fig:HistogramLocalReadingsK2}).
+We classified participants as {\it localists}, {\it globalists} or {\it inconsitent}.
+Table \ref{table:answer-types-as} shows how many of each type we observed.
+Further examination of the distribution of local readings revealed a clear pattern.
+The relative frequency of local judgments per participant strongly
+correlated between all four conditions (all $r>.6, p<.001$). Within the non-localists, about half of the participants (41.5\% of all
+participants) were consistently giving judgments that indicate literal readings. Only a minority of participants exhibited inconsistency.
+
+\begin{figure}[h]
+\centering
+\subfloat[][\as-accented]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_AKZ.jpg}
+\label{fig:ReadingsAE}
+}
+\subfloat[][\as-neutral]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_NTR.jpg}
+\label{fig:ReadingsGE}
+}
+
+\subfloat[][\es-accented]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_AKZ.jpg}
+\label{fig:ReadingsAE}
+}
+\subfloat[][\es-neutral]{
+\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_NTR.jpg}
+\label{fig:ReadingsGE}
+}
+\caption[]{Judgments for the four target conditions}
+\label{fig:HistogramLocalReadingsK2}
+\end{figure}
+
 %
@@
 %
-Further examination of the distribution of local readings revealed a
-clear pattern (see Figure~\ref{fig:HistogramLocalReadingsK2}). The
-relative frequency of local judgments per participant strongly
-correlated between all four conditions (all $r>.6, p<.001$). Appart
-from the localists about half of the participants (41.5\% of all
-participants)\dn{is this ``about half''?} were consistently giving
-judgments that indicate literal readings. Only a minority of
-participants exhibited inconsistency. Reading preferences were more
-clear-cut in the \as-conditions than in the \es-conditions. The number
-of consistent literalists was lower in the \es-conditions (25.6\%) as
-compared to the \as-conditions (57.3\%). Also, the number of
-participants that showed inconsistency was higher in these
-conditions. However, the number of consistent localists did hardly
-differ between constructions.
-
-\begin{figure}[h]
-\centering
-\subfloat[][\as-accented]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_AKZ.jpg}
-\label{fig:ReadingsAE}
-}
-\subfloat[][\as-neutral]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_NTR.jpg}
-\label{fig:ReadingsGE}
-}
-
-\subfloat[][\es-accented]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_AKZ.jpg}
-\label{fig:ReadingsAE}
-}
-\subfloat[][\es-neutral]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_NTR.jpg}
-\label{fig:ReadingsGE}
-}
-\caption[]{Judgments for the four target conditions}
-\label{fig:HistogramLocalReadingsK2}
-\end{figure}
-
-The three way-interaction of {\it Participant}, {\it Construction} and
-{\it Reading} is due to the fact that for some participants
-preferences for local over other readings deviated between the two
-construction types. These deviations were, however, not systematic to
-any degree. How much local preferences deviated between the two
-construction types per participant is depicted in Figure
-\ref{}.\dn{INCLUDE RELEVANT GRAPH!} Most
-participants had exactly the same preferences in the two
-constructions. However, a few had a stronger and a few others a weaker
-preference for local readings in the \es- than in the
-\as-conditions. Since we did not find any systematic patterns
-here, we speculate that the three-way interaction is due to the
-\es-construction beeing understood non-standardly by a
-few participants. This speculation is plausible given the higher
-number of errors in the \es- as compared to the \as-conditions.
-
-The absence of the interaction between {\it Construction} and {\it
-  Participant} indicates that the type of construction does not affect
-the amount of local readings. We assumed, based on the observed
-distribution of judgments, that the type of contsruction affected the
-amount of literal but not local and global readings. To further test
-this assumption, we also considered literal and global readings versus
-other judgments in separate analyses. Comparing global\dn{do you mean LITERAL?} readings versus
+
+In order to test whether local readings occurred reliably, we compared the
+number of local responses in each condition with the expected
+ chance level. Local responses had to be given on the last position in
+each trial where two responses were
+possible. One was compatible with a local reading the other was
+not. Therefore, we would expect 50\% local responses by chance. As it
+turned out, local responses were given significantly more often than
+50\% in all target conditions (all Bonferoni corrected p<.05). Note
+that this finding cannot be explained by a general response
+bias on the last position since local readings required a \emph{yes} judgment
+in the \es-conditions, but a \emph{no} judgment in the \as-conditions.
+
+In order to test whether accentuation or the quantifiers had an
+influence on the distribution of readings, log-linear models 
+including the factors {\it Reading}, {\it Accentuation} and 
+{\it Quantifier} were computed. Since the variability within participants caught
+our attention, we will below also report the interaction of {\it Participant} and {\it Reading}
+in addition to effects of our experimental manipulations.
+
+Unsurprisingly, there was an effect of \emph{Reading} ($LRCS_1=364.77,
+df_1 = 3, p_1<.001, LRCS_2=364.77, df_2 = 3, p_1<.001,$) because
+overall the readings were distributed inhomogeneously (see Figure
+\ref{fig:JudgementPercentages}). The quantifier had an influence on the
+distribution of readings as revealed by a reliable interaction of {\it
+  Reading} and {\it Quantifier} ($LRCS_1=49.32, p_1<.01,LRCS_2=32.16,
+p_1<.01,$). A difference in the distribution of judgment types
+between participants was revealed by a reliable interaction of {\it
+  Reading} and {\it Participant} ($LRCS_1=487.70, p_1<.01$).  Finally,
+there was a three-way interaction of {\it Participants}, {\it
+  Quantifier} and {\it Reading} ($LRCS_1, = 143.92, df_1 = 117,
+p_1<.05$) which could stem from the fact that some participants were
+more prone than others to make errors in the \es-conditions.
+
+In order to find out whether the interactions just reported affected
+the amount of local readings, the log-linear models were computed
+again with a different coding of the readings. Here, we only
+considered the amount of local readings versus all other kinds of
+judgments. Judgments were coded as {\it local} and {\it other}. If the
+reported interactions affected the amount of local readings, they should
+have shown up again. The expected but irrelevant effect of {\it Reading} was
+again significant ($LRCS_1=134.55, df_1 = 1, p_1<.001, LRCS_2=144.64,
+df_2 = 1, p_1<.001$). In addition, the interaction of {\it
+  Participant} and {\it Reading} ($LRCS_1=487.70, p_1<.01$) was significant. The interaction of {\it
+  Quantifier} and {\it Reading} was, however, not significant ($LRCS_1=2.10,
+p_1=.15,LRCS_2=.74, p_2=.39$).
+
+The interaction of {\it Participant} and {\it Reading} indicates that
+there are indeed varying preferences for local readings among German
+speakers (see Table~\ref{table:answer-types-as}). The absence of the interaction
+between {\it Quantifier} and {\it Reading} indicates that the type of quantifier does not affect the amount of local readings.
+Based on the observed distribution of judgments, we suspected that the type of quantifier affected the
+amount of literal but not local and global readings. To test
+this, we also compared literal and global readings versus
+other judgments in separate analyses. Comparing literal readings to
 other judgments {\it Construction} and {\it Reading} were found to
@@
 ($LRCS_1 = 38.4, df_1 =2, p_1 < 001$; $LRCS_2 = 26.1, df_2 =2, p_2 < .001$).
-
-In the analysis by participant, an interaction between {\it Participant} and {\it Reading}
-indicates that reading preferences differed between participants ($LRCS_1 = 376.6,df_1 =37,  
-p_1 < .001$).
-
-In the analysis by items, a three-way interaction between {\it Item}, {\it Prosody} and 
-{\it Reading} was observed ($LRCS_2 = 88.3, df_1 =54, p_2 < .01$). As this effect was 
-unexpected, we carried out additional descriptive analyses (crosstables) in order to examine whether
-the interaction might have been caused by specific items. When excluding the four items with
-the highest deviation from expected frequencies (Residuals > 2.4 in at least one cell), 
-the interaction was no longer significant ($p_2 = .18$).
 

### 2013-03-12 text/paper/paper3.tex
accoustic plots added

@@
 \newcommand{\ivt}{\acro{ivt}}
+
+\pgfplotscreateplotcyclelist{mylist}{% 
+    {solid,black},
+    {dotted,black}, 
+    {dashed,black}, 
+    {loosely dotted,gray}, 
+    {solid,black},
+    {dotted,black},
+    {dashed,black},
+    {loosely dotted}}
 
@@
 At the beginning of an experimental session participants received written instructions on their task.
-Then they completed an interactive training consisting with of 15 trials in which they were familiarized with the task.
+Then they completed an interactive training consisting of 15 trials in which they were familiarized with the task.
 After the training the actual experiment started.
@@
 	\subfloat[][\as-sentences]{
-		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_ae.png}}
+          \begin{tikzpicture}[scale=0.8]
+  \begin{axis}[
+    cycle list name = mylist,
+    legend pos = north west,
+    ymajorgrids,
+    ymax = 250,
+    y = 0.5,
+    x tick label style = {rotate = 50, anchor = east},
+    xtick = data,
+    xticklabels = {alle,diese,N1,sind,mit,einigen,ihrer,N2,verbunden}
+    ]
+    \addplot+[line width = 1.3pt] coordinates {
+      (0 ,17.6)
+      (1 ,27.4)
+      (2 ,82.6)
+      (3 ,32.6)
+      (4 ,62.4)
+      (5 ,211.3333333)
+      (6 ,57.6)
+      (7 ,36.66666667)
+      (8 ,47.13333333)};
+
+  \addplot+[line width = 1.3pt] coordinates {
+        (0 ,19.6        )
+        (1 ,36.46666667 )
+        (2 ,115.1333333 )
+        (3 ,60.6        )
+        (4 ,46          )
+        (5 ,69.86666667 )
+        (6 ,46.66666667)
+        (7 ,71.4)
+        (8 ,61.46666667)};
+
+      \legend{accented, neutral}
+  \end{axis}
+\end{tikzpicture}
+		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_ae.png}}
 	    \label{fig:minmax_ae}
@@
 	\subfloat[][\es-sentences]{
-		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_ge.png}}
+\begin{tikzpicture}[scale=0.8]
+  \begin{axis}[
+    cycle list name = mylist,
+    legend pos = north west,
+    ymajorgrids,
+    ymax = 250,
+    y = 0.5,
+    x tick label style = {rotate = 50, anchor = east},
+    xtick = data,
+    xticklabels = {genau,einer,dieser,N1,ist,mit,einigen,seiner,N2,verbunden}
+    ]
+    \addplot+[line width = 1.3pt] coordinates {
+        (     0 , 59.06666667 )
+        (     1 , 46.26666667 )
+        (     2 , 19          )
+        (     3 , 67.6        )
+        (     4 , 17.6        )
+        (     5 , 39.8        )
+        (     6 , 174.9333333 )
+        (     7 , 30.46666667 )
+        (     8 , 32.46666667 )
+        (     9 , 42.33333333 )};
+
+  \addplot+[line width = 1.3pt] coordinates {
+        (0 , 30.21428571 )
+        (1 , 34.21428571 )
+        (2 , 17.07142857 )
+        (3 , 93.78571429 )
+        (4 , 28.64285714 )
+        (5 , 67.64285714 )
+        (6, 75.5        )
+        (7 , 25.71428571 )
+        (8 , 54.85714286 )
+        (9 , 55)};
+
+      \legend{accented, neutral}
+
+  \end{axis}
+\end{tikzpicture}
+		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_ge.png}}
 	    \label{fig:minmax_ge}
@@
 	\subfloat[][\as-sentences]{ 
-		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_ae.png}}
+\begin{tikzpicture}[scale=0.8]
+  \begin{axis}[
+    cycle list name = mylist,
+    legend pos = north west,
+    ymajorgrids,
+    ymax = 800,
+    ymin = 0,
+    y = 0.15,
+    x tick label style = {rotate = 50, anchor = east},
+    xtick = data,
+    xticklabels = {alle,diese,N1,sind,mit,einigen,ihrer,N2,verbunden}
+    ]
+    \addplot+[line width = 1.3pt] coordinates {
+      (0 ,225.8333333)
+      (1 , 245.3333333 )
+      (2 , 397         )
+      (3 , 172.3333333 )
+      (4 , 230.1666667 )
+      (5 , 445.8333333 )
+      (6, 199.6666667)
+      (7, 503)
+      (8 ,722 )
+    };
+
+  \addplot+[line width = 1.3pt] coordinates {
+        (0 , 216.9212    )
+        (1 , 234.6666667 )
+        (2 , 414.6666667 )
+        (3 , 175.5       )
+        (4 , 170.5       )
+        (5 , 422         )
+        (6 , 194.6666667 )
+        (7 , 494.6666667 )
+        (8 , 748)
+};
+
+      \legend{accented, neutral}
+
+  \end{axis}
+\end{tikzpicture}
+		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_ae.png}}
 	    \label{fig:duration_ae}
@@
 	\subfloat[][\es-sentences]{
-		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_ge.png}}
+          \begin{tikzpicture}[scale=0.8]
+  \begin{axis}[
+    cycle list name = mylist,
+    legend pos = north west,
+    ymajorgrids,
+    ymax = 800,
+    ymin = 0,
+    y = 0.15,
+    x tick label style = {rotate = 50, anchor = east},
+    xtick = data,
+    xticklabels = {genau,einer,dieser,N1,ist,mit,einigen,seiner,N2,verbunden}
+    ]
+    \addplot+[line width = 1.3pt] coordinates {
+(       0 , 307         )
+(       1 , 256         )
+(       2 , 128.6666667 )
+(       3 , 398.6666667 )
+(       4 , 164.6666667 )
+(       5 , 226.6666667 )
+(       6 , 420.6666667 )
+(       7 , 235.3333333 )
+(       8 , 494.6666667 )
+(       9 , 704.6666667 )
+    };
+
+  \addplot+[line width = 1.3pt] coordinates {
+(0 , 285.8333333 )
+(1 , 244.6666667 )
+(2 , 128         )
+(3 , 400         )
+(4 , 152.6666667 )
+(5 , 170         )
+(6 , 383.3333333 )
+(7 , 249.3333333 )
+(8 , 494.6666667 )
+(9 , 764.6666667 )
+};
+
+      \legend{accented, neutral}
+
+  \end{axis}
+\end{tikzpicture}
+		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_ge.png}}
 	    \label{fig:duration_ge}
@@
 	\subfloat[][F0 values]{ 
-		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_fi.png}}
+\begin{tikzpicture}[scale=0.8]
+  \begin{axis}[
+    cycle list name = mylist,
+    legend pos = north west,
+    ymajorgrids,
+    ymax = 250,
+    ymin = 0,
+    y = 0.5,
+    x tick label style = {rotate = 50, anchor = east},
+    xtick = data,
+    xticklabels = {D1,N1,ist,mit,N2,und,N3,mit,N4,verbunden}
+    ]
+    \addplot+[line width = 1.3pt] coordinates {
+(       0 ,27.65517241 )
+(       1 ,91.20689655 )
+(       2 ,32.51724138 )
+(       3 ,27.20689655 )
+(       4 ,53.72413793 )
+(       5 ,19.5862069  )
+(       6 ,210.8965517 )
+(       7 ,15.48275862 )
+(       8 ,66.06896552 )
+(       9 ,68.72413793 )
+    };
+
+  \addplot+[line width = 1.3pt] coordinates {
+(0 ,23.48148148) 
+(1 ,63.07407407) 
+(2 ,13.7037037 ) 
+(3 ,22.7037037 ) 
+(4 ,197.0740741) 
+(5 ,34.03703704) 
+(6 ,95.37037037) 
+(7 ,15.22222222) 
+(8 ,52.18518519) 
+(9 ,123        ) };
+
+  \addplot+[line width = 1.3pt] coordinates {
+(0, 31.7        )
+(1, 80.2        )
+(2, 24.46666667 )
+(3, 31.2        )
+(4, 135.8333333 )
+(5, 54.46666667 )
+(6, 86.96666667 )
+(7, 16.76666667 )
+(8, 51.4        )
+(9, 62.53333333 )};
+
+      \legend{\textsc{ec},\textsc{lc},neutral}
+
+  \end{axis}
+\end{tikzpicture}
+		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_fi.png}}
 	    \label{fig:acoustics_fi}
@@
 	\subfloat[][duration]{
-		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_fi.png}}
+\begin{tikzpicture}[scale=0.8]
+  \begin{axis}[
+    cycle list name = mylist,
+    legend pos = north west,
+    ymajorgrids,
+    ymax = 1400,
+    ymin = 0,
+    y = 0.1,
+    x tick label style = {rotate = 50, anchor = east},
+    xtick = data,
+    xticklabels = {D1,N1,ist,mit,N2,und,N3,mit,N4,verbunden}
+    ]
+    \addplot+[line width = 1.3pt] coordinates {
+(0  , 105.75      )
+(1  , 332.3333333 )
+(2  , 168         )
+(3  , 135.3333333 )
+(4  , 561.3333333 )
+(5  , 143.3333333 )
+(6  , 1183.666667 )
+(7  , 167         )
+(8  , 384.6666667 )
+(9  , 691.3333333 )
+    };
+
+  \addplot+[line width = 1.3pt] coordinates {
+(0  , 100.75      )
+(1  , 306.6666667 )
+(2  , 167         )
+(3  , 139.6666667 )
+(4  , 1268.333333 )
+(5  , 176.3333333 )
+(6  , 535.3333333 )
+(7  , 150.3333333 )
+(8  , 381         )
+(9  , 681.3333333 )
+};
+
+  \addplot+[line width = 1.3pt] coordinates {
+(0  , 98.08333333 )
+(1  , 313.6666667 )
+(2  , 169.3333333 )
+(3  , 141.3333333 )
+(4  , 642.6666667 )
+(5  , 150         )
+(6  , 557.3333333 )
+(7  , 151         )
+(8  , 402.6666667 )
+(9  , 730)
+};
+
+      \legend{\textsc{ec},\textsc{lc},neutral}
+
+  \end{axis}
+\end{tikzpicture}
+		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_fi.png}}
 	    \label{fig:duration_fi}

### 2013-06-17 text/paper/paper3.tex
paper 3 typos and shit

@@
 
-\usepackage[]{svninfo}
 \usepackage{subfig}
@@
 
-\tableofcontents
-
-\svnInfo $Id: paper.tex 102 2012-07-04 10:19:59Z michael.franke $
-
 \section{Introduction}
@@
 \noindent The classical explanation of this inference, following the
-pioneering work of \citet{Grice1975:Logic-and-Conve} \citep[see][for
-recent overview]{Geurts2010:Quantity-Implic}, is that
+pioneering work of \citet{Grice1975:Logic-and-Conve}, is that
 (\ref{bsp:Plain-SI-Implicature}) is a pragmatic inference, a so-called
@@
 utter the semantically stronger and relevant
-(\ref{bsp:Plain-SI-Alternative}).
+(\ref{bsp:Plain-SI-Alternative}) \citep[see][for
+recent overview]{Geurts2010:Quantity-Implic}.
 
@@
 against either of the two rivaling positions as one would hope
-for. This is due to a number of reasons, the most important of which
-are the following. Firstly, previous studies have only accumulated
-limited evidence pertaining to the preference relations between
-putative readings of both types of sentences. Secondly, as
-\citet{Tielvan-Tiel2012:Embedded-Scalar} and
+for. This is due to several reasons. Firstly, previous studies have
+only accumulated limited evidence pertaining to the preference
+relations between putative readings of both types of
+sentences. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
 \citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue, the putative
@@
 sentence material auditorily and explicitly manipulated intonational
-stress on embedded scalar items so as to explicitly so as to test the
-intonational markedness hypothesis. To cater for potential pictorial
-confounds, such as from typicality
-\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi},
-we employed an \emph{incremental verification task} in which parts of
-a to-be-evaluated picture were hidden and only revealed piece-wise at
-the participants' request until they felt able to give a binary
-truth-value judgement (SEE CONROY ????). This way we obtained
-categorical behavioral data that is both indicative of the reading
-subjects assumed and independent of any potential pictorial
-confounds. We also made sure that our method is able to reveal
-information about reading preferences by including a control condition
-with ambiguous sentences with a well-known preference on available
-readings.
+stress on embedded scalar items. To cater for potential pictorial
+confounds, such as from typicality, we employed an \emph{incremental
+  verification task} in which parts of a to-be-evaluated picture were
+hidden and only revealed piece-wise at the participants' request until
+they felt able to give a binary truth-value judgement
+\citep[see][]{Conroy2008}. This way we obtained categorical behavioral
+data that is both indicative of the reading subjects assumed and
+independent of any potential pictorial confounds. We also made sure
+that our method is able to reveal information about reading
+preferences by including a control condition with ambiguous sentences
+with a well-known preference on available readings.
 
@@
 kinds of critical sentences, irrespective of intonational stress. Even
-the intonational markedness hypothesis on its own is contradicted by
+the intonational markedness hypothesis on its own is not supported by
 our data: stress on embedded scalar items did not lead to an increase
@@
 predictions of traditionalism and grammaticalism about availability
-and preference of readings of our target sentences. The intonational
-markedness hypothesis, which is frequently relied on to back-up
-traditionalism, is elaborated on in
-Section~\ref{sec:inton-mark-hypoth}, together with a concise
-assessment of the sparse empirical data on the effects of intonation
-on the interpretation of (embedded) scalar
-items. Section~\ref{sec:previous-studies} recaps the results of
-related experimental studies, pointing out the most important
-necessary amendments that motivated out own
-design. Section~\ref{sec:exp} eventually describes our experimental
-design and continues to state, analyze and interpret the results we
-obtained.
+and preference of readings of our target
+sentences. Section~\ref{sec:previous-studies} recaps the results of
+related experimental studies to the extent necessary to motivate our
+own approach. Section~\ref{sec:exp} eventually contributes our
+experimental design and our results.
 
@@
     \toprule
-    situation    & \multicolumn{3}{c}{truth value} 
+    situation    & \multicolumn{3}{c}{reading} 
   \\ 
@@
 predictions about the readings of \as- and \es-sentences
-\citep[c.f.][for
+\citep[see][for
 overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation}. We
@@
 some leeway in assessing the predictions for each (depending on which
-of several reasonable additional assumptions we should adopt), we will
-distinguish different varieties of both. For convenience, the
-predictions of each (variety of each) position are also summarized in
-Table~\ref{tab:predictions} at the end of this section.
+of several additional assumptions to adopt), we will distinguish
+different varieties of both. Predictions of all relevant variants are
+summarized in Table~\ref{tab:predictions} on
+page~\pageref{tab:predictions}.
 
@@
 
-We refer to traditionalism as traditionalism because of its
-conservative stance towards Grice's original theory of conversational
-implicatures \citep{Grice1975:Logic-and-Conve}. Many author's have
-defended traditionalist positions in this sense. Of the more recent
-literature, we would consider as traditionalist, among others,
-contributions by \citet{Spector2006:Scalar-Implicat},
+Traditionalism gets its name from its conservative stance towards
+Grice's original theory of conversational implicatures
+\citep{Grice1975:Logic-and-Conve}. Many author's have defended
+traditionalist positions in this sense. Of the more recent literature,
+we would consider as traditionalist, among others, contributions by
+\citet{Spector2006:Scalar-Implicat},
 \citet{Sauerland2004:Scalar-Implicat},
@@
 Consequently, the \mymark{Gricean recipe}
-\citep[c.f.][]{Geurts2010:Quantity-Implic} for deriving a simple
+\citep[see][]{Geurts2010:Quantity-Implic} for deriving a simple
 scalar inference like that in (\ref{bsp:Plain-SI-Implicature}) from an
@@
 auxiliary assumptions include relevance of the extra information
-provided in the global reading, mutual awareness that the stronger
+provided by the global reading, mutual awareness that the stronger
 alternative has been a speaker option, the speaker's competence about
@@
 exactly how many students solved how many problems, than that the
-speaker knows exactly how many problems, e.g., Hans solved. In that
-case, or if any other assumption of the Gricean recipe cannot be
-maintained, traditionalism would predict that the literal reading
-would be preferred over the global one. But that means that there are
-at least two varieties of traditionalism that, depending on which
-additional assumptions we would make, yield slightly different
-predictions: \mymark{the strong variety of traditionalism} maintains
-that the auxiliary assumptions of the Gricean recipe hold
+speaker knows exactly how many problems Hans solved. In that case, or
+if any other assumption of the Gricean recipe cannot be maintained,
+traditionalism would predict that the literal reading would be
+preferred over the global one. But that means that there are at least
+two varieties of traditionalism that, depending on which additional
+assumptions we would make, yield slightly different predictions:
+\mymark{the strong variety of traditionalism} maintains that the
+auxiliary assumptions of the Gricean recipe hold
 usually/strongly/unless-completely-intenable and therefore predicts
@@
 least not as a quantity implicature
-\citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. This
+\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. This
 is because traditionalism assumes that quantity implicatures are
@@
 
-The other currently prominent theoretical position is
+Another prominent theoretical position is
 \mymark{grammaticalism}. Recently, a lot of evidence based on
@@
 discussed in favor of this position
-\citep[c.f.][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}. % When
+\citep[see][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}. % When
 % it comes to the predictions of available readings of \as- and
@@
   operation is to be specified exactly within a compositional
-  semantics \citep[c.f.][]{Chierchia2006:Broaden-Your-Vi}.}
+  semantics \citep[see][]{Chierchia2006:Broaden-Your-Vi}.}
 \begin{exe}
@@
 principle that grammaticalists adhere to
-\citep[c.f.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}
+\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}
 is the \mymark{strongest meaning hypothesis} of
@@
   with respect to the readings that these parses give rise to
-  \citep[c.f.][]{ChierchiaFox2008:The-Grammatical}, but we may ignore
+  \citep[see][]{ChierchiaFox2008:The-Grammatical}, but we may ignore
   this detail here for ease of exposition.} then define \emph{ceteris
@@
 local readings are a marked phenomenon, and not the product of the
-same process as run-of-the-mill scalar implicatures associated with
-scalar items in matrix position. If supplemented with the intonational
-markedness hypothesis, traditionalists would therefore predict that
-local readings are available for \as- and \es-sentences, but only if
-intonationally marked by contrastive stress; since this reading is
-marked, presumably it would still be predicted to be dispreferred even
-if available.
+same process as run-of-the-mill scalar implicatures. If supplemented
+with the intonational markedness hypothesis, traditionalists would
+therefore predict that local readings are available for \as- and
+\es-sentences, but only if intonationally marked by contrastive
+stress; since this reading is marked, presumably it would still be
+predicted to be dispreferred even if available.
 
@@
 \citet{SchwarzClifton2008:Strengthening-o}, examining the effects of
-contrastive accentuation of "or" in non-embedded sentences like {\it
-  Mary will invite Fred or/OR Sam to barbecue}. After listening to
+contrastive accentuation of \emph{or} in non-embedded sentences like
+{\it Mary will invite Fred or/OR Sam to barbecue}. After listening to
 these sentences, participants were presented two alternative readings
@@
 To sum up so far, though an effect of contrastive accentuation has
-been claimed tobe essential for triggering local implicatures,
+been claimed to be essential for triggering local implicatures,
 experimental evidence is currently mixed, suggesting potential effects
@@
   is a little more complex, but we will gloss over this here, treating
-  their data, as if it was obtained for \es-sentences.} Subjects were
-presented with pictures like those in Figure~\ref{fig:weak} and
+  their data, as if it had been obtained for \es-sentences.} Subjects
+were presented with pictures like those in Figure~\ref{fig:weak} and
 \ref{fig:local} where the local reading gets a different truth-value
@@
 \citep{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. In
-the following, we will review these empirical studies in some detail,
-as they constitute an important background for our own experiment. We
-will first consider a comment by
-\citet{CliftonDube2010:Embedded-Implic}, which explicitly
-distinguishes between the availability of a reading and its
-preference.
+the following, we will review these empirical studies briefly, as they
+provide the background for our own experiment. % We will first consider
+% a comment by \citet{CliftonDube2010:Embedded-Implic}, which explicitly
+% distinguishes between the availability of a reading and its
+% preference.
 
@@
 In a reply to \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s
-study \citeauthor{CliftonDube2010:Embedded-Implic} raised the question
+study \citet{CliftonDube2010:Embedded-Implic} raised the question
 whether the use of a picture-verification paradigm might have been
@@
 local and literal readings. To this end, Clifton and Dube developed a
-picture-choice task where subjects were presented with an AS-sentence
+picture-choice task where subjects were presented with an \as-sentence
 and a pair of pictures, hence introducing the option to choose between
@@
 ``neither'' answers in this case again suggest that the local reading
-is available. Taken together,
+is available. In sum,
 \citeauthor{CliftonDube2010:Embedded-Implic} take these results to
@@
 cases where candidate readings stand in entailment relations
-\citep[c.f.][for this latter
+\citep[see][for this latter
 criticism]{Sauerland2010:Embedded-Implic}. To meet these potential
@@
 Figure~\ref{fig:Chemla-Spector}, to indicate how much they considered
-a picture fitting for a given sentence \citep[c.f.][for more on this
+a picture fitting for a given sentence \citep[see][for more on this
 method]{Chemla2009:Presuppositions}.
@@
 after all, so that no case can be made for lexicalism or
-grammaticalism on the basis of these data \citep[c.f.][for arguments
+grammaticalism on the basis of these data \citep[see][for arguments
 along these
@@
 \emph{few}, \emph{most} or \emph{many}
-\citep[c.f.][]{DegenTanenhaus2012:Processing-Scal}. For these reasons,
+\citep[see][]{DegenTanenhaus2012:Processing-Scal}. For these reasons,
 we believe that typicality and other pictorial effects need to be
@@
 preferences of different readings of \as- and \es-sentences in German,
-we were looking for a way to unambiguously map responses from a picture
-verification task to specific readings. We were particularly
+we were looking for a way to unambiguously map responses from a
+picture verification task to specific readings. We were particularly
 interested in the question whether local readings would be observed at
-all, and whether their presence or absence would be modulated by
-a contrastive accent on the scalar item. Moreover, we were  
-interested in obtaining information about the relative preferences 
-of the different readings. In addition, we wanted
-to minimize all effects of alleged typicality of pictures. To achieve this, we designed an experiment employing a
-modified version of picture verification, namely the
-\mymark{incremental verification task} (\acro{ivt}, SEE CONROY
-????). The general idea is that subjects are requested to judge
-sentence material based on pictures that do not necessarily contain
-all the information necessary to judge a certain reading true or
-false. In that case, participants can demand that more information be
+all, and whether their presence or absence would be modulated by a
+contrastive accent on the scalar item. Moreover, we were interested in
+obtaining information about the relative preferences of the different
+readings. In addition, we wanted to minimize all effects of alleged
+typicality of pictures. To achieve this, we used an
+\mymark{incremental verification task} (\acro{ivt}), which is a
+modified version of picture verification \citep[see][]{Conroy2008}. The
+general idea is that subjects are requested to judge sentence material
+based on pictures that do not necessarily contain all the information
+necessary to judge a certain reading true or false. In that case,
+participants can demand that more information be
 revealed. Participants are instructed to make a truth-value judgment
@@
 response, as all the connections of one of the letters are now
-uncovered, and it is now visible that one of the letters is not
+uncovered, and it is now clear that at least one of the letters is not
 connected to all of its triangles. Finally, decisions concerning the
@@
 uncovered. In this case, the critical position shown in
-Figure~\ref{fig:exseqAS3} is incompatible with a local reading: One of
+Figure~\ref{fig:exseqAS3} is incompatible with a local reading: one of
 the central elements is linked to all of its surrounding elements,
-thus yielding to \emph{false} answers if participants indeed adopted
+thus yielding \emph{false} answers if participants indeed adopted
 the local reading. Note that associating the final position with
@@
 positions in the incrementally revealed picture sequence can be mapped
-uniquely to candidate reading. All other \emph{true} or \emph{false}
-answer were counted as errors. The mapping between responses and
+uniquely to candidate readings. All other \emph{true} or \emph{false}
+answers were counted as errors. The mapping between responses and
 readings is summarized in Table~\ref{tab:mappingAS}.
@@
 the bells is linked to some but not all of its semicircles, while all
-of the other bells are linked to all of them. Note that again, global
-and literal readings differ from local readings with respect to their
-truth values. Mappings between responses and readings are summarized
-in Table \ref{tab:mappingES}.
+of the other bells are linked to all of them. Note that global and
+literal readings again differ from local readings with respect to
+their truth values. Mappings between responses and readings are
+summarized in Table \ref{tab:mappingES}.
 
 \paragraph{Positional controls.} In order to make sure that subjects
-understood the task, i.e., gave truth-value judgements neither sooner
-not later than at the first possible position in a sequence, we
-included a set of control conditions. These also controlled for
-response biases. For each of the three readings in the \as- and
-\es-conditions, we constructed an unambiguous control sentence as in
-(\ref{bsp:controls-as}) and (\ref{bsp:controls-es}), requiring the
-same judgement at the identical position in the same sequence used for
-the respective targets. For instance, example
-(\ref{bsp:controls-as-1}) requires a \emph{true}-response analogous to
-the \as-sentence in (\ref{ex:as}) under its literal reading,
-(\ref{bsp:controls-as-2}) corresponds to the \as-sentence under its
-global reading and (\ref{bsp:controls-as-3}) corresponds to its local
-reading. With regard to the \es-sentences, controls like
-(\ref{bsp:controls-es-1}) correspond to the global reading,
-(\ref{bsp:controls-es-2}) to the literal and (\ref{bsp:controls-es-3})
-to the local reading. If, independently of sentence meaning, there was
-any bias to respond in a certain way at any point in the sequences,
-such as to preferably unravel the whole picture, this should affect
-control sentences to the same degree as it affects target conditions.
+understood the task, i.e., gave truth-value judgements at the first
+possible position in a sequence, we included a set of control
+conditions. These also controlled for response biases. For each of the
+three readings in the \as- and \es-conditions, we constructed an
+unambiguous control sentence as in (\ref{bsp:controls-as}) and
+(\ref{bsp:controls-es}), requiring the same judgement at the identical
+position in the same sequence used for the respective targets. For
+instance, example (\ref{bsp:controls-as-1}) requires a
+\emph{true}-response analogous to the \as-sentence in (\ref{ex:as})
+under its literal reading, (\ref{bsp:controls-as-2}) corresponds to
+the \as-sentence under its global reading and
+(\ref{bsp:controls-as-3}) corresponds to its local reading. With
+regard to the \es-sentences, controls like (\ref{bsp:controls-es-1})
+correspond to the global reading, (\ref{bsp:controls-es-2}) to the
+literal and (\ref{bsp:controls-es-3}) to the local reading. If,
+independently of sentence meaning, there was any bias to respond in a
+certain way at any point in the sequences, such as to preferably
+unravel the whole picture, this should affect control sentences to the
+same degree as it affects target conditions.
 
@@
 had an influence on responses, we included a second type of control
-conditions. Secondly, these controls served as a test whether the
+conditions. Moreover, these controls served as a test whether the
 incremental verification task could possibly detect at least ordinal
@@
 thereby ending the trial. In that case it would be unclear if these
-decisions have been affected by a general unavailability of local
+decisions had been affected by a general unavailability of local
 readings or by the fact that one of the earlier presented readings is
@@
 whether participants in our task occasionally choose dispreferred
-readings, even if they were available only at a critical position
+readings, even if these were available only at a critical position
 following the preferred readings.
@@
 We therefore included globally ambiguous \emph{late-closure
-  structures} as in (\ref{bsp:target-related}), which have been
+  sentences} as in (\ref{bsp:target-related}), which have been
 repeatedly shown to exhibit interpretive preferences.
@@
 
-\ex \gll Der Brief ist mit Kreisen, die Sonnen beinhalten und Vierecken
-  verbunden. \label{bsp:target-related2}\\
-The letter is with circles, which suns contain and squares connected.\\
-The letter is connected with circles containing suns, and with squares.
-
 \end{exe}
 In late-closure sentences, a modifier such as a relative clause or a
-prepositional phrase can be attached to one of two preceding
-hosts. For instance, in (\ref{bsp:target-related}), the prepositional
-phrase \emph{with suns} can be attached to the preceding noun
-\emph{squares}, resulting in the so-called \emph{late-closure} or
+prepositional phrase (\acro{pp}) can be attached to one of two
+preceding hosts. For instance, in (\ref{bsp:target-related}), the
+\acro{pp} \emph{with suns} can be attached to the preceding
+noun \emph{squares}, resulting in the so-called \emph{late-closure} or
 \emph{low-attachment} reading
@@
 
-For each sentence, two sequences were designed. In the first one, the
+For each such sentence, two sequences were designed. In the first one, the
 critical position associated with the dispreferred early-closure
@@
 %
-\begin{figure}[ht]
+\begin{figure}[t]
 	\centering
@@
 
+We also tested structurally disambiguated versions like
+(\ref{bsp:target-related2}), one for each sentence type, for proper
+comparison.
+
+\begin{exe}
+
+\ex \gll Der Brief ist mit Kreisen, die Sonnen beinhalten, und Vierecken
+  verbunden. \label{bsp:target-related2}\\
+The letter is with circles, which suns contain and squares connected.\\
+The letter is connected with circles containing suns, and with squares.
+
+\end{exe}
+
 \begin{figure}[ht]
@@
 classification of contrast in German is still under debate
-\citep[see][]{Uhmann91,Fery93,Grabe98,Toepel06, Sudhoff10}.  These
-approaches have in common that from an acoustic perceptive, prosodic
-prominence of contrastively accented constituents is realized by
+\citep[see][]{Uhmann91,Fery93,Grabe98,Toepel06, Sudhoff10}.  Still,
+all of these approaches have in common that from an acoustic
+perceptive, prosodic prominence of contrastively accented constituents
+is realized by
 
@@
 
-\noindent We therefore recorded sentences by a trained speaker
-familiar with the concept of contrastive focus and instructed her to
-produce contrast as described in 1 and 2. Both \as-sentences and
-\es-sentences were recorded in two versions each. In the accented
-version, a pitch accent was placed on {\it einige}. The second version
-had neutral prosody.  If accentuation is the driving force for local
-readings, we would expect a higher proportion of local readings in the
-former than in the latter version of the sentences.
+\noindent We therefore recorded sentences by a phonetically trained
+female native speaker of German familiar with the concept of
+contrastive focus and instructed her to produce contrasts as described
+above. Both \as-sentences and \es-sentences were recorded in two
+versions each. In the accented version, a contrastive stress was
+placed on {\it einige}. The second version had neutral prosody.  If
+accentuation is the driving force for local readings, we would expect
+a higher proportion of local readings in the former than in the latter
+version of the sentences.
 
@@
 \label{sec:procedure} 
-Each experimental trial proceeded as described above.
-The sentence was presented using active PC loud speakers and the picture materials were presented on a computer screen.
-Participants responded using the keyboard.
-By pressing one of four buttons  they could (1) listen to the sentence (up to three times), (2) request additional pictorial information and (3) respond "yes, fits" or (4) "no, does not fit".
-At the beginning of an experimental session participants received written instructions on their task.
-Then they completed an interactive training consisting of 15 trials in which they were familiarized with the task.
-After the training the actual experiment started.
-Participants were tested individually in a silent room.
-Each session was divided into three blocks and participants were told they could take breaks between blocks.
-In total, an experimental session took about one hour.
-At the end of the session participants received 8 euros compensation.
+Each experimental trial proceeded as described above. The sentence was
+presented using active PC loud speakers and the picture materials were
+presented on a computer screen. Participants responded using the
+keyboard. By pressing one of four buttons they could (i) listen to the
+sentence (up to three times), (ii) request additional pictorial
+information, (iii) respond "yes, fits" or (iv) "no, does not
+fit". At the beginning of an experimental session participants
+received written instructions on their task. Then they completed an
+interactive training consisting of 15 trials in which they were
+familiarized with the task.  After the training the actual experiment
+started. Participants were tested individually in a silent room. Each
+session was divided into three blocks and participants were told they
+could take breaks between blocks. In total, an experimental session
+took about one hour. At the end of the session participants received 8
+euros compensation.
 
@@
 
-\paragraph{Target sentences and positional controls}
+\paragraph{Target sentences and positional controls.}
 
 We constructed a set of 15 items for German \as- and \es-sentences,
-respectively, analogous to the examples in \ref{ex:as} and
-\ref{ex:es}. Sentences were introduced by a subject {\small
-  \acro{DP}}, including the quantifiers {\it alle diese} ("all of
+respectively, analogous to the examples in (\ref{ex:as}) and
+(\ref{ex:es}). Sentences were introduced by a subject {\acro{dp}}, including the quantifiers {\it alle diese} ("all of
 these") or {\it genau eine(r) der} ("exactly one of these"), as well
 as the head noun which denoted different icons, such as letters or
-bells. Subjects were followed by an auxiliary, and a {\small
-  \acro{PP}} containing {\it einige}, a possessive pronoun, and a noun
-denoting a geometrical object, e.g. {\it einigen seiner
+bells. Subjects were followed by an auxiliary, and a {
+  \acro{pp}} containing {\it einige}, a possessive pronoun, and a noun
+denoting a geometrical object, e.g., {\it einigen seiner
   Dreiecke/Quadrate} ("some of its triangles/squares"). The possessive
@@
 
-\paragraph{Preference-related control sentences}
+\paragraph{Preference-related control sentences.}
 For controlling preferences, 28 sentences that were ambiguous between
@@
 disambiguated counterparts were constructed as described above. In
-these sentences, subject {\small \acro{DP}}s were always denoting
+these sentences, subject \acros{dp} were always denoting
 icons and were followed by an auxiliary. In the ambiguous sentences,
-the auxiliary was followed by two {\it mit}-{\small \acro{PP}}s.  The
-first of these {\small \acro{PP}}s consisted in a coordination of two
+the auxiliary was followed by two {\it mit}-\acros{pp}.  The
+first of these \acros{pp} consisted in a coordination of two
 nouns denoting geometrical objects, whereas the second PP denoted
@@
 
-\paragraph{Acoustic properties}
-A phonetically trained female native speaker of German was instructed
-to realize two prosodic versions of each target sentence, and three
-versions of the ambiguous preference-related controls. In addition to these
-sentences, the unambiguous preference-related controls, the positional controls
-and a set of unrelated fillers were also recorded. For these constructions, the speaker was instructed
-to realize prosodic contours as neutral and natural as possible.
+\paragraph{Acoustic properties.}
+% A phonetically trained female native speaker of German was instructed
+% to realize two prosodic versions of each target sentence, and three
+% versions of the ambiguous preference-related controls. In addition to
+% these sentences, the unambiguous preference-related controls, the
+% positional controls and a set of unrelated fillers were also
+% recorded. For these constructions, the speaker was instructed to
+% realize prosodic contours as neutral and natural as possible.
 
@@
 produced with a contrastive pitch accent as well as with a neutral
-accent. Contrastive accents in German are realized by an increase in F0 (range)
-as well as by a longer duration (see Section~\ref{sec:design} above). A set of 15 
+accent. % Contrastive accents in German are realized by an increase in F0 (range)
+% as well as by a longer duration (see Section~\ref{sec:design} above). 
+A set of 15 
 experimental items was recorded for each condition (\as vs.~\es, \emph{accented} 
@@
 properties, we calculated durational values as well as difference
-values between minimal and maximal F0 for each word. As targets
+values between minimal and maximal F0 for each word. Since targets
 slightly differed with respect to the total number of words as well as
@@
 Appendix~\ref{sec:audit-sent-mater} (F0 values: Table~\ref{tab:table-B};
-durational values: Table~\ref{tab:table-A})
+durational values: Table~\ref{tab:table-A}).
 
@@
 they do not
-\citep[c.f.][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
+\citep[see][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
 there is also competing evidence that scalar inferences are available
@@
   discussion of \emph{Hurford's constraint}
-  \citep[c.f.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2009:Hurfords-Constr,ChierchiaFox2008:The-Grammatical},
+  \citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2009:Hurfords-Constr,ChierchiaFox2008:The-Grammatical},
 so we skip this here.}
@@
 subjects reported this), the latter arguably is not
-\citep[c.f.][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
+\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
 if the distribution of responses is indicative of the known preference

### 2013-06-18 text/paper/paper3.tex
sec 4.4 streamlined

@@
 
-\subsection{Reflection: Categorical Judgements \& Typicality}
+\subsection{Reflection}
 \label{sec:local-read-categ}
 
-Summing up so far, three previous experimental studies have presented diverging
-pieces of evidence concerning the status of putative local
-readings. In their picture verification experiment
-\citet{GeurtsPouscoulous2009:Embedded-Implic} did not observe any
-truth value-judgments that would indicate local readings. On the basis
-of this observation, they argue that these readings are not
-available. On the other hand,
+Summing up, three experimental studies have presented diverging pieces
+of evidence. % \citet{GeurtsPouscoulous2009:Embedded-Implic} did not
+% observe any truth value-judgments that would indicate local readings
+% in a picture verification task and thus conclude that these readings
+% are unavailable. \citet{CliftonDube2010:Embedded-Implic} and
+% \citet{ChemlaSpector2010:Experimental-Ev} employed different designs
+% intended to be sensitive enough to reveal local readings. Both studies
+% found putative evidence in support of local readings.
+Differences in results are likely due to differences in experimental
+design, in particular due to (i) the type of elicited judgement and
+(ii) the possibility of conflating pictorial effects.
+
+\paragraph{Judgement Type.} We could draw a distinction between
+\emph{categorical} truth-value judgments and other more sensitive
+measures. The former are possibly not sensitive enough to reveal
+dispreferred readings with small samples, but the latter may be. We
+could then hypothesize along with
 \citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} argue that the findings
-of \citeauthor{GeurtsPouscoulous2009:Embedded-Implic} may be due to a
-bias in their experimental design. They employed different experimental methods
-intended to be sensitive enough to reveal local readings. In the experiment of \citeauthor{CliftonDube2010:Embedded-Implic}
- participants had to choose the depicted situation that best fits a given
-sentence among a set of alternatives. In the experiment of \citeauthor{ChemlaSpector2010:Experimental-Ev}  participants
-had to provide graded truth-value judgments. Both studies found
-putative evidence in support of local readings.
-
-How can we account for these diverging results? We can think of two possibilities.
-Firstly, we could draw a distinction between \emph{categorical} truth-value judgments
-and other more sensitive measures. It is possible, that truth value judgments are not sensitive enough
-to reveal local reading because they are a strongly dispreferred alternative or, alternatively,
-that a relatively large sample size is needed to detect local readings in truth value judgments (see, however, \citet{Crain1998} for arguments in favour of truth-value judgments as a means of detecting
-dispreferred readings). Secondly, we could explain the diverging results as
-an effect of the different experimental materials. The experiments of
-\citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} on the one hand and
-\citet{GeurtsPouscoulous2009:Embedded-Implic} on the other used differed
-with respect to the \emph{types} of situations (as distinguished in Figures~\ref{fig:AS-distinguishing-pics}
-and~\ref{fig:ES-distinguishing-pics}) participants saw during the course
-of the experiment. The presence or absence of alternative situations may
-have led to skewed distributions of judgments and could, thereby, explain the diverging results.
-Skewed distributions may emerge simply because the type of sentence-picture
-combinations shown during an experiment affects the standard of
-judgment. Alternatively, presentation of  particular sentence-picture pairs might have
-primed corresponding logical forms and thereby shift reading preferences in future trials
-(see \citet{Raffray2010}).
-
-With respect to the first alternative, we could then hypothesize along with
-\citeauthor{CliftonDube2010:Embedded-Implic} and \citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
-available, but so dispreferred that they do not affect categorical truth-value judgments.
-On the other hand, it could then also be argued, in line with traditionalism, that the apparent difference in sensitivity of the
-different judgment types can be explained by the stipulation that the
-results reported by \citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} reflect something other
-than (strongly) truth-relevant speaker-intended meaning enrichments
-after all, so that no case can be made for lexicalism or
-grammaticalism on the basis of these data \citep[see][for arguments
-along these
+\citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
+available, but so dispreferred that they do not affect categorical
+truth-value judgments.
+
+On the other hand, \citet{Crain1998} argues in
+favor of truth-value judgments as a means of detecting dispreferred
+readings. Consequently, traditionalists could reply that the putative
+evidence for local readings in non-categorical judgement tasks might
+reflect something other than (strongly) truth-relevant
+speaker-intended meaning enrichments. Hence no case can be made for
+lexicalism or grammaticalism on the basis of these data
+\citep[see][for arguments along these
 lines]{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}.
 
-Concerning the second possibility, we cannot ascribe the effects reported by
-\citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} to the availability of
-local readings with
-certainty. \citet{ChemlaSpector2010:Experimental-Ev} themselves
-acknowledge the possibility that the \emph{typicality} of a picture
-with respect to some meaning may affect graded truth-value
-judgments. Strengthening this possibility, they show that graded
-judgments of \as-sentences differ significantly for different
-instantiations of the situation types from
-Figure~\ref{fig:AS-distinguishing-pics}, that vary in the amount of
-connections without changing the assignment of truth values to
-candidate readings. \citeauthor{ChemlaSpector2010:Experimental-Ev}
-suggest that typicality of the pictorial material can account for
-these differences, but submit that this does not explain away the high
+To resolve this issue, we would ideally like to have a design that
+elicits categorical judgements, but is still possibly sensitive enough
+to detect dispreferred readings.
+
+\paragraph{Pictorial Effects.} Choice of pictorial material can have
+an effect on obtained results \citep[see][for related
+discussion]{Raffray2010}. It is often possible to present different
+numbers of links between icons in pictures like in
+Figures~\ref{fig:AS-distinguishing-pics}
+and~\ref{fig:ES-distinguishing-pics}, without changing the
+truth-values of relevant readings. Indeed, the pictorial material used
+in previous studies differed in this respect, and that might explain
+some of the differences in results.
+
+If that is so, then we cannot ascribe the effects reported by
+\citet{CliftonDube2010:Embedded-Implic} and
+\citet{ChemlaSpector2010:Experimental-Ev} to the availability of local
+readings with certainty. \citet{ChemlaSpector2010:Experimental-Ev}
+also acknowledge the possibility that the \emph{typicality} of a
+picture with respect to some meaning may affect graded truth-value
+judgments. They show that graded judgments of \as-sentences differ
+significantly for different pictures that agree on the truth value of
+relevant readings but differ with respect to the amount of connections
+between icons. \citeauthor{ChemlaSpector2010:Experimental-Ev} suggest
+that typicality of the pictorial material can account for these
+differences, but submit that this does not explain away the high
 acceptance of pictures like Figure \ref{fig:weak}. The latter point is
 disputed by \citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates
-that a huge chunk of variance in the data of
-\citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} on \as-sentences can be
+that a huge chunk of variance in the responses to \as-sentences can be
 explained as typicality effects, dispensing the need to appeal to the
@@
 typicality structures associated with the quantifiers {\it all} and
-{\it some} \citep[as done also by][]{DegenTanenhaus2011:Making-Inferenc} and predicted the judgments of \as-sentences obtained by
+{\it some} \citep[as done also
+by][]{DegenTanenhaus2011:Making-Inferenc} and predicted the judgments
+of \as-sentences obtained by
 \citeauthor{ChemlaSpector2010:Experimental-Ev} based on these
@@
 
-To resolve these issues, we need to evoke categorical truth value judgments
-for \as- and \es-sentences in a way that is as independent as
-possible of potentially conflating properties of the pictorial
-material and that is nonetheless sensitive enough to detect local
-readings even if they are dispreferred.
-
-On top of this, it would be desirable to obtain further information
-about the relative preferences among all putative readings, so as to
-be able to decide between theoretical positions, as outlined in
-Section~\ref{sec:theories-predictions}. Neither of the previous
-studies gives us that, either because they simply have not
-investigated all the relevant comparisons
-(\citet{GeurtsPouscoulous2009:Embedded-Implic},
-\citet{CliftonDube2010:Embedded-Implic}), or because they cannot
-safely derive the required information for danger of conflating
-preferences for readings with preferences for pictures
-(\citet{ChemlaSpector2010:Experimental-Ev}).
-
-Finally, the above-mentioned studies did not control for possible
-conflating effects of ``silent prosody''. A growing number of evidence
-suggests that numerous factors might influence accent placement and
-prosodic phrasing even while reading, amongst them default
-accentuation, constituent length, rhythmic phenomena, and individual
-variation \citep[e.g.][]{Augurzky08,Bader98,Fodor98,Fodor02,Kentner12,
+\paragraph{Upshot.} Taken together, we would ideally like a design
+that evokes categorical truth value judgments in a way that is as
+independent as possible of potentially conflating properties of the
+pictorial material and that is nonetheless sensitive enough to detect
+local readings even if they are dispreferred. The sensitivity to
+dispreferred readings should be controlled for. On top of this, it
+would be desirable to obtain further information about the relative
+preferences among all putative readings, so as to be able to decide
+between theoretical positions, as outlined in
+Section~\ref{sec:theories-predictions}. % Neither of the previous
+% studies gives us that, either because they simply have not
+% investigated all the relevant comparisons
+% (\citet{GeurtsPouscoulous2009:Embedded-Implic},
+% \citet{CliftonDube2010:Embedded-Implic}), or because they cannot
+% safely derive the required information for danger of conflating
+% preferences for readings with preferences for pictures
+% (\citet{ChemlaSpector2010:Experimental-Ev}).
+
+Finally, we need to control for ``silent prosody.'' A growing number
+of evidence suggests that numerous factors might influence accent
+placement and prosodic phrasing even while reading, amongst them
+default accentuation, constituent length, rhythmic phenomena, and
+individual variation
+\citep[e.g.][]{Augurzky08,Bader98,Fodor98,Fodor02,Kentner12,
   Steinhauer01}. If we adopt the intonational markedness hypothesis
@@
 But if intonation can have this role, it is necessary to control for
-this potential variation due to potential differences in silent accent
-placement. Ideally, therefore, we should present sentences auditorily
-and test the intonational markedness hypothesis explicitly by
-manipulating contrastive stress systematically.
+silent accent placement. Ideally, therefore, we should present
+sentences auditorily and manipulate contrastive stress systematically.
 

### 2013-06-18 text/paper/paper3.tex

@@
 % require special intonation, in particular emphatic stress on the
-% scalar item.\dn{give references}
+% scalar item.
 
@@
 
-\begin{figure}[]
+\begin{figure}[t]
   \centering
@@
 %
-\begin{figure}
-  \centering
+\begin{figure}[t]  \centering
       \fbox{\includegraphics[width=5cm]{../pictures/paper/ae_01_1.pdf}}
@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
 	\centering
@@
           (\ref{bsp:target-related-LC}) can be judged first.}
-	\label{fig:exec}
+	\label{fig:exlc}
 \end{figure}
@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
 	\centering
 	\subfloat[][\as-sentences]{
-          \begin{tikzpicture}[scale=0.8]
+          \begin{tikzpicture}[scale=0.75]
   \begin{axis}[
@@
 	\subfloat[][\es-sentences]{
-\begin{tikzpicture}[scale=0.8]
+\begin{tikzpicture}[scale=0.75]
   \begin{axis}[
@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
 	\centering
 	\subfloat[][\as-sentences]{ 
-\begin{tikzpicture}[scale=0.8]
+\begin{tikzpicture}[scale=0.75]
   \begin{axis}[
@@
 	\subfloat[][\es-sentences]{
-          \begin{tikzpicture}[scale=0.8]
+          \begin{tikzpicture}[scale=0.75]
   \begin{axis}[
@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
 	\centering
 	\subfloat[][F0 values]{ 
-\begin{tikzpicture}[scale=0.8]
+\begin{tikzpicture}[scale=0.75]
   \begin{axis}[
@@
 	}
-	\subfloat[][duration]{
-\begin{tikzpicture}[scale=0.8]
+	\subfloat[][Duration]{
+\begin{tikzpicture}[scale=0.75]
   \begin{axis}[
@@
 
-Statistical analyses for F0 on Region 5 reveal that all prosodic realizations
-(neutral vs. (\emph{early boundary} vs. (\emph{late boundary}) differ significantly
-from each other (effect of \acro{Prosody}: \emph{F}=129.3; \emph{p}<.001; all
-single comparisons \emph{p}<.001). On Region 7, F0 analyses again show a main
-effect of \acro{Prosody}: \emph{F}=132.5; \emph{p}<.001. However, the comparison
-between neutral prosody and a \emph{late boundary} did not reach significance 
-(\emph{p}>.2). Finally, durational analyses on reveal that all prosodic realizations
-(neutral vs. (\emph{early boundary} vs. (\emph{late boundary}) differ significantly
-from each other (Region 5: effect of \acro{Prosody}: \emph{F}=819.5; \emph{p}<.001; all
-single comparisons \emph{p}<.001; Region 7: effect of \acro{Prosody}: \emph{F}=1920.3; 
-\emph{p}<.001; all single comparisons \emph{p}<.001.)
-
-A list of the statistical results of each sentential region is provided in 
-Appendix~\ref{sec:audit-sent-mater} (F0 values: Table~\ref{tab:table-D};
-durational values: Table~\ref{tab:table-C})
-
-%\dn{Petras Kommentar: Vielleicht
-%  sollten wir hier jeweils 1 Figure für akzentuiert vs. nicht und
-%  boundary vs. nicht reinbringen. Fabian meint zurecht, dass man nicht
-%  einfach die Ergebnisse nur in den Appendix packen kann. Es wären
-%  dann halt 4 Figures, da wir ja F0 und duration ansehen, und wir
-%  würden nur die experimentell interessanten veranschaulichen und die
-%  Statistik dann im Appendix lassen - was meint Ihr? --- Micha sagt ``Ja!''}
+Statistical analyses for F0 on Region 5 reveal that all prosodic
+realizations (\emph{neutral} vs. (\emph{early boundary}
+vs. (\emph{late boundary}) differ significantly from each other
+(effect of \acro{Prosody}: \emph{F}=129.3; \emph{p}<.001; all single
+comparisons \emph{p}<.001). On Region 7, F0 analyses again show a main
+effect of \acro{Prosody}: \emph{F}=132.5; \emph{p}<.001. However, the
+comparison between neutral prosody and a \emph{late boundary} did not
+reach significance (\emph{p}>.2). Finally, durational analyses on
+reveal that all prosodic realizations (neutral vs. (\emph{early
+  boundary} vs. (\emph{late boundary}) differ significantly from each
+other (Region 5: effect of \acro{Prosody}: \emph{F}=819.5;
+\emph{p}<.001; all single comparisons \emph{p}<.001; Region 7: effect
+of \acro{Prosody}: \emph{F}=1920.3; \emph{p}<.001; all single
+comparisons \emph{p}<.001.)
+
+A list of the statistical results of each sentential region is
+provided in Appendix~\ref{sec:audit-sent-mater} (F0 values:
+Table~\ref{tab:table-D}; durational values: Table~\ref{tab:table-C})
 
@@
 The visual sequences accompanying each sentence consisted of pictures
-comparable to those illustrated in Figure \ref{fig:InitialPicture}. In
-each picture, four alternative sub-scenarios were presented, in which
-an icon was surrounded by six geometrical shapes. Depending on the
+like in Figures~\ref{fig:InitialPicture}--\ref{fig:exlc}. In each
+picture, four alternative sub-scenarios were presented, in which an
+icon was surrounded by six geometrical shapes. Depending on the
 sentence material, shapes and icons differed across sentence types and
@@
 whereas various icons and surrounding elements were used in each
-sequence of the preference-related control structures. As described in
-section xx, grey colour initially covered the links between icons and
-shapes. As the connections were to be uncovered step by step,
-different pictures were designed corresponding to different stages in
-the uncovering process. Note that the single conditions impose
-distinct requirements on sequences. For instance, inherent entailment
-relations between \as-sentences and \es-sentences lead to different
-critical positions at which participants can make their judgments. We
-will therefore describe the sequences for each condition separately.
+sequence of the preference-related control structures. Grey colour
+initially covered the links between icons and shapes. As the
+connections were to be uncovered step by step, different pictures were
+designed corresponding to different stages in the uncovering
+process. Inherent entailment relations between \as-sentences and
+\es-sentences lead to different critical positions at which
+participants can make their judgments. We will therefore describe the
+sequences for each condition separately.
 
@@
 controls) consisted of a set of five pictures with the following
-critical positions. The critical positions as illustrated in Figure
-\ref{fig:exseqES} are associated with the second picture (global
-reading), the third picture (literal reading), as well as with the
-final picture (local reading).
+critical positions. The critical positions (Figure \ref{fig:exseqES})
+are associated with the second picture (global reading), the third
+picture (literal reading), as well as with the final picture (local
+reading).
 
@@
 (preferred) late-closure reading was presented preceding the critical
-position for the early-closure reading ({\it LC sequence}), and
-second, a sequence in which the readings were presented in reversed
-order ({\it EC sequence}. In the LC sequences, seven pictures were
-presented, with the LC reading given at the third picture, and the EC
-reading at the sixth picture. EC sequences consisted of five pictures,
-in which the critical positions were realized at the third picture (EC
-reading) and at the fifth picture (LC reading).
+position for the early-closure reading (\LC-sequence), and second, a
+sequence in which the readings were presented in reversed order
+(\EC-sequence). In the \LC-sequences, seven pictures were presented,
+with the \LC-reading given at the third picture, and the \EC- reading
+at the sixth picture. \EC-sequences consisted of five pictures, in
+which the critical positions were realized at the third picture
+(\EC-reading) and at the fifth picture (\LC-reading).
 
@@
 correct answers).
-
-\begin{itemize}
-\item possibly mention ages, backgrounds and sexes?
-\end{itemize}
 
@@
 %
-\begin{figure}[]
+\begin{figure}[t]
 \centering
@@
 % \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
-\begin{tikzpicture}[scale=0.8]
+\begin{tikzpicture}[scale=0.75]
 
@@
 % \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
-\begin{tikzpicture}[scale=0.8]
+\begin{tikzpicture}[scale=0.75]
 
@@
 % \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
-\begin{tikzpicture}[scale=0.8]
+\begin{tikzpicture}[scale=0.75]
 
@@
 % \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
-\begin{tikzpicture}[scale=0.8]
+\begin{tikzpicture}[scale=0.75]
 
@@
 %
-\begin{figure}[]
+\begin{figure}[t]
 \centering
 \subfloat[][\as-condition]{
-\begin{tikzpicture}[scale=0.8]
+\begin{tikzpicture}[scale=0.75]
 
@@
 \subfloat[][\es-condition]{
-\begin{tikzpicture}[scale=0.8]
+\begin{tikzpicture}[scale=0.75]
 
@@
 Participants mostly gave judgments indicating literal or local
-readings. Judgments compatible with a global reading were seldomly
-observed. In the \as-conditions (see Figure~\ref{fig:JudgementPercentagesAE}),
-judgments were consistent with literal readings in 65.0\% of the
-trials with neutral prosody and in 67.5\% of the trials with accented
-prosody.\dn{IMPORTANT: Figure contains different numbers (even if
-  rounded)! Fabian, did you exclude the 3 bad performers when you
-  obtained this data?} Judgments indicating local readings were given 
-  in 22.0\% of both the neutral and accented trials. Global readings 
-occurred in 1.6\% of the neutral and 0.8\% of the accented trials
-(corresponding to a total of 3 answers across all trials).  
-In the \es-conditions (see Figure~\ref{fig:JudgementPercentagesGE}) 
-judgments consistent with literal readings were given in 47.2\% and 
-44.7\% of the trials with neutral and accented prosody, respectively. 
-Judgments indicating local readings were given in 22.8\% of
-the neutral and 27.6\% of the accented trials. Global readings were
-observed in 0.8\% of the trials in both the neutral and the accented
-condition. 
-As for the number of erroneous decisions, a discrepancy between 
-\as-conditions and \es-conditions was observed: In the former, 
-participants made hardly any errors, while in the latter, the amount 
-of errors was considerably larger.
+readings. Judgments compatible with a global reading were seldom
+observed. In the \as-conditions (see
+Figure~\ref{fig:JudgementPercentagesAE}), judgments were consistent
+with literal readings in 65.0\% of the trials with neutral prosody and
+in 67.5\% of the trials with accented prosody. Judgments indicating
+local readings were given in 22.0\% of both the neutral and accented
+trials. Global readings occurred in 1.6\% of the neutral and 0.8\% of
+the accented trials (corresponding to a total of 3 answers across all
+trials).  In the \es-conditions (see
+Figure~\ref{fig:JudgementPercentagesGE}) judgments consistent with
+literal readings were given in 47.2\% and 44.7\% of the trials with
+neutral and accented prosody, respectively.  Judgments indicating
+local readings were given in 22.8\% of the neutral and 27.6\% of the
+accented trials. Global readings were observed in 0.8\% of the trials
+in both the neutral and the accented condition.  As for the number of
+erroneous decisions, a discrepancy between \as-conditions and
+\es-conditions was observed: In the former, participants made hardly
+any errors, while in the latter, the amount of errors was considerably
+larger.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
@@
 
-\begin{figure}[]
+\begin{figure}[t]
 \centering
@@
   \subfloat[][\LC-condition]{
-        \begin{tikzpicture}[scale=0.8]
+        \begin{tikzpicture}[scale=0.75]
 
@@
   \subfloat[][\ec-condition]{
-    \begin{tikzpicture}[scale=0.8]
+    \begin{tikzpicture}[scale=0.75]
 
@@
 unavailable or simply severely dispreferred. Crucially, our data
-attests local readings independent of prosody, albeit that local
+attests local readings independently of prosody, albeit that local
 readings are not preferred to literal readings and given, as it seems,
@@
 
-These findings are hard to explain both by traditionalism and
-grammaticalism, as no version of either would predict the pattern in
+These findings are hard to for traditionalism and grammaticalism
+alike, as no version of either would predict the pattern in
 (\ref{bsp:observed-preferences}).  Traditionalism, if left on its own,
@@
 predict an increase in local readings in the accented conditions, and
-maybe even an absence of local readings in the unaccented
+presumably an absence of local readings in the unaccented
 conditions. Neither was observed. Local readings were observed in the
@@
 obvious candidates below), but that does not as such save
-traditionalism. Traditionalism alone, as well as traditionalism
-supplemented with the intonational markedness hypothesis, cannot
-explain (\ref{bsp:observed-preferences}), but needs an additional
-explanation of local readings for \emph{both} \as- \emph{and}
-\es-sentences.
+traditionalism. Traditionalism, even if supplemented with the
+intonational markedness hypothesis, cannot explain
+(\ref{bsp:observed-preferences}), but needs an additional explanation
+of local readings for \emph{both} \as- \emph{and} \es-sentences.
 
@@
 pattern in (\ref{bsp:observed-preferences}) for both \as- and
-\es-sentences at the same time. (Try, if you please!)
+\es-sentences at the same time.
 
@@
 \citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}. We
-argue below that neither explanation plausibly holds for the
+argue below that neither explanation plausibly applies in the
 incremental verification task. On the other hand, what grammaticalism
@@
 
-Interestingly, an alternative theory of scalar implicature explains
-the observed preference ordering (\ref{bsp:observed-preferences}) in a
-completely straightforward manner.  \emph{Conventionalism} (also
-sometimes called \emph{lexicalism}) proposes that if the
-upper-bounding inference from \emph{some} to \emph{some but not all}
-occurs frequently, it would be inefficient to execute over and over
-again the Gricean reasoning that traditionalists propose
+It is worth noting that an alternative theory of scalar implicature
+explains the observed preference ordering
+(\ref{bsp:observed-preferences}) in a completely straightforward
+manner.  \emph{Conventionalism} (also sometimes called
+\emph{lexicalism}) proposes that if the upper-bounding inference from
+\emph{some} to \emph{some but not all} occurs frequently, it would be
+inefficient to execute over and over again the Gricean reasoning that
+traditionalists propose
 \citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}. Conventionalism
@@
 generally able of exiting at the earliest possible location, as
-evidence by ceiling success rates in our positional controls. A second
+evidenced by ceiling success rates in our positional controls. A second
 argument that casts doubt on a contrast-based explanation is that our
@@
 
-Finally, we should address the obvious worry that maybe our results
+Also, we should address the obvious worry that maybe our results
 could have been the product of typicality after all. Remember that
@@
 interpretations with certain patterns of intonation are frequently
-made in the theoretical literature, but only backed up by
+made in the theoretical literature, but often only backed up by
 introspection and not made precise in their commitment to the exact
@@
 \citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi},
-we employed a novel experimental design, the incremental verification
-task, in which subjects were presented with partially covered pictures
-and asked to uncover the picture sequentially until they felt able to
-give a categorical truth-value judgements. Sentence material was
-presented auditorily and contrastive stress on embedded \emph{some}
-was manipulated so as to test the intonational markedness hypothesis,
+we employed an incremental verification task \citep{Conroy2008}, in
+which subjects were presented with partially covered pictures and
+asked to uncover the picture sequentially until they felt able to give
+a categorical truth-value judgements. Sentence material was presented
+auditorily and contrastive stress on embedded \emph{some} was
+manipulated so as to test the intonational markedness hypothesis,
 which is often used to supplement traditionalism. Both traditionalism
@@
 %Table~\ref{tab:table-D}. Again, the most reliable differences occur at
-%the boundary regions.\dn{provide caption for table D}
+%the boundary regions.
 

### 2013-06-20 text/micha_stat_analysis/notes.tex

\documentclass[fleqn,reqno,10pt]{article}

\usepackage{myarticlestyledefault}

\usepackage{subfig}

\title{K2 Analysis}
\author{Michael Franke}
\date{}

\newcommand{\lit}{\acro{lit}}
\newcommand{\glb}{\acro{glb}}
\newcommand{\loc}{\acro{loc}}

\newcommand{\as}{\acro{as}}
\renewcommand{\es}{\acro{es}}
\renewcommand{\AE}{\as}
\newcommand{\GE}{\es}
\newcommand{\ea}{\acro{ea}}

\newcommand{\lc}{\acro{lc}}
\newcommand{\ec}{\acro{ec}}
\newcommand{\LC}{\lc}
\newcommand{\EC}{\ec}

\begin{document}
\maketitle

\section{Controls}
\label{sec:controls}

\section{Target Conditions}
\label{sec:target-conditions}

Each participant saw each critical sentence type three times with
neutral and three times with constrastive stress intonation on the
scalar item. We coded judgements as either \emph{literal},
\emph{local}, \emph{global} or \emph{false}. Contingency tables of the
observed frequencies are in Table~XYZ.

\begin{table}[h]

\subfloat[][\as neutral]{\begin{tabular}{lcccc}
    & \emph{literal} & \emph{local} & \emph{global} & \emph{false} \\
    \midrule
    Pos 1 & 29 &  7 & 0 & 1 \\
    Pos 2 & 26 & 10 & 0 & 1 \\
    Pos 3 & 25 &  9 & 1 & 2 \\ \addlinespace[0.15cm]
    Total & 80 & 26 & 1 & 4
\end{tabular}}
%
\hspace{0.2cm}
%
\subfloat[][\es neutral]{\begin{tabular}{lcccc}
    & \emph{literal} & \emph{local} & \emph{global} & \emph{false} \\
    \midrule
    Pos 1 & 16 &  7 & 0 & 14 \\
    Pos 2 & 21 & 13 & 0 &  3 \\
    Pos 3 & 16 & 13 & 0 &  8 \\ \addlinespace[0.15cm]
    Total & 51 & 33 & 0 & 25
\end{tabular}}

\subfloat[][\as accented]{\begin{tabular}{lcccc}
    & \emph{literal} & \emph{local} & \emph{global} & \emph{false} \\
    \midrule
    Pos 1 & 28 &  7 & 1 & 1 \\
    Pos 2 & 25 &  8 & 1 & 3 \\
    Pos 3 & 24 & 10 & 0 & 3 \\ \addlinespace[0.15cm]
    Total & 77 & 25 & 2 & 7
\end{tabular}}
%
\hspace{0.2cm}
%
\subfloat[][\es accented]{\begin{tabular}{lcccc}
    & \emph{literal} & \emph{local} & \emph{global} & \emph{false} \\
    \midrule
    Pos 1 & 16 &  7 & 0 & 14 \\
    Pos 2 & 21 & 13 & 0 &  3 \\
    Pos 3 & 16 & 13 & 0 &  8 \\ \addlinespace[0.15cm]
    Total & 51 & 33 & 0 & 25
\end{tabular}}

\caption{Contingency table of raw judgements.}
\label{tab:CC-ContingencyTable}
\end{table}

\section{Preference-Related Controls}
\label{sec:pref-relat-contr}

\printbibliography[heading=bibintoc]

\end{document}

### 2013-06-22 text/micha_stat_analysis/notes.tex
stat notes sec com

@@
 \usepackage{subfig}
+\usepackage{todonotes}
 
@@
 \emph{local}, \emph{global} or \emph{false}. Contingency tables of the
-observed frequencies are in Table~XYZ.
-
+observed frequencies are in Table~\ref{tab:CC-ContingencyTable}.
+%
 \begin{table}[h]
@@
     Pos 3 & 16 & 13 & 0 &  8 \\ \addlinespace[0.15cm]
-    Total & 51 & 33 & 0 & 25
+    Total & 53 & 33 & 0 & 25
 \end{tabular}}
@@
     \midrule
-    Pos 1 & 16 &  7 & 0 & 14 \\
-    Pos 2 & 21 & 13 & 0 &  3 \\
-    Pos 3 & 16 & 13 & 0 &  8 \\ \addlinespace[0.15cm]
-    Total & 51 & 33 & 0 & 25
+    Pos 1 & 13 &  6 & 0 & 18 \\
+    Pos 2 & 24 &  7 & 1 &  5\\
+    Pos 3 & 19 & 13 & 0 &  5 \\ \addlinespace[0.15cm]
+    Total & 56 & 26 & 1 & 28
 \end{tabular}}
@@
 \end{table}
+%
+Two things strike the eye. Firstly, there are hardly any \emph{global}
+responses. For subsequent analysis in terms of log-linear models we
+must therefore lump together \emph{global} and \emph{false} responses
+into one more general category \emph{other}. Secondly, the number of
+\emph{false} responses drops remarkably in the \es-conditions. The
+following analysis should probe into this potential position effect.
+
+If we only look at the very first judgement that subjects gave to a
+target condition, we obtain the following table:
+\begin{center}
+\begin{tabular}{lcccc}
+    & \emph{literal} & \emph{local} & \emph{global} & \emph{false} \\
+    \midrule
+    accented & 15 &  5 & 0 &  9 \\
+    neutral  &  6 &  0 & 0 &  2 \\ \addlinespace[0.15cm]
+    Total    & 21 &  5 & 0 & 11
+\end{tabular}
+\end{center}
+Notably, nobody gave a \emph{local} answer on the first encounter of a
+target condition with neutral accentuation. Still, Pearson's $\chi^2$
+test does not reject the null hypothesis of an equal distribution
+of readings ($\chi^2 = 2.0546$, $p \approx 0.4318$).
+\todo[inline]{Is this test applicable at all? Don't we have too little
+data points? How else could a dependence be tested in this case?}
+
+To test which factors are relevant to explain the data distribution in
+Table~\ref{tab:CC-ContingencyTable}, we compute log-linear models
+\citep{KnokeBurke1980:Log-Linear-Mode}. The relevant factors are
+\textsc{Position}, \textsc{Response}, \textsc{Condition}, and
+\textsc{Accent}. To ensure applicability, we lump levels \emph{global}
+and \emph{false} of factor \textsc{Response} into a single level
+\emph{other}. The best predictor of the data takes all factors
+\textsc{Position}, \textsc{Response} and \textsc{Condition} and all
+their interactions into account ($\chi^2 = 7.493$, $df=18$, $p =
+0.985$, $AIC = 43.493$ (compared to $AIC=72$ of the saturated
+model)). Crucially, factor \textsc{Accent} is spurious.
+
+To test whether the effect of \textsc{Condition} could be due to the
+relatively high number of \emph{false} responses in the
+\es-conditions, we regrouped the factor \textsc{Response} once more to
+distinguish only \emph{local} responses from \emph{other}
+responses. Doing so allows us to address the question whether the
+amount of \emph{local} responses differed across conditions and
+accentuation types. But this does not seem to be the case. The
+smallest model that predicts the data well in this case contains
+factors \textsc{Response} and \textsc{Position} and their two-way
+interaction.
 

### 2013-06-22 text/micha_stat_analysis/notes.tex
stat notes sec com

@@
 target condition with neutral accentuation. Still, Pearson's $\chi^2$
-test does not reject the null hypothesis of an equal distribution
-of readings ($\chi^2 = 2.0546$, $p \approx 0.4318$).
-\todo[inline]{Is this test applicable at all? Don't we have too little
-data points? How else could a dependence be tested in this case?}
+test does not reject the null hypothesis of an equal distribution of
+readings ($\chi^2 = 2.0546$, $p \approx 0.4318$).  \todo[inline]{Is
+  this test applicable at all? Don't we have too little data points?
+  How else could a dependence be tested in this case?}
 
@@
 factors \textsc{Response} and \textsc{Position} and their two-way
-interaction.
+interaction ($\chi^2 = 4.71$, $df=18$, $p = 0.999$, $AIC = 16.711$
+(compared to $AIC=48$ of the saturated model)). This suggests that a
+shift in the distribution of \emph{local} responses can be
+satisfactorily explained as a position effect across conditions: later
+trials yielded less \emph{other} responses.
+
+To test, then, whether this prediction is the result of an decrease of
+\emph{false} responses in later trials or an actual shift in the
+distribution between \emph{literal} and \emph{local} distribution, we
+also computed the best log-linear predictor for the subset of our data
+including only \emph{literal} and \emph{local} responses. Doing so,
+the best predictor indeed drops factor \textsc{Position} and contains
+only factors \textsc{Response} and \textsc{Condition} and their
+two-way interaction ($\chi^2 = 12.497$, $df=20$, $p = 0.898$, $AIC =
+20.497$ (compared to $AIC=48$ of the saturated model)). This suggests
+that the factor \textsc{Position} is not relevant for explaining the
+distribution of \emph{literal} and \emph{local} readings. Its effects
+noted previously are most likely due to the decrease of \emph{false}
+responses in later trials of the \es-conditions.
 

### 2013-06-22 text/micha_stat_analysis/notes.tex
stat notes sec com

--- 2013-06-22 text/micha_stat_analysis/notes.tex
@@
 \usepackage{todonotes}
-
-\title{K2 Analysis}
-\author{Michael Franke}
-\date{}
 
@@
 
+\title{K2 Analysis}
+\author{}
+\date{}
+
 \begin{document}
 \maketitle
-
-\section{Controls}
-\label{sec:controls}
 
@@
 
-Each participant saw each critical sentence type three times with
-neutral and three times with constrastive stress intonation on the
-scalar item. We coded judgements as either \emph{literal},
-\emph{local}, \emph{global} or \emph{false}. Contingency tables of the
-observed frequencies are in Table~\ref{tab:CC-ContingencyTable}.
+There were two critical sentence-sequence types, \as and \es, which
+are the levels in factor \textsc{Condition}. Factor \textsc{Accent}
+codes whether a sentence was neutral or accented. Every participant
+saw each critical sentence type six times, of which three times had
+neutral, three times constrastive stress intonation on the scalar
+item. We coded into factor \textsc{Position} whether a particular
+encounter of a critical sentence and intonation pattern was the first,
+second or third time for a participant. Finally, we coded judgements
+as either \emph{literal}, \emph{local}, \emph{global} or \emph{false}
+for form factor \emph{Response}. Given these factors, contingency
+tables of the observed frequencies are in
+Table~\ref{tab:CC-ContingencyTable}.
 %
@@
 
-\caption{Contingency table of raw judgements.}
+\caption{Contingency table of raw judgements for target condition.}
 \label{tab:CC-ContingencyTable}
 \end{table}
-%
+
 Two things strike the eye. Firstly, there are hardly any \emph{global}
@@
 must therefore lump together \emph{global} and \emph{false} responses
-into one more general category \emph{other}. Secondly, the number of
-\emph{false} responses drops remarkably in the \es-conditions. The
-following analysis should probe into this potential position effect.
+into one more general category level \emph{other}. Secondly, the
+number of \emph{false} responses drops remarkably in the
+\es-conditions. The following analysis should probe into this
+potential position effect.
 
-If we only look at the very first judgement that subjects gave to a
-target condition, we obtain the following table:
+To test which factors are relevant to explain the data distribution in
+Table~\ref{tab:CC-ContingencyTable}, we compute log-linear models
+\citep{KnokeBurke1980:Log-Linear-Mode}. The relevant factors are
+\textsc{Position}, \textsc{Response}, \textsc{Condition}, and
+\textsc{Accent}. To ensure applicability, we lump levels \emph{global}
+and \emph{false} of factor \textsc{Response} into a single level
+\emph{other}. The best predictor of the data takes all factors
+\textsc{Position}, \textsc{Response} and \textsc{Condition} and all
+their interactions, including the three-way interaction, into account
+($\chi^2 = 7.493$, $df=18$, $p = 0.985$, $AIC = 43.493$ (compared to
+$AIC=72$ of the saturated model)). Crucially, factor \textsc{Accent}
+is spurious.
+
+% To test whether the effect of \textsc{Condition} could be due to the
+% relatively high number of \emph{false} responses in the
+% \es-conditions, we regrouped the factor \textsc{Response} once more
+% to distinguish only \emph{local} responses from \emph{other}
+% responses. Doing so allows us to address the question whether the
+% amount of \emph{local} responses differed across conditions and
+% accentuation types. But this does not seem to be the case. The model
+% that predicts the data best in this case contains factors
+% \textsc{Response} and \textsc{Position} and their two-way
+% interaction ($\chi^2 = 4.71$, $df=18$, $p = 0.999$, $AIC = 16.711$
+% (compared to $AIC=48$ of the saturated model)). This suggests that a
+% shift in the distribution of \emph{local} responses can be
+% satisfactorily explained as a position effect that is constant
+% across conditions: later trials yielded less \emph{other} responses.
+
+To test, then, whether \textsc{Position} affects the distribution of
+\emph{literal} and \emph{local} readings, we also computed the best
+log-linear predictor for the subset of our data including only
+\emph{literal} and \emph{local} responses. Doing so, the best
+predictor indeed drops factor \textsc{Position} and contains only
+factors \textsc{Response} and \textsc{Condition} and their two-way
+interaction ($\chi^2 = 12.497$, $df=20$, $p = 0.898$, $AIC = 20.497$
+(compared to $AIC=48$ of the saturated model)). This suggests that the
+factor \textsc{Position} is not relevant for explaining the
+distribution of \emph{literal} and \emph{local} readings. Its effects
+noted previously are most likely due to the decrease of \emph{false}
+responses in later trials of the \es-conditions.
+
+\section{Preference-Related Controls}
+\label{sec:pref-relat-contr}
+
+Some subjects saw three others four trials of preference-related
+controls. The relevant factors in this case are: \textsc{Condition}
+with levels \emph{lc} and \emph{ec} coding which reading could be
+judged first in a sequence; \textsc{Accent} with levels \emph{ntr},
+\emph{lc} and \emph{ec} coding which reading was cued by intonation;
+\textsc{Position} with levels 1 to 4; and \textsc{Response} with
+levels \emph{lc}, \emph{ec} and \emph{false}. The observed data under
+this classification is given in Table~\ref{tab:TF-ContingencyTable}.
+%
+\begin{table}[h]
+
+ \centering
+
+\subfloat[][\lc neutral]{\begin{tabular}{lccc}
+    & \emph{lc} & \emph{ec} & \emph{false} \\
+    \midrule
+    Pos 1 & 30 &  6 & 1  \\
+    Pos 2 & 24 &  9 & 4  \\
+    Pos 3 & 25 &  8 & 3  \\
+    Pos 4 & 11 & 10 & 1  \\ \addlinespace[0.15cm]
+    Total & 90 & 33 & 9 
+\end{tabular}}
+%
+\hspace{0.4cm}
+%
+\subfloat[][\ec neutral]{\begin{tabular}{lccc}
+    & \emph{lc} & \emph{ec} & \emph{false} \\
+    \midrule
+    Pos 1 &  28 &   4 &   5 \\ 
+    Pos 2 &  26 &  10 &   1 \\ 
+    Pos 3 &  19 &  11 &   6 \\ 
+    Pos 4 &  11 &   9 &   2 \\ \addlinespace[0.15cm]
+    Total &  65 &  34 &  14 
+\end{tabular}}
+
+\subfloat[][\lc with \lc cue]{\begin{tabular}{lccc}
+    & \emph{lc} & \emph{ec} & \emph{false} \\
+    \midrule
+    Pos 1 &  26 &   6 &   5 \\ 
+    Pos 2 &  30 &   4 &   3 \\ 
+    Pos 3 &  30 &   5 &   2 \\ 
+    Pos 4 &  14 &   1 &   1 \\ 
+    \addlinespace[0.15cm]
+    Total & 100 & 16 & 11 
+\end{tabular}}
+%
+\hspace{0.4cm}
+%
+\subfloat[][\ec with \lc cue]{\begin{tabular}{lccc}
+    & \emph{lc} & \emph{ec} & \emph{false} \\
+    \midrule
+    Pos 1 &  24 &   6 &   7 \\ 
+    Pos 2 &  30 &   3 &   4 \\ 
+    Pos 3 &  30 &   5 &   2 \\ 
+    Pos 4 &  13 &   2 &   1 \\ 
+    \addlinespace[0.15cm]
+    Total &  97 &  16 &  14 
+\end{tabular}}
+
+\subfloat[][\lc with \ec cue]{\begin{tabular}{lccc}
+    & \emph{lc} & \emph{ec} & \emph{false} \\
+    \midrule
+    Pos 1 &  15 &  15 &   7 \\ 
+    Pos 2 &  20 &  10 &   7 \\ 
+    Pos 3 &  24 &   7 &   5 \\ 
+    Pos 4 &   8 &   8 &   6 \\
+    \addlinespace[0.15cm]
+    Total &  67 & 40 &  25 
+\end{tabular}}
+%
+\hspace{0.4cm}
+%
+\subfloat[][\ec with \ec cue]{\begin{tabular}{lccc}
+    & \emph{lc} & \emph{ec} & \emph{false} \\
+    \midrule
+    Pos 1 &  21 &  12 &   4 \\ 
+    Pos 2 &  18 &  12 &   7 \\ 
+    Pos 3 &  22 &  12 &   2 \\ 
+    Pos 4 &  13 &   7 &   2 \\ 
+    \addlinespace[0.15cm]
+    Total &  74 &  43 &  15 
+\end{tabular}}
+
+\caption{Contingency table of raw judgements for target-related fillers.}
+\label{tab:TF-ContingencyTable}
+\end{table}
+
+The best hierarchical log-linear model (by $AIC$) includes factors
+\textsc{Response}, \textsc{Accent} and \textsc{Position}, as well as
+the two-way interaction between \textsc{Response} and \textsc{Accent}
+($\chi^2 = 48.802$, $df=60$, $p=0.85$, $AIC=72.802$ (compared to
+$AIC=144$ of the standard model)). Crucially, the observed response
+pattern does not differ significantly across conditions (i.e., which
+reading can be judged first), but does depend on intonational cues.
+
+The factor \textsc{Position} cannot be dropped without dramatically
+reducing explanatory power of the model. However, if we abstract over
+intonation and conditions, we get the following table:
+\begin{center}
+\centering
+\begin{tabular}{rrrr}
+  & \emph{lc} & \emph{ec} & \emph{false} \\ 
+  \midrule
+  Pos 1 & 144 & 49 & 29 \\ 
+  Pos 2 & 148 & 48 & 26 \\ 
+  Pos 3 & 150 & 48 & 20 \\ 
+  Pos 4 &  70 & 37 & 13 \\ 
+\end{tabular}
+\end{center}
+There is no interaction between \textsc{Position} and
+\textsc{Response} ($\chi^2$, $df=6$, $p=0.3798$), suggesting that
+\textsc{Position} does not affect the overal distribution of readings.
+
+\newpage
+
+\section{Loose Ends}
+\label{sec:loose-ends}
+
+If we only look at the judgement that subjects gave to the very first
+target condition that they saw (be it \as or \es), we obtain the
+following table:
 \begin{center}
@@
 target condition with neutral accentuation. Still, Pearson's $\chi^2$
-test does not reject the null hypothesis of an equal distribution
-of readings ($\chi^2 = 2.0546$, $p \approx 0.4318$).
-\todo[inline]{Is this test applicable at all? Don't we have too little
-data points? How else could a dependence be tested in this case?}
-
-To test which factors are relevant to explain the data distribution in
-Table~\ref{tab:CC-ContingencyTable}, we compute log-linear models
-\citep{KnokeBurke1980:Log-Linear-Mode}. The relevant factors are
-\textsc{Position}, \textsc{Response}, \textsc{Condition}, and
-\textsc{Accent}. To ensure applicability, we lump levels \emph{global}
-and \emph{false} of factor \textsc{Response} into a single level
-\emph{other}. The best predictor of the data takes all factors
-\textsc{Position}, \textsc{Response} and \textsc{Condition} and all
-their interactions into account ($\chi^2 = 7.493$, $df=18$, $p =
-0.985$, $AIC = 43.493$ (compared to $AIC=72$ of the saturated
-model)). Crucially, factor \textsc{Accent} is spurious.
-
-To test whether the effect of \textsc{Condition} could be due to the
-relatively high number of \emph{false} responses in the
-\es-conditions, we regrouped the factor \textsc{Response} once more to
-distinguish only \emph{local} responses from \emph{other}
-responses. Doing so allows us to address the question whether the
-amount of \emph{local} responses differed across conditions and
-accentuation types. But this does not seem to be the case. The
-smallest model that predicts the data well in this case contains
-factors \textsc{Response} and \textsc{Position} and their two-way
-interaction.
-
-\section{Preference-Related Controls}
-\label{sec:pref-relat-contr}
+test does not reject the null hypothesis of an equal distribution of
+readings ($\chi^2 = 2.0546$, $p \approx 0.4318$).  \todo[inline]{Is
+  this test applicable at all? Don't we have too little data points?
+  How else could a dependence be tested in this case?}
 

### 2013-06-22 text/micha_stat_analysis/notes.tex
stat notes sec com

@@
 
+\todo[inline]{is this convincing enough to dispense with any potential
+doubt about interferences from our screwed up block design?}
+
 \section{Preference-Related Controls}
@@
 The factor \textsc{Position} cannot be dropped without dramatically
-reducing explanatory power of the model. However, if we abstract over
-intonation and conditions, we get the following table:
+reducing explanatory power of the model. However, inspecting the
+coefficients of the above model, we see that the only role of factor
+\textsc{Position} is to account for the relatively fewer data points
+at position four. Moreover, if we abstract over intonation and
+conditions, we get the following table:
 \begin{center}
@@
 \textsc{Position} does not affect the overal distribution of readings.
+
+\todo[inline]{is this convincing to cast away \textsc{Position}
+  effects? do we really need to care in this case? there is no
+  particularly obvious difference across positions that one would need
+  to worry about; also the way conditions were presented in the second
+  block don't really lead to any obvious pattern either; in other
+  words, neither does the faulty design suggest a positional pattern
+  (or at least I can conceive of one), nor does there seem to be one
+  (or at least I don't see one) }
 

### 2013-10-23 text/prob_model/prob_model.tex
prob mod sec com

\documentclass[fleqn,reqno,10pt]{article}

\usepackage{myarticlestyledefault}

\usetikzlibrary{calc}

\title{A Bayesian model for the K2 data}
\author{Michael Franke}
\date{}

\begin{document}
\maketitle

\section{The new data}

We have 40 participants with 86 data points each. We should exclude 2
participants (VPs 2 and 29) due to bad overal performance (more than
40\% errors on controls and target-related fillers). The mean success
rate on positional controls after this exclusion is $.91$. The
observed answer patterns are:

\medskip

\begin{minipage}[t]{0.45\linewidth}
\begin{verbatim}
     lit loc glb false
as-n 100   6   0     8
as-a  95  11   2     6
es-n  65  13   0    36
es-a  73  21   0    20
\end{verbatim}
\end{minipage}
\begin{minipage}[t]{0.45\linewidth}
\begin{verbatim}
   late early false
ee   60    39    33
el  114    12     8
en   93    20    19
le   52    61    19
ll  108    14    12
ln   84    32    16
\end{verbatim}
\end{minipage}

\medskip

There are no longer glaring individual consistencies in answer
patterns. The contingency table for AS-N and ES-N conditions that we
had in the paper before, now looks as follows:
\begin{verbatim}
                           ES-N
AS-N           inconsistent literalist localist
  inconsistent            0          1        2
  literalist              5         26        3
  localist                0          0        1
\end{verbatim}
The same information for AS-A vs.~ES-A:
\begin{verbatim}
                           ES-A
AS-A           inconsistent literalist localist
  inconsistent            1          0        5
  literalist              2         28        1
  localist                0          0        1
\end{verbatim}
Across all critical conditions we only have one consistent localist
(VP 22):
\begin{verbatim}
inconsistent   literalist     localist 
          12           25            1 
\end{verbatim}

\section{A Bayesian model}

\paragraph{Motivation.} Our previous analysis did not really take into
account that choices are made in sequence. We hypothesized that there
might be a bias that VPs exit as early as possible, but we could not
operationalize or even \textbf{quantify} that bias. Of course, this is why we
had the target-related fillers. This way we could at least make sure
whether everybody would exit at the earliest possible position.

Our main argument is about three conceivable readings and how
accessible / salient / strong they are in relation to each other. We
wanted to conclude that our old data suggests that we get an ordering
like so: LIT > LOC > (GLB), where we left it open as to whether GLB
was attested (Sec.~5.6, p.~32, in (23)). This was the main leverage
for saying that neither traditionalism, nor grammaticalism predict are
entirely correct: they both fail to predict that preference
relation. Unfortunately, the conclusion that our data suggests this
preference relation was rather indirect. In any case, there was no
chance to \textbf{quantify} exactly how much more salient LIT was than
LOC, for example.

\paragraph{The model.} Here is a very simple probabilistic model that
quantifies the positional bias and the competing strength of available
readings. Take the AS-conditions as an example. There are three
potential readings. Let's assume that the relative strength between
these is given by a probability vector $\myvec{p}^\text{as-n} =
\tuple{p^\text{as-n}_{\text{lit}},p^\text{as-n}_{\text{loc}},p^\text{as-n}_{\text{glb}}}$. We
assume that when a subject is at a critical position where, say, the
literal reading can be judged true or false, then the subject's
probability of giving the right judgment at that position is
proportional to $p^\text{as-n}_{\text{lit}}$. In other words, if there
were no potential effects of sequentiality and no errors, the vector
$\myvec{p}^\text{as-n}$ would be our prediction of observed
frequencies of in answer patterns. We look at four such three-placed
vectors, one for each target condition.

For each preference-related control condition $k$, we look at a
two-placed vector of the form $p^k =
\tuple{p^{\text{k}}_{\text{late}},
  p^{\text{k}}_{\text{early}}}$. However, since conditions $EX$ and
$LX$ (with $X \in \set{E,L,N}$) differ only with respect to the order
in which readings can be judged, the underlying relative strengths of
readings, and hence the relevant vectors, are taken to be identical.

To add potential effects of sequentiality, we assume that there is a
factor $q \in [0;1]$ that is constant over all conditions with which a
reading that can be judged first is amplified (if $q > .5$) or
de-amplified (if $q <.5$). We may hypothesize that subjects like to
exit as early as possible ($q$ is almost one), but we don't know for
sure, so we let the data decide what we should believe eventually. In
the AS-sequences, LIT can be judged first, then LOC and then GLB. So
we will assume that $p_{\text{lit}}$ is multiplied by $q$, that
$p_{\text{loc}}$ is multiplied by $(1-q)q$ and that $p_{\text{glb}}$
is multiplied by $(1-q)^2$.

Finally, we also allow for the chance of subjects making mistakes. We
should first keep things as simple as possible (no consideration for
spill-overs, late decisions, preferences to unravel completely before
judging etc.). So we assume that there is a fixed error rate $e^k \in
[0;1]$ for each condition $k$ with which subjects make wrong decisions
along the sequence. We allow for different error rates for different
conditions, because it is known, for example, that non-monotonic
quantifiers are harder to process. A decision can be wrong but
incidentally coincide with a reading that is indicative of a relevant
reading. Error rates multiply in proportion to the number of steps in
a sequence: more choice, more chance to be wrong.

Taking this together we calculate, for each critical condition $k$ a
target probability vector $\myvec{t}^k =
\tuple{t^k_{\text{lit}},t^k_{\text{loc}},t^k_{\text{glb}},t^k_{\text{err}}}$
with which we expect an answer to be classified as LIT, LOC, GLB or as
an error. For example, for AS-N, where LIT can be judged before GLB
before LOC, we get:
\begin{align*}
  t^{\text{as-n}}_{\text{lit}} & \propto q \
  p^\text{as-n}_{\text{lit}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{loc}} & \propto (1-q)^2 \
  p^\text{as-n}_{\text{loc}} + e^\text{as-n} \\
  t^{\text{as-n}}_{\text{glb}} & \propto (1-q) \
  p^\text{as-n}_{\text{glb}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{err}} &
  \propto 12 e^\text{as-n}
\end{align*}
Two remarks. The vector $\myvec{t}^k$ should be normalized eventually,
which is why $\propto$ is used instead of $=$. Also, the probability
of error $t^{\text{as-n}}_{\text{err}}$ comes from the observation
that there are 15 positions in total in an AS-sequence at which
subjects can make an erroneous choice, but we have accounted for three
of these already as adding to the count of answers indicative of
relevant readings.

Similarly, we compute a target probability $\myvec{t}^k =
\tuple{t^k_{\text{late}},t^k_{\text{early}},t^k_{\text{err}}}$ for
each preference-related control condition $k$, taking into account
which reading can be judged first and the length of the respective
sequences.

The full probabilistic model is visualized in
Figure~\ref{fig:model_graph}. As indicated there, we assume largely
uninformative priors. Any positional bias $q \in [0;1]$ is assumed to
be equally likely. The error rates for each condition should be small,
so we sample uniformly from interval $[0,.2]$. The biases
$\myvec{p}_k$ are also determined uniformly at random, by sampling from a
Dirichlet distribution with equal weights on all dimensions.

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[node distance = 2.5cm, 
    double distance = 2pt,
    minimum size=1.25cm,
    thick]

    \node[rectangle, draw=black, fill=black!30] (obs)
    {obs$_k$};

    \node[rectangle, draw=black, fill=black!30,
    right of = obs] (n) {$n_k$};

    \node[below of = n, node distance= 1.5cm]
    (anchor) {};

    \node[left of = anchor, node distance= 0.5cm] (k) {$k \in
      \set{\text{as-n, as-e, \dots}}$};

    \node[circle, double, draw=black,
    above of = obs] (t) {$\myvec{t}_k$};

    \node[circle, draw=black, 
    above of = t] (p) {$\myvec{p}_k$};

    \node[circle, draw=black, 
    right of = p] (e) {$e_k$};

    \node[circle, draw=black, 
    left of = p] (q) {$q$};

    \draw[->] (t)--(obs);

    \draw[->] (n)--(obs);

    \draw[->] (q)--(t);

    \draw[->] (p)--(t);

    \draw[->] (e)--(t);

    \begin{pgfonlayer}{background}
       \node [rounded corners,
       very thick,draw=black!40,fit={($(obs.south)+(0,-30pt)$) 
                                 ($(n.east)+(+5pt,0)$) 
                                 ($(e.north)+(0,+5pt)$) 
                                 ($(p.west)+(-5pt,0)$)}] {};
    \end{pgfonlayer}

    \begin{scope}[xshift = 7.5cm, node distance = 1cm]

      \node[] (obsd) {$\text{obs}_k \sim \text{Multinomial}(\myvec{t}_k,n_k)$};

      \node[above of = obsd] (td) {$\myvec{t}_k = \text{as described
          in text}$};

      \node[above of = td] (pd) {$\myvec{p}_k =
        \text{Dirichlet}(\tuple{\nicefrac{1}{k}, \nicefrac{1}{k}, \dots})$};

      \node[above of = pd] (ed) {$e_k \sim \mathcal{U}(0,.2)$};

      \node[above of = ed] (qd) {$q \sim \mathcal{U}(0,1)$};

    \end{scope}

  \end{tikzpicture}
  \caption{Probabilistic graphical model}
  \label{fig:model_graph}
\end{figure}

\section{Analysis}

\printbibliography[heading=bibintoc]

\end{document}

### 2013-10-23 text/prob_model/prob_model.tex
prob mod 1st shot

@@
 \title{A Bayesian model for the K2 data}
-\author{Michael Franke}
+\author{}
 \date{}
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{pics/Posterior_TF.pdf}
+  \caption{Posterior over weights for target readings in
+    target-related control conditions.}
+  \label{fig:Posterior_TF}
+\end{figure}
+
+Using MCMC sampling, we obtain estimates for the posterior of the
+latent parameters given the data. We are most interested in the level
+of credence we should place on the weights of target readings in
+critical conditions. But to check whether the model yields sensible
+results we first look at the preference-related control
+conditions.
+
+Estimates for the posteriors over weights for target-related controls
+are plotted in Figure~\ref{fig:Posterior_TF}. The results are exactly
+as we would expect them to be. Given our data, we should believe that
+the late-closure reading is more prominent. But the level of
+prominence varies with accentuation. Under prosody that we
+hypothesized would favor the late-closure reading, the contrast is
+most pronounced. Contrarily, accentuation that we hypothesized favors
+the early-closure reading we are no longer justified in believing that
+the late-closure reading is certainly preferred (witness the clearly
+overlapping 95\% confidence regions).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{pics/Posterior_T.pdf}
+  \caption{Posteriors over weights for target readings in critical
+    conditions. Colored lines below the actual plots indicate 95\%
+    confidence intervals.}
+  \label{fig:Posterior_T}
+\end{figure}
+
+Turning to the critical conditions, estimates of posteriors over
+weights given our data are given in Figure~\ref{fig:Posterior_T}. We
+only have marginal reasons to believe that global readings have any
+non-negligible weight data in the AS-A condition. Apart from this, if
+the model is true, the data corroborates the belief that the literal
+reading is strongly preferred over the local reading over the global
+reading (again witness the non-overlapping 95\% confidence
+regions). We also see the expected general effect of intonational
+markedness. Qualitatively speaking, the preference for literal
+readings appears less pronounced in the accented conditions.
+
+\todo[inline]{still to be added: posteriors over $q$ and errors $e_k$}
+
+\paragraph{Model validation.} We should also check whether the model
+is actually a suitable model to predict the observed data. Posterior
+predictive checks indicate that it is. Figures~\ref{fig:Posterior_TF}
+and \ref{fig:Posterior_T} show simulated samples of answer patterns
+that the model predicts under the posterior values for the latent
+parameters. Everything looks almost perfect, with the only exception
+the estimation of global readings in the ES-conditions.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{pics/PPC_TF.pdf}
+  \caption{Posterior predictive check for the target-related control
+    conditions. The colored dots on the plots indicate the actual
+    observed numbers of choices. Intuitively speaking, the ``higher''
+    the dot on the curve, the more likely does the model (under the
+    posterior values for its parameters) predict the data (on which
+    the posterior estimate is based).}
+  \label{fig:Posterior_TF}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{pics/PPC_T.pdf}
+  \caption{Posterior predictive check for the target-related control
+    conditions.}
+  \label{fig:Posterior_T}
+\end{figure}
+
 \printbibliography[heading=bibintoc]

### 2013-11-03 text/prob_model/prob_model.tex

@@
 the late-closure reading is certainly preferred (witness the clearly
-overlapping 95\% confidence regions).
+overlapping 95\% HDIs).\footnote{A 95\% Highest Density Interval (HDI)
+  is a convex region of values over which 95\% of the distribution's
+  probability density is divided, such that no value outside of that
+  region has higher probability density than any point within
+  \citep{Kruschke2011:Doing-Bayesian-}. Intuitively speaking, the 95\%
+  HDI is the set of values into which we should believe most strongly,
+  and what falls outside this region is what can be excluded with
+  relative safety.}
 
@@
     conditions. Colored lines below the actual plots indicate 95\%
-    confidence intervals.}
+    HDIs.}
   \label{fig:Posterior_T}
@@
 reading is strongly preferred over the local reading over the global
-reading (again witness the non-overlapping 95\% confidence
-regions). We also see the expected general effect of intonational
+reading (again witness the non-overlapping 95\% HDIs). We also see the expected general effect of intonational
 markedness. Qualitatively speaking, the preference for literal
@@
 
+\paragraph{Hypothesis testing.} We are interested in two questions:
+(i) which readings are available? and (ii) what is the preference
+order over readings?
+
+The first question can be answered by looking at the HDIs of the
+posteriors of the candidate readings. The HDIs give the region of the
+95\% least unbelievable parameter values, given the data and the
+model. We would like to check the hypothesis that a given reading is
+unavailable, i.e., it's activation value in the probabilistic model is
+equal to 0, or close to zero, i.e., within a small distance away from
+the critical value, such as $0.01$ (Region of Practical Equivalence,
+ROPE). We reject the ``null-hypothesis'' that the true value is 0 if
+its ROPE lies entirely outside the 95\% HDI; we accept the
+``null-hypothesis'' if the ROPE lies entirely within the 95\% HDI
+\citep[][Ch.~12]{Kruschke2011:Doing-Bayesian-}. The following table
+lists approximations of the 95\% HDIs for each condition and reading:
+
+\begin{center}
+  \begin{tabular}{lllllll}
+    & lit & loc & glb & \\ \midrule
+    as-n & $(0.8595 , 0.9796)$ & $(0.017 , 0.1321)$
+    & $(0 , 0.021)$ \\
+    as-a 
+    & $(0.7633 , 0.9312)$
+    & $(0.0564 , 0.2063)$
+    & $(0 , 0.0639)$ \\
+    es-n 
+    & $(0.664 , 0.9502)$
+    & $(0.0486 , 0.3329)$
+    & $(0 , 0.0254)$ \\
+    es-a 
+    & $(0.5688 , 0.7998)$
+    & $(0.1987 , 0.4294)$
+    & $(0 , 0.0199)$ 
+  \end{tabular}
+\end{center}
+
+For a ROPE of up to $[0;0.017)$ we therefore should draw the same
+conclusion for all conditions: we reject the hypothesis that there are
+no local readings, but we neither accept nor reject the hypothesis
+that there are no global readings.
+
+The second question after the preference relations between readings
+can be answered in a similar way. Here, we look at the posterior
+beliefs about the differences of activation strengths and ask whether
+these posterior beliefs allow us to safely conclude that differences
+are bigger than zero or not. Figure~\ref{fig:PostDiffT} shows the
+relevant comparisons, together with the 95\% HDIs showing that the
+data provides evidence that the qualitative preference order is the
+same in all conditions: literal readings are preferred over local
+readings, which are in turn preferred over global readings.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{PostDiffT.pdf}
+  \caption{Posteriors over differences between activation strengths.}
+  \label{fig:PostDiffT}
+\end{figure}
+
 \printbibliography[heading=bibintoc]

### 2014-04-22 text/micha_stat_analysis/notes_new.tex

--- 2013-06-22 text/micha_stat_analysis/notes.tex
@@
 
+We excluded two participants from the analysis due to poor performance
+on control conditions (VPs 2 and 29).
+
 There were two critical sentence-sequence types, \as and \es, which
@@
     \midrule
-    Pos 1 & 29 &  7 & 0 & 1 \\
-    Pos 2 & 26 & 10 & 0 & 1 \\
-    Pos 3 & 25 &  9 & 1 & 2 \\ \addlinespace[0.15cm]
-    Total & 80 & 26 & 1 & 4
+    Pos 1 & 35 &  0 & 0 & 3 \\
+    Pos 2 & 32 &  3 & 0 & 3 \\
+    Pos 3 & 33 &  3 & 0 & 2 \\ \addlinespace[0.15cm]
+    Total &100 &  6 & 0 & 8
 \end{tabular}}
@@
     \midrule
-    Pos 1 & 16 &  7 & 0 & 14 \\
-    Pos 2 & 21 & 13 & 0 &  3 \\
-    Pos 3 & 16 & 13 & 0 &  8 \\ \addlinespace[0.15cm]
-    Total & 53 & 33 & 0 & 25
+    Pos 1 & 19 &  5 & 0 & 14 \\
+    Pos 2 & 25 &  2 & 0 & 11 \\
+    Pos 3 & 21 &  6 & 0 & 11 \\ \addlinespace[0.15cm]
+    Total & 65 & 13 & 0 & 36
 \end{tabular}}
@@
     \midrule
-    Pos 1 & 28 &  7 & 1 & 1 \\
-    Pos 2 & 25 &  8 & 1 & 3 \\
-    Pos 3 & 24 & 10 & 0 & 3 \\ \addlinespace[0.15cm]
-    Total & 77 & 25 & 2 & 7
+    Pos 1 & 33 &  2 & 1 &  2 \\
+    Pos 2 & 31 &  4 & 1 &  2 \\
+    Pos 3 & 31 &  5 & 0 &  2 \\ \addlinespace[0.15cm]
+    Total & 95 & 11 & 2 &  6
 \end{tabular}}
@@
     \midrule
-    Pos 1 & 13 &  6 & 0 & 18 \\
-    Pos 2 & 24 &  7 & 1 &  5\\
-    Pos 3 & 19 & 13 & 0 &  5 \\ \addlinespace[0.15cm]
-    Total & 56 & 26 & 1 & 28
+    Pos 1 & 24 &  8 & 0 &  6 \\
+    Pos 2 & 22 &  7 & 0 &  9 \\
+    Pos 3 & 27 &  6 & 0 &  5 \\ \addlinespace[0.15cm]
+    Total & 73 & 21 & 0 & 20
 \end{tabular}}
@@
 
-Two things strike the eye. Firstly, there are hardly any \emph{global}
-responses. For subsequent analysis in terms of log-linear models we
-must therefore lump together \emph{global} and \emph{false} responses
-into one more general category level \emph{other}. Secondly, the
-number of \emph{false} responses drops remarkably in the
-\es-conditions. The following analysis should probe into this
-potential position effect.
-
 To test which factors are relevant to explain the data distribution in
@@
 \textsc{Position}, \textsc{Response}, \textsc{Condition}, and
-\textsc{Accent}. To ensure applicability, we lump levels \emph{global}
-and \emph{false} of factor \textsc{Response} into a single level
-\emph{other}. The best predictor of the data takes all factors
-\textsc{Position}, \textsc{Response} and \textsc{Condition} and all
-their interactions, including the three-way interaction, into account
-($\chi^2 = 7.493$, $df=18$, $p = 0.985$, $AIC = 43.493$ (compared to
-$AIC=72$ of the saturated model)). Crucially, factor \textsc{Accent}
-is spurious.
+\textsc{Accent}. As there are hardly any \emph{global} responses, we
+must lump levels \emph{global} and \emph{false} of factor
+\textsc{Response} into a single level \emph{other}, because otherwise
+log-linear regression is not applicable. We select the ``best''
+predictor of the data by a gradient search over hierarchical models in
+terms of AICs. The best model takes factors \textsc{Accent},
+\textsc{Response} and \textsc{Condition} into account, as well as the
+interaction terms \textsc{Response:Accent} and
+\textsc{Response:Condition} ($\chi^2 = 14.29$, $df=27$, $p = 0.98$,
+$AIC = 32.29$ (compared to $AIC=72$ of the saturated
+model)). Crucially, factor \textsc{Position} is spurious. Response
+patterns only depended on the type of the sentence and whether it was
+produced with accentuation.
 
-% To test whether the effect of \textsc{Condition} could be due to the
-% relatively high number of \emph{false} responses in the
-% \es-conditions, we regrouped the factor \textsc{Response} once more
-% to distinguish only \emph{local} responses from \emph{other}
-% responses. Doing so allows us to address the question whether the
-% amount of \emph{local} responses differed across conditions and
-% accentuation types. But this does not seem to be the case. The model
-% that predicts the data best in this case contains factors
-% \textsc{Response} and \textsc{Position} and their two-way
-% interaction ($\chi^2 = 4.71$, $df=18$, $p = 0.999$, $AIC = 16.711$
-% (compared to $AIC=48$ of the saturated model)). This suggests that a
-% shift in the distribution of \emph{local} responses can be
-% satisfactorily explained as a position effect that is constant
-% across conditions: later trials yielded less \emph{other} responses.
-
-To test, then, whether \textsc{Position} affects the distribution of
-\emph{literal} and \emph{local} readings, we also computed the best
-log-linear predictor for the subset of our data including only
-\emph{literal} and \emph{local} responses. Doing so, the best
-predictor indeed drops factor \textsc{Position} and contains only
-factors \textsc{Response} and \textsc{Condition} and their two-way
-interaction ($\chi^2 = 12.497$, $df=20$, $p = 0.898$, $AIC = 20.497$
-(compared to $AIC=48$ of the saturated model)). This suggests that the
-factor \textsc{Position} is not relevant for explaining the
-distribution of \emph{literal} and \emph{local} readings. Its effects
-noted previously are most likely due to the decrease of \emph{false}
-responses in later trials of the \es-conditions.
+\todo[inline]{ what's the argument to accept that there are local readings
+    for neutral accentuation in the first place? ; make plots with ``raw responses'' on position
+}
 
@@
 
-Some subjects saw three others four trials of preference-related
-controls. The relevant factors in this case are: \textsc{Condition}
-with levels \emph{lc} and \emph{ec} coding which reading could be
-judged first in a sequence; \textsc{Accent} with levels \emph{ntr},
-\emph{lc} and \emph{ec} coding which reading was cued by intonation;
-\textsc{Position} with levels 1 to 4; and \textsc{Response} with
-levels \emph{lc}, \emph{ec} and \emph{false}. The observed data under
-this classification is given in Table~\ref{tab:TF-ContingencyTable}.
+For our preference-related control conditions the relevant factors
+are: \textsc{Condition} with levels \emph{lc} and \emph{ec} coding
+which reading could be judged first in a sequence, \textsc{Accent}
+with levels \emph{ntr}, \emph{lc} and \emph{ec} coding which reading
+was cued by intonation, \textsc{Response} with levels \emph{lc},
+\emph{ec} and \emph{false}, and finally \textsc{Position} encoding how
+frequently subjects had seen a given sentence-accentuation pair
+before. Some subjects saw three, others four trials, so that to ensure
+unbiased applicability of our log-linear models, we excluded every
+fourth encounter of the same sentence type and accentuation. The
+observed data under this classification is given in
+Table~\ref{tab:TF-ContingencyTable}.
 %
@@
     \midrule
-    Pos 1 & 30 &  6 & 1  \\
-    Pos 2 & 24 &  9 & 4  \\
-    Pos 3 & 25 &  8 & 3  \\
-    Pos 4 & 11 & 10 & 1  \\ \addlinespace[0.15cm]
-    Total & 90 & 33 & 9 
+    Pos 1 & 23 &  9 & 6  \\
+    Pos 2 & 23 & 11 & 4  \\
+    Pos 3 & 27 &  8 & 3  \\ \addlinespace[0.15cm]
+    Total & 73 & 28 & 13 
 \end{tabular}}
@@
     \midrule
-    Pos 1 &  28 &   4 &   5 \\ 
-    Pos 2 &  26 &  10 &   1 \\ 
-    Pos 3 &  19 &  11 &   6 \\ 
-    Pos 4 &  11 &   9 &   2 \\ \addlinespace[0.15cm]
-    Total &  65 &  34 &  14 
+    Pos 1 &  22 &   5 &  11 \\ 
+    Pos 2 &  28 &   5 &   5 \\ 
+    Pos 3 &  29 &   7 &   2 \\ \addlinespace[0.15cm]
+    Total &  79 &  17 &  18 
 \end{tabular}}
@@
     \midrule
-    Pos 1 &  26 &   6 &   5 \\ 
-    Pos 2 &  30 &   4 &   3 \\ 
-    Pos 3 &  30 &   5 &   2 \\ 
-    Pos 4 &  14 &   1 &   1 \\ 
+    Pos 1 &  26 &   6 &   6 \\ 
+    Pos 2 &  30 &   5 &   3 \\ 
+    Pos 3 &  34 &   2 &   2 \\ 
     \addlinespace[0.15cm]
-    Total & 100 & 16 & 11 
+    Total & 90  & 13 & 11 
 \end{tabular}}
@@
     \midrule
-    Pos 1 &  24 &   6 &   7 \\ 
-    Pos 2 &  30 &   3 &   4 \\ 
-    Pos 3 &  30 &   5 &   2 \\ 
-    Pos 4 &  13 &   2 &   1 \\ 
+    Pos 1 &  30 &   4 &   4 \\ 
+    Pos 2 &  33 &   4 &   1 \\ 
+    Pos 3 &  31 &   4 &   3 \\ 
     \addlinespace[0.15cm]
-    Total &  97 &  16 &  14 
+    Total &  94 &  12 &  8 
 \end{tabular}}
@@
     \midrule
-    Pos 1 &  15 &  15 &   7 \\ 
-    Pos 2 &  20 &  10 &   7 \\ 
-    Pos 3 &  24 &   7 &   5 \\ 
-    Pos 4 &   8 &   8 &   6 \\
+    Pos 1 &  15 &  18 &   5 \\ 
+    Pos 2 &  16 &  16 &   6 \\ 
+    Pos 3 &  15 &  16 &   6 \\
     \addlinespace[0.15cm]
-    Total &  67 & 40 &  25 
+    Total &  46 & 50 &  17 
 \end{tabular}}
@@
     \midrule
-    Pos 1 &  21 &  12 &   4 \\ 
-    Pos 2 &  18 &  12 &   7 \\ 
-    Pos 3 &  22 &  12 &   2 \\ 
-    Pos 4 &  13 &   7 &   2 \\ 
+    Pos 1 &  18 &  12 &   8 \\ 
+    Pos 2 &  18 &   9 &  11 \\ 
+    Pos 3 &  18 &  10 &  10 \\
     \addlinespace[0.15cm]
-    Total &  74 &  43 &  15 
+    Total &  54 &  31 &  29 
 \end{tabular}}
@@
 
-The best hierarchical log-linear model (by $AIC$) includes factors
-\textsc{Response}, \textsc{Accent} and \textsc{Position}, as well as
-the two-way interaction between \textsc{Response} and \textsc{Accent}
-($\chi^2 = 48.802$, $df=60$, $p=0.85$, $AIC=72.802$ (compared to
-$AIC=144$ of the standard model)). Crucially, the observed response
-pattern does not differ significantly across conditions (i.e., which
-reading can be judged first), but does depend on intonational cues.
-
-The factor \textsc{Position} cannot be dropped without dramatically
-reducing explanatory power of the model. However, if we abstract over
-intonation and conditions, we get the following table:
-\begin{center}
-\centering
-\begin{tabular}{rrrr}
-  & \emph{lc} & \emph{ec} & \emph{false} \\ 
-  \midrule
-  Pos 1 & 144 & 49 & 29 \\ 
-  Pos 2 & 148 & 48 & 26 \\ 
-  Pos 3 & 150 & 48 & 20 \\ 
-  Pos 4 &  70 & 37 & 13 \\ 
-\end{tabular}
-\end{center}
-There is no interaction between \textsc{Position} and
-\textsc{Response} ($\chi^2$, $df=6$, $p=0.3798$), suggesting that
-\textsc{Position} does not affect the overal distribution of readings.
-
-\newpage
+Just like for the target conditions, the best hierarchical log-linear
+model (by $AIC$) includes factors \textsc{Response}, \textsc{Accent}
+and \textsc{Condition}, as well as the two-way interactions
+\textsc{Response:Accent} and \textsc{Response:Condition} ($\chi^2 =
+23.14$, $df=42$, $p=0.99$, $AIC=47.14$ (compared to $AIC=108$ of the
+saturated model)). Crucially, the observed response pattern does not
+differ significantly across conditions (i.e., which reading can be
+judged first), but does depend on intonational cues.
 
@@
     \midrule
-    accented & 15 &  5 & 0 &  9 \\
-    neutral  &  6 &  0 & 0 &  2 \\ \addlinespace[0.15cm]
-    Total    & 21 &  5 & 0 & 11
+    accented & 10 &  3 & 1 &  2 \\
+    neutral  & 15 &  0 & 0 &  7 \\ \addlinespace[0.15cm]
+    Total    & 25 &  3 & 0 &  9
 \end{tabular}
@@
 Notably, nobody gave a \emph{local} answer on the first encounter of a
-target condition with neutral accentuation. Still, Pearson's $\chi^2$
-test does not reject the null hypothesis of an equal distribution of
-readings ($\chi^2 = 2.0546$, $p \approx 0.4318$).  \todo[inline]{Is
-  this test applicable at all? Don't we have too little data points?
-  How else could a dependence be tested in this case?}
+target condition with neutral accentuation. Pearson's $\chi^2$ test
+does reject the null hypothesis of an equal distribution of readings
+($\chi^2 = 7.0051$, $p \approx 0.034$).
 

### 2014-04-26 text/micha_stat_analysis/notes_new.tex

@@
 $AIC = 32.29$ (compared to $AIC=72$ of the saturated
-model)). Crucially, factor \textsc{Position} is spurious. Response
-patterns only depended on the type of the sentence and whether it was
-produced with accentuation.
+model)). Crucially, factor \textsc{Position} is spurious in the best
+model. This suggests that response patterns only depend on the type of
+the sentence and whether it was produced with accentuation. Moreover,
+there is no interaction effect between response, accent and condition,
+implying that accentuation had no relevantly different effect on
+response patterns in different conditions.
 
@@
 23.14$, $df=42$, $p=0.99$, $AIC=47.14$ (compared to $AIC=108$ of the
-saturated model)). Crucially, the observed response pattern does not
-differ significantly across conditions (i.e., which reading can be
-judged first), but does depend on intonational cues.
+saturated model)). Crucially, according to the best model, the
+observed response pattern does not differ relevantly across positions
+(i.e., which reading can be judged first), but does depend on
+intonational cues. Additionally, no interaction effect between
+response, accent and condition is included, suggesting that
+accentuation had the same effect on response patterns in different
+conditions.
 

### 2014-04-28 text/prob_model/prob_model.tex

@@
   p^\text{as-n}_{\text{loc}} + e^\text{as-n} \\
-  t^{\text{as-n}}_{\text{glb}} & \propto (1-q) \
+  t^{\text{as-n}}_{\text{glb}} & \propto (1-q)q \
   p^\text{as-n}_{\text{glb}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{err}} &

### 2014-05-15 text/paper/paper4.tex
reworked introduction

--- 2013-06-18 text/paper/paper3.tex
@@
 \usepackage{pgfplots}
+\usepackage{todonotes}
 
@@
 % \usepackage{../helpers/myenvironments}
-
-\usepackage{subfig}
 
@@
 \newcommand{\ivt}{\acro{ivt}}
+
+\renewcommand{\mymark}[1]{\textbf{#1}}
 
@@
 \begin{abstract}
-  Scalar item \emph{some} is widely assumed to undergo, given relevant
-  preconditions, a pragmatic meaning enrichment to \emph{some but not
-    all} if it occurs in matrix position. The question under which
-  circumstances this meaning enrichment can take place in embedded
-  position plays an important role in deciding how to delineate
-  semantics and pragmatics. % Some claim
+  Scalar item \emph{some} is widely assumed to receive a pragmatic
+  meaning enrichment to \emph{some but not all} if it occurs in matrix
+  position. The question under which circumstances this enrichment can
+  occur in certain embedded positions plays an important role in
+  deciding how to delineate semantics and pragmatics. % Some claim
   % that it requires marked intonation for the relevant pragmatic
@@
   % freely.
-  We present a novel experimental paradigm to test whether the
-  relevant pragmatic enrichment is available in embedded positions
-  with or without prosodic markedness. On top of adding prosodic
-  manipulation, our experimental design was catered to a number of
-  methodological difficulties that were identified for previous
-  related studies. The data obtained refutes both a traditional
-  Gricean view of scalar implicature calculation, as well as the more
-  recent grammatical approach.
+  We present new experimental data that bears on this theoretical
+  issue. In distinction to previous experimental approaches, we
+  presented sentence material auditorily in order to explicitly
+  control prosodic markedness of the scalar item. Moreover, our
+  experimental design gives insight into the preference of
+  hypothesized meaning differences, not only on their general
+  availability. The data obtained in this way turns out problematic
+  for both a traditional Gricean view of scalar implicature
+  calculation, as well as the more recent grammatical approach.
 \end{abstract}
@@
 The existential quantifier \emph{some} is usually assumed to receive a
-semantic interpretation similar to logical $\exists$, so that the
-sentence \emph{Some boys cried} is literally true in a situation where
-all boys cried. But it is also usually considered to be a
-\mymark{scalar item} in that its use invites comparison with (at
-least) the semantically stronger universal quantifier \emph{all}
+semantic interpretation similar to logical $\exists$, so that
+(\ref{bsp:Plain-SI-Target}) is literally true even when Hans solved
+all of the problems. But it is also usually considered to invite
+comparison with (at least) the semantically stronger universal
+quantifier \emph{all}
 \citep[c.f.][]{Horn1972:On-the-Semantic,Gazdar1979:Pragmatics:-Imp,AtlasLevinson1981}. This
-comparison can lead to an upper-bounding meaning enrichment, e.g.,
+scalar comparison can lead to an upper-bound meaning enrichment, e.g.,
 when an utterance of (\ref{bsp:Plain-SI-Target}) is taken to invite
@@
 
-% If this upper-bounding inference would occur often and
+% If this upper-bound inference would occur often and
 % systematically enough, then it may well be that also embedded
@@
 where the scalar item \emph{some} occurs in the scope of other logical
-operators. In \as-sentences (mnemonic for \textit{all \dots some \dots})
-as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded under
-universal quantifier \emph{all}. In \es-sentences (mnemonic for
+operators. In \as-sentences (mnemonic for \textit{all \dots some
+  \dots}) as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded
+under universal quantifier \emph{all}. In \es-sentences (mnemonic for
 \textit{exactly one \dots some \dots}) like (\ref{bsp:GE}) \emph{some}
@@
 (ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
-(\ref{bsp:GE-Global}) where, according to Gricean intuition, we enrich
-utterances of (\ref{bsp:AE}) and (\ref{bsp:GE}) with the negation of
-alternative utterances of the corresponding sentences
+(\ref{bsp:GE-Global}) where we enrich the meaning of (\ref{bsp:AE})
+and (\ref{bsp:GE}) with the negation of the corresponding sentences
 (\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
@@
 
-\noindent Given this relative abundance of theoretically conceivable
-readings, two interlocked empirical questions arise:
+\noindent Given this plurality of hypothesized readings, we need to
+ask:
 \begin{enumerate}[Q1:]
@@
 concerns the question under which circumstances and to what extent the
-upper-bounding inference from \emph{some} to \emph{some but not all}
-can occur within the compositional computation of semantic values. Two
+upper-bound inference from \emph{some} to \emph{some but not all} can
+occur within the compositional computation of semantic values. Two
 opposing theoretical positions can be distinguished here:
@@
 not be readily attested unless marked by special intonation;
-\emph{grammaticalism} holds that local readings are available and
-indeed preferred. To distinguish between these opposing positions, it
-is particularly relevant to assess the availability and relative
-preference of local readings for \as- and
-\es-sentences. %(Section~\ref{sec:theories-predictions}
-%will discuss the relevant theoretical positions and the significance
-%of alleged local readings in more detail.)
-
-% Firstly, there are \mymark{pragmatic traditionalists} who seek to
-% conserve the spirit of \citeauthor{Grice1975:Logic-and-Conve}'s
-% (\citeyear{Grice1975:Logic-and-Conve}) original ideas as much as
-% possible
-% \citep[e.g.][]{Spector2006:Scalar-Implicat,Sauerland2004:Scalar-Implicat,Russell2006:Against-Grammat,vanRooijSchulz:ExhaustiveInterpretation,Geurts2010:Quantity-Implic,Franke2011:Quantity-Implic}.
-Traditionalists
-% acknowledge the existence of global readings, but might consider local
-% readings either unavailable or a beast distinct from scalar
-% implicatures. An often phrased intuition of the traditionalists is
-% that local readings, since they are special kinds of inferences,
-% require special intonation, in particular emphatic stress on the
-% scalar item.
-
-% Opposed to that is the camp of \mymark{lexical conventionalists}
-% \citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}
-% who maintain that scalar \emph{some} is lexically ambiguous between
-% the standard logical meaning \emph{some and maybe all} and the
-% upper-bounded meaning \emph{some but not all}. As the latter is
-% considered a default, lexical conventionalism has no problem
-% accounting for local readings, and in fact would consider these the
-% preferred readings.
-
-% Thirdly and finally, there is the camp of \mymark{grammaticalists} who
-% defend that the distribution of upper-bounded readings of \emph{some}
-% is best explained by postulating a silent operator, akin to the
-% meaning of the particle \emph{only}
-% \citep{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}. According
-% to the grammatical view, this silent operator may be applied in
-% compositional semantics also in the scope of other logical operators,
-% but, so as not to overgenerate readings, the availability of readings
-% is constraint by the \emph{strongest meaning hypothesis}
-% \citep{DalrympleKanazawa1998:Reciprocal-Expr}. Grammaticalist theories
-% predict that all three types of readings are available. Moreover,
-% according to the grammatical view, the local reading is preferred for
-% \as-sentences, while the global one is preferred for
-% \es-sentences. (More precisely, as we will see
-% Section~\ref{sec:theories-predictions}, depending on the variant of
-% the strongest meaning hypothesis employed, either the global reading
-% is predicted to be preferred for \es-sentences, or the global and the
-% local reading are predicted to be equally preferred.)
-
-A number of empirical studies have already targeted this issue
+\emph{grammaticalism} holds that local readings are available and, at
+least under the most prominent of selection principles for candidate
+readings, even preferred (see Section~\ref{sec:grammaticalism}). To
+distinguish between these opposing positions, it is therefore
+necessary to assess the availability and relative preference of
+readings for \as- and \es-sentences under conditions that control for
+intonational markedness. This is what this paper aims to do.
+
+A number of empirical studies have already studied sentences like
+(\ref{bsp:AE}) and (\ref{bsp:GE}) this issue
 \citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. Unfortunately,
-results from these studies do not provide as clear-cut evidence for or
-against either of the two rivaling positions as one would hope
-for. This is due to several reasons. Firstly, previous studies have
-only accumulated limited evidence pertaining to the preference
-relations between putative readings of both types of
-sentences. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
+results from these studies do not provide uncontroversial evidence to
+decide between the two main rivaling positions. This is due to several
+reasons. Firstly, previous studies have only accumulated limited
+evidence pertaining to the preference relations between putative
+readings of both types of sentences. Secondly, as
+\citet{Tielvan-Tiel2012:Embedded-Scalar} and
 \citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue, the putative
@@
 will address this extant position as the \emph{intonational markedness
-  hypothesis}. But if intonation plays a role, it is absolutely vital
-to present target sentences auditorily, so as to be able to control
-for effects of ``silent prosody'' that subjects may apply when reading
-a sentence \citep[see][]{Bader98,Fodor98}.
+  hypothesis}. But if intonation plays a role, it is vital to present
+target sentences auditorily, so as to be able to control for effects
+of ``silent prosody'' that subjects may apply when reading a sentence
+\citep[see][]{Bader98,Fodor98}.
 
@@
 \citep[see][]{Conroy2008}. This way we obtained categorical behavioral
-data that is both indicative of the reading subjects assumed and
-independent of any potential pictorial confounds. We also made sure
-that our method is able to reveal information about reading
-preferences by including a control condition with ambiguous sentences
-with a well-known preference on available readings.
-
-The data obtained by this method contradicts both traditionalism and
-grammaticalism. Contrary to traditionalism and the intonational
-markedness hypothesis, we found evidence for local readings for both
-kinds of critical sentences, irrespective of intonational stress. Even
-the intonational markedness hypothesis on its own is not supported by
-our data: stress on embedded scalar items did not lead to an increase
-in answers suggesting a local reading. But also grammaticalism is
-incongruent with the observed pattern in our data.  Grammaticalism
-predicts local readings to be the preferred readings, but we found no
-evidence for that. More strongly even, the preference order among
-putative readings suggested by our data cannot even in principle be
-explained by the general kind of second-order selection criterion that
-is currently favored by grammaticalists, namely by comparison of
-logical strength of putative readings
-\citep[e.g.][]{ChierchiaFox2008:The-Grammatical}. In sum, our data
-sheds doubt on both traditionalism and grammaticalism in their
-currently most common forms. We conclude the paper by some speculation
-about how either position might be amended in the light of our data.
+data that is both clearly indicative of the reading that subjects
+assumed and fairly independent of any potential pictorial
+confounds. Moreover, this method also gives information about reading
+preferences. We validated this by including a control condition with
+ambiguous sentences with a well-known preference on available
+readings.
+
+The data obtained by this method is problematic for both
+traditionalism and grammaticalism. Contrary to traditionalism and the
+intonational markedness hypothesis, we found evidence for local
+readings for both kinds of critical sentences, irrespective of
+intonational stress. \todo{enlarge: how big was this effect? can
+  traditionalists explain this away?} But also grammaticalism is
+incongruent with the observed pattern in our data. Backed up by the
+Strongest Meaning Hypothesis
+\citep{DalrympleKanazawa1998:Reciprocal-Expr}, grammaticalism predicts
+local readings to be the preferred readings, but we found no evidence
+for that. More strongly even, the preference order among putative
+readings suggested by our data cannot even in principle be explained
+by comparisons of logical strength among putative readings. In sum,
+our data sheds doubt on both traditionalism and grammaticalism in
+their currently most common forms. We conclude the paper by some
+speculation about how either position might be amended in the light of
+our data.
 
@@
 predictions of traditionalism and grammaticalism about availability
-and preference of readings of our target
-sentences. Section~\ref{sec:previous-studies} recaps the results of
-related experimental studies to the extent necessary to motivate our
-own approach. Section~\ref{sec:exp} eventually contributes our
+and preference of readings for these
+sentences. Section~\ref{sec:previous-studies} reviews related
+experimental studies to the extent necessary to motivate our own
+approach. Section~\ref{sec:exp} eventually contributes our
 experimental design and our results.
@@
 manner.  \emph{Conventionalism} (also sometimes called
-\emph{lexicalism}) proposes that if the upper-bounding inference from
+\emph{lexicalism}) proposes that if the upper-bound inference from
 \emph{some} to \emph{some but not all} occurs frequently, it would be
@@
 could explain this by the assumption that some (lazy?, smart?)
-speakers have made a conventionalized upper-bounding meaning entry for
+speakers have made a conventionalized upper-bound meaning entry for
 scalar \emph{some} while others keep computing things on the fly. It

### 2014-05-15 text/paper/paper4.tex
update section 3

@@
             url=false]{biblatex}
-% \bibliography{../helpers/MyRefGlobal}
-\bibliography{paper}
+\bibliography{MyRefGlobal}
+% \bibliography{paper}
 
@@
 Consequently, the \mymark{Gricean recipe}
-\citep[see][]{Geurts2010:Quantity-Implic} for deriving a simple
-scalar inference like that in (\ref{bsp:Plain-SI-Implicature}) from an
+\citep[see][]{Geurts2010:Quantity-Implic} for deriving a simple scalar
+inference like that in (\ref{bsp:Plain-SI-Implicature}) from an
 utterance of (\ref{bsp:Plain-SI-Target}) is as follows: if the issue
@@
   derivation of implicatures targeting the speaker's epistemic state
-  \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit},
-  as this is not crucially relevant for the issues we are interested
-  in here.}
+  \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit}. The
+  concluding Section~\ref{sec:conclusions} will come back to this in
+  more detail.}
 
@@
 
-Which of these readings, if any, does traditionalism predict to be
-preferred? This depends on whether the auxiliary assumptions necessary
-to derive global readings by the Gricean recipe are plausibly met in
-the particular case of utterance of \as- and \es-sentences. These
-auxiliary assumptions include relevance of the extra information
-provided by the global reading, mutual awareness that the stronger
-alternative has been a speaker option, the speaker's competence about
-the issue, etc. Normally, traditionalist accounts would assume that
-these extra assumptions are met. In that case, traditionalism would
-predict that global readings should be preferred over literal
-readings. On the other hand, it might also be hypothesized that, for
-example, a competence assumption is harder to justify for \as- and
-\es-sentences in general than for simpler sentences such as
-(\ref{bsp:Plain-SI}): it might be less clear that the speaker knows
-exactly how many students solved how many problems, than that the
-speaker knows exactly how many problems Hans solved. In that case, or
-if any other assumption of the Gricean recipe cannot be maintained,
-traditionalism would predict that the literal reading would be
-preferred over the global one. But that means that there are at least
-two varieties of traditionalism that, depending on which additional
-assumptions we would make, yield slightly different predictions:
-\mymark{the strong variety of traditionalism} maintains that the
-auxiliary assumptions of the Gricean recipe hold
+Traditionalism's predictions about preferences between literal and
+global readings depend on whether the auxiliary assumptions necessary
+to derive global readings by the Gricean recipe are plausibly
+met. These auxiliary assumptions include relevance of the extra
+information provided by the global reading, mutual awareness that the
+stronger alternative has been a speaker option, the speaker's
+competence about the issue, etc. Normally, traditionalist accounts
+would assume that these extra assumptions are met. In that case,
+traditionalism would predict that global readings should be preferred
+over literal readings. On the other hand, if auxiliary assumptions are
+implausible, traditionalism would predict that the literal readings
+would be preferred over the global one. Consequently, there are at
+least two varieties of traditionalism that, depending on which
+additional assumptions we would make, yield slightly different
+predictions: \mymark{the strong variety of traditionalism} maintains
+that the auxiliary assumptions of the Gricean recipe hold
 usually/strongly/unless-completely-intenable and therefore predicts
@@
   similar to the global reading, that the speaker is uncertain whether
-  the stronger alternative is true. Whether it does predict that
-  depends on which auxiliary assumptions are assumed to be met and
-  which are not.}
+  the stronger alternative is true. (See also the discussion in
+  Section~\ref{sec:conclusions}.)}
 
 Does traditionalism also predict local readings to be available? The
-answer is slightly different for \as- and the \es-sentences.\fn{Some
-  traditionalists concede that (something like) local readings can
-  occur for both kinds of sentences if scalar items are marked with
-  special accentuation, albeit then as a signal of a different
-  pragmatic process
-  \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic}. We
-  will address this addition to traditionalism in more detail in
-  Section~\ref{sec:inton-mark-hypoth}.} For \es-sentences,
-traditionalism does not predict that a local reading is available, at
-least not as a quantity implicature
-\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. This
-is because traditionalism assumes that quantity implicatures are
-pragmatic enrichments of the literal meaning of an utterance, obtained
-by conjoining the literal meaning with a suitable set of negated
-alternatives. But since the literal and the local reading of
-\es-sentences are logically independent, there is no way that local
-readings can be derived in a traditionalist manner as a quantity
-implicature: if $X$ and $Y$ are logically independent propositions,
-then there is no proposition $Z$ such that $X$ would be equivalent to
-$Y \wedge \neg Z$.
+answer is slightly different for \as- and the \es-sentences. For
+\es-sentences, traditionalism does not predict that a local reading is
+available, at least not as a quantity implicature by conjoining the
+literal meaning with a suitable set of negated alternatives
+\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. The
+literal and the local reading of \es-sentences are logically
+independent. But if $X$ and $Y$ are logically independent
+propositions, then there is no proposition $Z$ such that $X$ would be
+equivalent to $Y \wedge \neg Z$.
 
@@
 
-Another prominent theoretical position is
-\mymark{grammaticalism}. Recently, a lot of evidence based on
-intuitive judgements and more theoretical considerations has been
-discussed in favor of this position
-\citep[see][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}. % When
+Recently, a lot of evidence based on intuitive judgements and more
+theoretical considerations has been discussed in favor of
+\mymark{grammaticalism}
+\citep[see][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical}. % When
 % it comes to the predictions of available readings of \as- and
@@
 \citep{Chierchia2006:Broaden-Your-Vi}, if necessary multiple times
-\citep{Fox2007:Free-Choice-and}. This silent operator is variably
-referred to as $\mathrm{O}(\cdot)$ or $\exh(\cdot)$, because it is
-assumed to be similar in effect to the meaning of particle \emph{only}
-or of the mechanism of \emph{exhaustive interpretation}
+\citep{Fox2007:Free-Choice-and}. This silent operator is referred to
+as $\mathrm{O}(\cdot)$ or $\exh(\cdot)$, because it is assumed to be
+similar in effect to the meaning of particle \emph{only} or of the
+mechanism of \emph{exhaustive interpretation}
 \citep{GroenendijkStokhofThesis1984,Stechowvon-StechowZimmermann1984:Term-Answers-an,Rooijvan-RooijSchulz2013:Exhaustive-Inte,vanRooijSchulz:ExhaustiveInterpretation,Fox2007:Free-Choice-and}. For
-our purposes, it is enough to note that $\exh(\cdot)$ is a
-poly-typed function that enriches an expression $X$, which crucially
-need not be a full proposition, based on a set $\alt(X)$ of
-(suitable, relevant) alternatives to $X$ that yields an enriched
-meaning of the form:\fn{More sophisticated formulations of exhaustive
-  interpretation have been proposed
+our purposes, it is enough to note that $\exh(\cdot)$ is a poly-typed
+function that enriches an expression $X$, which need not be a full
+proposition, based on a set $\alt(X)$ of (suitable, relevant)
+alternatives to $X$ that yields an enriched meaning of the
+form:\fn{More sophisticated formulations of exhaustive interpretation
+  have been proposed
   \citep[e.g.][]{Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}
   but this simple formulation is sufficient for the purposes of this
-  paper. Also, we gloss here over non-trivial details in the way this
-  operation is to be specified exactly within a compositional
-  semantics \citep[see][]{Chierchia2006:Broaden-Your-Vi}.}
+  paper.}
 \begin{exe}
@@
 
-The grammatical approach, as described so far, is rather flexible in
-that it makes many readings available. It is so flexible, in fact,
-that it must be constrained in some way or other to shield the
-approach against overgeneration. Grammaticalism is therefore aided by
-a principle that specifies which readings are to be preferred if
-several readings are generated by optional applications of
-$\exh(\cdot)$ in the compositional computation of semantic values. The
-principle that grammaticalists adhere to
-\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}
-is the \mymark{strongest meaning hypothesis} of
-\citet{DalrympleKanazawa1998:Reciprocal-Expr}. Roughly speaking, if a
-given sentence has several conceivable readings, the strongest meaning
-hypothesis selects for the strongest of
-these. \citet{ChierchiaFox2008:The-Grammatical} discuss two concrete
-variants of the strongest meaning hypothesis: fix a sentence with
-propositional content $S$ with candidate readings $C(S)$, where $C(S)$
-contains $S$ and all readings derivable from inserting $\exh(\cdot)$
-at suitable scope sites;\fn{Strictly speaking, we should compare
-  \emph{parses} of sentences with $\exh(\cdot)$ at various scope sites
-  with respect to the readings that these parses give rise to
+The grammatical approach, as described so far, is not yet a
+respectable theory. It makes little empirical commitments of
+substance. It must be supplemented by a selection principle that
+determines which of the many readings made available by the grammar
+actually obtain or are preferred. Proponents of grammaticalism are
+aware of this and have suggested some tentative disambiguation
+strategies. \citet{Magri2011:Another-Argumen}, for example, opts for
+obligatory presence of $\exh$ with variability in the set of relevant
+alternatives. \todo{verify that this is the proposal} Another proposal
+is that readings are preferred in relation to how well they answer the
+contextually given question under discussion
+\citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. Yet
+another proposal is to select readings by comparison of logical
+strengths, as suggested by the \mymark{strongest meaning hypothesis}
+of \citet{DalrympleKanazawa1998:Reciprocal-Expr}
+\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. We
+will focus entirely on this latter selection principle, because it
+seems to be the most prominent in the literature and because it makes
+the clearest predictions. That means that all we will say about
+grammaticalism in this paper strictly applies only to grammaticalism +
+strength based selection of readings.
+
+\citet{ChierchiaFox2008:The-Grammatical} discuss two concrete variants
+of strength-based disambiguation: fix a sentence with propositional
+content $S$ with candidate readings $C(S)$, where $C(S)$ contains $S$
+and all readings derivable from inserting $\exh(\cdot)$ at suitable
+scope sites;\fn{Strictly speaking, we should compare \emph{parses} of
+  sentences with $\exh(\cdot)$ at various scope sites with respect to
+  the readings that these parses give rise to
   \citep[see][]{ChierchiaFox2008:The-Grammatical}, but we may ignore
-  this detail here for ease of exposition.} then define \emph{ceteris
-  paribus} preferences among members of $X,Y \in C(S)$ as either
+  this detail here for ease of exposition.} then define for $X,Y \in
+C(S)$ either
 \begin{exe}
@@
 were not affected by capitalizing.\fn{Note that, unfortunately, the
-  authors do not provide percentages for the embedded conditions
+  paper does not provide percentages for the embedded conditions
   alone, but only the means across sentence types.}
-\citeauthor{Frazier08} concludes that accentuation did not affect
-their silent reading data, but raises the possibility that prosodic
-effects may have been present at least in a subset of the items (see
+\citeauthor{Frazier08} concludes that accentuation did not affect the
+silent reading data, but raises the possibility that prosodic effects
+may have been present at least in a subset of the items (see
 footnote~1 in \citet{Frazier08}, p.~330).

### 2014-05-15 text/paper/paper4.tex
update section 4

@@
 In order to test the divergent predictions of the relevant theoretical
-positions, a number of empirical studies have been carried out. In
-this section, we will focus on the influential studies by
+positions, a number of empirical studies have been carried out. We
+will focus on the works of
 \citet{GeurtsPouscoulous2009:Embedded-Implic},
 \citet{CliftonDube2010:Embedded-Implic} and
-\citet{ChemlaSpector2010:Experimental-Ev}. Unfortunately, as we argue
-here, the conjoined evidence from all of these studies is inconclusive
-as to the availability and preference of relevant readings.
+\citet{ChemlaSpector2010:Experimental-Ev}. Unfortunately, these
+studies do not provide conclusive evidence about the availability and
+preference of relevant readings and do not speak to intonational
+markedness effects.
 
@@
 
-On the other hand, \citet{Crain1998} argues in
-favor of truth-value judgments as a means of detecting dispreferred
-readings. Consequently, traditionalists could reply that the putative
-evidence for local readings in non-categorical judgement tasks might
-reflect something other than (strongly) truth-relevant
-speaker-intended meaning enrichments. Hence no case can be made for
-lexicalism or grammaticalism on the basis of these data
-\citep[see][for arguments along these
-lines]{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}.
+On the other hand, \citet{Crain1998} argue in favor of truth-value
+judgments as a means of detecting dispreferred readings. Consequently,
+traditionalists could reply that the putative evidence for local
+readings in non-categorical judgement tasks might reflect something
+other than (strongly) truth-relevant speaker-intended meaning
+enrichments. Hence no case can be made for lexicalism or
+grammaticalism on the basis of these data \citep[see][for arguments
+along these
+lines]{GeurtsTielvan-Tiel2013:Scalar-expressi,Tielvan-Tiel2014:Quantity-Matter,Tielvan-Tiel2012:Embedded-Scalar}.
 
@@
 obvious way. Moreover, typicality itself is not a satisfactory
-primitive in a putative explanation of the use of
-quantifiers. Plausibly, the reason why quantifier \emph{some} is more
-typical for some set sizes than others is at least dependent on, if
-not entirely derived from, its contrast with other conceivable
-alternatives, e.g., numerals within the subitizing range, as well as
-\emph{few}, \emph{most} or \emph{many}
-\citep[see][]{DegenTanenhaus2012:Processing-Scal}. For these reasons,
-we believe that typicality and other pictorial effects need to be
-taken seriously in the experimental design, but do not give a
-satisfactory account of the observed variation all by themselves.
+primitive in a putative explanation of the use of quantifiers. Rather
+it is possible to explain typicality judgements as the outcome of
+Gricean speaker preferences for informative descriptions, just like
+those that rationalize quantity implicatures
+\citep{Franke2014:Typical-use-of-}. For these reasons, we believe that
+typicality and other pictorial effects need to be taken seriously in
+the experimental design, but do not give a satisfactory account of the
+observed variation all by themselves.
 

### 2014-05-15 text/paper/paper4.tex
update section 4

@@
   derivation of implicatures targeting the speaker's epistemic state
-  \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit}. The
-  concluding Section~\ref{sec:conclusions} will come back to this in
-  more detail.}
+  \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit}. Section~\ref{sec:discussion-1}
+  will come back to this in more detail.}
 
@@
   the stronger alternative is true. (See also the discussion in
-  Section~\ref{sec:conclusions}.)}
+  Section~\ref{sec:discussion-1})}
 
@@
 \centering
-\subfloat[][\as-neutral]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.1,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
-                  ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,0) (2,0) (3,72) (4,1) (5,1) (6,0) (7,3)};
-
-        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,0) (6,0) (7,23)};
-
-        \legend{yes, no}
-
-      \end{axis}
-\end{tikzpicture}
-\label{fig:ReadingsAS-ntr}
-}
-\subfloat[][\es-neutral]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.2,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
-                  % ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,1) (2,4) (3,3) (4,0) (5,30)};
-
-        \addplot coordinates {(1,14) (2,0) (3,48) (4,2) (5,0)};
-
-        \legend{yes, no}
-
-      \end{axis}
-
-\end{tikzpicture}
-\label{fig:ReadingsES-ntr}
-}
-
-\subfloat[][\as-accented]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.1,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
-                  ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,0) (2,1) (3,69) (4,1) (5,2) (6,0) (7,4)};
-
-        \addplot coordinates {(1,0) (2,0) (3,1) (4,0) (5,0) (6,0) (7,23)};
-
-        \legend{yes, no}
-
-      \end{axis}
-
-\end{tikzpicture}
-\label{fig:ReadingsAS-acc}
-}
-\subfloat[][\es-accented]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.2,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
-                  % ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,0) (2,11) (3,9) (4,1) (5,23)};
-
-        \addplot coordinates {(1,0) (2,1) (3,50) (4,4) (5,1)};
-
-        \legend{yes, no}
-
-      \end{axis}
-
-\end{tikzpicture}
-\label{fig:ReadingsES-acc}
-}
-
-\caption{Positional judgments for the four target conditions. The
-  plots show rounded percentages of \emph{yes}/\emph{no} judgments
-  against the position within the trial. In the \as-conditions there
-  were seven positions. On the third position a \emph{yes} judgment
-  corresponded to a literal reading, while on the fifth position a
-  \emph{yes} judgment corresponded to a global reading.  A \emph{no}
-  judgment on the seventh position was only consistent with a local
-  reading. The \es-conditions had five positions. \emph{No} judgments
-  on positions two and three corresponded to global and literal
-  readings, respectively. A \emph{yes} judgment on the last segment
-  corresponded to a local reading.}
+
+\includegraphics[width=\textwidth]{positional_answers_critical.pdf}
+
+\caption{Positional judgments for the four target conditions. Bars
+  show the total number of \emph{yes} (up) and \emph{no} judgments
+  (down) against the position within a sequence. E.g., we recorded a
+  total of 84 \emph{yes} judgments at the third position in the
+  \as-sequence with neutral intonation, which corresponds to 84
+  answers that were classified as \emph{literal} answers. Notice that
+  the \as-condition has seven positions, the \es-condition only five.}
 \label{fig:JudgmentsK2}

### 2014-05-16 text/paper/paper4.tex
Section 5.1 included whole sequences

@@
 obtaining information about the relative preferences of the different
-readings. In addition, we wanted to minimize all effects of alleged
-typicality of pictures. To achieve this, we used an
-\mymark{incremental verification task} (\acro{ivt}), which is a
-modified version of picture verification \citep[see][]{Conroy2008}. The
-general idea is that subjects are requested to judge sentence material
-based on pictures that do not necessarily contain all the information
-necessary to judge a certain reading true or false. In that case,
-participants can demand that more information be
-revealed. Participants are instructed to make a truth-value judgment
-as soon as they are able to. When they do, the trial ends.
-
-\paragraph{Target Conditions.} In the present study, participants were
-presented with pictures depicting a set of four identical central
-elements (e.g., letters), which could be connected to surrounding
-elements (e.g., triangles). Initially, any potential connections
-between central and surrounding elements were covered by dark gray
-color (see Figure~\ref{fig:InitialPicture}).
-%
-\begin{figure}[t]  \centering
-      \fbox{\includegraphics[width=5cm]{../pictures/paper/ae_01_1.pdf}}
-      \caption{Initial picture presented to participants where all
-        possible connections from each letter to its surrounding
-        triangles are covered.}
-  \label{fig:InitialPicture}
+readings. In addition, we wanted to minimize potential picture
+typicality effects. To achieve this, we used an \mymark{incremental
+  verification task} (\acro{ivt}), which is a modified version of
+picture verification \citep[see][]{Conroy2008}. The general idea is
+that subjects are requested to judge sentence material based on
+pictures that do not necessarily contain all the information necessary
+to judge a certain reading true or false. In that case, participants
+can demand that more information be revealed. Participants are
+instructed to make a truth-value judgment as soon as they are able
+to. When they do, the trial ends.
+
+\paragraph{Target Conditions.} We present sequences of pictures
+depicting a set of four identical central elements (e.g., letters),
+which could be connected to surrounding elements (e.g., triangles), as
+shown in Figures~\ref{fig:exseqAS} and XYZ. Initially, any potential
+connections between central and surrounding elements were covered by
+dark gray color (see Figure~\ref{fig:exseqAS1}). Sentences to be
+judged were presented auditorily, and participants were asked to
+uncover the picture until they felt able to give a truth value
+judgment. Three options were available for participants at each step:
+(i) judge the sentence as true, (ii) judge the sentence as false,
+(iii) demand more information (unavailable when the picture was fully
+uncovered). Trials ended when a truth-value judgement was
+made. Importantly, each of the three potentially available readings
+corresponded to a specific step in the uncovering process where the
+truth value of that reading (and only of that reading) could be
+assessed for the first time. We refer to this step in the sequence as
+the {\it critical position} of a given reading. The critical position
+and the corresponding truth-value judgment differed between \as- and
+\es-sentences, as described presently. (This is, partly, because of
+the logical dependencies between readings, and, partly, also to rule
+out positional biases.)
+
+\begin{figure}[]
+	\centering
+	\subfloat[][Step 1]{ 
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_1.pdf}}
+	    \label{fig:exseqAS1}
+	}
+	\subfloat[][Step 2]{
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_2.pdf}}
+	    \label{fig:exseqAS2}
+	}
+	\subfloat[][Step 3 (\lit true)]{ 
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_3.pdf}}
+	    \label{fig:exseqAS3}
+	}
+        \\
+	\subfloat[][Step 4]{ 
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_4.pdf}}
+	    \label{fig:exseqAS4}
+	}
+	\subfloat[][Step 5 (\glb true)]{
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_5.pdf}}
+	    \label{fig:exseqAS5}
+	}
+	\subfloat[][Step 6]{ 
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_6.pdf}}
+	    \label{fig:exseqAS6}
+	}
+        \\
+	\subfloat[][Step 7 (\loc false)]{ 
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_7.pdf}}
+	    \label{fig:exseqAS7}
+	} 
+                \hspace*{7.85cm} 
+	\caption[]{Example picture sequence for \as-sentences.}
+	\label{fig:exseqAS}
 \end{figure}
-%
-Sentences to be judged 
-%were in German (see (\ref{ex:as}) and (\ref{ex:es}) below) and 
-were presented auditorily, and participants were asked to listen to a
-given sentence and then uncover the potential links step by step until
-they felt able to give a truth value judgment. Three options were
-available for participants at each step: (i) demand more information,
-(ii) judge the sentence as true, and (iii) judge the sentence as
-false. Trials ended with a truth-value judgement, and a judgement was
-required to end the trial when all connections had been
-revealed. Importantly, each of the three potentially available
-readings corresponded to a specific step in the uncovering process
-where the truth value of that reading (and only of that reading) could
-be assessed for the first time. We refer to this step in the sequence
-as the {\it critical position} of a given reading. The critical
-position and the corresponding truth-value judgment differed between
-\as- and \es-sentences, as described presently. (This is, partly,
-because of the logical dependencies between readings, and, partly,
-also to rule out positional biases.)
 
@@
 \end{exe}
-Figure~\ref{fig:exseqAS} shows the three corresponding critical
-positions for this sentence in the order of the uncovering
-process. First, the situation in Figure~\ref{fig:exseqAS1} becomes
-available, which is true under a literal reading, while the local and
-global readings cannot be evaluated yet. Second, in
-Figure~\ref{fig:exseqAS2}, the literal reading is still true, but now
-the global reading can be additionally confirmed by a \emph{true}
-response, as all the connections of one of the letters are now
-uncovered, and it is now clear that at least one of the letters is not
-connected to all of its triangles. Finally, decisions concerning the
-local reading are possible as soon as all connections have been
-uncovered. In this case, the critical position shown in
-Figure~\ref{fig:exseqAS3} is incompatible with a local reading: one of
-the central elements is linked to all of its surrounding elements,
-thus yielding \emph{false} answers if participants indeed adopted
-the local reading. Note that associating the final position with
-\emph{false} answers allows us to exclude both literal and global
-readings, which correspond to a \emph{true} answer at this
-position. In sum, \emph{true} or \emph{false} answers on particular
-positions in the incrementally revealed picture sequence can be mapped
-uniquely to candidate readings. All other \emph{true} or \emph{false}
-answers were counted as errors. The mapping between responses and
-readings is summarized in Table~\ref{tab:mappingAS}.
-
-\begin{figure}[t]
-	\centering
-	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/paper/ae_3_v_l.pdf}}
-	    \label{fig:exseqAS1}
-	}
-	\subfloat[][Step 2]{
-		\fbox{\includegraphics[width=3.5cm]{../pictures/paper/ae_5_v_l.pdf}}
-	    \label{fig:exseqAS2}
-	}
-	\subfloat[][Step 3]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/paper/ae_7_v_l.pdf}}
-	    \label{fig:exseqAS3}
-	}
-	\caption[]{Example sequence for \as-sentences}
-	\label{fig:exseqAS}
-\end{figure}
-
-\begin{table}[ht]
-	\centering
-	\subfloat[][\as-Sentences]{ 
-\begin{tabular}{cccc}
-&more info&true&false\\ \midrule
-Step 1&-&\lit&error\\
-Step 2&-&\glb&error\\
-Step 3&n.a.&error&\loc
-\end{tabular}
-
-	    \label{tab:mappingAS}
-	} \qquad
-	\subfloat[][\es-Sentences]{
-\begin{tabular}{cccc}
-&more info&true&false\\ \midrule
-Step 1&-&error&\glb\\
-Step 2&-&error&\lit\\
-Step 3&n.a.&\loc&error
-\end{tabular}
-	    \label{tab:mappingES}
-	}
-\caption{Mapping from response types to readings. Notice that on steps
-3 the option ``more info'' is not available because the whole picture
-has been revealed.}
-\label{tab:subfigureExample}
-\end{table}
-
-\es-sentences, due to the non-linear relationship of candidate
-readings described in Section~\ref{sec:get-know-your}, require a
-slightly different sequence of unfolding which yields a different
-order in which truth-value judgments can be made.
+Figure~\ref{fig:exseqAS} shows the corresponding picture sequence. The
+critical positions are on step 3, 5 and 7. Prior to step 3 there is
+not enough information to judge any candiate reading true or
+false. The situation at step 3 in Figure~\ref{fig:exseqAS3} is true
+under a literal reading, while the local and global readings cannot be
+evaluated yet. On step 5 in Figure~\ref{fig:exseqAS5} the literal
+reading is still true, but now also the global reading can be
+confirmed. Finally, decisions concerning the local reading are
+possible as soon as all connections have been uncovered at step 7 in
+Figure~\ref{fig:exseqAS7}. Note that the situation at step 7 is
+\emph{in}compatible with a local reading. This enables us to separate
+local readings, which would yield \emph{false} judgements at this
+position, from literal and global readings, which would yield
+\emph{true} judgements. In sum, \emph{true} or \emph{false} answers on
+particular positions in the incrementally revealed picture sequence
+can be mapped uniquely to candidate readings. All other \emph{true} or
+\emph{false} answers were counted as errors.
+
+\es-sentences, due to the non-linear relationship of readings
+described in Section~\ref{sec:get-know-your}, require a slightly
+different sequence of unfolding which yields a different order in
+which truth-value judgments can be made.
 %
@@
 	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=3cm]{../pictures/paper/ge_3_v_l.pdf}}
-	    \label{fig:subfig1}
-	}
-	\subfloat[][Step 2]{
-		\fbox{\includegraphics[width=3cm]{../pictures/paper/ge_4_v_l.pdf}}
-	    \label{fig:subfig2}
-	}
-	\subfloat[][Step 3]{ 
-		\fbox{\includegraphics[width=3cm]{../pictures/paper/ge_6_v_l.pdf}}
-	    \label{fig:subfig1}
-	}
-	\caption[]{Example sequence for \es-sentences}
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_1.pdf}}
+	    \label{fig:exseqES1}
+	}
+	\subfloat[][Step 2 (\glb false)]{
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_2.pdf}}
+	    \label{fig:exseqES2}
+	}
+	\subfloat[][Step 3 (\lit false)]{ 
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_3.pdf}}
+	    \label{fig:exseqES3}
+	}
+        \\
+	\subfloat[][Step 4]{ 
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_4.pdf}}
+	    \label{fig:exseqES4}
+	}
+	\subfloat[][Step 5 (\loc true)]{
+		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_5.pdf}}
+	    \label{fig:exseqES5}
+	}
+                \hspace*{3.9cm} 
+	\caption[]{Example sequence for \es-sentences.}
 	\label{fig:exseqES}
@@
 %
-For a sentence like (\ref{ex:es}) we obtain an unambiguous
-mapping between truth values and readings with respect to the sequence
-in \ref{fig:exseqES}.
+For a sentence like (\ref{ex:es}) we obtain an unambiguous mapping
+between truth judgements and readings with the sequence in
+\ref{fig:exseqES}.
 \begin{exe}
@@
 \end{exe}
-At the first critical position shown in Figure~\ref{fig:subfig1}, the
-global reading corresponds to a \emph{false} response, as one of the
-bells is already linked to all of its semicircles. The literal reading
-can be evaluated at the critical position shown in
-Figure~\ref{fig:subfig2}, where it would trigger a \emph{false}
-response, as there are two bells that are connected to at least some
-of their surrounding elements. Finally, confirming \ref{fig:subfig1}
-by a \emph{true} response corresponds to the local reading, as one of
-the bells is linked to some but not all of its semicircles, while all
-of the other bells are linked to all of them. Note that global and
-literal readings again differ from local readings with respect to
-their truth values. Mappings between responses and readings are
-summarized in Table \ref{tab:mappingES}.
+The critical positions are steps 2, 3 and 5. At step 2 in
+Figure~\ref{fig:exseqES2}, a global reading would yield a \emph{false}
+judgement. The literal reading can be evaluated at step 3 in
+Figure~\ref{fig:exseqES3}, where it would trigger a \emph{false}
+judgement. Finally, confirming \ref{fig:exseqES5} by a \emph{true}
+response indicates a local reading. Note that global and literal
+readings again differ from local readings with respect to their truth
+values.
 
@@
 
-\begin{table}[!hp]
+\begin{table}[hp]
   \centering

### 2014-05-16 text/paper/paper4.tex
Section 5.4 reworked

@@
 Figure~\ref{fig:exseqAS} shows the corresponding picture sequence. The
-critical positions are on step 3, 5 and 7. Prior to step 3 there is
-not enough information to judge any candiate reading true or
-false. The situation at step 3 in Figure~\ref{fig:exseqAS3} is true
-under a literal reading, while the local and global readings cannot be
-evaluated yet. On step 5 in Figure~\ref{fig:exseqAS5} the literal
-reading is still true, but now also the global reading can be
-confirmed. Finally, decisions concerning the local reading are
-possible as soon as all connections have been uncovered at step 7 in
-Figure~\ref{fig:exseqAS7}. Note that the situation at step 7 is
-\emph{in}compatible with a local reading. This enables us to separate
-local readings, which would yield \emph{false} judgements at this
-position, from literal and global readings, which would yield
-\emph{true} judgements. In sum, \emph{true} or \emph{false} answers on
-particular positions in the incrementally revealed picture sequence
-can be mapped uniquely to candidate readings. All other \emph{true} or
-\emph{false} answers were counted as errors.
+critical positions are on step 3, 5 and 7. Pictures that were
+interspersed between these positions served as
+spillover-pictures. These were used in order to control for
+potentially delayed judgments and they additionally served as
+distractor items. Prior to step 3 there is not enough information to
+judge any candiate reading true or false. The situation at step 3 in
+Figure~\ref{fig:exseqAS3} is true under a literal reading, while the
+local and global readings cannot be evaluated yet. On step 5 in
+Figure~\ref{fig:exseqAS5} the literal reading is still true, but now
+also the global reading can be confirmed. Finally, decisions
+concerning the local reading are possible as soon as all connections
+have been uncovered at step 7 in Figure~\ref{fig:exseqAS7}. Note that
+the situation at step 7 is \emph{in}compatible with a local
+reading. This enables us to separate local readings, which would yield
+\emph{false} judgements at this position, from literal and global
+readings, which would yield \emph{true} judgements. In sum,
+\emph{true} or \emph{false} answers on particular positions in the
+incrementally revealed picture sequence can be mapped uniquely to
+candidate readings. All other \emph{true} or \emph{false} answers were
+counted as errors.
 
@@
 
-\paragraph{Positional controls.} In order to make sure that subjects
-understood the task, i.e., gave truth-value judgements at the first
-possible position in a sequence, we included a set of control
-conditions. These also controlled for response biases. For each of the
-three readings in the \as- and \es-conditions, we constructed an
-unambiguous control sentence as in (\ref{bsp:controls-as}) and
-(\ref{bsp:controls-es}), requiring the same judgement at the identical
-position in the same sequence used for the respective targets. For
-instance, example (\ref{bsp:controls-as-1}) requires a
-\emph{true}-response analogous to the \as-sentence in (\ref{ex:as})
-under its literal reading, (\ref{bsp:controls-as-2}) corresponds to
+\paragraph{Positional controls.} To make sure that subjects understood
+the task, i.e., gave truth-value judgements at the first possible
+position in a sequence, we included a set of control conditions. These
+also controlled for response biases. For each of the three readings in
+the \as- and \es-conditions, we constructed an unambiguous control
+sentence as in (\ref{bsp:controls-as}) and (\ref{bsp:controls-es}),
+requiring the same judgement at the identical position in the same
+sequence used for the respective targets. For instance, example
+(\ref{bsp:controls-as-1}) requires a \emph{true}-response analogous to
+the \as-sentence in (\ref{ex:as}) under its literal reading at step 3
+in Figure~\ref{fig:exseqAS3}, (\ref{bsp:controls-as-2}) corresponds to
 the \as-sentence under its global reading and
@@
 readings always require local readings to be evaluated at the end of a
-sequence. It could thus in principle be possible that no subject ever
-reaches this point, because they gave truth-value judgements earlier,
+sequence. It could thus in principle be possible that subjects never
+reach this point, because they give truth-value judgements earlier,
 thereby ending the trial. In that case it would be unclear if these
@@
 preceding hosts. For instance, in (\ref{bsp:target-related}), the
-\acro{pp} \emph{with suns} can be attached to the preceding
-noun \emph{squares}, resulting in the so-called \emph{late-closure} or
-\emph{low-attachment} reading
-((\ref{bsp:target-related-LC}). Alternatively, the \acro{pp} can be
-attached to the whole conjoined \acro{np} \emph{circles and squares},
-corresponding to the \emph{early-closure} or \emph{high-attachment}
-reading (\ref{bsp:target-related-EC}).  Late-closure readings have
-been observed to be preferred over the early-closure reading for
-sentences comparable to those in (\ref{bsp:target-related})
-\citep[e.g.][]{Frazier87,Frazier82}.
-
-For each such sentence, two sequences were designed. In the first one, the
-critical position associated with the dispreferred early-closure
-reading preceded the critical position for the preferred late-closure
-reading. In this case, a partly covered picture as in
-Figure~\ref{fig:exec1} preceded a picture as in \ref{fig:exec2}.
+\acro{pp} \emph{with suns} can be attached to the preceding noun
+\emph{squares}, resulting in the so-called \emph{late-closure} (\lc)
+reading ((\ref{bsp:target-related-LC}). Alternatively, the \acro{pp}
+can be attached to the whole conjoined \acro{np} \emph{circles and
+  squares}, corresponding to the \emph{early-closure} (\ec) reading
+(\ref{bsp:target-related-EC}).  \lc-readings have been observed to be
+preferred over \ec-readings for sentences comparable to those in
+(\ref{bsp:target-related}) \citep[e.g.][]{Frazier87,Frazier82}.
+
+For each such sentence, two sequences were designed: one in which the
+preferred \lc-reading could be judged first (Figure~\ref{fig:exlc}),
 %
-\begin{figure}[t]
+\begin{figure}[]
 	\centering
-	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/ec_01_3.pdf}}
+	\subfloat[][Step 2]{ 
+		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_2.pdf}}
+	    \label{fig:exlc2}
+	}
+	\subfloat[][Step 3 (\lc true)]{
+		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_3.pdf}}
+	    \label{fig:exlc3}
+	}
+        \\
+	\subfloat[][Step 4]{
+		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_4.pdf}}
+	    \label{fig:exlc4}
+	}
+	\subfloat[][Step 5 (\lc true)]{
+		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_5.pdf}}
+	    \label{fig:exlc5}
+	}
+        \\
+	\subfloat[][Step 6 (\ec false)]{
+		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_6.pdf}}
+	    \label{fig:exlc6}
+	}
+	\subfloat[][Step 7 (\lc true)]{
+		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_7.pdf}}
+	    \label{fig:exlc7}
+	}
+	\caption[]{Example of an \lc-sequence for sentence
+          (\ref{bsp:target-related}) where the \lc-reading
+          (\ref{bsp:target-related-LC}) can be judged first. The first
+          step where all connections are covered is omitted.}
+	\label{fig:exlc}
+\end{figure}
+%
+and another in which the dispreferred \ec-reading could be judged
+first (Figure~\ref{fig:exec}).
+%
+\begin{figure}[]
+	\centering
+	\subfloat[][Step 2]{ 
+		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_2.pdf}}
 	    \label{fig:exec1}
 	}
-	\subfloat[][Step 2]{
-		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/ec_01_5.pdf}}
+	\subfloat[][Step 3 (\ec false)]{
+		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_3.pdf}}
 	    \label{fig:exec2}
 	}
-	\caption[]{Critical steps of a sequence for sentence
-          (\ref{bsp:target-related}) where the early-closure reading
-          (\ref{bsp:target-related-EC}) can be judged first.}
+        \\
+	\subfloat[][Step 4]{
+		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_4.pdf}}
+	    \label{fig:exec2}
+	}
+	\subfloat[][Step 5 (\lc true)]{
+		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_5.pdf}}
+	    \label{fig:exec2}
+	}
+	\caption[]{Example of an \ec-sequence for sentence
+          (\ref{bsp:target-related}) where the \ec-reading
+          (\ref{bsp:target-related-EC}) can be judged first. The first
+          step where all connections are covered is omitted.}
 	\label{fig:exec}
@@
 %
-If participants adopted an early-closure reading as in
-(\ref{bsp:target-related-EC}), a \emph{false}-judgment would be
-expected at the position illustrated in \ref{fig:exec1}, as none of
-the circles connected to the letter contain any suns. Under the
-late-closure reading in (\ref{bsp:target-related-LC}), in contrast, a
-\emph{true}-response would be expected no sooner than in the step
-shown in Figure~\ref{fig:exec2}. The order of possible judgements is
-reversed in the second kind of sequence including pictures like
-\ref{fig:exlc1} followed by pictures like \ref{fig:exlc2}. Here, the
-late-closure reading in (\ref{bsp:target-related-LC}) can be judged
-first requiring a \emph{true}-response on \ref{fig:exlc1}. The
-early-closure reading in (\ref{bsp:target-related-EC}) can only be
-judged later in the sequence. When we reach \ref{fig:exlc2} a
-\emph{false}-response is expected under an
-early-closure/high-attachment reading.
-
 We also tested structurally disambiguated versions like
-(\ref{bsp:target-related2}), one for each sentence type, for proper
-comparison.
+(\ref{bsp:target-related2}), one for each sentence type, on each
+sequence type for proper comparison.
 
@@
 \end{exe}
-
-\begin{figure}[t]
-	\centering
-	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/lc_01_3.pdf}}
-	    \label{fig:exlc1}
-	}
-	\subfloat[][Step 2]{
-		\fbox{\includegraphics[width=5.5cm]{../pictures/paper/lc_01_6.pdf}}
-	    \label{fig:exlc2}
-	}
-	\caption[]{Critical steps of a sequence for sentence
-          (\ref{bsp:target-related}) where the late-closure reading
-          (\ref{bsp:target-related-LC}) can be judged first.}
-	\label{fig:exlc}
-\end{figure}
 
@@
 Preference-related controls also differed prosodically. Modifier
-attachment ambiguities comparable to the examples in
-(\ref{bsp:target-related}) and (\ref{bsp:target-related2}) have been
-shown to be sensitive to differences in prosodic phrasing. Though
-there has been discussion as to whether speakers reliably
-\textit{produce} disambiguating cues in such constructions
-\citep[e.g.][]{Allbritton96,Kraljik05, Snedeker03, Schafer00}, overt
-prosodic boundaries are generally acknowledged to guide interpretive
-processes of late-closure sentences in \textit{comprehension}
-\citep[e.g.][]{Steinhauer99, Augurzky06}.  Specifically, it has been
-shown that prosodically separating a modifier from the directly
-preceding material supports an early-closure reading, whereas
-separating the two potential attachment sites is supportive of a late
-closure reading. Thus, a phrase boundary between {\it squares} and
-{\it with} in (\ref{bsp:target-related}) corresponds to a
-high-attachment reading, whereas a prosodic phrase boundary following
-{\it circles} corresponds to a low-attachment reading.
+attachment ambiguities have been shown to be sensitive to differences
+in prosodic phrasing. Though there has been discussion as to whether
+speakers reliably \textit{produce} disambiguating cues in such
+constructions \citep[e.g.][]{Allbritton96,Kraljik05, Snedeker03,
+  Schafer00}, overt prosodic boundaries are generally acknowledged to
+guide interpretive processes of late-closure sentences in
+\textit{comprehension} \citep[e.g.][]{Steinhauer99, Augurzky06}.
+Specifically, it has been shown that prosodically separating a
+modifier from the directly preceding material supports an \ec-reading,
+whereas separating the two potential attachment sites is supportive of
+an \lc-reading. Thus, a phrase boundary between {\it squares} and {\it
+  with} in (\ref{bsp:target-related}) corresponds to an \ec-reading,
+whereas a prosodic phrase boundary following {\it circles} corresponds
+to an \lc-reading.
 
@@
 we also presented unambiguous sentences corresponding to the
-early-closure reading. As in the case of the \as- and \es-sentences,
+\ec-reading. As in the case of the \as- and \es-sentences,
 the unambiguous counterparts served as a baseline to control for
@@
 Each experimental trial proceeded as described above. The sentence was
-presented using active PC loud speakers and the picture materials were
+presented using active PC loudspeakers and the picture materials were
 presented on a computer screen. Participants responded using the
@@
 sentence (up to three times), (ii) request additional pictorial
-information, (iii) respond "yes, fits" or (iv) "no, does not
-fit". At the beginning of an experimental session participants
-received written instructions on their task. Then they completed an
-interactive training consisting of 15 trials in which they were
-familiarized with the task.  After the training the actual experiment
+information, (iii) respond "yes, fits" or (iv) "no, does not fit". At
+the beginning of an experimental session participants received written
+instructions on their task. Then they completed an interactive
+training consisting of 15 trials in which they were familiarized with
+the task.  After the training the actual experiment
 started. Participants were tested individually in a silent room. Each
-session was divided into three blocks and participants were told they
-could take breaks between blocks. In total, an experimental session
-took about one hour. At the end of the session participants received 8
-euros compensation.
+session was divided into three blocks and participants were told that
+they could take breaks between blocks. In total, an experimental
+session took about one hour. At the end of the session participants
+received 8 euros compensation.
 
@@
 respectively, analogous to the examples in (\ref{ex:as}) and
-(\ref{ex:es}). Sentences were introduced by a subject {\acro{dp}}, including the quantifiers {\it alle diese} ("all of
-these") or {\it genau eine(r) der} ("exactly one of these"), as well
-as the head noun which denoted different icons, such as letters or
-bells. Subjects were followed by an auxiliary, and a {
-  \acro{pp}} containing {\it einige}, a possessive pronoun, and a noun
-denoting a geometrical object, e.g., {\it einigen seiner
-  Dreiecke/Quadrate} ("some of its triangles/squares"). The possessive
-pronoun was used in order to fix relative quantifier scope to surface
-scope, thus ensuring that {\it einige} has embedded status. The last
-word was the main verb {\it verbunden} ("connected").  Each sentence
-was recorded in a stressed and an unstressed version of scalar {\it
-  einige}. As described above, three control
-sentences were created for each experimental item, corresponding to
-the critical positions in the course of uncovering the accompanying
-sequences.  The positional controls were recorded with
-neutral prosody.  Items were evenly distributed across 5 lists using a
-Latin square design.
+(\ref{ex:es}). Sentences were introduced by a subject {\acro{dp}},
+including the quantifiers {\it alle diese} ("all of these") or {\it
+  genau eine(r) der} ("exactly one of these"), as well as the head
+noun which denoted different icons, such as letters or bells. Subjects
+were followed by an auxiliary, and a \acro{pp} containing {\it
+  einige}, a possessive pronoun, and a noun denoting a geometrical
+object, e.g., {\it einigen seiner Dreiecke/Quadrate} ("some of its
+triangles/squares"). The possessive pronoun was used in order to fix
+relative quantifier scope to surface scope, thus ensuring that {\it
+  einige} has embedded status. The last word was the main verb {\it
+  verbunden} ("connected").  Each sentence was recorded in a stressed
+and an unstressed version of scalar {\it einige}. As described above,
+three control sentences were created for each experimental item,
+corresponding to the critical positions in the course of uncovering
+the accompanying sequences.  The positional controls were recorded
+with neutral prosody.  Items were evenly distributed across 5 lists
+using a Latin square design.
 
@@
 For controlling preferences, 28 sentences that were ambiguous between
-a late-closure and an early-closure reading, as well as 28 of their
+a \lc and an \ec-reading, as well as 28 of their
 disambiguated counterparts were constructed as described above. In
-these sentences, subject \acros{dp} were always denoting
-icons and were followed by an auxiliary. In the ambiguous sentences,
-the auxiliary was followed by two {\it mit}-\acros{pp}.  The
-first of these \acros{pp} consisted in a coordination of two
-nouns denoting geometrical objects, whereas the second PP denoted
-icons. In contrast to these sentences, the unambiguous sentences
-contained only one PP with a conjunction the first part of which was
-modified by a relative clause.
+these sentences, subject \acros{dp} were always denoting icons and
+were followed by an auxiliary. In the ambiguous sentences, the
+auxiliary was followed by two {\it mit}-\acros{pp}.  The first of
+these \acros{pp} consisted in a coordination of two nouns denoting
+geometrical objects, whereas the second \acro{pp} denoted icons. In
+contrast to these sentences, the unambiguous sentences contained only
+one \acro{pp} with a conjunction the first part of which was modified
+by a relative clause.
 
@@
 
-In contrast to the accent manipulation, the ambiguous preference-related controls
-differed with respect to prosodic phrasing. Prosodic phrase boundaries
-in German are realized by a rise in F0 as well as by a durational
-increase on the final part of the constituent preceding the boundary
-(prefinal lengthening) plus an optional pause \citep[e.g.][]{Vaissiere83,Fery93}.
-Boundaries for these control sentences were either realized at the position 
-separating the second {\small \acro{PP}}
-from the preceding material (\emph{late boundary}, corresponding to a
-high-attachment reading) or directly preceding the second conjunct in
-the first {\small \acro{PP}} (\emph{early boundary}, corresponding to a
-low-attachment reading). As the prosodic realization of the targets
-involved the comparison between an accented and a neutral variant, we
-also included a third version of the ambiguous preference-related controls, in which our
-speaker produced the sentences without any pronounced
-boundaries. For each prosodic variant, a set of
-30 items was read, yielding 90 preference-related fillers.
-
-Altogether a total number of 300 sentences consisting of 60 target sentences, 90 ambiguous preference-related controls, 30 unambiguous preference-related controls, 90 positional control sentences and 30 unrelated fillers was recorded.
-The session was recorded in an acoustically
-shielded booth (44.1\,kHz sampling rate, 16 bit amplitude resolution).
+In contrast to the accent manipulation, the ambiguous
+preference-related controls differed with respect to prosodic
+phrasing. Prosodic phrase boundaries in German are realized by a rise
+in F0 as well as by a durational increase on the final part of the
+constituent preceding the boundary (prefinal lengthening) plus an
+optional pause \citep[e.g.][]{Vaissiere83,Fery93}.  Boundaries for
+these control sentences were either realized at the position
+separating the second \acro{pp} from the preceding material
+(\emph{late boundary}, corresponding to an \ec-reading) or directly
+preceding the second conjunct in the first \acro{pp} (\emph{early
+  boundary}, corresponding to an \lc-reading). As the prosodic
+realization of the targets involved the comparison between an accented
+and a neutral variant, we also included a third version of the
+ambiguous preference-related controls without any pronounced
+boundaries. For each prosodic variant, a set of 30 items was read,
+yielding 90 preference-related controls.
+
+Altogether a total number of 300 sentences consisting of 60 target
+sentences, 90 ambiguous preference-related controls, 30 unambiguous
+preference-related controls, 90 positional control sentences and 30
+unrelated fillers was recorded. The session was recorded in an
+acoustically shielded booth (44.1\,kHz sampling rate, 16 bit amplitude
+resolution).
 
@@
 
-\begin{figure}[t]
+\begin{figure}[]
 	\centering
@@
 
-Figure~\ref{fig:duration_targets} shows the durational values 
-for each of the single regions in the sentence. 
-Though descriptively small, the duration of accented determiners 
-was significantly increased as opposed to their non-accented counterparts 
-(effects on
-the determiner: \acro{Quantifier}: \emph{F}=31.4; \emph{p}<.001;
-\acro{Prosody}: \emph{F}=23.8; \emph{p}<.001).
-
-\begin{figure}[t]
+\begin{figure}[]
 	\centering
@@
     ymin = 0,
-    y = 0.15,
+    y = 0.125,
     x tick label style = {rotate = 50, anchor = east},
@@
 
+Figure~\ref{fig:duration_targets} shows the durational values 
+for each of the single regions in the sentence. 
+Though descriptively small, the duration of accented determiners 
+was significantly increased as opposed to their non-accented counterparts 
+(effects on
+the determiner: \acro{Quantifier}: \emph{F}=31.4; \emph{p}<.001;
+\acro{Prosody}: \emph{F}=23.8; \emph{p}<.001).
+
 A list of the statistical results of each sentential region is provided in 
@@
     ymin = 0,
-    y = 0.5,
+    y = 0.55,
     x tick label style = {rotate = 50, anchor = east},
@@
 realizations (\emph{neutral} vs. (\emph{early boundary}
-vs. (\emph{late boundary}) differ significantly from each other
+vs. (\emph{late boundary})) differ significantly from each other
 (effect of \acro{Prosody}: \emph{F}=129.3; \emph{p}<.001; all single
@@
 reach significance (\emph{p}>.2). Finally, durational analyses on
-reveal that all prosodic realizations (neutral vs. (\emph{early
-  boundary} vs. (\emph{late boundary}) differ significantly from each
+reveal that all prosodic realizations (\emph{neutral} vs. (\emph{early
+  boundary} vs. (\emph{late boundary})) differ significantly from each
 other (Region 5: effect of \acro{Prosody}: \emph{F}=819.5;
@@
 The visual sequences accompanying each sentence consisted of pictures
-like in Figures~\ref{fig:InitialPicture}--\ref{fig:exlc}. In each
-picture, four alternative sub-scenarios were presented, in which an
-icon was surrounded by six geometrical shapes. Depending on the
-sentence material, shapes and icons differed across sentence types and
+like in Figures~\ref{fig:exseqAS}--\ref{fig:exlc}. In each picture,
+four alternative sub-scenarios were presented, in which an icon was
+surrounded by six geometrical shapes. Depending on the sentence
+material, shapes and icons differed across sentence types and
 conditions. For example, in our target conditions, 4 identical icons
@@
 whereas various icons and surrounding elements were used in each
-sequence of the preference-related control structures. Grey colour
-initially covered the links between icons and shapes. As the
-connections were to be uncovered step by step, different pictures were
-designed corresponding to different stages in the uncovering
-process. Inherent entailment relations between \as-sentences and
-\es-sentences lead to different critical positions at which
-participants can make their judgments. We will therefore describe the
-sequences for each condition separately.
-
-For \as-sentences, as well as for the corresponding positional control
-sentences described in Section \ref{sec:design}, we designed a set of
-seven pictures for each trial. In each sequence, the critical position
-associated with the literal meaning was presented at the third step,
-the position associated with the global meaning was shown at the fifth
-step, and the local reading was presented at the final step (see
-Figure \ref{fig:exseqAS} for an illustration of the critical
-positions). Pictures that were interspersed between these positions
-served as spillover-pictures. These were used in order to control for
-potentially delayed judgments and they additionally served as
-distractor items.
-
-Sequences in the \es conditions (and their respective positional
-controls) consisted of a set of five pictures with the following
-critical positions. The critical positions (Figure \ref{fig:exseqES})
-are associated with the second picture (global reading), the third
-picture (literal reading), as well as with the final picture (local
-reading).
-
-For the preference-related controls, we used two types of
-sequences. First, a sequence in which the crirical position for the
-(preferred) late-closure reading was presented preceding the critical
-position for the early-closure reading (\LC-sequence), and second, a
-sequence in which the readings were presented in reversed order
-(\EC-sequence). In the \LC-sequences, seven pictures were presented,
-with the \LC-reading given at the third picture, and the \EC- reading
-at the sixth picture. \EC-sequences consisted of five pictures, in
-which the critical positions were realized at the third picture
-(\EC-reading) and at the fifth picture (\LC-reading).
-
-Finally, we added pictures compatible with unrelated fillers with
-critical position at random uncovering stages, including cases where
-no uncovering was needed for a truth-value judgement.
+sequence of the preference-related control structures (see
+Section~\ref{sec:design} for more detailed exposition). Pictures for
+unrelated fillers had critical positions at random uncovering stages,
+including cases where no uncovering was needed for a truth-value
+judgement.
 

### 2014-05-20 text/paper/paper4.tex

@@
 
-Forty native speakers of German took part in our study, none of which had
-any prior exposure to logic or formal semantics. We excluded three
-participants due to insufficient performance on controls ($\le 50\%$
+Forty native speakers of German took part in our study, none of which
+had any prior exposure to logic or formal semantics. We excluded two
+participant due to insufficient performance on controls ($\le 60\%$
 correct answers).
@@
 preference-related controls separately. After providing the
-descriptive results, we present statistical analyses, which were
-carried out in the following manner.  We computed log-linear models
-(see SCHEEPERS 2003 ????) in two variants (by item and by participant). In
-the first, the factor {\it Item} was included, and in the second
-analysis, the factor {\it Participants} was included. Inclusion of
-these two factors allowed us to test whether the distribution of
-participants' choices was identical accros items and participants. We
-report log-likelihood ratio Chi-squares ($LRCS_1$ and $LRCS_2$),
-degrees of freedom ($df_1$, $df_2$) and significance levels ($p_1$ and
-$p_2$). The relevant experimental factors are provided in the specific
-subsections below.
+descriptive results, we present statistical analyses using log-linear
+models (i.e., generalized linear regression for count data). To
+complement the picture, we also provide a Bayesian analysis that
+probes specifically into the preference relations between candidate
+readings.
 
 \paragraph{Target conditions and positional controls.}
-Performance on positional controls was overwhelmingly correct (92\% correct responses on
-average) indicating that participants understood the task and were able to give
-correct truth-value judgments at the adequate point in a sequence. 
-In general, they were not affected by inessential features of the picture materials
-or general response biases.
-
-The judgments obtained for the four target conditions are depicted in
+Performance on positional controls was overwhelmingly correct (90\%
+correct responses on average with a variance of 0.012) indicating that
+participants understood the task and were able to give correct
+truth-value judgments at the adequate point in a sequence. In
+general, they were not affected by inessential features of the picture
+materials or general response biases.
+
+The answers obtained for the four target conditions are depicted in
 Figure \ref{fig:JudgmentsK2}.
@@
 
-\includegraphics[width=\textwidth]{positional_answers_critical.pdf}
+\includegraphics[width=0.9\textwidth]{positional_answers_critical.pdf}
 
@@
   (down) against the position within a sequence. E.g., we recorded a
-  total of 84 \emph{yes} judgments at the third position in the
-  \as-sequence with neutral intonation, which corresponds to 84
+  total of 103 \emph{yes} judgments at the third position in the
+  \as-sequence with neutral intonation, which corresponds to 103
   answers that were classified as \emph{literal} answers. Notice that
@@
 %
-We coded the judgments as {\it literal}, {\it global} or {\it local}
+We coded these answers as {\it literal}, {\it global} or {\it local}
 if they were as expected under one of these readings and as {\it
   error} if not. The distribution of readings thus coded is presented
-in Figure~\ref{fig:JudgementPercentages}.
+in Table~\ref{tab:CC-ContingencyTable}. The table also classifies
+responses according to the position (1--3) in the experiment, i.e.,
+whether it was the first, second or third time that a participant saw
+the critical condition in question.
 %
-\begin{figure}[t]
+\begin{table}[h]
 \centering
-\subfloat[][\as-condition]{
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.5,
-                  enlarge y limits=0.25,
-                  legend style={at={(0.5,-0.15)}, anchor=north, legend columns=-1},
-        ylabel={\% of answers (rounded)}, symbolic x
-        coords={neutral,accented}, xtick=data, nodes
-        near coords, nodes near coords align={vertical},x=65, bar
-        width=3mm, ymin = 8, ymax = 73 ]
-
-        \addplot coordinates {(neutral,73) (accented,70)};
-
-        \addplot coordinates {(neutral,23) (accented,22)};
-
-        \addplot coordinates {(neutral,1) (accented,2)};
-
-        \addplot coordinates {(neutral,4) (accented,6)};
-
-        % \addplot coordinates {(ae-ntr,83) (ae-acc,80) (ge-ntr,53)
-        % (ge-acc,56)};
-
-        % \addplot coordinates {(ae-ntr,26) (ae-acc,25) (ge-ntr,33)
-        % (ge-acc,26)};
-
-        % \addplot coordinates {(ae-ntr,1) (ae-acc,2) (ge-ntr,0)
-        % (ge-acc,1)};
-
-        % \addplot coordinates {(ae-ntr,4) (ae-acc,7) (ge-ntr,28)
-        % (ge-acc,31)};
-
-        \legend{literal, local, global, error}
-
-      \end{axis}
-
-    \end{tikzpicture}
-
-% \includegraphics[width=5cm]{../pictures/paper/ReadingsAE.pdf}
-\label{fig:JudgementPercentagesAE}
-}
-\subfloat[][\es-condition]{
-\begin{tikzpicture}[scale=0.75]
-
-  \begin{axis}[ybar, 
-               enlarge x limits=0.5,
-               enlarge y limits=0.25, 
-               legend style={at={(0.5,-0.15)},
-                 anchor=north,
-                 legend columns=-1}, 
-               % ylabel={\% of answers}, 
-               symbolic x coords={neutral,accented}, 
-               xtick=data,
-               nodes near coords,
-               nodes near coords align={vertical},
-               x=65, bar width=3mm,
-               ymin = 8, ymax = 73
-               ]
-
-    \addplot coordinates {(neutral,47) (accented,49)};
-
-    \addplot coordinates {(neutral,29) (accented,23)};
-
-    \addplot coordinates {(neutral,0) (accented,1)};
-
-    \addplot coordinates {(neutral,25) (accented,27)};
-
-    % \addplot coordinates {(ae-ntr,83) (ae-acc,80) (ge-ntr,53) (ge-acc,56)};
-
-    % \addplot coordinates {(ae-ntr,26) (ae-acc,25) (ge-ntr,33) (ge-acc,26)};
-
-    % \addplot coordinates {(ae-ntr,1) (ae-acc,2) (ge-ntr,0) (ge-acc,1)};
-
-    % \addplot coordinates {(ae-ntr,4) (ae-acc,7) (ge-ntr,28) (ge-acc,31)};
-
-    \legend{literal, local, global, error}
-
-  \end{axis}
-
-\end{tikzpicture}
-
-% \includegraphics[width=5cm]{../pictures/paper/ReadingsGE.pdf}
-\label{fig:JudgementPercentagesGE}
-}
-\caption[Optional caption for list of figures]{Response type
-  frequencies for target conditions}
-\label{fig:JudgementPercentages}
+
+\begin{tabular}{lccccc}
+  condition & position & \multicolumn{4}{c}{response type} \\ \cmidrule(r){3-6}
+  && \emph{literal} & \emph{local} & \emph{global} & \emph{error} \\
+  \midrule \addlinespace[0.15cm]
+  \textbf{\as neutral} 
+  & Pos 1 & 35 &  0 & 0 & 3 \\
+  & Pos 2 & 35 &  1 & 0 & 2 \\
+  & Pos 3 & 33 &  2 & 0 & 3 \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{103} &  \textbf{3} & \textbf{0} &
+  \textbf{8} \\
+  \addlinespace[0.25cm]
+  \textbf{\as accented} 
+  & Pos 1 & 33 &  2 & 1 & 2 \\
+  & Pos 2 & 33 &  3 & 1 & 1 \\
+  & Pos 3 & 33 &  3 & 0 & 2 \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2} &
+  \textbf{5} \\
+  \addlinespace[0.25cm]
+  \textbf{\es neutral} 
+  & Pos 1 & 26 &  5 & 0 & 7 \\
+  & Pos 2 & 26 &  3 & 0 & 9 \\
+  & Pos 3 & 26 &  6 & 0 & 6 \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{78} &  \textbf{14} & \textbf{0} &
+  \textbf{22} \\
+  \addlinespace[0.25cm]
+  \textbf{\es accented} 
+  & Pos 1 & 26 &  6 & 0 & 6 \\
+  & Pos 2 & 24 &  5 & 0 & 9 \\
+  & Pos 3 & 28 &  5 & 0 & 5 \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{78} &  \textbf{16} & \textbf{0} &
+  \textbf{20}
+\end{tabular}
+
+\caption{Contingency table of classified responses for the critical
+  conditions. The factor position encodes whether participants saw the
+  condition in question for the first, second or third time during the
+  whole experiment.}
+\label{tab:CC-ContingencyTable}
+\end{table}
+%
+The majority of answers are indicative of a literal reading (90.35\% /
+86.84\% in neutral / accented \as-conditions, and 68.42\% in both
+neutral / accented \es-conditions). Only two answers across all
+critical conditions fall into the category indicative of global
+readings. Judgements indicative of local readings, on the other hand,
+are more frequent (2.63\% / 7.02\% for neutral / accented
+\as-conditions, and 12.28\% / 14.04\% for neutral / accented
+\es-conditions).
+
+The number of responses that fell out of our classification scheme
+differs substantially between \as- and \es-conditions. There are
+7.02\% / 4.39\% unclassifiable judgements in the neutral / accented
+\as-conditions, but 19.30\% / 17.54\% 'error' in the neutral /
+accented \es-conditions. A look at Figure~\ref{fig:JudgmentsK2}
+reveals that there is some systematicity in 'error' answers. Most
+answers that we classified as 'errors' are plausibly explained as a
+few random errors, a handful of mistakes resulting from confusing
+buttons for \emph{true} and \emph{false} and a few 'spill-overs' where
+participants gave responses one position too late. There is one
+notable exception, though. A substantial number of \emph{true}
+responses where given at the second position of \es-sequences (9.65\%
+/ 8.77\%) which is shown in Figure~\ref{fig:exseqES2}. Although this
+position in the sequence is the critical position to reveal a global
+reading, the latter would be indicated by a \emph{false} response. It
+appears that subjects read \es-sentences as if the non-monotonic
+quantifier \emph{exactly one} was a non-monotonic \emph{at least one},
+without pragmatic enrichment of \emph{some}. 16 out of the total 21
+answers in this category come from 5 subjects, while the remaining 5
+were single answers by 5 different subjects. \todo{subjects 1, 9, 12,
+  21, 84} This suggests that at least for some subjects non-monotonic
+quantifiers were problematic. \todo{how to deal with this in the future?}
+
+We fitted generalized linear models to the contingency table data in
+Table~\ref{tab:CC-ContingencyTable}, using factors \textsc{Condition}
+with levels \as and \es, \textsc{Accent} with levels \emph{neutral}
+and \emph{accented}, and \textsc{Position} with levels 1 through 3 to
+predict the dependent factor \emph{Response} with levels
+\emph{literal}, \emph{local}, and \emph{other}. The latter levels
+lumps \emph{global} and \emph{error} responses together, because
+otherwise we would not have enough cell counts to apply log-linear
+regression. We selected the ``best'' predictor of the data by a
+gradient search over hierarchical models in terms of AICs, starting
+from the saturated model. The best model takes main factors
+\textsc{Response} and \textsc{Condition} into account, as well as the
+interaction term \textsc{Response:Condition} ($\chi^2 = 17.19$,
+$df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$ of the
+saturated model)). Crucially, factors \textsc{Position} and
+\emph{Accent} are spurious in the best model. This suggests that
+response patterns only depend on the type of the sentence, but that
+there were no learning or fatigation effects and that accentuation did
+not influence answer patterns significantly.
+
+In order to test whether there is support for the postulation of local
+readings, we compared the previous ``best'' model to a model that only
+differs from the former in that it subsumes the level \emph{local} of
+factor \textsc{Reading} under level \emph{other} as well
+\citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model comparison
+reveals that there is no significant improvement in explanatory power
+($Pr(|\chi|) = 0.2689$) of the more complex model that includes the
+level \emph{local} (df=30, residual deviance = 9.76) over the leaner
+model without this level (df=32, residual deviance = 12.39,
+AIC=156.63). This means that our data does not provide strong evidence
+for the maintenance of belief in \emph{local} readings in our
+setting. (Subsequent analysis will shed more light on this.)
+
+\paragraph{Preference-related controls.} Positional answers for our
+preference-related control conditions are shown in
+Figure~\ref{Fig:TF_judgments}.
+%
+\begin{figure}[]
+\centering
+
+ \subfloat[][\LC-sequence]{
+
+\includegraphics[width=0.9\textwidth]{positional_answers_TF_LC.pdf}
+}
+
+ \subfloat[][\EC-sequence]{
+
+\includegraphics[width=0.9\textwidth]{positional_answers_TF_EC.pdf}
+}
+
+\caption{Positional answers for \lc-sequences and
+  \ec-sequences. \emph{True} judgements are plotted upwards on each
+  position, \emph{false} judgements downwards.}
+\label{Fig:TF_judgments}
 \end{figure}
 %
-Participants mostly gave judgments indicating literal or local
-readings. Judgments compatible with a global reading were seldom
-observed. In the \as-conditions (see
-Figure~\ref{fig:JudgementPercentagesAE}), judgments were consistent
-with literal readings in 65.0\% of the trials with neutral prosody and
-in 67.5\% of the trials with accented prosody. Judgments indicating
-local readings were given in 22.0\% of both the neutral and accented
-trials. Global readings occurred in 1.6\% of the neutral and 0.8\% of
-the accented trials (corresponding to a total of 3 answers across all
-trials).  In the \es-conditions (see
-Figure~\ref{fig:JudgementPercentagesGE}) judgments consistent with
-literal readings were given in 47.2\% and 44.7\% of the trials with
-neutral and accented prosody, respectively.  Judgments indicating
-local readings were given in 22.8\% of the neutral and 27.6\% of the
-accented trials. Global readings were observed in 0.8\% of the trials
-in both the neutral and the accented condition.  As for the number of
-erroneous decisions, a discrepancy between \as-conditions and
-\es-conditions was observed: In the former, participants made hardly
-any errors, while in the latter, the amount of errors was considerably
-larger.
-
-Interestingly, there was considerable variation of response patterns within participants.
-The relative frequencies of local responses seemed to be distributed bimodally (see Figure \ref{fig:HistogramLocalReadingsK2}).
-We classified participants as {\it localists}, {\it globalists} or {\it inconsitent}.
-Table \ref{table:answer-types-as} shows how many of each type we observed.
-Further examination of the distribution of local readings revealed a clear pattern.
-The relative frequency of local judgments per participant strongly
-correlated between all four conditions (all $r>.6, p<.001$). Within the non-localists, about half of the participants (41.5\% of all
-participants) were consistently giving judgments that indicate literal readings. Only a minority of participants exhibited inconsistency.
-
-\begin{figure}[t]
+Judgments were coded as \ec or as \lc if they were as expected under
+one of these readings, and as \emph{error} if they were not. The
+distributions of readings thus coded, for each position at which this
+critical item occurred during the experiment, is given in
+Table~\ref{tab:CC-ContingencyTable-TF}.
+
+\begin{table}[]
 \centering
-\subfloat[][\as-accented]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_AKZ.jpg}
-\label{fig:ReadingsAE}
-}
-\subfloat[][\as-neutral]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingAE_NTR.jpg}
-\label{fig:ReadingsGE}
-}
-
-\subfloat[][\es-accented]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_AKZ.jpg}
-\label{fig:ReadingsAE}
-}
-\subfloat[][\es-neutral]{
-\includegraphics[width=5cm]{../pictures/paper/histLocalReadingGE_NTR.jpg}
-\label{fig:ReadingsGE}
-}
-\caption[]{Judgments for the four target conditions}
-\label{fig:HistogramLocalReadingsK2}
-\end{figure}
-
-%
-\begin{table}[t]
-  \centering
-      \begin{tabular}{lccc}
-      & \multicolumn{3}{c}{\es} \\ \cmidrule(r){2-4}
-      \as & literalist & localist & incons. \\ \midrule
-      literalist   & 19 & 2 & 6\\
-      localist     &  0 & 7 & 0 \\
-      incons. &  2 & 1 & 1\\
+
+\begin{tabular}{lcccc}
+  condition & position & \multicolumn{3}{c}{response type} \\ \cmidrule(r){3-5}
+  && \emph{LC} & \emph{EC} & \emph{error}  \\
+  \midrule \addlinespace[0.15cm]
+  \textbf{\lc neutral} 
+  & Pos 1 & 27 &  7  & 4 \\
+  & Pos 2 & 23 &  11 & 4 \\
+  & Pos 3 & 26 &  9  & 3 \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{103} &  \textbf{3} & \textbf{0}  \\
+  \addlinespace[0.25cm]
+  \textbf{\lc with \lc cue} 
+  & Pos 1 & 26 &  6 & 5  \\
+  & Pos 2 & 31 &  5 & 2  \\
+  & Pos 3 & 33 &  3 & 2  \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
+  \addlinespace[0.25cm]
+  \textbf{\lc with \ec cue} 
+  & Pos 1 & 14 &  18 & 3  \\
+  & Pos 2 & 16 &  16 & 1  \\
+  & Pos 3 & 14 &  17 & 5  \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
+  \addlinespace[0.25cm]
+  \textbf{\ec neutral} 
+  & Pos 1 & 22 &  6 & 10  \\
+  & Pos 2 & 28 &  6 & 4  \\
+  & Pos 3 & 28 &  8 & 2  \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
+  \addlinespace[0.25cm]
+  \textbf{\ec with \lc cue} 
+  & Pos 1 & 30 &  5 & 3  \\
+  & Pos 2 & 32 &  5 & 1  \\
+  & Pos 3 & 30 &  3 & 2  \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
+  \addlinespace[0.25cm]
+  \textbf{\ec with \ec cue} 
+  & Pos 1 & 19 &  10 & 9  \\
+  & Pos 2 & 19 &  7  & 12  \\
+  & Pos 3 & 19 &  7  & 12  \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
 \end{tabular}
-    \caption{Contingency table showing the number of occurrences of
-      \emph{response types} in the \as- and \es-conditions with
-      neutral intonation. \emph{Literalists} are subjects who gave
-      responses that were classified as either a literal response or
-      an error; \emph{localist} are subjects who gave responses
-      that were classified as either a 
-      local response or an error. Subjects who gave at least two
-      responses from different categories (literal, global, local) are
-      classified as \emph{inconsistent}. (No subject's responses where
-      errors exclusively and there where no \emph{globalists}, as
-      defined in parallel fashion.)}
-    \label{table:answer-types-as}
+
+\caption{Contingency table of classified responses for the
+  preference-related controls. As before, the factor position encodes
+  whether participants saw the condition in question for the first,
+  second or third time during the whole experiment.}
+\label{tab:CC-ContingencyTable-TF}
 \end{table}
-%
-
-In order to test whether local readings occurred reliably, we compared the
-number of local responses in each condition with the expected
- chance level. Local responses had to be given on the last position in
-each trial where two responses were
-possible. One was compatible with a local reading the other was
-not. Therefore, we would expect 50\% local responses by chance. As it
-turned out, local responses were given significantly more often than
-50\% in all target conditions (all Bonferoni corrected p<.05). Note
-that this finding cannot be explained by a general response
-bias on the last position since local readings required a \emph{yes} judgment
-in the \es-conditions, but a \emph{no} judgment in the \as-conditions.
-
-In order to test whether accentuation or the quantifiers had an
-influence on the distribution of readings, log-linear models 
-including the factors {\it Reading}, {\it Accentuation} and 
-{\it Quantifier} were computed. Since the variability within participants caught
-our attention, we will below also report the interaction of {\it Participant} and {\it Reading}
-in addition to effects of our experimental manipulations.
-
-Unsurprisingly, there was an effect of \emph{Reading} ($LRCS_1=364.77,
-df_1 = 3, p_1<.001, LRCS_2=364.77, df_2 = 3, p_1<.001,$) because
-overall the readings were distributed inhomogeneously (see Figure
-\ref{fig:JudgementPercentages}). The quantifier had an influence on the
-distribution of readings as revealed by a reliable interaction of {\it
-  Reading} and {\it Quantifier} ($LRCS_1=49.32, p_1<.01,LRCS_2=32.16,
-p_1<.01,$). A difference in the distribution of judgment types
-between participants was revealed by a reliable interaction of {\it
-  Reading} and {\it Participant} ($LRCS_1=487.70, p_1<.01$).  Finally,
-there was a three-way interaction of {\it Participants}, {\it
-  Quantifier} and {\it Reading} ($LRCS_1, = 143.92, df_1 = 117,
-p_1<.05$) which could stem from the fact that some participants were
-more prone than others to make errors in the \es-conditions.
-
-In order to find out whether the interactions just reported affected
-the amount of local readings, the log-linear models were computed
-again with a different coding of the readings. Here, we only
-considered the amount of local readings versus all other kinds of
-judgments. Judgments were coded as {\it local} and {\it other}. If the
-reported interactions affected the amount of local readings, they should
-have shown up again. The expected but irrelevant effect of {\it Reading} was
-again significant ($LRCS_1=134.55, df_1 = 1, p_1<.001, LRCS_2=144.64,
-df_2 = 1, p_1<.001$). In addition, the interaction of {\it
-  Participant} and {\it Reading} ($LRCS_1=487.70, p_1<.01$) was significant. The interaction of {\it
-  Quantifier} and {\it Reading} was, however, not significant ($LRCS_1=2.10,
-p_1=.15,LRCS_2=.74, p_2=.39$).
-
-The interaction of {\it Participant} and {\it Reading} indicates that
-there are indeed varying preferences for local readings among German
-speakers (see Table~\ref{table:answer-types-as}). The absence of the interaction
-between {\it Quantifier} and {\it Reading} indicates that the type of quantifier does not affect the amount of local readings.
-Based on the observed distribution of judgments, we suspected that the type of quantifier affected the
-amount of literal but not local and global readings. To test
-this, we also compared literal and global readings versus
-other judgments in separate analyses. Comparing literal readings to
-other judgments {\it Construction} and {\it Reading} were found to
-interact ($LRCS_1=42.80, df= 1, p<.001; LRCS_2=22.14, df= 1,
-p<.001$). Comparing global readings to other judgments no such
-interaction was obeserved ($LRCS_1=1.24, df= 1, p=.29, LRCS_1=.21, df=
-1, p=.65$).
-
-\paragraph{Preference-related controls.} Participants' judgments are
-depicted in Figures \ref{Fig:EC_judgments} and
-\ref{Fig:LC_judgments}. Judgments were coded as \ec or as \lc if they
-were as expected under one of these readings, and as "other" if they
-were not. The distributions of readings thus coded is illustrated in
-Figure \ref{fig:response-type-freque-TRF}.  Overall, participants
-mainly gave answers corresponding to the \lc-reading (65\%).
-Moreover, this pattern was constrained by prosody. When prosody
-supported a dispreferred \ec-reading, the number of \ec-decisions were
-increased and vice versa.
+
+\bigskip
+
+Judgments were
+coded as \ec or as \lc if they were as expected under one of these
+readings, and as "other" if they were not. The distributions of
+readings thus coded is illustrated in Figure
+\ref{fig:response-type-freque-TRF}.  Overall, participants mainly gave
+answers corresponding to the \lc-reading (65\%).  Moreover, this
+pattern was constrained by prosody. When prosody supported a
+dispreferred \ec-reading, the number of \ec-decisions were increased
+and vice versa.
 
@@
 ($LRCS_1 = 38.4, df_1 =2, p_1 < 001$; $LRCS_2 = 26.1, df_2 =2, p_2 < .001$).
-
-\begin{figure}[t]
-\centering
-\subfloat[][neutral accentuation]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.2,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
-                  ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,64)};
-
-        \addplot coordinates {(1,4) (2,2) (3,26) (4,1) (5,5)};
-
-        \legend{yes, no}
-
-      \end{axis}
-\end{tikzpicture}
-% \label{fig:ReadingsAS-ntr}
-}
-\subfloat[][prosody cues \lc-reading]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.2,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
-                  % ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,76)};
-
-        \addplot coordinates {(1,4) (2,0) (3,13) (4,2) (5,5)};
-
-        % \legend{yes, no}
-
-      \end{axis}
-
-\end{tikzpicture}
-\label{fig:ReadingsES-ntr}
-}
-
-\subfloat[][prosody cues \ec-reading]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.2,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
-                  ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,0) (2,0) (3,0) (4,0) (5,56)};
-
-        \addplot coordinates {(1,2) (2,1) (3,33) (4,2) (5,6)};
-
-        % \legend{yes, no}
-
-      \end{axis}
-
-\end{tikzpicture}
-% \label{fig:ReadingsAS-acc}
-}
-\subfloat[][unambiguous \lc-reading]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.2,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
-                  % ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,1) (2,0) (3,0) (4,1) (5,86)};
-
-        \addplot coordinates {(1,6) (2,0) (3,5) (4,0) (5,2)};
-
-        % \legend{yes, no}
-
-      \end{axis}
-
-\end{tikzpicture}
-% \label{fig:ReadingsES-acc}
-}
-% \includegraphics[width=\textwidth]{../pictures/paper/graph_ec.pdf}
-\caption{Judgments for preference-related controls (EC
-  sequence). Rounded percentages of {\it yes/no} judgments are plotted
-  against the position within the trial. Each EC sequence consisted of
-  five pictures, in which the critical positions for a reading were
-  the third position (\emph{no} corresponded to an \ec reading) and
-  the fifth position (\emph{yes} corresponded to an \lc reading).}
-\label{Fig:EC_judgments}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-\subfloat[][neutral accentuation]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_AE_NTR.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.1,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
-                  ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,0) (2,0) (3,68) (4,0) (5,0) (6,1) (7,0)};
-
-        \addplot coordinates {(1,0) (2,0) (3,5) (4,0) (5,0) (6,25) (7,2)};
-
-        \legend{yes, no}
-
-      \end{axis}
-\end{tikzpicture}
-% \label{fig:ReadingsAS-ntr}
-}
-\subfloat[][prosody cues \lc-reading]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_GE_NTR.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.1,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
-                  % ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,0) (2,0) (3,79) (4,1) (5,1) (6,2) (7,1)};
-
-        \addplot coordinates {(1,0) (2,1) (3,3) (4,0) (5,0) (6,13) (7,0)};
-
-        % \legend{yes, no}
-
-      \end{axis}
-
-\end{tikzpicture}
-% \label{fig:ReadingsES-ntr}
-}
-
-\subfloat[][prosody cues \ec-reading]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_AE_AKZ.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.1,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.3,0.95)}, anchor=north, legend columns=-1},
-                  ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,0) (2,0) (3,51) (4,2) (5,1) (6,4) (7,0)};
-
-        \addplot coordinates {(1,2) (2,0) (3,8) (4,1) (5,0) (6,30) (7,2)};
-
-        % \legend{yes, no}
-
-      \end{axis}
-
-\end{tikzpicture}
-% \label{fig:ReadingsAS-acc}
-}
-\subfloat[][unambiguous \lc-reading]{
-% \includegraphics[width=5cm]{../pictures/paper/graph_GE_AKZ.jpg}
-\begin{tikzpicture}[scale=0.75]
-
-      \begin{axis}[ybar, 
-                  enlarge x limits=0.1,
-                  enlarge y limits=0.1,
-                  legend style={at={(0.4,0.95)}, anchor=north, legend columns=-1},
-                  % ylabel={\% of answers (rounded)}, 
-                  % xlabel={position}, 
-                  symbolic x coords={1, 2, 3, 4, 5, 6, 7}, 
-                  xtick=data, 
-                  nodes near coords,
-                  nodes near coords align={vertical}, 
-                  x=20, y=1,
-                  ymin = 0, ymax = 100,
-                  bar width=2mm
-        ]
-
-        \addplot coordinates {(1,0) (2,0) (3,88) (4,2) (5,0) (6,5) (7,0)};
-
-        \addplot coordinates {(1,1) (2,0) (3,1) (4,0) (5,0) (6,3) (7,0)};
-
-        % \legend{yes, no}
-
-      \end{axis}
-
-\end{tikzpicture}
-% \label{fig:ReadingsES-acc}
-}
-% \includegraphics[width=\textwidth]{../pictures/paper/graph_lc.pdf}
-\caption{Judgments for preference-related controls (LC
-  sequence). Rounded percentages of {\it yes/no} judgments are plotted
-  against the position within the trial. Each LC sequence consisted of
-  seven pictures, in which the critical positions for a reading were
-  the third position (\emph{yes} corresponded to an \lc reading) and the
-  sixth position (\emph{no} corresponded to an \ec reading).}
-\label{Fig:LC_judgments}
-\end{figure}
-
-% \begin{figure}
-% \includegraphics[width=\textwidth]{../pictures/graph_lc.pdf}
-% \end{figure}
-
-%\begin{itemize}
-%\item see Figure~\ref{fig:response-type-freque-TRF}
-%\end{itemize}
 

### 2014-05-21 text/paper/paper4.tex
statistical analyses critical

@@
 models (i.e., generalized linear regression for count data). To
-complement the picture, we also provide a Bayesian analysis that
-probes specifically into the preference relations between candidate
-readings.
+complement the picture, we also report a Bayesian analysis that probes
+specifically into the preference relations between candidate readings.
 
@@
 
-\caption{Positional judgments for the four target conditions. Bars
-  show the total number of \emph{yes} (up) and \emph{no} judgments
-  (down) against the position within a sequence. E.g., we recorded a
-  total of 103 \emph{yes} judgments at the third position in the
-  \as-sequence with neutral intonation, which corresponds to 103
-  answers that were classified as \emph{literal} answers. Notice that
-  the \as-condition has seven positions, the \es-condition only five.}
+\caption{Answers for the \as- and \es-sequences. Bars show the total
+  number of \emph{yes} (up) and \emph{no} judgments (down) collected
+  at each step during a sequence. E.g., we recorded a total of 103
+  \emph{yes} judgments at the third position in the \as-sequence with
+  neutral intonation, which corresponds to 103 answers that were
+  classified as \emph{literal} answers. Notice that the \as-condition
+  had seven steps, the \es-condition only five.}
 \label{fig:JudgmentsK2}
@@
 if they were as expected under one of these readings and as {\it
-  error} if not. The distribution of readings thus coded is presented
-in Table~\ref{tab:CC-ContingencyTable}. The table also classifies
+  error} if not. The distribution of readings thus coded is given in
+Table~\ref{tab:CC-ContingencyTable}. The table also classifies
 responses according to the position (1--3) in the experiment, i.e.,
@@
 7.02\% / 4.39\% unclassifiable judgements in the neutral / accented
-\as-conditions, but 19.30\% / 17.54\% 'error' in the neutral /
-accented \es-conditions. A look at Figure~\ref{fig:JudgmentsK2}
-reveals that there is some systematicity in 'error' answers. Most
-answers that we classified as 'errors' are plausibly explained as a
-few random errors, a handful of mistakes resulting from confusing
-buttons for \emph{true} and \emph{false} and a few 'spill-overs' where
-participants gave responses one position too late. There is one
-notable exception, though. A substantial number of \emph{true}
-responses where given at the second position of \es-sequences (9.65\%
-/ 8.77\%) which is shown in Figure~\ref{fig:exseqES2}. Although this
-position in the sequence is the critical position to reveal a global
-reading, the latter would be indicated by a \emph{false} response. It
-appears that subjects read \es-sentences as if the non-monotonic
-quantifier \emph{exactly one} was a non-monotonic \emph{at least one},
-without pragmatic enrichment of \emph{some}. 16 out of the total 21
-answers in this category come from 5 subjects, while the remaining 5
-were single answers by 5 different subjects. \todo{subjects 1, 9, 12,
-  21, 84} This suggests that at least for some subjects non-monotonic
-quantifiers were problematic. \todo{how to deal with this in the future?}
+\as-conditions, but 19.30\% / 17.54\% in the neutral / accented
+\es-conditions. A look at Figure~\ref{fig:JudgmentsK2} reveals that
+there is some systematicity in 'error' answers. Most answers that we
+classified as 'errors' are plausibly explained as a few random errors,
+a handful of mistakes resulting from confusing buttons for \emph{true}
+and \emph{false} and a few 'spill-overs' where participants gave
+responses one position too late. There is one notable exception,
+though. A substantial number of \emph{true} responses where given at
+the second position of \es-sequences (9.65\% / 8.77\%) which is shown
+in Figure~\ref{fig:exseqES2}. Although this position in the sequence
+is the critical position to reveal a global reading, the latter would
+be indicated by a \emph{false} response. It appears that subjects read
+\es-sentences as if the non-monotonic quantifier \emph{exactly one}
+was a monotonic \emph{at least one}, without pragmatic enrichment of
+\emph{some}.\fn{If \emph{some} is pragmatically strengthened under the
+  scope of \emph{at least one}, we would expect \emph{true} judgements
+  at position 3. Although exactly 3 \emph{true} answers occurred there
+  for each neutral and accented \es-conditions, the main point to
+  notice is that this misreading of the non-monotonic quantifier does
+  not explain \emph{true} judgements at position 5. These are
+  therefore still indicative of local readings.} 16 out of the total
+21 answers in this category come from 5 subjects, while the remaining
+5 were single answers by 5 different subjects. \todo{subjects 1, 9,
+  12, 21, 84} This suggests that at least for some subjects
+non-monotonic quantifiers were problematic. \todo{how to deal with
+  this in the future?}
 
@@
 and \emph{accented}, and \textsc{Position} with levels 1 through 3 to
-predict the dependent factor \emph{Response} with levels
+predict the dependent factor \textsc{Reading} with levels
 \emph{literal}, \emph{local}, and \emph{other}. The latter levels
@@
 In order to test whether there is support for the postulation of local
-readings, we compared the previous ``best'' model to a model that only
-differs from the former in that it subsumes the level \emph{local} of
-factor \textsc{Reading} under level \emph{other} as well
-\citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model comparison
-reveals that there is no significant improvement in explanatory power
-($Pr(|\chi|) = 0.2689$) of the more complex model that includes the
-level \emph{local} (df=30, residual deviance = 9.76) over the leaner
-model without this level (df=32, residual deviance = 12.39,
-AIC=156.63). This means that our data does not provide strong evidence
-for the maintenance of belief in \emph{local} readings in our
-setting. (Subsequent analysis will shed more light on this.)
+readings, we compared the previous ``best'' predictor to a model that
+only differs from the former in that it subsumes the level
+\emph{local} of factor \textsc{Reading} under level \emph{other} as
+well \citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model
+comparison reveals that there is no significant improvement in
+explanatory power ($Pr(|\chi|) = 0.2689$) of the more complex model
+that includes the level \emph{local} (df=30, residual deviance = 9.76)
+over the simpler model without this level (df=32, residual deviance =
+12.39, AIC=156.63).
+
+This latter analysis suggests that our data does not provide strong
+evidence for the maintenance of belief in local readings in our
+setting. But we need to be careful. So far we have not taken into
+account the sequential structure of our task. It might be that local
+readings are infrequent because subjects tend to exit early in the
+sequence, rather than late. This is why we need preference-related
+controls.
 
@@
 preference-related control conditions are shown in
-Figure~\ref{Fig:TF_judgments}.
+Figure~\ref{Fig:TF_judgments}.\fn{We removed 19 data points for the
+  \ec-conditions because of a coding mistake that presented subjects
+  with incongruent sentence-picture pairs. Including these and
+  classifying them as \emph{errors} does not change the results of the
+  reported analyses.}
 %
@@
 
-\caption{Positional answers for \lc-sequences and
-  \ec-sequences. \emph{True} judgements are plotted upwards on each
-  position, \emph{false} judgements downwards.}
+\caption{Answers for \lc-sequences and \ec-sequences. \emph{True}
+  judgements are plotted upwards for each step in the sequence,
+  \emph{false} judgements downwards.}
 \label{Fig:TF_judgments}
@@
 one of these readings, and as \emph{error} if they were not. The
-distributions of readings thus coded, for each position at which this
-critical item occurred during the experiment, is given in
-Table~\ref{tab:CC-ContingencyTable-TF}.
-
+distributions of readings thus coded is given in
+Table~\ref{tab:CC-ContingencyTable-TF}. Some subjects saw 4 trials of
+some target-related control conditions, but the table and the
+subsequent analysis of the count data only looks at the data from the
+first three encounters. This is because otherwise we would see a
+spurious main effect of \textsc{Position} that is just needed to
+account for the less frequent occurrence of judgements at position 4.
+%
 \begin{table}[]
@@
   & Pos 3 & 26 &  9  & 3 \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{103} &  \textbf{3} & \textbf{0}  \\
+  & \textbf{Total} & \textbf{76} &  \textbf{27} & \textbf{1}  \\
   \addlinespace[0.25cm]
   \textbf{\lc with \lc cue} 
-  & Pos 1 & 26 &  6 & 5  \\
+  & Pos 1 & 26 &  7 & 5  \\
   & Pos 2 & 31 &  5 & 2  \\
   & Pos 3 & 33 &  3 & 2  \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
+  & \textbf{Total} & \textbf{90} &  \textbf{15} & \textbf{9}  \\
   \addlinespace[0.25cm]
   \textbf{\lc with \ec cue} 
-  & Pos 1 & 14 &  18 & 3  \\
-  & Pos 2 & 16 &  16 & 1  \\
-  & Pos 3 & 14 &  17 & 5  \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
+  & Pos 1 & 14 &  17 & 7  \\
+  & Pos 2 & 15 &  16 & 7  \\
+  & Pos 3 & 15 &  17 & 6  \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{44} &  \textbf{50} & \textbf{20}  \\
   \addlinespace[0.25cm]
   \textbf{\ec neutral} 
-  & Pos 1 & 22 &  6 & 10  \\
+  & Pos 1 & 22 &  6 & 5  \\
   & Pos 2 & 28 &  6 & 4  \\
-  & Pos 3 & 28 &  8 & 2  \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
+  & Pos 3 & 29 &  7 & 2  \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{79} &  \textbf{19} & \textbf{11}  \\
   \addlinespace[0.25cm]
   \textbf{\ec with \lc cue} 
-  & Pos 1 & 30 &  5 & 3  \\
-  & Pos 2 & 32 &  5 & 1  \\
-  & Pos 3 & 30 &  3 & 2  \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
+  & Pos 1 & 30 &  5 & 1  \\
+  & Pos 2 & 32 &  5 & 0  \\
+  & Pos 3 & 31 &  3 & 2  \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{93} &  \textbf{13} & \textbf{3}  \\
   \addlinespace[0.25cm]
   \textbf{\ec with \ec cue} 
-  & Pos 1 & 19 &  10 & 9  \\
-  & Pos 2 & 19 &  7  & 12  \\
-  & Pos 3 & 19 &  7  & 12  \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2}  \\
+  & Pos 1 & 19 &  10 & 7  \\
+  & Pos 2 & 19 &  7  & 9  \\
+  & Pos 3 & 19 &  7  & 11  \\ \addlinespace[0.15cm]
+  & \textbf{Total} & \textbf{57} &  \textbf{24} & \textbf{27}  \\
 \end{tabular}
@@
 \end{table}
+
+As expected, most answers classify as \lc-readings, fewer as
+\ec-readings. Moreover, intonation does seem to have the expected
+effect as well: as compared to neutral intonation, \lc-cueing
+intonation ups the count for \lc-readings, while \ec-cueing ups the
+count for \ec-readings. If we compare the number of \lc- or
+\ec-readings for each intonation type across sequences, we see that
+there are always more answers indicative of the relevant readings when
+that reading can be judged later in the sequence.
+
+There are only very few answers that appear to be random
+mistakes. Some answers in the `error' category are plausibly
+`spill-over' errors. But on top of that, a substantial number of
+`error' answers occur on critical positions. In the \lc-sequence there
+are 23 \emph{true} answers at step 6 where \emph{false} answers would
+be taken as indicative of \ec-readings. In the \ec-sequence there are
+28 \emph{false} answers at step 5 where \emph{true} answers would be
+taken as indicative of \lc-readings. \todo{A general tendency to
+  answer later in the sequence does explain this. We don't see a
+  similar effect in the critical conditions because the literal
+  reading is so dominant.} Finally, intonation patterns that cue
+\ec-readings seem to have led to more mistakes than other intonation
+patterns.
+
+\begin{itemize}
+\item \textcolor{red}{LOG-LINEAR MODELS}
+\end{itemize}
 

### 2014-05-21 text/paper/paper4.tex
statistical analyses preference-related controls

@@
 
-In order to test whether there is support for the postulation of local
-readings, we compared the previous ``best'' predictor to a model that
-only differs from the former in that it subsumes the level
-\emph{local} of factor \textsc{Reading} under level \emph{other} as
-well \citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model
-comparison reveals that there is no significant improvement in
-explanatory power ($Pr(|\chi|) = 0.2689$) of the more complex model
-that includes the level \emph{local} (df=30, residual deviance = 9.76)
-over the simpler model without this level (df=32, residual deviance =
-12.39, AIC=156.63).
+\begin{table}
+  \centering
+  \begin{tabular}{lllll}
+    coefficient & estimate & std.~error & $z$-value & $\Pr(>|z|)$ \\
+    \midrule
+    \textsc{Intercept} & 1.679  &  0.134 &  12.499  & < 0.001 \\
+    \textsc{Reading}.\emph{literal} & -0.219  &  0.281 & -0.781 &
+    0.435 \\
+    \textsc{Reading}.\emph{local} & -2.249 &   0.172 & -13.084 & < 0.001 \\
+    \textsc{Condition}.\es & 0.592 &  0.159 & 3.732 &  < 0.001 \\
+    \textsc{Reading}.\emph{literal}:\textsc{Condition}.\es & -0.0186 &
+    0.328 & -0.057 &  0.95471 \\
+    \textsc{Reading}.\emph{local}:\textsc{Condition}.\es & 1.041 &
+    0.208 &  4.999 &  < 0.001
+  \end{tabular}
+  \caption{Coefficients of the ``best'' log-linear model for the count
+    data in Table~\ref{tab:CC-ContingencyTable}.}
+  \label{tab:Coefficients-CC}
+\end{table}
+
+Inspection of the coefficients of the ``best'' model suggests that the
+distinction between levels \emph{local} and \emph{other} in factor
+\textsc{Reading} might not be necessary. In order to test whether
+there is support for the postulation of local readings, we therefore
+compared the previous ``best'' predictor to a model that only differs
+from the former in that it subsumes the level \emph{local} of factor
+\textsc{Reading} under level \emph{other} as well
+\citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model comparison
+reveals that there is no significant improvement in explanatory power
+($Pr(|\chi|) = 0.2689$) of the more complex model that includes the
+level \emph{local} (df=30, residual deviance = 9.76) over the simpler
+model without this level (df=32, residual deviance = 12.39,
+AIC=156.63).
 
@@
   & Pos 3 & 26 &  9  & 3 \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{76} &  \textbf{27} & \textbf{1}  \\
+  & \textbf{Total} & \textbf{76} &  \textbf{27} & \textbf{11}  \\
   \addlinespace[0.25cm]
@@
 
-\begin{itemize}
-\item \textcolor{red}{LOG-LINEAR MODELS}
-\end{itemize}
-
-\bigskip
-
-Judgments were
-coded as \ec or as \lc if they were as expected under one of these
-readings, and as "other" if they were not. The distributions of
-readings thus coded is illustrated in Figure
-\ref{fig:response-type-freque-TRF}.  Overall, participants mainly gave
-answers corresponding to the \lc-reading (65\%).  Moreover, this
-pattern was constrained by prosody. When prosody supported a
-dispreferred \ec-reading, the number of \ec-decisions were increased
-and vice versa.
-
-In both \lc- and \ec-sequences, the number of \ec-answers was highest
-when this reading was supported by prosodic phrasing (30\% and
-32\%, respectively), and a bit lower with neutral prosody (24\% and
-25\%). When prosodic phrasing supported the \lc-reading, the number of
-\ec choices was lowest (12\% in both sequences). The number of
-erroneous answers did not differ between the single
-conditions. Finally, the availability of readings within a sequence
-did not yield any significant effects.
-
-In order to test statistically whether prosodic phrasing and
-sequential ordering had an effect on the number of \ec-choices, we
-contrasted the number of \ec-choices with non-\ec -choices (i.e.,
-\lc-answers and erroneous responses together), calculating log-linear
-model analyses with the factors {\it Reading}, {\it Prosody}, and {\it
-  Sequence}.
-
-An effect of {\it Reading} reflects that overall, readings were distributed inhomogeneously
-($LRCS_1 = 252.8, df_1 =1, p_1 < .001$; $LRCS_2 = 252.8, df_2 =1, p_2 < 001$). 
-As revealed by an interaction between {\it Prosody} and
-{\it Reading}, prosodic phrasing had an influence upon the distribution of readings 
-($LRCS_1 = 38.4, df_1 =2, p_1 < 001$; $LRCS_2 = 26.1, df_2 =2, p_2 < .001$).
-
-\begin{figure}[t]
+As for the critical conditions, we compute logistic regression models
+including factors \textsc{Reading} with levels \lc, \ec and
+\emph{error}, \textsc{Accent} with levels \emph{neutral},
+\emph{\lc-cue} and \emph{\ec-cue}, \textsc{Position} with levels 1 to
+3, and \textsc{Condition} with levels \lc and \ec for the picture
+sequences. Starting search from the saturated model along a gradient
+of decreasing AICs, we find that the ``best'' predictor relies on main
+effects of \textsc{Reading}, \textsc{Accent} and \textsc{Condition}
+and two two-way interactions \textsc{Response:Condition} and
+\textsc{Response:Accent} ($\chi^2=18.34$, $df=42$, $p=0.99$,
+$AIC=256.63$ (compared to $AIC=322.3$ of the saturated model)). Factor
+\textsc{Position} again turned out to be spurious, suggesting that
+answer patterns are stable over the duration of the experiment. Unlike
+for the critical conditions, factor \textsc{Accent} is retained, and
+it interacts with \textsc{Reading}, suggesting that intonational cues
+significantly influenced the dominant reading.
+
+\begin{table}
   \centering
-  \subfloat[][\LC-condition]{
-        \begin{tikzpicture}[scale=0.75]
-
-  \begin{axis}[ybar, 
-               enlarge x limits=0.45,
-               enlarge y limits=0.25, 
-               legend style={at={(0.5,-0.15)},
-                 anchor=north,
-                 legend columns=-1}, 
-               ylabel={\% of answers (rounded)}, 
-               symbolic x coords={neutral,LC-pref,EC-pref}, 
-               xtick=data,
-               nodes near coords,
-               nodes near coords align={vertical},
-               x = 45, 
-               bar width = 3mm,
-               ymin = 8
-               ]
-
-    \addplot coordinates {(neutral, 69) (LC-pref, 77) (EC-pref, 52)};
-
-    \addplot coordinates {(neutral, 24) (LC-pref, 12) (EC-pref, 30)};
-
-    \addplot coordinates {(neutral, 7) (LC-pref, 11) (EC-pref, 19)};
-
-    % \addplot coordinates {(l-ntr, 93) (l-l, 101) (l-e, 70) (e-ntr, 85)
-    %   (e-l, 100) (e-e, 75)};
-
-    % \addplot coordinates {(l-ntr, 33) (l-l, 16) (l-e, 40) (e-ntr, 34)
-    %   (e-l, 16) (e-e, 43)};
-
-    % \addplot coordinates {(l-ntr, 9) (l-l, 14) (l-e, 25) (e-ntr, 16)
-    %   (e-l, 15) (e-e, 17)};
-
-    \legend{LC, EC, error}
-
-  \end{axis}
-
-\end{tikzpicture}
-  }
-  \subfloat[][\ec-condition]{
-    \begin{tikzpicture}[scale=0.75]
-
-  \begin{axis}[ybar, 
-               enlarge x limits=0.45, 
-               enlarge y limits=0.25, 
-               legend style={at={(0.5,-0.15)},
-                 anchor=north,
-                 legend columns=-1}, 
-               % ylabel={\% of answers}, 
-               symbolic x coords={neutral,LC-pref,EC-pref}, 
-               xtick=data,
-               nodes near coords,
-               nodes near coords align={vertical},
-               x = 45, 
-               bar width = 3mm,
-               ymin = 8
-               ]
-
-    \addplot coordinates {(neutral, 63)
-      (LC-pref, 76) (EC-pref, 56)};
-
-    \addplot coordinates {(neutral, 25)
-      (LC-pref, 12) (EC-pref, 32)};
-
-    \addplot coordinates {(neutral, 12)
-      (LC-pref, 11) (EC-pref, 13)};
-
-    % \addplot coordinates {(l-ntr, 93) (l-l, 101) (l-e, 70) (e-ntr, 85)
-    %   (e-l, 100) (e-e, 75)};
-
-    % \addplot coordinates {(l-ntr, 33) (l-l, 16) (l-e, 40) (e-ntr, 34)
-    %   (e-l, 16) (e-e, 43)};
-
-    % \addplot coordinates {(l-ntr, 9) (l-l, 14) (l-e, 25) (e-ntr, 16)
-    %   (e-l, 15) (e-e, 17)};
-
-    \legend{LC, EC, error}
-
-  \end{axis}
-
-\end{tikzpicture}
-}
-  \caption{Response type frequences for preference-related controls}
-  \label{fig:response-type-freque-TRF}
-\end{figure}
+  \begin{tabular}{lllll}
+    coefficient & estimate & std.~error & $z$-value & $\Pr(>|z|)$ \\
+    \midrule
+    \textsc{Intercept} & 2.119  &   0.162 & 13.079   & < 0.001 \\
+    \textsc{Reading}.\emph{error} & -0.343 &  0.259 & -1.328 &  0.184
+    \\
+    \textsc{Reading}.\lc & 0.526 &  0.202 & 2.607 & < 0.01 \\
+    \textsc{Condition}.\lc & 0.497 &  0.170  & 2.929 & < 0.01 \\
+    \textsc{Accent}.\lc & -1.054 & 0.242 & -4.354 & < 0.001 \\
+    \textsc{Accent}.\emph{neutral} & -0.112 & 0.180 &  -0.626 &  0.531
+    \\
+    \textsc{Reading}.\emph{error}:\textsc{Condition}.\lc & -0.521 &
+    0.280 & -1.87 & 0.062 \\
+    \textsc{Reading}.\lc:\textsc{Condition}.\lc & -0.583 & 0.195 &
+    -2.997 &  < 0.01 \\
+    \textsc{Reading}.\emph{error}:\textsc{Accent}.\lc & -0.103 &
+    0.422 &  -0.245 & 0.807  \\
+    \textsc{Reading}.\lc:\textsc{Accent}.\lc & 1.657 &  0.279 & 5.943
+    & < 0.001 \\
+    \textsc{Reading}.\emph{error}:\textsc{Accent}.\emph{neutral} & 0.112 &
+    0.299  &  0.375 &  0.708 \\
+    \textsc{Reading}.\lc:\textsc{Accent}.\emph{neutral} & 1.065  &
+    0.222 &  4.800 & < 0.001 \\
+  \end{tabular}
+  \caption{Coefficients of the ``best'' log-linear model for the count
+    data in Table~\ref{tab:CC-ContingencyTable-TF}.}
+  \label{tab:Coefficients-TF}
+\end{table}
+
+Closer examination of the coefficients of the fitted model, shown in
+Table~\ref{tab:Coefficients-TF}, reveals that there were significantly
+more \ec-readings in the \lc-condition and vice versa. This is evident
+from the significant \emph{negative} deviation from the baseline of
+\ec-readings in the interaction coefficient for
+\textsc{Reading}.\lc:\textsc{Condition}.\lc. The log-linear model
+therefore suggests that there is a bias for late responses in a
+sequence. If such a preference for late responses holds for critical
+conditions as well, then the marginal numer of local responses that we
+observed is more likely overemphasized by our sequential decision task
+than that it is underemphasized. The following Bayesian analysis
+further probes into this matter in order to establish how strongly the
+sequence-effect might have emphasized local readings and, from there,
+whether we should uphold belief in local readings.
+
+\newpage
 

### 2014-05-27 text/paper/paper4.tex

@@
     {loosely dotted}}
+
+\usetikzlibrary{calc}
+\usepackage{nicefrac}
 
@@
 which could be connected to surrounding elements (e.g., triangles), as
-shown in Figures~\ref{fig:exseqAS} and XYZ. Initially, any potential
-connections between central and surrounding elements were covered by
-dark gray color (see Figure~\ref{fig:exseqAS1}). Sentences to be
-judged were presented auditorily, and participants were asked to
-uncover the picture until they felt able to give a truth value
-judgment. Three options were available for participants at each step:
-(i) judge the sentence as true, (ii) judge the sentence as false,
-(iii) demand more information (unavailable when the picture was fully
-uncovered). Trials ended when a truth-value judgement was
-made. Importantly, each of the three potentially available readings
-corresponded to a specific step in the uncovering process where the
-truth value of that reading (and only of that reading) could be
-assessed for the first time. We refer to this step in the sequence as
-the {\it critical position} of a given reading. The critical position
-and the corresponding truth-value judgment differed between \as- and
-\es-sentences, as described presently. (This is, partly, because of
-the logical dependencies between readings, and, partly, also to rule
-out positional biases.)
+shown in Figures~\ref{fig:exseqAS}--\ref{fig:exec}. Initially,
+any potential connections between central and surrounding elements
+were covered by dark gray color (see
+Figure~\ref{fig:exseqAS1}). Sentences to be judged were presented
+auditorily, and participants were asked to uncover the picture until
+they felt able to give a truth value judgment. Three options were
+available for participants at each step: (i) judge the sentence as
+true, (ii) judge the sentence as false, (iii) demand more information
+(unavailable when the picture was fully uncovered). Trials ended when
+a truth-value judgement was made. Importantly, each of the three
+potentially available readings corresponded to a specific step in the
+uncovering process where the truth value of that reading (and only of
+that reading) could be assessed for the first time. We refer to this
+step in the sequence as the {\it critical position} of a given
+reading. The critical position and the corresponding truth-value
+judgment differed between \as- and \es-sentences, as described
+presently. (This is, partly, because of the logical dependencies
+between readings, and, partly, also to rule out positional biases.)
 
@@
 had any prior exposure to logic or formal semantics. We excluded two
-participant due to insufficient performance on controls ($\le 60\%$
+participants due to insufficient performance on controls ($\le 60\%$
 correct answers).
@@
 predict the dependent factor \textsc{Reading} with levels
-\emph{literal}, \emph{local}, and \emph{other}. The latter levels
-lumps \emph{global} and \emph{error} responses together, because
-otherwise we would not have enough cell counts to apply log-linear
+\emph{literal}, \emph{local}, and \emph{other}. The latter lumps
+\emph{global} and \emph{error} responses together, because otherwise
+we would not have enough cell counts to apply log-linear
 regression. We selected the ``best'' predictor of the data by a
@@
 saturated model)). Crucially, factors \textsc{Position} and
-\emph{Accent} are spurious in the best model. This suggests that
+\textsc{Accent} are spurious in the best model. This suggests that
 response patterns only depend on the type of the sentence, but that
@@
     \midrule
-    \textsc{Intercept} & 1.679  &  0.134 &  12.499  & < 0.001 \\
-    \textsc{Reading}.\emph{literal} & -0.219  &  0.281 & -0.781 &
+    \textsc{Intercept} & 0.916  &  0.258 &  3.49  & < 0.001 \\
+    \textsc{Reading}.\emph{literal} & 2.600 &   0.268 & 9.716 & < 0.001 \\
+    \textsc{Reading}.\emph{local} & -0.310  &  0.397 & -0.781 &
     0.435 \\
-    \textsc{Reading}.\emph{local} & -2.249 &   0.172 & -13.084 & < 0.001 \\
-    \textsc{Condition}.\es & 0.592 &  0.159 & 3.732 &  < 0.001 \\
-    \textsc{Reading}.\emph{literal}:\textsc{Condition}.\es & -0.0186 &
-    0.328 & -0.057 &  0.95471 \\
-    \textsc{Reading}.\emph{local}:\textsc{Condition}.\es & 1.041 &
-    0.208 &  4.999 &  < 0.001
+    \textsc{Condition}.\es & 1.030 &  0.301 & 3.423 &  < 0.001 \\
+    \textsc{Reading}.\emph{literal}:\textsc{Condition}.\es & -1.288 &
+    0.319 & -4.036 &  < 0.001 \\
+    \textsc{Reading}.\emph{local}:\textsc{Condition}.\es & -0.026 &
+    0.463 &  -0.0579 &  0.955
   \end{tabular}
   \caption{Coefficients of the ``best'' log-linear model for the count
-    data in Table~\ref{tab:CC-ContingencyTable}.}
+    data in Table~\ref{tab:CC-ContingencyTable}. Notice that factor
+    levels \emph{local} do not cause a significant shift in counts,
+    given reference level
+    \emph{false}.}
   \label{tab:Coefficients-CC}
@@
 distinction between levels \emph{local} and \emph{other} in factor
-\textsc{Reading} might not be necessary. In order to test whether
-there is support for the postulation of local readings, we therefore
-compared the previous ``best'' predictor to a model that only differs
-from the former in that it subsumes the level \emph{local} of factor
+\textsc{Reading} might not be necessary (see
+Table~\ref{tab:Coefficients-CC}). In order to test whether there is
+support for the postulation of local readings, we therefore compared
+the previous ``best'' predictor to a model that only differs from the
+former in that it subsumes the level \emph{local} of factor
 \textsc{Reading} under level \emph{other} as well
@@
 ($Pr(|\chi|) = 0.2689$) of the more complex model that includes the
-level \emph{local} (df=30, residual deviance = 9.76) over the simpler
-model without this level (df=32, residual deviance = 12.39,
-AIC=156.63).
+level \emph{local} (residual df=30, residual deviance = 10.497) over the simpler
+model without this level (residual df=32, residual deviance = 13.124,
+AIC=157.268).
 
@@
 evidence for the maintenance of belief in local readings in our
-setting. But we need to be careful. So far we have not taken into
-account the sequential structure of our task. It might be that local
-readings are infrequent because subjects tend to exit early in the
-sequence, rather than late. This is why we need preference-related
-controls.
+setting. But we need to be careful. The regression analysis tells us
+that the number of errors and the number of local readings were
+similar in all conditions. But the distribution of answers in
+Figure~\ref{fig:JudgmentsK2} shows that small error counts occur at
+many different steps, whereas we do see a concentrated rise in answers
+at the critical position for local readings. Also, so far we have not
+taken into account the sequential structure of our task. It might be
+that local readings are infrequent because subjects tend to exit early
+in the sequence, rather than late. This is why we need
+preference-related controls and a more fine-grained analysis
+eventually.
 
@@
   with incongruent sentence-picture pairs. Including these and
-  classifying them as \emph{errors} does not change the results of the
-  reported analyses.}
+  classifying them as \emph{errors} does not change the qualitative
+  results of the reported analyses.}
 %
@@
 effect as well: as compared to neutral intonation, \lc-cueing
-intonation ups the count for \lc-readings, while \ec-cueing ups the
-count for \ec-readings. If we compare the number of \lc- or
-\ec-readings for each intonation type across sequences, we see that
+intonation increases the count for \lc-readings, while \ec-cueing
+increases the count for \ec-readings. If we compare the number of \lc-
+or \ec-readings for each intonation type across sequences, we see that
 there are always more answers indicative of the relevant readings when
-that reading can be judged later in the sequence.
+that reading can be judged later in the sequence. This suggests a
+general tendency to answer later in the sequence, rather than at the
+earliest possible step.
 
@@
 mistakes. Some answers in the `error' category are plausibly
-`spill-over' errors. But on top of that, a substantial number of
-`error' answers occur on critical positions. In the \lc-sequence there
+`spill-over errors', where participants gave answers one step too
+late. But on top of that, a substantial number of `error' answers
+occurs on critical positions. For example, in the \lc-sequence there
 are 23 \emph{true} answers at step 6 where \emph{false} answers would
@@
 28 \emph{false} answers at step 5 where \emph{true} answers would be
-taken as indicative of \lc-readings. \todo{A general tendency to
-  answer later in the sequence does explain this. We don't see a
-  similar effect in the critical conditions because the literal
-  reading is so dominant.} Finally, intonation patterns that cue
-\ec-readings seem to have led to more mistakes than other intonation
-patterns.
+taken as indicative of \lc-readings.\fn{A general tendency to answer
+  later in the sequence would explain this. The reason why we do not
+  see a similar effect in the critical conditions, might be because
+  the literal reading is so dominant.} Finally, intonation patterns
+that cue \ec-readings seem to have led to more mistakes than other
+intonation patterns.
 
@@
 whether we should uphold belief in local readings.
+
+\subsubsection{Probabilistic salience competition.}
+
+Our previous regression-based analyses did not take the sequential
+nature of the task into account. We initially hypothesized that
+subjects might exit as early as possible, but the data from the
+target-related controls suggests otherwise. In order to estimate this
+bias and the preference for candidate readings, we use a simple
+Bayesian cognitive model that computes the likelihood of answer
+patterns for different latent sequential biases and reading
+preferences. We use the data to estimate the posterior likelihood of
+these latent parameters to gain insight into the likely preference
+relations and the salience of local readings.
+
+\paragraph{The model.} We outline a simple probabilistic model that
+quantifies the positional bias and the competing strength of available
+readings. Take the AS-conditions as an example. There are three
+potential readings. The relative strength between these is given by a
+probability vector $\myvec{p}^\text{as-n} =
+\tuple{p^\text{as-n}_{\text{lit}},p^\text{as-n}_{\text{loc}},p^\text{as-n}_{\text{glb}}}$. We
+think of $p^\text{as-n}_{\text{lit}}$, for instance, as the salience
+of the literal reading for \as-sentences with neutral prosody,
+relative to the global and local reading. If there were no potential
+effects of sequentiality and no errors (or other readings that we
+classify as errors), the vector $\myvec{p}^\text{as-n}$ would be our
+prediction of observed frequencies of answer patterns. We look at four
+such three-placed vectors, one for each target condition.
+
+For the preference-related control conditions we look at three vectors
+$p^k = \tuple{p^{\text{k}}_{\text{\lc}}, p^{\text{k}}_{\text{\ec}}}$,
+where $k \in \set{text{ntr}, \text{\lc-cue}, \text{\ec-cue}}$. These
+vectors give the relative salience of \lc- and \ec-readings for
+different types of intonation. The salience of readings is independent
+of the pictorial sequence. If there is a tendency to judge sentences
+earlier in the sequence, rather than later, that is to be attributed
+to the sequential bias, not a difference in general, task-independent
+salience of readings.
+
+To add potential effects of sequentiality, we assume that there is a
+constant bias factor $q \in [0;1]$. This bias is held constant over
+all conditions, because we assume that there is a global tendency to
+answer early or late, independent of the sentence subjects are
+confronted with. The bias factor captures whether there is a tendency
+to answer early ($q > .5$) or later ($q <.5$) in the sequence. In the
+\as-sequences, the literal reading can be judged first, then the local
+and then the global reading. So we will assume that $p_{\text{lit}}$
+is multiplied by $q$, that $p_{\text{loc}}$ is multiplied by $(1-q)q$
+and that $p_{\text{glb}}$ is multiplied by $(1-q)^2$.
+
+Finally, we also allow for the chance of subjects making mistakes. To
+keep things as simple as possible (no consideration for spill-overs,
+late decisions, preferences to unravel completely before judging
+etc.), we assume that there is a fixed error rate $e^k \in [0;1]$ for
+each sentence-intonation pair $k$. We allow for different error
+rates for different sentence-intonation pairs, because we want to
+allow for the possibility that non-monotonic quantifiers might be
+harder to process, or that some kind of intonation (like the \ec-cue)
+is harder than others. A decision can be wrong but incidentally
+coincide with a reading that is indicative of a relevant
+reading. Error rates multiply in proportion to the number of steps in
+a sequence: more choice, more chance to be wrong.
+
+\bigskip
+
+HERE
+
+Taking this together we calculate, for each critical
+sentence-intonation pair $k$ a target probability vector $\myvec{t}^k
+=
+\tuple{t^k_{\text{lit}},t^k_{\text{loc}},t^k_{\text{glb}},t^k_{\text{err}}}$
+with which we expect an answer to be classified as LIT, LOC, GLB or as
+an error. For example, for AS-N, where LIT can be judged before GLB
+before LOC, we get:
+\begin{align*}
+  t^{\text{as-n}}_{\text{lit}} & \propto q \
+  p^\text{as-n}_{\text{lit}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{loc}} & \propto (1-q)^2 \
+  p^\text{as-n}_{\text{loc}} + e^\text{as-n} \\
+  t^{\text{as-n}}_{\text{glb}} & \propto (1-q)q \
+  p^\text{as-n}_{\text{glb}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{err}} &
+  \propto 12 e^\text{as-n}
+\end{align*}
+Two remarks. The vector $\myvec{t}^k$ should be normalized eventually,
+which is why $\propto$ is used instead of $=$. Also, the probability
+of error $t^{\text{as-n}}_{\text{err}}$ comes from the observation
+that there are 15 positions in total in an AS-sequence at which
+subjects can make an erroneous choice, but we have accounted for three
+of these already as adding to the count of answers indicative of
+relevant readings.
+
+Similarly, we compute a target probability $\myvec{t}^k =
+\tuple{t^k_{\text{late}},t^k_{\text{early}},t^k_{\text{err}}}$ for
+each preference-related control condition $k$, taking into account
+which reading can be judged first and the length of the respective
+sequences.
+
+The full probabilistic model is visualized in
+Figure~\ref{fig:model_graph}. As indicated there, we assume largely
+uninformative priors. Any positional bias $q \in [0;1]$ is assumed to
+be equally likely. The error rates for each condition should be small,
+so we sample uniformly from interval $[0,.2]$. The biases
+$\myvec{p}_k$ are also determined uniformly at random, by sampling from a
+Dirichlet distribution with equal weights on all dimensions.
+
+\begin{figure}[t]
+  \centering
+  \begin{tikzpicture}[node distance = 2.5cm, 
+    double distance = 2pt,
+    minimum size=1.25cm,
+    thick]
+
+    \node[rectangle, draw=black, fill=black!30] (obs)
+    {obs$_k$};
+
+    \node[rectangle, draw=black, fill=black!30,
+    right of = obs] (n) {$n_k$};
+
+    \node[below of = n, node distance= 1.5cm]
+    (anchor) {};
+
+    \node[left of = anchor, node distance= 0.5cm] (k) {$k \in
+      \set{\text{as-n, as-e, \dots}}$};
+
+    \node[circle, double, draw=black,
+    above of = obs] (t) {$\myvec{t}_k$};
+
+    \node[circle, draw=black, 
+    above of = t] (p) {$\myvec{p}_k$};
+
+    \node[circle, draw=black, 
+    right of = p] (e) {$e_k$};
+
+    \node[circle, draw=black, 
+    left of = p] (q) {$q$};
+
+    \draw[->] (t)--(obs);
+
+    \draw[->] (n)--(obs);
+
+    \draw[->] (q)--(t);
+
+    \draw[->] (p)--(t);
+
+    \draw[->] (e)--(t);
+
+    \begin{pgfonlayer}{background}
+       \node [rounded corners,
+       very thick,draw=black!40,fit={($(obs.south)+(0,-30pt)$) 
+                                 ($(n.east)+(+5pt,0)$) 
+                                 ($(e.north)+(0,+5pt)$) 
+                                 ($(p.west)+(-5pt,0)$)}] {};
+    \end{pgfonlayer}
+
+    \begin{scope}[xshift = 7.5cm, node distance = 1cm]
+
+      \node[] (obsd) {$\text{obs}_k \sim \text{Multinomial}(\myvec{t}_k,n_k)$};
+
+      \node[above of = obsd] (td) {$\myvec{t}_k = \text{as described
+          in text}$};
+
+      \node[above of = td] (pd) {$\myvec{p}_k =
+        \text{Dirichlet}(\tuple{\nicefrac{1}{k}, \nicefrac{1}{k}, \dots})$};
+
+      \node[above of = pd] (ed) {$e_k \sim \mathcal{U}(0,.2)$};
+
+      \node[above of = ed] (qd) {$q \sim \mathcal{U}(0,1)$};
+
+    \end{scope}
+
+  \end{tikzpicture}
+  \caption{Probabilistic graphical model}
+  \label{fig:model_graph}
+\end{figure}
 

### 2014-05-28 text/paper/paper4.tex

@@
 
-Our previous regression-based analyses did not take the sequential
+The previous regression-based analyses did not take the sequential
 nature of the task into account. We initially hypothesized that
 subjects might exit as early as possible, but the data from the
-target-related controls suggests otherwise. In order to estimate this
-bias and the preference for candidate readings, we use a simple
-Bayesian cognitive model that computes the likelihood of answer
-patterns for different latent sequential biases and reading
-preferences. We use the data to estimate the posterior likelihood of
-these latent parameters to gain insight into the likely preference
-relations and the salience of local readings.
+target-related controls suggests otherwise. The following paragraphs
+spell out a simple Bayesian cognitive model that computes the
+likelihood of answer patterns for different latent sequential biases
+and reading preferences. We use the data to estimate the posterior
+likelihood of these latent parameters to gain insight into the likely
+preference relations and the salience of local readings.
 
@@
 prediction of observed frequencies of answer patterns. We look at four
-such three-placed vectors, one for each target condition.
+such three-placed vectors, one for each target sentence-intonation
+pair.
 
@@
 $p^k = \tuple{p^{\text{k}}_{\text{\lc}}, p^{\text{k}}_{\text{\ec}}}$,
-where $k \in \set{text{ntr}, \text{\lc-cue}, \text{\ec-cue}}$. These
+where $k \in \set{\text{ntr}, \text{\lc-cue}, \text{\ec-cue}}$. These
 vectors give the relative salience of \lc- and \ec-readings for
@@
 earlier in the sequence, rather than later, that is to be attributed
-to the sequential bias, not a difference in general, task-independent
-salience of readings.
+to the sequential bias.
 
 To add potential effects of sequentiality, we assume that there is a
-constant bias factor $q \in [0;1]$. This bias is held constant over
-all conditions, because we assume that there is a global tendency to
-answer early or late, independent of the sentence subjects are
-confronted with. The bias factor captures whether there is a tendency
-to answer early ($q > .5$) or later ($q <.5$) in the sequence. In the
-\as-sequences, the literal reading can be judged first, then the local
-and then the global reading. So we will assume that $p_{\text{lit}}$
-is multiplied by $q$, that $p_{\text{loc}}$ is multiplied by $(1-q)q$
-and that $p_{\text{glb}}$ is multiplied by $(1-q)^2$.
-
-Finally, we also allow for the chance of subjects making mistakes. To
-keep things as simple as possible (no consideration for spill-overs,
-late decisions, preferences to unravel completely before judging
-etc.), we assume that there is a fixed error rate $e^k \in [0;1]$ for
-each sentence-intonation pair $k$. We allow for different error
-rates for different sentence-intonation pairs, because we want to
-allow for the possibility that non-monotonic quantifiers might be
-harder to process, or that some kind of intonation (like the \ec-cue)
-is harder than others. A decision can be wrong but incidentally
-coincide with a reading that is indicative of a relevant
-reading. Error rates multiply in proportion to the number of steps in
-a sequence: more choice, more chance to be wrong.
-
-\bigskip
-
-HERE
-
-Taking this together we calculate, for each critical
-sentence-intonation pair $k$ a target probability vector $\myvec{t}^k
-=
+bias factor $q \in [0;1]$. This bias is a global parameter held
+constant over all conditions, because we think of it as a general
+tendency to answer early or late in the incremental verification
+task. The bias factor captures whether there is a tendency to access
+readings that appear earlier ($q > .5$) or later ($q <.5$) in the
+sequence. In the \as-sequences, the literal reading can be judged
+first, then the local and then the global reading. So we will assume
+that $p_{\text{lit}}$ is multiplied by $q$, that $p_{\text{loc}}$ is
+multiplied by $(1-q)q$ and that $p_{\text{glb}}$ is multiplied by
+$(1-q)^2$, when determining the eventual weights of readings.
+
+Finally, we also allow for mistakes. To keep things as simple as
+possible (no consideration for spill-overs, late decisions,
+preferences to unravel completely before judging etc.), we assume that
+there is a fixed error rate $e^k \in [0;1]$ for each relevant
+condition $k$. We allow for different error rates for different
+conditions, because we want to allow for the possibility that some
+sentence types (e.g., non-monotonic quantifiers) or some kind of
+intonation (e.g., the \ec-cues) might be harder to process. A decision
+can be wrong but incidentally coincide with an answer that is
+indicative of a relevant reading. Error rates multiply in proportion
+to the number of steps in a sequence: more choice, more chance to be
+wrong.
+
+Taking this together we calculate, for each pair $k$ of target
+sentence type and intonation type, a probability vector $\myvec{t}^k =
 \tuple{t^k_{\text{lit}},t^k_{\text{loc}},t^k_{\text{glb}},t^k_{\text{err}}}$
-with which we expect an answer to be classified as LIT, LOC, GLB or as
-an error. For example, for AS-N, where LIT can be judged before GLB
-before LOC, we get:
+with which we expect an answer to be classified as literal, local,
+global or as error. For example, for \as-sentences with neutral
+intonation, where literal can be judged before global before local, we
+get:
 \begin{align*}
@@
 Two remarks. The vector $\myvec{t}^k$ should be normalized eventually,
-which is why $\propto$ is used instead of $=$. Also, the probability
-of error $t^{\text{as-n}}_{\text{err}}$ comes from the observation
-that there are 15 positions in total in an AS-sequence at which
-subjects can make an erroneous choice, but we have accounted for three
-of these already as adding to the count of answers indicative of
+which is why `$\propto$' is used above instead of `$=$.' Also, the
+probability of error $t^{\text{as-n}}_{\text{err}}$ comes from the
+observation that there are 15 positions in total in an \as-sequence at
+which subjects can make an erroneous choice, but we have accounted for
+three of these already as adding to the count of answers indicative of
 relevant readings.
@@
 \tuple{t^k_{\text{late}},t^k_{\text{early}},t^k_{\text{err}}}$ for
-each preference-related control condition $k$, taking into account
-which reading can be judged first and the length of the respective
-sequences.
+each preference-related control sentence under intonation $k$, taking
+into account which reading can be judged first and the length of the
+respective sequences.
 

### 2014-05-28 text/paper/paper4.tex
integrated the Bayesian analysis

@@
 
-\begin{figure}[t]
+\begin{figure}[]
   \centering
@@
 
-    \node[left of = anchor, node distance= 0.5cm] (k) {$k \in
-      \set{\text{as-n, as-e, \dots}}$};
+    \node[left of = anchor, node distance= 0.95cm] (k) {$k \in
+      \set{\text{\as-ntr, \as-acc, \dots}}$};
 
@@
 
-    \draw[->] (q)--(t);
-
-    \draw[->] (p)--(t);
-
-    \draw[->] (e)--(t);
+    \draw[->,shorten >=0.05cm] (q)--(t);
+
+    \draw[->,shorten >=0.05cm] (p)--(t);
+
+    \draw[->,shorten >=0.05cm] (e)--(t);
 
@@
 
-    \begin{scope}[xshift = 7.5cm, node distance = 1cm]
+    \begin{scope}[xshift = 6.5cm, node distance = 1cm]
 
@@
 
-      \node[above of = td] (pd) {$\myvec{p}_k =
-        \text{Dirichlet}(\tuple{\nicefrac{1}{k}, \nicefrac{1}{k}, \dots})$};
+      \node[above of = td] (pd) {$\myvec{p}_k \sim
+        \text{unbiased Dirichlet}$};
 
@@
   \end{tikzpicture}
-  \caption{Probabilistic graphical model}
+  \caption{Probabilistic graphical model. All nodes represent
+    variables, arrows represent functional relations between them.
+    Using conventions of \citet{LeeWagenmakers2013:Bayesian-Cognit},
+    the higher a node, the more latent it is. Square nodes represent
+    discrete-valued variables, circular squares represent
+    continuous-valued variables. Gray squares show the observable
+    variables. Double-lined nodes show deterministic dependency on
+    values of input nodes. The variables in the box are repeated for
+    each of the $k$ relevant conditions.}
   \label{fig:model_graph}
@@
 
-\newpage
+\paragraph{Model fitting.} We use JAGS
+\citep{Plummer2003:JAGS:-A-Program} to estimate the posteriors over
+paramater values given our data. Results reported here are based on
+two chains of 10.000 samples from the joint posterior distribution
+MCMC sampling, obtained after an initial burn-in of 10.000 steps. The
+latter guaranteed convergence.
+
+, we obtain estimates
+for the posterior of the latent parameters given the data. To check
+whether the model yields sensible results we first look at the
+preference-related control conditions.
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{pics/post_salience_TF.pdf}
+  \caption{Estimated posteriors for the relative salience of \lc- and
+    \ec-readings for different intonational cues. The lines under the
+    curves mark the estimated 95\% HDIs (see Footnote~\ref{fn:HDI}).}
+  \label{fig:Posterior_TF}
+\end{figure}
+%
+Estimates for the posteriors over relative salience levels for
+target-related controls are plotted in
+Figure~\ref{fig:Posterior_TF}. The results are exactly as we would
+expect them to be. Given our data, we should believe that the
+\lc-reading is most prominent. But the level of prominence varies with
+accentuation. Under prosody that we hypothesized would favor the
+\lc-reading, the contrast is most pronounced. Contrarily, accentuation
+that we hypothesized favors the \ec-reading we are no longer justified
+in believing that the late-closure reading is certainly preferred
+(witness the clearly overlapping 95\% HDIs).\footnote{\label{fn:HDI} A
+  95\% Highest Density Interval (HDI) is a convex region of values
+  over which 95\% of the distribution's probability density is
+  divided, such that no value outside of that region has higher
+  probability density than any point within
+  \citep{Kruschke2011:Doing-Bayesian-}. Intuitively speaking, the 95\%
+  HDI is the set of values which we may believe to be true with some
+  confidence; what falls outside this region is what can be excluded
+  with relative safety.}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{pics/post_salience.pdf}
+  \caption{Posteriors over relative salience of target readings in
+    critical conditions.}
+  \label{fig:Posterior_T}
+\end{figure}
+
+Estimates of posteriors over salience of readings in the target
+conditions are given in Figure~\ref{fig:Posterior_T}. In the
+\es-conditions, literal readings are by far the most salient, followed
+by local, followed by global readings. There does not appear to be a
+significant effect of intonation (by visual comparison of 95\%
+HDIs). For \as-sentences, the same preference order holds in tendency,
+but we cannot assert with full confidence that local readings are
+attested or that they are preferred over global readings (see below).
+
+Posteriors over error rates are conceptually less interesting, and we
+will skip them here. Posteriors over the sequential bias parameter are
+shown in Figure~\ref{fig:post_q}, and show that, given the model and
+our data, we have reason for believing in a bias for late responses.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{pics/post_q.pdf}
+  \caption{Estimated Posteriors over global sequential bias parameter
+    $q$.}
+  \label{fig:post_q}
+\end{figure}
+
+\paragraph{Model validation.} As a crude sanity check that our model
+is able to predict the observed data, we gathered 10.000 random values
+from the posterior predictive distribution and found a highly
+significant correlation between these and the observed data ($R^2 =
+0.987$, $p < 0.001$).
+
+\paragraph{Hypothesis testing.} We are chiefly interested in two
+questions: (i) which readings are available? and (ii) what is the
+preference order over readings?
+
+The first question can be answered by looking at the HDIs of the
+posteriors of the candidate readings. The HDIs give the region of the
+95\% least unbelievable parameter values, given the data and the
+model. We would like to check the hypothesis that a given reading is
+unavailable, i.e., its activation value in the probabilistic model is
+equal to 0, or close to zero for practical purposes (Region of
+Practical Equivalence, ROPE). We reject the ``null-hypothesis'' that
+the true value is 0 if its ROPE lies entirely outside the 95\% HDI; we
+accept the ``null-hypothesis'' if the ROPE lies entirely within the
+95\% HDI \citep[][Ch.~12]{Kruschke2011:Doing-Bayesian-}. The following
+table lists approximations of the 95\% HDIs for each condition and
+reading:
+
+\begin{center}
+  \begin{tabular}{lllllll}
+    & lit & loc & glb & \\ \midrule
+    \as-ntr & $(0.924 , 1)$ & $(0 , 0.068)$
+    & $(0 , 0.022)$ \\
+    \as-acc 
+    & $(0.816 , 0.964)$
+    & $(0.028 , 0.152)$
+    & $(0 , 0.066)$ \\
+    \es-ntr 
+    & $(0.665 , 0.873)$
+    & $(0.117 , 0.323)$
+    & $(0 , 0.024)$ \\
+    \es-acc 
+    & $(0.634 , 0.851)$
+    & $(0.139 , 0.356)$
+    & $(0 , 0.022)$ 
+  \end{tabular}
+\end{center}
+
+\noindent We should thus accept the hypothesis that there are no
+global readings at all, and no local readings for \as-sentence under
+neutral intonation. There is support for a belief in local readings in
+the \as-acc condition up to a ROPE of $[0;0.028)$.
+
+The question after the preference relations between readings can be
+answered in a similar way. Here, we look at the posterior beliefs
+about the differences of activation strengths and ask whether these
+posterior beliefs allow us to safely conclude that differences are
+bigger than zero or not. It is obvious enough that literal readings
+are always the most preferred, and that local readings are preferred
+over global readings for \es-sentences. Figure~\ref{fig:PostDiffTAS}
+shows the posteriors over differences between local and global
+readings for \as-sentences. Since the 95\% HDIs include 0, the data
+provides no ground for confidence that, given the model, local
+readings of \as-sentences are preferred over global ones, despite the
+obvious tendency. In sum, with the exception of remaining uncertainty
+about local readings of \as-sentences, the model and the data suggest
+that global readings are absent entirely, while literal readings are
+preferred over local readings.
+
+\begin{figure}
+  \centering
+  \subfloat[neutral][]{
+      \includegraphics[width=0.45\textwidth]{PostDiffT_ASntr.pdf}
+  }
+  \hfill
+  \subfloat[accented][]{
+      \includegraphics[width=0.45\textwidth]{PostDiffT_ASntr.pdf}
+  }
+  \caption{Posteriors over differences between salience levels for
+    local and global readings of \as-sentences.}
+  \label{fig:PostDiffTAS}
+\end{figure}
 

### 2014-05-29 text/paper/paper4.tex
Bayesian model revision, simpler presentation of raw results

@@
 descriptive results, we present statistical analyses using log-linear
-models (i.e., generalized linear regression for count data). To
-complement the picture, we also report a Bayesian analysis that probes
-specifically into the preference relations between candidate readings.
+models. We complement these with a Bayesian analysis that is sensitive
+to the sequential nature of the incremental verification task and
+probes specifically into the preference relations between candidate
+readings.
 
@@
 
-The answers obtained for the four target conditions are depicted in
-Figure \ref{fig:JudgmentsK2}.
+% \begin{figure}[t] 
+% \centering
+
+% \includegraphics[width=0.9\textwidth]{positional_answers_critical.pdf}
+
+% \caption{Answers for the \as- and \es-sequences. Bars show the total
+%   number of \emph{yes} (up) and \emph{no} judgments (down) collected
+%   at each step during a sequence. E.g., we recorded a total of 103
+%   \emph{yes} judgments at the third position in the \as-sequence with
+%   neutral intonation, which corresponds to 103 answers that were
+%   classified as \emph{literal} answers. Notice that the \as-condition
+%   had seven steps, the \es-condition only five.}
+% \label{fig:JudgmentsK2}
+% \end{figure}
 %
-\begin{figure}[t]
+
+\begin{table}
   \centering
-
-\includegraphics[width=0.9\textwidth]{positional_answers_critical.pdf}
-
-\caption{Answers for the \as- and \es-sequences. Bars show the total
-  number of \emph{yes} (up) and \emph{no} judgments (down) collected
-  at each step during a sequence. E.g., we recorded a total of 103
-  \emph{yes} judgments at the third position in the \as-sequence with
-  neutral intonation, which corresponds to 103 answers that were
-  classified as \emph{literal} answers. Notice that the \as-condition
-  had seven steps, the \es-condition only five.}
-\label{fig:JudgmentsK2}
-\end{figure}
+  \begin{tabular}{lcccccccc@{\hskip 0.6cm}cccc}
+    && \multicolumn{7}{c}{truth value at step}
+    & \multicolumn{4}{c}{classification}
+    \\ \cmidrule(l){3-9} \cmidrule(r){10-13}
+    condition &
+    & 1
+    & 2
+    & 3
+    & 4
+    & 5
+    & 6
+    & 7
+    & \lit
+    & \loc
+    & \glb
+    & err \\ \midrule
+    \as-ntr 
+    & T & 1 & 1 & \textbf{103} & 2 & \textbf{0} & 0 & 2 
+    & 103 & 3 & 0 & 8 \\
+    & F & 0 & 0 & 0 & 0 & 2 & 0 & \textbf{3} \\ 
+    \addlinespace[0.25cm]
+    \as-acc
+    & T & 0 & 1 & \textbf{99} & 2 & \textbf{2} & 0 & 1 
+    & 99 & 8 & 5 & 5 \\
+    & F & 0 & 0 & 1 & 0 & 0 & 0 & \textbf{8} \\
+    \addlinespace[0.25cm]
+    \es-ntr
+    & T & 0 & 11 & 3 & 1 & \textbf{14} & - & - 
+    & 78 & 14 & 0 & 22 \\
+    & F & 0 & \textbf{0} & \textbf{78} & 5 & 2 & - & - \\
+    \addlinespace[0.25cm]
+    \es-acc
+    & T & 0 & 10 & 3 & 0 & \textbf{16} & - & - 
+    & 78 & 16 & 0 & 20 \\
+    & F & 0 & \textbf{0} & \textbf{78} & 5 & 2 & - & -
+  \end{tabular}
+  \caption{Observed truth-value judgments in critical conditions. The
+    left-hand part of the table shows the number of \emph{true} and
+    \emph{false} responses obtained at each step in the sequence. The
+    right-hand part shows the count for our imposed classification
+    scheme. The answer counts indicative of relevant readings are
+    given in bold-face on the left-hand side.}
+  \label{tab:count_data_CC}
+\end{table}
+
 %
-We coded these answers as {\it literal}, {\it global} or {\it local}
-if they were as expected under one of these readings and as {\it
-  error} if not. The distribution of readings thus coded is given in
-Table~\ref{tab:CC-ContingencyTable}. The table also classifies
-responses according to the position (1--3) in the experiment, i.e.,
-whether it was the first, second or third time that a participant saw
-the critical condition in question.
+% \begin{table}[h]
+% \centering
+
+% \begin{tabular}{lccccc}
+%   condition & position & \multicolumn{4}{c}{response type} \\ \cmidrule(r){3-6}
+%   && \emph{literal} & \emph{local} & \emph{global} & \emph{error} \\
+%   \midrule \addlinespace[0.15cm]
+%   \textbf{\as neutral} 
+%   & Pos 1 & 35 &  0 & 0 & 3 \\
+%   & Pos 2 & 35 &  1 & 0 & 2 \\
+%   & Pos 3 & 33 &  2 & 0 & 3 \\ \addlinespace[0.15cm]
+%   & \textbf{Total} & \textbf{103} &  \textbf{3} & \textbf{0} &
+%   \textbf{8} \\
+%   \addlinespace[0.25cm]
+%   \textbf{\as accented} 
+%   & Pos 1 & 33 &  2 & 1 & 2 \\
+%   & Pos 2 & 33 &  3 & 1 & 1 \\
+%   & Pos 3 & 33 &  3 & 0 & 2 \\ \addlinespace[0.15cm]
+%   & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2} &
+%   \textbf{5} \\
+%   \addlinespace[0.25cm]
+%   \textbf{\es neutral} 
+%   & Pos 1 & 26 &  5 & 0 & 7 \\
+%   & Pos 2 & 26 &  3 & 0 & 9 \\
+%   & Pos 3 & 26 &  6 & 0 & 6 \\ \addlinespace[0.15cm]
+%   & \textbf{Total} & \textbf{78} &  \textbf{14} & \textbf{0} &
+%   \textbf{22} \\
+%   \addlinespace[0.25cm]
+%   \textbf{\es accented} 
+%   & Pos 1 & 26 &  6 & 0 & 6 \\
+%   & Pos 2 & 24 &  5 & 0 & 9 \\
+%   & Pos 3 & 28 &  5 & 0 & 5 \\ \addlinespace[0.15cm]
+%   & \textbf{Total} & \textbf{78} &  \textbf{16} & \textbf{0} &
+%   \textbf{20}
+% \end{tabular}
+
+% \caption{Contingency table of classified responses for the critical
+%   conditions. The factor position encodes whether participants saw the
+%   condition in question for the first, second or third time during the
+%   whole experiment.}
+% \label{tab:CC-ContingencyTable}
+% \end{table}
 %
-\begin{table}[h]
-\centering
-
-\begin{tabular}{lccccc}
-  condition & position & \multicolumn{4}{c}{response type} \\ \cmidrule(r){3-6}
-  && \emph{literal} & \emph{local} & \emph{global} & \emph{error} \\
-  \midrule \addlinespace[0.15cm]
-  \textbf{\as neutral} 
-  & Pos 1 & 35 &  0 & 0 & 3 \\
-  & Pos 2 & 35 &  1 & 0 & 2 \\
-  & Pos 3 & 33 &  2 & 0 & 3 \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{103} &  \textbf{3} & \textbf{0} &
-  \textbf{8} \\
-  \addlinespace[0.25cm]
-  \textbf{\as accented} 
-  & Pos 1 & 33 &  2 & 1 & 2 \\
-  & Pos 2 & 33 &  3 & 1 & 1 \\
-  & Pos 3 & 33 &  3 & 0 & 2 \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2} &
-  \textbf{5} \\
-  \addlinespace[0.25cm]
-  \textbf{\es neutral} 
-  & Pos 1 & 26 &  5 & 0 & 7 \\
-  & Pos 2 & 26 &  3 & 0 & 9 \\
-  & Pos 3 & 26 &  6 & 0 & 6 \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{78} &  \textbf{14} & \textbf{0} &
-  \textbf{22} \\
-  \addlinespace[0.25cm]
-  \textbf{\es accented} 
-  & Pos 1 & 26 &  6 & 0 & 6 \\
-  & Pos 2 & 24 &  5 & 0 & 9 \\
-  & Pos 3 & 28 &  5 & 0 & 5 \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{78} &  \textbf{16} & \textbf{0} &
-  \textbf{20}
-\end{tabular}
-
-\caption{Contingency table of classified responses for the critical
-  conditions. The factor position encodes whether participants saw the
-  condition in question for the first, second or third time during the
-  whole experiment.}
-\label{tab:CC-ContingencyTable}
-\end{table}
-%
-The majority of answers are indicative of a literal reading (90.35\% /
-86.84\% in neutral / accented \as-conditions, and 68.42\% in both
-neutral / accented \es-conditions). Only two answers across all
-critical conditions fall into the category indicative of global
+
+Judgements obtained for the four target conditions are listed in
+Table~\ref{tab:count_data_CC}. We coded these answers as {\it
+  literal}, {\it global} or {\it local} if they were as expected under
+one of these readings and as {\it error} if not. The majority of
+answers are indicative of a literal reading (90.35\% / 86.84\% in
+neutral / accented \as-conditions, and 68.42\% in both neutral /
+accented \es-conditions). Only two answers across all critical
+conditions fall into the category indicative of global
 readings. Judgements indicative of local readings, on the other hand,
@@
 \as-conditions, but 19.30\% / 17.54\% in the neutral / accented
-\es-conditions. A look at Figure~\ref{fig:JudgmentsK2} reveals that
-there is some systematicity in 'error' answers. Most answers that we
-classified as 'errors' are plausibly explained as a few random errors,
-a handful of mistakes resulting from confusing buttons for \emph{true}
-and \emph{false} and a few 'spill-overs' where participants gave
-responses one position too late. There is one notable exception,
-though. A substantial number of \emph{true} responses where given at
-the second position of \es-sequences (9.65\% / 8.77\%) which is shown
-in Figure~\ref{fig:exseqES2}. Although this position in the sequence
-is the critical position to reveal a global reading, the latter would
-be indicated by a \emph{false} response. It appears that subjects read
+\es-conditions. A look at the right-hand side of
+Table~\ref{tab:count_data_CC} reveals that there is some systematicity
+in 'error' answers. Most answers that we classified as 'errors' are
+plausibly explained as a few random errors, a handful of mistakes
+resulting from confusing buttons for \emph{true} and \emph{false} and
+a few 'spill-over errors' where participants gave responses one
+position too late. There is one notable exception, though. A
+substantial number of \emph{true} responses where given at the second
+position of \es-sequences (9.65\% / 8.77\%) which is shown in
+Figure~\ref{fig:exseqES2}. Although this position in the sequence is
+the critical position to reveal a global reading, the latter would be
+indicated by a \emph{false} response. It appears that subjects read
 \es-sentences as if the non-monotonic quantifier \emph{exactly one}
@@
 21 answers in this category come from 5 subjects, while the remaining
-5 were single answers by 5 different subjects. \todo{subjects 1, 9,
-  12, 21, 84} This suggests that at least for some subjects
-non-monotonic quantifiers were problematic. \todo{how to deal with
-  this in the future?}
-
-We fitted generalized linear models to the contingency table data in
-Table~\ref{tab:CC-ContingencyTable}, using factors \textsc{Condition}
-with levels \as and \es, \textsc{Accent} with levels \emph{neutral}
-and \emph{accented}, and \textsc{Position} with levels 1 through 3 to
-predict the dependent factor \textsc{Reading} with levels
-\emph{literal}, \emph{local}, and \emph{other}. The latter lumps
-\emph{global} and \emph{error} responses together, because otherwise
-we would not have enough cell counts to apply log-linear
-regression. We selected the ``best'' predictor of the data by a
-gradient search over hierarchical models in terms of AICs, starting
-from the saturated model. The best model takes main factors
-\textsc{Response} and \textsc{Condition} into account, as well as the
-interaction term \textsc{Response:Condition} ($\chi^2 = 17.19$,
-$df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$ of the
-saturated model)). Crucially, factors \textsc{Position} and
+5 were single answers by 5 different subjects.
+% subjects 1, 9, 12, 21, 84
+This suggests that at least for some subjects non-monotonic
+quantifiers were problematic. (We will come back to this point later.)
+
+We fitted generalized linear models to the count data in
+Table~\ref{tab:count_data_CC}, using factors \textsc{Condition} with
+levels \as and \es, \textsc{Accent} with levels \emph{neutral} and
+\emph{accented}, and \textsc{Position} with levels 1 through 3 (coding
+whether it was the first, second or third time that a participant saw
+a critical condition during the experiment) to predict the dependent
+factor \textsc{Reading} with levels \emph{literal}, \emph{local}, and
+\emph{other}. The latter lumps \emph{global} and \emph{error}
+responses together, because otherwise we would not have enough cell
+counts to apply log-linear regression. We determined the ``best''
+predictor of the data by a gradient search over hierarchical models in
+terms of AICs, starting from the saturated model. The best model takes
+main factors \textsc{Response} and \textsc{Condition} into account, as
+well as the interaction term \textsc{Response:Condition} ($\chi^2 =
+17.19$, $df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$
+of the saturated model)). Crucially, factors \textsc{Position} and
 \textsc{Accent} are spurious in the best model. This suggests that
@@
 there were no learning or fatigation effects and that accentuation did
-not influence answer patterns significantly.
+not influence answer patterns significantly (at this level of
+abstraction).
 
@@
   \caption{Coefficients of the ``best'' log-linear model for the count
-    data in Table~\ref{tab:CC-ContingencyTable}. Notice that factor
-    levels \emph{local} do not cause a significant shift in counts,
-    given reference level
-    \emph{false}.}
+    data in Table~\ref{tab:count_data_CC}.}
   \label{tab:Coefficients-CC}
@@
 
-Inspection of the coefficients of the ``best'' model suggests that the
-distinction between levels \emph{local} and \emph{other} in factor
-\textsc{Reading} might not be necessary (see
-Table~\ref{tab:Coefficients-CC}). In order to test whether there is
-support for the postulation of local readings, we therefore compared
-the previous ``best'' predictor to a model that only differs from the
-former in that it subsumes the level \emph{local} of factor
-\textsc{Reading} under level \emph{other} as well
-\citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model comparison
-reveals that there is no significant improvement in explanatory power
-($Pr(|\chi|) = 0.2689$) of the more complex model that includes the
-level \emph{local} (residual df=30, residual deviance = 10.497) over the simpler
-model without this level (residual df=32, residual deviance = 13.124,
-AIC=157.268).
+Inspection of the coefficients of the ``best'' model in
+Table~\ref{tab:Coefficients-CC} suggests that the distinction between
+levels \emph{local} and \emph{other} in factor \textsc{Reading} might
+not be necessary: factor levels \emph{local} do not cause a
+significant shift in counts, given reference level \emph{false}. In
+order to test whether there is support for the postulation of local
+readings, we therefore compared the previous ``best'' predictor to a
+model that only differs from the former in that it subsumes the level
+\emph{local} of factor \textsc{Reading} under level \emph{other} as
+well \citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model
+comparison reveals that there is no significant improvement in
+explanatory power ($Pr(|\chi|) = 0.2689$) of the more complex model
+that includes the level \emph{local} (residual df=30, residual
+deviance = 10.497) over the simpler model without this level (residual
+df=32, residual deviance = 13.124, AIC=157.268).
 
@@
 that local readings are infrequent because subjects tend to exit early
-in the sequence, rather than late. This is why we need
-preference-related controls and a more fine-grained analysis
-eventually.
+in the sequence, rather than late. Or it might be that our count for
+local answers is exaggerated by a bias to answer later in the
+sequence. This is why we need preference-related controls and a more
+fine-grained analysis eventually.
 
@@
 preference-related control conditions are shown in
-Figure~\ref{Fig:TF_judgments}.\fn{We removed 19 data points for the
+Table~\ref{tab:count_data_TF}.\fn{We removed 19 data points for the
   \ec-conditions because of a coding mistake that presented subjects
@@
   classifying them as \emph{errors} does not change the qualitative
-  results of the reported analyses.}
-%
-\begin{figure}[]
+  results of the reported analyses.} Judgments were coded as \ec or as
+\lc if they were as expected under one of these readings, and as
+\emph{error} if they were not. As expected, most answers classify as
+\lc-readings, fewer as \ec-readings. Moreover, intonation does seem to
+have the expected effect as well: as compared to neutral intonation,
+\lc-cueing intonation increases the count for \lc-readings, while
+\ec-cueing increases the count for \ec-readings. If we compare the
+number of \lc- or \ec-readings for each intonation type across
+sequences, we see that there are always more answers indicative of the
+relevant readings when that reading can be judged later in the
+sequence. This suggests a general tendency to answer later in the
+sequence, rather than at the earliest possible step.
+
+\begin{table}
   \centering
-
- \subfloat[][\LC-sequence]{
-
-\includegraphics[width=0.9\textwidth]{positional_answers_TF_LC.pdf}
-}
-
- \subfloat[][\EC-sequence]{
-
-\includegraphics[width=0.9\textwidth]{positional_answers_TF_EC.pdf}
-}
-
-\caption{Answers for \lc-sequences and \ec-sequences. \emph{True}
-  judgements are plotted upwards for each step in the sequence,
-  \emph{false} judgements downwards.}
-\label{Fig:TF_judgments}
-\end{figure}
-%
-Judgments were coded as \ec or as \lc if they were as expected under
-one of these readings, and as \emph{error} if they were not. The
-distributions of readings thus coded is given in
-Table~\ref{tab:CC-ContingencyTable-TF}. Some subjects saw 4 trials of
-some target-related control conditions, but the table and the
-subsequent analysis of the count data only looks at the data from the
-first three encounters. This is because otherwise we would see a
-spurious main effect of \textsc{Position} that is just needed to
-account for the less frequent occurrence of judgements at position 4.
-%
-\begin{table}[]
-\centering
-
-\begin{tabular}{lcccc}
-  condition & position & \multicolumn{3}{c}{response type} \\ \cmidrule(r){3-5}
-  && \emph{LC} & \emph{EC} & \emph{error}  \\
-  \midrule \addlinespace[0.15cm]
-  \textbf{\lc neutral} 
-  & Pos 1 & 27 &  7  & 4 \\
-  & Pos 2 & 23 &  11 & 4 \\
-  & Pos 3 & 26 &  9  & 3 \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{76} &  \textbf{27} & \textbf{11}  \\
+  \begin{tabular}{lcccccccc@{\hskip 0.6cm}ccc}
+    && \multicolumn{7}{c}{truth value at step}
+    & \multicolumn{3}{c}{classification}
+    \\ \cmidrule(l){3-9} \cmidrule(r){10-12}
+    condition &
+    & 1
+    & 2
+    & 3
+    & 4
+    & 5
+    & 6
+    & 7
+    & \lc
+    & \ec
+    & err \\ \midrule
+    \lc-ntr 
+    & T & 0 & 0 & \textbf{87} & 1 & 0 & 9 & 0 
+    & 87 & 32 & 13 \\
+    & F & 0 & 0 & 3 & 0 & 0 & \textbf{32} & 0 \\
     \addlinespace[0.25cm]
-  \textbf{\lc with \lc cue} 
-  & Pos 1 & 26 &  7 & 5  \\
-  & Pos 2 & 31 &  5 & 2  \\
-  & Pos 3 & 33 &  3 & 2  \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{90} &  \textbf{15} & \textbf{9}  \\
+    \lc-\lc-cue
+    & T & 0 & 0 & \textbf{108} & 1 & 1 & 7 & 0 
+    & 108 & 16 & 10 \\
+    & F & 0 & 0 & 1 & 0 & 0 & \textbf{16} & 0 \\
     \addlinespace[0.25cm]
-  \textbf{\lc with \ec cue} 
-  & Pos 1 & 14 &  17 & 7  \\
-  & Pos 2 & 15 &  16 & 7  \\
-  & Pos 3 & 15 &  17 & 6  \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{44} &  \textbf{50} & \textbf{20}  \\
+    \lc-\ec-cue
+    & T & 0 & 0 & \textbf{51} & 4 & 0 & 7 & 0 
+    & 51 & 59 & 25 \\
+    & F & 2 & 1 & 7 & 0 & 0 & \textbf{59} & 1 \\
     \addlinespace[0.25cm]
-  \textbf{\ec neutral} 
-  & Pos 1 & 22 &  6 & 5  \\
-  & Pos 2 & 28 &  6 & 4  \\
-  & Pos 3 & 29 &  7 & 2  \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{79} &  \textbf{19} & \textbf{11}  \\
+    \ec-ntr
+    & T & 0 & 0 & 0 & 0 & \textbf{92} & - & - 
+    & 92 & 22 & 13 \\
+    & F & 1 & 0 & \textbf{22} & 6 & 6 & - & - \\
     \addlinespace[0.25cm]
-  \textbf{\ec with \lc cue} 
-  & Pos 1 & 30 &  5 & 1  \\
-  & Pos 2 & 32 &  5 & 0  \\
-  & Pos 3 & 31 &  3 & 2  \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{93} &  \textbf{13} & \textbf{3}  \\
+    \ec-\lc-cue
+    & T & 0 & 0 & 0 & 0 & \textbf{112} & - & - 
+    & 112 & 13 & 4 \\
+    & F & 0 & 1 & \textbf{13} & 1 & 2 & - & - \\
     \addlinespace[0.25cm]
-  \textbf{\ec with \ec cue} 
-  & Pos 1 & 19 &  10 & 7  \\
-  & Pos 2 & 19 &  7  & 9  \\
-  & Pos 3 & 19 &  7  & 11  \\ \addlinespace[0.15cm]
-  & \textbf{Total} & \textbf{57} &  \textbf{24} & \textbf{27}  \\
+    \ec-\ec-cue
+    & T & 0 & 0 & 0 & 0 & \textbf{65} & - & - 
+    & 65 & 31 & 30 \\
+    & F & 2 & 0 & \textbf{31} & 8 & 20 & - & - \\
+    \addlinespace[0.25cm]
+
   \end{tabular}
-
-\caption{Contingency table of classified responses for the
-  preference-related controls. As before, the factor position encodes
-  whether participants saw the condition in question for the first,
-  second or third time during the whole experiment.}
-\label{tab:CC-ContingencyTable-TF}
+  \caption{Observed truth-value judgments in preference-related controls.}
+  \label{tab:count_data_TF}
 \end{table}
 
-As expected, most answers classify as \lc-readings, fewer as
-\ec-readings. Moreover, intonation does seem to have the expected
-effect as well: as compared to neutral intonation, \lc-cueing
-intonation increases the count for \lc-readings, while \ec-cueing
-increases the count for \ec-readings. If we compare the number of \lc-
-or \ec-readings for each intonation type across sequences, we see that
-there are always more answers indicative of the relevant readings when
-that reading can be judged later in the sequence. This suggests a
-general tendency to answer later in the sequence, rather than at the
-earliest possible step.
+% \begin{figure}[]
+% \centering
+
+%  \subfloat[][\LC-sequence]{
+
+% \includegraphics[width=0.9\textwidth]{positional_answers_TF_LC.pdf}
+% }
+
+%  \subfloat[][\EC-sequence]{
+
+% \includegraphics[width=0.9\textwidth]{positional_answers_TF_EC.pdf}
+% }
+
+% \caption{Answers for \lc-sequences and \ec-sequences. \emph{True}
+%   judgements are plotted upwards for each step in the sequence,
+%   \emph{false} judgements downwards.}
+% \label{Fig:TF_judgments}
+% \end{figure}
+
+% \begin{table}[]
+% \centering
+
+% \begin{tabular}{lcccc}
+%   condition & position & \multicolumn{3}{c}{response type} \\ \cmidrule(r){3-5}
+%   && \emph{LC} & \emph{EC} & \emph{error}  \\
+%   \midrule \addlinespace[0.15cm]
+%   \textbf{\lc neutral} 
+%   & Pos 1 & 27 &  7  & 4 \\
+%   & Pos 2 & 23 &  11 & 4 \\
+%   & Pos 3 & 26 &  9  & 3 \\ \addlinespace[0.15cm]
+%   & \textbf{Total} & \textbf{76} &  \textbf{27} & \textbf{11}  \\
+%   \addlinespace[0.25cm]
+%   \textbf{\lc with \lc cue} 
+%   & Pos 1 & 26 &  7 & 5  \\
+%   & Pos 2 & 31 &  5 & 2  \\
+%   & Pos 3 & 33 &  3 & 2  \\ \addlinespace[0.15cm]
+%   & \textbf{Total} & \textbf{90} &  \textbf{15} & \textbf{9}  \\
+%   \addlinespace[0.25cm]
+%   \textbf{\lc with \ec cue} 
+%   & Pos 1 & 14 &  17 & 7  \\
+%   & Pos 2 & 15 &  16 & 7  \\
+%   & Pos 3 & 15 &  17 & 6  \\ \addlinespace[0.15cm]
+%   & \textbf{Total} & \textbf{44} &  \textbf{50} & \textbf{20}  \\
+%   \addlinespace[0.25cm]
+%   \textbf{\ec neutral} 
+%   & Pos 1 & 22 &  6 & 5  \\
+%   & Pos 2 & 28 &  6 & 4  \\
+%   & Pos 3 & 29 &  7 & 2  \\ \addlinespace[0.15cm]
+%   & \textbf{Total} & \textbf{79} &  \textbf{19} & \textbf{11}  \\
+%   \addlinespace[0.25cm]
+%   \textbf{\ec with \lc cue} 
+%   & Pos 1 & 30 &  5 & 1  \\
+%   & Pos 2 & 32 &  5 & 0  \\
+%   & Pos 3 & 31 &  3 & 2  \\ \addlinespace[0.15cm]
+%   & \textbf{Total} & \textbf{93} &  \textbf{13} & \textbf{3}  \\
+%   \addlinespace[0.25cm]
+%   \textbf{\ec with \ec cue} 
+%   & Pos 1 & 19 &  10 & 7  \\
+%   & Pos 2 & 19 &  7  & 9  \\
+%   & Pos 3 & 19 &  7  & 11  \\ \addlinespace[0.15cm]
+%   & \textbf{Total} & \textbf{57} &  \textbf{24} & \textbf{27}  \\
+% \end{tabular}
+
+% \caption{Contingency table of classified responses for the
+%   preference-related controls. As before, the factor position encodes
+%   whether participants saw the condition in question for the first,
+%   second or third time during the whole experiment.}
+% \label{tab:CC-ContingencyTable-TF}
+% \end{table}
 
@@
 28 \emph{false} answers at step 5 where \emph{true} answers would be
-taken as indicative of \lc-readings.\fn{A general tendency to answer
-  later in the sequence would explain this. The reason why we do not
-  see a similar effect in the critical conditions, might be because
-  the literal reading is so dominant.} Finally, intonation patterns
+taken as indicative of \lc-readings.% \fn{A general tendency to answer
+% later in the sequence would explain this. The reason why we do not
+% see a similar effect in the critical conditions, might be because
+% the literal reading is so dominant.}
+Finally, intonation patterns
 that cue \ec-readings seem to have led to more mistakes than other
@@
 
-As for the critical conditions, we compute logistic regression models
+As for the critical conditions, we computed logistic regression models
 including factors \textsc{Reading} with levels \lc, \ec and
@@
   \caption{Coefficients of the ``best'' log-linear model for the count
-    data in Table~\ref{tab:CC-ContingencyTable-TF}.}
+    data in Table~\ref{tab:count_data_TF}.}
   \label{tab:Coefficients-TF}
@@
 sequence. If such a preference for late responses holds for critical
-conditions as well, then the marginal numer of local responses that we
-observed is more likely overemphasized by our sequential decision task
-than that it is underemphasized. The following Bayesian analysis
-further probes into this matter in order to establish how strongly the
-sequence-effect might have emphasized local readings and, from there,
-whether we should uphold belief in local readings.
+conditions as well, then the rather small numer of local responses
+that we observed is more likely overemphasized by our sequential
+decision task than that it is underemphasized. The following Bayesian
+analysis further probes into this matter in order to establish how
+strongly the sequence-effect might have emphasized local readings and,
+from there, whether we should uphold belief in local readings.
 
@@
 The previous regression-based analyses did not take the sequential
-nature of the task into account. We initially hypothesized that
-subjects might exit as early as possible, but the data from the
-target-related controls suggests otherwise. The following paragraphs
-spell out a simple Bayesian cognitive model that computes the
-likelihood of answer patterns for different latent sequential biases
-and reading preferences. We use the data to estimate the posterior
-likelihood of these latent parameters to gain insight into the likely
-preference relations and the salience of local readings.
-
-\paragraph{The model.} We outline a simple probabilistic model that
-quantifies the positional bias and the competing strength of available
-readings. Take the AS-conditions as an example. There are three
-potential readings. The relative strength between these is given by a
-probability vector $\myvec{p}^\text{as-n} =
+nature of the task into account. The following paragraphs therefore
+spell out a generative Bayesian model which computes the
+likelihood of answer patterns for different latent relative saliencies
+of candidate readings and biases to answer early or late in a
+sequence. We use the data to estimate the posterior likelihood of
+these latent parameters to gain insight into the likely ordering
+relations over the strength of latent salience of candidate readings.
+
+\paragraph{The model.} We present a model that aims to capture the
+competition between candidate readings, all of which have a given
+latent level of relative salience, in the incremental verification
+task, where some readings can be judged before others. Take the
+AS-conditions with its three candidate readings. The relative strength
+between these is given by a probability vector $\myvec{p}^\text{as-n}
+=
 \tuple{p^\text{as-n}_{\text{lit}},p^\text{as-n}_{\text{loc}},p^\text{as-n}_{\text{glb}}}$. We
@@
 prediction of observed frequencies of answer patterns. We look at four
-such three-placed vectors, one for each target sentence-intonation
-pair.
-
-For the preference-related control conditions we look at three vectors
-$p^k = \tuple{p^{\text{k}}_{\text{\lc}}, p^{\text{k}}_{\text{\ec}}}$,
-where $k \in \set{\text{ntr}, \text{\lc-cue}, \text{\ec-cue}}$. These
+such three-placed vectors for the critical conditions, one for each
+target sentence-intonation pair. For the preference-related control
+conditions, we look at three vectors $p^k =
+\tuple{p^{\text{k}}_{\text{\lc}}, p^{\text{k}}_{\text{\ec}}}$, where
+$k \in \set{\text{ntr}, \text{\lc-cue}, \text{\ec-cue}}$. These
 vectors give the relative salience of \lc- and \ec-readings for
@@
 
-To add potential effects of sequentiality, we assume that there is a
-bias factor $q \in [0;1]$. This bias is a global parameter held
-constant over all conditions, because we think of it as a general
-tendency to answer early or late in the incremental verification
-task. The bias factor captures whether there is a tendency to access
-readings that appear earlier ($q > .5$) or later ($q <.5$) in the
-sequence. In the \as-sequences, the literal reading can be judged
-first, then the local and then the global reading. So we will assume
-that $p_{\text{lit}}$ is multiplied by $q$, that $p_{\text{loc}}$ is
-multiplied by $(1-q)q$ and that $p_{\text{glb}}$ is multiplied by
-$(1-q)^2$, when determining the eventual weights of readings.
-
-Finally, we also allow for mistakes. To keep things as simple as
-possible (no consideration for spill-overs, late decisions,
-preferences to unravel completely before judging etc.), we assume that
-there is a fixed error rate $e^k \in [0;1]$ for each relevant
-condition $k$. We allow for different error rates for different
-conditions, because we want to allow for the possibility that some
-sentence types (e.g., non-monotonic quantifiers) or some kind of
-intonation (e.g., the \ec-cues) might be harder to process. A decision
-can be wrong but incidentally coincide with an answer that is
+To add potential effects of sequentiality, consider bias factor $q
+\in [0;1]$. This bias is a global parameter held constant over all
+conditions, because we think of it as a general tendency to answer
+early or late in the incremental verification task. The bias factor
+captures whether there is a tendency to access readings that appear
+earlier ($q > .5$) or later ($q <.5$) in the sequence. In the
+\as-sequences, the literal reading can be judged first, then the local
+and then the global reading. So we will assume that $p_{\text{lit}}$
+is multiplied by $q$, that $p_{\text{loc}}$ is multiplied by $(1-q)q$
+and that $p_{\text{glb}}$ is multiplied by $(1-q)^2$, when determining
+the eventual weights of readings.
+
+Finally, we also allow for mistakes. To keep things simple (no
+differential consideration for spill-overs, button mix-ups etc.), we
+assume that there is a fixed error rate $e^k \in [0;1]$ for each
+relevant condition $k$. We allow for different error rates for
+different conditions, because we want to allow for the possibility
+that some sentence types (e.g., non-monotonic quantifiers) or some
+kind of intonation (e.g., \ec-cues) might be harder to process. A
+decision can be wrong but incidentally coincide with an answer that is
 indicative of a relevant reading. Error rates multiply in proportion
@@
   \centering
-  \begin{tikzpicture}[node distance = 2.5cm, 
+  \begin{tikzpicture}[node distance = 2cm, 
     double distance = 2pt,
@@
     the higher a node, the more latent it is. Square nodes represent
-    discrete-valued variables, circular squares represent
-    continuous-valued variables. Gray squares show the observable
-    variables. Double-lined nodes show deterministic dependency on
-    values of input nodes. The variables in the box are repeated for
-    each of the $k$ relevant conditions.}
+    discrete-valued variables, circular nodes represent
+    continuous-valued variables. Gray nodes show the observable
+    variables. Values at double-lined nodes are derived
+    deterministically. The variables in the box are repeated for each
+    of the $k$ relevant cases.}
   \label{fig:model_graph}
@@
 
-\paragraph{Model fitting.} We use JAGS
+\paragraph{Model fitting.} We used JAGS
 \citep{Plummer2003:JAGS:-A-Program} to estimate the posteriors over
 paramater values given our data. Results reported here are based on
-two chains of 10.000 samples from the joint posterior distribution
-MCMC sampling, obtained after an initial burn-in of 10.000 steps. The
+two chains of 10.000 MCMC samples from the joint posterior
+distribution, obtained after an initial burn-in of 10.000 steps. The
 latter guaranteed convergence.
 
-, we obtain estimates
-for the posterior of the latent parameters given the data. To check
-whether the model yields sensible results we first look at the
-preference-related control conditions.
+To check whether the model yields sensible results we first look at
+the preference-related control conditions.
 %
@@
   \includegraphics[width=0.8\textwidth]{pics/post_salience_TF.pdf}
-  \caption{Estimated posteriors for the relative salience of \lc- and
-    \ec-readings for different intonational cues. The lines under the
-    curves mark the estimated 95\% HDIs (see Footnote~\ref{fn:HDI}).}
+  \caption{Estimated posteriors for the salience of \lc- and
+    \ec-readings for different intonational cues. Lines under curves
+    mark are 95\% HDIs (see Footnote~\ref{fn:HDI}).}
   \label{fig:Posterior_TF}
@@
 %
-Estimates for the posteriors over relative salience levels for
-target-related controls are plotted in
+Estimates for the (marginalized) posteriors over relative salience
+levels for target-related controls are plotted in
 Figure~\ref{fig:Posterior_TF}. The results are exactly as we would
 expect them to be. Given our data, we should believe that the
-\lc-reading is most prominent. But the level of prominence varies with
+\lc-reading is most prominent. The level of prominence varies with
 accentuation. Under prosody that we hypothesized would favor the
-\lc-reading, the contrast is most pronounced. Contrarily, accentuation
-that we hypothesized favors the \ec-reading we are no longer justified
-in believing that the late-closure reading is certainly preferred
-(witness the clearly overlapping 95\% HDIs).\footnote{\label{fn:HDI} A
-  95\% Highest Density Interval (HDI) is a convex region of values
-  over which 95\% of the distribution's probability density is
-  divided, such that no value outside of that region has higher
-  probability density than any point within
+\lc-reading, the contrast is most pronounced. Under accentuation that
+we hypothesized favors the \ec-reading we are no longer justified in
+believing with certainty that the \lc-reading is preferred (by
+comparison of 95\% HDIs, see below).\footnote{\label{fn:HDI} A 95\%
+  Highest Density Interval (HDI) is a convex region of values over
+  which 95\% of the distribution's probability density is divided,
+  such that no value outside of that region has higher probability
+  density than any point within
   \citep{Kruschke2011:Doing-Bayesian-}. Intuitively speaking, the 95\%
@@
   confidence; what falls outside this region is what can be excluded
-  with relative safety.}
+  safely.}
 
@@
 
-Estimates of posteriors over salience of readings in the target
+Estimates of posteriors over salience of readings in the critical
 conditions are given in Figure~\ref{fig:Posterior_T}. In the
@@
 Posteriors over error rates are conceptually less interesting, and we
-will skip them here. Posteriors over the sequential bias parameter are
-shown in Figure~\ref{fig:post_q}, and show that, given the model and
-our data, we have reason for believing in a bias for late responses.
+will skip them here. The posterior over the sequential bias parameter
+is shown in Figure~\ref{fig:post_q}. Since the 95\% is clearly
+entirely below .5, we have reason for believing, given the model and
+our data, in a bias for late responses.
 
@@
 The first question can be answered by looking at the HDIs of the
-posteriors of the candidate readings. The HDIs give the region of the
-95\% least unbelievable parameter values, given the data and the
-model. We would like to check the hypothesis that a given reading is
-unavailable, i.e., its activation value in the probabilistic model is
-equal to 0, or close to zero for practical purposes (Region of
-Practical Equivalence, ROPE). We reject the ``null-hypothesis'' that
-the true value is 0 if its ROPE lies entirely outside the 95\% HDI; we
-accept the ``null-hypothesis'' if the ROPE lies entirely within the
-95\% HDI \citep[][Ch.~12]{Kruschke2011:Doing-Bayesian-}. The following
-table lists approximations of the 95\% HDIs for each condition and
-reading:
+posteriors of the candidate readings. We would like to check the
+hypothesis that a given reading is unavailable, i.e., its activation
+value in the probabilistic model is equal to 0, or close to zero for
+practical purposes (Region of Practical Equivalence, ROPE). We reject
+the ``null-hypothesis'' that the true value is 0 if its ROPE lies
+entirely outside the 95\% HDI; we accept the ``null-hypothesis'' if
+the ROPE lies entirely within the 95\% HDI
+\citep[][Ch.~12]{Kruschke2011:Doing-Bayesian-}. The following table
+lists approximations of the 95\% HDIs for each condition and reading:
 
@@
 
-The question after the preference relations between readings can be
-answered in a similar way. Here, we look at the posterior beliefs
-about the differences of activation strengths and ask whether these
-posterior beliefs allow us to safely conclude that differences are
-bigger than zero or not. It is obvious enough that literal readings
-are always the most preferred, and that local readings are preferred
-over global readings for \es-sentences. Figure~\ref{fig:PostDiffTAS}
-shows the posteriors over differences between local and global
-readings for \as-sentences. Since the 95\% HDIs include 0, the data
-provides no ground for confidence that, given the model, local
-readings of \as-sentences are preferred over global ones, despite the
-obvious tendency. In sum, with the exception of remaining uncertainty
-about local readings of \as-sentences, the model and the data suggest
-that global readings are absent entirely, while literal readings are
-preferred over local readings.
+The preference relations between readings can be checked in a similar
+way. We look at the posterior beliefs about the \emph{differences} of
+activation strengths and ask whether these posterior beliefs allow us
+to safely conclude that differences are bigger than zero or not. It is
+obvious enough that literal readings are always the most preferred,
+and that local readings are preferred over global readings for
+\es-sentences. Figure~\ref{fig:PostDiffTAS} shows the posteriors over
+differences for the only non-trivial cases, namely those between local
+and global readings for \as-sentences. Since the 95\% HDIs include 0,
+the data provides no ground for confidence that, given the model,
+local readings of \as-sentences are preferred over global ones,
+despite the obvious tendency. In sum, with the exception of remaining
+uncertainty about local readings of \as-sentences, the model and the
+data suggest that global readings are absent entirely, while literal
+readings are preferred over local readings.
 

### 2014-05-29 text/paper/paper4.tex
Conclusions sec com

@@
 
-\paragraph{Summary \& Interpretation.} High scores of success clearly
-indicate that participants understood the incremental verification
-task and were in general able to give judgements at the earliest
-possible point in a picture sequence.  Moreover, results obtained for
-the preference-related controls show that our design is able to detect
-multiple readings and preferences among these. Crucially, the amount
-of response types for \lc- and \ec-readings reflected the known
-preference for the former, \emph{irrespective} of the order in which
-each reading could first be judged in a given sequence.  Finally, the
-incremental verification task was generally sensitive to
-prosody. However, prosodic effects were restricted to the
-preference-related controls. As expected, in these conditions, the
-dispreferred \ec-reading was chosen significantly more often when
-supported by prosodic phrasing. Interestingly, contrastively accenting
-scalar \emph{some} had no effect on the observed decisions in the
-target conditions. Crucially, local readings occurred in both \as- and
-\es-sentences, independently of prosody. Finally, closer examination
-of the participants' decisions revealed two groups: participants in
-the first group consistently gave answers corresponding to local
-readings, whereas participants in the second group consistently showed
-a literal interpretation.
-
-Given the overall pattern of results, the most straightforward 
-explanation of the observed data is the hypothesis that the actual 
-preferences among readings for both \as- and \es-sentences alike are:
+\paragraph{Summary \& Interpretation.} High scores of success in
+control conditions show that participants understood the incremental
+verification task and were able to give judgements at the right point
+in a picture sequence. Results for the preference-related controls
+show that our design is able to detect multiple readings and
+preferences among these. Crucially, the amount of response types for
+\lc- and \ec-readings reflected the known preference for the former,
+\emph{irrespective} of the order in which each reading could first be
+judged in a given sequence. Finally, the incremental verification task
+was generally sensitive to prosody. However, significant prosodic
+effects were restricted to preference-related controls. Contrastively
+accenting scalar \emph{some} generally led to more local readings, but
+that effect was not significant. Local readings occurred in
+\es-sentences, independently of prosody, but required intonational
+marking in \as-sentences. Our analyses support the impression that
+inspection of the raw data gives, namely that the general qualitative
+pattern of reading preferences is the same for \as- and \es
+conditions, namely that literal readings are preferred over local
+readings which are preferred over global readings. More concretely,
+our analyses suggest the following preference/availability patterns
+(bracketed readings are unattested, in the sense that they are either
+unavailable or heavily dispreferred):
 
 \begin{exe}
-  \ex \label{bsp:observed-preferences} \lit \ > \ \loc \ \ ( > \glb)
+  \ex \label{bsp:observed-preferences}
+    \begin{xlist}
+      \ex \as-ntr: \ \ \ \lit \ >  (\loc \ \  $\sim$ \glb)
+      \ex \as-acc: \ \ \ \lit \ > \ \loc \ \ ( $\sim$ \glb)
+      \ex \es-ntr: \ \ \ \lit \ > \ \loc \ \ ( > \glb)
+      \ex \es-acc: \ \ \ \lit \ > \ \loc \ \ ( > \glb)
+    \end{xlist}
+
 \end{exe}
 
-\noindent where it is unclear whether the global readings are entirely
-unavailable or simply severely dispreferred. Crucially, our data
-attests local readings independently of prosody, albeit that local
-readings are not preferred to literal readings and given, as it seems,
-only by a small, but substantial number of consistent localists.
-
-These findings are hard to for traditionalism and grammaticalism
-alike, as no version of either would predict the pattern in
-(\ref{bsp:observed-preferences}).  Traditionalism, if left on its own,
-fails to predict local readings, while grammaticalism, when it relies
-on the strongest meaning hypothesis, fails to predict the right
-preference order and, more importantly, cannot explain the absence of
-answers indicative of a global reading. Let's look more closely at
-each position in turn.
-
-For traditionalism, the absence of global readings \textit{per se} can
-be explained, for instance, by proposing that the extra assumptions
-needed to derive global readings are not standardly available (as in
-the weak variety of traditionalism).  Alternatively, traditionalists
-could argue that the task's rather high processing demands lead to a
+If we compare (\ref{bsp:observed-preferences}) with
+Table~\ref{tab:predictions}, we quickly see that these findings are
+not predicted by neither traditionalism nor
+grammaticalism. Traditionalism, if left on its own, fails to predict
+local readings in the \es-conditions. A Grammaticalism that relies on
+the strongest meaning hypothesis fails to predict the right preference
+order and cannot explain the absence of answers indicative of global
+readings. Let's look more closely at what is and is not surprising
+under each theoretical position and then reflect on how each position
+might be adapted do deal with the observations that it does not
+predict.
+
+Traditionalism easily explains the absence of global readings. Weak
+traditionalism, introduced in Section~\ref{sec:traditionalism}, for
+instance, would hold that the extra assumptions needed to derive
+global readings are not available or only allow for epistemic weak
+implicatures that would be show as responses indicative of literal
+readings in our task. In support of this view, traditionalists could
+argue that the task's rather high processing demands lead to a
 suppression of global readings, in line with the findings of
@@
 load negatively affects the number of scalar implicature responses in
-sentence verification tasks. However, it then remains unclear why
-memory effects should be restricted to global readings.  As a result,
-approaches like the unrestricted variety of traditionalism thereby
-loose the possibility of accounting for local readings of
-\as-sentences.\fn{Remember that unrestricted traditionalism, as we
-  called it, can account for local readings of \as-sentences by
-  assuming that a sentence of the form \emph{Some of the $X$ are
-    related to some of the $Y$} is a feasible alternative.} This is
-because unrestricted traditionalism explains local and global readings
-of \as-sentences in essentially the same manner. On top of that,
-traditionalism cannot explain local readings for
-\es-sentences. Resorting to the intonational markedness hypothesis
-does not help improve predictions of traditionalism. The latter would
-predict an increase in local readings in the accented conditions, and
-presumably an absence of local readings in the unaccented
-conditions. Neither was observed. Local readings were observed in the
-accented as well as in the unaccented condition, thus countering
-previous traditionalist suggestions that local readings are to be
-attributed to specific pragmatic mechanisms. Other mechanisms might be
-hypothesized as the source of local readings (and we will look at some
-obvious candidates below), but that does not as such save
-traditionalism. Traditionalism, even if supplemented with the
-intonational markedness hypothesis, cannot explain
-(\ref{bsp:observed-preferences}), but needs an additional explanation
-of local readings for \emph{both} \as- \emph{and} \es-sentences.
-
-Grammaticalism, on the other hand, fails to predict the preference
-relation in (\ref{bsp:observed-preferences}), in particular the
-absence of answers indicative of global readings. This is because
-(\ref{bsp:observed-preferences}) strictly contradicts the strongest
-meaning hypothesis in either of the two varieties suggested by
-\citet{ChierchiaFox2008:The-Grammatical}. This shows most clearly in
-the fact that both versions of the strongest meaning hypothesis
-predict that local readings of \as-sentences are preferred over
-literal ones. The problem, therefore, seems to be the selection of
-readings by the strongest meaning hypothesis. In fact, if
-(\ref{bsp:observed-preferences}) is the actual preference over
-readings, then the strongest meaning hypothesis is also conceptually
-on the wrong track, because no account that merely looks at the
-logical strengths of readings can plausibly predict the preference
-pattern in (\ref{bsp:observed-preferences}) for both \as- and
-\es-sentences at the same time.
-
-Summing up so far, the existing versions of traditionalism, even if
-aided by the intonational markedness hypothesis, and grammaticalism
-cannot explain the present results. What would it take to amend either
-framework to make it fit the data we observed? Traditionalism would
-need to explain the possibility of local readings of intonationally
-unmarked sentences. To do so within a traditionalist framework seems
-impossible, so the most common approach is to explain putative
-evidence for local readings away as the result of some other
+sentence verification tasks. The small number of local readings in
+\as-sentences with contrastive stress is easily explained by adopting
+the Intonational Markedness Hypothesis. What traditionalism does not
+predict is the high number of answers indicative of local readings in
+the \es-conditions. Resorting to the Intonational Markedness
+Hypothesis does not help, because local readings were observed for
+accented as well as in unaccented \es-sentences. It would also remain
+unclear why intonational cues should have such differential effects on
+\as- and \es-sentences.
+
+Grammaticalism, on the other hand, fails to predict the pattern in
+(\ref{bsp:observed-preferences}) entirely if it equates preference for
+readings with logical strength. Failure to predict the patter in
+(\ref{bsp:observed-preferences}) is still relatively unproblematic for
+\es-sentences, where strong grammaticalism (see
+Section~\ref{sec:grammaticalism}) would simply not make any
+predictions. But for \as-sentences grammaticalism would actually
+predict that literal readings should be the least preferred. Again,
+we need to bare the caveat of Section~\ref{sec:grammaticalism} in mind
+that we are only evaluating grammaticalism with respect to a
+particular selection criterion here. The verdict, however, seems to be
+totally clear. If (\ref{bsp:observed-preferences}) is the actual
+preference order over readings, then meaning selection in terms of
+logical strength is generally on the wrong track, because no account
+that merely looks at the logical strengths of readings can plausibly
+predict the preference pattern in (\ref{bsp:observed-preferences}) for
+both \as- and \es-sentences at the same time.
+
+If the pattern in (\ref{bsp:observed-preferences}) cannot be explained
+in terms of the austere and stylized versions of traditionalism and
+grammaticalism that we have set up so far, what plausible additional
+assumptions would enable either framework accommodate the data? Again,
+let us look at each position in turn.
+
+Traditionalism would need to explain the possibility of local readings
+of intonationally unmarked sentences. To do so within a traditionalist
+framework seems impossible, so the most common approach is to explain
+putative evidence for local readings away as the result of some other
 phenomenon, such as typicality or contrast

### 2014-05-29 text/paper/paper4.tex
Conclusions sec com

@@
 
-If the pattern in (\ref{bsp:observed-preferences}) cannot be explained
-in terms of the austere and stylized versions of traditionalism and
-grammaticalism that we have set up so far, what plausible additional
-assumptions would enable either framework accommodate the data? Again,
-let us look at each position in turn.
-
-Traditionalism would need to explain the possibility of local readings
-of intonationally unmarked sentences. To do so within a traditionalist
-framework seems impossible, so the most common approach is to explain
-putative evidence for local readings away as the result of some other
-phenomenon, such as typicality or contrast
-\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}. We
-argue below that neither explanation plausibly applies in the
-incremental verification task. On the other hand, what grammaticalism
-would have to change is the selection criterion over preferred
-readings, i.e., to reconsider the strongest meaning
-hypothesis. Turning away from comparisons of logical strength, a
-\emph{prima facie} plausible selection criterion that produces
-(\ref{bsp:observed-preferences}) is ready at hand: if we assume that
-each insertion of the $\exh(\cdot)$ operator is \emph{costly}
+In sum, if we are justified in asserting that the pattern in
+(\ref{bsp:observed-preferences}) reflects the true default preferences
+over candidate readings (see below for a critical discussion), then
+this cannot be explained in terms of the austere and stylized versions
+of traditionalism and grammaticalism that we have set up so far. We
+should then ask what plausible additional assumptions would enable
+either framework accommodate the data? Again, let us look at each
+position in turn.
+
+Consider grammaticalism first. Our data quite clearly contradicts the
+notion that preferences follow logical strength. It seems clear that
+grammaticalism needs to be supplemented by a conceptually different
+selection criterion. Selecting readings in terms of how well they
+answer the contextually given question under discussion, as suggested
+by \citet{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An},
+is an option. But it is quite unclear what the question under
+discussion should be that guided judgements in our task. As long as a
+theory of accommodating implicit questions under discussion is
+missing, this selection criterion does not make any clear, testable
+predictions. However, looking at the qualitative pattern in
+(\ref{bsp:observed-preferences}), a \emph{prima facie} plausible
+disambiguation criterion is ready at hand: if we assume that each
+insertion of the $\exh(\cdot)$ operator is \emph{costly}
 anti-proportional to the depth of its embedding under other logical
@@
 sound and in line with further empirical data would then be an
-interesting matter of further investigation.
-
-It is worth noting that an alternative theory of scalar implicature
-explains the observed preference ordering
-(\ref{bsp:observed-preferences}) in a completely straightforward
-manner.  \emph{Conventionalism} (also sometimes called
-\emph{lexicalism}) proposes that if the upper-bound inference from
-\emph{some} to \emph{some but not all} occurs frequently, it would be
-inefficient to execute over and over again the Gricean reasoning that
-traditionalists propose
-\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}. Conventionalism
-therefore assumes that scalar inferences have become routinized,
-hard-wired, so much so that there are two lexical entries for a scalar
-item like \emph{some}, one with logical meaning \emph{some and maybe
-  all} and one with the upper-bounded meaning \emph{some but not
-  all}. \citet{LevinsonPresumptiveMeanings2000} proposed that the
-latter is the preferred default meaning, a position which has
-therefore ofttimes be addressed as \mymark{defaultism}. Unfortunately,
-defaultism has strong empirical evidence against it, because several
-processing studies show that the computation of scalar inferences
-appears to be time- and effort-consuming, when they do arise, not when
-they do not
-\citep[see][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
-there is also competing evidence that scalar inferences are available
-in immediate, low-level processes, such as the resolution of
-referential expressions in a visual-world paradigm
-\citep{GrodnerKlein2010:Some-and-Possib}. For our purposes, it is
-interesting to note that the preference relation in
-(\ref{bsp:observed-preferences}) is predicted by the dual of
-defaultism, which has not been defended in the literature as far as we
-know, which posits a lexical ambiguity but predicts that the logical
-meanings are \emph{ceteris paribus} preferred over the upper-bounded
-meanings.
-
-Unfortunately, there are problems with conventionalism, no matter
-which lexical reading is assumed to be preferred, that seem to require
-that it be backed up by traditionalism
-\citep[e.g.][]{Sauerland2012:The-Computation}.\fn{\citet{Sauerland2012:The-Computation}
-  eventually dismisses even conventionalism backed up by
-  traditionalism in favor of grammaticalism based on cases of
-  so-called \emph{intermediate implicatures}, where what seems to be
-  necessary is the insertion of an exhaustivity operator in
-  intermediate scope position \citep[see][for
-  details]{Sauerland2012:The-Computation}. Appreciation of such
-  intermediate implicatures requires more argumentation, involving a
-  discussion of \emph{Hurford's constraint}
-  \citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2009:Hurfords-Constr,ChierchiaFox2008:The-Grammatical},
-so we skip this here.}
-For instance, conventionalism cannot account for \emph{indirect
-  implicatures}, such as the inference from
-(\ref{bsp:indirect-SI-Target}) to (\ref{bsp:indirect-SI-Inference})
-which cannot be explained by positing a lexical ambiguity for
-\emph{all}.
-
-\begin{exe}
-  \ex \label{bsp:indirect-SI}
-    \begin{xlist}
-      \ex \label{bsp:indirect-SI-Target} Hans did not solve all of the problems.
-      \ex \label{bsp:indirect-SI-Inference} Hans solved some of the problems.
-    \end{xlist}
-\end{exe}
-
-\noindent In the context of the present study, this would then be good
-news for traditionalism, because a combined
-traditionalism+conventionalism would predict the observed data
-well. The combined position would even be able to explain something
-that grammaticalism cannot make sense of as easily, namely the
-observation that there were rather consistent localists among the
-participants of our study. The combined tradionalism+conventionalism
-could explain this by the assumption that some (lazy?, smart?)
-speakers have made a conventionalized upper-bound meaning entry for
-scalar \emph{some} while others keep computing things on the fly. It
-is not clear how grammaticalism can account for the intra-subjective
-consistency. Still, this is not an argument \emph{for} traditionalism,
-because the point remains that traditionalism as such fails to predict
-the observed data.
-
-In sum, if the interpretation of our data as suggested here is
-correct, then both traditionalism and grammaticalism are in need of
-revision. Traditionalism must explain the availability of local
-readings, grammaticalism must revise its selection criterion among
-readings.
+interesting matter of further investigation. What this economy
+principle does not explain yet is the quantitative differences in the
+preference orders between \as- and \es-sentences. Still, if combined
+with further information about the global properties of the sentences
+in question, this might be an interesting alternative disambiguation
+criterion for an empirically testable grammaticalism.
+
+Traditionalism, on the other hand, has to explain the possibility of
+local readings of intonationally unmarked \es-sentences, and, perhaps,
+also the large number of local readings in accented \es-sentence
+compared to that in accented \as-sentences. To do so within a
+traditionalist framework seems impossible, so the most common approach
+is to explain putative evidence for local readings away as the result
+of some other phenomenon, such as typicality or contrast
+\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi,Tielvan-Tiel2014:Quantity-Matter}.
+Since this ties into a critical reflection on our design, we will
+enlarge on the possibility of typicality- and contrast-based effects
+in our setting. Eventually, we argue that contrast-effects alone are
+unlikely to explain the observed high number of local answers in
+\es-sentences, but that the additional assumption of 
+``shallow processing'' of the non-monotonic quantifiers might save
+traditionalism.
+
+As discussed in Section~\ref{sec:previous-studies},
+\citet{Tielvan-Tiel2012:Embedded-Scalar} and
+\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue that the
+distribution of responses to \as-sentences found by
+\citet{CliftonDube2010:Embedded-Implic}, as well as
+\citet{ChemlaSpector2010:Experimental-Ev} could be explained by
+differences in how \emph{typical} the presented pictures were for an
+\as-sentence. Notice that this does not help in the present situation
+where the task is to explain away the local readings of \es-sentences,
+for which no alternative explanation in terms of typicality has been
+offered. Moreover, to apply typicality-explanations to the incremental
+verification task, one would have to reason about the typicality of
+parts of pictures or to figure in subjects' expectations of pictorial
+typicality given their uncertainty about parts of the picture that
+they have not yet seen. On intuitive grounds, we take either extension
+to be far-fetched and implausible. But even if this line of
+explanation can be plausibly extended to incrementally revealed
+picture verification, it would still be unclear why typicality-effects
+should show so strongly in categorical truth-value judgements, and why
+there is such a stark contrast between \as- and \es-sentences. For
+these reasons, we put typicality-based explanations of local readings
+of \es-sentences aside.
+
+\bigskip
 

### 2014-05-29 text/paper/paper4.tex
Conclusions sec com

@@
 \es-sentences, but that the additional assumption of 
-``shallow processing'' of the non-monotonic quantifiers might save
+``shallow interpretation'' of the non-monotonic quantifiers might save
 traditionalism.
@@
 
-\bigskip
-
-\paragraph{Some Potential Objections.} There are a number of
-conceivable objections to our interpretation of the presented
-results. We will consider the most pressing ones in the following.
+A more promising alternative explanation for local readings of
+\es-sentences is pursued by
+\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} \citep[see
+also][]{Tielvan-Tiel2014:Quantity-Matter} in response to the data
+reported by \citet{ChemlaSpector2010:Experimental-Ev}. The main idea
+is that visual contrast between an item that is connected to all, and
+one that is connected to only some but not all of the relevant
+elements may trigger exceptional local enrichment of \emph{some}. In
+support of this idea,
+\citeauthor{GeurtsTielvan-Tiel2013:Scalar-expressi} show that the
+strength of agreement to an \es-sentence on a 7-point Likert-scale
+depends on how strong the relevant visual contrast is. When an item
+with only some connections is contrasted presented alongside two
+universally connected elements, the mean rate of agreement with a
+suitable \es-sentence is significantly higher than when only one
+universally connected element is present. So, maybe our \es-sequences
+similarly provoked local readings because of an overemphasized visual
+contrast between \emph{some but not all} and \emph{all}.
+
+The third step of our \es-sequences in Figure~\ref{fig:exseqES} is a
+relevant case of direct contrast between a \emph{some-but-not-all-}
+and an \emph{all}-situation, but it is a weak contrast, in the sense
+of \citet{GeurtsTielvan-Tiel2013:Embedded-Scalar}, because there is
+only one universally connected element. Moreover, our study elicited
+categorical truth-value judgements. Unlike in
+\citeauthor{ChemlaSpector2010:Experimental-Ev}'s
+(\citeyear{ChemlaSpector2010:Experimental-Ev}) and
+\citeauthor{GeurtsTielvan-Tiel2013:Scalar-expressi}'s
+(\citeyear{GeurtsTielvan-Tiel2013:Scalar-expressi}) experiments, we
+did not record degrees of agreement with a statement. For a purely
+contrast-based explanation to work, it would have to be made plausible
+why the (weak) visual contrast in a picture like in
+Figure~\ref{fig:exseqES3} alone is enough to overrule a truth-value
+judgment so as to contradict the semantic meaning (even when there is
+no intonational markedness to support such a reinterpretation).
+
+What might make this contrast-based explanation more plausible is the
+observation that subjects found \es-sentences difficult. As discussed
+in Section~\ref{sec:results}, there were a non-negligible number of
+\emph{true} answer at step 2 in the \es-sequence. This can be
+explained on the assumption that participants read the non-monotonic
+quantifier \emph{exactly one} as a monotonic quantifier \emph{at least
+  one}. Similar ``shallow interpretation'' of \emph{exactly one} would
+explain the high number of local answers for \es-sentences (and for
+\es-sentence alone). If participants processed the truth-value for an
+\es-sentence by looking for a \emph{unique} element that could be
+singled out somehow, they would need to unravel the \es-sequence up to
+the last picture. At this step contrast effects are stronger and would
+not need to compete with the proper semantic interpretation of
+\emph{exactly one}. Together, pictorial contrast effects in symbiosis
+with a ``shallow interpretation'' non-monotonic quantifiers could be
+an alternative explanation of (\ref{bsp:observed-preferences}) for
+traditionalism.
+
+\paragraph{Critique.} There are a number of conceivable objections to
+our design and our interpretation of the presented results. We will
+consider the most pressing ones in the following.
 
@@
 responses.
-
-A third objection could be that pictures in our tasks may unduly
-overemphasize the contrast between cases where items are connected
-with all or merely some but not all of their surrounding shapes. This
-is essentially the line of argument pursued by
-\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} against the data
-reported by \citet{ChemlaSpector2010:Experimental-Ev} in support of
-local readings of
-\es-sentences. \citeauthor{GeurtsTielvan-Tiel2013:Scalar-expressi}
-show that the strength of agreement to an \es-sentence on a 7-point
-Likert-scale depends on a visual contrast between, on the one hand,
-one element connected to some but not all of its surrounding shapes,
-and, on the other hand, a variable number of elements connected to all
-of their surrounding shapes. When two universally connected elements
-are present, the mean rate of agreement with a suitable \es-sentence
-is higher than when only one is present. So, maybe our displays
-similarly provoked local readings because of an overemphasized visual
-contrast.
-
-This cannot be a plausible explanation for the number of local
-responses we found in our study. Although it is true that the critical
-position for judging the local reading is a picture with a high visual
-contrast in the above sense (see Figure~\ref{fig:exseqES}), a purely
-contrast-based explanation of the local responses in our data is not
-feasible for two reasons. The first is that visual contrast does not
-explain how subjects ever even got past the second critical position
-where the sentence can be judged false under its literal reading. At
-this position there is a visual contrast of the alleged kind but it is
-as small as possible. So something must have motivated subjects
-already at this position to continue unraveling, given that they were
-generally able of exiting at the earliest possible location, as
-evidenced by ceiling success rates in our positional controls. A second
-argument that casts doubt on a contrast-based explanation is that our
-study elicited categorical truth-value judgements. Unlike in
-\citeauthor{ChemlaSpector2010:Experimental-Ev}'s
-(\citeyear{ChemlaSpector2010:Experimental-Ev}) and
-\citeauthor{GeurtsTielvan-Tiel2013:Scalar-expressi}'s
-(\citeyear{GeurtsTielvan-Tiel2013:Scalar-expressi}) experiments, we
-did not record degrees of agreement with a statement. But it is hardly
-plausible that the visual contrast in a picture like in
-Figure~\ref{fig:subfig1} alone is enough to overrule a truth-value
-judgment so as to contradict the semantic meaning (even when there is
-no intonational markedness to support such a
-reinterpretation). Ultimately, however, even if the local answers in
-our study are contrast effects, the verdict remains that
-traditionalism can not account for that piece of the data unless aided
-by yet another auxiliary and grammaticalism cannot explain why it is
-relatively dispreferred.
-
-% A fourth major conceivable objection maintains that we cannot rule out
-% that the way we realized the intonational markedness in the accented
-% conditions was not the right kind of intonational
-% markedness. Therefore the intonational markedness hypothesis that
-% links an increase in local readings to intonation might not be
-% falsified by our results. Although true, this still does not help
-% vindicate traditionalism, for even without marked intonation local
-% readings were available.
-
-Also, we should address the obvious worry that maybe our results
-could have been the product of typicality after all. Remember that
-\citet{Tielvan-Tiel2012:Embedded-Scalar} and
-\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue that the
-distribution of responses to \as-sentences found by
-\citet{CliftonDube2010:Embedded-Implic}, as well as
-\citet{ChemlaSpector2010:Experimental-Ev} could be explained by
-differences in how typical representations for an \as-sentence the
-presented pictures were. To apply typicality-explanations to the
-incremental verification task, one would have to reason about the
-typicality of parts of pictures or to figure in subjects' expectations
-of pictorial typicality given their uncertainty about parts of the
-picture that they have not yet seen. On intuitive grounds, we take
-either extension to be far-fetched and implausible. But even if this
-line of explanation can be plausibly extended to incrementally
-revealed picture verification, this does not as such save the day for
-traditionalism or grammaticalism, because, as argued above, typicality
-effects are arguably insufficient to explain the change in categorical
-truth-value judgement that we found in our experiment.
-
-% Still, graphical properties might affect judgments in the worst
-% case. In the first step of the \as-condition local and global readings
-% cannot be judged, yet. Therefore, graphical properties should not
-% affect judgments if participants have one of these readings in
-% mind. If participants have a literal reading in mind, the worst case
-% scenario is that they refrain from judging the sentence as true at
-% this point due to some, say, atypical, graphical property of the
-% picture. The situation is similar at the second step. The local
-% reading is still not decidable. Therefore, graphical properties should
-% not play a role if participants have a local reading in mind. A
-% positive judgment might, however, be a delayed judgment of a literal
-% reading. Again, the worst case scenario for our purpose is that
-% participants refrain from answering because of graphical
-% properties. At the last step the local reading requires a negative
-% judgment. Now, we could obtain delayed negative responses from literal
-% or global readings because the graph as a whole is, e.g., logically
-% true but atypical with respect to these readings. These kinds of
-% judgments would be indistinguishable from local responses. Note,
-% however, that we have no reason to believe that typicality has large
-% effects, because, given the results from van Tiel, the picture as a
-% whole is expected to be one of the more typical situations for
-% \as-sentences. Still, we cannot exclude the possibility that graphical
-% properties of the pictures might have the described effect. In the
-% \es-conditions this type of effect is, however, entirely impossible
-% since the literal and global reading is plainly false given the
-% initial parts as well as the whole graph. Summing up, in the worst
-% case, which we consider implausible, graphical effects might lead to
-% an enhanced number of local responses in the \as- as compared to the
-% \es-condition. We have to keep this possibility in mind. We want to
-% stress, however, that the design presented here improves on previous
-% studies with respect to possible graphical effects.
 

### 2014-05-29 text/paper/paper4.tex
Conclusions sec com

@@
 
-\title{Embedded Scalars: {A}n Experimental Revisit} \author{Fabian
-  Schlotterbeck, Michael Franke and Petra Augurzky} \date{}
+\title{Embedded Scalars, Preferred Readings \& Intonation: {A}n
+  Experimental Revisit} 
+\author{% Fabian
+  % Schlotterbeck, Michael Franke and Petra Augurzky
+} 
+\date{}
 
@@
 The data obtained by this method is problematic for both
-traditionalism and grammaticalism. Contrary to traditionalism and the
-intonational markedness hypothesis, we found evidence for local
-readings for both kinds of critical sentences, irrespective of
-intonational stress. \todo{enlarge: how big was this effect? can
-  traditionalists explain this away?} But also grammaticalism is
-incongruent with the observed pattern in our data. Backed up by the
-Strongest Meaning Hypothesis
+traditionalism and grammaticalism. Contrary to the predictions of
+traditionalism, we observed many answers indicative of local readings
+of \es-sentences, irrespective of intonational markedness. But also
+grammaticalism is incongruent with the observed pattern in our
+data. Backed up by the Strongest Meaning Hypothesis
 \citep{DalrympleKanazawa1998:Reciprocal-Expr}, grammaticalism predicts
@@
 obligatory presence of $\exh$ with variability in the set of relevant
-alternatives. \todo{verify that this is the proposal} Another proposal
-is that readings are preferred in relation to how well they answer the
-contextually given question under discussion
+alternatives. Another proposal is that readings are preferred in
+relation to how well they answer the contextually given question under
+discussion
 \citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. Yet
@@
 
-A related objection would be that maybe it is not feasible to actually
-compare results from the preference-related controls to results from
-our target conditions, because the source of different readings is
+A related objection is that it is not feasible to actually compare
+results from the preference-related controls to results from our
+target conditions, because the source of different readings is
 fundamentally different. In the former we have a syntactic ambiguity,
-in the latter a small number of competing putative pragmatic
-enrichments. The former is a case of perceived ambiguity (some of our
-subjects reported this), the latter arguably is not
+in the latter a set of putative pragmatic enrichments. The former is a
+case of perceived ambiguity (some of our subjects reported this), the
+latter arguably is not
 \citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
@@
 mean that the distribution of responses in target conditions is
-indicative of preference relations.
-
-Although we cannot rule out that the incremental verification task
-detects preferences among multiple readings only for some sources of
-variability in readings and not others, it is by no means clear why
-this should be so. The burden of argument is on the sceptic. But even
-if we assume that the incremental verification task is incapable of
-reliably indicating preferences among candidate pragmatic enrichments
-of the relevant kind, then it should at least be able to indicate
-availability of readings. So if we deny the observed response patterns
-the power to indicate preference, what should the information about
-availability of readings be that we may safely infer from it? It
-should be that local readings are available and that global readings
-are not. But that is not predicted by either traditionalism or
-grammaticalism. The former cannot explain the substantial number of
-local responses, the latter doesn't explain the absence of global
-responses.
-
-\paragraph{Future Directions.} The data obtained from our experiment
-also raises a number of issues for future research. Firstly, we found
-a tendency of subjects to give literal or local answers rather
-consistently. This seems to be related to what has been reported in a
-number of previous studies on unembedded \emph{some}, where a tendency
-was found as well in subjects to either consistently interpret
-\emph{some} `semantically' as \emph{some and possibly all} or to
-consistently interpret it `pragmatically' as \emph{some and not all}
-\citep[e.g.][]{NoveckPosada2003:Characterizing-,BottNoveck2004:Some-Utterances,DegenTanenhaus2012:Processing-Scal}. This
-inter-subjective consistency has not been paid any attention to in
-previous studies on embedded scalar items. It would be interesting to
-test whether there is any indication of a correlation between, on the
-one hand, subjects' tendencies to give literal vs.~local answers for
-embedded occurrences of \emph{some} and, on the other hand, subjects'
-tendencies to interpret unembedded \emph{some} semantically or
-pragmatically. If such a correlation exists, it would point towards
-the possibility that different subjects may even have different
-lexical representations of \emph{some} or possibly employ different
-processes of interpreting it. If so, this would severely mix up the
-theoretical landscape and should also be taken into account in any
-further study on the processing of scalar items.
-
-Secondly, given the scarce literature on the topic, more research into
-the role of intonational markedness on pragmatic interpretation is
-clearly needed. Claims about the correlation of certain
-interpretations with certain patterns of intonation are frequently
-made in the theoretical literature, but often only backed up by
-introspection and not made precise in their commitment to the exact
-kind of intonational pattern that is hypothesized to be relevant. The
-intonational markedness hypothesis, for instance, seems \emph{prima
-  facie} plausible, but we did not find any evidence for it in our
-experiment. This much is not yet any direct evidence against it
-either, because it is certainly possible that the contrastive accents
-we realized in our experiments, although the most plausible and in
-line with current theorizing about German contrast marking, was not
-the right kind of intonational markedness. This shows for one that
-claims about the putative effects of intonation and prosody must be
-more carefully phrased and filled with detail, but also points to
-further empirical research. The combination of production experiments
-the output of which is fed into a subsequent interpretation experiment
-comes to mind as a first natural continuation.
+indicative of preference relations. Although we cannot rule out that
+the incremental verification task detects preferences among multiple
+readings only for some sources of variability in readings and not
+others, it is by no means clear why this should be so. The burden of
+argument is on the sceptic. But even if we assume that the incremental
+verification task is incapable of reliably indicating preferences
+among candidate pragmatic enrichments of the relevant kind, then it
+should at least be able to indicate availability of readings. So if we
+deny the observed response patterns the power to indicate preference,
+what should the information about availability of readings be that we
+may safely infer from it? It should be that local readings are
+available in \es-sentences and that global readings are unattested in
+\as- and \es-sentences. But that alone is not predicted by either
+traditionalism or grammaticalism. The former cannot explain the
+substantial number of local responses in \es-sentences, the latter
+does not explain the absence of total global responses.
+
+Another line of criticism that challenges the validity of
+(\ref{bsp:observed-preferences}) targets the Bayesian
+salience-competition model that we used to derive it. We readily admit
+that our model is highly simplistic. Several aspects are especially
+noteworthy here. Firstly, we did not distinguish different types of
+errors, and did not take into account that when errors occurred
+earlier in the sequence, later decision points could no longer be
+reached. This way the model may actually have unduly de-emphasized the
+salience of readings that can be judged later in a sequence. Another,
+more complicated model of the likelihood of answer patterns, might
+therefore have given support to different conclusions. Unfortunately,
+it is not clear how exactly such a more complex generating model
+should be set-up. Eventually, a full processing model, design for data
+from incremental verification tasks would be needed. We cannot offer
+such a model here, but can only the offer the model that we did use as
+a first step in that direction. More importantly, though, the only
+part of our conclusions that might plausibly change in
+(\ref{bsp:observed-preferences}) for a different generating model is
+that the 3 \emph{false} answers in the \as-conditions with neutral
+intonation might support the conclusion that the local reading is
+marginally attested. But this hypothetical effect will certainly be no
+bigger than marginal, and so no genuinely different conclusions of
+theoretical relevance should be expected.
 
@@
 grammaticalism with respect to the availability of and preferences
-over three types of conceivable pragmatic readings of two types of
+over three types of conceivable pragmatic enrichments of two types of
 sentences, in which scalar \emph{some} occurred in the scope of either
@@
 asked to uncover the picture sequentially until they felt able to give
-a categorical truth-value judgements. Sentence material was presented
-auditorily and contrastive stress on embedded \emph{some} was
-manipulated so as to test the intonational markedness hypothesis,
-which is often used to supplement traditionalism. Both traditionalism
-and grammaticalism do not predict our data well.  Traditionalism fails
-to account for the non-negligible number of responses indicating local
-readings even for intonationally unmarked sentences. Grammaticalism
-fails to predict the absence of answers indicative of global readings
-and the relative abundance of answers indicative of literal readings.
+a categorical truth-value judgements. In order to control for
+potential confounds of ``silent prosody,'' sentence material was
+presented auditorily and contrastive stress on embedded \emph{some}
+was manipulated. This way we were able to also explicitly test the
+intonational markedness hypothesis, which is often used to supplement
+traditionalism. Additionally, we included preference-related control
+conditions in order to be able to deduce latent preferences for
+candidate readings from the answer patterns we gathered. To this end,
+we introduced a generative Bayesian model that gives probabilistic
+predictions about possibly observable answer patterns in our task,
+given concrete instances of relatives saliences of readings and other
+parameters. Using the observed data, in particular in connection with
+the preference-related control conditions, we inferred a posteriori
+likely values of the latent cognitive parameters.
+
+Backed up by our analyses, we concluded that both traditionalism and
+grammaticalism do not predict our data well. Traditionalism fails to
+account for high numbers of responses indicating local readings even
+for intonationally unmarked \es-sentences. Grammaticalism, insofar as
+it builds on disambiguation by logical strength, fails to predict the
+absence of answers indicative of global readings and the relative
+abundance of answers indicative of literal readings.
+
+The clearest upshot of theoretical importance of this study is that
+strength-based meaning selection does not seem to be a good
+disambiguation criterion for grammaticalism. We tentatively suggested
+an alternative selection principle for grammaticalism in terms of
+``parsing economy.'' Another important conclusion from our data is
+that \es-sentences, using non-monotonic quantifier \emph{exactly one},
+appeared to be prone to receive a ``shallow interpretation.'' This may
+be used by traditionalism to explain answers indicative of local
+readings for \es-sentences. But the point is relevant in general. The
+possibility of ``shallow interpretation'' of non-monotonic quantifiers
+should be considered also when interpreting the results of other
+experimental designs \citep[e.g.][]{CliftonDube2010:Embedded-Implic,
+  ChemlaSpector2010:Experimental-Ev}.
+
+On the methodologically side, we have argued that auditory
+presentation of sentence material should be mandatory if prosodic
+information is hypothesized to influence availability and preferences
+of readings. We also argued that theoretical positions must be
+formulated in such a way that they make testable predictions about
+reading preferences where different potential readings are allowed
+(contra a grammaticalism without commitment to any testable
+disambiguation principle). We should then try to obtain information
+about actual preference patterns by explicit comparison with
+structures whose preference structures are well-studied, ideally with
+some model of the data generating process for optimal data analysis.
 

### 2014-05-29 text/paper/paper4.tex
K2 almost final

@@
 A number of empirical studies have already studied sentences like
-(\ref{bsp:AE}) and (\ref{bsp:GE}) this issue
+(\ref{bsp:AE}) and (\ref{bsp:GE})
 \citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. Unfortunately,
-results from these studies do not provide uncontroversial evidence to
-decide between the two main rivaling positions. This is due to several
-reasons. Firstly, previous studies have only accumulated limited
-evidence pertaining to the preference relations between putative
-readings of both types of sentences. Secondly, as
-\citet{Tielvan-Tiel2012:Embedded-Scalar} and
-\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue, the putative
+results from these studies do not provide uncontroversial
+evidence. This is due to several reasons. Firstly, previous studies
+have only accumulated limited evidence pertaining to the preference
+relations between candidate readings of both types of
+sentences. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
+\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue, the alleged
 evidence for the availability of local readings of \as-sentences
@@
 grammaticalism is incongruent with the observed pattern in our
-data. Backed up by the Strongest Meaning Hypothesis
+data. Backed up by the strongest meaning hypothesis
 \citep{DalrympleKanazawa1998:Reciprocal-Expr}, grammaticalism predicts
@@
 \lc- and \ec-readings reflected the known preference for the former,
-\emph{irrespective} of the order in which each reading could first be
-judged in a given sequence. Finally, the incremental verification task
-was generally sensitive to prosody. However, significant prosodic
-effects were restricted to preference-related controls. Contrastively
-accenting scalar \emph{some} generally led to more local readings, but
-that effect was not significant. Local readings occurred in
-\es-sentences, independently of prosody, but required intonational
-marking in \as-sentences. Our analyses support the impression that
-inspection of the raw data gives, namely that the general qualitative
-pattern of reading preferences is the same for \as- and \es
-conditions, namely that literal readings are preferred over local
-readings which are preferred over global readings. More concretely,
-our analyses suggest the following preference/availability patterns
-(bracketed readings are unattested, in the sense that they are either
-unavailable or heavily dispreferred):
+with a mild bias for readings that can be judged later in the
+sequence. Also, the incremental verification task was generally
+sensitive to prosody. However, significant prosodic effects were
+restricted to preference-related controls. Contrastively accenting
+scalar \emph{some} generally led to more local readings, but that
+effect was not significant. Local readings occurred in \es-sentences,
+independently of prosody, but required intonational marking in
+\as-sentences. Our analyses support the impression that inspection of
+the raw data gives, namely that the general qualitative pattern of
+reading preferences is the same for \as- and \es-conditions: literal
+readings are preferred over local readings which are preferred over
+global readings. More concretely, our analyses suggest the following
+preference/availability patterns (bracketed readings are unattested,
+in the sense that they are either unavailable or heavily
+dispreferred):
 
@@
 Table~\ref{tab:predictions}, we quickly see that these findings are
-not predicted by neither traditionalism nor
-grammaticalism. Traditionalism, if left on its own, fails to predict
-local readings in the \es-conditions. A Grammaticalism that relies on
-the strongest meaning hypothesis fails to predict the right preference
-order and cannot explain the absence of answers indicative of global
-readings. Let's look more closely at what is and is not surprising
-under each theoretical position and then reflect on how each position
-might be adapted do deal with the observations that it does not
-predict.
+not predicted by either traditionalism or
+grammaticalism. Traditionalism fails to predict local readings in the
+\es-conditions. Disambiguation in terms of logical strength has
+grammaticalism mispredict the observed reading preferences. Let's look
+more closely at what is and is not surprising under each theoretical
+position and then reflect on how each position might be adapted do
+deal with the observations that it does not predict.
 
@@
 global readings are not available or only allow for epistemic weak
-implicatures that would be show as responses indicative of literal
+implicatures that would show as responses indicative of literal
 readings in our task. In support of this view, traditionalists could
@@
 \as-sentences with contrastive stress is easily explained by adopting
-the Intonational Markedness Hypothesis. What traditionalism does not
+the intonational markedness hypothesis. What traditionalism does not
 predict is the high number of answers indicative of local readings in
-the \es-conditions. Resorting to the Intonational Markedness
-Hypothesis does not help, because local readings were observed for
+the \es-conditions. Resorting to the intonational markedness
+hypothesis does not help, because local readings were observed for
 accented as well as in unaccented \es-sentences. It would also remain
@@
 (\ref{bsp:observed-preferences}) entirely if it equates preference for
-readings with logical strength. Failure to predict the patter in
-(\ref{bsp:observed-preferences}) is still relatively unproblematic for
-\es-sentences, where strong grammaticalism (see
-Section~\ref{sec:grammaticalism}) would simply not make any
-predictions. But for \as-sentences grammaticalism would actually
-predict that literal readings should be the least preferred. Again,
-we need to bare the caveat of Section~\ref{sec:grammaticalism} in mind
-that we are only evaluating grammaticalism with respect to a
-particular selection criterion here. The verdict, however, seems to be
-totally clear. If (\ref{bsp:observed-preferences}) is the actual
-preference order over readings, then meaning selection in terms of
-logical strength is generally on the wrong track, because no account
-that merely looks at the logical strengths of readings can plausibly
-predict the preference pattern in (\ref{bsp:observed-preferences}) for
-both \as- and \es-sentences at the same time.
+readings with logical strength. Grammaticalism predicts that literal
+readings of \as-sentences are the least preferred, contrary to
+(\ref{bsp:observed-preferences}). Again, we need to bare the caveat of
+Section~\ref{sec:grammaticalism} in mind that we are only evaluating
+grammaticalism with respect to a particular selection criterion
+here. The verdict, however, seems to be clear. If
+(\ref{bsp:observed-preferences}) is the actual preference order over
+readings, then meaning selection in terms of logical strength is
+generally on the wrong track, because no account that merely looks at
+the logical strengths of readings can plausibly predict the preference
+pattern in (\ref{bsp:observed-preferences}) for both \as- and
+\es-sentences at the same time.
 
@@
 should then ask what plausible additional assumptions would enable
-either framework accommodate the data? Again, let us look at each
+either framework to accommodate the data? Again, let us look at each
 position in turn.
@@
 Consider grammaticalism first. Our data quite clearly contradicts the
-notion that preferences follow logical strength. It seems clear that
-grammaticalism needs to be supplemented by a conceptually different
-selection criterion. Selecting readings in terms of how well they
-answer the contextually given question under discussion, as suggested
-by \citet{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An},
-is an option. But it is quite unclear what the question under
-discussion should be that guided judgements in our task. As long as a
-theory of accommodating implicit questions under discussion is
-missing, this selection criterion does not make any clear, testable
+notion that preferences follow logical strength. But grammaticalism
+could be supplemented by a conceptually different selection
+criterion. Selecting readings in terms of how well they answer the
+contextually given question under discussion, as suggested by
+\citet{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}, is
+an option. But it is quite unclear what the question under discussion
+should be that guided judgements in our task. As long as a theory of
+accommodating implicit questions under discussion is missing, this
+selection criterion does not make any clear, testable
 predictions. However, looking at the qualitative pattern in
@@
 local readings of intonationally unmarked \es-sentences, and, perhaps,
-also the large number of local readings in accented \es-sentence
+also the large number of local readings in accented \es-sentences
 compared to that in accented \as-sentences. To do so within a
-traditionalist framework seems impossible, so the most common approach
-is to explain putative evidence for local readings away as the result
-of some other phenomenon, such as typicality or contrast
+traditionalist framework is difficult, if possible at all. A common
+approach is to explain putative evidence for local readings away as
+the result of some other phenomenon, such as typicality or contrast
 \citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi,Tielvan-Tiel2014:Quantity-Matter}.
@@
 unlikely to explain the observed high number of local answers in
-\es-sentences, but that the additional assumption of 
-``shallow interpretation'' of the non-monotonic quantifiers might save
+\es-sentences, but that the additional assumption of ``shallow
+interpretation'' of the non-monotonic quantifiers might save
 traditionalism.
@@
 \es-sentences is pursued by
-\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} \citep[see
-also][]{Tielvan-Tiel2014:Quantity-Matter} in response to the data
+\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} in response to the data
 reported by \citet{ChemlaSpector2010:Experimental-Ev}. The main idea
@@
 depends on how strong the relevant visual contrast is. When an item
-with only some connections is contrasted presented alongside two
-universally connected elements, the mean rate of agreement with a
-suitable \es-sentence is significantly higher than when only one
-universally connected element is present. So, maybe our \es-sequences
-similarly provoked local readings because of an overemphasized visual
-contrast between \emph{some but not all} and \emph{all}.
+with only some connections is presented alongside two universally
+connected elements, the mean rate of agreement with a suitable
+\es-sentence is significantly higher than when only one universally
+connected element is present. So, maybe our \es-sequences similarly
+provoked local readings because of an overemphasized visual contrast
+between \emph{some but not all} and \emph{all}.
 
@@
 
-What might make this contrast-based explanation more plausible is the
-observation that subjects found \es-sentences difficult. As discussed
-in Section~\ref{sec:results}, there were a non-negligible number of
-\emph{true} answer at step 2 in the \es-sequence. This can be
-explained on the assumption that participants read the non-monotonic
-quantifier \emph{exactly one} as a monotonic quantifier \emph{at least
-  one}. Similar ``shallow interpretation'' of \emph{exactly one} would
-explain the high number of local answers for \es-sentences (and for
-\es-sentence alone). If participants processed the truth-value for an
-\es-sentence by looking for a \emph{unique} element that could be
-singled out somehow, they would need to unravel the \es-sequence up to
-the last picture. At this step contrast effects are stronger and would
-not need to compete with the proper semantic interpretation of
-\emph{exactly one}. Together, pictorial contrast effects in symbiosis
-with a ``shallow interpretation'' non-monotonic quantifiers could be
-an alternative explanation of (\ref{bsp:observed-preferences}) for
-traditionalism.
+On the other hand, what might make this contrast-based explanation
+more plausible is the observation that subjects found \es-sentences
+difficult. As discussed in Section~\ref{sec:results}, there were a
+non-negligible number of \emph{true} answer at step 2 in the
+\es-sequence. This can be explained on the assumption that
+participants read the non-monotonic quantifier \emph{exactly one} as a
+monotonic quantifier \emph{at least one}. Similar ``shallow
+interpretation'' of \emph{exactly one} would explain the high number
+of local answers for \es-sentences (and for \es-sentence alone). If
+participants processed the truth-value for an \es-sentence by looking
+for a \emph{unique} element that could be singled out a description
+like ``\dots is connected to some of its \dots'', they would need to
+unravel the \es-sequence up to the last picture where the relevant
+visual contrast is stronger. A ``shallow interpretation''-theory also
+sidesteps the puzzle why answers are given that are incompatible with
+the proper semantic meaning of \es-sentences. Together, pictorial
+contrast effects in symbiosis with a ``shallow interpretation'' of
+non-monotonic quantifiers could be an alternative explanation of
+(\ref{bsp:observed-preferences}) for traditionalism.
 
@@
 To begin with, it could be questioned whether our design reliably
-indicates the preference relation in (\ref{bsp:observed-preferences})
-among readings of our target sentences. After all, our incremental
-verification task might simply select for the weakest possible
-reading. This idea can be grounded in the observation that the
-preferred \lc-readings of our target-related controls entail the
-dispreferred \ec-readings. It could thus be argued that the difference
-in responses for preference-related controls are due to the entailment
-properties, not the known preference relation over \lc- and
-\ec-readings. However, this does not explain why the distribution of
-responses in the target conditions are obviously not governed by
-logical strength. In fact, it is a very noteworthy point that although
-entailment relations among readings differ between \as- and
-\es-sentences, the observed response pattern does not. (This is what
-is at the heart of the problem for a grammaticalism that relies on the
-strongest meaning hypothesis.)
-
-A related objection is that it is not feasible to actually compare
-results from the preference-related controls to results from our
-target conditions, because the source of different readings is
-fundamentally different. In the former we have a syntactic ambiguity,
-in the latter a set of putative pragmatic enrichments. The former is a
-case of perceived ambiguity (some of our subjects reported this), the
-latter arguably is not
+indicates the preference relations in
+(\ref{bsp:observed-preferences}). One could object that it is not
+feasible to compare results from the preference-related controls to
+results from our target conditions, because the source of different
+readings is fundamentally different. In the former we have a syntactic
+ambiguity, in the latter a set of putative pragmatic enrichments. The
+former is a case of perceived ambiguity (some of our subjects reported
+this), the latter arguably is not
 \citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
@@
 it is not clear how exactly such a more complex generating model
-should be set-up. Eventually, a full processing model, design for data
-from incremental verification tasks would be needed. We cannot offer
-such a model here, but can only the offer the model that we did use as
-a first step in that direction. More importantly, though, the only
-part of our conclusions that might plausibly change in
-(\ref{bsp:observed-preferences}) for a different generating model is
-that the 3 \emph{false} answers in the \as-conditions with neutral
-intonation might support the conclusion that the local reading is
-marginally attested. But this hypothetical effect will certainly be no
-bigger than marginal, and so no genuinely different conclusions of
-theoretical relevance should be expected.
+should be set-up. Eventually, a full processing model, designed for
+data from incremental verification tasks, would be needed. We cannot
+offer such a model here, but can only the offer a first step in that
+direction. More importantly, though, the only part of
+(\ref{bsp:observed-preferences}) that might plausibly change for a
+more encompassing model along the lines sketched above is that the 3
+\emph{false} answers in the \as-conditions with neutral intonation
+might support the conclusion that the local reading is attested. But
+this hypothetical effect will certainly be no bigger than marginal,
+and so no genuinely different conclusions of theoretical relevance
+should be expected.
 
@@
 we introduced a generative Bayesian model that gives probabilistic
-predictions about possibly observable answer patterns in our task,
-given concrete instances of relatives saliences of readings and other
+predictions about observable answer patterns in our task, given
+concrete instances of relative saliences of readings and other
 parameters. Using the observed data, in particular in connection with

### 2014-08-29 text/paper/paper4.tex
integrated comments by Fabian and Petra

@@
 \begin{abstract}
-  Scalar item \emph{some} is widely assumed to receive a pragmatic
+  The scalar item \emph{some} is widely assumed to receive a pragmatic
   meaning enrichment to \emph{some but not all} if it occurs in matrix
@@
   % freely.
-  We present new experimental data that bears on this theoretical
+  We present new experimental data that bear on this theoretical
   issue. In distinction to previous experimental approaches, we
@@
   control prosodic markedness of the scalar item. Moreover, our
-  experimental design gives insight into the preference of
-  hypothesized meaning differences, not only on their general
-  availability. The data obtained in this way turns out problematic
+  experimental sheds light on the relative preferences or salience of
+  candidate readings. The presented data turns out to be problematic
   for both a traditional Gricean view of scalar implicature
@@
 (\ref{bsp:Plain-SI-Target}) is literally true even when Hans solved
-all of the problems. But it is also usually considered to invite
-comparison with (at least) the semantically stronger universal
-quantifier \emph{all}
+all of the problems. But use of \emph{some} is also usually considered
+to invite comparison with (at least) the semantically stronger
+universal quantifier \emph{all}
 \citep[c.f.][]{Horn1972:On-the-Semantic,Gazdar1979:Pragmatics:-Imp,AtlasLevinson1981}. This
@@
 utter the semantically stronger and relevant
-(\ref{bsp:Plain-SI-Alternative}) \citep[see][for
-recent overview]{Geurts2010:Quantity-Implic}.
+(\ref{bsp:Plain-SI-Alternative}) \citep[see][for a recent
+overview]{Geurts2010:Quantity-Implic}.
 
@@
 
-This paper deals with the interpretation of two types of sentences,
-where the scalar item \emph{some} occurs in the scope of other logical
-operators. In \as-sentences (mnemonic for \textit{all \dots some
-  \dots}) as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded
-under universal quantifier \emph{all}. In \es-sentences (mnemonic for
-\textit{exactly one \dots some \dots}) like (\ref{bsp:GE}) \emph{some}
-takes scope under the non-monotonic quantifier \emph{exactly one}.
-According to current pragmatic theory, there are at least three
-relevant candidate readings for \as- and \es-sentences: (i) a
-\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
-(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
-(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
-(\ref{bsp:GE-Global}) where we enrich the meaning of (\ref{bsp:AE})
-and (\ref{bsp:GE}) with the negation of the corresponding sentences
-(\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
-\emph{some} is replaced by \emph{all}; and also (iii) a \emph{local
+Whereas the existence of such implicatures is rather uncontroversial
+for plain occurrences of \emph{some}, it is still an issue of debate
+whether comparable enrichments are also found in so-called
+``embedded'' cases, where the scalar item \emph{some} occurs in the
+scope of other logical operators. This paper deals with to such cases.
+In \as-sentences (mnemonic for \textit{all \dots some \dots}) as in
+(\ref{bsp:AE}) the scalar item \emph{some} is embedded under universal
+quantifier \emph{all}. In \es-sentences (mnemonic for \textit{exactly
+  one \dots some \dots}) like (\ref{bsp:GE}) \emph{some} takes scope
+under the non-monotonic quantifier \emph{exactly one}.  According to
+current pragmatic theory, there are at least three relevant candidate
+readings for \as- and \es-sentences: (i) a \emph{literal reading} like
+in (\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where \emph{some}
+has only its literal meaning; (ii) a \emph{global reading} like in
+(\ref{bsp:AE-Global}) and (\ref{bsp:GE-Global}) where the meaning of
+(\ref{bsp:AE}) is enriched and (\ref{bsp:GE}) with the negation of the
+corresponding sentences (\ref{bsp:AE-Alternative}) and
+(\ref{bsp:GE-Alternative}) respectively; and also (iii) a \emph{local
   reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
@@
 Addressing these questions empirically is relevant because they lie at
-the heart of the current debate about the exact location and nature of
-the interface between semantics and pragmatics. The controversy
+the heart of a current debate about the nature of quantity inferences
+and the demarkation between semantics and pragmatics. The controversy
 concerns the question under which circumstances and to what extent the
@@
 occur within the compositional computation of semantic values. Two
-opposing theoretical positions can be distinguished here:
+main theoretical positions can be distinguished here:
 \emph{traditionalism} holds in particular that local readings should
-not be readily attested unless marked by special intonation;
+not occur frequently unless marked by special intonation;
 \emph{grammaticalism} holds that local readings are available and, at
@@
 readings, even preferred (see Section~\ref{sec:grammaticalism}). To
-distinguish between these opposing positions, it is therefore
-necessary to assess the availability and relative preference of
-readings for \as- and \es-sentences under conditions that control for
-intonational markedness. This is what this paper aims to do.
-
-A number of empirical studies have already studied sentences like
+distinguish between these opposing positions, it is necessary to
+assess the availability and relative preference of readings for \as-
+and \es-sentences under conditions that control for prosodic
+markedness.
+
+A number of empirical studies have already examined sentences like
 (\ref{bsp:AE}) and (\ref{bsp:GE})
@@
 sentences. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
-\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue, the alleged
+\citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue, the alleged
 evidence for the availability of local readings of \as-sentences
 suggested by studies of \citet{CliftonDube2010:Embedded-Implic} and
-\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounds
-with what van Tiel and Geurts call \emph{typicality effects}. Finally,
-and most importantly, previous studies presented target sentences
-visually. This is highly problematic, because traditionalists admit to
-the availability of local readings as long as it is intonationally
-marked
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}.
+\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounds of
+what van Tiel and Geurts call \emph{typicality effects} (see
+Section~\ref{sec:previous-studies} for discussion). Finally, and most
+importantly, previous studies presented target sentences
+visually. However, traditionalists admit to the availability of local
+readings as long as the utterance is prosodically marked
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
 We
-will address this extant position as the \emph{intonational markedness
-  hypothesis}. But if intonation plays a role, it is vital to present
-target sentences auditorily, so as to be able to control for effects
-of ``silent prosody'' that subjects may apply when reading a sentence
+will address this extant position as the \emph{prosodic markedness
+  hypothesis}. If intonation plays a role, it is vital to present
+target sentences auditorily, and to control for effects of ``silent
+prosody'' that subjects may apply when reading a sentence
 \citep[see][]{Bader98,Fodor98}.
 
-This paper therefore presents results form an experimental study
-designed to deal with the above mentioned problems. We presented
-sentence material auditorily and explicitly manipulated intonational
-stress on embedded scalar items. To cater for potential pictorial
-confounds, such as from typicality, we employed an \emph{incremental
-  verification task} in which parts of a to-be-evaluated picture were
-hidden and only revealed piece-wise at the participants' request until
-they felt able to give a binary truth-value judgement
+This paper presents results form an experimental study designed to
+deal with the above mentioned problems. We presented sentence
+materials auditorily and explicitly manipulated intonational stress on
+embedded scalar items. To cater for potential pictorial confounds,
+such as from typicality, we employed an \emph{incremental verification
+  task} in which parts of a to-be-evaluated picture were hidden and
+only revealed piece-wise at the participants' request until they felt
+able to give a binary truth-value judgement
 \citep[see][]{Conroy2008}. This way we obtained categorical behavioral
-data that is both clearly indicative of the reading that subjects
-assumed and fairly independent of any potential pictorial
-confounds. Moreover, this method also gives information about reading
-preferences. We validated this by including a control condition with
-ambiguous sentences with a well-known preference on available
-readings.
-
-The data obtained by this method is problematic for both
-traditionalism and grammaticalism. Contrary to the predictions of
-traditionalism, we observed many answers indicative of local readings
-of \es-sentences, irrespective of intonational markedness. But also
-grammaticalism is incongruent with the observed pattern in our
-data. Backed up by the strongest meaning hypothesis
-\citep{DalrympleKanazawa1998:Reciprocal-Expr}, grammaticalism predicts
-local readings to be the preferred readings, but we found no evidence
-for that. More strongly even, the preference order among putative
-readings suggested by our data cannot even in principle be explained
-by comparisons of logical strength among putative readings. In sum,
-our data sheds doubt on both traditionalism and grammaticalism in
-their currently most common forms. We conclude the paper by some
-speculation about how either position might be amended in the light of
-our data.
+data that is both more clearly indicative of the reading that subjects
+assumed and mor independent of any potential pictorial confounds, such
+as the mentioned typicality effects. Moreover, this method also gives
+information about reading preferences. We validated this by including
+control conditions with ambiguous sentences with a well-known
+preference on available readings.
+
+% The data obtained by this method is problematic for both
+% traditionalism and grammaticalism. Contrary to the predictions of
+% traditionalism, we observed many answers indicative of local readings
+% of \es-sentences, irrespective of intonational markedness. But also
+% grammaticalism is incongruent with the observed pattern in our
+% data. Backed up by the strongest meaning hypothesis
+% \citep{DalrympleKanazawa1998:Reciprocal-Expr}, grammaticalism predicts
+% local readings to be the preferred readings, but we found no evidence
+% for that. More strongly even, the preference order among putative
+% readings suggested by our data cannot even in principle be explained
+% by comparisons of logical strength among putative readings. In sum,
+% our data sheds doubt on both traditionalism and grammaticalism in
+% their currently most common forms. We conclude the paper by some
+% speculation about how either position might be amended in the light of
+% our data.
 
@@
 approach. Section~\ref{sec:exp} eventually contributes our
-experimental design and our results.
+experimental design, analyses and results.
 
@@
 An \as-sentence like (\ref{bsp:AE}), repeated below, has a literal
-reading (\lit) as in (\ref{bsp:AE-Literal}), a global reading (\glb) as in
-(\ref{bsp:AE-Global}) and a local reading (\loc) as in (\ref{bsp:AE-Local}).
+reading (\lit) as in (\ref{bsp:AE-Literal}), a global reading (\glb)
+as paraphrased in (\ref{bsp:AE-Global}) and a local reading (\loc) as
+in (\ref{bsp:AE-Local}).
 
@@
 %
-Examples of these kinds of situations are given in
+Examples of these kinds of situations are shown in
 Figure~\ref{fig:AS-distinguishing-pics}, where the dots on the right
@@
 papers and an arrow from a student to a paper indicates that the
-student read the paper. Notice that other arrangements of arrows might
-equally well serve as examples for the various situations.
+student read the paper. % Notice that other arrangements of arrows might
+% equally well serve as examples for the various situations.
 
@@
 
-  \caption{Distinguishing scenarios for \as-sentences}
+\caption{Examples of distinguishing situations for \as-sentences}
   \label{fig:AS-distinguishing-pics}
@@
 
-The situation for \es-sentences like (\ref{bsp:GE}) is similar but a
+The case for \es-sentences like (\ref{bsp:GE}) is similar but a
 little more complicated because the embedding quantifier is
@@
 
-\noindent Entailment relations in this case are non-linear:
+\noindent Entailment relations in this case are non-linearly ordered:
 \begin{exe}
@@
 \noindent Finally, \loc and \lit are logically independent: all
-possible combinations of truth-values for \loc and \lit are possible.
+combinations of truth-values for \loc and \lit are possible.
 
@@
 values for candidate readings. These are given in
-Table~\ref{fig:situations-GS} and named following
-\citet{ChemlaSpector2010:Experimental-Ev}. Examples for each situation
-are given in Figure~\ref{fig:ES-distinguishing-pics}.
+Table~\ref{fig:situations-GS} on page~\pageref{fig:situations-GS} and
+named following \citet{ChemlaSpector2010:Experimental-Ev}. Examples
+for each situation are given in
+Figure~\ref{fig:ES-distinguishing-pics}.
 
@@
 
-  \caption{Distinguishing scenarios for \es-sentences}
+  \caption{Examples of distinguishing situations for \es-sentences}
   \label{fig:ES-distinguishing-pics}
@@
 overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation}. We
-will refer to these here as \mymark{traditionalism} and
+will refer to these as \mymark{traditionalism} and
 \mymark{grammaticalism} and treat each one in turn. Since there is
-some leeway in assessing the predictions for each (depending on which
-of several additional assumptions to adopt), we will distinguish
-different varieties of both. Predictions of all relevant variants are
-summarized in Table~\ref{tab:predictions} on
+some leeway in assessing the predictions for each approach (depending
+on which of several additional assumptions to adopt), we will
+distinguish different varieties of both of them. Predictions of all
+relevant variants are summarized in Table~\ref{tab:predictions} on
 page~\pageref{tab:predictions}.
@@
 implicature, but as a different pragmatic process triggered by
-prosodic markedness. We examine this \emph{intonational markedness
+prosodic markedness. We address this \emph{prosodic markedness
   hypothesis} separately in Section~\ref{sec:inton-mark-hypoth},
@@
 
-The Gricean recipe applies also to \as- and \es-sentences and derives
-the global reading in a straightforward way. Consequently,
-traditionalism predicts that both literal and global readings are
-available: literal readings, because these form the starting point of
-pragmatic reasoning; global readings because these may be arrived at
-by the Gricean recipe.
+As for \as- and \es-sentences, the Gricean recipe derives global
+readings in a straightforward way. Consequently, traditionalism
+predicts that both literal and global readings are available: literal
+readings, because these form the starting point of pragmatic
+reasoning; global readings because these may be arrived at by the
+Gricean recipe.
 
@@
 over literal readings. On the other hand, if auxiliary assumptions are
-implausible, traditionalism would predict that the literal readings
-would be preferred over the global one. Consequently, there are at
-least two varieties of traditionalism that, depending on which
-additional assumptions we would make, yield slightly different
-predictions: \mymark{the strong variety of traditionalism} maintains
-that the auxiliary assumptions of the Gricean recipe hold
-usually/strongly/unless-completely-intenable and therefore predicts
-that global readings are preferred over literal ones; \mymark{the weak
-  variety of traditionalism} holds that the auxiliary assumptions are
-more fragile and predicts that literal readings are preferred over the
-global ones.\fn{We mention for clarity that although weak
-  traditionalism does not predict the global reading to be preferred,
-  it might still predict an \emph{epistemically weak implicature},
-  similar to the global reading, that the speaker is uncertain whether
-  the stronger alternative is true. (See also the discussion in
+implausible, traditionalism would predict that literal readings would
+be preferred over global ones. Consequently, there are at least two
+varieties of traditionalism that, depending on which additional
+assumptions we would make, yield slightly different predictions:
+\mymark{the strong variety of traditionalism} maintains that the
+auxiliary assumptions of the Gricean recipe hold (e.g., as a matter of
+strong default) and therefore predicts that global readings are
+preferred over literal ones; \mymark{the weak variety of
+  traditionalism} holds that the auxiliary assumptions are more
+fragile and predicts that literal readings are preferred over global
+ones.\fn{We mention for clarity that although weak traditionalism does
+  not predict global readings to be preferred, it might still
+  predict an \emph{epistemically weak implicature}, similar to the
+  global reading, that the speaker is uncertain whether the stronger
+  alternative is true. (See also the discussion in
   Section~\ref{sec:discussion-1})}
@@
 (\ref{bsp:AE-Alternatives-Extended}) is an available alternative. We
-should therefore introduce another distinction: \mymark{restricted
+therefore introduce another distinction: \mymark{restricted
   traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
@@
 
-Still, even unrestricted traditionalism would not predict that the
-local reading is preferred over the global reading. This is because
-the derivation of the local reading via
+As far as preferences are concerned, even unrestricted traditionalism
+would not predict that the local reading is preferred over the global
+reading. This is because the derivation of the local reading via
 (\ref{bsp:AE-Alternatives-Extended}) hinges on yet another auxiliary
@@
   have been proposed
-  \citep[e.g.][]{Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}
-  but this simple formulation is sufficient for the purposes of this
-  paper.}
+  \citep[e.g.][]{Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}.}
 \begin{exe}
@@
       \ex \label{Grammar-Local-GE} \mymark{Exactly one} of the
-        students \mymark{$\exh$}( solved
+        students \mymark{$\exh$}(solved
         \mymark{some} of the problems).
@@
 
-The grammatical approach, as described so far, is not yet a
-respectable theory. It makes little empirical commitments of
-substance. It must be supplemented by a selection principle that
-determines which of the many readings made available by the grammar
-actually obtain or are preferred. Proponents of grammaticalism are
-aware of this and have suggested some tentative disambiguation
+The grammatical approach, as described so far, is not yet a fully
+articulated theory. To make concrete predictions, it must be
+supplemented by a selection principle that determines which of the
+many readings made available by the grammar actually obtain or are
+preferred. Proponents of grammaticalism are aware of this and have
+suggested some tentative disambiguation
 strategies. \citet{Magri2011:Another-Argumen}, for example, opts for
@@
 seems to be the most prominent in the literature and because it makes
-the clearest predictions. That means that all we will say about
-grammaticalism in this paper strictly applies only to grammaticalism +
-strength based selection of readings.
+the clearest predictions.
 
@@
 (\ref{bsp:Entailments-AS}) and (\ref{bsp:Entailments-GE}): for
-\as-sentences weak grammaticalism predicts that local readings are
+\as-sentences, weak grammaticalism predicts that local readings are
 preferred over global readings which in turn are preferred over
@@
 
-\subsection{The Intonational Markedness Hypothesis}
+\subsection{The Prosodic Markedness Hypothesis}
 \label{sec:inton-mark-hypoth}
@@
 be available, many authors who adhere to a traditionalist position
-maintain that local readings are available if and only if the
-embedded scalar item is intonationally marked by contrastive stress
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Scalar-expressi}. This
+propose that local readings are available if the embedded scalar item
+is prosodically marked by contrastive stress
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
 is taken to be continuous with other cases where pragmatic enrichments
-can take scope under logical operators if and only if the relevant
-focal accent is present (\ref{bsp:Stress}).
+can take scope under logical operators if the relevant focal accent is
+present (\ref{bsp:Stress}).
 
@@
 
-\noindent The \emph{intonational markedness hypothesis}, as we will
-call it here, is then an addition to the traditionalist's explanatory
-repertoire. The crucial point is that under this extra assumption,
-local readings are a marked phenomenon, and not the product of the
-same process as run-of-the-mill scalar implicatures. If supplemented
-with the intonational markedness hypothesis, traditionalists would
-therefore predict that local readings are available for \as- and
-\es-sentences, but only if intonationally marked by contrastive
-stress; since this reading is marked, presumably it would still be
-predicted to be dispreferred even if available.
-
-Though there seems to be general consensus about such potential
-prosodic effects, empirical evidence for this assumption is still
-scarce. One notable exception comes from a pilot study reported in
+\noindent The \emph{prosodic markedness hypothesis}, as we will call
+it here, is then an addition to the traditionalist's explanatory
+repertoire. Under this extra assumption, local readings are a marked
+phenomenon, and not the product of the same process as run-of-the-mill
+scalar implicatures. If supplemented with the prosodic markedness
+hypothesis, traditionalists would therefore predict that local
+readings are available for \as- and \es-sentences, but only if
+prosodicly marked by contrastive stress.
+
+To date, empirical evidence for this assumption is still scarce. One
+notable exception comes from a pilot study reported in
 \citet{Frazier08}, in which participants were instructed to read
@@
   She will invite Fred or Sam but not both}). Contratry to the
-silent-prosodic effects reported in the pilot experiment by Frazier
-and colleagues, the authors found a significant impact of overtly
-realized contrastive accents on implicature processing: Besides a
-general advantage for non-strengthened readings, focal accents
-significantly increased the strengthened interpretation (from 16.4 \%
-to 28.6 \%). These results are compatible with the "focus
-strengthening hypothesis" proposed by the authors.
+silent-prosodic effects reported in the pilot experiment by Frazier,
+the authors found a significant impact of overtly realized contrastive
+accents on implicature processing: Besides a general advantage for
+non-strengthened readings, focal accents significantly increased the
+strengthened interpretation (from 16.4 \% to 28.6 \%). These results
+are compatible with the "focus strengthening hypothesis" proposed by
+the authors.
 
@@
 of \as- and \es-sentences should present sentential material
-auditorily and explicitly address the intonational markedness
+auditorily and explicitly address the prosodic markedness
 hypothesis.
@@
 studies do not provide conclusive evidence about the availability and
-preference of relevant readings and do not speak to intonational
+preference of relevant readings and do not speak to prosodic
 markedness effects.
@@
 were presented with pictures like those in Figure~\ref{fig:weak} and
-\ref{fig:local} where the local reading gets a different truth-value
-than the literal and the global reading. For \as-sentences, the local
-reading is false for the critical picture in Figure~\ref{fig:weak}
-whereas the literal and global readings are true; for \es-sentences
-the local reading is true for the critical picture in
-Figure~\ref{fig:local}, whereas the literal and global readings are
-false.
+\ref{fig:local} (pages \pageref{fig:weak} and \pageref{fig:local})
+where the local reading gets a different truth-value than the literal
+and the global reading. For \as-sentences, the local reading is false
+for the critical picture in Figure~\ref{fig:weak} whereas the literal
+and global readings are true; for \es-sentences the local reading is
+true for the critical picture in Figure~\ref{fig:local}, whereas the
+literal and global readings are false.
 
@@
 In a reply to \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s
-study \citet{CliftonDube2010:Embedded-Implic} raised the question
+study. \citet{CliftonDube2010:Embedded-Implic} raised the question
 whether the use of a picture-verification paradigm might have been
@@
 \citeauthor{CliftonDube2010:Embedded-Implic} seem to indicate that
-participants' choices for readings of \as-sentences might be affected
-by the specific experimental paradigm used \citep[but see][for
-critique of the latter
-design]{GeurtsTielvan-Tiel2013:Scalar-expressi}. Unfortunately,
+participants' choices for readings of \as-sentences might have been
+affected by the specific experimental paradigm used \citep[but
+see][for critique of the latter
+design]{GeurtsTielvan-Tiel2013:Embedded-Scalar}. Unfortunately,
 \citet{CliftonDube2010:Embedded-Implic} did not test both universal
@@
 along these
-lines]{GeurtsTielvan-Tiel2013:Scalar-expressi,Tielvan-Tiel2014:Quantity-Matter,Tielvan-Tiel2012:Embedded-Scalar}.
+lines]{GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter,Tielvan-Tiel2012:Embedded-Scalar}.
 
@@
 typicality-based explanation does not extend to \es-sentences in an
-obvious way. Moreover, typicality itself is not a satisfactory
-primitive in a putative explanation of the use of quantifiers. Rather
-it is possible to explain typicality judgements as the outcome of
-Gricean speaker preferences for informative descriptions, just like
-those that rationalize quantity implicatures
-\citep{Franke2014:Typical-use-of-}. For these reasons, we believe that
-typicality and other pictorial effects need to be taken seriously in
-the experimental design, but do not give a satisfactory account of the
-observed variation all by themselves.
+obvious way \citep[c.f.][for critical reflection on typicality-based
+explanations]{Cummins2014:Typicality-made}. Moreover, typicality
+itself is not a satisfactory primitive in a putative explanation of
+the use of quantifiers. Rather it is possible to explain typicality
+judgements as the outcome of Gricean speaker preferences for
+informative descriptions, just like those that rationalize quantity
+implicatures \citep{Franke2014:Typical-use-of-}. For these reasons, we
+believe that typicality and other pictorial effects need to be taken
+seriously in the experimental design, but do not give a satisfactory
+account of the observed variation all by themselves.
 
@@
 \citep[e.g.][]{Augurzky08,Bader98,Fodor98,Fodor02,Kentner12,
-  Steinhauer01}. If we adopt the intonational markedness hypothesis
+  Steinhauer01}. If we adopt the prosodic markedness hypothesis
 described in Section~\ref{sec:inton-mark-hypoth}, as many
@@
 item
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}.
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
 But if intonation can have this role, it is necessary to control for
 silent accent placement. Ideally, therefore, we should present
-sentences auditorily and manipulate contrastive stress systematically.
+sentences auditorily and systematically manipulate contrastive stress.
 
@@
 picture verification \citep[see][]{Conroy2008}. The general idea is
-that subjects are requested to judge sentence material based on
-pictures that do not necessarily contain all the information necessary
-to judge a certain reading true or false. In that case, participants
-can demand that more information be revealed. Participants are
-instructed to make a truth-value judgment as soon as they are able
-to. When they do, the trial ends.
+that subjects are requested to judge sentence material with respect to
+pictures that do not necessarily contain all the information relevant
+for judging a certain reading true or false. In that case,
+participants can demand that more information be
+revealed. Participants are instructed to make a truth-value judgment
+as soon as they are able to. When they do, the trial ends.
 
@@
 
-\es-sentences, due to the non-linear relationship of readings
-described in Section~\ref{sec:get-know-your}, require a slightly
-different sequence of unfolding which yields a different order in
+Due to the non-linear entailment order of readings described in
+Section~\ref{sec:get-know-your}, \es-sentences require a slightly
+different sequence of unfolding, which yields a different order in
 which truth-value judgments can be made.
@@
 %
-For a sentence like (\ref{ex:es}) we obtain an unambiguous mapping
+For a sentence like (\ref{ex:es}), we obtain an unambiguous mapping
 between truth judgements and readings with the sequence in
@@
 had an influence on responses, we included a second type of control
-conditions. Moreover, these controls served as a test whether the
-incremental verification task could possibly detect at least ordinal
-preference relations among multiple candidate readings. Finally, these
-conditions also controlled whether prosodic information can, in
-principle, shift answer patterns in the present task. Note that for
-our target sentences, the logical entailment relations between
-readings always require local readings to be evaluated at the end of a
-sequence. It could thus in principle be possible that subjects never
-reach this point, because they give truth-value judgements earlier,
-thereby ending the trial. In that case it would be unclear if these
+conditions.  These controls served as a test whether the incremental
+verification task could possibly detect at least ordinal preference
+relations among multiple candidate readings. Finally, these conditions
+also controlled whether prosodic information can, in principle, shift
+answer patterns in the present task. Note that for our target
+sentences, the logical entailment relations between readings always
+require local readings to be evaluated at the end of a sequence. It
+could thus in principle be possible that subjects never reach this
+point, because they give truth-value judgements earlier, thereby
+ending the trial. In that case it would be unclear whether these
 decisions had been affected by a general unavailability of local
@@
 the preferred one. By including globally ambiguous structures with a
-known preference over available readings, we thus intended to test
-whether participants in our task occasionally choose dispreferred
-readings, even if these were available only at a critical position
-following the preferred readings.
+known preference over available readings, we thus tested whether
+participants in our task occasionally choose dispreferred readings,
+even if these were available only at a critical position following the
+preferred readings.
 
@@
 \end{exe}
-In late-closure sentences, a modifier such as a relative clause or a
+In late-closure sentences, a modifier like a relative clause or a
 prepositional phrase (\acro{pp}) can be attached to one of two
@@
 reading ((\ref{bsp:target-related-LC}). Alternatively, the \acro{pp}
-can be attached to the whole conjoined \acro{np} \emph{circles and
+can be attached to the whole conjunctive \acro{np} \emph{circles and
   squares}, corresponding to the \emph{early-closure} (\ec) reading
@@
 
-For each such sentence, two sequences were designed: one in which the
+For each sentence, two sequences were designed: one in which the
 preferred \lc-reading could be judged first (Figure~\ref{fig:exlc}),
@@
 
-\noindent We therefore recorded sentences by a phonetically trained
-female native speaker of German familiar with the concept of
-contrastive focus and instructed her to produce contrasts as described
-above. Both \as-sentences and \es-sentences were recorded in two
+\noindent Out sentences were read by a phonetically trained female
+native speaker of German familiar with the concept of contrastive
+focus. Both \as-sentences and \es-sentences were recorded in two
 versions each. In the accented version, a contrastive stress was
@@
 an \lc-reading. Thus, a phrase boundary between {\it squares} and {\it
-  with} in (\ref{bsp:target-related}) corresponds to an \ec-reading,
-whereas a prosodic phrase boundary following {\it circles} corresponds
-to an \lc-reading.
+  with} in (\ref{bsp:target-related}) supports an \ec-reading, whereas
+a prosodic phrase boundary following {\it circles} supports an
+\lc-reading.
 
@@
 
-\subsection{Procedure}
+\subsection{Methods}
+\label{sec:materials}
+
+\subsubsection{Procedure}
 \label{sec:procedure}
+
 Each experimental trial proceeded as described above. The sentence was
@@
 sentence (up to three times), (ii) request additional pictorial
-information, (iii) respond "yes, fits" or (iv) "no, does not fit". At
-the beginning of an experimental session participants received written
-instructions on their task. Then they completed an interactive
-training consisting of 15 trials in which they were familiarized with
-the task.  After the training the actual experiment
-started. Participants were tested individually in a silent room. Each
-session was divided into three blocks and participants were told that
-they could take breaks between blocks. In total, an experimental
-session took about one hour. At the end of the session participants
-received 8 euros compensation.
-
-\subsection{Materials}
-\label{sec:materials}
+information, (iii) respond ``yes, fits'' or (iv) ``no, does not fit''
+(German: ``passt'' or ``passt nicht''). At the beginning of an
+experimental session participants received written instructions on
+their task. Then they completed an interactive training consisting of
+15 trials in which they were familiarized with the task.  After the
+training the actual experiment started. Participants were tested
+individually in a silent room. Each session was divided into two
+blocks and participants were told that they could take breaks between
+blocks. In total, an experimental session took about one hour. At the
+end of the session participants received 8 euros compensation.
+
+\subsubsection{Materials}
 
@@
 \paragraph{Preference-related control sentences.}
-For controlling preferences, 28 sentences that were ambiguous between
-a \lc and an \ec-reading, as well as 28 of their
-disambiguated counterparts were constructed as described above. In
-these sentences, subject \acros{dp} were always denoting icons and
-were followed by an auxiliary. In the ambiguous sentences, the
-auxiliary was followed by two {\it mit}-\acros{pp}.  The first of
-these \acros{pp} consisted in a coordination of two nouns denoting
+For controlling preferences, 30 sentences that were ambiguous between
+a \lc and an \ec-reading, as well as 30 of their disambiguated
+counterparts were constructed as described above. In these sentences,
+subject \acros{dp} were always denoting icons and were followed by an
+auxiliary. In the ambiguous sentences, the auxiliary was followed by
+two {\it with}-\acros{pp} (German: ``mit'').  The first of these
+\acros{pp} consisted in a coordination of two nouns denoting
 geometrical objects, whereas the second \acro{pp} denoted icons. In
@@
 Before entering the judgment task, experimental items and
-preference-related fillers were analyzed with respect to their acoustic
+preference-related controls were analyzed with respect to their acoustic
 properties. As both accented elements as well as prosodic boundaries
@@
 due to lexical differences between the \as and \es-conditions. As
-preference-related fillers did not differ with respect to their lexical
+preference-related controls did not differ with respect to their lexical
 properties, we carried out word-by-word analyses for these
@@
 vs.~\emph{exactly one}) and \acro{Prosody} (accented vs.~unaccented) were
-carried out. For the preference-related fillers, we carried out
+carried out. For the preference-related controls, we carried out
 one-factorial \acros{anova} with the factor \acro{Prosody} (early
@@
 
-\paragraph{Preference-related fillers.} 
+\paragraph{Preference-related controls.} 
 Differences between maximal and minimal F0 values for each of the
@@
 comparison between neutral prosody and a \emph{late boundary} did not
-reach significance (\emph{p}>.2). Finally, durational analyses on
-reveal that all prosodic realizations (\emph{neutral} vs. (\emph{early
+reach significance (\emph{p}>.2). Finally, durational analyses reveal
+that all prosodic realizations (\emph{neutral} vs. (\emph{early
   boundary} vs. (\emph{late boundary})) differ significantly from each
@@
 duration and F0 range, prosodic boundaries for our preference-related
-fillers were realized by pre-final lengthening (i.e., an increase in F0
+controls were realized by pre-final lengthening (i.e., an increase in F0
 and duration at the position preceding the boundary).
@@
 \paragraph{Lists.}
-Experimental items and preference-related fillers were evenly
+Experimental items and preference-related controls were evenly
 distributed across lists. For the \as- and \es-sentences together with
@@
 
-\subsection{Participants}
-\label{sec:participants}
+\subsubsection{Participants.}
 
@@
 one of these readings and as {\it error} if not. The majority of
-answers are indicative of a literal reading (90.35\% / 86.84\% in
-neutral / accented \as-conditions, and 68.42\% in both neutral /
-accented \es-conditions). Only two answers across all critical
-conditions fall into the category indicative of global
-readings. Judgements indicative of local readings, on the other hand,
-are more frequent (2.63\% / 7.02\% for neutral / accented
-\as-conditions, and 12.28\% / 14.04\% for neutral / accented
-\es-conditions).
+answers are indicative of a literal reading (\as-neutral: 90.4\%,
+\as-accented: 86.8\%, \es-neutral: 68.4\%, \es-accented: 68.4\%). Only
+two answers across all critical conditions fall into the category
+indicative of global readings. Judgements indicative of local
+readings, on the other hand, are more frequent (\as-neutral: 2.6\%,
+\as-accented: 7.0\%, \es-neutral: 12.3\%, \es-accented: 14.0\%).
 
@@
 differs substantially between \as- and \es-conditions. There are
-7.02\% / 4.39\% unclassifiable judgements in the neutral / accented
-\as-conditions, but 19.30\% / 17.54\% in the neutral / accented
-\es-conditions. A look at the right-hand side of
+7.0\% / 4.4\% unclassifiable judgements in the neutral / accented
+\as-conditions, but 19.3\% / 17.6\% in the neutral / accented
+\es-conditions respectively. A look at the right-hand side of
 Table~\ref{tab:count_data_CC} reveals that there is some systematicity
-in 'error' answers. Most answers that we classified as 'errors' are
-plausibly explained as a few random errors, a handful of mistakes
+in 'error' answers. Most answers that we classified as 'errors' have a
+plausible explanation: random errors, a handful of mistakes
 resulting from confusing buttons for \emph{true} and \emph{false} and
@@
 substantial number of \emph{true} responses where given at the second
-position of \es-sequences (9.65\% / 8.77\%) which is shown in
+position of \es-sequences (9.7\% / 8.8\%) which is shown in
 Figure~\ref{fig:exseqES2}. Although this position in the sequence is
@@
 levels \as and \es, \textsc{Accent} with levels \emph{neutral} and
-\emph{accented}, and \textsc{Position} with levels 1 through 3 (coding
+\emph{accented}, and \textsc{Trial} with levels 1 through 3 (coding
 whether it was the first, second or third time that a participant saw
@@
 counts to apply log-linear regression. We determined the ``best''
-predictor of the data by a gradient search over hierarchical models in
+model of the data by a gradient search over hierarchical models in
 terms of AICs, starting from the saturated model. The best model takes
@@
 17.19$, $df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$
-of the saturated model)). Crucially, factors \textsc{Position} and
+of the saturated model)). Crucially, factors \textsc{Trial} and
 \textsc{Accent} are spurious in the best model. This suggests that
@@
 evidence for the maintenance of belief in local readings in our
-setting. But we need to be careful. The regression analysis tells us
-that the number of errors and the number of local readings were
-similar in all conditions. But the distribution of answers in
-Figure~\ref{fig:JudgmentsK2} shows that small error counts occur at
-many different steps, whereas we do see a concentrated rise in answers
-at the critical position for local readings. Also, so far we have not
-taken into account the sequential structure of our task. It might be
-that local readings are infrequent because subjects tend to exit early
-in the sequence, rather than late. Or it might be that our count for
-local answers is exaggerated by a bias to answer later in the
-sequence. This is why we need preference-related controls and a more
-fine-grained analysis eventually.
+setting. The regression analysis tells us that the number of errors
+and the number of local readings were similar in all conditions. But
+the distribution of answers in Table~\ref{tab:count_data_CC} shows
+that small error counts occur at many different steps, whereas we do
+see a concentrated rise in answers at the critical position for local
+readings. Also, so far we have not taken into account the sequential
+structure of our task. This is where preference-related controls
+are relevant.
 
@@
 \lc-readings, fewer as \ec-readings. Moreover, intonation does seem to
-have the expected effect as well: as compared to neutral intonation,
+have the expected effect as well: as compared to neutral phrasing,
 \lc-cueing intonation increases the count for \lc-readings, while
-\ec-cueing increases the count for \ec-readings. If we compare the
-number of \lc- or \ec-readings for each intonation type across
+\ec-cueing prosody increases the count for \ec-readings. If we compare
+the number of \lc- or \ec-readings for each intonation type across
 sequences, we see that there are always more answers indicative of the
@@
 28 \emph{false} answers at step 5 where \emph{true} answers would be
-taken as indicative of \lc-readings.% \fn{A general tendency to answer
-% later in the sequence would explain this. The reason why we do not
-% see a similar effect in the critical conditions, might be because
-% the literal reading is so dominant.}
-Finally, intonation patterns
-that cue \ec-readings seem to have led to more mistakes than other
-intonation patterns.
+taken as indicative of \lc-readings. Finally, intonation patterns that
+cue dispreferred \ec-readings seem to have led to more mistakes than
+other intonation patterns.
 
@@
 \emph{error}, \textsc{Accent} with levels \emph{neutral},
-\emph{\lc-cue} and \emph{\ec-cue}, \textsc{Position} with levels 1 to
+\emph{\lc-cue} and \emph{\ec-cue}, \textsc{Trial} with levels 1 to
 3, and \textsc{Condition} with levels \lc and \ec for the picture
@@
 $AIC=256.63$ (compared to $AIC=322.3$ of the saturated model)). Factor
-\textsc{Position} again turned out to be spurious, suggesting that
+\textsc{Trial} again turned out to be spurious, suggesting that
 answer patterns are stable over the duration of the experiment. Unlike
 for the critical conditions, factor \textsc{Accent} is retained, and
-it interacts with \textsc{Reading}, suggesting that intonational cues
+it interacts with \textsc{Reading}, suggesting that prosodic cues
 significantly influenced the dominant reading.
@@
 Table~\ref{tab:Coefficients-TF}, reveals that there were significantly
-more \ec-readings in the \lc-condition and vice versa. This is evident
-from the significant \emph{negative} deviation from the baseline of
-\ec-readings in the interaction coefficient for
+more \ec-readings in the \lc-condition than in the \ec-condition, and
+more \lc-readings in the \ec-condition than in the \lc-condition. This
+is evident from the significant \emph{negative} deviation from the
+baseline of \ec-readings in the interaction coefficient for
 \textsc{Reading}.\lc:\textsc{Condition}.\lc. The log-linear model
-therefore suggests that there is a bias for late responses in a
-sequence. If such a preference for late responses holds for critical
-conditions as well, then the rather small numer of local responses
-that we observed is more likely overemphasized by our sequential
-decision task than that it is underemphasized. The following Bayesian
-analysis further probes into this matter in order to establish how
-strongly the sequence-effect might have emphasized local readings and,
-from there, whether we should uphold belief in local readings.
+therefore indicates that there is a bias for late responses in a
+sequence. Given this, the number of local responses in critical
+conditions might be increased by a sequential bias to answer late. The
+following Bayesian analysis further probes into this matter in order
+to establish how strongly the sequence-effect might have emphasized
+local readings and, from there, whether we should uphold belief in
+local readings.
 
@@
 of the pictorial sequence. If there is a tendency to judge sentences
-earlier in the sequence, rather than later, that is to be attributed
+earlier in the sequence, rather than later, that has to be attributed
 to the sequential bias.
@@
   \caption{Estimated posteriors for the salience of \lc- and
-    \ec-readings for different intonational cues. Lines under curves
-    mark are 95\% HDIs (see Footnote~\ref{fn:HDI}).}
+    \ec-readings for different prosodic cues. Lines under curves
+    indicate 95\% HDIs (see Footnote~\ref{fn:HDI}).}
   \label{fig:Posterior_TF}
@@
   Highest Density Interval (HDI) is a convex region of values over
-  which 95\% of the distribution's probability density is divided,
+  which 95\% of the distribution's probability density is distributed,
   such that no value outside of that region has higher probability
@@
   \centering
-  \subfloat[neutral][]{
+  \subfloat[][neutral]{
       \includegraphics[width=0.45\textwidth]{PostDiffT_ASntr.pdf}
@@
   \hfill
-  \subfloat[accented][]{
-      \includegraphics[width=0.45\textwidth]{PostDiffT_ASntr.pdf}
+  \subfloat[][accented]{
+      \includegraphics[width=0.45\textwidth]{PostDiffT_ASacc.pdf}
   }
   \caption{Posteriors over differences between salience levels for
-    local and global readings of \as-sentences.}
+    local and global readings of \as-sentences. As zero is contained
+    in the 95\% HDI for both neutral and accented variants, there is
+    no justification for assuming a difference in salience.}
   \label{fig:PostDiffTAS}
@@
 
-\paragraph{Summary \& Interpretation.} High scores of success in
-control conditions show that participants understood the incremental
-verification task and were able to give judgements at the right point
-in a picture sequence. Results for the preference-related controls
-show that our design is able to detect multiple readings and
-preferences among these. Crucially, the amount of response types for
-\lc- and \ec-readings reflected the known preference for the former,
-with a mild bias for readings that can be judged later in the
-sequence. Also, the incremental verification task was generally
-sensitive to prosody. However, significant prosodic effects were
-restricted to preference-related controls. Contrastively accenting
-scalar \emph{some} generally led to more local readings, but that
-effect was not significant. Local readings occurred in \es-sentences,
-independently of prosody, but required intonational marking in
-\as-sentences. Our analyses support the impression that inspection of
-the raw data gives, namely that the general qualitative pattern of
+\paragraph{Summary \& Interpretation.} The present study investigated
+prosodic effects on quantifier interpretation by employing a new
+experimental paradigm, the incremental verification
+task. Based on a current debate in the literature, we were
+specifically interested in whether ``local readings'' of sentences
+where \emph{some} is embedded under another quantifier can be found,
+and how salient these readings are under varying prosody of auditorily
+presented sentence material, in particular the presence or absence of
+contrastive stress on embedded \emph{some}.
+
+High scores of success in control conditions show that participants
+understood the incremental verification task and were able to give
+judgements at the right point in a picture sequence. Results for the
+preference-related controls show that our design is able to detect
+multiple readings and preferences among these. Crucially, the amount
+of response types for \lc- and \ec-readings reflected the known
+preference for the former, with a mild bias for readings that can be
+judged later in the sequence. Also, the incremental verification task
+was generally sensitive to prosody. However, significant prosodic
+effects were restricted to preference-related controls. Contrastively
+accenting scalar \emph{some} generally led to more local readings, but
+that effect was not significant. Local readings occurred in
+\es-sentences, independently of prosody, but required prosodic marking
+in \as-sentences. Our analyses support the impression that inspection
+of the raw data gives, namely that the general qualitative pattern of
 reading preferences is the same for \as- and \es-conditions: literal
@@
     \begin{xlist}
-      \ex \as-ntr: \ \ \ \lit \ >  (\loc \ \  $\sim$ \glb)
+      \ex \as-ntr: \ \ \ \lit \ (>  \loc \ \  $\sim$ \glb)
       \ex \as-acc: \ \ \ \lit \ > \ \loc \ \ ( $\sim$ \glb)
@@
 not predicted by either traditionalism or
-grammaticalism. Traditionalism fails to predict local readings in the
-\es-conditions. Disambiguation in terms of logical strength has
-grammaticalism mispredict the observed reading preferences. Let's look
-more closely at what is and is not surprising under each theoretical
-position and then reflect on how each position might be adapted do
-deal with the observations that it does not predict.
+grammaticalism. We address each position separately in the following.
 
@@
 instance, would hold that the extra assumptions needed to derive
-global readings are not available or only allow for epistemic weak
-implicatures that would show as responses indicative of literal
-readings in our task. In support of this view, traditionalists could
-argue that the task's rather high processing demands lead to a
-suppression of global readings, in line with the findings of
+global readings (e.g., a speaker competence assumption) are not
+available or only allow for epistemic weak implicatures that would
+show as responses indicative of literal readings in our task. In
+support of this view, traditionalists could argue that the task's
+rather high processing demands lead to a suppression of global
+readings, in line with the findings of
 \citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
@@
 \as-sentences with contrastive stress is easily explained by adopting
-the intonational markedness hypothesis. What traditionalism does not
+the prosodic markedness hypothesis. What traditionalism does not
 predict is the high number of answers indicative of local readings in
-the \es-conditions. Resorting to the intonational markedness
-hypothesis does not help, because local readings were observed for
-accented as well as in unaccented \es-sentences. It would also remain
-unclear why intonational cues should have such differential effects on
-\as- and \es-sentences.
+the \es-conditions. Resorting to the prosodic markedness hypothesis
+does not help, because local readings were observed for accented as
+well as in unaccented \es-sentences. It would also remain unclear why
+prosodic cues should have such differential effects on \as- and
+\es-sentences.
 
@@
 
-In sum, if we are justified in asserting that the pattern in
-(\ref{bsp:observed-preferences}) reflects the true default preferences
-over candidate readings (see below for a critical discussion), then
-this cannot be explained in terms of the austere and stylized versions
-of traditionalism and grammaticalism that we have set up so far. We
-should then ask what plausible additional assumptions would enable
-either framework to accommodate the data? Again, let us look at each
-position in turn.
-
-Consider grammaticalism first. Our data quite clearly contradicts the
-notion that preferences follow logical strength. But grammaticalism
-could be supplemented by a conceptually different selection
+In sum, the present findings cannot be explained in terms of the
+austere and stylized versions of traditionalism and grammaticalism
+that we have set up so far. We should then ask what plausible
+additional assumptions would enable either framework to accommodate
+the data? Again, let us look at each position in turn.
+
+Consider grammaticalism first. Our data contradicts the notion that
+preferences follow logical strength. But grammaticalism could be
+supplemented by a conceptually different selection
 criterion. Selecting readings in terms of how well they answer the
@@
 Traditionalism, on the other hand, has to explain the possibility of
-local readings of intonationally unmarked \es-sentences, and, perhaps,
+local readings of prosodically unmarked \es-sentences, and, perhaps,
 also the large number of local readings in accented \es-sentences
@@
 traditionalist framework is difficult, if possible at all. A common
-approach is to explain putative evidence for local readings away as
-the result of some other phenomenon, such as typicality or contrast
-\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi,Tielvan-Tiel2014:Quantity-Matter}.
+approach is to account for local readings as the result of some other
+phenomenon, such as typicality or contrast
+\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter}.
 Since this ties into a critical reflection on our design, we will
@@
 \citet{Tielvan-Tiel2012:Embedded-Scalar} and
-\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue that the
+\citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue that the
 distribution of responses to \as-sentences found by
@@
 differences in how \emph{typical} the presented pictures were for an
-\as-sentence. Notice that this does not help in the present situation
+\as-sentence. Notice that this does not apply in the present situation
 where the task is to explain away the local readings of \es-sentences,
@@
 they have not yet seen. On intuitive grounds, we take either extension
-to be far-fetched and implausible. But even if this line of
-explanation can be plausibly extended to incrementally revealed
-picture verification, it would still be unclear why typicality-effects
-should show so strongly in categorical truth-value judgements, and why
-there is such a stark contrast between \as- and \es-sentences. For
-these reasons, we put typicality-based explanations of local readings
-of \es-sentences aside.
+to be implausible. But even if this line of explanation can be
+plausibly extended to incrementally revealed picture verification, it
+would still be unclear why typicality-effects should show so strongly
+in categorical truth-value judgements, and why there is such a stark
+contrast between \as- and \es-sentences.
 
@@
 \es-sentences is pursued by
-\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} in response to the data
+\citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} in response to the data
 reported by \citet{ChemlaSpector2010:Experimental-Ev}. The main idea
@@
 support of this idea,
-\citeauthor{GeurtsTielvan-Tiel2013:Scalar-expressi} show that the
+\citeauthor{GeurtsTielvan-Tiel2013:Embedded-Scalar} show that the
 strength of agreement to an \es-sentence on a 7-point Likert-scale
@@
 (\citeyear{ChemlaSpector2010:Experimental-Ev}) and
-\citeauthor{GeurtsTielvan-Tiel2013:Scalar-expressi}'s
-(\citeyear{GeurtsTielvan-Tiel2013:Scalar-expressi}) experiments, we
+\citeauthor{GeurtsTielvan-Tiel2013:Embedded-Scalar}'s
+(\citeyear{GeurtsTielvan-Tiel2013:Embedded-Scalar}) experiments, we
 did not record degrees of agreement with a statement. For a purely
@@
 judgment so as to contradict the semantic meaning (even when there is
-no intonational markedness to support such a reinterpretation).
+no prosodic markedness to support such a reinterpretation).
 
 On the other hand, what might make this contrast-based explanation
-more plausible is the observation that subjects found \es-sentences
-difficult. As discussed in Section~\ref{sec:results}, there were a
+more plausible is the observation that subjects had difficulties with
+\es-sentences. As discussed in Section~\ref{sec:results}, there were a
 non-negligible number of \emph{true} answer at step 2 in the
@@
 participants processed the truth-value for an \es-sentence by looking
-for a \emph{unique} element that could be singled out a description
+for a \emph{unique} element that could be singled out by a description
 like ``\dots is connected to some of its \dots'', they would need to
@@
 
-\paragraph{Critique.} There are a number of conceivable objections to
-our design and our interpretation of the presented results. We will
-consider the most pressing ones in the following.
-
-To begin with, it could be questioned whether our design reliably
-indicates the preference relations in
-(\ref{bsp:observed-preferences}). One could object that it is not
-feasible to compare results from the preference-related controls to
-results from our target conditions, because the source of different
-readings is fundamentally different. In the former we have a syntactic
-ambiguity, in the latter a set of putative pragmatic enrichments. The
-former is a case of perceived ambiguity (some of our subjects reported
-this), the latter arguably is not
-\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
-if the distribution of responses is indicative of the known preference
-patterns in preference-related controls, this would not necessarily
-mean that the distribution of responses in target conditions is
-indicative of preference relations. Although we cannot rule out that
-the incremental verification task detects preferences among multiple
-readings only for some sources of variability in readings and not
-others, it is by no means clear why this should be so. The burden of
-argument is on the sceptic. But even if we assume that the incremental
-verification task is incapable of reliably indicating preferences
-among candidate pragmatic enrichments of the relevant kind, then it
-should at least be able to indicate availability of readings. So if we
-deny the observed response patterns the power to indicate preference,
-what should the information about availability of readings be that we
-may safely infer from it? It should be that local readings are
-available in \es-sentences and that global readings are unattested in
-\as- and \es-sentences. But that alone is not predicted by either
-traditionalism or grammaticalism. The former cannot explain the
-substantial number of local responses in \es-sentences, the latter
-does not explain the absence of total global responses.
-
-Another line of criticism that challenges the validity of
-(\ref{bsp:observed-preferences}) targets the Bayesian
-salience-competition model that we used to derive it. We readily admit
-that our model is highly simplistic. Several aspects are especially
-noteworthy here. Firstly, we did not distinguish different types of
-errors, and did not take into account that when errors occurred
-earlier in the sequence, later decision points could no longer be
-reached. This way the model may actually have unduly de-emphasized the
-salience of readings that can be judged later in a sequence. Another,
-more complicated model of the likelihood of answer patterns, might
-therefore have given support to different conclusions. Unfortunately,
-it is not clear how exactly such a more complex generating model
-should be set-up. Eventually, a full processing model, designed for
-data from incremental verification tasks, would be needed. We cannot
-offer such a model here, but can only the offer a first step in that
-direction. More importantly, though, the only part of
-(\ref{bsp:observed-preferences}) that might plausibly change for a
-more encompassing model along the lines sketched above is that the 3
-\emph{false} answers in the \as-conditions with neutral intonation
-might support the conclusion that the local reading is attested. But
-this hypothetical effect will certainly be no bigger than marginal,
-and so no genuinely different conclusions of theoretical relevance
-should be expected.
+% \paragraph{Critique.} There are a number of conceivable objections to
+% our design and our interpretation of the presented results. We will
+% consider the most pressing ones in the following.
+
+% To begin with, it could be questioned whether our design reliably
+% indicates the preference relations in
+% (\ref{bsp:observed-preferences}). One could object that it is not
+% feasible to compare results from the preference-related controls to
+% results from our target conditions, because the source of different
+% readings is fundamentally different. In the former we have a syntactic
+% ambiguity, in the latter a set of putative pragmatic enrichments. The
+% former is a case of perceived ambiguity (some of our subjects reported
+% this), the latter arguably is not
+% \citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
+% if the distribution of responses is indicative of the known preference
+% patterns in preference-related controls, this would not necessarily
+% mean that the distribution of responses in target conditions is
+% indicative of preference relations. Although we cannot rule out that
+% the incremental verification task detects preferences among multiple
+% readings only for some sources of variability in readings and not
+% others, it is by no means clear why this should be so. The burden of
+% argument is on the sceptic. But even if we assume that the incremental
+% verification task is incapable of reliably indicating preferences
+% among candidate pragmatic enrichments of the relevant kind, then it
+% should at least be able to indicate availability of readings. So if we
+% deny the observed response patterns the power to indicate preference,
+% what should the information about availability of readings be that we
+% may safely infer from it? It should be that local readings are
+% available in \es-sentences and that global readings are unattested in
+% \as- and \es-sentences. But that alone is not predicted by either
+% traditionalism or grammaticalism. The former cannot explain the
+% substantial number of local responses in \es-sentences, the latter
+% does not explain the absence of total global responses.
+
+% Another line of criticism that challenges the validity of
+% (\ref{bsp:observed-preferences}) targets the Bayesian
+% salience-competition model that we used to derive it. We readily admit
+% that our model is highly simplistic. Several aspects are especially
+% noteworthy here. Firstly, we did not distinguish different types of
+% errors, and did not take into account that when errors occurred
+% earlier in the sequence, later decision points could no longer be
+% reached. This way the model may actually have unduly de-emphasized the
+% salience of readings that can be judged later in a sequence. Another,
+% more complicated model of the likelihood of answer patterns, might
+% therefore have given support to different conclusions. Unfortunately,
+% it is not clear how exactly such a more complex generating model
+% should be set-up. Eventually, a full processing model, designed for
+% data from incremental verification tasks, would be needed. We cannot
+% offer such a model here, but can only the offer a first step in that
+% direction. More importantly, though, the only part of
+% (\ref{bsp:observed-preferences}) that might plausibly change for a
+% more encompassing model along the lines sketched above is that the 3
+% \emph{false} answers in the \as-conditions with neutral intonation
+% might support the conclusion that the local reading is attested. But
+% this hypothetical effect will certainly be no bigger than marginal,
+% and so no genuinely different conclusions of theoretical relevance
+% should be expected.
 
@@
 material, such as through typicality or contrast
-\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi},
+\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar},
 we employed an incremental verification task \citep{Conroy2008}, in
@@
 was manipulated. This way we were able to also explicitly test the
-intonational markedness hypothesis, which is often used to supplement
+prosodic markedness hypothesis, which is often used to supplement
 traditionalism. Additionally, we included preference-related control
@@
 the preference-related control conditions, we inferred a posteriori
-likely values of the latent cognitive parameters.
+likely values of the latent model parameters.
 
@@
 account for high numbers of responses indicating local readings even
-for intonationally unmarked \es-sentences. Grammaticalism, insofar as
+for prosodically unmarked \es-sentences. Grammaticalism, insofar as
 it builds on disambiguation by logical strength, fails to predict the
@@
 
-On the methodologically side, we have argued that auditory
-presentation of sentence material should be mandatory if prosodic
-information is hypothesized to influence availability and preferences
-of readings. We also argued that theoretical positions must be
-formulated in such a way that they make testable predictions about
-reading preferences where different potential readings are allowed
-(contra a grammaticalism without commitment to any testable
-disambiguation principle). We should then try to obtain information
-about actual preference patterns by explicit comparison with
-structures whose preference structures are well-studied, ideally with
-some model of the data generating process for optimal data analysis.
+We have argued that auditory presentation of sentence material should
+be controlled for if prosodic information is hypothesized to influence
+availability and preferences of readings. We also argued that
+theoretical positions must be formulated in such a way that they make
+testable predictions about reading preferences where different
+potential readings are allowed (contra a grammaticalism without
+commitment to any testable disambiguation principle). We should then
+try to obtain information about actual preference patterns by explicit
+comparison with structures whose preference structures are
+well-studied, ideally with some model of the data generating process
+for optimal data analysis.
 
@@
   for each of the single regions in
-    the preference-related fillers. Regions 5 and 7 correspond to the
+    the preference-related controls. Regions 5 and 7 correspond to the
     nouns preceding the boundaries.}  
@@
   \caption{Durational values in ms for each of the single regions in
-    the preference-related fillers. Regions 5 and 7 correspond to the
+    the preference-related controls. Regions 5 and 7 correspond to the
     nouns preceding the boundaries.}  
@@
 
-%\paragraph{Preference-related fillers.} Table~\ref{tab:table-C} shows the
+%\paragraph{Preference-related controls.} Table~\ref{tab:table-C} shows the
 %durational values of each of the single words in the sentence. As is

### 2014-08-29 text/paper/paper4.tex
discussion improved

@@
 
-\noindent Given this plurality of hypothesized readings, we need to
-ask:
-\begin{enumerate}[Q1:]
-\item which of these readings are available to na\"{i}ve subjects; and
-\item which of the available readings are preferred.\fn{It may
-    ultimately be impossible to keep unavailability and strong
-    dispreference strictly apart. For our purposes this is not
-    important. Every time we speak of availability, the so-inclined
-    reader may think of non-negligible preference.}
-\end{enumerate}
-Addressing these questions empirically is relevant because they lie at
-the heart of a current debate about the nature of quantity inferences
-and the demarkation between semantics and pragmatics. The controversy
-concerns the question under which circumstances and to what extent the
-upper-bound inference from \emph{some} to \emph{some but not all} can
-occur within the compositional computation of semantic values. Two
-main theoretical positions can be distinguished here:
-\emph{traditionalism} holds in particular that local readings should
-not occur frequently unless marked by special intonation;
-\emph{grammaticalism} holds that local readings are available and, at
-least under the most prominent of selection principles for candidate
-readings, even preferred (see Section~\ref{sec:grammaticalism}). To
-distinguish between these opposing positions, it is necessary to
-assess the availability and relative preference of readings for \as-
-and \es-sentences under conditions that control for prosodic
-markedness.
+\noindent Given this plurality of hypothesized readings, the question
+arises:
+
+\begin{exe}
+\ex How salient or preferred are these theoretically conceivable
+  readings compared to each other (if they are detectable by empirical
+  means at all)?  
+\end{exe}
+
+\noindent Addressing this question empirically is relevant because it
+lies at the heart of a current debate about the nature of quantity
+inferences and the demarkation between semantics and pragmatics. The
+controversy is usually seen as one between two main competing
+theoretical positions. \emph{Traditionalism} holds in particular that
+local readings should not occur frequently unless marked by special
+intonation. \emph{Grammaticalism} holds that local readings are
+unproblematically available and, at least under the most prominent of
+selection principles for candidate readings, even at least as salient
+as the literal reading (see Section~\ref{sec:grammaticalism}). To
+distinguish between these opposing positions, it is therefore
+necessary to assess the empirical observability and relative
+preference of readings for \as- and \es-sentences under conditions
+that control for prosodic markedness.
 
@@
 \citet{CliftonDube2010:Embedded-Implic} and
-\citet{ChemlaSpector2010:Experimental-Ev}. Unfortunately, these
+\citet{ChemlaSpector2010:Experimental-Ev} \citep[c.f.][for related
+discussion]{BenzGotzner2014:Embedded-implic}. Unfortunately, these
 studies do not provide conclusive evidence about the availability and
@@
 \as-conditions, but 19.3\% / 17.6\% in the neutral / accented
-\es-conditions respectively. A look at the right-hand side of
+\es-conditions respectively. A look at the left-hand side of
 Table~\ref{tab:count_data_CC} reveals that there is some systematicity
@@
 position too late. There is one notable exception, though. A
-substantial number of \emph{true} responses where given at the second
+substantial number of \emph{true} responses were given at the second
 position of \es-sequences (9.7\% / 8.8\%) which is shown in
@@
 
-If we compare (\ref{bsp:observed-preferences}) with
+\noindent If we compare (\ref{bsp:observed-preferences}) with
 Table~\ref{tab:predictions}, we quickly see that these findings are
-not predicted by either traditionalism or
-grammaticalism. We address each position separately in the following.
+not predicted by either traditionalism or grammaticalism. We address
+each position separately in the following.
 
@@
 readings of \as-sentences are the least preferred, contrary to
-(\ref{bsp:observed-preferences}). Again, we need to bare the caveat of
+(\ref{bsp:observed-preferences}). Again, we need to bear the caveat of
 Section~\ref{sec:grammaticalism} in mind that we are only evaluating

### 2014-09-01 text/paper/paper4.tex
K2 alternative explanation modern traditionalism

@@
 ``embedded'' cases, where the scalar item \emph{some} occurs in the
-scope of other logical operators. This paper deals with to such cases.
+scope of other logical operators. This paper deals with two such cases.
 In \as-sentences (mnemonic for \textit{all \dots some \dots}) as in
@@
 
-% Section~\ref{sec:get-know-your} will discuss these readings
-% in more detail, showing that all three readings of each sentence are
-% distinct but logically dependent on each other in interesting ways.
-
-\noindent Given this plurality of hypothesized readings, the question
-arises:
-
-\begin{exe}
-\ex How salient or preferred are these theoretically conceivable
-  readings compared to each other (if they are detectable by empirical
-  means at all)?  
-\end{exe}
-
-\noindent Addressing this question empirically is relevant because it
+Given this plurality of hypothesized readings, the question arises:
+how salient or preferred are these theoretically conceivable readings
+compared to each other (if they are detectable by empirical means at
+all)?  Addressing this question empirically is relevant because it
 lies at the heart of a current debate about the nature of quantity
@@
 distinguish between these opposing positions, it is therefore
-necessary to assess the empirical observability and relative
-preference of readings for \as- and \es-sentences under conditions
-that control for prosodic markedness.
+necessary to assess the relative salience of readings for \as- and
+\es-sentences under conditions that control for prosodic markedness.
 
@@
 (\ref{bsp:AE}) and (\ref{bsp:GE})
-\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. Unfortunately,
+\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,BenzGotzner2014:Embedded-implic}. Unfortunately,
 results from these studies do not provide uncontroversial
 evidence. This is due to several reasons. Firstly, previous studies
-have only accumulated limited evidence pertaining to the preference
-relations between candidate readings of both types of
-sentences. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
+have only accumulated limited evidence pertaining to the relative
+salience of candidate readings of both types of sentences. Secondly,
+as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
 \citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue, the alleged
@@
 importantly, previous studies presented target sentences
-visually. However, traditionalists admit to the availability of local
-readings as long as the utterance is prosodically marked
+visually. However, traditionalists acknowledge the availability of
+local readings for prosodically marked utterances
 \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
@@
 will address this extant position as the \emph{prosodic markedness
-  hypothesis}. If intonation plays a role, it is vital to present
-target sentences auditorily, and to control for effects of ``silent
-prosody'' that subjects may apply when reading a sentence
-\citep[see][]{Bader98,Fodor98}.
+  hypothesis} and argue that, if intonation is hypothesized to play a
+central role, it is vital to present target sentences auditorily, and
+to control for effects of ``silent prosody'' that subjects may apply
+when reading a sentence \citep[see][]{Bader98,Fodor98}.
 
@@
 data that is both more clearly indicative of the reading that subjects
-assumed and mor independent of any potential pictorial confounds, such
+assumed and more independent of any potential pictorial confounds, such
 as the mentioned typicality effects. Moreover, this method also gives
@@
 
-% The data obtained by this method is problematic for both
-% traditionalism and grammaticalism. Contrary to the predictions of
-% traditionalism, we observed many answers indicative of local readings
-% of \es-sentences, irrespective of intonational markedness. But also
-% grammaticalism is incongruent with the observed pattern in our
-% data. Backed up by the strongest meaning hypothesis
-% \citep{DalrympleKanazawa1998:Reciprocal-Expr}, grammaticalism predicts
-% local readings to be the preferred readings, but we found no evidence
-% for that. More strongly even, the preference order among putative
-% readings suggested by our data cannot even in principle be explained
-% by comparisons of logical strength among putative readings. In sum,
-% our data sheds doubt on both traditionalism and grammaticalism in
-% their currently most common forms. We conclude the paper by some
-% speculation about how either position might be amended in the light of
-% our data.
+The data obtained by this method is \emph{prima facie} problematic for
+both traditionalism and grammaticalism. Contrary to the predictions of
+traditionalism, we observed many answers indicative of local readings
+of \es-sentences, irrespective of intonational markedness. But also
+grammaticalism is incongruent with the observed pattern in our
+data. Backed up by the strongest meaning hypothesis
+\citep{DalrympleKanazawa1998:Reciprocal-Expr} as a disambiguation
+criterion \citep[as suggested by][]{ChierchiaFox2008:The-Grammatical},
+grammaticalism predicts local readings to be the preferred readings,
+but we found no evidence for that. More strongly even, the preference
+order among putative readings suggested by our data cannot even in
+principle be explained by comparisons of logical strength among
+putative readings. In sum, our data sheds doubt on both traditionalism
+and grammaticalism in their currently most common forms. We conclude
+the paper by some speculation about how either position might be
+amended in the light of our data.
 
@@
 
-Finally, we need to control for ``silent prosody.'' A growing number
-of evidence suggests that numerous factors might influence accent
-placement and prosodic phrasing even while reading, amongst them
-default accentuation, constituent length, rhythmic phenomena, and
-individual variation
-\citep[e.g.][]{Augurzky08,Bader98,Fodor98,Fodor02,Kentner12,
-  Steinhauer01}. If we adopt the prosodic markedness hypothesis
-described in Section~\ref{sec:inton-mark-hypoth}, as many
-traditionalists do, we predict that the availability of a local
-reading hinges on the realization of contrastive stress on the scalar
-item
+Finally, we need to control for ``silent prosody.'' Several studies
+suggest that numerous factors might influence accent placement and
+prosodic phrasing even while reading, amongst them default
+accentuation, constituent length, rhythmic phenomena, and individual
+variation
+\citep[e.g.][]{Bader98,Fodor98,Steinhauer01,Fodor02,Augurzky08,BreenWatson2011:Intonational-ph,Kentner12}. If
+we adopt the prosodic markedness hypothesis described in
+Section~\ref{sec:inton-mark-hypoth}, as many traditionalists do, we
+predict that the availability of a local reading hinges on the
+realization of contrastive stress on the scalar item
 \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
@@
 The number of responses that fell out of our classification scheme
-differs substantially between \as- and \es-conditions. There are
-7.0\% / 4.4\% unclassifiable judgements in the neutral / accented
+differs substantially between \as- and \es-conditions. There are 7.0\%
+/ 4.4\% unclassifiable judgements in the neutral / accented
 \as-conditions, but 19.3\% / 17.6\% in the neutral / accented
@@
 in 'error' answers. Most answers that we classified as 'errors' have a
-plausible explanation: random errors, a handful of mistakes
-resulting from confusing buttons for \emph{true} and \emph{false} and
-a few 'spill-over errors' where participants gave responses one
-position too late. There is one notable exception, though. A
-substantial number of \emph{true} responses were given at the second
-position of \es-sequences (9.7\% / 8.8\%) which is shown in
+plausible explanation: random errors, a handful of mistakes resulting
+from confusing buttons for \emph{true} and \emph{false} and a few
+'spill-over errors' where participants gave responses one position too
+late. There is one notable exception, though. A substantial number of
+\emph{true} responses were given at the second position of
+\es-sequences (9.7\% / 8.8\%) which is shown in
 Figure~\ref{fig:exseqES2}. Although this position in the sequence is
@@
 was a monotonic \emph{at least one}, without pragmatic enrichment of
-\emph{some}.\fn{If \emph{some} is pragmatically strengthened under the
-  scope of \emph{at least one}, we would expect \emph{true} judgements
-  at position 3. Although exactly 3 \emph{true} answers occurred there
-  for each neutral and accented \es-conditions, the main point to
-  notice is that this misreading of the non-monotonic quantifier does
-  not explain \emph{true} judgements at position 5. These are
-  therefore still indicative of local readings.} 16 out of the total
-21 answers in this category come from 5 subjects, while the remaining
-5 were single answers by 5 different subjects.
+\emph{some}. 16 out of the total 21 answers in this category come from
+5 subjects, while the remaining 5 were single answers by 5 different
+subjects.
 % subjects 1, 9, 12, 21, 84
 This suggests that at least for some subjects non-monotonic
-quantifiers were problematic. (We will come back to this point later.)
+quantifiers were problematic. (We will come back to this intriguing
+observation later in Section~\ref{sec:discussion-1}, where we suggest
+that a non-monotonic reading of \emph{exactly one} might also explain
+the high number of \emph{true} answers in step 5 of the
+\es-conditions.)
 
@@
 global readings. More concretely, our analyses suggest the following
-preference/availability patterns (bracketed readings are unattested,
-in the sense that they are either unavailable or heavily
-dispreferred):
+preference patterns (bracketed readings are not supported by our data
+and the previous analyses):
 
@@
 does not help, because local readings were observed for accented as
-well as in unaccented \es-sentences. It would also remain unclear why
+well as for unaccented \es-sentences. It would also remain unclear why
 prosodic cues should have such differential effects on \as- and
@@
 Section~\ref{sec:grammaticalism} in mind that we are only evaluating
-grammaticalism with respect to a particular selection criterion
+grammaticalism with respect to a particular disambiguation criterion
 here. The verdict, however, seems to be clear. If
 (\ref{bsp:observed-preferences}) is the actual preference order over
-readings, then meaning selection in terms of logical strength is
+readings, then meaning disambiguation in terms of logical strength is
 generally on the wrong track, because no account that merely looks at
@@
 also the large number of local readings in accented \es-sentences
-compared to that in accented \as-sentences. To do so within a
-traditionalist framework is difficult, if possible at all. A common
-approach is to account for local readings as the result of some other
-phenomenon, such as typicality or contrast
+compared to the much lower number in accented \as-sentences. To do so
+within a strict traditionalist framework seems difficult. A first
+options might be to account for local readings as the result of some
+other phenomenon, such as typicality or contrast
 \citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter}.
@@
 unlikely to explain the observed high number of local answers in
-\es-sentences, but that the additional assumption of ``shallow
-interpretation'' of the non-monotonic quantifiers might save
-traditionalism.
+\es-sentences, but that a ``modern traditionalist'' explanation of the
+answer pattern might be available if we allow for the possibility that
+\emph{exactly one} gets an unexpected ``referential interpretation.''
 
@@
 for which no alternative explanation in terms of typicality has been
-offered. Moreover, to apply typicality-explanations to the incremental
-verification task, one would have to reason about the typicality of
-parts of pictures or to figure in subjects' expectations of pictorial
-typicality given their uncertainty about parts of the picture that
-they have not yet seen. On intuitive grounds, we take either extension
-to be implausible. But even if this line of explanation can be
-plausibly extended to incrementally revealed picture verification, it
-would still be unclear why typicality-effects should show so strongly
-in categorical truth-value judgements, and why there is such a stark
-contrast between \as- and \es-sentences.
+offered. Moreover, to apply typicality-based explanations to the
+incremental verification task, one would have to reason about the
+typicality of parts of pictures or to figure in subjects' expectations
+of pictorial typicality given their uncertainty about parts of the
+picture that they have not yet seen. On intuitive grounds, we take
+either extension to be implausible. But even if this line of
+explanation can be plausibly extended to incrementally revealed
+picture verification, it would still be unclear why typicality-effects
+should show so strongly in categorical truth-value judgements, and why
+there is such a stark contrast between \as- and \es-sentences.
 
@@
 
-On the other hand, what might make this contrast-based explanation
-more plausible is the observation that subjects had difficulties with
-\es-sentences. As discussed in Section~\ref{sec:results}, there were a
-non-negligible number of \emph{true} answer at step 2 in the
-\es-sequence. This can be explained on the assumption that
-participants read the non-monotonic quantifier \emph{exactly one} as a
-monotonic quantifier \emph{at least one}. Similar ``shallow
-interpretation'' of \emph{exactly one} would explain the high number
-of local answers for \es-sentences (and for \es-sentence alone). If
-participants processed the truth-value for an \es-sentence by looking
-for a \emph{unique} element that could be singled out by a description
-like ``\dots is connected to some of its \dots'', they would need to
-unravel the \es-sequence up to the last picture where the relevant
-visual contrast is stronger. A ``shallow interpretation''-theory also
-sidesteps the puzzle why answers are given that are incompatible with
-the proper semantic meaning of \es-sentences. Together, pictorial
-contrast effects in symbiosis with a ``shallow interpretation'' of
-non-monotonic quantifiers could be an alternative explanation of
-(\ref{bsp:observed-preferences}) for traditionalism.
+On the other hand, there is a conceivable ``modern traditionalist''
+alternative explanation of the puzzling data for \es-sentences that
+would also account for the large and systematic error
+responses. Recall from Section~\ref{sec:results} and
+Table~\ref{tab:count_data_CC} on \pageref{tab:count_data_CC} that a
+surprisingly high number of \emph{true} answers was given at the
+second step of the \es-sequence. This answer does not correspond to
+any of the three candidate readings that the previous literature has
+focused on. We hypothesized in Section~\ref{sec:results} that these
+readings can be explained under the assumption that \emph{exactly one}
+gets a reading similar to \emph{there is (at least) one}, while the
+scalar item \emph{some} would just receive its semantic
+interpretation. Such a reading of \emph{exactly one}, although
+surprising, could actually be supported by some theories of numerals
+and modifiers
+\citep[e.g.][]{Geurts2006:Take-five,MartyChemla2014:Phantom-reading},
+as the outcome of an ``existential closure'' type-shifting rule in the
+sense of \citet{Partee1986:Noun-phrase-int} to the effect that
+\emph{exactly one} is mapped onto an existential reading of the form
+``there is a group with cardinality exactly one.''
+
+What happens if \emph{some} is additionally strengthened in some way
+or other under such a reading of \emph{exactly one}? If \emph{some} is
+pragmatically strengthened under the scope of \emph{at least one} in a
+pure traditionalist manner by adding the negation of a sentence type
+\emph{at least one \dots all \dots}, we would expect \emph{true}
+judgements at position 3 of the \es-sequence. Although exactly 3
+\emph{true} answers occurred there for each neutral and accented
+\es-conditions respectively, the main point to notice is that this
+construal does not explain \emph{true} judgements at position 5. These
+would therefore still seem indicative of local readings. However,
+under the hypothesized existentially closed reading of \emph{exactly
+  one}, a ``modern traditionalist'' approach that takes discourse
+effects into account \citep[][Chapter~8.4]{Geurts2010:Quantity-Implic}
+would predict the availability of a pragmatically strengthened reading
+of \es-sentences of the form: ``there is a group of cardinality exactly
+one and that group has the property that its members are connected to
+some but not all of their surrounding elements.'' This would explain
+the observed patterns in \es-conditions. Participants who read
+\emph{exactly one} as a non-monotonic quantifier would, pace
+traditionalist logic, prefer a literal interpretation and answer
+\emph{false} at step 3 unless they made a mistake. Participants who
+assumed an existentially-closed quantifier reading could, according to
+a discourse-sensitive ``modern traditionalism'', apply a literal or a
+pragmatically strengthened reading. In the former case, they would
+answer \emph{true} at step 2, in the latter case they would answer
+\emph{true} at step 5, without this being necessarily a ``local
+reading'' in the sense put forward by proponents of grammaticalism.
+
+This alternative explanation is not without problems and is not backed
+up by a full account of discourse-based pragmatic reasoning. In
+conclusion, then, it appears that our data provides interesting
+challenges to both traditionalism and grammaticalism.
 

### 2014-09-04 text/paper/paper4.tex
Fabian changes reworked conclusion

@@
   control prosodic markedness of the scalar item. Moreover, our
-  experimental sheds light on the relative preferences or salience of
+  experiment sheds light on the relative preferences or salience of
   candidate readings. The presented data turns out to be problematic
@@
 (\ref{bsp:Plain-SI-Implicature}) is a pragmatic inference, a so-called
-\emph{quantity implicature}, derived by an abductive inference as the
+\emph{quantity implicature}, derived by an abductive inference to the
 best explanation of why informed, knowledgable and cooperative
@@
 ``embedded'' cases, where the scalar item \emph{some} occurs in the
-scope of other logical operators. This paper deals with two such cases.
-In \as-sentences (mnemonic for \textit{all \dots some \dots}) as in
-(\ref{bsp:AE}) the scalar item \emph{some} is embedded under universal
-quantifier \emph{all}. In \es-sentences (mnemonic for \textit{exactly
-  one \dots some \dots}) like (\ref{bsp:GE}) \emph{some} takes scope
-under the non-monotonic quantifier \emph{exactly one}.  According to
-current pragmatic theory, there are at least three relevant candidate
-readings for \as- and \es-sentences: (i) a \emph{literal reading} like
-in (\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where \emph{some}
-has only its literal meaning; (ii) a \emph{global reading} like in
-(\ref{bsp:AE-Global}) and (\ref{bsp:GE-Global}) where the meaning of
-(\ref{bsp:AE}) is enriched and (\ref{bsp:GE}) with the negation of the
-corresponding sentences (\ref{bsp:AE-Alternative}) and
-(\ref{bsp:GE-Alternative}) respectively; and also (iii) a \emph{local
-  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
-\emph{some} is interpreted as \emph{some but not all} in the scope of
-the embedding quantifier.
+scope of other logical operators. This paper deals with two such
+cases.  In \as-sentences (mnemonic for \textit{all \dots some \dots})
+as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded the under
+universal quantifier \emph{all}. In \es-sentences (mnemonic for
+\textit{exactly one \dots some \dots}) like (\ref{bsp:GE}) \emph{some}
+takes scope under the non-monotonic quantifier \emph{exactly one}.
+According to current pragmatic theory, there are at least three
+relevant candidate readings for \as- and \es-sentences: (i) a
+\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
+(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
+(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
+(\ref{bsp:GE-Global}) where the meaning of (\ref{bsp:AE}) and
+(\ref{bsp:GE}) is enriched with the negation of the corresponding
+sentences (\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative})
+respectively; and also (iii) a \emph{local reading} like in
+(\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where \emph{some} is
+interpreted as \emph{some but not all} in the scope of the embedding
+quantifier.
 
@@
 controversy is usually seen as one between two main competing
-theoretical positions. \emph{Traditionalism} holds in particular that
-local readings should not occur frequently unless marked by special
-intonation. \emph{Grammaticalism} holds that local readings are
-unproblematically available and, at least under the most prominent of
-selection principles for candidate readings, even at least as salient
-as the literal reading (see Section~\ref{sec:grammaticalism}). To
-distinguish between these opposing positions, it is therefore
-necessary to assess the relative salience of readings for \as- and
-\es-sentences under conditions that control for prosodic markedness.
+theoretical positions. \emph{Traditionalism} holds, in particular,
+that local readings should not occur frequently unless marked by
+special intonation. \emph{Grammaticalism} holds that local readings
+are unproblematically available and, at least under the most prominent
+of selection principles for candidate readings, even at least as
+salient as the literal reading (see
+Section~\ref{sec:grammaticalism}). To distinguish between these
+opposing positions, it is therefore necessary to assess the relative
+salience of readings for \as- and \es-sentences under conditions that
+control for prosodic markedness.
 
@@
 suggested by studies of \citet{CliftonDube2010:Embedded-Implic} and
-\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounds of
-what van Tiel and Geurts call \emph{typicality effects} (see
+\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounded
+with what van Tiel and Geurts call \emph{typicality effects} (see
 Section~\ref{sec:previous-studies} for discussion). Finally, and most
@@
 grammaticalism is incongruent with the observed pattern in our
-data. Backed up by the strongest meaning hypothesis
+data. Backed up by the \emph{strongest meaning hypothesis}
 \citep{DalrympleKanazawa1998:Reciprocal-Expr} as a disambiguation
@@
 principle be explained by comparisons of logical strength among
-putative readings. In sum, our data sheds doubt on both traditionalism
+putative readings. In sum, our data shed doubt on both traditionalism
 and grammaticalism in their currently most common forms. We conclude
-the paper by some speculation about how either position might be
-amended in the light of our data.
-
-The paper is structured as follows. Section~\ref{sec:get-know-your}
-elaborates on the three kinds of relevant readings for our target
+the paper by some thoughts on how either position could be amended in
+the light of our data.
+
+The remainder of the paper is structured as
+follows. Section~\ref{sec:get-know-your} elaborates on the three kinds
+of relevant readings for our target
 sentences. Section~\ref{sec:theories-predictions} works out the
@@
 where all of the students read some but not all of the papers is a
-special case of the set of situations where all of the students read
+special case of the class of situations where all of the students read
 some (and maybe all), while not all of the students read all of the
@@
 \begin{exe}
-  \ex \label{bsp:Entailments-GE}       \lit\ $\supset$ \glb\ $\color{mycol}{\subset}$ \loc 
+  \ex \label{bsp:Entailments-GE}       \loc\ $\supset$ \glb\ $\color{mycol}{\subset}$ \lit 
     % \hspace{1cm} and \hspace{1cm}  \lit\ $\not \supset$ \loc
 \end{exe}
-By definition of global readings $\glb$ entails $\lit$. This
+By definition of global readings, $\glb$ entails $\lit$. This
 entailment is asymmetric because the extra information that it is not
@@
 Traditionalism's predictions about preferences between literal and
-global readings depend on whether the auxiliary assumptions necessary
-to derive global readings by the Gricean recipe are plausibly
-met. These auxiliary assumptions include relevance of the extra
-information provided by the global reading, mutual awareness that the
-stronger alternative has been a speaker option, the speaker's
+global readings depend on whether certain auxiliary assumptions
+necessary to derive global readings by the Gricean recipe are
+plausibly met. These auxiliary assumptions include relevance of the
+extra information provided by the global reading, mutual awareness
+that the stronger alternative has been a speaker option, the speaker's
 competence about the issue, etc. Normally, traditionalist accounts
@@
 ones.\fn{We mention for clarity that although weak traditionalism does
-  not predict global readings to be preferred, it might still
-  predict an \emph{epistemically weak implicature}, similar to the
-  global reading, that the speaker is uncertain whether the stronger
+  not predict global readings to be preferred, it might still predict
+  an \emph{epistemically weak implicature}, similar to the global
+  reading, that the speaker is uncertain whether the stronger
   alternative is true. (See also the discussion in
@@
 
-As far as preferences are concerned, even unrestricted traditionalism
-would not predict that the local reading is preferred over the global
-reading. This is because the derivation of the local reading via
+As far as preferences over readings of \as-sentences are concerned,
+even unrestricted traditionalism would not predict that the local
+reading is preferred over the global reading. This is because the
+derivation of the local reading via
 (\ref{bsp:AE-Alternatives-Extended}) hinges on yet another auxiliary
 assumption, namely the availability of the alternative in
-(\ref{bsp:AE-Alternatives-Extended}), which seems much less obvious
-and therefore presumably is less readily available than the
-alternative in (\ref{bsp:AE-Alternative}). Consequently, we derive the
-following predictions about preferences for unrestricted
-traditionalism: weak unrestricted traditionalism prefers the literal
-over the global over the local reading, while strong unrestricted
-traditionalism prefers the global over the local over the literal
-reading (see also Table~\ref{tab:predictions}).
+(\ref{bsp:AE-Alternatives-Extended}), which seems, by comparing
+numbers of replacements, much less obvious and therefore presumably is
+less readily available than the alternative in
+(\ref{bsp:AE-Alternative}). Consequently, we derive the following
+predictions about preferences for unrestricted traditionalism: weak
+unrestricted traditionalism prefers the literal over the global over
+the local reading, while strong unrestricted traditionalism prefers
+the global over the local over the literal reading (see also
+Table~\ref{tab:predictions}).
 
@@
 obligatory presence of $\exh$ with variability in the set of relevant
-alternatives. Another proposal is that readings are preferred in
-relation to how well they answer the contextually given question under
+alternatives. Another proposal is that readings are the more preferred
+the better they answer the contextually given question under
 discussion
@@
 of strength-based disambiguation: fix a sentence with propositional
-content $S$ with candidate readings $C(S)$, where $C(S)$ contains $S$
+content $S$ and candidate readings $C(S)$, where $C(S)$ contains $S$
 and all readings derivable from inserting $\exh(\cdot)$ at suitable
@@
 ({\it 1. She will invite Fred or Sam or possibly both}, or {\it 2.
-  She will invite Fred or Sam but not both}). Contratry to the
-silent-prosodic effects reported in the pilot experiment by Frazier,
-the authors found a significant impact of overtly realized contrastive
-accents on implicature processing: Besides a general advantage for
+  She will invite Fred or Sam but not both}).  The authors found a
+significant impact of overtly realized contrastive accents on
+implicature inferences: Besides a general advantage for
 non-strengthened readings, focal accents significantly increased the
@@
 \citet{GeurtsPouscoulous2009:Embedded-Implic} conducted a
-picture-verification task to find out whether local readings of \as-
-and \es-sentences are available.\fn{We will focus here on a subset of
-  the conditions tested by
+picture-verification task (their Experiment~3) to find out whether
+local readings of \as- and \es-sentences are available.\fn{We will
+  focus here on a subset of the conditions tested by
   \citet{GeurtsPouscoulous2009:Embedded-Implic}. Actually, these
@@
   their data, as if it had been obtained for \es-sentences.} Subjects
-were presented with pictures like those in Figure~\ref{fig:weak} and
+were presented with pictures similar to in Figure~\ref{fig:weak} and
 \ref{fig:local} (pages \pageref{fig:weak} and \pageref{fig:local})
@@
 \paragraph{Judgement Type.} We could draw a distinction between
-\emph{categorical} truth-value judgments and other more sensitive
+categorical truth-value judgments and other potentially more sensitive
 measures. The former are possibly not sensitive enough to reveal
@@
 traditionalists could reply that the putative evidence for local
-readings in non-categorical judgement tasks might reflect something
+readings in allegedly more sensitive tasks might reflect something
 other than (strongly) truth-relevant speaker-intended meaning
@@
 To resolve this issue, we would ideally like to have a design that
-elicits categorical judgements, but is still possibly sensitive enough
-to detect dispreferred readings.
-
-\paragraph{Pictorial Effects.} Choice of pictorial material can have
-an effect on obtained results \citep[see][for related
-discussion]{Raffray2010}. It is often possible to present different
-numbers of links between icons in pictures like in
+elicits categorical truth-value judgements, but is still possibly
+sensitive enough to detect dispreferred readings.
+
+\paragraph{Pictorial Effects.} It is often possible to present
+different numbers of links between icons in pictures like in
 Figures~\ref{fig:AS-distinguishing-pics}
@@
 in previous studies differed in this respect, and that might explain
-some of the differences in results.
-
-If that is so, then we cannot ascribe the effects reported by
+some of the differences in results. If that is so, then we cannot
+ascribe the effects reported by
 \citet{CliftonDube2010:Embedded-Implic} and
@@
 differences, but submit that this does not explain away the high
-acceptance of pictures like Figure \ref{fig:weak}. The latter point is
-disputed by \citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates
-that a huge chunk of variance in the responses to \as-sentences can be
-explained as typicality effects, dispensing the need to appeal to the
+acceptance of pictures like Figure \ref{fig:weak}.
+
+The latter point is disputed by
+\citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates that a huge
+chunk of variance in the responses to \as-sentences can be explained
+as typicality effects, dispensing the need to appeal to the
 distribution of different readings. In support of this idea,
@@
 typicality-based explanation does not extend to \es-sentences in an
-obvious way \citep[c.f.][for critical reflection on typicality-based
-explanations]{Cummins2014:Typicality-made}. Moreover, typicality
-itself is not a satisfactory primitive in a putative explanation of
-the use of quantifiers. Rather it is possible to explain typicality
-judgements as the outcome of Gricean speaker preferences for
-informative descriptions, just like those that rationalize quantity
-implicatures \citep{Franke2014:Typical-use-of-}. For these reasons, we
-believe that typicality and other pictorial effects need to be taken
-seriously in the experimental design, but do not give a satisfactory
-account of the observed variation all by themselves.
+obvious way. Moreover, typicality itself is not a satisfactory
+primitive in a putative explanation of the use of quantifiers, but
+rather something that needs explanation itself \citep[c.f.][for
+critical reflection on typicality-based
+explanations]{Cummins2014:Typicality-made}. Indeed, it is possible to
+explain typicality judgements as the outcome of Gricean speaker
+preferences for informative descriptions, just like those that
+rationalize quantity implicatures \citep{Franke2014:Typical-use-of-}.
+For these reasons, we believe that typicality and other pictorial
+effects need to be taken seriously in the experimental design, but do
+not necessarily give a satisfactory account of the observed variation
+all by themselves.
 
@@
 readings. In addition, we wanted to minimize potential picture
-typicality effects. To achieve this, we used an \mymark{incremental
-  verification task} (\acro{ivt}), which is a modified version of
-picture verification \citep[see][]{Conroy2008}. The general idea is
-that subjects are requested to judge sentence material with respect to
-pictures that do not necessarily contain all the information relevant
-for judging a certain reading true or false. In that case,
-participants can demand that more information be
-revealed. Participants are instructed to make a truth-value judgment
-as soon as they are able to. When they do, the trial ends.
+typicality effects. To achieve this (see
+Section~\ref{sec:discussion-1} for discussion), we used an
+\mymark{incremental verification task} (\acro{ivt}), which is a
+modified version of picture verification
+\citep[see][]{Conroy2008}. The general idea is that subjects are
+requested to judge sentence material with respect to pictures that do
+not necessarily contain all the information relevant for judging a
+certain reading true or false. In that case, participants can demand
+that more information be revealed. Participants are instructed to make
+a truth-value judgment as soon as they are able to. When they do, the
+trial ends.
 
@@
 interspersed between these positions served as
-spillover-pictures. These were used in order to control for
-potentially delayed judgments and they additionally served as
-distractor items. Prior to step 3 there is not enough information to
-judge any candiate reading true or false. The situation at step 3 in
+spillover-pictures. These were used in order to counter potentially
+delayed judgments and they additionally served as distractor
+items. Prior to step 3 there is not enough information to judge any
+candiate reading true or false. The situation at step 3 in
 Figure~\ref{fig:exseqAS3} is true under a literal reading, while the
@@
 
-\noindent Out sentences were read by a phonetically trained female
+\noindent Our sentences were read by a phonetically trained female
 native speaker of German familiar with the concept of contrastive
@@
   genau eine(r) der} ("exactly one of these"), as well as the head
-noun which denoted different icons, such as letters or bells. Subjects
+noun which denoted different icons, such as letters or bells. Subject \acros{DP}
 were followed by an auxiliary, and a \acro{pp} containing {\it
@@
 \acros{pp} consisted in a coordination of two nouns denoting
-geometrical objects, whereas the second \acro{pp} denoted icons. In
-contrast to these sentences, the unambiguous sentences contained only
-one \acro{pp} with a conjunction the first part of which was modified
-by a relative clause.
+geometrical objects, whereas the nouns in the second \acro{pp} denoted
+icons. In contrast to these sentences, the unambiguous sentences
+contained only one \acro{pp} with a conjunction the first part of
+which was modified by a relative clause.
 
@@
 
-Figure~\ref{fig:duration_targets} shows the durational values 
-for each of the single regions in the sentence. 
-Though descriptively small, the duration of accented determiners 
-was significantly increased as opposed to their non-accented counterparts 
-(effects on
-the determiner: \acro{Quantifier}: \emph{F}=31.4; \emph{p}<.001;
-\acro{Prosody}: \emph{F}=23.8; \emph{p}<.001).
-
-A list of the statistical results of each sentential region is provided in 
-Appendix~\ref{sec:audit-sent-mater} (F0 values: Table~\ref{tab:table-B};
-durational values: Table~\ref{tab:table-A}).
+Figure~\ref{fig:duration_targets} shows the durational values for each
+of the single regions in the sentence.  Though descriptively small,
+the duration of accented determiners was significantly increased as
+opposed to their non-accented counterparts (effects on the determiner:
+\acro{Quantifier}: \emph{F}=31.4; \emph{p}<.001; \acro{Prosody}:
+\emph{F}=23.8; \emph{p}<.001).  A list of the statistical results of
+each sentential region is provided in
+Appendix~\ref{sec:audit-sent-mater} (F0 values:
+Table~\ref{tab:table-B}; durational values: Table~\ref{tab:table-A}).
 
@@
 of \acro{Prosody}: \emph{F}=1920.3; \emph{p}<.001; all single
-comparisons \emph{p}<.001.)
-
-A list of the statistical results of each sentential region is
-provided in Appendix~\ref{sec:audit-sent-mater} (F0 values:
-Table~\ref{tab:table-D}; durational values: Table~\ref{tab:table-C})
+comparisons \emph{p}<.001.) A list of the statistical results of each
+sentential region is provided in Appendix~\ref{sec:audit-sent-mater}
+(F0 values: Table~\ref{tab:table-D}; durational values:
+Table~\ref{tab:table-C}).
 
@@
 indicated by a \emph{false} response. It appears that subjects read
-\es-sentences as if the non-monotonic quantifier \emph{exactly one}
+\es-sentences as if the upward-monotonic quantifier \emph{exactly one}
 was a monotonic \emph{at least one}, without pragmatic enrichment of
@@
 terms of AICs, starting from the saturated model. The best model takes
-main factors \textsc{Response} and \textsc{Condition} into account, as
-well as the interaction term \textsc{Response:Condition} ($\chi^2 =
+main factors \textsc{Reading} and \textsc{Condition} into account, as
+well as the interaction term \textsc{Reading:Condition} ($\chi^2 =
 17.19$, $df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$
 of the saturated model)). Crucially, factors \textsc{Trial} and
-\textsc{Accent} are spurious in the best model. This suggests that
+\textsc{Accent} were dropped in the best model. This suggests that
 response patterns only depend on the type of the sentence, but that
@@
 order to test whether there is support for the postulation of local
-readings, we therefore compared the previous ``best'' predictor to a
+readings, we therefore compared the previous ``best'' model to a
 model that only differs from the former in that it subsumes the level
@@
 sequences. Starting search from the saturated model along a gradient
-of decreasing AICs, we find that the ``best'' predictor relies on main
+of decreasing AICs, we find that the ``best'' model relies on main
 effects of \textsc{Reading}, \textsc{Accent} and \textsc{Condition}
-and two two-way interactions \textsc{Response:Condition} and
-\textsc{Response:Accent} ($\chi^2=18.34$, $df=42$, $p=0.99$,
+and two two-way interactions \textsc{Reading:Condition} and
+\textsc{Reading:Accent} ($\chi^2=18.34$, $df=42$, $p=0.99$,
 $AIC=256.63$ (compared to $AIC=322.3$ of the saturated model)). Factor
-\textsc{Trial} again turned out to be spurious, suggesting that
+\textsc{Trial} was dropped from the best model, suggesting that
 answer patterns are stable over the duration of the experiment. Unlike
@@
 
-To add potential effects of sequentiality, consider bias factor $q
-\in [0;1]$. This bias is a global parameter held constant over all
+To add potential effects of sequentiality, consider bias factor $q \in
+[0;1]$. This bias is a global parameter held constant over all
 conditions, because we think of it as a general tendency to answer
 early or late in the incremental verification task. The bias factor
-captures whether there is a tendency to access readings that appear
+captures whether there is a tendency to choose readings that appear
 earlier ($q > .5$) or later ($q <.5$) in the sequence. In the
@@
 
-On the other hand, there is a conceivable ``modern traditionalist''
-alternative explanation of the puzzling data for \es-sentences that
-would also account for the large and systematic error
-responses. Recall from Section~\ref{sec:results} and
-Table~\ref{tab:count_data_CC} on \pageref{tab:count_data_CC} that a
-surprisingly high number of \emph{true} answers was given at the
-second step of the \es-sequence. This answer does not correspond to
-any of the three candidate readings that the previous literature has
-focused on. We hypothesized in Section~\ref{sec:results} that these
-readings can be explained under the assumption that \emph{exactly one}
-gets a reading similar to \emph{there is (at least) one}, while the
-scalar item \emph{some} would just receive its semantic
-interpretation. Such a reading of \emph{exactly one}, although
-surprising, could actually be supported by some theories of numerals
-and modifiers
+On the other hand, there is a conceivable alternative explanation of
+the puzzling data for \es-sentences that would also account for the
+large and systematic error responses. Recall from
+Section~\ref{sec:results} and Table~\ref{tab:count_data_CC} on
+\pageref{tab:count_data_CC} that a surprisingly high number of
+\emph{true} answers was given at the second step of the
+\es-sequence. This answer type does not correspond to any of the three
+candidate readings that the previous literature has focused on. As
+suggested earlier, this answer type can be explained under the
+assumption that \emph{exactly one} gets a reading similar to
+\emph{there is (at least) one}, while the scalar item \emph{some}
+would just receive its semantic interpretation. Such a reading of
+\emph{exactly one}, although surprising, could actually be supported
+by some theories of numerals and modifiers
 \citep[e.g.][]{Geurts2006:Take-five,MartyChemla2014:Phantom-reading},
@@
 would therefore still seem indicative of local readings. However,
-under the hypothesized existentially closed reading of \emph{exactly
-  one}, a ``modern traditionalist'' approach that takes discourse
-effects into account \citep[][Chapter~8.4]{Geurts2010:Quantity-Implic}
-would predict the availability of a pragmatically strengthened reading
-of \es-sentences of the form: ``there is a group of cardinality exactly
-one and that group has the property that its members are connected to
-some but not all of their surrounding elements.'' This would explain
-the observed patterns in \es-conditions. Participants who read
-\emph{exactly one} as a non-monotonic quantifier would, pace
-traditionalist logic, prefer a literal interpretation and answer
-\emph{false} at step 3 unless they made a mistake. Participants who
-assumed an existentially-closed quantifier reading could, according to
-a discourse-sensitive ``modern traditionalism'', apply a literal or a
-pragmatically strengthened reading. In the former case, they would
-answer \emph{true} at step 2, in the latter case they would answer
-\emph{true} at step 5, without this being necessarily a ``local
-reading'' in the sense put forward by proponents of grammaticalism.
-
-This alternative explanation is not without problems and is not backed
-up by a full account of discourse-based pragmatic reasoning. In
-conclusion, then, it appears that our data provides interesting
+there is a slight variant of the hypothesized existentially closed
+reading of \emph{exactly one}, that would explain \emph{true}
+judgments at position 5 in an ``modern traditionalist'' manner. This
+is a reading of \emph{exactly one} as ``there is a \emph{unique} group
+with cardinality exactly one.'' Although this is admittedly only a
+vague sketch of a possible line of explanation, it is not entirely
+implausible that such a uniqueness requirement has participants look
+for a distinguished referent, which they find on position 5. But if
+the reading in question is about a unique discourse referent, we can
+explain how the predicate \emph{is connected to some if its \dots} can
+be pragmatically enriched in the desired fashion, along the lines of a
+``modern traditionalist'' account that takes discourse effects into
+account \citep[][Chapter~8.4]{Geurts2010:Quantity-Implic}. The
+listener would then conclude that the referent in question was not
+connected to all of its surrounding elements, because otherwise the
+speaker would have attributed that to the now fixed referent in
+question. This is parallel, so Geurts suggests, to the reasoning that
+an utterance of ``Smith met a woman'' implicates that \emph{the woman
+  referred to} was not Smith's mother and not that Smith didn't meet
+his mother at all. But this alternative explanation is at present only
+a tentative sketch of a possibility.
+
+In conclusion, then, it appears that our data provides interesting
 challenges to both traditionalism and grammaticalism.

### 2014-09-09 text/paper/paper4.tex

@@
     & T & 0 & 1 & \textbf{99} & 2 & \textbf{2} & 0 & 1 
-    & 99 & 8 & 5 & 5 \\
+    & 99 & 8 & 2 & 5 \\
     & F & 0 & 0 & 1 & 0 & 0 & 0 & \textbf{8} \\
@@
 global readings (e.g., a speaker competence assumption) are not
-available or only allow for epistemic weak implicatures that would
+available or only allow for epistemically weak implicatures that would
 show as responses indicative of literal readings in our task. In
@@
 within a strict traditionalist framework seems difficult. A first
-options might be to account for local readings as the result of some
-other phenomenon, such as typicality or contrast
+option might be to account for alleged local readings as the result of
+some other phenomenon, such as typicality or contrast
 \citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter}.
@@
 
-A more promising alternative explanation for local readings of
-\es-sentences is pursued by
+A more promising alternative explanation for data indicative of local
+readings of \es-sentences is pursued by
 \citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} in response to the data
@@
 large and systematic error responses. Recall from
-Section~\ref{sec:results} and Table~\ref{tab:count_data_CC} on
+Section~\ref{sec:results} and Table~\ref{tab:count_data_CC} on page
 \pageref{tab:count_data_CC} that a surprisingly high number of
@@
 \es-conditions respectively, the main point to notice is that this
-construal does not explain \emph{true} judgements at position 5. These
-would therefore still seem indicative of local readings. However,
-there is a slight variant of the hypothesized existentially closed
-reading of \emph{exactly one}, that would explain \emph{true}
-judgments at position 5 in an ``modern traditionalist'' manner. This
-is a reading of \emph{exactly one} as ``there is a \emph{unique} group
-with cardinality exactly one.'' Although this is admittedly only a
-vague sketch of a possible line of explanation, it is not entirely
-implausible that such a uniqueness requirement has participants look
-for a distinguished referent, which they find on position 5. But if
-the reading in question is about a unique discourse referent, we can
-explain how the predicate \emph{is connected to some if its \dots} can
-be pragmatically enriched in the desired fashion, along the lines of a
-``modern traditionalist'' account that takes discourse effects into
-account \citep[][Chapter~8.4]{Geurts2010:Quantity-Implic}. The
-listener would then conclude that the referent in question was not
-connected to all of its surrounding elements, because otherwise the
-speaker would have attributed that to the now fixed referent in
-question. This is parallel, so Geurts suggests, to the reasoning that
-an utterance of ``Smith met a woman'' implicates that \emph{the woman
-  referred to} was not Smith's mother and not that Smith didn't meet
-his mother at all. But this alternative explanation is at present only
-a tentative sketch of a possibility.
-
-In conclusion, then, it appears that our data provides interesting
-challenges to both traditionalism and grammaticalism.
+construal does not explain \emph{true} judgements at position 5, which
+we classified as local responses. These would therefore still seem
+indicative of local readings. However, there is a slight variant of
+the hypothesized existentially closed reading of \emph{exactly one},
+that would explain \emph{true} judgments at position 5. This is a
+reading of \emph{exactly one} as ``there is a \emph{unique} group with
+cardinality exactly one.''  Although this is admittedly only a vague
+sketch of a possible line of explanation, it is not entirely
+implausible that such a uniqueness requirement has participants, in a
+first step of evaluation, look for a distinguished referent, which
+they can find no sooner than on position 5 when the whole picture is
+unravelled. The search for uniqueness would result in a witness for
+the existential quantifier that appears to take a pragmatically
+strengthened reading of \emph{some} into account, but that is not
+necessarily a ``local reading'' in the sense of
+grammaticalism. Moreover, although not strictly required to explain
+the behavioral data, we can furthermore explain how the predicate
+\emph{is connected to some if its \dots} can be pragmatically enriched
+in the desired fashion, along the lines of a ``modern traditionalist''
+account that makes use of interpretive mechanisms originally developed
+to account for certain discourse phenomena
+\citep[][Chapter~8.4]{Geurts2010:Quantity-Implic}. The listener would
+then conclude that the referent in question was not connected to all
+of its surrounding elements, because otherwise the speaker would have
+attributed that to the now fixed referent in question. This is
+parallel, so Geurts suggests, to the reasoning that an utterance of
+``Smith met a woman'' implicates that \emph{the woman referred to} was
+not Smith's mother and not that Smith didn't meet his mother at all.
+
+To wrap up, we suggested amendements to grammaticalism and
+traditionalism that could help either position explain the data we
+observed. Whether these suggestions can be vindicated by further
+empirical research is a matter that we must leave open. It remains,
+however, that our data provides interesting challenges to both
+traditionalism and grammaticalism.
 

### 2014-09-09 text/paper/submission/cover_letter.tex
this version first submission to JoS

\documentclass[fleqn,reqno,10pt]{article}

\usepackage{applicationstyle}

\begin{document}

\thispagestyle{empty}

\begin{minipage}{7.5cm}
  The editors of\\
  Journal of Semantics
\end{minipage}\hfill
\begin{minipage}{5.3cm}
  Michael Franke \\
  Universtit\"at T\"ubingen \\
  Seminar f\"ur Sprachwissenschaft \\
  Wilhelmstra\ss e 19\\
  72072 T\"ubingen\\
  Germany  \\
  \medskip \href{mailto:mchfranke@gmail.com}{\tt
    mchfranke@gmail.com}
\end{minipage}

\vspace{0.75cm}

\hfill Emden, September 9, 2014

\vspace{0.75cm}

submission of manuscript ``Embedded Scalars, Preferred Readings \& Intonation: An
  Experimental Revisit''

\vspace{0.75cm}

Dear colleagues:

\bigskip

here is a first submission of the paper ``Embedded Scalars, Preferred
Readings \& Intonation: An Experimental Revisit'' authored by Michael
Franke, Fabian Schlotterbeck and Petra Augurzky, all from the
University of T\"ubingen.

Please note that the paper contains, next to a ``classical''
statistical analysis, also a Bayesian analysis. I mention this here
because it could easily be overlooked but it might be relevant to your
choice of reviewers.

Thank you for your efforts.

\vspace{0.75cm}

\hfill Best wishes,\hspace{2.5cm}

\medskip

\hfill \includegraphics{signature.jpg}\hspace{1.7cm}

\vspace{-.3cm}

% \hfill Michael Franke\hspace{2cm}

% \vfill
% \begin{description}
% \item[enclosed:] research accomplishments; future research; approach to
%   teaching; curriculum vitae; list of three referees
% \end{description}

\end{document}

### 2014-09-09 text/paper/submission/paper.tex
this version first submission to JoS

--- 2014-09-09 text/paper/paper4.tex
@@
-\documentclass[fleqn,reqno,10pt,draft]{article}
+\documentclass[fleqn,reqno,10pt]{article}
 
@@
 
-\usepackage{../helpers/gb4e_micha}
-\usepackage{../helpers/proofing}
-
-\usepackage{../helpers/mycommands}
+\usepackage{../../helpers/gb4e_micha}
+\usepackage{../../helpers/proofing}
+
+\usepackage{../../helpers/mycommands}
 % \usepackage{../helpers/myenvironments}
@@
   experiment sheds light on the relative preferences or salience of
-  candidate readings. The presented data turns out to be problematic
+  candidate readings. The presented data turn out to be problematic
   for both a traditional Gricean view of scalar implicature
@@
     \begin{center}
-      \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
-      \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
+      \includegraphics[scale=0.25]{../../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
+      \includegraphics[scale=0.25]{../../pictures/paper/Chemla_Spector_2010_RatingBar.png}
     \end{center}
@@
     \label{fig:CS-Results-as}
-        \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
+        \includegraphics[width=5.5cm]{../../pictures/paper/Chemla_Spector_2010_Results_AE.png}
   }
@@
     \label{fig:CS-Results-es}
-    \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
+    \includegraphics[width=5.5cm]{../../pictures/paper/Chemla_Spector_2010_Results_GE.png}
   }  
@@
 	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_1.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_1.pdf}}
 	    \label{fig:exseqAS1}
@@
 	\subfloat[][Step 2]{
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_2.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_2.pdf}}
 	    \label{fig:exseqAS2}
@@
 	\subfloat[][Step 3 (\lit true)]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_3.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_3.pdf}}
 	    \label{fig:exseqAS3}
@@
 	\subfloat[][Step 4]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_4.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_4.pdf}}
 	    \label{fig:exseqAS4}
@@
 	\subfloat[][Step 5 (\glb true)]{
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_5.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_5.pdf}}
 	    \label{fig:exseqAS5}
@@
 	\subfloat[][Step 6]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_6.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_6.pdf}}
 	    \label{fig:exseqAS6}
@@
 	\subfloat[][Step 7 (\loc false)]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_7.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_7.pdf}}
 	    \label{fig:exseqAS7}
@@
 	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_1.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ge_01_1.pdf}}
 	    \label{fig:exseqES1}
@@
 	\subfloat[][Step 2 (\glb false)]{
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_2.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ge_01_2.pdf}}
 	    \label{fig:exseqES2}
@@
 	\subfloat[][Step 3 (\lit false)]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_3.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ge_01_3.pdf}}
 	    \label{fig:exseqES3}
@@
 	\subfloat[][Step 4]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_4.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ge_01_4.pdf}}
 	    \label{fig:exseqES4}
@@
 	\subfloat[][Step 5 (\loc true)]{
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_5.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{../../pictures/ge_01_5.pdf}}
 	    \label{fig:exseqES5}
@@
 	\subfloat[][Step 2]{ 
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_2.pdf}}
+		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_2.pdf}}
 	    \label{fig:exlc2}
@@
 	\subfloat[][Step 3 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_3.pdf}}
+		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_3.pdf}}
 	    \label{fig:exlc3}
@@
 	\subfloat[][Step 4]{
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_4.pdf}}
+		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_4.pdf}}
 	    \label{fig:exlc4}
@@
 	\subfloat[][Step 5 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_5.pdf}}
+		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_5.pdf}}
 	    \label{fig:exlc5}
@@
 	\subfloat[][Step 6 (\ec false)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_6.pdf}}
+		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_6.pdf}}
 	    \label{fig:exlc6}
@@
 	\subfloat[][Step 7 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_7.pdf}}
+		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_7.pdf}}
 	    \label{fig:exlc7}
@@
 	\subfloat[][Step 2]{ 
-		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_2.pdf}}
+		\fbox{\includegraphics[width=5cm]{../../pictures/ec_01_2.pdf}}
 	    \label{fig:exec1}
@@
 	\subfloat[][Step 3 (\ec false)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_3.pdf}}
+		\fbox{\includegraphics[width=5cm]{../../pictures/ec_01_3.pdf}}
 	    \label{fig:exec2}
@@
 	\subfloat[][Step 4]{
-		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_4.pdf}}
+		\fbox{\includegraphics[width=5cm]{../../pictures/ec_01_4.pdf}}
 	    \label{fig:exec2}
@@
 	\subfloat[][Step 5 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_5.pdf}}
+		\fbox{\includegraphics[width=5cm]{../../pictures/ec_01_5.pdf}}
 	    \label{fig:exec2}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_ae.png}}
+		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/minmax_ae.png}}
 	    \label{fig:minmax_ae}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_ge.png}}
+		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/minmax_ge.png}}
 	    \label{fig:minmax_ge}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_ae.png}}
+		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/duration_ae.png}}
 	    \label{fig:duration_ae}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_ge.png}}
+		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/duration_ge.png}}
 	    \label{fig:duration_ge}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_fi.png}}
+		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/minmax_fi.png}}
 	    \label{fig:acoustics_fi}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_fi.png}}
+		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/duration_fi.png}}
 	    \label{fig:duration_fi}
@@
 
-  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-B.png}
+  \includegraphics[width=\textwidth]{../../pictures/Acoustics/Table-B.png}
 
@@
 
-  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-A.png}
+  \includegraphics[width=\textwidth]{../../pictures/Acoustics/Table-A.png}
 
@@
 
-  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-D.png}
+  \includegraphics[width=\textwidth]{../../pictures/Acoustics/Table-D.png}
 
@@
 
-  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-C.png}
+  \includegraphics[width=\textwidth]{../../pictures/Acoustics/Table-C.png}
 

### 2014-09-09 text/paper/submission/titlePage.tex
this version first submission to JoS

--- 2014-09-04 text/paper/paper4.tex
@@
-\documentclass[fleqn,reqno,10pt,draft]{article}
+\documentclass[fleqn,reqno,12pt]{article}
 
-\usepackage[natbib=true,
-            style=authoryear-comp,
-            backend=bibtex,
-            sortcites=false,
-            maxnames=2,
-            doi=false,
-            url=false]{biblatex}
+%========================================
+% Packages
+%========================================
+
+\usepackage[]{mypackages}
 \bibliography{MyRefGlobal}
-% \bibliography{paper}
+\usepackage{mycommands}
 
-\usepackage[final,            % override "draft" which means "no nothing"
-            colorlinks,       % rather than outlining them in boxes
-            linkcolor=gray,   % override truly awful color choices
-            citecolor=gray,   %   (ditto)
-            urlcolor=gray,    %   (ditto)
-            plainpages=false, % to overcome complaints with multiple
-            pdfpagelabels,    % multiple page 1-s due to preface
-            hypertexnames=false % solves warning, but interferes with
-                                % index and \autoref apparently
-            ]{hyperref}
+\usepackage{array}
+% \usepackage{authblk}
 
-\usepackage{amsmath}            % Formeln
-\usepackage{amsfonts}           % Fonts for Formulas
-\usepackage{amssymb}
-\usepackage[final]{graphicx}
-\usepackage{booktabs}
-\usepackage{enumerate}
-\usepackage{lipsum}
-\usepackage{txfonts} % for strict implication symbols
-\usepackage{soul}
-\usepackage{relsize} % provides command \relsize{+/-x} for relative
-                     % font size changes
-\usepackage[german,english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc} 
-\usepackage{subfig}
-\usepackage{xypic}
-\usepackage{url}
-\usepackage{tikz}
-\usetikzlibrary{arrows,shapes,automata,backgrounds,petri,fit,decorations.pathmorphing}
-\usepackage{refcount}
-\usepackage{xspace} % for \xspace in definition of acronyms etc.
-\usepackage{attrib} % for right-aligned references at the end of
-                    % quotes; part of Frankenstein bundle, but 
-\renewcommand\PreTrib {}   % overwrite these commands, from attrib.sty
-\renewcommand\PostTrib {}  % to suppress additional brackets around
-                           % attributions
-\usepackage{eurosym}
-\usepackage{pgfplots}
-\usepackage{todonotes}
-
-\usepackage{../helpers/gb4e_micha}
-\usepackage{../helpers/proofing}
-
-\usepackage{../helpers/mycommands}
-% \usepackage{../helpers/myenvironments}
-
-% \usepackage{geometry}
-% \linespread{1.2}
-
-%%%% Additional Macros
-
-\newcommand{\lit}{\acro{lit}}
-\newcommand{\glb}{\acro{glb}}
-\newcommand{\loc}{\acro{loc}}
-
-\newcommand{\as}{\acro{as}}
-\renewcommand{\es}{\acro{es}}
-\renewcommand{\AE}{\as}
-\newcommand{\GE}{\es}
-\newcommand{\ea}{\acro{ea}}
-
-\newcommand{\lc}{\acro{lc}}
-\newcommand{\ec}{\acro{ec}}
-\newcommand{\LC}{\lc}
-\newcommand{\EC}{\ec}
-
-\newcommand{\exh}{\ensuremath{\mathrm{Exh}}}
-\newcommand{\alt}{\ensuremath{\mathrm{Alt}}}
-
-\newcommand{\ivt}{\acro{ivt}}
-
-\renewcommand{\mymark}[1]{\textbf{#1}}
-
-\pgfplotscreateplotcyclelist{mylist}{% 
-    {solid,black},
-    {dotted,black}, 
-    {dashed,black}, 
-    {loosely dotted,gray}, 
-    {solid,black},
-    {dotted,black},
-    {dashed,black},
-    {loosely dotted}}
-
-\usetikzlibrary{calc}
-\usepackage{nicefrac}
-
-%%%% Document
+\newcommand{\ia}{\acro{ia}}
 
@@
   Experimental Revisit} 
-\author{% Fabian
-  % Schlotterbeck, Michael Franke and Petra Augurzky
+\author{Michael Franke, Fabian Schlotterbeck and Petra Augurzky
 }
+
 \date{}
@@
 \maketitle
+
+\thispagestyle{empty}
+
+\vspace*{-1cm}
+\begin{center}
+  Universtit\"at T\"ubingen \\
+  Seminar f\"ur Sprachwissenschaft \\
+  Wilhelmstra\ss e 19\\
+  72072 T\"ubingen\\
+  Germany  \\
+  \bigskip \href{mailto:mchfranke@gmail.com}{corresponding email: \tt
+    mchfranke@gmail.com}
+\end{center}
+
+ \vspace*{1cm}
 
@@
 
-\section{Introduction}
-\label{sec:introduction}
-
-The existential quantifier \emph{some} is usually assumed to receive a
-semantic interpretation similar to logical $\exists$, so that
-(\ref{bsp:Plain-SI-Target}) is literally true even when Hans solved
-all of the problems. But use of \emph{some} is also usually considered
-to invite comparison with (at least) the semantically stronger
-universal quantifier \emph{all}
-\citep[c.f.][]{Horn1972:On-the-Semantic,Gazdar1979:Pragmatics:-Imp,AtlasLevinson1981}. This
-scalar comparison can lead to an upper-bound meaning enrichment, e.g.,
-when an utterance of (\ref{bsp:Plain-SI-Target}) is taken to invite
-the inference in (\ref{bsp:Plain-SI-Implicature}).
-
-\begin{exe}
-  \ex \label{bsp:Plain-SI}
-    \begin{xlist}
-      \ex \label{bsp:Plain-SI-Target} Hans solved some of the
-        problems.
-      \ex \label{bsp:Plain-SI-Implicature} $\implicates$ Hans solved
-        some but not all of the problems.
-      \ex \label{bsp:Plain-SI-Alternative} Hans solved all of the problems.
-    \end{xlist}
-\end{exe}
-
-\noindent The classical explanation of this inference, following the
-pioneering work of \citet{Grice1975:Logic-and-Conve}, is that
-(\ref{bsp:Plain-SI-Implicature}) is a pragmatic inference, a so-called
-\emph{quantity implicature}, derived by an abductive inference to the
-best explanation of why informed, knowledgable and cooperative
-speakers would utter (\ref{bsp:Plain-SI-Target}) when they could also
-utter the semantically stronger and relevant
-(\ref{bsp:Plain-SI-Alternative}) \citep[see][for a recent
-overview]{Geurts2010:Quantity-Implic}.
-
-% If this upper-bound inference would occur often and
-% systematically enough, then it may well be that also embedded
-% occurrences of \emph{some} get enriched, in some fashion or other, to
-% contribute the enriched meaning \emph{some but not all} also under the
-% scope of other logical operators.
-% Indeed, even
-% \citeauthor{Grice1975:Logic-and-Conve} envisaged this possibility when
-% he wrote: ``It may not be impossible for what starts life, so to
-% speak, as a conversational implicature to become conventionalized''
-% \citep[p.58]{Grice1975:Logic-and-Conve}.
-
-Whereas the existence of such implicatures is rather uncontroversial
-for plain occurrences of \emph{some}, it is still an issue of debate
-whether comparable enrichments are also found in so-called
-``embedded'' cases, where the scalar item \emph{some} occurs in the
-scope of other logical operators. This paper deals with two such
-cases.  In \as-sentences (mnemonic for \textit{all \dots some \dots})
-as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded the under
-universal quantifier \emph{all}. In \es-sentences (mnemonic for
-\textit{exactly one \dots some \dots}) like (\ref{bsp:GE}) \emph{some}
-takes scope under the non-monotonic quantifier \emph{exactly one}.
-According to current pragmatic theory, there are at least three
-relevant candidate readings for \as- and \es-sentences: (i) a
-\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
-(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
-(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
-(\ref{bsp:GE-Global}) where the meaning of (\ref{bsp:AE}) and
-(\ref{bsp:GE}) is enriched with the negation of the corresponding
-sentences (\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative})
-respectively; and also (iii) a \emph{local reading} like in
-(\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where \emph{some} is
-interpreted as \emph{some but not all} in the scope of the embedding
-quantifier.
-
-\begin{exe}
-  \ex \label{bsp:AE} \mymark{All} of the students read {\mymark{some}} of the
-  papers. \hfill{(\as)}
-
-  \begin{xlist}
-  \ex \label{bsp:AE-Literal} \mymark{All} of the students read
-    {\mymark{some and maybe all}} of the papers. \hfill (\as-\lit)
-  \ex \label{bsp:AE-Global}
-    \mymark{All} of the students read \mymark{some and maybe all} 
-    and  \hfill (\as-\glb)\\
-    it's not the case that \mymark{all} of the students read \mymark{all} of the papers.
-  \ex \label{bsp:AE-Local}
-    \mymark{All} of the students read {\mymark{some  but not all}} of the
-    papers. \hfill (\as-\loc)
-  \end{xlist}
-\end{exe}
-
-\begin{exe}
-\ex  \label{bsp:GE} \mymark{Exactly one} of the students read {\mymark{some}} of the
-  papers. \hfill{(\es)}
-
-  \begin{xlist}
-  \ex \label{bsp:GE-Literal} \mymark{Exactly one} of the students read
-    {\mymark{some and maybe all}} of the papers. \hfill (\es-\lit)
-  \ex \label{bsp:GE-Global}
-    \mymark{Exactly one} of the students read \mymark{some and maybe all} 
-    and  \hfill (\es-\glb)\\
-    it's not the case that \mymark{exactly one} of the students read \mymark{all} of the papers.
-  \ex \label{bsp:GE-Local}
-    \mymark{Exactly one} of the students read {\mymark{some  but not all}} of the
-    papers. \hfill (\es-\loc)
-  \end{xlist}
-\end{exe}
-
-\begin{exe}
-\ex \label{bsp:AE-Alternative} \mymark{All} of the students read
-  {\mymark{all}} of the papers.
-
-\ex \label{bsp:GE-Alternative} \mymark{Exactly one} of the students
-  read {\mymark{all}} of the papers.
-\end{exe}
-
-Given this plurality of hypothesized readings, the question arises:
-how salient or preferred are these theoretically conceivable readings
-compared to each other (if they are detectable by empirical means at
-all)?  Addressing this question empirically is relevant because it
-lies at the heart of a current debate about the nature of quantity
-inferences and the demarkation between semantics and pragmatics. The
-controversy is usually seen as one between two main competing
-theoretical positions. \emph{Traditionalism} holds, in particular,
-that local readings should not occur frequently unless marked by
-special intonation. \emph{Grammaticalism} holds that local readings
-are unproblematically available and, at least under the most prominent
-of selection principles for candidate readings, even at least as
-salient as the literal reading (see
-Section~\ref{sec:grammaticalism}). To distinguish between these
-opposing positions, it is therefore necessary to assess the relative
-salience of readings for \as- and \es-sentences under conditions that
-control for prosodic markedness.
-
-A number of empirical studies have already examined sentences like
-(\ref{bsp:AE}) and (\ref{bsp:GE})
-\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,BenzGotzner2014:Embedded-implic}. Unfortunately,
-results from these studies do not provide uncontroversial
-evidence. This is due to several reasons. Firstly, previous studies
-have only accumulated limited evidence pertaining to the relative
-salience of candidate readings of both types of sentences. Secondly,
-as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
-\citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue, the alleged
-evidence for the availability of local readings of \as-sentences
-suggested by studies of \citet{CliftonDube2010:Embedded-Implic} and
-\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounded
-with what van Tiel and Geurts call \emph{typicality effects} (see
-Section~\ref{sec:previous-studies} for discussion). Finally, and most
-importantly, previous studies presented target sentences
-visually. However, traditionalists acknowledge the availability of
-local readings for prosodically marked utterances
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
-We
-will address this extant position as the \emph{prosodic markedness
-  hypothesis} and argue that, if intonation is hypothesized to play a
-central role, it is vital to present target sentences auditorily, and
-to control for effects of ``silent prosody'' that subjects may apply
-when reading a sentence \citep[see][]{Bader98,Fodor98}.
-
-This paper presents results form an experimental study designed to
-deal with the above mentioned problems. We presented sentence
-materials auditorily and explicitly manipulated intonational stress on
-embedded scalar items. To cater for potential pictorial confounds,
-such as from typicality, we employed an \emph{incremental verification
-  task} in which parts of a to-be-evaluated picture were hidden and
-only revealed piece-wise at the participants' request until they felt
-able to give a binary truth-value judgement
-\citep[see][]{Conroy2008}. This way we obtained categorical behavioral
-data that is both more clearly indicative of the reading that subjects
-assumed and more independent of any potential pictorial confounds, such
-as the mentioned typicality effects. Moreover, this method also gives
-information about reading preferences. We validated this by including
-control conditions with ambiguous sentences with a well-known
-preference on available readings.
-
-The data obtained by this method is \emph{prima facie} problematic for
-both traditionalism and grammaticalism. Contrary to the predictions of
-traditionalism, we observed many answers indicative of local readings
-of \es-sentences, irrespective of intonational markedness. But also
-grammaticalism is incongruent with the observed pattern in our
-data. Backed up by the \emph{strongest meaning hypothesis}
-\citep{DalrympleKanazawa1998:Reciprocal-Expr} as a disambiguation
-criterion \citep[as suggested by][]{ChierchiaFox2008:The-Grammatical},
-grammaticalism predicts local readings to be the preferred readings,
-but we found no evidence for that. More strongly even, the preference
-order among putative readings suggested by our data cannot even in
-principle be explained by comparisons of logical strength among
-putative readings. In sum, our data shed doubt on both traditionalism
-and grammaticalism in their currently most common forms. We conclude
-the paper by some thoughts on how either position could be amended in
-the light of our data.
-
-The remainder of the paper is structured as
-follows. Section~\ref{sec:get-know-your} elaborates on the three kinds
-of relevant readings for our target
-sentences. Section~\ref{sec:theories-predictions} works out the
-predictions of traditionalism and grammaticalism about availability
-and preference of readings for these
-sentences. Section~\ref{sec:previous-studies} reviews related
-experimental studies to the extent necessary to motivate our own
-approach. Section~\ref{sec:exp} eventually contributes our
-experimental design, analyses and results.
-
-\section{Get to know your readings}
-\label{sec:get-know-your}
-
-Three readings are \emph{prima facie} conceivable for the \as- and
-\es-sentences in (\ref{bsp:AE}) and (\ref{bsp:GE}). These are
-logically dependent in intricate ways.
-
-\paragraph{\as-sentences.}
-
-An \as-sentence like (\ref{bsp:AE}), repeated below, has a literal
-reading (\lit) as in (\ref{bsp:AE-Literal}), a global reading (\glb)
-as paraphrased in (\ref{bsp:AE-Global}) and a local reading (\loc) as
-in (\ref{bsp:AE-Local}).
-
-\begin{exer}{bsp:AE}
-
-  \ex \mymark{All} of the students read {\mymark{some}} of the
-  papers.
-
-  \begin{xlist}
-  \ex \mymark{All} of the students read
-    {\mymark{some and maybe all}} of the papers. \hfill (\as-\lit)
-  \ex
-    \mymark{All} of the students read \mymark{some and maybe all} 
-    and  \hfill (\as-\glb)\\
-    it's not the case that \mymark{all} of the students read \mymark{all} of the papers.
-  \ex
-    \mymark{All} of the students read {\mymark{some  but not all}} of the
-    papers. \hfill (\as-\loc)
-  \end{xlist}
-\end{exer}
-
-\noindent These readings stand in a strict entailment relation: the
-local reading asymmetrically entails the global reading, which
-asymmetrically entails the literal reading:
-\begin{exe}
-  \ex \label{bsp:Entailments-AS} \loc $\subset$ \glb $\subset$ \lit
-\end{exe}
-\glb entails \lit because, in general, global readings are defined as
-the conjunction of the literal reading and the negated
-(relevant/feasible) alternative(s) of the to-be-interpreted
-utterance. This entailment is asymmetric, because the information that
-not all of the students read all of the papers is not entailed by the
-literal reading. To see that \loc $\subset$ \glb, notice that the case
-where all of the students read some but not all of the papers is a
-special case of the class of situations where all of the students read
-some (and maybe all), while not all of the students read all of the
-papers.
-
-Given these entailment relations, there are four kinds of situations,
-the names for which we borrow from
-\citet{ChemlaSpector2010:Experimental-Ev}, that we can distinguish
-based on different truth values for our candidate readings. These are
-given in Table~\ref{fig:situations-AE}.
-%
-\begin{table}
-  \centering
-  \subfloat[][\as-sentences]{
-  \label{fig:situations-AE}
-    \begin{tabular}{lccc}
-    \toprule
-    situation    & \multicolumn{3}{c}{reading} 
-  \\ 
-  \cmidrule(r){2-4}
-     & \lit & \glb & \loc \\ \midrule
-    false   & 0 & 0 & 0 \\
-    literal & 1 & 0 & 0 \\
-    weak    & 1 & 1 & 0 \\
-    strong  & 1 & 1 & 1 \\ \bottomrule
-  \end{tabular}
-} \qquad \qquad
-  \subfloat[][\es-sentences]{
-  \label{fig:situations-GS}
-  \begin{tabular}{lccc}
-    \toprule
-    situation    & \multicolumn{3}{c}{reading} 
-  \\ 
-  \cmidrule(r){2-4}
-    & \textsc{lit} & \textsc{glb} & \textsc{loc} \\ \midrule
-    false   & 0 & 0 & 0 \\
-    literal & 1 & 0 & 0 \\
-    local   & 0 & 0 & 1 \\
-    all     & 1 & 1 & 1 \\ \bottomrule
-  \end{tabular}
-}
-\caption{Possible truth-value distributions for readings of \as- and \es-sentences}
-\label{tab:situations}
-\end{table}
-%
-Examples of these kinds of situations are shown in
-Figure~\ref{fig:AS-distinguishing-pics}, where the dots on the right
-of each diagram represent students, the dots on the left represent
-papers and an arrow from a student to a paper indicates that the
-student read the paper. % Notice that other arrangements of arrows might
-% equally well serve as examples for the various situations.
-
-\begin{figure}[t]
-  \centering
-
-\subfloat[fig:false][false]{
-  \label{fig:false-AE}
-
-\begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & false \\
-            \glb & false \\
-            \loc & false 
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=blue,->] (X-1) -> (Y-1);
-
-        \path [draw=blue,->] (X-1) -> (Y-2);
-
-        \path [draw=red,->] (X-3) -> (Y-3);
-
-        \path [draw=red,->] (X-3) -> (Y-4);
-
-      \end{tikzpicture}
-
-}
-\subfloat[fig:literal][literal]{
-  \label{fig:literal-AE}
-
-  \begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & true \\
-            \glb & false \\
-            \loc & false 
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=blue,->] (X-1) -> (Y-1);
-
-        \path [draw=blue,->] (X-1) -> (Y-2);
-
-        \path [draw=blue,->] (X-1) -> (Y-3);
-
-        \path [draw=blue,->] (X-1) -> (Y-4);
-
-        \path [draw=black,->] (X-2) -> (Y-1);
-
-        \path [draw=black,->] (X-2) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-3);
-
-        \path [draw=black,->] (X-2) -> (Y-4);
-
-        \path [draw=red,->] (X-3) -> (Y-1);
-
-        \path [draw=red,->] (X-3) -> (Y-2);
-
-        \path [draw=red,->] (X-3) -> (Y-3);
-
-        \path [draw=red,->] (X-3) -> (Y-4);
-
-      \end{tikzpicture}
-
-}
-\subfloat[fig:weak][weak]{
-  \label{fig:weak}
-
-\begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & true \\
-            \glb & true \\
-            \loc & false 
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=blue,->] (X-1) -> (Y-1);
-
-        \path [draw=blue,->] (X-1) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-1);
-
-        \path [draw=black,->] (X-2) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-3);
-
-        \path [draw=black,->] (X-2) -> (Y-4);
-
-        \path [draw=red,->] (X-3) -> (Y-3);
-
-        \path [draw=red,->] (X-3) -> (Y-4);
-
-      \end{tikzpicture}
-
-}
-\subfloat[fig:strong][strong]{
-  \label{fig:strong}
-
-\begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & true \\
-            \glb & true \\
-            \loc & true 
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=blue,->] (X-1) -> (Y-1);
-
-        \path [draw=blue,->] (X-1) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-3);
-
-        \path [draw=red,->] (X-3) -> (Y-3);
-
-        \path [draw=red,->] (X-3) -> (Y-4);
-
-      \end{tikzpicture}
-
-}
-
-\caption{Examples of distinguishing situations for \as-sentences}
-  \label{fig:AS-distinguishing-pics}
-\end{figure}
-
-\paragraph{\es-sentences.}
-
-The case for \es-sentences like (\ref{bsp:GE}) is similar but a
-little more complicated because the embedding quantifier is
-non-monotonic. Again, we consider a literal reading as in
-(\ref{bsp:GE-Literal}), repeated below, a global reading as in
-(\ref{bsp:GE-Global}) and a local reading as in (\ref{bsp:GE-Local}).
-
-\begin{exer}{bsp:GE}
-\ex \mymark{Exactly one} of the students read {\mymark{some}} of the
-  papers.
-
-  \begin{xlist}
-  \ex \mymark{Exactly one} of the students read
-    {\mymark{some and maybe all}} of the papers. \hfill (\es-\lit)
-  \ex 
-    \mymark{Exactly one} of the students read \mymark{some and maybe all} 
-    and  \hfill (\es-\glb)\\
-    it's not the case that \mymark{exactly one} of the students read \mymark{all} of the papers.
-  \ex 
-    \mymark{Exactly one} of the students read {\mymark{some  but not all}} of the
-    papers. \hfill (\es-\loc)
-  \end{xlist}
-\end{exer}
-
-\noindent Entailment relations in this case are non-linearly ordered:
-\begin{exe}
-  \ex \label{bsp:Entailments-GE}       \loc\ $\supset$ \glb\ $\color{mycol}{\subset}$ \lit 
-    % \hspace{1cm} and \hspace{1cm}  \lit\ $\not \supset$ \loc
-\end{exe}
-By definition of global readings, $\glb$ entails $\lit$. This
-entailment is asymmetric because the extra information that it is not
-the case that exactly one student read all of the papers is not
-entailed by the literal reading (\ref{bsp:GE-Literal}). However,
-unlike for \as-sentences, \loc is not stronger than \glb, but
-asymmetrically entailed by the latter. To see this, notice that the
-global reading is equivalent to:
-
-\begin{exe}
-  \exp{bsp:GE-Global} \mymark{Exactly one} of the students read \mymark{some but not
-    all} and \\
-  \mymark{everybody else} read \mymark{none} of the papers.
-\end{exe}
-
-\noindent Finally, \loc and \lit are logically independent: all
-combinations of truth-values for \loc and \lit are possible.
-
-Given these entailment relations, there are again four different
-situations corresponding to the four possible distributions of truth
-values for candidate readings. These are given in
-Table~\ref{fig:situations-GS} on page~\pageref{fig:situations-GS} and
-named following \citet{ChemlaSpector2010:Experimental-Ev}. Examples
-for each situation are given in
-Figure~\ref{fig:ES-distinguishing-pics}.
-
-\begin{figure}[t]
-  \centering
-
-\subfloat[fig:false][false]{
-  \label{fig:false-GE}
-
-  \begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & false \\
-            \glb & false \\
-            \loc & false 
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=blue,->] (X-1) -> (Y-1);
-
-        \path [draw=blue,->] (X-1) -> (Y-2);
-
-        \path [draw=red,->] (X-3) -> (Y-3);
-
-        \path [draw=red,->] (X-3) -> (Y-4);
-
-      \end{tikzpicture}
-
-}
-\subfloat[fig:literal][literal]{
-  \label{fig:literal-GE}
-
-      \begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & true \\
-            \glb & false \\
-            \loc & false 
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=black,->] (X-2) -> (Y-1);
-
-        \path [draw=black,->] (X-2) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-3);
-
-        \path [draw=black,->] (X-2) -> (Y-4);
-
-      \end{tikzpicture}
-
-}
-\subfloat[fig:local][local]{
-  \label{fig:local}
-
-            \begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & false \\
-            \glb & false \\
-            \loc & true 
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=blue,->] (X-1) -> (Y-1);
-
-        \path [draw=blue,->] (X-1) -> (Y-2);
-
-        \path [draw=blue,->] (X-1) -> (Y-3);
-
-        \path [draw=blue,->] (X-1) -> (Y-4);
-
-        \path [draw=black,->] (X-2) -> (Y-2);
-
-        \path [draw=black,->] (X-2) -> (Y-3);
-
-        \path [draw=black,->] (X-2) -> (Y-4);
-
-        \path [draw=red,->] (X-3) -> (Y-1);
-
-        \path [draw=red,->] (X-3) -> (Y-2);
-
-        \path [draw=red,->] (X-3) -> (Y-3);
-
-        \path [draw=red,->] (X-3) -> (Y-4);
-
-      \end{tikzpicture}
-
-}
-\subfloat[fig:all][all]{
-  \label{fig:all}
-
-      \begin{tikzpicture}[node distance = 1cm]
-        % Nodes
-
-        \node (X-1) {$\Large{\bullet}$};
-
-        \node (X-2) [below of = X-1] {$\Large{\bullet}$};
-
-        \node (X-3) [below of = X-2] {$\Large{\bullet}$};
-
-        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};
-
-        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};
-
-        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};
-
-        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};
-
-        % table added from here
-
-        \node (X-4) [below of = X-3, node distance = 2cm] {};
-
-        \node (table) [right of = X-4] {
-          \begin{tabular}{ll}
-            \lit & true \\
-            \glb & true \\
-            \loc & true 
-          \end{tabular}};
-
-        % Arrows
-
-        \path [draw=blue,->] (X-1) -> (Y-1);
-
-        \path [draw=blue,->] (X-1) -> (Y-2);
-
-      \end{tikzpicture}
-
-}
-
-  \caption{Examples of distinguishing situations for \es-sentences}
-  \label{fig:ES-distinguishing-pics}
-
-\end{figure}
-
-\section{Theories and predictions}
-\label{sec:theories-predictions}
-
-There are two main theoretical positions which make different
-predictions about the readings of \as- and \es-sentences
-\citep[see][for
-overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation}. We
-will refer to these as \mymark{traditionalism} and
-\mymark{grammaticalism} and treat each one in turn. Since there is
-some leeway in assessing the predictions for each approach (depending
-on which of several additional assumptions to adopt), we will
-distinguish different varieties of both of them. Predictions of all
-relevant variants are summarized in Table~\ref{tab:predictions} on
-page~\pageref{tab:predictions}.
-
-Although strictly speaking not a part of a Gricean theory of scalar
-implicature calculation, traditionalists frequently concede that local
-readings are in principle available, albeit not as a standard scalar
-implicature, but as a different pragmatic process triggered by
-prosodic markedness. We address this \emph{prosodic markedness
-  hypothesis} separately in Section~\ref{sec:inton-mark-hypoth},
-alongside a brief revision of the relevant experimental data.
-
-\subsection{Traditionalism}
-\label{sec:traditionalism}
-
-Traditionalism gets its name from its conservative stance towards
-Grice's original theory of conversational implicatures
-\citep{Grice1975:Logic-and-Conve}. Many author's have defended
-traditionalist positions in this sense. Of the more recent literature,
-we would consider as traditionalist, among others, contributions by
-\citet{Spector2006:Scalar-Implicat},
-\citet{Sauerland2004:Scalar-Implicat},
-\citet{Russell2006:Against-Grammat},
-\citet{vanRooijSchulz:ExhaustiveInterpretation},
-\citet{Geurts2010:Quantity-Implic} or
-\citet{Franke2011:Quantity-Implic}.
-
-According to Grice, conversational implicatures, of which quantity
-implicatures are a special case, are to be thought of as
-rationalizations of speaker behavior. Central in this reasoning is the
-assumption that the speaker's behavior is efficient (if not optimal)
-and goal-oriented. Usually, the assumed goal of conversation is the
-cooperative exchange of relevant information from speaker to hearer.
-
-Consequently, the \mymark{Gricean recipe}
-\citep[see][]{Geurts2010:Quantity-Implic} for deriving a simple scalar
-inference like that in (\ref{bsp:Plain-SI-Implicature}) from an
-utterance of (\ref{bsp:Plain-SI-Target}) is as follows: if the issue
-whether Hans solved only some or all of the problems is relevant, then
-a cooperative and knowledgable speaker would utter
-(\ref{bsp:Plain-SI-Alternative}) if in a position to do so; hence, one
-of the most natural explanations of why such a speaker has not uttered
-(\ref{bsp:Plain-SI-Alternative}), but only (\ref{bsp:Plain-SI-Target})
-is that she is uncertain of whether (\ref{bsp:Plain-SI-Alternative})
-is true; but on the assumption that she is knowledgeable (competent,
-opinionated, informed \dots) it follows that
-(\ref{bsp:Plain-SI-Implicature}) should in fact be true.\fn{We are
-  glossing here somewhat swiftly over the more nuanced details of the
-  derivation of implicatures targeting the speaker's epistemic state
-  \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit}. Section~\ref{sec:discussion-1}
-  will come back to this in more detail.}
-
-\begin{exer}{bsp:Plain-SI}
-  \ex 
-    \begin{xlist}
-      \ex \label{bsp:Plain-SI-Target} Hans solved \mymark{some} of the problems.
-      \ex \label{bsp:Plain-SI-Implicature} $\implicates$ Hans solved
-        \mymark{some but not all} of the problems.
-      \ex  \label{bsp:Plain-SI-Alternative}  Hans solved \mymark{all} of the problems.
-    \end{xlist}
-\end{exer}
-
-As for \as- and \es-sentences, the Gricean recipe derives global
-readings in a straightforward way. Consequently, traditionalism
-predicts that both literal and global readings are available: literal
-readings, because these form the starting point of pragmatic
-reasoning; global readings because these may be arrived at by the
-Gricean recipe.
-
-Traditionalism's predictions about preferences between literal and
-global readings depend on whether certain auxiliary assumptions
-necessary to derive global readings by the Gricean recipe are
-plausibly met. These auxiliary assumptions include relevance of the
-extra information provided by the global reading, mutual awareness
-that the stronger alternative has been a speaker option, the speaker's
-competence about the issue, etc. Normally, traditionalist accounts
-would assume that these extra assumptions are met. In that case,
-traditionalism would predict that global readings should be preferred
-over literal readings. On the other hand, if auxiliary assumptions are
-implausible, traditionalism would predict that literal readings would
-be preferred over global ones. Consequently, there are at least two
-varieties of traditionalism that, depending on which additional
-assumptions we would make, yield slightly different predictions:
-\mymark{the strong variety of traditionalism} maintains that the
-auxiliary assumptions of the Gricean recipe hold (e.g., as a matter of
-strong default) and therefore predicts that global readings are
-preferred over literal ones; \mymark{the weak variety of
-  traditionalism} holds that the auxiliary assumptions are more
-fragile and predicts that literal readings are preferred over global
-ones.\fn{We mention for clarity that although weak traditionalism does
-  not predict global readings to be preferred, it might still predict
-  an \emph{epistemically weak implicature}, similar to the global
-  reading, that the speaker is uncertain whether the stronger
-  alternative is true. (See also the discussion in
-  Section~\ref{sec:discussion-1})}
-
-Does traditionalism also predict local readings to be available? The
-answer is slightly different for \as- and the \es-sentences. For
-\es-sentences, traditionalism does not predict that a local reading is
-available, at least not as a quantity implicature by conjoining the
-literal meaning with a suitable set of negated alternatives
-\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. The
-literal and the local reading of \es-sentences are logically
-independent. But if $X$ and $Y$ are logically independent
-propositions, then there is no proposition $Z$ such that $X$ would be
-equivalent to $Y \wedge \neg Z$.
-
-On the other hand, as for \as-sentences, there is a traditionalist way
-of deriving the local reading, namely by assuming that not only
-(\ref{bsp:AE-Alternative}) is an alternative to (\ref{bsp:AE}), but
-also the sentence in (\ref{bsp:AE-Alternatives-Extended}).
-
-\begin{exer}{bsp:AE}
-  \ex \mymark{All} of the students solved \mymark{some} of the problems.
-\end{exer}
-
-\begin{exer}{bsp:AE-Alternative}
-  \ex \mymark{All} of the students solved \mymark{all} of the problems.
-\end{exer}
-
-\begin{exe}
-\ex \label{bsp:AE-Alternatives-Extended} \mymark{Some} of the students solved \mymark{all} of the problems.
-\end{exe}
-
-\noindent Clearly, if we conjoin a literal reading of (\ref{bsp:AE})
-with the negation of (\ref{bsp:AE-Alternatives-Extended}) we obtain
-exactly the local reading. (Notice that the negation of
-(\ref{bsp:AE-Alternatives-Extended}) entails the negation of
-(\ref{bsp:AE-Alternative}), so it makes no difference (not) to add it
-in this case.) Consequently, traditionalism does predict that the
-local reading of \as-sentences is available if
-(\ref{bsp:AE-Alternatives-Extended}) is an available alternative. We
-therefore introduce another distinction: \mymark{restricted
-  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
-not available and therefore predicts that the local reading for
-\as-sentences is not available; in contrast, \mymark{unrestricted
-  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
-available and so is the local reading.
-
-As far as preferences over readings of \as-sentences are concerned,
-even unrestricted traditionalism would not predict that the local
-reading is preferred over the global reading. This is because the
-derivation of the local reading via
-(\ref{bsp:AE-Alternatives-Extended}) hinges on yet another auxiliary
-assumption, namely the availability of the alternative in
-(\ref{bsp:AE-Alternatives-Extended}), which seems, by comparing
-numbers of replacements, much less obvious and therefore presumably is
-less readily available than the alternative in
-(\ref{bsp:AE-Alternative}). Consequently, we derive the following
-predictions about preferences for unrestricted traditionalism: weak
-unrestricted traditionalism prefers the literal over the global over
-the local reading, while strong unrestricted traditionalism prefers
-the global over the local over the literal reading (see also
-Table~\ref{tab:predictions}).
-
-\subsection{Grammaticalism}
-\label{sec:grammaticalism}
-
-Recently, a lot of evidence based on intuitive judgements and more
-theoretical considerations has been discussed in favor of
-\mymark{grammaticalism}
-\citep[see][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical}. % When
-% it comes to the predictions of available readings of \as- and
-% \es-sentences, grammaticalism appears like the conjunction of
-% traditionalism and conventionalism. But conceptually speaking,
-% grammaticalism goes down a road of its own.
-Grammaticalism approaches quantity implicatures by postulating a
-silent operator that can be variably applied during compositional
-computation of a sentence's truth-value
-\citep{Chierchia2006:Broaden-Your-Vi}, if necessary multiple times
-\citep{Fox2007:Free-Choice-and}. This silent operator is referred to
-as $\mathrm{O}(\cdot)$ or $\exh(\cdot)$, because it is assumed to be
-similar in effect to the meaning of particle \emph{only} or of the
-mechanism of \emph{exhaustive interpretation}
-\citep{GroenendijkStokhofThesis1984,Stechowvon-StechowZimmermann1984:Term-Answers-an,Rooijvan-RooijSchulz2013:Exhaustive-Inte,vanRooijSchulz:ExhaustiveInterpretation,Fox2007:Free-Choice-and}. For
-our purposes, it is enough to note that $\exh(\cdot)$ is a poly-typed
-function that enriches an expression $X$, which need not be a full
-proposition, based on a set $\alt(X)$ of (suitable, relevant)
-alternatives to $X$ that yields an enriched meaning of the
-form:\fn{More sophisticated formulations of exhaustive interpretation
-  have been proposed
-  \citep[e.g.][]{Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}.}
-\begin{exe}
-  \ex \label{bsp:Exh-Def} $\exh(X,\alt(X)) = X \bigwedge_{A \in
-      \alt(X)} \neg A$.
-\end{exe}
-
-As this operator can apply at various scope sites, the grammatical
-approach predicts that all three readings of \as- and \es-sentences
-are available: literal readings arise if no exhaustification operator
-is applied; global readings arise if the exhaustification operator
-takes sentence-wide scope as in (\ref{Grammar-Global}); and local
-readings arise if the exhaustification operator takes scope under the
-respective quantifiers as in (\ref{Grammar-Local}).
-
-\begin{exe}
-  \ex \label{Grammar-Global}
-    \begin{xlist}
-      \ex \label{Grammar-Global-AE} \mymark{$\exh$}(\mymark{All} of the students solved
-        \mymark{some} of the problems).
-      \ex \label{Grammar-Global-GE} \mymark{$\exh$}(\mymark{Exactly one} of the students solved
-        \mymark{some} of the problems).
-    \end{xlist}
-\end{exe}
-
-\begin{exe}
-  \ex \label{Grammar-Local}
-    \begin{xlist}
-      \ex \label{Grammar-Local-AE} \mymark{All} of the students \mymark{$\exh$}(solved
-        \mymark{some} of the problems).
-      \ex \label{Grammar-Local-GE} \mymark{Exactly one} of the
-        students \mymark{$\exh$}(solved
-        \mymark{some} of the problems).
-    \end{xlist}
-\end{exe}
-
-The grammatical approach, as described so far, is not yet a fully
-articulated theory. To make concrete predictions, it must be
-supplemented by a selection principle that determines which of the
-many readings made available by the grammar actually obtain or are
-preferred. Proponents of grammaticalism are aware of this and have
-suggested some tentative disambiguation
-strategies. \citet{Magri2011:Another-Argumen}, for example, opts for
-obligatory presence of $\exh$ with variability in the set of relevant
-alternatives. Another proposal is that readings are the more preferred
-the better they answer the contextually given question under
-discussion
-\citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. Yet
-another proposal is to select readings by comparison of logical
-strengths, as suggested by the \mymark{strongest meaning hypothesis}
-of \citet{DalrympleKanazawa1998:Reciprocal-Expr}
-\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. We
-will focus entirely on this latter selection principle, because it
-seems to be the most prominent in the literature and because it makes
-the clearest predictions.
-
-\citet{ChierchiaFox2008:The-Grammatical} discuss two concrete variants
-of strength-based disambiguation: fix a sentence with propositional
-content $S$ and candidate readings $C(S)$, where $C(S)$ contains $S$
-and all readings derivable from inserting $\exh(\cdot)$ at suitable
-scope sites;\fn{Strictly speaking, we should compare \emph{parses} of
-  sentences with $\exh(\cdot)$ at various scope sites with respect to
-  the readings that these parses give rise to
-  \citep[see][]{ChierchiaFox2008:The-Grammatical}, but we may ignore
-  this detail here for ease of exposition.} then define for $X,Y \in
-C(S)$ either
-\begin{exe}
-\ex \label{bsp:SMH-Total} 
-  $X$ is preferred to $Y$ iff $X \subset Y$ 
-  \attrib{\citep[(104)]{ChierchiaFox2008:The-Grammatical}}
-\end{exe}
-or
-\begin{exe}
-\ex \label{bsp:SMH-Partial}  $X$ is preferred to $Y$ iff $X \subset Y$
-  and $X$ and $Y$ are readings obtained from applications of
-  $\exh(\cdot)$ at exactly the same scope sites, except for
-  one. \attrib{\citep[(105)]{ChierchiaFox2008:The-Grammatical}} 
-\end{exe}
-Since the former is entailed by the latter, we will speak of
-\mymark{weak grammaticalism} and \mymark{strong grammaticalism},
-depending on whether (\ref{bsp:SMH-Total}) or (\ref{bsp:SMH-Partial})
-is used.
-
-These two varieties of grammaticalism give rise to different
-predictions about preferred readings. The preference for readings that
-weak grammaticalism predicts mirrors the entailment relations in
-(\ref{bsp:Entailments-AS}) and (\ref{bsp:Entailments-GE}): for
-\as-sentences, weak grammaticalism predicts that local readings are
-preferred over global readings which in turn are preferred over
-literal readings; for \es-sentences weak grammaticalism predicts that
-global readings are most preferred, while literal and local readings
-are not ranked with respect to preference. Strong grammaticalism, on
-the other hand, predicts that \as-sentences preferably get either a
-local or a global reading rather than a literal reading, but does not
-rank these former two with respect to each other because they differ
-in more than one application of the $\exh(\cdot)$ operator. For
-\es-sentences, then, strong grammaticalism does not predict \emph{any}
-preference relations between candidate readings at all.
-
-\medskip
-
-Taking stock, traditionalism and grammaticalism predict different
-patterns of availability and preference for \as- and
-\es-sentences. Most notably, traditionalism does not predict local
-readings for \es-sentences to be available. Grammaticalism predicts
-that all readings are available, but, given the strongest meaning
-hypothesis, also comes with a clear indication of preference: literal
-meanings are dispreferred. All predictions are summarized in
-Table~\ref{tab:predictions}.
-
-\begin{table}[t]
-  \centering
-  \begin{tabular}{lcc}
-    & \multicolumn{2}{c}{preference \& availability}
-    \\ \cmidrule(r){2-3}
-    theoretical position
-    & \as
-    & \es
-    \\ \midrule
-    traditionalism
-    \\
-    \ \ \ \ weak restricted 
-    & \lit > \glb 
-    & \lit > \glb
-    \\
-    \ \ \ \ weak unrestricted
-    & \lit > \glb > \loc 
-    & \lit > \glb
-    \\
-    \ \ \ \ strong restricted
-    & \glb > \lit 
-    & \glb > \lit
-    \\
-    \ \ \ \ strong unrestricted
-    & \glb > \loc > \lit 
-    & \glb > \lit
-    \\
-    % conventionalism
-    % \\
-    % \ \ defaultism
-    % & \loc >  \lit 
-    % & \loc >  \lit
-    % \\
-    % \ \ literalism
-    % & \lit >  \loc 
-    % & \lit >  \loc
-    % \\
-    grammaticalism
-    \\
-    \ \ \ \ weak
-    & \loc > \glb > \lit 
-    & \glb > \lit, \loc
-    \\
-    \ \ \ \ strong
-    & \glb, \loc > \lit 
-    & \glb, \loc , \lit
-    \\
-  \end{tabular}
-  \caption{Predictions of the relevant theoretical positions. Listed
-    are the predicted preference relations. If a reading is not
-    listed, it is predicted to be unavailable.}
-  \label{tab:predictions}
-\end{table}
-
-% \begin{table}[t]
-%   \centering
-%   \begin{tabular}{lcccccc}
-%     & \multicolumn{4}{c}{availability} 
-%     & \multicolumn{2}{c}{preference}
-%     \\ \cmidrule(r){2-5}  \cmidrule(r){6-7}
-%     theoretical position
-%     & \as-\glb
-%     & \as-\loc
-%     & \es-\glb
-%     & \es-\loc
-%     & \as
-%     & \es
-%     \\ \midrule
-%     traditionalism
-%     \\
-%     \ \ weak restricted 
-%     & $\checkmark$
-%     & $-$
-%     & $\checkmark$
-%     & $-$
-%     & \lit > \glb 
-%     & \lit > \glb
-%     \\
-%     \ \ weak unrestricted
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $-$
-%     & \lit > \glb > \loc 
-%     & \lit > \glb
-%     \\
-%     \ \ strong restricted
-%     & $\checkmark$
-%     & $-$
-%     & $\checkmark$
-%     & $-$
-%     & \glb > \lit 
-%     & \glb > \lit
-%     \\
-%     \ \ strong unrestricted
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $-$
-%     & \glb > \loc > \lit 
-%     & \glb > \lit
-%     \\
-%     conventionalism
-%     \\
-%     \ \ defaultism
-%     & $-$
-%     & $\checkmark$
-%     & $-$
-%     & $\checkmark$
-%     & \loc >  \lit 
-%     & \loc >  \lit
-%     \\
-%     \ \ literalism
-%     & $-$
-%     & $\checkmark$
-%     & $-$
-%     & $\checkmark$
-%     & \lit >  \loc 
-%     & \lit >  \loc
-%     \\
-%     grammaticalism
-%     \\
-%     \ \ weak
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & \loc > \glb > \lit 
-%     & \glb > \lit, \loc
-%     \\
-%     \ \ strong
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & \glb, \loc > \lit 
-%     & \glb, \loc >  \lit
-%     \\
-%   \end{tabular}
-%   \caption{Predictions of the relevant theoretical positions}
-%   \label{tab:predictions}
-% \end{table}
-
-\subsection{The Prosodic Markedness Hypothesis}
-\label{sec:inton-mark-hypoth}
-
-Although traditionalism does not of itself predict local readings to
-be available, many authors who adhere to a traditionalist position
-propose that local readings are available if the embedded scalar item
-is prosodically marked by contrastive stress
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
-is taken to be continuous with other cases where pragmatic enrichments
-can take scope under logical operators if the relevant focal accent is
-present (\ref{bsp:Stress}).
-
-\begin{exe}
-\ex \label{bsp:Stress} This chili is not \textsc{spicy}, it's \textsc{SPICY}.
-\end{exe}
-
-\noindent The \emph{prosodic markedness hypothesis}, as we will call
-it here, is then an addition to the traditionalist's explanatory
-repertoire. Under this extra assumption, local readings are a marked
-phenomenon, and not the product of the same process as run-of-the-mill
-scalar implicatures. If supplemented with the prosodic markedness
-hypothesis, traditionalists would therefore predict that local
-readings are available for \as- and \es-sentences, but only if
-prosodicly marked by contrastive stress.
-
-To date, empirical evidence for this assumption is still scarce. One
-notable exception comes from a pilot study reported in
-\citet{Frazier08}, in which participants were instructed to read
-embedded and non-embedded versions of English \as-sentences. In the
-embedded sentences (e.g. {\it All of the students wrote some of the
-  official memos}), {\it some} was either capitalized or
-non-capitalized. Prior to the experiment, participants were informed
-that capitalizing corresponded to contrastive stress. The task
-consisted in a forced-choice questionnaire with two given alternatives
-(such as {\it All of the students wrote some but not all of the
-  official memos} vs. {\it All of the students wrote at least some of
-  the official memos}). Interestingly, strengthened interpretations
-occurred rather often across all sentences in this task (59 \%), but
-were not affected by capitalizing.\fn{Note that, unfortunately, the
-  paper does not provide percentages for the embedded conditions
-  alone, but only the means across sentence types.}
-\citeauthor{Frazier08} concludes that accentuation did not affect the
-silent reading data, but raises the possibility that prosodic effects
-may have been present at least in a subset of the items (see
-footnote~1 in \citet{Frazier08}, p.~330).
-
-Another study relevant for the present considerations comes from
-\citet{SchwarzClifton2008:Strengthening-o}, examining the effects of
-contrastive accentuation of \emph{or} in non-embedded sentences like
-{\it Mary will invite Fred or/OR Sam to barbecue}. After listening to
-these sentences, participants were presented two alternative readings
-({\it 1. She will invite Fred or Sam or possibly both}, or {\it 2.
-  She will invite Fred or Sam but not both}).  The authors found a
-significant impact of overtly realized contrastive accents on
-implicature inferences: Besides a general advantage for
-non-strengthened readings, focal accents significantly increased the
-strengthened interpretation (from 16.4 \% to 28.6 \%). These results
-are compatible with the "focus strengthening hypothesis" proposed by
-the authors.
-
-To sum up so far, though an effect of contrastive accentuation has
-been claimed to be essential for triggering local implicatures,
-experimental evidence is currently mixed, suggesting potential effects
-of presentation mode (visual vs.~auditory), item-specific
-characteristics, as well as the specific construction under
-investigation (e.g., embedded cases vs.~non-embedded cases such as in
-\citet{SchwarzClifton2008:Strengthening-o}). It is for these reasons
-that an experimental investigation into the availability of readings
-of \as- and \es-sentences should present sentential material
-auditorily and explicitly address the prosodic markedness
-hypothesis.
-
-\section{Previous studies}
-\label{sec:previous-studies}
-
-In order to test the divergent predictions of the relevant theoretical
-positions, a number of empirical studies have been carried out. We
-will focus on the works of
-\citet{GeurtsPouscoulous2009:Embedded-Implic},
-\citet{CliftonDube2010:Embedded-Implic} and
-\citet{ChemlaSpector2010:Experimental-Ev} \citep[c.f.][for related
-discussion]{BenzGotzner2014:Embedded-implic}. Unfortunately, these
-studies do not provide conclusive evidence about the availability and
-preference of relevant readings and do not speak to prosodic
-markedness effects.
-
-\subsection{\citet{GeurtsPouscoulous2009:Embedded-Implic}}
-\label{sec:Geurts-and-Pouscoulous}
-
-\citet{GeurtsPouscoulous2009:Embedded-Implic} conducted a
-picture-verification task (their Experiment~3) to find out whether
-local readings of \as- and \es-sentences are available.\fn{We will
-  focus here on a subset of the conditions tested by
-  \citet{GeurtsPouscoulous2009:Embedded-Implic}. Actually, these
-  authors did not use \es-sentences, but sentences where scalar
-  \emph{some} was embedded under non-monotonic quantifier
-  \emph{exactly two} (with appropriate pictures, of course). This case
-  is a little more complex, but we will gloss over this here, treating
-  their data, as if it had been obtained for \es-sentences.} Subjects
-were presented with pictures similar to in Figure~\ref{fig:weak} and
-\ref{fig:local} (pages \pageref{fig:weak} and \pageref{fig:local})
-where the local reading gets a different truth-value than the literal
-and the global reading. For \as-sentences, the local reading is false
-for the critical picture in Figure~\ref{fig:weak} whereas the literal
-and global readings are true; for \es-sentences the local reading is
-true for the critical picture in Figure~\ref{fig:local}, whereas the
-literal and global readings are false.
-
-The results of \citeauthor{GeurtsPouscoulous2009:Embedded-Implic} were
-strikingly unambiguous: there were \emph{no} responses indicative of a
-local reading; \emph{all} of the subjects judged \as-sentences true in
-a situation like in Figure~\ref{fig:weak} and \emph{all} of the
-subjects judged \es-sentences false in situations like
-\ref{fig:local}.
-
-These results were criticized on theoretical grounds (e.g.,
-\citet{Sauerland2010:Embedded-Implic}, but see
-\citet{Ippolito2010:Embedded-Implic} for support), as well as based on
-empirical observations
-\citep{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. In
-the following, we will review these empirical studies briefly, as they
-provide the background for our own experiment. % We will first consider
-% a comment by \citet{CliftonDube2010:Embedded-Implic}, which explicitly
-% distinguishes between the availability of a reading and its
-% preference.
-
-\subsection{\citet{CliftonDube2010:Embedded-Implic}}
-\label{sec:clifton-dube}
-
-In a reply to \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s
-study. \citet{CliftonDube2010:Embedded-Implic} raised the question
-whether the use of a picture-verification paradigm might have been
-infelicitous for testing the availability of strong readings, at least
-in the case of \as-sentences. Asking whether a sentence fits a picture
-might have created a bias for accepting sentences also on a weaker and
-probably dispreferred reading. Clifton and Dube's study was therefore
-aimed at finding out about a potential preference relation between
-local and literal readings. To this end, Clifton and Dube developed a
-picture-choice task where subjects were presented with an \as-sentence
-and a pair of pictures, hence introducing the option to choose between
-different alternatives. Subjects were asked to ``indicate which shape
-is best described by the sentence'' and could choose either picture,
-or options `both' and `neither.' There were two versions of this
-experiment, differing in which kind of picture pairs were presented on
-critical trials. In version 1, the picture pair consisted of the weak
-and strong situations in Figures~\ref{fig:weak} and
-\ref{fig:strong}. The response percentages observed by
-\citeauthor{CliftonDube2010:Embedded-Implic} were:
-
-\begin{center}
-  \begin{tabular}{cccc}
-    weak & strong & both & neither
-    \\ \midrule 
- 3 & 39 & 57 & 1 
-  \end{tabular}
-\end{center}
-
-\noindent That the majority answer is ``both'' could be taken as
-evidence that the literal reading is the preferred one. But the almost
-40\% of choices for the strong situation, so
-\citeauthor{CliftonDube2010:Embedded-Implic} argue, is indicative of
-the availability of the local reading. In version 2 of the experiment,
-the picture pair consisted of the literal and weak situations in
-Figures~\ref{fig:literal-AE} and \ref{fig:weak}. In this case,
-response percentages were:
-
-\begin{center}
-  \begin{tabular}{cccc}
-    weak & literal & both & neither
-    \\ \midrule 
-    28 & 6 & 50 & 17 
-  \end{tabular}
-\end{center}
-
-\noindent Again, the majority response ``both'' might speak for a
-preference for the literal reading, but, as
-\citeauthor{CliftonDube2010:Embedded-Implic} propose, the 17\% of
-``neither'' answers in this case again suggest that the local reading
-is available. In sum,
-\citeauthor{CliftonDube2010:Embedded-Implic} take these results to
-contradict \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s
-findings. Local readings are, after all, attested if subjects are
-given a choice as to which situation they consider most fitting for an
-\as-sentence.
-
-The diverging results of
-\citeauthor{GeurtsPouscoulous2009:Embedded-Implic} and
-\citeauthor{CliftonDube2010:Embedded-Implic} seem to indicate that
-participants' choices for readings of \as-sentences might have been
-affected by the specific experimental paradigm used \citep[but
-see][for critique of the latter
-design]{GeurtsTielvan-Tiel2013:Embedded-Scalar}. Unfortunately,
-\citet{CliftonDube2010:Embedded-Implic} did not test both universal
-and non-monotonic quantifiers within the same
-experiment. Additionally, it would be informative to also probe into
-the availability of global readings. The study of
-\citet{ChemlaSpector2010:Experimental-Ev} did both of that.
-
-\subsection{\citet{ChemlaSpector2010:Experimental-Ev}}
-\label{sec:Chemla-Spector}
-
-\citet{ChemlaSpector2010:Experimental-Ev} also took issue with
-\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s design, arguing
-that, firstly, the pictorial material used in
-\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s study was unduly
-difficult; that, secondly, these pictures also may have failed to make
-the local reading sufficiently relevant; and that, thirdly, the
-restriction to a categorial choice (whether the sentence fits the
-picture of not) may induce a bias against non-preferred readings in
-cases where candidate readings stand in entailment relations
-\citep[see][for this latter
-criticism]{Sauerland2010:Embedded-Implic}. To meet these potential
-problems, \citet{ChemlaSpector2010:Experimental-Ev} presented subjects
-with pictorial material like that in Figure~\ref{fig:Chemla-Spector},
-which was assumed to be easier to assess and better at highlighting
-the relevance of the local readings. Albeit in a different format, the
-pictures used by \citeauthor{ChemlaSpector2010:Experimental-Ev} were
-instantiations of the situation types in
-Figures~\ref{fig:AS-distinguishing-pics} and
-\ref{fig:ES-distinguishing-pics}. Additionally, subjects were asked,
-not for categorial judgements, but for \textit{graded judgements}:
-subjects could freely click on a scale, as shown in
-Figure~\ref{fig:Chemla-Spector}, to indicate how much they considered
-a picture fitting for a given sentence \citep[see][for more on this
-method]{Chemla2009:Presuppositions}.
-
-\begin{figure}[t]
-  \centering
-
-  \subfloat[][Example of the \as-weak condition of
-  \citet{ChemlaSpector2010:Experimental-Ev}]{
-      \label{fig:Chemla-Spector}
-  \begin{minipage}{0.45\linewidth}
-    \begin{center}
-      \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
-      \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
-    \end{center}
-
-  \end{minipage}
-    }
-   \begin{minipage}{6cm}
-     \subfloat[][Results \as-condition]{
-    \label{fig:CS-Results-as}
-        \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
-  }
-
-  \subfloat[test][Results \es-condition]{
-    \label{fig:CS-Results-es}
-    \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
-  }  
-   \end{minipage}
-        \caption{Example trial and results of
-          \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
-          (\citeyear{ChemlaSpector2010:Experimental-Ev}) study.}
-\end{figure}
-
-% \begin{figure}[t]
-%   \centering
-%       \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
-%       \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
-%         \caption{Example of critical trial for \as-condition by
-%           \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
-%           (\citeyear{ChemlaSpector2010:Experimental-Ev})}
-%   \label{fig:Chemla-Spector}
-% \end{figure}
-
-\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the
-degree to which a sentence is rated acceptable is proportional to the
-number of available true readings. Observed averaged clicking
-positions are shown in Figures~\ref{fig:CS-Results-as} and
-\ref{fig:CS-Results-es}.
-%
-% \begin{figure}
-%   \centering
-%   \subfloat[][\as-condition]{
-%     \label{fig:CS-Results-as}
-%         \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
-%   }
-%   \subfloat[test][\es-condition]{
-%     \label{fig:CS-Results-es}
-%     \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
-%   }
-%   \caption{Results from
-%     \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
-%     (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
-%   \label{fig:Chemla-Spector-Results}
-% \end{figure}
-%
-According to \citeauthor{ChemlaSpector2010:Experimental-Ev}, the
-crucial piece of evidence for the availability of local readings for
-\as-sentences is that these sentences yielded higher graded
-acceptability scores for the strong situation than for the weak
-situation (although these differ only with respect to the truth value
-of the local reading). Evidence for the availability
-of the local reading for \es-sentences comes from the difference
-between the local and the literal situation. Strikingly, \es-sentences
-received an average 73\% degree of acceptability in the local
-situation although the literal and global readings are false in this
-case.
-
-\subsection{Reflection}
-\label{sec:local-read-categ}
-
-Summing up, three experimental studies have presented diverging pieces
-of evidence. % \citet{GeurtsPouscoulous2009:Embedded-Implic} did not
-% observe any truth value-judgments that would indicate local readings
-% in a picture verification task and thus conclude that these readings
-% are unavailable. \citet{CliftonDube2010:Embedded-Implic} and
-% \citet{ChemlaSpector2010:Experimental-Ev} employed different designs
-% intended to be sensitive enough to reveal local readings. Both studies
-% found putative evidence in support of local readings.
-Differences in results are likely due to differences in experimental
-design, in particular due to (i) the type of elicited judgement and
-(ii) the possibility of conflating pictorial effects.
-
-\paragraph{Judgement Type.} We could draw a distinction between
-categorical truth-value judgments and other potentially more sensitive
-measures. The former are possibly not sensitive enough to reveal
-dispreferred readings with small samples, but the latter may be. We
-could then hypothesize along with
-\citeauthor{CliftonDube2010:Embedded-Implic} and
-\citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
-available, but so dispreferred that they do not affect categorical
-truth-value judgments.
-
-On the other hand, \citet{Crain1998} argue in favor of truth-value
-judgments as a means of detecting dispreferred readings. Consequently,
-traditionalists could reply that the putative evidence for local
-readings in allegedly more sensitive tasks might reflect something
-other than (strongly) truth-relevant speaker-intended meaning
-enrichments. Hence no case can be made for lexicalism or
-grammaticalism on the basis of these data \citep[see][for arguments
-along these
-lines]{GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter,Tielvan-Tiel2012:Embedded-Scalar}.
-
-To resolve this issue, we would ideally like to have a design that
-elicits categorical truth-value judgements, but is still possibly
-sensitive enough to detect dispreferred readings.
-
-\paragraph{Pictorial Effects.} It is often possible to present
-different numbers of links between icons in pictures like in
-Figures~\ref{fig:AS-distinguishing-pics}
-and~\ref{fig:ES-distinguishing-pics}, without changing the
-truth-values of relevant readings. Indeed, the pictorial material used
-in previous studies differed in this respect, and that might explain
-some of the differences in results. If that is so, then we cannot
-ascribe the effects reported by
-\citet{CliftonDube2010:Embedded-Implic} and
-\citet{ChemlaSpector2010:Experimental-Ev} to the availability of local
-readings with certainty. \citet{ChemlaSpector2010:Experimental-Ev}
-also acknowledge the possibility that the \emph{typicality} of a
-picture with respect to some meaning may affect graded truth-value
-judgments. They show that graded judgments of \as-sentences differ
-significantly for different pictures that agree on the truth value of
-relevant readings but differ with respect to the amount of connections
-between icons. \citeauthor{ChemlaSpector2010:Experimental-Ev} suggest
-that typicality of the pictorial material can account for these
-differences, but submit that this does not explain away the high
-acceptance of pictures like Figure \ref{fig:weak}.
-
-The latter point is disputed by
-\citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates that a huge
-chunk of variance in the responses to \as-sentences can be explained
-as typicality effects, dispensing the need to appeal to the
-distribution of different readings. In support of this idea,
-\citet{Tielvan-Tiel2012:Embedded-Scalar} elicited what he calls the
-typicality structures associated with the quantifiers {\it all} and
-{\it some} \citep[as done also
-by][]{DegenTanenhaus2011:Making-Inferenc} and predicted the judgments
-of \as-sentences obtained by
-\citeauthor{ChemlaSpector2010:Experimental-Ev} based on these
-data. Thereby, he obtained an excellent model fit.
-
-We are generally sympathetic towards
-\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
-reinterpretation of the data, but note, as
-\citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
-typicality-based explanation does not extend to \es-sentences in an
-obvious way. Moreover, typicality itself is not a satisfactory
-primitive in a putative explanation of the use of quantifiers, but
-rather something that needs explanation itself \citep[c.f.][for
-critical reflection on typicality-based
-explanations]{Cummins2014:Typicality-made}. Indeed, it is possible to
-explain typicality judgements as the outcome of Gricean speaker
-preferences for informative descriptions, just like those that
-rationalize quantity implicatures \citep{Franke2014:Typical-use-of-}.
-For these reasons, we believe that typicality and other pictorial
-effects need to be taken seriously in the experimental design, but do
-not necessarily give a satisfactory account of the observed variation
-all by themselves.
-
-\paragraph{Upshot.} Taken together, we would ideally like a design
-that evokes categorical truth value judgments in a way that is as
-independent as possible of potentially conflating properties of the
-pictorial material and that is nonetheless sensitive enough to detect
-local readings even if they are dispreferred. The sensitivity to
-dispreferred readings should be controlled for. On top of this, it
-would be desirable to obtain further information about the relative
-preferences among all putative readings, so as to be able to decide
-between theoretical positions, as outlined in
-Section~\ref{sec:theories-predictions}. % Neither of the previous
-% studies gives us that, either because they simply have not
-% investigated all the relevant comparisons
-% (\citet{GeurtsPouscoulous2009:Embedded-Implic},
-% \citet{CliftonDube2010:Embedded-Implic}), or because they cannot
-% safely derive the required information for danger of conflating
-% preferences for readings with preferences for pictures
-% (\citet{ChemlaSpector2010:Experimental-Ev}).
-
-Finally, we need to control for ``silent prosody.'' Several studies
-suggest that numerous factors might influence accent placement and
-prosodic phrasing even while reading, amongst them default
-accentuation, constituent length, rhythmic phenomena, and individual
-variation
-\citep[e.g.][]{Bader98,Fodor98,Steinhauer01,Fodor02,Augurzky08,BreenWatson2011:Intonational-ph,Kentner12}. If
-we adopt the prosodic markedness hypothesis described in
-Section~\ref{sec:inton-mark-hypoth}, as many traditionalists do, we
-predict that the availability of a local reading hinges on the
-realization of contrastive stress on the scalar item
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
-But if intonation can have this role, it is necessary to control for
-silent accent placement. Ideally, therefore, we should present
-sentences auditorily and systematically manipulate contrastive stress.
-
-\section{An Incremental Verification Task}
-\label{sec:exp}
-
-\subsection{Design}
-\label{sec:design}
-
-\paragraph{General Idea.} In order to test the availability and
-preferences of different readings of \as- and \es-sentences in German,
-we were looking for a way to unambiguously map responses from a
-picture verification task to specific readings. We were particularly
-interested in the question whether local readings would be observed at
-all, and whether their presence or absence would be modulated by a
-contrastive accent on the scalar item. Moreover, we were interested in
-obtaining information about the relative preferences of the different
-readings. In addition, we wanted to minimize potential picture
-typicality effects. To achieve this (see
-Section~\ref{sec:discussion-1} for discussion), we used an
-\mymark{incremental verification task} (\acro{ivt}), which is a
-modified version of picture verification
-\citep[see][]{Conroy2008}. The general idea is that subjects are
-requested to judge sentence material with respect to pictures that do
-not necessarily contain all the information relevant for judging a
-certain reading true or false. In that case, participants can demand
-that more information be revealed. Participants are instructed to make
-a truth-value judgment as soon as they are able to. When they do, the
-trial ends.
-
-\paragraph{Target Conditions.} We present sequences of pictures
-depicting a set of four identical central elements (e.g., letters),
-which could be connected to surrounding elements (e.g., triangles), as
-shown in Figures~\ref{fig:exseqAS}--\ref{fig:exec}. Initially,
-any potential connections between central and surrounding elements
-were covered by dark gray color (see
-Figure~\ref{fig:exseqAS1}). Sentences to be judged were presented
-auditorily, and participants were asked to uncover the picture until
-they felt able to give a truth value judgment. Three options were
-available for participants at each step: (i) judge the sentence as
-true, (ii) judge the sentence as false, (iii) demand more information
-(unavailable when the picture was fully uncovered). Trials ended when
-a truth-value judgement was made. Importantly, each of the three
-potentially available readings corresponded to a specific step in the
-uncovering process where the truth value of that reading (and only of
-that reading) could be assessed for the first time. We refer to this
-step in the sequence as the {\it critical position} of a given
-reading. The critical position and the corresponding truth-value
-judgment differed between \as- and \es-sentences, as described
-presently. (This is, partly, because of the logical dependencies
-between readings, and, partly, also to rule out positional biases.)
-
-\begin{figure}[]
-	\centering
-	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_1.pdf}}
-	    \label{fig:exseqAS1}
-	}
-	\subfloat[][Step 2]{
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_2.pdf}}
-	    \label{fig:exseqAS2}
-	}
-	\subfloat[][Step 3 (\lit true)]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_3.pdf}}
-	    \label{fig:exseqAS3}
-	}
-        \\
-	\subfloat[][Step 4]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_4.pdf}}
-	    \label{fig:exseqAS4}
-	}
-	\subfloat[][Step 5 (\glb true)]{
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_5.pdf}}
-	    \label{fig:exseqAS5}
-	}
-	\subfloat[][Step 6]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_6.pdf}}
-	    \label{fig:exseqAS6}
-	}
-        \\
-	\subfloat[][Step 7 (\loc false)]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ae_01_7.pdf}}
-	    \label{fig:exseqAS7}
-	} 
-                \hspace*{7.85cm} 
-	\caption[]{Example picture sequence for \as-sentences.}
-	\label{fig:exseqAS}
-\end{figure}
-
-Consider the German \as-sentence in (\ref{ex:as}), included in our study.
-\begin{exe}
-\ex \gll \mymark{Alle} diese Briefe sind mit \mymark{einigen} ihrer Dreiecke
-  verbunden.\label{ex:as}\\
-All these letters are with some their triangles connected.\\
-\trans All of these letters are connected to some of their triangles.
-\end{exe}
-Figure~\ref{fig:exseqAS} shows the corresponding picture sequence. The
-critical positions are on step 3, 5 and 7. Pictures that were
-interspersed between these positions served as
-spillover-pictures. These were used in order to counter potentially
-delayed judgments and they additionally served as distractor
-items. Prior to step 3 there is not enough information to judge any
-candiate reading true or false. The situation at step 3 in
-Figure~\ref{fig:exseqAS3} is true under a literal reading, while the
-local and global readings cannot be evaluated yet. On step 5 in
-Figure~\ref{fig:exseqAS5} the literal reading is still true, but now
-also the global reading can be confirmed. Finally, decisions
-concerning the local reading are possible as soon as all connections
-have been uncovered at step 7 in Figure~\ref{fig:exseqAS7}. Note that
-the situation at step 7 is \emph{in}compatible with a local
-reading. This enables us to separate local readings, which would yield
-\emph{false} judgements at this position, from literal and global
-readings, which would yield \emph{true} judgements. In sum,
-\emph{true} or \emph{false} answers on particular positions in the
-incrementally revealed picture sequence can be mapped uniquely to
-candidate readings. All other \emph{true} or \emph{false} answers were
-counted as errors.
-
-Due to the non-linear entailment order of readings described in
-Section~\ref{sec:get-know-your}, \es-sentences require a slightly
-different sequence of unfolding, which yields a different order in
-which truth-value judgments can be made.
-%
-\begin{figure}[t]
-	\centering
-	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_1.pdf}}
-	    \label{fig:exseqES1}
-	}
-	\subfloat[][Step 2 (\glb false)]{
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_2.pdf}}
-	    \label{fig:exseqES2}
-	}
-	\subfloat[][Step 3 (\lit false)]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_3.pdf}}
-	    \label{fig:exseqES3}
-	}
-        \\
-	\subfloat[][Step 4]{ 
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_4.pdf}}
-	    \label{fig:exseqES4}
-	}
-	\subfloat[][Step 5 (\loc true)]{
-		\fbox{\includegraphics[width=3.5cm]{../pictures/ge_01_5.pdf}}
-	    \label{fig:exseqES5}
-	}
-                \hspace*{3.9cm} 
-	\caption[]{Example sequence for \es-sentences.}
-	\label{fig:exseqES}
-\end{figure}
-%
-For a sentence like (\ref{ex:es}), we obtain an unambiguous mapping
-between truth judgements and readings with the sequence in
-\ref{fig:exseqES}.
-\begin{exe}
-\ex \label{ex:es} \gll \mymark{Genau} eine der Glocken ist mit
-  \mymark{einigen} ihrer Halbkreise verbunden.\\ 
-  Exactly one of-the bells is with some its semicircles connected.\\
-  \trans Exactly one bell is connected to some of its semicircless.
-\end{exe}
-The critical positions are steps 2, 3 and 5. At step 2 in
-Figure~\ref{fig:exseqES2}, a global reading would yield a \emph{false}
-judgement. The literal reading can be evaluated at step 3 in
-Figure~\ref{fig:exseqES3}, where it would trigger a \emph{false}
-judgement. Finally, confirming \ref{fig:exseqES5} by a \emph{true}
-response indicates a local reading. Note that global and literal
-readings again differ from local readings with respect to their truth
-values.
-
-\paragraph{Positional controls.} To make sure that subjects understood
-the task, i.e., gave truth-value judgements at the first possible
-position in a sequence, we included a set of control conditions. These
-also controlled for response biases. For each of the three readings in
-the \as- and \es-conditions, we constructed an unambiguous control
-sentence as in (\ref{bsp:controls-as}) and (\ref{bsp:controls-es}),
-requiring the same judgement at the identical position in the same
-sequence used for the respective targets. For instance, example
-(\ref{bsp:controls-as-1}) requires a \emph{true}-response analogous to
-the \as-sentence in (\ref{ex:as}) under its literal reading at step 3
-in Figure~\ref{fig:exseqAS3}, (\ref{bsp:controls-as-2}) corresponds to
-the \as-sentence under its global reading and
-(\ref{bsp:controls-as-3}) corresponds to its local reading. With
-regard to the \es-sentences, controls like (\ref{bsp:controls-es-1})
-correspond to the global reading, (\ref{bsp:controls-es-2}) to the
-literal and (\ref{bsp:controls-es-3}) to the local reading. If,
-independently of sentence meaning, there was any bias to respond in a
-certain way at any point in the sequences, such as to preferably
-unravel the whole picture, this should affect control sentences to the
-same degree as it affects target conditions.
-
-\begin{exe}
-  \ex \label{bsp:controls-as}
-    \begin{xlist}
-\ex \label{bsp:controls-as-1} \gll Alle Briefe sind mit mindestens drei ihrer Dreiecke verbunden.\\
-  All letters are with at-least three their triangles connected.\\
-  \trans All letters are connected to at least three of their triangles.
-\ex \label{bsp:controls-as-2} \gll Mindestens ein Brief ist mit genau f\"unf seiner Dreiecke verbunden.\\
-  At-least one letter is with exactly five his triangles connected.\\
-  \trans At least one letter is connected with exactly five of its triangles.
-\ex \label{bsp:controls-as-3} \gll Jeder Brief ist mit mindestens vier seiner Dreiecke verbunden.\\
-  Every letter is with at-least four his triangles connected.\\
-  \trans Every letter is connected to at least four of its triangles.
-\end{xlist}
-\end{exe}
-
-\begin{exe}
-\ex \label{bsp:controls-es}
-  \begin{xlist}
-\ex \label{bsp:controls-es-1} \gll Alle Glocken sind mit weniger als
-  vier ihrer Halbkreise verbunden. \\ 
-All bells are with fewer than four their semicircles connected.\\
-\trans All bells are connected with fewer than four of their semicircles.  
-\ex \label{bsp:controls-es-2} \gll Alle Glocken sind mit allen ihren Halbkreisen verbunden.\\
-All bells are with all their semicircles connected.\\
-\trans All bells are connected to all of their semicircles. 
-\ex \label{bsp:controls-es-3} \gll Mindestens drei Glocken sind mit
-  allen ihren Halbkreisen verbunden.\\ 
-  At-least three bells are with all  their semicircles connected.\\
-  \trans At least three bells are connectd with all of their semicircles.
-\end{xlist}
-\end{exe}
-
-\paragraph{Preference-related controls.} In order to test whether the
-order of critical positions for different readings within a sequence
-had an influence on responses, we included a second type of control
-conditions.  These controls served as a test whether the incremental
-verification task could possibly detect at least ordinal preference
-relations among multiple candidate readings. Finally, these conditions
-also controlled whether prosodic information can, in principle, shift
-answer patterns in the present task. Note that for our target
-sentences, the logical entailment relations between readings always
-require local readings to be evaluated at the end of a sequence. It
-could thus in principle be possible that subjects never reach this
-point, because they give truth-value judgements earlier, thereby
-ending the trial. In that case it would be unclear whether these
-decisions had been affected by a general unavailability of local
-readings or by the fact that one of the earlier presented readings is
-the preferred one. By including globally ambiguous structures with a
-known preference over available readings, we thus tested whether
-participants in our task occasionally choose dispreferred readings,
-even if these were available only at a critical position following the
-preferred readings.
-
-We therefore included globally ambiguous \emph{late-closure
-  sentences} as in (\ref{bsp:target-related}), which have been
-repeatedly shown to exhibit interpretive preferences.
-\begin{exe}
-\ex \gll Der Brief ist mit Kreisen und Vierecken mit Sonnen
-  verbunden. \label{bsp:target-related}\\
-The letter is with circles and squares with suns connected.\\
-The letter is connected with circles and squares with suns.
-\begin{xlist}
-  \ex \label{bsp:target-related-LC} The letter is connected with squares containing suns, and it is
-    also connected with circles. \hfill{(\lc)}
-  \ex \label{bsp:target-related-EC} The letter is connected with circles and squares, both of which
-    are containing suns.  \hfill{(\ec)} 
-\end{xlist}
-
-\end{exe}
-In late-closure sentences, a modifier like a relative clause or a
-prepositional phrase (\acro{pp}) can be attached to one of two
-preceding hosts. For instance, in (\ref{bsp:target-related}), the
-\acro{pp} \emph{with suns} can be attached to the preceding noun
-\emph{squares}, resulting in the so-called \emph{late-closure} (\lc)
-reading ((\ref{bsp:target-related-LC}). Alternatively, the \acro{pp}
-can be attached to the whole conjunctive \acro{np} \emph{circles and
-  squares}, corresponding to the \emph{early-closure} (\ec) reading
-(\ref{bsp:target-related-EC}).  \lc-readings have been observed to be
-preferred over \ec-readings for sentences comparable to those in
-(\ref{bsp:target-related}) \citep[e.g.][]{Frazier87,Frazier82}.
-
-For each sentence, two sequences were designed: one in which the
-preferred \lc-reading could be judged first (Figure~\ref{fig:exlc}),
-%
-\begin{figure}[]
-	\centering
-	\subfloat[][Step 2]{ 
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_2.pdf}}
-	    \label{fig:exlc2}
-	}
-	\subfloat[][Step 3 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_3.pdf}}
-	    \label{fig:exlc3}
-	}
-        \\
-	\subfloat[][Step 4]{
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_4.pdf}}
-	    \label{fig:exlc4}
-	}
-	\subfloat[][Step 5 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_5.pdf}}
-	    \label{fig:exlc5}
-	}
-        \\
-	\subfloat[][Step 6 (\ec false)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_6.pdf}}
-	    \label{fig:exlc6}
-	}
-	\subfloat[][Step 7 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/lc_01_7.pdf}}
-	    \label{fig:exlc7}
-	}
-	\caption[]{Example of an \lc-sequence for sentence
-          (\ref{bsp:target-related}) where the \lc-reading
-          (\ref{bsp:target-related-LC}) can be judged first. The first
-          step where all connections are covered is omitted.}
-	\label{fig:exlc}
-\end{figure}
-%
-and another in which the dispreferred \ec-reading could be judged
-first (Figure~\ref{fig:exec}).
-%
-\begin{figure}[]
-	\centering
-	\subfloat[][Step 2]{ 
-		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_2.pdf}}
-	    \label{fig:exec1}
-	}
-	\subfloat[][Step 3 (\ec false)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_3.pdf}}
-	    \label{fig:exec2}
-	}
-        \\
-	\subfloat[][Step 4]{
-		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_4.pdf}}
-	    \label{fig:exec2}
-	}
-	\subfloat[][Step 5 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../pictures/ec_01_5.pdf}}
-	    \label{fig:exec2}
-	}
-	\caption[]{Example of an \ec-sequence for sentence
-          (\ref{bsp:target-related}) where the \ec-reading
-          (\ref{bsp:target-related-EC}) can be judged first. The first
-          step where all connections are covered is omitted.}
-	\label{fig:exec}
-\end{figure}
-%
-We also tested structurally disambiguated versions like
-(\ref{bsp:target-related2}), one for each sentence type, on each
-sequence type for proper comparison.
-
-\begin{exe}
-
-\ex \gll Der Brief ist mit Kreisen, die Sonnen beinhalten, und Vierecken
-  verbunden. \label{bsp:target-related2}\\
-The letter is with circles, which suns contain and squares connected.\\
-The letter is connected with circles containing suns, and with squares.
-
-\end{exe}
-
-\paragraph{Testing Effects of prosody.} Whereas contrastive accents
-are usually assumed to be realized by a special contour in English
-(i.e. L+H*, see \citet{Pierrehumbert90}), the exact phonological
-classification of contrast in German is still under debate
-\citep[see][]{Uhmann91,Fery93,Grabe98,Toepel06, Sudhoff10}.  Still,
-all of these approaches have in common that from an acoustic
-perceptive, prosodic prominence of contrastively accented constituents
-is realized by
-
-\begin{enumerate}[(i)]
-\item a higher F0 maximum or a higher pitch range (difference 
-between minimal and maximal F0 values), and
-\item a longer duration of the accented element as opposed to its 
-non-accented counterpart.
-\end{enumerate}
-
-\noindent Our sentences were read by a phonetically trained female
-native speaker of German familiar with the concept of contrastive
-focus. Both \as-sentences and \es-sentences were recorded in two
-versions each. In the accented version, a contrastive stress was
-placed on {\it einige}. The second version had neutral prosody.  If
-accentuation is the driving force for local readings, we would expect
-a higher proportion of local readings in the former than in the latter
-version of the sentences.
-
-Preference-related controls also differed prosodically. Modifier
-attachment ambiguities have been shown to be sensitive to differences
-in prosodic phrasing. Though there has been discussion as to whether
-speakers reliably \textit{produce} disambiguating cues in such
-constructions \citep[e.g.][]{Allbritton96,Kraljik05, Snedeker03,
-  Schafer00}, overt prosodic boundaries are generally acknowledged to
-guide interpretive processes of late-closure sentences in
-\textit{comprehension} \citep[e.g.][]{Steinhauer99, Augurzky06}.
-Specifically, it has been shown that prosodically separating a
-modifier from the directly preceding material supports an \ec-reading,
-whereas separating the two potential attachment sites is supportive of
-an \lc-reading. Thus, a phrase boundary between {\it squares} and {\it
-  with} in (\ref{bsp:target-related}) supports an \ec-reading, whereas
-a prosodic phrase boundary following {\it circles} supports an
-\lc-reading.
-
-To test whether prosodic information is taken into account in our
-task, we presented sentences in both of these prosodic variants. In
-addition, in order to test prosody-independent preferences, we also
-included a neutral version without any pronounced boundary. Further,
-we also presented unambiguous sentences corresponding to the
-\ec-reading. As in the case of the \as- and \es-sentences,
-the unambiguous counterparts served as a baseline to control for
-response biases that are independent of sentence meaning.
-
-\subsection{Methods}
-\label{sec:materials}
-
-\subsubsection{Procedure}
-\label{sec:procedure}
-
-Each experimental trial proceeded as described above. The sentence was
-presented using active PC loudspeakers and the picture materials were
-presented on a computer screen. Participants responded using the
-keyboard. By pressing one of four buttons they could (i) listen to the
-sentence (up to three times), (ii) request additional pictorial
-information, (iii) respond ``yes, fits'' or (iv) ``no, does not fit''
-(German: ``passt'' or ``passt nicht''). At the beginning of an
-experimental session participants received written instructions on
-their task. Then they completed an interactive training consisting of
-15 trials in which they were familiarized with the task.  After the
-training the actual experiment started. Participants were tested
-individually in a silent room. Each session was divided into two
-blocks and participants were told that they could take breaks between
-blocks. In total, an experimental session took about one hour. At the
-end of the session participants received 8 euros compensation.
-
-\subsubsection{Materials}
-
-\paragraph{Target sentences and positional controls.}
-
-We constructed a set of 15 items for German \as- and \es-sentences,
-respectively, analogous to the examples in (\ref{ex:as}) and
-(\ref{ex:es}). Sentences were introduced by a subject {\acro{dp}},
-including the quantifiers {\it alle diese} ("all of these") or {\it
-  genau eine(r) der} ("exactly one of these"), as well as the head
-noun which denoted different icons, such as letters or bells. Subject \acros{DP}
-were followed by an auxiliary, and a \acro{pp} containing {\it
-  einige}, a possessive pronoun, and a noun denoting a geometrical
-object, e.g., {\it einigen seiner Dreiecke/Quadrate} ("some of its
-triangles/squares"). The possessive pronoun was used in order to fix
-relative quantifier scope to surface scope, thus ensuring that {\it
-  einige} has embedded status. The last word was the main verb {\it
-  verbunden} ("connected").  Each sentence was recorded in a stressed
-and an unstressed version of scalar {\it einige}. As described above,
-three control sentences were created for each experimental item,
-corresponding to the critical positions in the course of uncovering
-the accompanying sequences.  The positional controls were recorded
-with neutral prosody.  Items were evenly distributed across 5 lists
-using a Latin square design.
-
-\paragraph{Preference-related control sentences.}
-For controlling preferences, 30 sentences that were ambiguous between
-a \lc and an \ec-reading, as well as 30 of their disambiguated
-counterparts were constructed as described above. In these sentences,
-subject \acros{dp} were always denoting icons and were followed by an
-auxiliary. In the ambiguous sentences, the auxiliary was followed by
-two {\it with}-\acros{pp} (German: ``mit'').  The first of these
-\acros{pp} consisted in a coordination of two nouns denoting
-geometrical objects, whereas the nouns in the second \acro{pp} denoted
-icons. In contrast to these sentences, the unambiguous sentences
-contained only one \acro{pp} with a conjunction the first part of
-which was modified by a relative clause.
-
-\paragraph{Acoustic properties.}
-% A phonetically trained female native speaker of German was instructed
-% to realize two prosodic versions of each target sentence, and three
-% versions of the ambiguous preference-related controls. In addition to
-% these sentences, the unambiguous preference-related controls, the
-% positional controls and a set of unrelated fillers were also
-% recorded. For these constructions, the speaker was instructed to
-% realize prosodic contours as neutral and natural as possible.
-
-For all target sentences (\as and \es), the determiner \emph{einige} was
-produced with a contrastive pitch accent as well as with a neutral
-accent. % Contrastive accents in German are realized by an increase in F0 (range)
-% as well as by a longer duration (see Section~\ref{sec:design} above). 
-A set of 15 
-experimental items was recorded for each condition (\as vs.~\es, \emph{accented} 
-vs.~\emph{unaccented}), resulting in a total number of 60 target sentences.
-
-In contrast to the accent manipulation, the ambiguous
-preference-related controls differed with respect to prosodic
-phrasing. Prosodic phrase boundaries in German are realized by a rise
-in F0 as well as by a durational increase on the final part of the
-constituent preceding the boundary (prefinal lengthening) plus an
-optional pause \citep[e.g.][]{Vaissiere83,Fery93}.  Boundaries for
-these control sentences were either realized at the position
-separating the second \acro{pp} from the preceding material
-(\emph{late boundary}, corresponding to an \ec-reading) or directly
-preceding the second conjunct in the first \acro{pp} (\emph{early
-  boundary}, corresponding to an \lc-reading). As the prosodic
-realization of the targets involved the comparison between an accented
-and a neutral variant, we also included a third version of the
-ambiguous preference-related controls without any pronounced
-boundaries. For each prosodic variant, a set of 30 items was read,
-yielding 90 preference-related controls.
-
-Altogether a total number of 300 sentences consisting of 60 target
-sentences, 90 ambiguous preference-related controls, 30 unambiguous
-preference-related controls, 90 positional control sentences and 30
-unrelated fillers was recorded. The session was recorded in an
-acoustically shielded booth (44.1\,kHz sampling rate, 16 bit amplitude
-resolution).
-
-Before entering the judgment task, experimental items and
-preference-related controls were analyzed with respect to their acoustic
-properties. As both accented elements as well as prosodic boundaries
-were expected to differ with respect to their F0 and/or durational
-properties, we calculated durational values as well as difference
-values between minimal and maximal F0 for each word. Since targets
-slightly differed with respect to the total number of words as well as
-with respect to certain lexical properties (i.e., \emph{seinen}
-vs.~\emph{ihren}, we considered the following analysis regions:
-
-\begin{exe}
-  \ex
-    \begin{xlist}
-      \ex $|_{\text{R}1}$~Alle  	\ $|_{\text{R}2}$~diese 
-      \ $|_{\text{R}3}$~$\acro{np}_1$  
-      \ $|_{\text{R}4}$~sind  \ $|_{\text{R}5}$~mit  \
-      $|_{\text{R}6}$~einigen  \ $|_{\text{R}7}$~ihrer 
-       \ $|_{\text{R}8}$~{$\acro{np}_2$}  \ $|_{\text{R}9}$~verbunden.
-    \ex       $|_{\text{R}1}$~Genau einer  	\ $|_{\text{R}2}$~der 
-      \ $|_{\text{R}3}$~$\acro{np}_1$  
-      \ $|_{\text{R}4}$~ist  \ $|_{\text{R}5}$~mit  \
-      $|_{\text{R}6}$~einigen  \ $|_{\text{R}7}$~seiner 
-       \ $|_{\text{R}8}$~{$\acro{np}_2$}  \ $|_{\text{R}9}$~verbunden.
-    \end{xlist}
-    % \begin{tabbing}
-    %   $|_{\text{R}1}$ Genau einer \= 	\ $|_{\text{R}2}$ diese \=
-    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \= 
-    %   \ $|_{\text{R}4}$ sind \= \ $|_{\text{R}5}$ mit \= \
-    %   $|_{\text{R}6}$ einigen \= \ $|_{\text{R}7}$ seiner 
-    %   \= \ $|_{\text{R}8}$  \acro{np}$_2$ \= \ $|_{\text{R}9}$
-    %   verbunden. \kill
-    %   $|_{\text{R}1}$ Alle \> 	\ $|_{\text{R}2}$ dieser \>
-    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \> 
-    %   \ $|_{\text{R}4}$ sind \> \ $|_{\text{R}5}$ mit \> \
-    %   $|_{\text{R}6}$ einigen \> \ $|_{\text{R}7}$ ihrer 
-    %   \> \ $|_{\text{R}8}$  \acro{np}$_1$ \> \ $|_{\text{R}9}$
-    %   verbunden. \\
-    %   $|_{\text{R}1}$ Genau einer \> 	\ $|_{\text{R}2}$ der \>
-    %   \ $|_{\text{R}3}$ \acro{np}$_1$ \> 
-    %   \ $|_{\text{R}4}$ ist \> \ $|_{\text{R}5}$ mit \> \
-    %   $|_{\text{R}6}$ einigen \> \ $|_{\text{R}7}$ seiner 
-    %   \> \ $|_{\text{R}8}$  \acro{np}$_1$ \> \ $|_{\text{R}9}$ verbunden.
-    % \end{tabbing}
-\end{exe}
-
-\noindent Note that differences between Regions 1, 2, 4 and 7 can be expected
-due to lexical differences between the \as and \es-conditions. As
-preference-related controls did not differ with respect to their lexical
-properties, we carried out word-by-word analyses for these
-conditions. Durational values included the respective word plus any
-following silent interval. We did not include the
-disambiguated fillers in these analyses as they involved very
-different sentence types (i.e., constructions involving prepositional
-phrases vs.~relative clauses).
-
-\begin{exe}
-  \ex $|_{\text{R}1}$ \acro{D}  	\ $|_{\text{R}2}$ $\acro{np}_1$
-      \ $|_{\text{R}3}$ ist 
-      \ $|_{\text{R}4}$ mit  \ $|_{\text{R}5}$ $\acro{np}_2$   \
-      $|_{\text{R}6}$ und  \ $|_{\text{R}7}$ $\acro{np}_3$ 
-       \ $|_{\text{R}8}$  mit  \ $|_{\text{R}9}$ $\acro{np}_4$ \ $|_{\text{R}10}$~verbunden.
-\end{exe}
-
-For the durational analyses, constituents were automatically labeled
-by the \emph{Aligner} tool \citep{Rapp98}, and the
-obtained values were manually corrected afterwards. For the targets,
-two-factorial \acros{anova} with the factors \acro{Quantifier} (\emph{all}
-vs.~\emph{exactly one}) and \acro{Prosody} (accented vs.~unaccented) were
-carried out. For the preference-related controls, we carried out
-one-factorial \acros{anova} with the factor \acro{Prosody} (early
-boundary, late boundary, neutral prosody). F0 values were extracted by
-means of special Praat scripts
-(\url{http://www.fon.hum.uva.nl/praat/}). For the present analyses,
-differences between minimal and maximal F0 values for each region or
-word were calculated. Again, two-factorial \acros{anova} were carried
-out for statistical comparison of the target sentences, and one-factorial
-\acros{anova} were carried out for preference-related controls.
-
-\paragraph{Targets.} 
-Differences between maximal and minimal F0 values for each of the
-single words in the sentence are depicted in
-Figure~\ref{fig:minmax_targets}. As expected, accented
-determiners showed a larger F0 range compared to unaccented versions,
-an effect which was confirmed by statistical analyses (effects on
-the determiner: \acro{Prosody}: \emph{F}=94.8; \emph{p}<.001); 
-Interaction of \acro{Quantifier} and \acro{Prosody}: \emph{F}=13.7; 
-\emph{p}<.01). The observed interaction indicates that these differences
-are even more pronounced in the \as-condition.
-
-\begin{figure}[]
-	\centering
-	\subfloat[][\as-sentences]{
-          \begin{tikzpicture}[scale=0.75]
-  \begin{axis}[
-    cycle list name = mylist,
-    legend pos = north west,
-    ymajorgrids,
-    ymax = 250,
-    y = 0.5,
-    x tick label style = {rotate = 50, anchor = east},
-    xtick = data,
-    xticklabels = {alle,diese,N1,sind,mit,einigen,ihrer,N2,verbunden}
-    ]
-    \addplot+[line width = 1.3pt] coordinates {
-      (0 ,17.6)
-      (1 ,27.4)
-      (2 ,82.6)
-      (3 ,32.6)
-      (4 ,62.4)
-      (5 ,211.3333333)
-      (6 ,57.6)
-      (7 ,36.66666667)
-      (8 ,47.13333333)};
-
-  \addplot+[line width = 1.3pt] coordinates {
-        (0 ,19.6        )
-        (1 ,36.46666667 )
-        (2 ,115.1333333 )
-        (3 ,60.6        )
-        (4 ,46          )
-        (5 ,69.86666667 )
-        (6 ,46.66666667)
-        (7 ,71.4)
-        (8 ,61.46666667)};
-
-      \legend{accented, neutral}
-  \end{axis}
-\end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_ae.png}}
-	    \label{fig:minmax_ae}
-	}
-	\subfloat[][\es-sentences]{
-\begin{tikzpicture}[scale=0.75]
-  \begin{axis}[
-    cycle list name = mylist,
-    legend pos = north west,
-    ymajorgrids,
-    ymax = 250,
-    y = 0.5,
-    x tick label style = {rotate = 50, anchor = east},
-    xtick = data,
-    xticklabels = {genau,einer,dieser,N1,ist,mit,einigen,seiner,N2,verbunden}
-    ]
-    \addplot+[line width = 1.3pt] coordinates {
-        (     0 , 59.06666667 )
-        (     1 , 46.26666667 )
-        (     2 , 19          )
-        (     3 , 67.6        )
-        (     4 , 17.6        )
-        (     5 , 39.8        )
-        (     6 , 174.9333333 )
-        (     7 , 30.46666667 )
-        (     8 , 32.46666667 )
-        (     9 , 42.33333333 )};
-
-  \addplot+[line width = 1.3pt] coordinates {
-        (0 , 30.21428571 )
-        (1 , 34.21428571 )
-        (2 , 17.07142857 )
-        (3 , 93.78571429 )
-        (4 , 28.64285714 )
-        (5 , 67.64285714 )
-        (6, 75.5        )
-        (7 , 25.71428571 )
-        (8 , 54.85714286 )
-        (9 , 55)};
-
-      \legend{accented, neutral}
-
-  \end{axis}
-\end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_ge.png}}
-	    \label{fig:minmax_ge}
-	}
-	\caption[]{Differences between minimal and maximal F0 values (in Hz) for 
-	the single regions for \as-sentences (a) and \es-sentences (b).}
-	\label{fig:minmax_targets}
-\end{figure}
-
-\begin{figure}[]
-	\centering
-	\subfloat[][\as-sentences]{ 
-\begin{tikzpicture}[scale=0.75]
-  \begin{axis}[
-    cycle list name = mylist,
-    legend pos = north west,
-    ymajorgrids,
-    ymax = 800,
-    ymin = 0,
-    y = 0.125,
-    x tick label style = {rotate = 50, anchor = east},
-    xtick = data,
-    xticklabels = {alle,diese,N1,sind,mit,einigen,ihrer,N2,verbunden}
-    ]
-    \addplot+[line width = 1.3pt] coordinates {
-      (0 ,225.8333333)
-      (1 , 245.3333333 )
-      (2 , 397         )
-      (3 , 172.3333333 )
-      (4 , 230.1666667 )
-      (5 , 445.8333333 )
-      (6, 199.6666667)
-      (7, 503)
-      (8 ,722 )
-    };
-
-  \addplot+[line width = 1.3pt] coordinates {
-        (0 , 216.9212    )
-        (1 , 234.6666667 )
-        (2 , 414.6666667 )
-        (3 , 175.5       )
-        (4 , 170.5       )
-        (5 , 422         )
-        (6 , 194.6666667 )
-        (7 , 494.6666667 )
-        (8 , 748)
-};
-
-      \legend{accented, neutral}
-
-  \end{axis}
-\end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_ae.png}}
-	    \label{fig:duration_ae}
-	}
-	\subfloat[][\es-sentences]{
-          \begin{tikzpicture}[scale=0.75]
-  \begin{axis}[
-    cycle list name = mylist,
-    legend pos = north west,
-    ymajorgrids,
-    ymax = 800,
-    ymin = 0,
-    y = 0.125,
-    x tick label style = {rotate = 50, anchor = east},
-    xtick = data,
-    xticklabels = {genau,einer,dieser,N1,ist,mit,einigen,seiner,N2,verbunden}
-    ]
-    \addplot+[line width = 1.3pt] coordinates {
-(       0 , 307         )
-(       1 , 256         )
-(       2 , 128.6666667 )
-(       3 , 398.6666667 )
-(       4 , 164.6666667 )
-(       5 , 226.6666667 )
-(       6 , 420.6666667 )
-(       7 , 235.3333333 )
-(       8 , 494.6666667 )
-(       9 , 704.6666667 )
-    };
-
-  \addplot+[line width = 1.3pt] coordinates {
-(0 , 285.8333333 )
-(1 , 244.6666667 )
-(2 , 128         )
-(3 , 400         )
-(4 , 152.6666667 )
-(5 , 170         )
-(6 , 383.3333333 )
-(7 , 249.3333333 )
-(8 , 494.6666667 )
-(9 , 764.6666667 )
-};
-
-      \legend{accented, neutral}
-
-  \end{axis}
-\end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_ge.png}}
-	    \label{fig:duration_ge}
-	}
-	\caption[]{Durational values (in ms) for 
-	the single regions for \as-sentences (a) and \es-sentences (b).}
-	\label{fig:duration_targets}
-\end{figure}
-
-Figure~\ref{fig:duration_targets} shows the durational values for each
-of the single regions in the sentence.  Though descriptively small,
-the duration of accented determiners was significantly increased as
-opposed to their non-accented counterparts (effects on the determiner:
-\acro{Quantifier}: \emph{F}=31.4; \emph{p}<.001; \acro{Prosody}:
-\emph{F}=23.8; \emph{p}<.001).  A list of the statistical results of
-each sentential region is provided in
-Appendix~\ref{sec:audit-sent-mater} (F0 values:
-Table~\ref{tab:table-B}; durational values: Table~\ref{tab:table-A}).
-
-\paragraph{Preference-related controls.} 
-Differences between maximal and minimal F0 values for each of the
-single words in the sentence as well as durational values are depicted in
-Figure~\ref{fig:acoustics_fi}. As is
-evident, the largest durational and F0 differences were
-realized at the boundary regions (i.e. Region 5 and Region
-7).
-
-\begin{figure}[t]
-	\centering
-	\subfloat[][F0 values]{ 
-\begin{tikzpicture}[scale=0.75]
-  \begin{axis}[
-    cycle list name = mylist,
-    legend pos = north west,
-    ymajorgrids,
-    ymax = 250,
-    ymin = 0,
-    y = 0.55,
-    x tick label style = {rotate = 50, anchor = east},
-    xtick = data,
-    xticklabels = {D1,N1,ist,mit,N2,und,N3,mit,N4,verbunden}
-    ]
-    \addplot+[line width = 1.3pt] coordinates {
-(       0 ,27.65517241 )
-(       1 ,91.20689655 )
-(       2 ,32.51724138 )
-(       3 ,27.20689655 )
-(       4 ,53.72413793 )
-(       5 ,19.5862069  )
-(       6 ,210.8965517 )
-(       7 ,15.48275862 )
-(       8 ,66.06896552 )
-(       9 ,68.72413793 )
-    };
-
-  \addplot+[line width = 1.3pt] coordinates {
-(0 ,23.48148148) 
-(1 ,63.07407407) 
-(2 ,13.7037037 ) 
-(3 ,22.7037037 ) 
-(4 ,197.0740741) 
-(5 ,34.03703704) 
-(6 ,95.37037037) 
-(7 ,15.22222222) 
-(8 ,52.18518519) 
-(9 ,123        ) };
-
-  \addplot+[line width = 1.3pt] coordinates {
-(0, 31.7        )
-(1, 80.2        )
-(2, 24.46666667 )
-(3, 31.2        )
-(4, 135.8333333 )
-(5, 54.46666667 )
-(6, 86.96666667 )
-(7, 16.76666667 )
-(8, 51.4        )
-(9, 62.53333333 )};
-
-      \legend{\textsc{ec},\textsc{lc},neutral}
-
-  \end{axis}
-\end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/minmax_fi.png}}
-	    \label{fig:acoustics_fi}
-	}
-	\subfloat[][Duration]{
-\begin{tikzpicture}[scale=0.75]
-  \begin{axis}[
-    cycle list name = mylist,
-    legend pos = north west,
-    ymajorgrids,
-    ymax = 1400,
-    ymin = 0,
-    y = 0.1,
-    x tick label style = {rotate = 50, anchor = east},
-    xtick = data,
-    xticklabels = {D1,N1,ist,mit,N2,und,N3,mit,N4,verbunden}
-    ]
-    \addplot+[line width = 1.3pt] coordinates {
-(0  , 105.75      )
-(1  , 332.3333333 )
-(2  , 168         )
-(3  , 135.3333333 )
-(4  , 561.3333333 )
-(5  , 143.3333333 )
-(6  , 1183.666667 )
-(7  , 167         )
-(8  , 384.6666667 )
-(9  , 691.3333333 )
-    };
-
-  \addplot+[line width = 1.3pt] coordinates {
-(0  , 100.75      )
-(1  , 306.6666667 )
-(2  , 167         )
-(3  , 139.6666667 )
-(4  , 1268.333333 )
-(5  , 176.3333333 )
-(6  , 535.3333333 )
-(7  , 150.3333333 )
-(8  , 381         )
-(9  , 681.3333333 )
-};
-
-  \addplot+[line width = 1.3pt] coordinates {
-(0  , 98.08333333 )
-(1  , 313.6666667 )
-(2  , 169.3333333 )
-(3  , 141.3333333 )
-(4  , 642.6666667 )
-(5  , 150         )
-(6  , 557.3333333 )
-(7  , 151         )
-(8  , 402.6666667 )
-(9  , 730)
-};
-
-      \legend{\textsc{ec},\textsc{lc},neutral}
-
-  \end{axis}
-\end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../pictures/paper/duration_fi.png}}
-	    \label{fig:duration_fi}
-	}
-	\caption[]{Differences between minimal and maximal F0 values (in Hz) (a) as well
-	as durational values (in ms)(b) for 
-	the single regions  .}
-	\label{fig:acoustics_fi}
-\end{figure}
-
-Statistical analyses for F0 on Region 5 reveal that all prosodic
-realizations (\emph{neutral} vs. (\emph{early boundary}
-vs. (\emph{late boundary})) differ significantly from each other
-(effect of \acro{Prosody}: \emph{F}=129.3; \emph{p}<.001; all single
-comparisons \emph{p}<.001). On Region 7, F0 analyses again show a main
-effect of \acro{Prosody}: \emph{F}=132.5; \emph{p}<.001. However, the
-comparison between neutral prosody and a \emph{late boundary} did not
-reach significance (\emph{p}>.2). Finally, durational analyses reveal
-that all prosodic realizations (\emph{neutral} vs. (\emph{early
-  boundary} vs. (\emph{late boundary})) differ significantly from each
-other (Region 5: effect of \acro{Prosody}: \emph{F}=819.5;
-\emph{p}<.001; all single comparisons \emph{p}<.001; Region 7: effect
-of \acro{Prosody}: \emph{F}=1920.3; \emph{p}<.001; all single
-comparisons \emph{p}<.001.) A list of the statistical results of each
-sentential region is provided in Appendix~\ref{sec:audit-sent-mater}
-(F0 values: Table~\ref{tab:table-D}; durational values:
-Table~\ref{tab:table-C}).
-
-In sum, our speaker reliably
-produced (i) differences in accent realization for the target
-sentences and (ii) the expected boundary realizations for the
-preference-related controls. Whereas accented elements clearly
-differed from their unaccented counterpart by showing an increase in
-duration and F0 range, prosodic boundaries for our preference-related
-controls were realized by pre-final lengthening (i.e., an increase in F0
-and duration at the position preceding the boundary).
-
-\paragraph{Pictures.}
-The visual sequences accompanying each sentence consisted of pictures
-like in Figures~\ref{fig:exseqAS}--\ref{fig:exlc}. In each picture,
-four alternative sub-scenarios were presented, in which an icon was
-surrounded by six geometrical shapes. Depending on the sentence
-material, shapes and icons differed across sentence types and
-conditions. For example, in our target conditions, 4 identical icons
-were surrounded by geometrical shapes that were all of the same type,
-whereas various icons and surrounding elements were used in each
-sequence of the preference-related control structures (see
-Section~\ref{sec:design} for more detailed exposition). Pictures for
-unrelated fillers had critical positions at random uncovering stages,
-including cases where no uncovering was needed for a truth-value
-judgement.
-
-\paragraph{Lists.}
-Experimental items and preference-related controls were evenly
-distributed across lists. For the \as- and \es-sentences together with
-their respective controls, five lists were used employing a Latin
-square design. Picture sentence-pairs for the preference-related
-controls were spread across eight lists. Each target list was combined
-with each list from the preference-related controls, thus yielding to
-a total of forty lists. The thirty unrelated filler items were
-included in each of these resulting lists.
-
-\subsubsection{Participants.}
-
-Forty native speakers of German took part in our study, none of which
-had any prior exposure to logic or formal semantics. We excluded two
-participants due to insufficient performance on controls ($\le 60\%$
-correct answers).
-
-\subsection{Results}
-\label{sec:results}
-
-In the following, we will report the results for targets and
-preference-related controls separately. After providing the
-descriptive results, we present statistical analyses using log-linear
-models. We complement these with a Bayesian analysis that is sensitive
-to the sequential nature of the incremental verification task and
-probes specifically into the preference relations between candidate
-readings.
-
-\paragraph{Target conditions and positional controls.}
-Performance on positional controls was overwhelmingly correct (90\%
-correct responses on average with a variance of 0.012) indicating that
-participants understood the task and were able to give correct
-truth-value judgments at the adequate point in a sequence. In
-general, they were not affected by inessential features of the picture
-materials or general response biases.
-
-% \begin{figure}[t] 
-% \centering
-
-% \includegraphics[width=0.9\textwidth]{positional_answers_critical.pdf}
-
-% \caption{Answers for the \as- and \es-sequences. Bars show the total
-%   number of \emph{yes} (up) and \emph{no} judgments (down) collected
-%   at each step during a sequence. E.g., we recorded a total of 103
-%   \emph{yes} judgments at the third position in the \as-sequence with
-%   neutral intonation, which corresponds to 103 answers that were
-%   classified as \emph{literal} answers. Notice that the \as-condition
-%   had seven steps, the \es-condition only five.}
-% \label{fig:JudgmentsK2}
-% \end{figure}
-%
-
-\begin{table}
-  \centering
-  \begin{tabular}{lcccccccc@{\hskip 0.6cm}cccc}
-    && \multicolumn{7}{c}{truth value at step}
-    & \multicolumn{4}{c}{classification}
-    \\ \cmidrule(l){3-9} \cmidrule(r){10-13}
-    condition &
-    & 1
-    & 2
-    & 3
-    & 4
-    & 5
-    & 6
-    & 7
-    & \lit
-    & \loc
-    & \glb
-    & err \\ \midrule
-    \as-ntr 
-    & T & 1 & 1 & \textbf{103} & 2 & \textbf{0} & 0 & 2 
-    & 103 & 3 & 0 & 8 \\
-    & F & 0 & 0 & 0 & 0 & 2 & 0 & \textbf{3} \\ 
-    \addlinespace[0.25cm]
-    \as-acc
-    & T & 0 & 1 & \textbf{99} & 2 & \textbf{2} & 0 & 1 
-    & 99 & 8 & 5 & 5 \\
-    & F & 0 & 0 & 1 & 0 & 0 & 0 & \textbf{8} \\
-    \addlinespace[0.25cm]
-    \es-ntr
-    & T & 0 & 11 & 3 & 1 & \textbf{14} & - & - 
-    & 78 & 14 & 0 & 22 \\
-    & F & 0 & \textbf{0} & \textbf{78} & 5 & 2 & - & - \\
-    \addlinespace[0.25cm]
-    \es-acc
-    & T & 0 & 10 & 3 & 0 & \textbf{16} & - & - 
-    & 78 & 16 & 0 & 20 \\
-    & F & 0 & \textbf{0} & \textbf{78} & 5 & 2 & - & -
-  \end{tabular}
-  \caption{Observed truth-value judgments in critical conditions. The
-    left-hand part of the table shows the number of \emph{true} and
-    \emph{false} responses obtained at each step in the sequence. The
-    right-hand part shows the count for our imposed classification
-    scheme. The answer counts indicative of relevant readings are
-    given in bold-face on the left-hand side.}
-  \label{tab:count_data_CC}
-\end{table}
-
-%
-% \begin{table}[h]
-% \centering
-
-% \begin{tabular}{lccccc}
-%   condition & position & \multicolumn{4}{c}{response type} \\ \cmidrule(r){3-6}
-%   && \emph{literal} & \emph{local} & \emph{global} & \emph{error} \\
-%   \midrule \addlinespace[0.15cm]
-%   \textbf{\as neutral} 
-%   & Pos 1 & 35 &  0 & 0 & 3 \\
-%   & Pos 2 & 35 &  1 & 0 & 2 \\
-%   & Pos 3 & 33 &  2 & 0 & 3 \\ \addlinespace[0.15cm]
-%   & \textbf{Total} & \textbf{103} &  \textbf{3} & \textbf{0} &
-%   \textbf{8} \\
-%   \addlinespace[0.25cm]
-%   \textbf{\as accented} 
-%   & Pos 1 & 33 &  2 & 1 & 2 \\
-%   & Pos 2 & 33 &  3 & 1 & 1 \\
-%   & Pos 3 & 33 &  3 & 0 & 2 \\ \addlinespace[0.15cm]
-%   & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2} &
-%   \textbf{5} \\
-%   \addlinespace[0.25cm]
-%   \textbf{\es neutral} 
-%   & Pos 1 & 26 &  5 & 0 & 7 \\
-%   & Pos 2 & 26 &  3 & 0 & 9 \\
-%   & Pos 3 & 26 &  6 & 0 & 6 \\ \addlinespace[0.15cm]
-%   & \textbf{Total} & \textbf{78} &  \textbf{14} & \textbf{0} &
-%   \textbf{22} \\
-%   \addlinespace[0.25cm]
-%   \textbf{\es accented} 
-%   & Pos 1 & 26 &  6 & 0 & 6 \\
-%   & Pos 2 & 24 &  5 & 0 & 9 \\
-%   & Pos 3 & 28 &  5 & 0 & 5 \\ \addlinespace[0.15cm]
-%   & \textbf{Total} & \textbf{78} &  \textbf{16} & \textbf{0} &
-%   \textbf{20}
-% \end{tabular}
-
-% \caption{Contingency table of classified responses for the critical
-%   conditions. The factor position encodes whether participants saw the
-%   condition in question for the first, second or third time during the
-%   whole experiment.}
-% \label{tab:CC-ContingencyTable}
-% \end{table}
-%
-
-Judgements obtained for the four target conditions are listed in
-Table~\ref{tab:count_data_CC}. We coded these answers as {\it
-  literal}, {\it global} or {\it local} if they were as expected under
-one of these readings and as {\it error} if not. The majority of
-answers are indicative of a literal reading (\as-neutral: 90.4\%,
-\as-accented: 86.8\%, \es-neutral: 68.4\%, \es-accented: 68.4\%). Only
-two answers across all critical conditions fall into the category
-indicative of global readings. Judgements indicative of local
-readings, on the other hand, are more frequent (\as-neutral: 2.6\%,
-\as-accented: 7.0\%, \es-neutral: 12.3\%, \es-accented: 14.0\%).
-
-The number of responses that fell out of our classification scheme
-differs substantially between \as- and \es-conditions. There are 7.0\%
-/ 4.4\% unclassifiable judgements in the neutral / accented
-\as-conditions, but 19.3\% / 17.6\% in the neutral / accented
-\es-conditions respectively. A look at the left-hand side of
-Table~\ref{tab:count_data_CC} reveals that there is some systematicity
-in 'error' answers. Most answers that we classified as 'errors' have a
-plausible explanation: random errors, a handful of mistakes resulting
-from confusing buttons for \emph{true} and \emph{false} and a few
-'spill-over errors' where participants gave responses one position too
-late. There is one notable exception, though. A substantial number of
-\emph{true} responses were given at the second position of
-\es-sequences (9.7\% / 8.8\%) which is shown in
-Figure~\ref{fig:exseqES2}. Although this position in the sequence is
-the critical position to reveal a global reading, the latter would be
-indicated by a \emph{false} response. It appears that subjects read
-\es-sentences as if the upward-monotonic quantifier \emph{exactly one}
-was a monotonic \emph{at least one}, without pragmatic enrichment of
-\emph{some}. 16 out of the total 21 answers in this category come from
-5 subjects, while the remaining 5 were single answers by 5 different
-subjects.
-% subjects 1, 9, 12, 21, 84
-This suggests that at least for some subjects non-monotonic
-quantifiers were problematic. (We will come back to this intriguing
-observation later in Section~\ref{sec:discussion-1}, where we suggest
-that a non-monotonic reading of \emph{exactly one} might also explain
-the high number of \emph{true} answers in step 5 of the
-\es-conditions.)
-
-We fitted generalized linear models to the count data in
-Table~\ref{tab:count_data_CC}, using factors \textsc{Condition} with
-levels \as and \es, \textsc{Accent} with levels \emph{neutral} and
-\emph{accented}, and \textsc{Trial} with levels 1 through 3 (coding
-whether it was the first, second or third time that a participant saw
-a critical condition during the experiment) to predict the dependent
-factor \textsc{Reading} with levels \emph{literal}, \emph{local}, and
-\emph{other}. The latter lumps \emph{global} and \emph{error}
-responses together, because otherwise we would not have enough cell
-counts to apply log-linear regression. We determined the ``best''
-model of the data by a gradient search over hierarchical models in
-terms of AICs, starting from the saturated model. The best model takes
-main factors \textsc{Reading} and \textsc{Condition} into account, as
-well as the interaction term \textsc{Reading:Condition} ($\chi^2 =
-17.19$, $df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$
-of the saturated model)). Crucially, factors \textsc{Trial} and
-\textsc{Accent} were dropped in the best model. This suggests that
-response patterns only depend on the type of the sentence, but that
-there were no learning or fatigation effects and that accentuation did
-not influence answer patterns significantly (at this level of
-abstraction).
-
-\begin{table}
-  \centering
-  \begin{tabular}{lllll}
-    coefficient & estimate & std.~error & $z$-value & $\Pr(>|z|)$ \\
-    \midrule
-    \textsc{Intercept} & 0.916  &  0.258 &  3.49  & < 0.001 \\
-    \textsc{Reading}.\emph{literal} & 2.600 &   0.268 & 9.716 & < 0.001 \\
-    \textsc{Reading}.\emph{local} & -0.310  &  0.397 & -0.781 &
-    0.435 \\
-    \textsc{Condition}.\es & 1.030 &  0.301 & 3.423 &  < 0.001 \\
-    \textsc{Reading}.\emph{literal}:\textsc{Condition}.\es & -1.288 &
-    0.319 & -4.036 &  < 0.001 \\
-    \textsc{Reading}.\emph{local}:\textsc{Condition}.\es & -0.026 &
-    0.463 &  -0.0579 &  0.955
-  \end{tabular}
-  \caption{Coefficients of the ``best'' log-linear model for the count
-    data in Table~\ref{tab:count_data_CC}.}
-  \label{tab:Coefficients-CC}
-\end{table}
-
-Inspection of the coefficients of the ``best'' model in
-Table~\ref{tab:Coefficients-CC} suggests that the distinction between
-levels \emph{local} and \emph{other} in factor \textsc{Reading} might
-not be necessary: factor levels \emph{local} do not cause a
-significant shift in counts, given reference level \emph{false}. In
-order to test whether there is support for the postulation of local
-readings, we therefore compared the previous ``best'' model to a
-model that only differs from the former in that it subsumes the level
-\emph{local} of factor \textsc{Reading} under level \emph{other} as
-well \citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model
-comparison reveals that there is no significant improvement in
-explanatory power ($Pr(|\chi|) = 0.2689$) of the more complex model
-that includes the level \emph{local} (residual df=30, residual
-deviance = 10.497) over the simpler model without this level (residual
-df=32, residual deviance = 13.124, AIC=157.268).
-
-This latter analysis suggests that our data does not provide strong
-evidence for the maintenance of belief in local readings in our
-setting. The regression analysis tells us that the number of errors
-and the number of local readings were similar in all conditions. But
-the distribution of answers in Table~\ref{tab:count_data_CC} shows
-that small error counts occur at many different steps, whereas we do
-see a concentrated rise in answers at the critical position for local
-readings. Also, so far we have not taken into account the sequential
-structure of our task. This is where preference-related controls
-are relevant.
-
-\paragraph{Preference-related controls.} Positional answers for our
-preference-related control conditions are shown in
-Table~\ref{tab:count_data_TF}.\fn{We removed 19 data points for the
-  \ec-conditions because of a coding mistake that presented subjects
-  with incongruent sentence-picture pairs. Including these and
-  classifying them as \emph{errors} does not change the qualitative
-  results of the reported analyses.} Judgments were coded as \ec or as
-\lc if they were as expected under one of these readings, and as
-\emph{error} if they were not. As expected, most answers classify as
-\lc-readings, fewer as \ec-readings. Moreover, intonation does seem to
-have the expected effect as well: as compared to neutral phrasing,
-\lc-cueing intonation increases the count for \lc-readings, while
-\ec-cueing prosody increases the count for \ec-readings. If we compare
-the number of \lc- or \ec-readings for each intonation type across
-sequences, we see that there are always more answers indicative of the
-relevant readings when that reading can be judged later in the
-sequence. This suggests a general tendency to answer later in the
-sequence, rather than at the earliest possible step.
-
-\begin{table}
-  \centering
-  \begin{tabular}{lcccccccc@{\hskip 0.6cm}ccc}
-    && \multicolumn{7}{c}{truth value at step}
-    & \multicolumn{3}{c}{classification}
-    \\ \cmidrule(l){3-9} \cmidrule(r){10-12}
-    condition &
-    & 1
-    & 2
-    & 3
-    & 4
-    & 5
-    & 6
-    & 7
-    & \lc
-    & \ec
-    & err \\ \midrule
-    \lc-ntr 
-    & T & 0 & 0 & \textbf{87} & 1 & 0 & 9 & 0 
-    & 87 & 32 & 13 \\
-    & F & 0 & 0 & 3 & 0 & 0 & \textbf{32} & 0 \\
-    \addlinespace[0.25cm]
-    \lc-\lc-cue
-    & T & 0 & 0 & \textbf{108} & 1 & 1 & 7 & 0 
-    & 108 & 16 & 10 \\
-    & F & 0 & 0 & 1 & 0 & 0 & \textbf{16} & 0 \\
-    \addlinespace[0.25cm]
-    \lc-\ec-cue
-    & T & 0 & 0 & \textbf{51} & 4 & 0 & 7 & 0 
-    & 51 & 59 & 25 \\
-    & F & 2 & 1 & 7 & 0 & 0 & \textbf{59} & 1 \\
-    \addlinespace[0.25cm]
-    \ec-ntr
-    & T & 0 & 0 & 0 & 0 & \textbf{92} & - & - 
-    & 92 & 22 & 13 \\
-    & F & 1 & 0 & \textbf{22} & 6 & 6 & - & - \\
-    \addlinespace[0.25cm]
-    \ec-\lc-cue
-    & T & 0 & 0 & 0 & 0 & \textbf{112} & - & - 
-    & 112 & 13 & 4 \\
-    & F & 0 & 1 & \textbf{13} & 1 & 2 & - & - \\
-    \addlinespace[0.25cm]
-    \ec-\ec-cue
-    & T & 0 & 0 & 0 & 0 & \textbf{65} & - & - 
-    & 65 & 31 & 30 \\
-    & F & 2 & 0 & \textbf{31} & 8 & 20 & - & - \\
-    \addlinespace[0.25cm]
-
-  \end{tabular}
-  \caption{Observed truth-value judgments in preference-related controls.}
-  \label{tab:count_data_TF}
-\end{table}
-
-% \begin{figure}[]
-% \centering
-
-%  \subfloat[][\LC-sequence]{
-
-% \includegraphics[width=0.9\textwidth]{positional_answers_TF_LC.pdf}
-% }
-
-%  \subfloat[][\EC-sequence]{
-
-% \includegraphics[width=0.9\textwidth]{positional_answers_TF_EC.pdf}
-% }
-
-% \caption{Answers for \lc-sequences and \ec-sequences. \emph{True}
-%   judgements are plotted upwards for each step in the sequence,
-%   \emph{false} judgements downwards.}
-% \label{Fig:TF_judgments}
-% \end{figure}
-
-% \begin{table}[]
-% \centering
-
-% \begin{tabular}{lcccc}
-%   condition & position & \multicolumn{3}{c}{response type} \\ \cmidrule(r){3-5}
-%   && \emph{LC} & \emph{EC} & \emph{error}  \\
-%   \midrule \addlinespace[0.15cm]
-%   \textbf{\lc neutral} 
-%   & Pos 1 & 27 &  7  & 4 \\
-%   & Pos 2 & 23 &  11 & 4 \\
-%   & Pos 3 & 26 &  9  & 3 \\ \addlinespace[0.15cm]
-%   & \textbf{Total} & \textbf{76} &  \textbf{27} & \textbf{11}  \\
-%   \addlinespace[0.25cm]
-%   \textbf{\lc with \lc cue} 
-%   & Pos 1 & 26 &  7 & 5  \\
-%   & Pos 2 & 31 &  5 & 2  \\
-%   & Pos 3 & 33 &  3 & 2  \\ \addlinespace[0.15cm]
-%   & \textbf{Total} & \textbf{90} &  \textbf{15} & \textbf{9}  \\
-%   \addlinespace[0.25cm]
-%   \textbf{\lc with \ec cue} 
-%   & Pos 1 & 14 &  17 & 7  \\
-%   & Pos 2 & 15 &  16 & 7  \\
-%   & Pos 3 & 15 &  17 & 6  \\ \addlinespace[0.15cm]
-%   & \textbf{Total} & \textbf{44} &  \textbf{50} & \textbf{20}  \\
-%   \addlinespace[0.25cm]
-%   \textbf{\ec neutral} 
-%   & Pos 1 & 22 &  6 & 5  \\
-%   & Pos 2 & 28 &  6 & 4  \\
-%   & Pos 3 & 29 &  7 & 2  \\ \addlinespace[0.15cm]
-%   & \textbf{Total} & \textbf{79} &  \textbf{19} & \textbf{11}  \\
-%   \addlinespace[0.25cm]
-%   \textbf{\ec with \lc cue} 
-%   & Pos 1 & 30 &  5 & 1  \\
-%   & Pos 2 & 32 &  5 & 0  \\
-%   & Pos 3 & 31 &  3 & 2  \\ \addlinespace[0.15cm]
-%   & \textbf{Total} & \textbf{93} &  \textbf{13} & \textbf{3}  \\
-%   \addlinespace[0.25cm]
-%   \textbf{\ec with \ec cue} 
-%   & Pos 1 & 19 &  10 & 7  \\
-%   & Pos 2 & 19 &  7  & 9  \\
-%   & Pos 3 & 19 &  7  & 11  \\ \addlinespace[0.15cm]
-%   & \textbf{Total} & \textbf{57} &  \textbf{24} & \textbf{27}  \\
-% \end{tabular}
-
-% \caption{Contingency table of classified responses for the
-%   preference-related controls. As before, the factor position encodes
-%   whether participants saw the condition in question for the first,
-%   second or third time during the whole experiment.}
-% \label{tab:CC-ContingencyTable-TF}
-% \end{table}
-
-There are only very few answers that appear to be random
-mistakes. Some answers in the `error' category are plausibly
-`spill-over errors', where participants gave answers one step too
-late. But on top of that, a substantial number of `error' answers
-occurs on critical positions. For example, in the \lc-sequence there
-are 23 \emph{true} answers at step 6 where \emph{false} answers would
-be taken as indicative of \ec-readings. In the \ec-sequence there are
-28 \emph{false} answers at step 5 where \emph{true} answers would be
-taken as indicative of \lc-readings. Finally, intonation patterns that
-cue dispreferred \ec-readings seem to have led to more mistakes than
-other intonation patterns.
-
-As for the critical conditions, we computed logistic regression models
-including factors \textsc{Reading} with levels \lc, \ec and
-\emph{error}, \textsc{Accent} with levels \emph{neutral},
-\emph{\lc-cue} and \emph{\ec-cue}, \textsc{Trial} with levels 1 to
-3, and \textsc{Condition} with levels \lc and \ec for the picture
-sequences. Starting search from the saturated model along a gradient
-of decreasing AICs, we find that the ``best'' model relies on main
-effects of \textsc{Reading}, \textsc{Accent} and \textsc{Condition}
-and two two-way interactions \textsc{Reading:Condition} and
-\textsc{Reading:Accent} ($\chi^2=18.34$, $df=42$, $p=0.99$,
-$AIC=256.63$ (compared to $AIC=322.3$ of the saturated model)). Factor
-\textsc{Trial} was dropped from the best model, suggesting that
-answer patterns are stable over the duration of the experiment. Unlike
-for the critical conditions, factor \textsc{Accent} is retained, and
-it interacts with \textsc{Reading}, suggesting that prosodic cues
-significantly influenced the dominant reading.
-
-\begin{table}
-  \centering
-  \begin{tabular}{lllll}
-    coefficient & estimate & std.~error & $z$-value & $\Pr(>|z|)$ \\
-    \midrule
-    \textsc{Intercept} & 2.119  &   0.162 & 13.079   & < 0.001 \\
-    \textsc{Reading}.\emph{error} & -0.343 &  0.259 & -1.328 &  0.184
-    \\
-    \textsc{Reading}.\lc & 0.526 &  0.202 & 2.607 & < 0.01 \\
-    \textsc{Condition}.\lc & 0.497 &  0.170  & 2.929 & < 0.01 \\
-    \textsc{Accent}.\lc & -1.054 & 0.242 & -4.354 & < 0.001 \\
-    \textsc{Accent}.\emph{neutral} & -0.112 & 0.180 &  -0.626 &  0.531
-    \\
-    \textsc{Reading}.\emph{error}:\textsc{Condition}.\lc & -0.521 &
-    0.280 & -1.87 & 0.062 \\
-    \textsc{Reading}.\lc:\textsc{Condition}.\lc & -0.583 & 0.195 &
-    -2.997 &  < 0.01 \\
-    \textsc{Reading}.\emph{error}:\textsc{Accent}.\lc & -0.103 &
-    0.422 &  -0.245 & 0.807  \\
-    \textsc{Reading}.\lc:\textsc{Accent}.\lc & 1.657 &  0.279 & 5.943
-    & < 0.001 \\
-    \textsc{Reading}.\emph{error}:\textsc{Accent}.\emph{neutral} & 0.112 &
-    0.299  &  0.375 &  0.708 \\
-    \textsc{Reading}.\lc:\textsc{Accent}.\emph{neutral} & 1.065  &
-    0.222 &  4.800 & < 0.001 \\
-  \end{tabular}
-  \caption{Coefficients of the ``best'' log-linear model for the count
-    data in Table~\ref{tab:count_data_TF}.}
-  \label{tab:Coefficients-TF}
-\end{table}
-
-Closer examination of the coefficients of the fitted model, shown in
-Table~\ref{tab:Coefficients-TF}, reveals that there were significantly
-more \ec-readings in the \lc-condition than in the \ec-condition, and
-more \lc-readings in the \ec-condition than in the \lc-condition. This
-is evident from the significant \emph{negative} deviation from the
-baseline of \ec-readings in the interaction coefficient for
-\textsc{Reading}.\lc:\textsc{Condition}.\lc. The log-linear model
-therefore indicates that there is a bias for late responses in a
-sequence. Given this, the number of local responses in critical
-conditions might be increased by a sequential bias to answer late. The
-following Bayesian analysis further probes into this matter in order
-to establish how strongly the sequence-effect might have emphasized
-local readings and, from there, whether we should uphold belief in
-local readings.
-
-\subsubsection{Probabilistic salience competition.}
-
-The previous regression-based analyses did not take the sequential
-nature of the task into account. The following paragraphs therefore
-spell out a generative Bayesian model which computes the
-likelihood of answer patterns for different latent relative saliencies
-of candidate readings and biases to answer early or late in a
-sequence. We use the data to estimate the posterior likelihood of
-these latent parameters to gain insight into the likely ordering
-relations over the strength of latent salience of candidate readings.
-
-\paragraph{The model.} We present a model that aims to capture the
-competition between candidate readings, all of which have a given
-latent level of relative salience, in the incremental verification
-task, where some readings can be judged before others. Take the
-AS-conditions with its three candidate readings. The relative strength
-between these is given by a probability vector $\myvec{p}^\text{as-n}
-=
-\tuple{p^\text{as-n}_{\text{lit}},p^\text{as-n}_{\text{loc}},p^\text{as-n}_{\text{glb}}}$. We
-think of $p^\text{as-n}_{\text{lit}}$, for instance, as the salience
-of the literal reading for \as-sentences with neutral prosody,
-relative to the global and local reading. If there were no potential
-effects of sequentiality and no errors (or other readings that we
-classify as errors), the vector $\myvec{p}^\text{as-n}$ would be our
-prediction of observed frequencies of answer patterns. We look at four
-such three-placed vectors for the critical conditions, one for each
-target sentence-intonation pair. For the preference-related control
-conditions, we look at three vectors $p^k =
-\tuple{p^{\text{k}}_{\text{\lc}}, p^{\text{k}}_{\text{\ec}}}$, where
-$k \in \set{\text{ntr}, \text{\lc-cue}, \text{\ec-cue}}$. These
-vectors give the relative salience of \lc- and \ec-readings for
-different types of intonation. The salience of readings is independent
-of the pictorial sequence. If there is a tendency to judge sentences
-earlier in the sequence, rather than later, that has to be attributed
-to the sequential bias.
-
-To add potential effects of sequentiality, consider bias factor $q \in
-[0;1]$. This bias is a global parameter held constant over all
-conditions, because we think of it as a general tendency to answer
-early or late in the incremental verification task. The bias factor
-captures whether there is a tendency to choose readings that appear
-earlier ($q > .5$) or later ($q <.5$) in the sequence. In the
-\as-sequences, the literal reading can be judged first, then the local
-and then the global reading. So we will assume that $p_{\text{lit}}$
-is multiplied by $q$, that $p_{\text{loc}}$ is multiplied by $(1-q)q$
-and that $p_{\text{glb}}$ is multiplied by $(1-q)^2$, when determining
-the eventual weights of readings.
-
-Finally, we also allow for mistakes. To keep things simple (no
-differential consideration for spill-overs, button mix-ups etc.), we
-assume that there is a fixed error rate $e^k \in [0;1]$ for each
-relevant condition $k$. We allow for different error rates for
-different conditions, because we want to allow for the possibility
-that some sentence types (e.g., non-monotonic quantifiers) or some
-kind of intonation (e.g., \ec-cues) might be harder to process. A
-decision can be wrong but incidentally coincide with an answer that is
-indicative of a relevant reading. Error rates multiply in proportion
-to the number of steps in a sequence: more choice, more chance to be
-wrong.
-
-Taking this together we calculate, for each pair $k$ of target
-sentence type and intonation type, a probability vector $\myvec{t}^k =
-\tuple{t^k_{\text{lit}},t^k_{\text{loc}},t^k_{\text{glb}},t^k_{\text{err}}}$
-with which we expect an answer to be classified as literal, local,
-global or as error. For example, for \as-sentences with neutral
-intonation, where literal can be judged before global before local, we
-get:
-\begin{align*}
-  t^{\text{as-n}}_{\text{lit}} & \propto q \
-  p^\text{as-n}_{\text{lit}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{loc}} & \propto (1-q)^2 \
-  p^\text{as-n}_{\text{loc}} + e^\text{as-n} \\
-  t^{\text{as-n}}_{\text{glb}} & \propto (1-q)q \
-  p^\text{as-n}_{\text{glb}} + e^\text{as-n} &   t^{\text{as-n}}_{\text{err}} &
-  \propto 12 e^\text{as-n}
-\end{align*}
-Two remarks. The vector $\myvec{t}^k$ should be normalized eventually,
-which is why `$\propto$' is used above instead of `$=$.' Also, the
-probability of error $t^{\text{as-n}}_{\text{err}}$ comes from the
-observation that there are 15 positions in total in an \as-sequence at
-which subjects can make an erroneous choice, but we have accounted for
-three of these already as adding to the count of answers indicative of
-relevant readings.
-
-Similarly, we compute a target probability $\myvec{t}^k =
-\tuple{t^k_{\text{late}},t^k_{\text{early}},t^k_{\text{err}}}$ for
-each preference-related control sentence under intonation $k$, taking
-into account which reading can be judged first and the length of the
-respective sequences.
-
-The full probabilistic model is visualized in
-Figure~\ref{fig:model_graph}. As indicated there, we assume largely
-uninformative priors. Any positional bias $q \in [0;1]$ is assumed to
-be equally likely. The error rates for each condition should be small,
-so we sample uniformly from interval $[0,.2]$. The biases
-$\myvec{p}_k$ are also determined uniformly at random, by sampling from a
-Dirichlet distribution with equal weights on all dimensions.
-
-\begin{figure}[]
-  \centering
-  \begin{tikzpicture}[node distance = 2cm, 
-    double distance = 2pt,
-    minimum size=1.25cm,
-    thick]
-
-    \node[rectangle, draw=black, fill=black!30] (obs)
-    {obs$_k$};
-
-    \node[rectangle, draw=black, fill=black!30,
-    right of = obs] (n) {$n_k$};
-
-    \node[below of = n, node distance= 1.5cm]
-    (anchor) {};
-
-    \node[left of = anchor, node distance= 0.95cm] (k) {$k \in
-      \set{\text{\as-ntr, \as-acc, \dots}}$};
-
-    \node[circle, double, draw=black,
-    above of = obs] (t) {$\myvec{t}_k$};
-
-    \node[circle, draw=black, 
-    above of = t] (p) {$\myvec{p}_k$};
-
-    \node[circle, draw=black, 
-    right of = p] (e) {$e_k$};
-
-    \node[circle, draw=black, 
-    left of = p] (q) {$q$};
-
-    \draw[->] (t)--(obs);
-
-    \draw[->] (n)--(obs);
-
-    \draw[->,shorten >=0.05cm] (q)--(t);
-
-    \draw[->,shorten >=0.05cm] (p)--(t);
-
-    \draw[->,shorten >=0.05cm] (e)--(t);
-
-    \begin{pgfonlayer}{background}
-       \node [rounded corners,
-       very thick,draw=black!40,fit={($(obs.south)+(0,-30pt)$) 
-                                 ($(n.east)+(+5pt,0)$) 
-                                 ($(e.north)+(0,+5pt)$) 
-                                 ($(p.west)+(-5pt,0)$)}] {};
-    \end{pgfonlayer}
-
-    \begin{scope}[xshift = 6.5cm, node distance = 1cm]
-
-      \node[] (obsd) {$\text{obs}_k \sim \text{Multinomial}(\myvec{t}_k,n_k)$};
-
-      \node[above of = obsd] (td) {$\myvec{t}_k = \text{as described
-          in text}$};
-
-      \node[above of = td] (pd) {$\myvec{p}_k \sim
-        \text{unbiased Dirichlet}$};
-
-      \node[above of = pd] (ed) {$e_k \sim \mathcal{U}(0,.2)$};
-
-      \node[above of = ed] (qd) {$q \sim \mathcal{U}(0,1)$};
-
-    \end{scope}
-
-  \end{tikzpicture}
-  \caption{Probabilistic graphical model. All nodes represent
-    variables, arrows represent functional relations between them.
-    Using conventions of \citet{LeeWagenmakers2013:Bayesian-Cognit},
-    the higher a node, the more latent it is. Square nodes represent
-    discrete-valued variables, circular nodes represent
-    continuous-valued variables. Gray nodes show the observable
-    variables. Values at double-lined nodes are derived
-    deterministically. The variables in the box are repeated for each
-    of the $k$ relevant cases.}
-  \label{fig:model_graph}
-\end{figure}
-
-\paragraph{Model fitting.} We used JAGS
-\citep{Plummer2003:JAGS:-A-Program} to estimate the posteriors over
-paramater values given our data. Results reported here are based on
-two chains of 10.000 MCMC samples from the joint posterior
-distribution, obtained after an initial burn-in of 10.000 steps. The
-latter guaranteed convergence.
-
-To check whether the model yields sensible results we first look at
-the preference-related control conditions.
-%
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{pics/post_salience_TF.pdf}
-  \caption{Estimated posteriors for the salience of \lc- and
-    \ec-readings for different prosodic cues. Lines under curves
-    indicate 95\% HDIs (see Footnote~\ref{fn:HDI}).}
-  \label{fig:Posterior_TF}
-\end{figure}
-%
-Estimates for the (marginalized) posteriors over relative salience
-levels for target-related controls are plotted in
-Figure~\ref{fig:Posterior_TF}. The results are exactly as we would
-expect them to be. Given our data, we should believe that the
-\lc-reading is most prominent. The level of prominence varies with
-accentuation. Under prosody that we hypothesized would favor the
-\lc-reading, the contrast is most pronounced. Under accentuation that
-we hypothesized favors the \ec-reading we are no longer justified in
-believing with certainty that the \lc-reading is preferred (by
-comparison of 95\% HDIs, see below).\footnote{\label{fn:HDI} A 95\%
-  Highest Density Interval (HDI) is a convex region of values over
-  which 95\% of the distribution's probability density is distributed,
-  such that no value outside of that region has higher probability
-  density than any point within
-  \citep{Kruschke2011:Doing-Bayesian-}. Intuitively speaking, the 95\%
-  HDI is the set of values which we may believe to be true with some
-  confidence; what falls outside this region is what can be excluded
-  safely.}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{pics/post_salience.pdf}
-  \caption{Posteriors over relative salience of target readings in
-    critical conditions.}
-  \label{fig:Posterior_T}
-\end{figure}
-
-Estimates of posteriors over salience of readings in the critical
-conditions are given in Figure~\ref{fig:Posterior_T}. In the
-\es-conditions, literal readings are by far the most salient, followed
-by local, followed by global readings. There does not appear to be a
-significant effect of intonation (by visual comparison of 95\%
-HDIs). For \as-sentences, the same preference order holds in tendency,
-but we cannot assert with full confidence that local readings are
-attested or that they are preferred over global readings (see below).
-
-Posteriors over error rates are conceptually less interesting, and we
-will skip them here. The posterior over the sequential bias parameter
-is shown in Figure~\ref{fig:post_q}. Since the 95\% is clearly
-entirely below .5, we have reason for believing, given the model and
-our data, in a bias for late responses.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{pics/post_q.pdf}
-  \caption{Estimated Posteriors over global sequential bias parameter
-    $q$.}
-  \label{fig:post_q}
-\end{figure}
-
-\paragraph{Model validation.} As a crude sanity check that our model
-is able to predict the observed data, we gathered 10.000 random values
-from the posterior predictive distribution and found a highly
-significant correlation between these and the observed data ($R^2 =
-0.987$, $p < 0.001$).
-
-\paragraph{Hypothesis testing.} We are chiefly interested in two
-questions: (i) which readings are available? and (ii) what is the
-preference order over readings?
-
-The first question can be answered by looking at the HDIs of the
-posteriors of the candidate readings. We would like to check the
-hypothesis that a given reading is unavailable, i.e., its activation
-value in the probabilistic model is equal to 0, or close to zero for
-practical purposes (Region of Practical Equivalence, ROPE). We reject
-the ``null-hypothesis'' that the true value is 0 if its ROPE lies
-entirely outside the 95\% HDI; we accept the ``null-hypothesis'' if
-the ROPE lies entirely within the 95\% HDI
-\citep[][Ch.~12]{Kruschke2011:Doing-Bayesian-}. The following table
-lists approximations of the 95\% HDIs for each condition and reading:
-
-\begin{center}
-  \begin{tabular}{lllllll}
-    & lit & loc & glb & \\ \midrule
-    \as-ntr & $(0.924 , 1)$ & $(0 , 0.068)$
-    & $(0 , 0.022)$ \\
-    \as-acc 
-    & $(0.816 , 0.964)$
-    & $(0.028 , 0.152)$
-    & $(0 , 0.066)$ \\
-    \es-ntr 
-    & $(0.665 , 0.873)$
-    & $(0.117 , 0.323)$
-    & $(0 , 0.024)$ \\
-    \es-acc 
-    & $(0.634 , 0.851)$
-    & $(0.139 , 0.356)$
-    & $(0 , 0.022)$ 
-  \end{tabular}
-\end{center}
-
-\noindent We should thus accept the hypothesis that there are no
-global readings at all, and no local readings for \as-sentence under
-neutral intonation. There is support for a belief in local readings in
-the \as-acc condition up to a ROPE of $[0;0.028)$.
-
-The preference relations between readings can be checked in a similar
-way. We look at the posterior beliefs about the \emph{differences} of
-activation strengths and ask whether these posterior beliefs allow us
-to safely conclude that differences are bigger than zero or not. It is
-obvious enough that literal readings are always the most preferred,
-and that local readings are preferred over global readings for
-\es-sentences. Figure~\ref{fig:PostDiffTAS} shows the posteriors over
-differences for the only non-trivial cases, namely those between local
-and global readings for \as-sentences. Since the 95\% HDIs include 0,
-the data provides no ground for confidence that, given the model,
-local readings of \as-sentences are preferred over global ones,
-despite the obvious tendency. In sum, with the exception of remaining
-uncertainty about local readings of \as-sentences, the model and the
-data suggest that global readings are absent entirely, while literal
-readings are preferred over local readings.
-
-\begin{figure}
-  \centering
-  \subfloat[][neutral]{
-      \includegraphics[width=0.45\textwidth]{PostDiffT_ASntr.pdf}
-  }
-  \hfill
-  \subfloat[][accented]{
-      \includegraphics[width=0.45\textwidth]{PostDiffT_ASacc.pdf}
-  }
-  \caption{Posteriors over differences between salience levels for
-    local and global readings of \as-sentences. As zero is contained
-    in the 95\% HDI for both neutral and accented variants, there is
-    no justification for assuming a difference in salience.}
-  \label{fig:PostDiffTAS}
-\end{figure}
-
-\subsection{Discussion}
-\label{sec:discussion-1}
-
-\paragraph{Summary \& Interpretation.} The present study investigated
-prosodic effects on quantifier interpretation by employing a new
-experimental paradigm, the incremental verification
-task. Based on a current debate in the literature, we were
-specifically interested in whether ``local readings'' of sentences
-where \emph{some} is embedded under another quantifier can be found,
-and how salient these readings are under varying prosody of auditorily
-presented sentence material, in particular the presence or absence of
-contrastive stress on embedded \emph{some}.
-
-High scores of success in control conditions show that participants
-understood the incremental verification task and were able to give
-judgements at the right point in a picture sequence. Results for the
-preference-related controls show that our design is able to detect
-multiple readings and preferences among these. Crucially, the amount
-of response types for \lc- and \ec-readings reflected the known
-preference for the former, with a mild bias for readings that can be
-judged later in the sequence. Also, the incremental verification task
-was generally sensitive to prosody. However, significant prosodic
-effects were restricted to preference-related controls. Contrastively
-accenting scalar \emph{some} generally led to more local readings, but
-that effect was not significant. Local readings occurred in
-\es-sentences, independently of prosody, but required prosodic marking
-in \as-sentences. Our analyses support the impression that inspection
-of the raw data gives, namely that the general qualitative pattern of
-reading preferences is the same for \as- and \es-conditions: literal
-readings are preferred over local readings which are preferred over
-global readings. More concretely, our analyses suggest the following
-preference patterns (bracketed readings are not supported by our data
-and the previous analyses):
-
-\begin{exe}
-  \ex \label{bsp:observed-preferences}
-    \begin{xlist}
-      \ex \as-ntr: \ \ \ \lit \ (>  \loc \ \  $\sim$ \glb)
-      \ex \as-acc: \ \ \ \lit \ > \ \loc \ \ ( $\sim$ \glb)
-      \ex \es-ntr: \ \ \ \lit \ > \ \loc \ \ ( > \glb)
-      \ex \es-acc: \ \ \ \lit \ > \ \loc \ \ ( > \glb)
-    \end{xlist}
-
-\end{exe}
-
-\noindent If we compare (\ref{bsp:observed-preferences}) with
-Table~\ref{tab:predictions}, we quickly see that these findings are
-not predicted by either traditionalism or grammaticalism. We address
-each position separately in the following.
-
-Traditionalism easily explains the absence of global readings. Weak
-traditionalism, introduced in Section~\ref{sec:traditionalism}, for
-instance, would hold that the extra assumptions needed to derive
-global readings (e.g., a speaker competence assumption) are not
-available or only allow for epistemic weak implicatures that would
-show as responses indicative of literal readings in our task. In
-support of this view, traditionalists could argue that the task's
-rather high processing demands lead to a suppression of global
-readings, in line with the findings of
-\citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
-load negatively affects the number of scalar implicature responses in
-sentence verification tasks. The small number of local readings in
-\as-sentences with contrastive stress is easily explained by adopting
-the prosodic markedness hypothesis. What traditionalism does not
-predict is the high number of answers indicative of local readings in
-the \es-conditions. Resorting to the prosodic markedness hypothesis
-does not help, because local readings were observed for accented as
-well as for unaccented \es-sentences. It would also remain unclear why
-prosodic cues should have such differential effects on \as- and
-\es-sentences.
-
-Grammaticalism, on the other hand, fails to predict the pattern in
-(\ref{bsp:observed-preferences}) entirely if it equates preference for
-readings with logical strength. Grammaticalism predicts that literal
-readings of \as-sentences are the least preferred, contrary to
-(\ref{bsp:observed-preferences}). Again, we need to bear the caveat of
-Section~\ref{sec:grammaticalism} in mind that we are only evaluating
-grammaticalism with respect to a particular disambiguation criterion
-here. The verdict, however, seems to be clear. If
-(\ref{bsp:observed-preferences}) is the actual preference order over
-readings, then meaning disambiguation in terms of logical strength is
-generally on the wrong track, because no account that merely looks at
-the logical strengths of readings can plausibly predict the preference
-pattern in (\ref{bsp:observed-preferences}) for both \as- and
-\es-sentences at the same time.
-
-In sum, the present findings cannot be explained in terms of the
-austere and stylized versions of traditionalism and grammaticalism
-that we have set up so far. We should then ask what plausible
-additional assumptions would enable either framework to accommodate
-the data? Again, let us look at each position in turn.
-
-Consider grammaticalism first. Our data contradicts the notion that
-preferences follow logical strength. But grammaticalism could be
-supplemented by a conceptually different selection
-criterion. Selecting readings in terms of how well they answer the
-contextually given question under discussion, as suggested by
-\citet{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}, is
-an option. But it is quite unclear what the question under discussion
-should be that guided judgements in our task. As long as a theory of
-accommodating implicit questions under discussion is missing, this
-selection criterion does not make any clear, testable
-predictions. However, looking at the qualitative pattern in
-(\ref{bsp:observed-preferences}), a \emph{prima facie} plausible
-disambiguation criterion is ready at hand: if we assume that each
-insertion of the $\exh(\cdot)$ operator is \emph{costly}
-anti-proportional to the depth of its embedding under other logical
-operators, then we derive a preference of literal readings over local
-ones over global ones. Whether such an \emph{economy principle} is
-sound and in line with further empirical data would then be an
-interesting matter of further investigation. What this economy
-principle does not explain yet is the quantitative differences in the
-preference orders between \as- and \es-sentences. Still, if combined
-with further information about the global properties of the sentences
-in question, this might be an interesting alternative disambiguation
-criterion for an empirically testable grammaticalism.
-
-Traditionalism, on the other hand, has to explain the possibility of
-local readings of prosodically unmarked \es-sentences, and, perhaps,
-also the large number of local readings in accented \es-sentences
-compared to the much lower number in accented \as-sentences. To do so
-within a strict traditionalist framework seems difficult. A first
-options might be to account for local readings as the result of some
-other phenomenon, such as typicality or contrast
-\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter}.
-Since this ties into a critical reflection on our design, we will
-enlarge on the possibility of typicality- and contrast-based effects
-in our setting. Eventually, we argue that contrast-effects alone are
-unlikely to explain the observed high number of local answers in
-\es-sentences, but that a ``modern traditionalist'' explanation of the
-answer pattern might be available if we allow for the possibility that
-\emph{exactly one} gets an unexpected ``referential interpretation.''
-
-As discussed in Section~\ref{sec:previous-studies},
-\citet{Tielvan-Tiel2012:Embedded-Scalar} and
-\citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue that the
-distribution of responses to \as-sentences found by
-\citet{CliftonDube2010:Embedded-Implic}, as well as
-\citet{ChemlaSpector2010:Experimental-Ev} could be explained by
-differences in how \emph{typical} the presented pictures were for an
-\as-sentence. Notice that this does not apply in the present situation
-where the task is to explain away the local readings of \es-sentences,
-for which no alternative explanation in terms of typicality has been
-offered. Moreover, to apply typicality-based explanations to the
-incremental verification task, one would have to reason about the
-typicality of parts of pictures or to figure in subjects' expectations
-of pictorial typicality given their uncertainty about parts of the
-picture that they have not yet seen. On intuitive grounds, we take
-either extension to be implausible. But even if this line of
-explanation can be plausibly extended to incrementally revealed
-picture verification, it would still be unclear why typicality-effects
-should show so strongly in categorical truth-value judgements, and why
-there is such a stark contrast between \as- and \es-sentences.
-
-A more promising alternative explanation for local readings of
-\es-sentences is pursued by
-\citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} in response to the data
-reported by \citet{ChemlaSpector2010:Experimental-Ev}. The main idea
-is that visual contrast between an item that is connected to all, and
-one that is connected to only some but not all of the relevant
-elements may trigger exceptional local enrichment of \emph{some}. In
-support of this idea,
-\citeauthor{GeurtsTielvan-Tiel2013:Embedded-Scalar} show that the
-strength of agreement to an \es-sentence on a 7-point Likert-scale
-depends on how strong the relevant visual contrast is. When an item
-with only some connections is presented alongside two universally
-connected elements, the mean rate of agreement with a suitable
-\es-sentence is significantly higher than when only one universally
-connected element is present. So, maybe our \es-sequences similarly
-provoked local readings because of an overemphasized visual contrast
-between \emph{some but not all} and \emph{all}.
-
-The third step of our \es-sequences in Figure~\ref{fig:exseqES} is a
-relevant case of direct contrast between a \emph{some-but-not-all-}
-and an \emph{all}-situation, but it is a weak contrast, in the sense
-of \citet{GeurtsTielvan-Tiel2013:Embedded-Scalar}, because there is
-only one universally connected element. Moreover, our study elicited
-categorical truth-value judgements. Unlike in
-\citeauthor{ChemlaSpector2010:Experimental-Ev}'s
-(\citeyear{ChemlaSpector2010:Experimental-Ev}) and
-\citeauthor{GeurtsTielvan-Tiel2013:Embedded-Scalar}'s
-(\citeyear{GeurtsTielvan-Tiel2013:Embedded-Scalar}) experiments, we
-did not record degrees of agreement with a statement. For a purely
-contrast-based explanation to work, it would have to be made plausible
-why the (weak) visual contrast in a picture like in
-Figure~\ref{fig:exseqES3} alone is enough to overrule a truth-value
-judgment so as to contradict the semantic meaning (even when there is
-no prosodic markedness to support such a reinterpretation).
-
-On the other hand, there is a conceivable alternative explanation of
-the puzzling data for \es-sentences that would also account for the
-large and systematic error responses. Recall from
-Section~\ref{sec:results} and Table~\ref{tab:count_data_CC} on
-\pageref{tab:count_data_CC} that a surprisingly high number of
-\emph{true} answers was given at the second step of the
-\es-sequence. This answer type does not correspond to any of the three
-candidate readings that the previous literature has focused on. As
-suggested earlier, this answer type can be explained under the
-assumption that \emph{exactly one} gets a reading similar to
-\emph{there is (at least) one}, while the scalar item \emph{some}
-would just receive its semantic interpretation. Such a reading of
-\emph{exactly one}, although surprising, could actually be supported
-by some theories of numerals and modifiers
-\citep[e.g.][]{Geurts2006:Take-five,MartyChemla2014:Phantom-reading},
-as the outcome of an ``existential closure'' type-shifting rule in the
-sense of \citet{Partee1986:Noun-phrase-int} to the effect that
-\emph{exactly one} is mapped onto an existential reading of the form
-``there is a group with cardinality exactly one.''
-
-What happens if \emph{some} is additionally strengthened in some way
-or other under such a reading of \emph{exactly one}? If \emph{some} is
-pragmatically strengthened under the scope of \emph{at least one} in a
-pure traditionalist manner by adding the negation of a sentence type
-\emph{at least one \dots all \dots}, we would expect \emph{true}
-judgements at position 3 of the \es-sequence. Although exactly 3
-\emph{true} answers occurred there for each neutral and accented
-\es-conditions respectively, the main point to notice is that this
-construal does not explain \emph{true} judgements at position 5. These
-would therefore still seem indicative of local readings. However,
-there is a slight variant of the hypothesized existentially closed
-reading of \emph{exactly one}, that would explain \emph{true}
-judgments at position 5 in an ``modern traditionalist'' manner. This
-is a reading of \emph{exactly one} as ``there is a \emph{unique} group
-with cardinality exactly one.'' Although this is admittedly only a
-vague sketch of a possible line of explanation, it is not entirely
-implausible that such a uniqueness requirement has participants look
-for a distinguished referent, which they find on position 5. But if
-the reading in question is about a unique discourse referent, we can
-explain how the predicate \emph{is connected to some if its \dots} can
-be pragmatically enriched in the desired fashion, along the lines of a
-``modern traditionalist'' account that takes discourse effects into
-account \citep[][Chapter~8.4]{Geurts2010:Quantity-Implic}. The
-listener would then conclude that the referent in question was not
-connected to all of its surrounding elements, because otherwise the
-speaker would have attributed that to the now fixed referent in
-question. This is parallel, so Geurts suggests, to the reasoning that
-an utterance of ``Smith met a woman'' implicates that \emph{the woman
-  referred to} was not Smith's mother and not that Smith didn't meet
-his mother at all. But this alternative explanation is at present only
-a tentative sketch of a possibility.
-
-In conclusion, then, it appears that our data provides interesting
-challenges to both traditionalism and grammaticalism.
-
-% \paragraph{Critique.} There are a number of conceivable objections to
-% our design and our interpretation of the presented results. We will
-% consider the most pressing ones in the following.
-
-% To begin with, it could be questioned whether our design reliably
-% indicates the preference relations in
-% (\ref{bsp:observed-preferences}). One could object that it is not
-% feasible to compare results from the preference-related controls to
-% results from our target conditions, because the source of different
-% readings is fundamentally different. In the former we have a syntactic
-% ambiguity, in the latter a set of putative pragmatic enrichments. The
-% former is a case of perceived ambiguity (some of our subjects reported
-% this), the latter arguably is not
-% \citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
-% if the distribution of responses is indicative of the known preference
-% patterns in preference-related controls, this would not necessarily
-% mean that the distribution of responses in target conditions is
-% indicative of preference relations. Although we cannot rule out that
-% the incremental verification task detects preferences among multiple
-% readings only for some sources of variability in readings and not
-% others, it is by no means clear why this should be so. The burden of
-% argument is on the sceptic. But even if we assume that the incremental
-% verification task is incapable of reliably indicating preferences
-% among candidate pragmatic enrichments of the relevant kind, then it
-% should at least be able to indicate availability of readings. So if we
-% deny the observed response patterns the power to indicate preference,
-% what should the information about availability of readings be that we
-% may safely infer from it? It should be that local readings are
-% available in \es-sentences and that global readings are unattested in
-% \as- and \es-sentences. But that alone is not predicted by either
-% traditionalism or grammaticalism. The former cannot explain the
-% substantial number of local responses in \es-sentences, the latter
-% does not explain the absence of total global responses.
-
-% Another line of criticism that challenges the validity of
-% (\ref{bsp:observed-preferences}) targets the Bayesian
-% salience-competition model that we used to derive it. We readily admit
-% that our model is highly simplistic. Several aspects are especially
-% noteworthy here. Firstly, we did not distinguish different types of
-% errors, and did not take into account that when errors occurred
-% earlier in the sequence, later decision points could no longer be
-% reached. This way the model may actually have unduly de-emphasized the
-% salience of readings that can be judged later in a sequence. Another,
-% more complicated model of the likelihood of answer patterns, might
-% therefore have given support to different conclusions. Unfortunately,
-% it is not clear how exactly such a more complex generating model
-% should be set-up. Eventually, a full processing model, designed for
-% data from incremental verification tasks, would be needed. We cannot
-% offer such a model here, but can only the offer a first step in that
-% direction. More importantly, though, the only part of
-% (\ref{bsp:observed-preferences}) that might plausibly change for a
-% more encompassing model along the lines sketched above is that the 3
-% \emph{false} answers in the \as-conditions with neutral intonation
-% might support the conclusion that the local reading is attested. But
-% this hypothetical effect will certainly be no bigger than marginal,
-% and so no genuinely different conclusions of theoretical relevance
-% should be expected.
-
-\section{Conclusions}
-\label{sec:conclusions}
-
-We tested experimentally the predictions of traditionalism and
-grammaticalism with respect to the availability of and preferences
-over three types of conceivable pragmatic enrichments of two types of
-sentences, in which scalar \emph{some} occurred in the scope of either
-a monotonic quantifier \emph{all} or the non-monotonic quantifier
-\emph{exactly one}. To avoid potential confounds of the pictorial
-material, such as through typicality or contrast
-\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar},
-we employed an incremental verification task \citep{Conroy2008}, in
-which subjects were presented with partially covered pictures and
-asked to uncover the picture sequentially until they felt able to give
-a categorical truth-value judgements. In order to control for
-potential confounds of ``silent prosody,'' sentence material was
-presented auditorily and contrastive stress on embedded \emph{some}
-was manipulated. This way we were able to also explicitly test the
-prosodic markedness hypothesis, which is often used to supplement
-traditionalism. Additionally, we included preference-related control
-conditions in order to be able to deduce latent preferences for
-candidate readings from the answer patterns we gathered. To this end,
-we introduced a generative Bayesian model that gives probabilistic
-predictions about observable answer patterns in our task, given
-concrete instances of relative saliences of readings and other
-parameters. Using the observed data, in particular in connection with
-the preference-related control conditions, we inferred a posteriori
-likely values of the latent model parameters.
-
-Backed up by our analyses, we concluded that both traditionalism and
-grammaticalism do not predict our data well. Traditionalism fails to
-account for high numbers of responses indicating local readings even
-for prosodically unmarked \es-sentences. Grammaticalism, insofar as
-it builds on disambiguation by logical strength, fails to predict the
-absence of answers indicative of global readings and the relative
-abundance of answers indicative of literal readings.
-
-The clearest upshot of theoretical importance of this study is that
-strength-based meaning selection does not seem to be a good
-disambiguation criterion for grammaticalism. We tentatively suggested
-an alternative selection principle for grammaticalism in terms of
-``parsing economy.'' Another important conclusion from our data is
-that \es-sentences, using non-monotonic quantifier \emph{exactly one},
-appeared to be prone to receive a ``shallow interpretation.'' This may
-be used by traditionalism to explain answers indicative of local
-readings for \es-sentences. But the point is relevant in general. The
-possibility of ``shallow interpretation'' of non-monotonic quantifiers
-should be considered also when interpreting the results of other
-experimental designs \citep[e.g.][]{CliftonDube2010:Embedded-Implic,
-  ChemlaSpector2010:Experimental-Ev}.
-
-We have argued that auditory presentation of sentence material should
-be controlled for if prosodic information is hypothesized to influence
-availability and preferences of readings. We also argued that
-theoretical positions must be formulated in such a way that they make
-testable predictions about reading preferences where different
-potential readings are allowed (contra a grammaticalism without
-commitment to any testable disambiguation principle). We should then
-try to obtain information about actual preference patterns by explicit
-comparison with structures whose preference structures are
-well-studied, ideally with some model of the data generating process
-for optimal data analysis.
-
-\newpage
-
-\appendix
-
-\section{The auditory sentence material}
-\label{sec:audit-sent-mater}
-
-\begin{table}[!hp]
-  \centering
-
-  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-B.png}
-
-  \caption{Difference between minimal and maximal F0 values in Hz for
-    each of the single words in the target sentences. Region 6
-    corresponds to the determiner \emph{einigen}.} 
-  \label{tab:table-B}
-\end{table}
-
-\begin{table}[!hp]
-  \centering
-
-  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-A.png}
-
-  \caption{Durational values in ms for each of the single regions in the target sentences. 
-  Region 6 corresponds to the determiner \emph{einigen}.}
-  \label{tab:table-A}
-\end{table}
-
-\begin{table}[hp]
-  \centering
-
-  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-D.png}
-
-  \caption{Difference between minimal and maximal F0 values in Hz  
-  for each of the single regions in
-    the preference-related controls. Regions 5 and 7 correspond to the
-    nouns preceding the boundaries.}  
-  \label{tab:table-D}
-\end{table}
-
-\begin{table}[hp]
-  \centering
-
-  \includegraphics[width=\textwidth]{../pictures/Acoustics/Table-C.png}
-
-  \caption{Durational values in ms for each of the single regions in
-    the preference-related controls. Regions 5 and 7 correspond to the
-    nouns preceding the boundaries.}  
-  \label{tab:table-C}
-\end{table}
-
-%\paragraph{Targets.} Table~\ref{tab:table-A} shows the durational values for each of
-%the single regions in the sentence. Crucially, durational values of
-%accented determiners were significantly increased as opposed to their
-%non-accented counterparts. Overall, \acro{Quantifier} effects were
-%observed, which might be attributed to the above-mentioned lexical
-%differences, as well as to the fact that \es-structures generally
-%contained fewer words, thus leading to a tendency of a durational
-%decrease for each of the single words.
-%
-%Differences between maximal and minimal F0 values for each of the
-%single words in the sentence are depicted in
-%Table~\ref{tab:table-B}. As is descriptively evident, accented
-%determiners showed a larger F0 range compared to unaccented versions,
-%an effect which is confirmed by statistical analyses. An additional
-%\acro{Quantifier}*\acro{Prosody} interaction indicates that these
-%differences are even more pronounced in the \as-condition. Finally,
-%comparable to the durational analyses, \acro{Quantifier} effects were
-%observed when conditions exhibited lexical differences.
-%
-%Finally, differences between maximal and minimal F0 values for each of
-%the single words in the sentence are given in
-%Table~\ref{tab:table-D}. Again, the most reliable differences occur at
-%the boundary regions.
-
-%\paragraph{Preference-related controls.} Table~\ref{tab:table-C} shows the
-%durational values of each of the single words in the sentence. As is
-%descriptively evident, the largest durational differences were
-%realized at the boundary regions (i.e. Region 5 and Region
-%7). Interestingly, small differences between conditions also yielded
-%significance at other positions, suggesting that our speaker produced
-%the different conditions very consistently (i.e., with little
-%variance).
-
-\newpage
-
-\printbibliography[heading=bibintoc]
-
 \end{document}

### 2014-12-10 text/paper/submission/paper.tex
reviews added

@@
 as the outcome of an ``existential closure'' type-shifting rule in the
-sense of \citet{Partee1986:Noun-phrase-int} to the effect that
+sense of \citet{Partee1987:Noun-phrase-int} to the effect that
 \emph{exactly one} is mapped onto an existential reading of the form

### 2014-12-11 MT/exp_01-correlation-bysubject/pic.tex
rearranged MT experiment folder

\documentclass{article}

\usepackage[palatino]{mypackages}

\usepackage{mycommands}

\usepackage{verbatim}
\usepackage[active,tightpage]{preview}
\PreviewEnvironment{tikzpicture}
\setlength\PreviewBorder{5pt}

\usepackage{pgfplots}

\begin{document}

\begin{tikzpicture}[node distance = 2cm]

  \node[rectangle, fill = blue, draw=black, minimum size = 1cm] (s1)
  at (0,0) {};

  \node[rectangle, fill = blue, draw=black, minimum size = 1cm] (s2)
  at (0,3) {};

  \node[rectangle, fill = blue, draw=black, minimum size = 1cm] at (0,6) (s3) {};

  \node[circle, fill = yellow, draw=black, minimum size = 1cm] at (4,0) (c1) {};

  \node[circle, fill = yellow, draw=black, minimum size = 1cm] at (4,2) (c2) {};

  \node[circle, fill = yellow, draw=black, minimum size = 1cm] at (4,4) (c3) {};

  \node[circle, fill = yellow, draw=black, minimum size = 1cm] at (4,6) (c4) {};

  \draw[very thick,-] (s1) -- (c1);
  \draw[very thick,-] (s1) -- (c2);
  \draw[very thick,-] (s1) -- (c3);
  \draw[very thick,-] (s1) -- (c4);

  \draw[very thick,-] (s2) -- (c1);
  \draw[very thick,-] (s2) -- (c2);
  \draw[very thick,-] (s2) -- (c3);
  \draw[very thick,-] (s2) -- (c4);

  \draw[very thick,-] (s3) -- (c4);
  \draw[very thick,-] (s3) -- (c3);

\end{tikzpicture}

\end{document}

### 2014-12-11 MT/exp_02-K2-unembedded-postTest/pics/letter_triangles_dashedLines.tex
new experiment K2 Post

\documentclass{article}

\usepackage[palatino]{mypackages}

\usepackage{mycommands}

\usepackage[]{mathdesign}
%\usepackage{MnSymbol}
% \usepackage{ulsy}
\usepackage{wasysym}
\usepackage{ascii}
\usepackage{marvosym}
\usepackage{pifont}
\usepackage{phaistos}
\usepackage{epsdice}
\usepackage{skak}

\usepackage{verbatim}
\usepackage[active,tightpage]{preview}
\PreviewEnvironment{tikzpicture}
\setlength\PreviewBorder{20pt}

\usetikzlibrary{shapes.geometric}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}

\begin{document}
\begin{tikzpicture}[node distance = 3cm]

    \tikzset{ctype/.style={circle,thick,minimum
      width=18mm},
      htype/.style={},
      p6type/.style={thick,minimum width=20mm},
      p4type/.style={thick,minimum width=20mm},
      arrow/.style={-,very thick}}
\begin{pgfonlayer}{background}
      \node at (0,0) [circle,draw=black!70,fill=gray!20,minimum size = 8.5cm] {};
    \end{pgfonlayer}\begin{pgfonlayer}{foreground}

      \node at (0,0)  [ctype,draw=black!70,fill=brown!20] 
      (c0)   {\textcolor{black}{\Huge{$\text{\Letter}$}}};

    \end{pgfonlayer}
\begin{pgfonlayer}{foreground}

\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, above left of = c0]  (p0)   {};

\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, above of = c0]  (p1)   {};

\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, above right of = c0]  (p2)   {};

\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, below right of = c0]  (p3)   {};

\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, below of = c0]  (p4)   {};

\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, below left of = c0]  (p5)   {};

\draw [arrow, dashed] (c0) to (p3) node[midway, above] {\Large{?}};

\draw [arrow, dashed] (c0) to (p4) node[midway, left] {\Large{?}};

\draw [arrow, dashed] (c0) to (p5) node[midway, above] {\Large{?}};

\end{pgfonlayer}

\draw [arrow] (c0) to (p0);

\draw [arrow] (c0) to (p1);

\draw [arrow] (c0) to (p2);

                %  \begin{scope}

                %       \clip (-4.1,-4.1) rectangle (4.1,0);

                %       \node at (0,0) [circle,draw=gray!80,fill=gray!80,minimum size = 8.1cm] {};

                % \end{scope}

        \begin{pgfonlayer}{background}
      \node at (0,0) [circle,draw=black!70,fill=gray!20,minimum size = 8.5cm] {};
    \end{pgfonlayer}

\end{tikzpicture}

\end{document}

### 2014-12-12 MT/exp_02-K2-unembedded-postTest/data_exploration.R
K2 post exp 2 summary of results

@@ -1,0 +1,10 @@
+data = read.csv("results.csv")
+data = subset(data, data$Answer.S1 == "false" &
+                data$Answer.S2 == "ct" &
+                data$Answer.S4 == "true")
+attach(data)
+table(Answer.S1)
+table(Answer.S2)
+table(Answer.S3)
+table(Answer.S4)
+

### 2014-12-19 MT/exp_03_MT-IVT-Small/pics/Var01_scissors_circle/0-0.tex
pics for post experiment

--- 2014-12-11 MT/exp_02-K2-unembedded-postTest/pics/letter_triangles_dashedLines.tex
@@
 
-\usepackage[palatino]{mypackages}
-
-\usepackage{mycommands}
+\usepackage[palatino]{mypackages}\usepackage{mycommands}
 
@@
 %\usepackage{MnSymbol}
-% \usepackage{ulsy}
 \usepackage{wasysym}
@@
       htype/.style={},
-      p6type/.style={thick,minimum width=20mm},
-      p4type/.style={thick,minimum width=20mm},
+      p6type/.style={thick,minimum width=14mm},
+      p4type/.style={thick,minimum width=14mm},
       arrow/.style={-,very thick}}
@@
       \node at (0,0)  [ctype,draw=black!70,fill=brown!20] 
-      (c0)   {\textcolor{black}{\Huge{$\text{\Letter}$}}};
+      (c0)   {\textcolor{black}{\Huge{$\text{\Rightscissors}$}}};
 
@@
 
-\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, above left of = c0]  (p0)   {};
+\node [p6type,circle,draw=black!70,fill=blue!50, above left of = c0]  (p0)   {};
 
-\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, above of = c0]  (p1)   {};
+\node [p6type,circle,draw=black!70,fill=blue!50, above of = c0]  (p1)   {};
 
-\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, above right of = c0]  (p2)   {};
+\node [p6type,circle,draw=black!70,fill=blue!50, above right of = c0]  (p2)   {};
 
-\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, below right of = c0]  (p3)   {};
+\node [p6type,circle,draw=black!70,fill=blue!50, below right of = c0]  (p3)   {};
 
-\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, below of = c0]  (p4)   {};
+\node [p6type,circle,draw=black!70,fill=blue!50, below of = c0]  (p4)   {};
 
-\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=blue!50, below left of = c0]  (p5)   {};
-
-\draw [arrow, dashed] (c0) to (p3) node[midway, above] {\Large{?}};
-
-\draw [arrow, dashed] (c0) to (p4) node[midway, left] {\Large{?}};
-
-\draw [arrow, dashed] (c0) to (p5) node[midway, above] {\Large{?}};
+\node [p6type,circle,draw=black!70,fill=blue!50, below left of = c0]  (p5)   {};
 
@@
 
-\draw [arrow] (c0) to (p0);
+                 \begin{scope}
 
-\draw [arrow] (c0) to (p1);
+                      \node at (0,0) [circle,draw=gray!80,fill=gray!80,minimum size = 8.1cm] {};
 
-\draw [arrow] (c0) to (p2);
-
-                %  \begin{scope}
-
-                %       \clip (-4.1,-4.1) rectangle (4.1,0);
-
-                %       \node at (0,0) [circle,draw=gray!80,fill=gray!80,minimum size = 8.1cm] {};
-
-                % \end{scope}
+                \end{scope}
 
         \begin{pgfonlayer}{background}
-      \node at (0,0) [circle,draw=black!70,fill=gray!20,minimum size = 8.5cm] {};
-    \end{pgfonlayer}
-
-\end{tikzpicture}
+      \node at (0,0) [circle,draw=black!70,fill=gray!20,minimum size =
+      8.5cm] {};
+      \node at (0,0) [rectangle,minimum size = 11cm] {};
+    \end{pgfonlayer}\end{tikzpicture}
 

### 2014-12-19 MT/exp_03_MT-IVT-Small/pics/Var02_letter_rectangle/0-0.tex
pics for post experiment

--- 2014-12-19 MT/exp_03_MT-IVT-Small/pics/Var01_scissors_circle/0-0.tex
@@
       \node at (0,0)  [ctype,draw=black!70,fill=brown!20] 
-      (c0)   {\textcolor{black}{\Huge{$\text{\Rightscissors}$}}};
+      (c0)   {\textcolor{black}{\Huge{$\text{\Letter}$}}};
 
@@
 
-\node [p6type,circle,draw=black!70,fill=blue!50, above left of = c0]  (p0)   {};
+\node [p6type,regular polygon, regular polygon sides=4,draw=black!70,fill=red!50, above left of = c0]  (p0)   {};
 
-\node [p6type,circle,draw=black!70,fill=blue!50, above of = c0]  (p1)   {};
+\node [p6type,regular polygon, regular polygon sides=4,draw=black!70,fill=red!50, above of = c0]  (p1)   {};
 
-\node [p6type,circle,draw=black!70,fill=blue!50, above right of = c0]  (p2)   {};
+\node [p6type,regular polygon, regular polygon sides=4,draw=black!70,fill=red!50, above right of = c0]  (p2)   {};
 
-\node [p6type,circle,draw=black!70,fill=blue!50, below right of = c0]  (p3)   {};
+\node [p6type,regular polygon, regular polygon sides=4,draw=black!70,fill=red!50, below right of = c0]  (p3)   {};
 
-\node [p6type,circle,draw=black!70,fill=blue!50, below of = c0]  (p4)   {};
+\node [p6type,regular polygon, regular polygon sides=4,draw=black!70,fill=red!50, below of = c0]  (p4)   {};
 
-\node [p6type,circle,draw=black!70,fill=blue!50, below left of = c0]  (p5)   {};
+\node [p6type,regular polygon, regular polygon sides=4,draw=black!70,fill=red!50, below left of = c0]  (p5)   {};
 

### 2014-12-19 MT/exp_03_MT-IVT-Small/pics/Var03_bell_triangle/0-0.tex
pics for post experiment

--- 2014-12-19 MT/exp_03_MT-IVT-Small/pics/Var01_scissors_circle/0-0.tex
@@
       \node at (0,0)  [ctype,draw=black!70,fill=brown!20] 
-      (c0)   {\textcolor{black}{\Huge{$\text{\Rightscissors}$}}};
+      (c0)   {\textcolor{black}{\Huge{$\text{\bell}$}}};
 
@@
 
-\node [p6type,circle,draw=black!70,fill=blue!50, above left of = c0]  (p0)   {};
+\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=green!50, above left of = c0]  (p0)   {};
 
-\node [p6type,circle,draw=black!70,fill=blue!50, above of = c0]  (p1)   {};
+\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=green!50, above of = c0]  (p1)   {};
 
-\node [p6type,circle,draw=black!70,fill=blue!50, above right of = c0]  (p2)   {};
+\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=green!50, above right of = c0]  (p2)   {};
 
-\node [p6type,circle,draw=black!70,fill=blue!50, below right of = c0]  (p3)   {};
+\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=green!50, below right of = c0]  (p3)   {};
 
-\node [p6type,circle,draw=black!70,fill=blue!50, below of = c0]  (p4)   {};
+\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=green!50, below of = c0]  (p4)   {};
 
-\node [p6type,circle,draw=black!70,fill=blue!50, below left of = c0]  (p5)   {};
+\node [p6type,regular polygon, regular polygon sides=3,draw=black!70,fill=green!50, below left of = c0]  (p5)   {};
 

### 2015-02-03 text/paper/revision_01/paper.tex
K2 1st revision initial export

--- 2014-12-10 text/paper/submission/paper.tex
@@
 
-\usepackage{../../helpers/gb4e_micha}
-\usepackage{../../helpers/proofing}
-
-\usepackage{../../helpers/mycommands}
-% \usepackage{../helpers/myenvironments}
+\usepackage{gb4e_micha}
+
+\usepackage{mycommands}
 
@@
 
-\title{Embedded Scalars, Preferred Readings \& Intonation: {A}n
+\title{Embedded Scalars, Preferred Readings \& Prosody: {A}n
   Experimental Revisit} 
@@
 takes scope under the non-monotonic quantifier \emph{exactly one}.
-According to current pragmatic theory, there are at least three
-relevant candidate readings for \as- and \es-sentences: (i) a
-\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
+Current theories, have proposed at least three candidate readings
+for \as- and \es-sentences: (i) a \emph{literal reading} like in (\ref{bsp:AE-Literal}) and
 (\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
@@
 Given this plurality of hypothesized readings, the question arises:
-how salient or preferred are these theoretically conceivable readings
+how salient are these theoretically conceivable readings
 compared to each other (if they are detectable by empirical means at
@@
 lies at the heart of a current debate about the nature of quantity
-inferences and the demarkation between semantics and pragmatics. The
-controversy is usually seen as one between two main competing
-theoretical positions. \emph{Traditionalism} holds, in particular,
-that local readings should not occur frequently unless marked by
-special intonation. \emph{Grammaticalism} holds that local readings
-are unproblematically available and, at least under the most prominent
-of selection principles for candidate readings, even at least as
-salient as the literal reading (see
-Section~\ref{sec:grammaticalism}). To distinguish between these
-opposing positions, it is therefore necessary to assess the relative
-salience of readings for \as- and \es-sentences under conditions that
-control for prosodic markedness.
-
-A number of empirical studies have already examined sentences like
-(\ref{bsp:AE}) and (\ref{bsp:GE})
-\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,BenzGotzner2014:Embedded-implic}. Unfortunately,
-results from these studies do not provide uncontroversial
-evidence. This is due to several reasons. Firstly, previous studies
-have only accumulated limited evidence pertaining to the relative
-salience of candidate readings of both types of sentences. Secondly,
-as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
-\citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue, the alleged
-evidence for the availability of local readings of \as-sentences
-suggested by studies of \citet{CliftonDube2010:Embedded-Implic} and
-\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounded
-with what van Tiel and Geurts call \emph{typicality effects} (see
-Section~\ref{sec:previous-studies} for discussion). Finally, and most
-importantly, previous studies presented target sentences
-visually. However, traditionalists acknowledge the availability of
-local readings for prosodically marked utterances
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
-We
-will address this extant position as the \emph{prosodic markedness
-  hypothesis} and argue that, if intonation is hypothesized to play a
-central role, it is vital to present target sentences auditorily, and
-to control for effects of ``silent prosody'' that subjects may apply
-when reading a sentence \citep[see][]{Bader98,Fodor98}.
-
-This paper presents results form an experimental study designed to
-deal with the above mentioned problems. We presented sentence
-materials auditorily and explicitly manipulated intonational stress on
-embedded scalar items. To cater for potential pictorial confounds,
-such as from typicality, we employed an \emph{incremental verification
-  task} in which parts of a to-be-evaluated picture were hidden and
-only revealed piece-wise at the participants' request until they felt
-able to give a binary truth-value judgement
-\citep[see][]{Conroy2008}. This way we obtained categorical behavioral
-data that is both more clearly indicative of the reading that subjects
-assumed and more independent of any potential pictorial confounds, such
-as the mentioned typicality effects. Moreover, this method also gives
-information about reading preferences. We validated this by including
-control conditions with ambiguous sentences with a well-known
-preference on available readings.
-
-The data obtained by this method is \emph{prima facie} problematic for
-both traditionalism and grammaticalism. Contrary to the predictions of
-traditionalism, we observed many answers indicative of local readings
-of \es-sentences, irrespective of intonational markedness. But also
-grammaticalism is incongruent with the observed pattern in our
-data. Backed up by the \emph{strongest meaning hypothesis}
-\citep{DalrympleKanazawa1998:Reciprocal-Expr} as a disambiguation
-criterion \citep[as suggested by][]{ChierchiaFox2008:The-Grammatical},
-grammaticalism predicts local readings to be the preferred readings,
-but we found no evidence for that. More strongly even, the preference
-order among putative readings suggested by our data cannot even in
-principle be explained by comparisons of logical strength among
-putative readings. In sum, our data shed doubt on both traditionalism
-and grammaticalism in their currently most common forms. We conclude
-the paper by some thoughts on how either position could be amended in
-the light of our data.
+inferences and the demarkation between grammar (i.e. syntax/semantics)
+and domain-general reasoning procedures (i.e. pragmatics). The controversy
+is usually seen as one between two main competing theoretical positions
+\citep[see][for a detailed comparison of the two]{ChemlaSingh2014:Remarks-on-the-}.
+Simplifying things for now, these two types of theories make clearly different
+predictions about how salient the local readings, in particular, should be.
+The first position which we refer to as \mymark{traditionalism} (Chemla \& Singh’s ``Gricean approach'') holds that local readings should not be salient at all.
+The second one which we call \mymark{grammaticalism}
+(Chemla \& Singh’s ``grammatical approach'') holds that local readings
+are unproblematically available and even at least as salient
+as the literal ones (see Section \ref{sec:theories-predictions} for a more
+thorough exposition of the theories and their predictions).
+
+That matters actually are not as simple as just described is reflected
+by lively discussions about which conclusions are permitted by previous
+experimental research \citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,BenzGotzner2014:Embedded-implic}.
+The results of these studies
+were discussed controversially because of several specific reasons. Firstly,
+and most importantly, previous studies presented target sentences visually.
+However, traditionalists often acknowledge the availability of local readings for
+prosodically marked utterances, albeit not as the result of
+a standard scalar implicature but of a different pragmatic process triggered by
+prosodic markedness \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
+Under this view, evidence for the availability of local readings \citep[see][]{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev} may be
+an effect of “silent prosody”  \citep[see e.g.][]{Bader98,Fodor98}. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and \citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue,
+the alleged evidence for the availability of local readings of \as-sentences, might well be
+confounded with “typicality effects”  (see Section~\ref{sec:previous-studies} for discussion).
+Finally, previous studies have only accumulated limited evidence pertaining to the relative
+salience of candidate readings of sentences like (\ref{bsp:AE}) and (\ref{bsp:GE}) (see
+Section~\ref{sec:previous-studies} for discussion).
+
+More generally, two prerequisites have to be met in order to make use of
+experimental data to decide between theoretical positions regarding the
+computation of quantity inferences. Firstly, both traditionalism and grammaticalism
+have to be amended with additional assumptions to derive testable
+predictions about the relative salience of candidate readings. For example,
+hypothezised effects of prosodic marking have to be taken into account before
+we can test traditionalism empirically using sentences  (\ref{bsp:AE}) and (\ref{bsp:GE}).
+We will address this extant position as the \mymark{prosodic markedness hypothesis}
+and argue that, if prosody is hypothesized to play a central role, it is vital
+to present target sentences auditorily or to control for effects of  “silent prosody”
+that subjects may apply when reading a sentence. Secondly, the relative
+salience of candidate readings has to be operationalized properly, i.e. we
+have to devise methods to measure relative salience. For example, typicality
+effects and logical dependencies between readings have to be controlled for
+when evaluating speaker judgments in terms of the salience of candidate readings.
+Both of these prerequisites are related to formulating what \citet{ChemlaSingh2014:Remarks-on-the-}
+call ``linking functions'' which connect the core theories to the dependent
+variables of an experiment. Without proper linking functions it is hard
+(or impossible) to test traditionalism or grammaticalism empirically.
+
+This paper presents results form an experimental study designed to deal with
+the mentioned problems. The focus is on testing certain formulations of traditionalism
+and grammaticalsim that are explicit enough to derive testable predictions about the
+relative salience of candidate readings. For practical reasons, we choose what we consider
+the most prominent of such formulations. In order to address the prosodic markedness
+hypothesis, we presented sentence materials auditorily and explicitly manipulated contrastive
+stress on embedded scalar items. In order operationalize the relative salience of candidate
+readings, we employed an \mymark{incremental verification task} in which parts of a to-be-evaluated
+picture were hidden and only revealed piece-wise at the participants’ request until they felt able
+to give a binary truth-value judgement \citep[see][]{Conroy2008}. This way, we catered for
+potential pictorial confounds, such as from typicality. To analyze the obtained data in terms
+of relative salience of candidate readings, we furthermore employed a statistical model of
+how the salience of readings guided participants judgments in the incremental verification task. We
+validated this method by including control conditions testing ambiguous sentences with a
+well-known preference on available readings. We argue that this method provides
+categorical behavioral data that is both clearly indicative of the reading preferences
+among participants and independent of any potential pictorial confounds, such as
+the mentioned typicality effects.
+
+The data obtained by this method is \emph{prima facie} problematic for both
+traditionalism and grammaticalism (or at least what we consider the most
+prominent versions thereof). However, we want to stress from the outset
+that, while the experimental results allow us to derive restrictions on which
+linking functions are conceivable for traditionalism and grammaticalism, conclusions
+about the general validity of the two core theories will be limited
+\citep[cf.][]{ChemlaSingh2014:Remarks-on-the-} because these hardly make falsifiable
+predictions without the necessary linking functions. Contrary to the predictions
+of common versions of traditionalism, we observed many answers indicative of
+local readings of \es-sentences, irrespective of prosodic markedness. But also
+prominent versions of grammaticalism are incongruent with the observed data.
+Backed up by the \mymark{strongest meaning hypothesis}
+\citep{DalrympleKanazawa1998:Reciprocal-Expr} as a
+disambiguation criterion \citep[as suggested by][]{ChierchiaFox2008:The-Grammatical},
+grammaticalism predicts local readings to be the preferred ones, but
+we found no evidence for that. More strongly even, the preference order among
+putative readings suggested by our data cannot even in principle be
+explained by comparisons of logical strength among putative
+readings. In sum, our data shed doubt on both traditionalism and grammaticalism
+in their currently most common forms. We conclude the paper by some thoughts on
+how either position could be amended in the light of our data.
 
@@
 sentences. Section~\ref{sec:theories-predictions} works out the
-predictions of traditionalism and grammaticalism about availability
-and preference of readings for these
+predictions of traditionalism and grammaticalism (plus prominent linking functions) 
+about availability and relative salience of readings for these
 sentences. Section~\ref{sec:previous-studies} reviews related
@@
 There are two main theoretical positions which make different 
-predictions about the readings of \as- and \es-sentences
-\citep[see][for
-overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation}. We
-will refer to these as \mymark{traditionalism} and
-\mymark{grammaticalism} and treat each one in turn. Since there is
-some leeway in assessing the predictions for each approach (depending
-on which of several additional assumptions to adopt), we will
-distinguish different varieties of both of them. Predictions of all
-relevant variants are summarized in Table~\ref{tab:predictions} on
-page~\pageref{tab:predictions}.
+predictions about the readings of \as- and \es-sentences \citep[see][for
+overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation,ChemlaSingh2014:Remarks-on-the-}.
+We will refer to these as \mymark{traditionalism} and \mymark{grammaticalism}
+and treat each one in turn.  As already mentioned in the introduction there is some
+leeway in assessing the predictions for each approach depending on which of several
+additional assumptions to adopt. Therefore, we will distinguish different varieties
+of both of them. While these are certainly not the only possible varieties, they are,
+in our perception, the most prominent ones. Focusing on exactly these thus has
+practical relevance. Their predictions are summarized in Table~\ref{tab:predictions}
+on page~\pageref{tab:predictions}. Below, in the discussion section
+(section~\ref{sec:discussion-1}), further conceivable varieties of traditionalism
+and grammaticalism will be discussed.
 
@@
 Grice's original theory of conversational implicatures
-\citep{Grice1975:Logic-and-Conve}. Many author's have defended
+\citep{Grice1975:Logic-and-Conve}. Many authors have defended
 traditionalist positions in this sense. Of the more recent literature,
@@
 predicts that both literal and global readings are available:  literal
-readings, because these form the starting point of pragmatic
-reasoning; global readings because these may be arrived at by the
-Gricean recipe.
-
-Traditionalism's predictions about preferences between literal and
+readings, because these are the result of semantic interpretation
+and form the starting point of pragmatic reasoning; global readings
+because these may be arrived at by the Gricean recipe.
+
+Traditionalism's predictions about relative salience of literal and
 global readings depend on whether certain auxiliary assumptions
@@
 traditionalism would predict that global readings should be preferred
-over literal readings. On the other hand, if auxiliary assumptions are
-implausible, traditionalism would predict that literal readings would
-be preferred over global ones. Consequently, there are at least two
-varieties of traditionalism that, depending on which additional
-assumptions we would make, yield slightly different predictions:
-\mymark{the strong variety of traditionalism} maintains that the
-auxiliary assumptions of the Gricean recipe hold (e.g., as a matter of
-strong default) and therefore predicts that global readings are
-preferred over literal ones; \mymark{the weak variety of
-  traditionalism} holds that the auxiliary assumptions are more
-fragile and predicts that literal readings are preferred over global
-ones.\fn{We mention for clarity that although weak traditionalism does
-  not predict global readings to be preferred, it might still predict
+over literal readings. On the other hand, if these extra assumptions
+are implausible, traditionalism would predict that literal readings
+are preferred over global ones \citep[see][for experimental evidence
+indicating that manipulation of speaker knowledgeability indeed
+affects the rate of quantity implicatures drawn by the listener
+for unembedded occurrences of \emph{some}]{GoodmanStuhlmuller2013:Knowledge-and-I}.
+
+Consequently, there are at least two varieties of traditionalism that,
+depending on which extra assumptions we make, yield slightly
+different predictions: the \mymark{the strong variety of traditionalism}
+maintains that the extra assumptions of the Gricean recipe hold
+(e.g., as a matter of strong default) and therefore predicts that global
+readings are preferred over literal ones; \mymark{the weak variety of
+traditionalism} holds that the auxiliary assumptions are more fragile
+and context dependent and thus predicts that literal readings may
+often be preferred over global ones. In Table~\ref{tab:predictions}
+(p.~\pageref{tab:predictions}), this prediction of weak traditionalism
+is captured by a preference of literal over global readings because it
+may \emph{a priori} seem implausible from the perspective of weak
+traditionalism that all the necessary assumptions to derive global
+readings are met. \fn{We mention for clarity that although weak traditionalism does
+  not predict global readings to be generally preferred, it might still predict
   an \emph{epistemically weak implicature}, similar to the global
@@
   alternative is true. (See also the discussion in
-  Section~\ref{sec:discussion-1})}
+  Section~\ref{sec:discussion-1})} For weak traditionalism, it is of course an empirical
+task to determine under which circumstances the auxiliary assumptions
+are met.
 
@@
 (\ref{bsp:AE-Alternative}) is an alternative to (\ref{bsp:AE}), but
-also the sentence in (\ref{bsp:AE-Alternatives-Extended}).
+also the sentence in (\ref{bsp:AE-Alternatives-Extended}) \citep[e.g.][]{Sauerland2004:Scalar-Implicat}.
 
@@
 \begin{exer}{bsp:AE-Alternative}
-  \ex \mymark{All} of the students solved \mymark{all} of the problems.
+  \ex \label{bsp:AE-Alternatives-Standard}\mymark{All} of the students solved \mymark{all} of the problems.
 \end{exer}
@@
 \as-sentences is not available; in contrast, \mymark{unrestricted
-  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
-available and so is the local reading.
+  traditionalism} assumes that
+(\ref{bsp:AE-Alternatives-Extended}) is available and so is the
+local reading.\fn{The term traditionalism may be misleading here
+because traditionalists usually assume that scalar implicatures should
+only be computed when a sentence is uttered in a context in which a
+logically stronger alternative is relevant \cite{ChemlaSingh2014:Remarks-on-the-}. However, the alternative
+in (\ref{bsp:AE-Alternatives-Extended}) is not stronger than
+(\ref{bsp:AE}). For completeness sake, we still decided to subsume
+“unrestricted traditionalism” under traditionalism because, once
+alternatives like (\ref{bsp:AE-Alternatives-Extended}) are acknowledged,
+the local reading of \as-sentences can be derived in a
+straightforward traditionalist manner \citep[see also][]{ChemlaSpector2010:Experimental-Ev}
+who call this type of theory ``unrestricted globalism'').}
 
@@
 
-The grammatical approach, as described so far, is not yet a fully
-articulated theory. To make concrete predictions, it must be
-supplemented by a selection principle that determines which of the
+The grammatical approach, as described so far, does not
+make testable predictions about the relative salience of our three
+candidate readings. In order to derive predictions about reading preferences,
+a selection principle is needed that determines which of the
 many readings made available by the grammar actually obtain or are
@@
 obligatory presence of $\exh$ with variability in the set of relevant
-alternatives. Another proposal is that readings are the more preferred
-the better they answer the contextually given question under
-discussion
-\citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. Yet
-another proposal is to select readings by comparison of logical
-strengths, as suggested by the \mymark{strongest meaning hypothesis}
+alternatives.  In the approach of \citet{Magri2011:Another-Argumen},
+alternatives may be pruned entirely in the extreme case. In that case, all occurrences
+of $\exh$ become vacuous resulting in a literal reading. However,
+\citet{Magri2011:Another-Argumen} does not formulate an explicit theory
+about which alternatives enter into the computation of sentence meaning
+under what circumstances. Therefore, it is not clear what his approach
+predicts about the relative salience of the candidate readings.
+
+Other proponents of grammaticalism assume that insertion of $\exh$ is optional.
+These approaches treat the ambiguity between our candidate readings as a
+structural one which resembles syntactic ambiguities. In order to derive
+predictions about reading preferences a mechanism of ambiguity resolution
+is needed in these approaches. One proposal is that readings are the
+more preferred the better they answer the contextually given question
+under discussion \citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}.
+Another proposal is to select readings by comparison of logical strengths, as suggested by the \mymark{strongest meaning hypothesis}
 of \citet{DalrympleKanazawa1998:Reciprocal-Expr}
-\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. We
-will focus entirely on this latter selection principle, because it
-seems to be the most prominent in the literature and because it makes
-the clearest predictions.
+\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. For now, we focus
+exclusively on this latter selection principle, because it seems to be
+the most prominent in the literature and because it makes the clearest
+predictions. In the discussion section (section~\ref{sec:discussion-1})
+alternative selection principles will be reconsidered.
 
@@
 
-Taking stock, traditionalism and grammaticalism predict different
-patterns of availability and preference for \as- and
-\es-sentences. Most notably, traditionalism does not predict local
-readings for \es-sentences to be available. Grammaticalism predicts
-that all readings are available, but, given the strongest meaning
-hypothesis, also comes with a clear indication of preference: literal
-meanings are dispreferred. All predictions are summarized in
-Table~\ref{tab:predictions}.
+Taking stock, traditionalism and grammaticalism make different
+predictions about the relative salience (and thus preference) of our candidate
+readings. Most notably, traditionalism does not predict local
+readings for \es-sentences to be available at all while grammaticalism does.
+Grammaticalism predicts that all candidate readings are available and,
+employing the strongest meaning hypothesis as selection principle, also
+comes with a clear prediction about preference: literal meanings are dispreferred.
+All predictions are summarized in Table~\ref{tab:predictions}.
 
@@
 
-Although traditionalism does not of itself predict local readings to
-be available, many authors who adhere to a traditionalist position
+Although restricted traditionalism does not of itself predict local readings to be
+available at all and even unrestricted traditionalism does not predict local
+readings for \es-sentences,  many authors who adhere to a traditionalist position
 propose that local readings are available if the embedded scalar item
-is prosodically marked by contrastive stress
-\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
-is taken to be continuous with other cases where pragmatic enrichments
-can take scope under logical operators if the relevant focal accent is
-present (\ref{bsp:Stress}).
+is prosodically marked by contrastive stress \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
+is taken to be continuous with other cases where pragmatic enrichments can
+take scope under logical operators if the relevant focal accent is present (\ref{bsp:Stress}).
 
@@
 
-To date, empirical evidence for this assumption is still scarce. One
-notable exception comes from a pilot study reported in
+To date, empirical investigations of this assumption are still scarce.  One
+notable exception is a pilot study reported in
 \citet{Frazier08}, in which participants were instructed to read
@@
 that capitalizing corresponded to contrastive stress. The task
-consisted in a forced-choice questionnaire with two given alternatives
-(such as {\it All of the students wrote some but not all of the
+consisted in a forced-choice questionnaire with two given alternative
+paraphrases  (such as {\it All of the students wrote some but not all of the
   official memos} vs. {\it All of the students wrote at least some of
@@
 {\it Mary will invite Fred or/OR Sam to barbecue}. After listening to
-these sentences, participants were presented two alternative readings
-({\it 1. She will invite Fred or Sam or possibly both}, or {\it 2.
+these sentences, two alternative paraphrases were presented to
+the participants (e.g. {\it She will invite Fred or Sam or possibly both} vs. {\it
   She will invite Fred or Sam but not both}).  The authors found a
@@
     \begin{center}
-      \includegraphics[scale=0.25]{../../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
-      \includegraphics[scale=0.25]{../../pictures/paper/Chemla_Spector_2010_RatingBar.png}
+      \includegraphics[scale=0.25]{pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
+      \includegraphics[scale=0.25]{pictures/paper/Chemla_Spector_2010_RatingBar.png}
     \end{center}
@@
     \label{fig:CS-Results-as}
-        \includegraphics[width=5.5cm]{../../pictures/paper/Chemla_Spector_2010_Results_AE.png}
+        \includegraphics[width=5.5cm]{pictures/paper/Chemla_Spector_2010_Results_AE.png}
   }
@@
     \label{fig:CS-Results-es}
-    \includegraphics[width=5.5cm]{../../pictures/paper/Chemla_Spector_2010_Results_GE.png}
+    \includegraphics[width=5.5cm]{pictures/paper/Chemla_Spector_2010_Results_GE.png}
   }  
@@
 \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
-But if intonation can have this role, it is necessary to control for
+But if prosody can have this role, it is necessary to control for
 silent accent placement. Ideally, therefore, we should present
@@
 	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_1.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_1.pdf}}
 	    \label{fig:exseqAS1}
@@
 	\subfloat[][Step 2]{
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_2.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_2.pdf}}
 	    \label{fig:exseqAS2}
@@
 	\subfloat[][Step 3 (\lit true)]{ 
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_3.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_3.pdf}}
 	    \label{fig:exseqAS3}
@@
 	\subfloat[][Step 4]{ 
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_4.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_4.pdf}}
 	    \label{fig:exseqAS4}
@@
 	\subfloat[][Step 5 (\glb true)]{
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_5.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_5.pdf}}
 	    \label{fig:exseqAS5}
@@
 	\subfloat[][Step 6]{ 
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_6.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_6.pdf}}
 	    \label{fig:exseqAS6}
@@
 	\subfloat[][Step 7 (\loc false)]{ 
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ae_01_7.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_7.pdf}}
 	    \label{fig:exseqAS7}
@@
 	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ge_01_1.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ge_01_1.pdf}}
 	    \label{fig:exseqES1}
@@
 	\subfloat[][Step 2 (\glb false)]{
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ge_01_2.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ge_01_2.pdf}}
 	    \label{fig:exseqES2}
@@
 	\subfloat[][Step 3 (\lit false)]{ 
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ge_01_3.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ge_01_3.pdf}}
 	    \label{fig:exseqES3}
@@
 	\subfloat[][Step 4]{ 
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ge_01_4.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ge_01_4.pdf}}
 	    \label{fig:exseqES4}
@@
 	\subfloat[][Step 5 (\loc true)]{
-		\fbox{\includegraphics[width=3.5cm]{../../pictures/ge_01_5.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{pictures/ge_01_5.pdf}}
 	    \label{fig:exseqES5}
@@
 verification task could possibly detect at least ordinal preference
-relations among multiple candidate readings. Finally, these conditions
-also controlled whether prosodic information can, in principle, shift
-answer patterns in the present task. Note that for our target
+relations among multiple candidate readings. Note that for our target
 sentences, the logical entailment relations between readings always
@@
 even if these were available only at a critical position following the
-preferred readings.
-
-We therefore included globally ambiguous \emph{late-closure
-  sentences} as in (\ref{bsp:target-related}), which have been
-repeatedly shown to exhibit interpretive preferences.
+preferred readings. Finally, these conditions also controlled whether 
+prosodic information can, in principle, shift answer patterns in the 
+present task.
+
+We therefore included globally ambiguous \emph{attachment ambiguities} 
+as in (\ref{bsp:target-related}), which have been shown to exhibit 
+interpretive preferences and can be disambiguated by prosodic information.
+
 \begin{exe}
@@
 \end{exe}
-In late-closure sentences, a modifier like a relative clause or a
-prepositional phrase (\acro{pp}) can be attached to one of two
-preceding hosts. For instance, in (\ref{bsp:target-related}), the
+In attachment ambiguities involving post-nominal modification, 
+an adjunct like a relative clause or a prepositional phrase 
+(\acro{pp}) can be attached to one of two preceding hosts. 
+For instance, in (\ref{bsp:target-related}), the
 \acro{pp} \emph{with suns} can be attached to the preceding noun
@@
   squares}, corresponding to the \emph{early-closure} (\ec) reading
-(\ref{bsp:target-related-EC}).  \lc-readings have been observed to be
-preferred over \ec-readings for sentences comparable to those in
-(\ref{bsp:target-related}) \citep[e.g.][]{Frazier87,Frazier82}.
+(\ref{bsp:target-related-EC}).  \lc-readings have been generally 
+observed to be preferred over \ec-readings \citep[e.g.][]{Fodor98}
+for an overview of different languages; but see \citet{CliftonCarlsonFrazier2002}
+for counterevidence). Crucially, an \lc-preference for \acro{pp}-attachment 
+structures has also been attested for German \citep[][]{KoniecznyHemforth2000}.
 
@@
 	\subfloat[][Step 2]{ 
-		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_2.pdf}}
+		\fbox{\includegraphics[width=5cm]{pictures/lc_01_2.pdf}}
 	    \label{fig:exlc2}
@@
 	\subfloat[][Step 3 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_3.pdf}}
+		\fbox{\includegraphics[width=5cm]{pictures/lc_01_3.pdf}}
 	    \label{fig:exlc3}
@@
 	\subfloat[][Step 4]{
-		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_4.pdf}}
+		\fbox{\includegraphics[width=5cm]{pictures/lc_01_4.pdf}}
 	    \label{fig:exlc4}
@@
 	\subfloat[][Step 5 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_5.pdf}}
+		\fbox{\includegraphics[width=5cm]{pictures/lc_01_5.pdf}}
 	    \label{fig:exlc5}
@@
 	\subfloat[][Step 6 (\ec false)]{
-		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_6.pdf}}
+		\fbox{\includegraphics[width=5cm]{pictures/lc_01_6.pdf}}
 	    \label{fig:exlc6}
@@
 	\subfloat[][Step 7 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../../pictures/lc_01_7.pdf}}
+		\fbox{\includegraphics[width=5cm]{pictures/lc_01_7.pdf}}
 	    \label{fig:exlc7}
@@
 	\subfloat[][Step 2]{ 
-		\fbox{\includegraphics[width=5cm]{../../pictures/ec_01_2.pdf}}
+		\fbox{\includegraphics[width=5cm]{pictures/ec_01_2.pdf}}
 	    \label{fig:exec1}
@@
 	\subfloat[][Step 3 (\ec false)]{
-		\fbox{\includegraphics[width=5cm]{../../pictures/ec_01_3.pdf}}
+		\fbox{\includegraphics[width=5cm]{pictures/ec_01_3.pdf}}
 	    \label{fig:exec2}
@@
 	\subfloat[][Step 4]{
-		\fbox{\includegraphics[width=5cm]{../../pictures/ec_01_4.pdf}}
+		\fbox{\includegraphics[width=5cm]{pictures/ec_01_4.pdf}}
 	    \label{fig:exec2}
@@
 	\subfloat[][Step 5 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{../../pictures/ec_01_5.pdf}}
+		\fbox{\includegraphics[width=5cm]{pictures/ec_01_5.pdf}}
 	    \label{fig:exec2}
@@
 are usually assumed to be realized by a special contour in English
-(i.e. L+H*, see \citet{Pierrehumbert90}), the exact phonological
+(i.e. L+H*, see \cite{Pierrehumbert90}), the exact phonological
 classification of contrast in German is still under debate
-\citep[see][]{Uhmann91,Fery93,Grabe98,Toepel06, Sudhoff10}.  Still,
+\citep[see][]{Uhmann91,Fery93,Grabe98,Toepel06,Sudhoff10}.  Still,
 all of these approaches have in common that from an acoustic
@@
 speakers reliably \textit{produce} disambiguating cues in such
-constructions \citep[e.g.][]{Allbritton96,Kraljik05, Snedeker03,
-  Schafer00}, overt prosodic boundaries are generally acknowledged to
-guide interpretive processes of late-closure sentences in
-\textit{comprehension} \citep[e.g.][]{Steinhauer99, Augurzky06}.
-Specifically, it has been shown that prosodically separating a
-modifier from the directly preceding material supports an \ec-reading,
-whereas separating the two potential attachment sites is supportive of
-an \lc-reading. Thus, a phrase boundary between {\it squares} and {\it
-  with} in (\ref{bsp:target-related}) supports an \ec-reading, whereas
-a prosodic phrase boundary following {\it circles} supports an
-\lc-reading.
+constructions
+\citep[e.g.][]{Allbritton96,Kraljik05,Snedeker03,Schafer00}, overt
+prosodic boundaries are generally acknowledged to guide interpretive
+processes of attachment ambiguities in \textit{comprehension}
+\citep[e.g.][]{Augurzky06,Beach1991,CliftonCarlsonFrazier2002,KjelgaardSpeer1999,
+  SchaferSpeerWarrenWhite2000,Steinhauer99}.  Specifically, it has
+been shown that prosodically separating a modifier from the directly
+preceding material supports an \ec-reading, whereas separating the two
+potential attachment sites is supportive of an \lc-reading
+\citep[e.g.][]{CliftonCarlsonFrazier2002,Fodor02,Jun2003}.  Thus, a
+phrase boundary between {\it squares} and {\it with} in
+(\ref{bsp:target-related}) supports an \ec-reading, whereas a prosodic
+phrase boundary following {\it circles} supports an \lc-reading.
 
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/minmax_ae.png}}
+		% \fbox{\includegraphics[width=5.5cm]{pictures/paper/minmax_ae.png}}
 	    \label{fig:minmax_ae}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/minmax_ge.png}}
+		% \fbox{\includegraphics[width=5.5cm]{pictures/paper/minmax_ge.png}}
 	    \label{fig:minmax_ge}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/duration_ae.png}}
+		% \fbox{\includegraphics[width=5.5cm]{pictures/paper/duration_ae.png}}
 	    \label{fig:duration_ae}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/duration_ge.png}}
+		% \fbox{\includegraphics[width=5.5cm]{pictures/paper/duration_ge.png}}
 	    \label{fig:duration_ge}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/minmax_fi.png}}
+		% \fbox{\includegraphics[width=5.5cm]{pictures/paper/minmax_fi.png}}
 	    \label{fig:acoustics_fi}
@@
 \end{tikzpicture}
-		% \fbox{\includegraphics[width=5.5cm]{../../pictures/paper/duration_fi.png}}
+		% \fbox{\includegraphics[width=5.5cm]{pictures/paper/duration_fi.png}}
 	    \label{fig:duration_fi}
@@
 \emph{error} if they were not. As expected, most answers classify as
-\lc-readings, fewer as \ec-readings. Moreover, intonation does seem to
+\lc-readings, fewer as \ec-readings. Moreover, prosody does seem to
 have the expected effect as well: as compared to neutral phrasing,
-\lc-cueing intonation increases the count for \lc-readings, while
+\lc-cueing prosody increases the count for \lc-readings, while
 \ec-cueing prosody increases the count for \ec-readings. If we compare
-the number of \lc- or \ec-readings for each intonation type across
+the number of \lc- or \ec-readings for each prosodic variant across
 sequences, we see that there are always more answers indicative of the
@@
 28 \emph{false} answers at step 5 where \emph{true} answers would be
-taken as indicative of \lc-readings. Finally, intonation patterns that
-cue dispreferred \ec-readings seem to have led to more mistakes than
-other intonation patterns.
+taken as indicative of \lc-readings. Finally, prosodic cues for
+dispreferred \ec-readings seem to have led to more mistakes than
+other prosodic patterns.
 
@@
 such three-placed vectors for the critical conditions, one for each
-target sentence-intonation pair. For the preference-related control
+target sentence-prosody pair. For the preference-related control
 conditions, we look at three vectors $p^k =
@@
 vectors give the relative salience of \lc- and \ec-readings for
-different types of intonation. The salience of readings is independent
+different types of prosody. The salience of readings is independent
 of the pictorial sequence. If there is a tendency to judge sentences
@@
 that some sentence types (e.g., non-monotonic quantifiers) or some
-kind of intonation (e.g., \ec-cues) might be harder to process. A
+kind of prosody (e.g., \ec-cues) might be harder to process. A
 decision can be wrong but incidentally coincide with an answer that is
@@
 Taking this together we calculate, for each pair $k$ of target
-sentence type and intonation type, a probability vector $\myvec{t}^k =
+sentence type and prosody type, a probability vector $\myvec{t}^k =
 \tuple{t^k_{\text{lit}},t^k_{\text{loc}},t^k_{\text{glb}},t^k_{\text{err}}}$
@@
 global or as error. For example, for \as-sentences with neutral
-intonation, where literal can be judged before global before local, we
+prosody, where literal can be judged before global before local, we
 get:
@@
 \tuple{t^k_{\text{late}},t^k_{\text{early}},t^k_{\text{err}}}$ for
-each preference-related control sentence under intonation $k$, taking
+each preference-related control sentence under prosody $k$, taking
 into account which reading can be judged first and the length of the
@@
 by local, followed by global readings. There does not appear to be a
-significant effect of intonation (by visual comparison of 95\%
+significant effect of prosody (by visual comparison of 95\%
 HDIs). For \as-sentences, the same preference order holds in tendency,
@@
 global readings at all, and no local readings for \as-sentence under
-neutral intonation. There is support for a belief in local readings in
+neutral prosody. There is support for a belief in local readings in
 the \as-acc condition up to a ROPE of $[0;0.028)$.
@@
   \subfloat[][neutral]{
-      \includegraphics[width=0.45\textwidth]{PostDiffT_ASntr.pdf}
+      \includegraphics[width=0.45\textwidth]{pics/PostDiffT_ASntr.pdf}
   }
@@
   \subfloat[][accented]{
-      \includegraphics[width=0.45\textwidth]{PostDiffT_ASacc.pdf}
+      \includegraphics[width=0.45\textwidth]{pics/PostDiffT_ASacc.pdf}
   }
@@
 
-  \includegraphics[width=\textwidth]{../../pictures/Acoustics/Table-B.png}
+  \includegraphics[width=\textwidth]{pictures/Acoustics/Table-B.png}
 
@@
 
-  \includegraphics[width=\textwidth]{../../pictures/Acoustics/Table-A.png}
+  \includegraphics[width=\textwidth]{pictures/Acoustics/Table-A.png}
 
@@
 
-  \includegraphics[width=\textwidth]{../../pictures/Acoustics/Table-D.png}
+  \includegraphics[width=\textwidth]{pictures/Acoustics/Table-D.png}
 
@@
 
-  \includegraphics[width=\textwidth]{../../pictures/Acoustics/Table-C.png}
+  \includegraphics[width=\textwidth]{pictures/Acoustics/Table-C.png}
 

### 2015-02-03 text/paper/revision_01/paper.tex
K2 paper revisions my turn started

@@
   Experimental Revisit} 
-\author{% Fabian
-  % Schlotterbeck, Michael Franke and Petra Augurzky
+\author{% Michael Franke, Fabian Schlotterbeck and Petra Augurzky
 } 
@@
 lies at the heart of a current debate about the nature of quantity
-inferences and the demarkation between grammar (i.e. syntax/semantics)
-and domain-general reasoning procedures (i.e. pragmatics). The controversy
-is usually seen as one between two main competing theoretical positions
-\citep[see][for a detailed comparison of the two]{ChemlaSingh2014:Remarks-on-the-}.
-Simplifying things for now, these two types of theories make clearly different
-predictions about how salient the local readings, in particular, should be.
-The first position which we refer to as \mymark{traditionalism} (Chemla \& Singh’s ``Gricean approach'') holds that local readings should not be salient at all.
-The second one which we call \mymark{grammaticalism}
-(Chemla \& Singh’s ``grammatical approach'') holds that local readings
-are unproblematically available and even at least as salient
-as the literal ones (see Section \ref{sec:theories-predictions} for a more
-thorough exposition of the theories and their predictions).
+inferences. %  and the demarkation between grammar (i.e. syntax/semantics)
+% and domain-general reasoning procedures (i.e. pragmatics).
+The controversy is usually seen as one between two main competing
+theoretical positions \citep[see][for a detailed comparison of the
+two]{ChemlaSingh2014:Remarks-on-the-}.  Simplifying things for now,
+these two types of theories make clearly different predictions about
+how salient the local readings, in particular, should be.  The first
+position which we refer to as \mymark{traditionalism} (similar to, but
+not identical to Chemla \& Singh’s ``Gricean approach'') holds that
+local readings should not be salient at all. The second one which we
+call \mymark{grammaticalism} (Chemla \& Singh’s ``grammatical
+approach'') holds that local readings are unproblematically available
+and maybe even at least as salient as the literal ones (see Section
+\ref{sec:theories-predictions} for a more thorough exposition of the
+theories and their predictions).
 
@@
 
-More generally, two prerequisites have to be met in order to make use of
-experimental data to decide between theoretical positions regarding the
-computation of quantity inferences. Firstly, both traditionalism and grammaticalism
-have to be amended with additional assumptions to derive testable
-predictions about the relative salience of candidate readings. For example,
-hypothezised effects of prosodic marking have to be taken into account before
-we can test traditionalism empirically using sentences  (\ref{bsp:AE}) and (\ref{bsp:GE}).
-We will address this extant position as the \mymark{prosodic markedness hypothesis}
-and argue that, if prosody is hypothesized to play a central role, it is vital
-to present target sentences auditorily or to control for effects of  “silent prosody”
-that subjects may apply when reading a sentence. Secondly, the relative
-salience of candidate readings has to be operationalized properly, i.e. we
-have to devise methods to measure relative salience. For example, typicality
-effects and logical dependencies between readings have to be controlled for
-when evaluating speaker judgments in terms of the salience of candidate readings.
-Both of these prerequisites are related to formulating what \citet{ChemlaSingh2014:Remarks-on-the-}
-call ``linking functions'' which connect the core theories to the dependent
-variables of an experiment. Without proper linking functions it is hard
+More generally, two prerequisites have to be met in order to make use
+of experimental data to decide between theoretical positions regarding
+the computation of quantity inferences. Firstly, both traditionalism
+and grammaticalism have to be augmented with additional assumptions to
+derive testable predictions about the relative salience of candidate
+readings. For example, hypothezised effects of prosodic marking have
+to be taken into account before we can test traditionalism empirically
+using sentences (\ref{bsp:AE}) and (\ref{bsp:GE}).  We will address
+this extant position as the \mymark{prosodic markedness hypothesis}
+and argue that, if prosody is hypothesized to play a central role, it
+is vital to present target sentences auditorily or to control for
+effects of “silent prosody” that subjects may apply when reading a
+sentence. Secondly, the relative salience of candidate readings has to
+be operationalized properly, i.e., we have to devise methods to
+measure relative salience. For example, typicality effects and logical
+dependencies between readings have to be controlled for when
+evaluating speaker judgments in terms of the salience of candidate
+readings.  Both of these prerequisites are related to formulating what
+\citet{ChemlaSingh2014:Remarks-on-the-} call ``auxiliary assumptions''
+that are necessary to enable theoretical accounts to make predictions
+about processing. Our emphasis here is not on processing accounts, but
+on predictions of behavioral data --- what is sometimes, perhaps
+misleadingly, called a computational-level perspective. But even so,
+traditionalism and grammaticalism have to summon auxiliary assumptions
+which connect the core theories to the dependent variables of a
+behavioral experiment. Without proper auxiliary assumptions it is hard
 (or impossible) to test traditionalism or grammaticalism empirically.
 
-This paper presents results form an experimental study designed to deal with
-the mentioned problems. The focus is on testing certain formulations of traditionalism
-and grammaticalsim that are explicit enough to derive testable predictions about the
-relative salience of candidate readings. For practical reasons, we choose what we consider
-the most prominent of such formulations. In order to address the prosodic markedness
-hypothesis, we presented sentence materials auditorily and explicitly manipulated contrastive
-stress on embedded scalar items. In order operationalize the relative salience of candidate
-readings, we employed an \mymark{incremental verification task} in which parts of a to-be-evaluated
-picture were hidden and only revealed piece-wise at the participants’ request until they felt able
-to give a binary truth-value judgement \citep[see][]{Conroy2008}. This way, we catered for
-potential pictorial confounds, such as from typicality. To analyze the obtained data in terms
-of relative salience of candidate readings, we furthermore employed a statistical model of
-how the salience of readings guided participants judgments in the incremental verification task. We
-validated this method by including control conditions testing ambiguous sentences with a
-well-known preference on available readings. We argue that this method provides
-categorical behavioral data that is both clearly indicative of the reading preferences
-among participants and independent of any potential pictorial confounds, such as
-the mentioned typicality effects.
-
-The data obtained by this method is \emph{prima facie} problematic for both
-traditionalism and grammaticalism (or at least what we consider the most
-prominent versions thereof). However, we want to stress from the outset
-that, while the experimental results allow us to derive restrictions on which
-linking functions are conceivable for traditionalism and grammaticalism, conclusions
-about the general validity of the two core theories will be limited
-\citep[cf.][]{ChemlaSingh2014:Remarks-on-the-} because these hardly make falsifiable
-predictions without the necessary linking functions. Contrary to the predictions
-of common versions of traditionalism, we observed many answers indicative of
-local readings of \es-sentences, irrespective of prosodic markedness. But also
-prominent versions of grammaticalism are incongruent with the observed data.
-Backed up by the \mymark{strongest meaning hypothesis}
-\citep{DalrympleKanazawa1998:Reciprocal-Expr} as a
-disambiguation criterion \citep[as suggested by][]{ChierchiaFox2008:The-Grammatical},
-grammaticalism predicts local readings to be the preferred ones, but
-we found no evidence for that. More strongly even, the preference order among
-putative readings suggested by our data cannot even in principle be
-explained by comparisons of logical strength among putative
-readings. In sum, our data shed doubt on both traditionalism and grammaticalism
-in their currently most common forms. We conclude the paper by some thoughts on
-how either position could be amended in the light of our data.
+This paper presents results form an experimental study designed to
+deal with the mentioned problems. The focus is on testing certain
+formulations of traditionalism and grammaticalsim that are explicit
+enough to derive testable predictions about the relative salience of
+candidate readings. For practical reasons, we must choose auxiliary
+assumptions that actually deliver \emph{ex ante} predictions, even
+though this may not exhaust the space of variations on either core
+theory that have been floated in the recent literature (see
+Section~\ref{sec:theories-predictions} for discussion). In order to
+address the prosodic markedness hypothesis, we presented sentence
+materials auditorily and explicitly manipulated contrastive stress on
+embedded scalar items. In order operationalize the relative salience
+of candidate readings, we employed an \mymark{incremental verification
+  task} in which parts of a to-be-evaluated picture were hidden and
+only revealed piece-wise at the participants’ request until they felt
+able to give a binary truth-value judgement
+\citep[see][]{Conroy2008}. To analyze the obtained data in terms of
+relative salience of candidate readings, we furthermore employed a
+statistical model of how the salience of readings guided participants
+judgments in the incremental verification task. We validated this
+method by including control conditions testing ambiguous sentences
+with a well-known preference on available readings. We argue that this
+method provides categorical behavioral data that is both clearly
+indicative of the reading preferences among participants and largely
+independent of potential pictorial confounds, such as the mentioned
+typicality effects.
+
+The data obtained by this method is \emph{prima facie} problematic for
+both traditionalism and grammaticalism, at least if augmented by the
+auxiliary assumptions which we adopted here. However, we want to
+stress from the outset that, while the experimental results allow us
+to derive restrictions on which auxiliary assumptions are conceivable
+for traditionalism and grammaticalism, definite conclusions about the
+general validity of the two core theories will be limited
+\citep[cf.][]{ChemlaSingh2014:Remarks-on-the-}. Bearing this in mind,
+we can summarize our main findings crudely as follows. Contrary to the
+predictions of common versions of traditionalism, we observed many
+answers indicative of local readings of \es-sentences, irrespective of
+prosodic markedness. But also prominent versions of grammaticalism are
+incongruent with the observed data.  Backed up by the
+\mymark{strongest meaning hypothesis}
+\citep{DalrympleKanazawa1998:Reciprocal-Expr} as a disambiguation
+criterion \citep[as suggested by][]{ChierchiaFox2008:The-Grammatical},
+grammaticalism predicts local readings to be much more salient than we
+found evidence for in our data. More strongly even, the preference
+order among putative readings suggested by our data cannot even in
+principle be explained by comparisons of logical strength among
+putative readings. This finding is independently relevant in the light
+of the fact that the strongest meaning hypothesis is frequently
+summoned as a disambiguation criterion also in other domains, such as
+the interpretation of reciprocals
+\citep{DalrympleKanazawa1998:Reciprocal-Expr} or vague predicates
+\citep{CobrerosEgre2012:Tolerant-Classi}. In sum, our data shed doubt
+on both traditionalism and grammaticalism under prominent auxiliary
+assumptions. We conclude the paper by some thoughts on how either
+position could be amended in the light of our data.
 
@@
 sentences. Section~\ref{sec:theories-predictions} works out the
-predictions of traditionalism and grammaticalism (plus prominent linking functions) 
+predictions of traditionalism and grammaticalism (plus prominent auxiliary assumptions) 
 about availability and relative salience of readings for these
@@
 There are two main theoretical positions which make different
-predictions about the readings of \as- and \es-sentences \citep[see][for
-overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation,ChemlaSingh2014:Remarks-on-the-}.
-We will refer to these as \mymark{traditionalism} and \mymark{grammaticalism}
-and treat each one in turn.  As already mentioned in the introduction there is some
-leeway in assessing the predictions for each approach depending on which of several
-additional assumptions to adopt. Therefore, we will distinguish different varieties
-of both of them. While these are certainly not the only possible varieties, they are,
-in our perception, the most prominent ones. Focusing on exactly these thus has
-practical relevance. Their predictions are summarized in Table~\ref{tab:predictions}
-on page~\pageref{tab:predictions}. Below, in the discussion section
-(section~\ref{sec:discussion-1}), further conceivable varieties of traditionalism
-and grammaticalism will be discussed.
+predictions about the readings of \as- and \es-sentences
+\citep[see][for
+overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation,ChemlaSingh2014:Remarks-on-the-}. We
+will refer to these as \mymark{traditionalism} and
+\mymark{grammaticalism} and treat each one in turn.  As already
+mentioned in the introduction, there is some leeway in assessing the
+predictions for each approach depending on which auxiliary assumptions
+to adopt. Therefore, we will distinguish different varieties of either
+core theory. While there are certainly other varieties conceivable,
+they are, in our perception, the most prominent ones, but, more
+importantly, also the most practical ones in that they give us precise
+and testable \emph{ex ante} predictions about expected behavioral data
+(as opposed to \emph{ex post} explanations after inspecting the
+data). The predictions of the considere core theories plus their
+auxiliary assumptions are summarized in Table~\ref{tab:predictions} on
+page~\pageref{tab:predictions}. Below, in the discussion section
+(section~\ref{sec:discussion-1}), further conceivable varieties of
+traditionalism and grammaticalism will be discussed \emph{after}
+inspecting the relevant data.
 
@@
 \citet{vanRooijSchulz:ExhaustiveInterpretation},
-\citet{Geurts2010:Quantity-Implic} or
-\citet{Franke2011:Quantity-Implic}.
+\citet{Geurts2010:Quantity-Implic},
+\citet{Franke2011:Quantity-Implic}, or \citet{GoodmanStuhlmuller2013:Knowledge-and-I}.
 
@@
 and goal-oriented. Usually, the assumed goal of conversation is the
-cooperative exchange of relevant information from speaker to hearer.
+cooperative exchange of relevant information from speaker to
+hearer.\footnote{Our conception of ``traditionalism'' is less
+  stringent that \citeauthor{ChemlaSingh2014:Remarks-on-the-}'s
+  ``Gricean approach.'' We allow our traditionalism to violate the
+  constraint that all considered alternatives must be stronger than
+  the one to be interpreted, so as to allow, for instance, global
+  readings of \es-sentences where the alternative
+  (\ref{bsp:GE-Alternative}) does not asymmetrically entail the
+  to-be-interpreted (\ref{bsp:GE}) (see more below). We would even
+  subsume under traditionalism abductive reasoning to the best
+  explanation of what lexical meaning a speaker had intended to convey
+  on an occasion of use in an embedded context, if such an account
+  could be formulated consistently and in such a manner that it makes
+  testable predictions.}
 
@@
 
-Consequently, there are at least two varieties of traditionalism that,
-depending on which extra assumptions we make, yield slightly
-different predictions: the \mymark{the strong variety of traditionalism}
-maintains that the extra assumptions of the Gricean recipe hold
-(e.g., as a matter of strong default) and therefore predicts that global
-readings are preferred over literal ones; \mymark{the weak variety of
-traditionalism} holds that the auxiliary assumptions are more fragile
-and context dependent and thus predicts that literal readings may
-often be preferred over global ones. In Table~\ref{tab:predictions}
-(p.~\pageref{tab:predictions}), this prediction of weak traditionalism
-is captured by a preference of literal over global readings because it
-may \emph{a priori} seem implausible from the perspective of weak
-traditionalism that all the necessary assumptions to derive global
-readings are met. \fn{We mention for clarity that although weak traditionalism does
-  not predict global readings to be generally preferred, it might still predict
-  an \emph{epistemically weak implicature}, similar to the global
-  reading, that the speaker is uncertain whether the stronger
-  alternative is true. (See also the discussion in
-  Section~\ref{sec:discussion-1})} For weak traditionalism, it is of course an empirical
-task to determine under which circumstances the auxiliary assumptions
-are met.
+Consequently, there are at least two varieties of traditionalism that
+yield slightly different predictions, depending on which extra
+assumptions we make about the relevant context of interpretation. If
+the context (e.g., our experimental design) makes the extra
+assumptions of the Gricean recipe needed to derive non-epistemic
+global readings sufficiently salient, then we get the prediction that
+global readings should be preferred over literal ones; otherwise the
+prediction is that literal readings are preferred over global ones. We
+call the former position \mymark{the strong variety of traditionalism}
+and the latter the \mymark{the weak variety of traditionalism}.\fn{We
+  mention for clarity that although weak traditionalism does not
+  predict literal readings to be more salient than non-epistemic
+  global readings, it might still predict an \emph{epistemically weak
+    implicature}, similar to the global reading, that the speaker is
+  uncertain whether the stronger alternative is true. (See also the
+  discussion in Section~\ref{sec:discussion-1})} It is of course an
+empirical task to determine when a context would favor either variety
+of traditionalism. For our purposes, however, it suffices to note that
+the core theory is plausibly compatible with either preference
+relation: literal over global or the other way around (see also
+Table\ref{tab:predictions}).
 
@@
 \as-sentences is not available; in contrast, \mymark{unrestricted
-  traditionalism} assumes that
-(\ref{bsp:AE-Alternatives-Extended}) is available and so is the
-local reading.\fn{The term traditionalism may be misleading here
-because traditionalists usually assume that scalar implicatures should
-only be computed when a sentence is uttered in a context in which a
-logically stronger alternative is relevant \cite{ChemlaSingh2014:Remarks-on-the-}. However, the alternative
-in (\ref{bsp:AE-Alternatives-Extended}) is not stronger than
-(\ref{bsp:AE}). For completeness sake, we still decided to subsume
-“unrestricted traditionalism” under traditionalism because, once
-alternatives like (\ref{bsp:AE-Alternatives-Extended}) are acknowledged,
-the local reading of \as-sentences can be derived in a
-straightforward traditionalist manner \citep[see also][]{ChemlaSpector2010:Experimental-Ev}
-who call this type of theory ``unrestricted globalism'').}
+  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
+available and so is the local reading.\fn{The term traditionalism may
+  be misleading here because traditionalists usually assume that
+  scalar implicatures should only be computed when a sentence is
+  uttered in a context in which a logically stronger alternative is
+  relevant \cite{ChemlaSingh2014:Remarks-on-the-}. However, the
+  alternative in (\ref{bsp:AE-Alternatives-Extended}) is not stronger
+  than (\ref{bsp:AE}). For completeness sake, we still decided to
+  subsume “unrestricted traditionalism” under traditionalism because,
+  once alternatives like (\ref{bsp:AE-Alternatives-Extended}) are
+  acknowledged, the local reading of \as-sentences can be derived in a
+  straightforward traditionalist manner \citep[see also][who call this
+  type of theory ``unrestricted
+  globalism'']{ChemlaSpector2010:Experimental-Ev}.}
 
@@
 
-The grammatical approach, as described so far, does not
-make testable predictions about the relative salience of our three
-candidate readings. In order to derive predictions about reading preferences,
-a selection principle is needed that determines which of the
-many readings made available by the grammar actually obtain or are
+The grammatical approach, as described so far, does not yet make
+falsifiable predictions about the relative salience of our three
+candidate readings. In order to derive predictions about reading
+preferences, a selection principle is needed that determines which of
+the many readings made available by the grammar actually obtain or are
 preferred. Proponents of grammaticalism are aware of this and have
@@
 alternatives.  In the approach of \citet{Magri2011:Another-Argumen},
-alternatives may be pruned entirely in the extreme case. In that case, all occurrences
-of $\exh$ become vacuous resulting in a literal reading. However,
-\citet{Magri2011:Another-Argumen} does not formulate an explicit theory
-about which alternatives enter into the computation of sentence meaning
-under what circumstances. Therefore, it is not clear what his approach
-predicts about the relative salience of the candidate readings.
-
-Other proponents of grammaticalism assume that insertion of $\exh$ is optional.
-These approaches treat the ambiguity between our candidate readings as a
-structural one which resembles syntactic ambiguities. In order to derive
-predictions about reading preferences a mechanism of ambiguity resolution
-is needed in these approaches. One proposal is that readings are the
-more preferred the better they answer the contextually given question
-under discussion \citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}.
-Another proposal is to select readings by comparison of logical strengths, as suggested by the \mymark{strongest meaning hypothesis}
+alternatives may be pruned entirely in the extreme case. In that case,
+all occurrences of $\exh$ become vacuous resulting in a literal
+reading. However, \citet{Magri2011:Another-Argumen} does not formulate
+an explicit theory about which alternatives enter into the computation
+of sentence meaning under what circumstances. Therefore, it is not
+clear what his approach predicts about the relative salience of the
+candidate readings.
+
+Other proponents of grammaticalism assume that insertion of $\exh$ is
+optional.  These approaches treat the ambiguity between our candidate
+readings as a structural one which resembles syntactic ambiguities. In
+order to derive predictions about reading preferences a mechanism of
+ambiguity resolution is needed in these approaches. One proposal is
+that readings are the more preferred the better they answer the
+contextually given question under discussion
+\citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}.
+Another proposal is to select readings by comparison of logical
+strengths, as suggested by the \mymark{strongest meaning hypothesis}
 of \citet{DalrympleKanazawa1998:Reciprocal-Expr}
-\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. For now, we focus
-exclusively on this latter selection principle, because it seems to be
-the most prominent in the literature and because it makes the clearest
-predictions. In the discussion section (section~\ref{sec:discussion-1})
-alternative selection principles will be reconsidered.
+\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. For
+now, we focus exclusively on this latter selection principle, because
+it seems to be the most prominent in the literature and because it
+makes the clearest predictions. In the discussion section
+(section~\ref{sec:discussion-1}) alternative selection principles will
+be reconsidered.
 
@@
 
-Taking stock, traditionalism and grammaticalism make different
-predictions about the relative salience (and thus preference) of our candidate
-readings. Most notably, traditionalism does not predict local
-readings for \es-sentences to be available at all while grammaticalism does.
+Taking stock, under the auxiliary assumptions adopted here,
+traditionalism and grammaticalism make different predictions about the
+relative salience (and thus preference) of our candidate
+readings. Most notably, traditionalism does not predict local readings
+for \es-sentences to be available at all while grammaticalism does.
 Grammaticalism predicts that all candidate readings are available and,
-employing the strongest meaning hypothesis as selection principle, also
-comes with a clear prediction about preference: literal meanings are dispreferred.
-All predictions are summarized in Table~\ref{tab:predictions}.
+employing the strongest meaning hypothesis as disambiguation
+principle, also comes with a clear prediction about preference:
+literal meanings are dispreferred.  All predictions are summarized in
+Table~\ref{tab:predictions}.
 
@@
   their data, as if it had been obtained for \es-sentences.} Subjects
-were presented with pictures similar to in Figure~\ref{fig:weak} and
+were presented with pictures similar to those in Figure~\ref{fig:weak} and
 \ref{fig:local} (pages \pageref{fig:weak} and \pageref{fig:local})
@@
 picture with respect to some meaning may affect graded truth-value
-judgments. They show that graded judgments of \as-sentences differ
-significantly for different pictures that agree on the truth value of
-relevant readings but differ with respect to the amount of connections
-between icons. \citeauthor{ChemlaSpector2010:Experimental-Ev} suggest
-that typicality of the pictorial material can account for these
+judgments: a sentence like \emph{Some of the 10 marbles are white} is
+more typical, intuitively speaking, in a situation with 4 white
+marbles than in a situation with 8 or 9 white marbles \citep[for more
+on the controversial interpretation of ``typicality'' in this context
+see][]{Tielvan-Tiel2014:Quantity-Matter,Cummins2014:Typicality-made,
+  ,Franke2014:Typical-use-of-}. \citeauthor{ChemlaSpector2010:Experimental-Ev}
+show that graded judgments of \as-sentences differ significantly for
+different pictures that agree on the truth value of relevant readings
+but differ with respect to the amount of connections between
+icons. \citeauthor{ChemlaSpector2010:Experimental-Ev} suggest that
+typicality of the pictorial material can account for these
 differences, but submit that this does not explain away the high
@@
 had an influence on responses, we included a second type of control
-conditions.  These controls served as a test whether the incremental
+conditions.  These controls also tested whether the incremental
 verification task could possibly detect at least ordinal preference
@@
 require local readings to be evaluated at the end of a sequence. It
-could thus in principle be possible that subjects never reach this
-point, because they give truth-value judgements earlier, thereby
-ending the trial. In that case it would be unclear whether these
-decisions had been affected by a general unavailability of local
-readings or by the fact that one of the earlier presented readings is
-the preferred one. By including globally ambiguous structures with a
-known preference over available readings, we thus tested whether
-participants in our task occasionally choose dispreferred readings,
-even if these were available only at a critical position following the
-preferred readings. Finally, these conditions also controlled whether 
-prosodic information can, in principle, shift answer patterns in the 
-present task.
-
-We therefore included globally ambiguous \emph{attachment ambiguities} 
-as in (\ref{bsp:target-related}), which have been shown to exhibit 
-interpretive preferences and can be disambiguated by prosodic information.
+could be that subjects never reach this point, because they give
+truth-value judgements earlier, thereby ending the trial. In that case
+it would be unclear whether these decisions had been affected by a
+general unavailability of local readings or by the fact that one of
+the earlier presented readings is the preferred one. By including
+globally ambiguous structures with a known preference over available
+readings, we thus tested whether participants in our task occasionally
+choose dispreferred readings, even if these were available only at a
+critical position following the preferred readings. Finally, these
+conditions also controlled whether prosodic information can, in
+principle, shift answer patterns in the present task.
+
+We therefore included sentences with \emph{attachment ambiguities} as
+in (\ref{bsp:target-related}), which have been shown to exhibit
+interpretive preferences and can be disambiguated by prosodic
+information.\footnote{It is possible that attachment ambiguities are
+  different from the ``pragmatic ambiguity'' in \as- and
+  \es-sentences, so that information about the former is not ideally
+  informative about the latter. We will address this worry in
+  Section~\textcolor{red}{XYZ}, where we argue that this does not
+  affect the main conclusion that we would like to draw from our data
+  eventually.}
 
@@
 \end{xlist}
-
 \end{exe}
-In attachment ambiguities involving post-nominal modification, 
-an adjunct like a relative clause or a prepositional phrase 
-(\acro{pp}) can be attached to one of two preceding hosts. 
-For instance, in (\ref{bsp:target-related}), the
-\acro{pp} \emph{with suns} can be attached to the preceding noun
-\emph{squares}, resulting in the so-called \emph{late-closure} (\lc)
-reading ((\ref{bsp:target-related-LC}). Alternatively, the \acro{pp}
-can be attached to the whole conjunctive \acro{np} \emph{circles and
+In attachment ambiguities involving post-nominal modification, an
+adjunct like a relative clause or a prepositional phrase (\acro{pp})
+can be attached to one of two preceding hosts.  For instance, in
+(\ref{bsp:target-related}), the \acro{pp} \emph{with suns} can be
+attached to the preceding noun \emph{squares}, resulting in the
+so-called \emph{late-closure} (\lc) reading
+((\ref{bsp:target-related-LC}). Alternatively, the \acro{pp} can be
+attached to the whole conjunctive \acro{np} \emph{circles and
   squares}, corresponding to the \emph{early-closure} (\ec) reading
 (\ref{bsp:target-related-EC}).  \lc-readings have been generally
-observed to be preferred over \ec-readings \citep[e.g.][]{Fodor98}
-for an overview of different languages; but see \citet{CliftonCarlsonFrazier2002}
-for counterevidence). Crucially, an \lc-preference for \acro{pp}-attachment 
-structures has also been attested for German \citep[][]{KoniecznyHemforth2000}.
+observed to be preferred over \ec-readings (e.g., \cite{Fodor98} for
+an overview of different languages, but see also
+\cite{CliftonCarlsonFrazier2002} for counterevidence). Crucially, an
+\lc-preference for \acro{pp}-attachment structures has also been
+attested for German \citep[][]{KoniecznyHemforth2000}.
 
@@
 constructions
-\citep[e.g.][]{Allbritton96,Kraljik05,Snedeker03,Schafer00}, overt
+\citep[e.g.][]{Allbritton96,Schafer00,Snedeker03,Kraljik05}, overt
 prosodic boundaries are generally acknowledged to guide interpretive
 processes of attachment ambiguities in \textit{comprehension}
-\citep[e.g.][]{Augurzky06,Beach1991,CliftonCarlsonFrazier2002,KjelgaardSpeer1999,
-  SchaferSpeerWarrenWhite2000,Steinhauer99}.  Specifically, it has
-been shown that prosodically separating a modifier from the directly
-preceding material supports an \ec-reading, whereas separating the two
-potential attachment sites is supportive of an \lc-reading
+\citep[e.g.][]{Beach1991,KjelgaardSpeer1999,Steinhauer99,SchaferSpeerWarrenWhite2000,CliftonCarlsonFrazier2002,Augurzky06}.
+Specifically, it has been shown that prosodically separating a
+modifier from the directly preceding material supports an \ec-reading,
+whereas separating the two potential attachment sites is supportive of
+an \lc-reading
 \citep[e.g.][]{CliftonCarlsonFrazier2002,Fodor02,Jun2003}.  Thus, a
@@
 
-To test whether prosodic information is taken into account in our
-task, we presented sentences in both of these prosodic variants. In
-addition, in order to test prosody-independent preferences, we also
-included a neutral version without any pronounced boundary. Further,
-we also presented unambiguous sentences corresponding to the
-\ec-reading. As in the case of the \as- and \es-sentences,
-the unambiguous counterparts served as a baseline to control for
-response biases that are independent of sentence meaning.
+To test whether prosodic information could generally have an effect on
+answer patterns in our task, we presented sentences in both of these
+prosodic variants. In addition, in order to test prosody-independent
+preferences, we also included a neutral version without any pronounced
+boundary. Further, we also presented unambiguous sentences
+corresponding to the \ec-reading. As in the case of the \as- and
+\es-sentences, the unambiguous counterparts served as a baseline to
+control for response biases that are independent of sentence meaning.
 
@@
 
-In the following, we will report the results for targets and
+In the following, we will report the results for target conditions and
 preference-related controls separately. After providing the
@@
 The previous regression-based analyses did not take the sequential
-nature of the task into account. The following paragraphs therefore
-spell out a generative Bayesian model which computes the
-likelihood of answer patterns for different latent relative saliencies
-of candidate readings and biases to answer early or late in a
-sequence. We use the data to estimate the posterior likelihood of
-these latent parameters to gain insight into the likely ordering
-relations over the strength of latent salience of candidate readings.
+nature of the task into account. We noted a possible bias for exiting
+later in a sequence, but ideally we would like to quantify how strong
+this effect is and what this entails for the likelihood of local
+readings. The following paragraphs therefore spell out a generative
+Bayesian model which computes the likelihood of answer patterns for
+different latent relative saliencies of candidate readings and biases
+to answer early or late in a sequence. We use the data to estimate the
+posterior likelihood of these latent parameters to gain insight into
+the likely ordering relations over the strength of latent salience of
+candidate readings.
 
@@
 Table~\ref{tab:predictions}, we quickly see that these findings are
-not predicted by either traditionalism or grammaticalism. We address
-each position separately in the following.
+not predicted by either traditionalism or grammaticalism under the
+auxiliary assumptions that we considered so far. We address each
+position separately in the following.
 
@@
 here. The verdict, however, seems to be clear. If
-(\ref{bsp:observed-preferences}) is the actual preference order over
-readings, then meaning disambiguation in terms of logical strength is
-generally on the wrong track, because no account that merely looks at
-the logical strengths of readings can plausibly predict the preference
-pattern in (\ref{bsp:observed-preferences}) for both \as- and
-\es-sentences at the same time.
+(\ref{bsp:observed-preferences}) shows the actual preference orders
+over readings, then meaning disambiguation in terms of logical
+strength is generally on the wrong track, because no account that
+merely looks at the logical strengths of readings can plausibly
+predict the preference pattern in (\ref{bsp:observed-preferences}) for
+both \as- and \es-sentences at the same time.
 
@@
 austere and stylized versions of traditionalism and grammaticalism
-that we have set up so far. We should then ask what plausible
-additional assumptions would enable either framework to accommodate
-the data? Again, let us look at each position in turn.
+that we have set up so far. But we should ask what plausible
+additional assumptions or alternative auxiliary assumptions would
+enable either core theory to accommodate the data \emph{ex post}. This
+is what we do in the next section, where we also reflect critically on
+our design and our interpretation of the data.
+
+\section{Critical reflection}
+\label{sec:critical-reflection}
+
+\paragraph{Alternative explanations based on traditionalism and
+  grammaticalism.} Section~\ref{sec:theories-predictions} introduced
+traditionalism and grammaticalism as two competing core theories,
+whose ability to make empirical prediction depends on additional
+auxiliary assumptions. We choose, in part for practical reasons,
+particular auxiliary assumptions, but we should also ask more
+generally: on the supposition that our design and the offered
+interpretation of our data are sound, what would it take to
+accommodate the observed data under the core theories that we
+considered?
 
 Consider grammaticalism first. Our data contradicts the notion that
-preferences follow logical strength. But grammaticalism could be
-supplemented by a conceptually different selection
+preferences follow logical strength. But, as noted in
+Section~\ref{sec:theories-predictions}, grammaticalism could be
+supplemented by a conceptually different disambiguation
 criterion. Selecting readings in terms of how well they answer the
@@
 an option. But it is quite unclear what the question under discussion
-should be that guided judgements in our task. As long as a theory of
-accommodating implicit questions under discussion is missing, this
-selection criterion does not make any clear, testable
-predictions. However, looking at the qualitative pattern in
+should be that guided judgements in our particular task. Similarly, it
+is not impossible that \citeauthor{Magri2011:Another-Argumen}'s
+(\citeyear{Magri2011:Another-Argumen}) proposal involving obligatory
+exhaustification and variable alternatives that feed into it can
+accommodate the observed data. \todo{look at reviewer comment and
+  acknowledge duly.}
+
+However, looking at the qualitative pattern in
 (\ref{bsp:observed-preferences}), a \emph{prima facie} plausible

### 2015-02-04 text/paper/revision_01/paper.tex
K2 revision reflection

@@
   \centering
-  \includegraphics[width=0.8\textwidth]{pics/post_salience_TF.pdf}
+  \includegraphics[width=0.8\textwidth]{pics/post_salience_TF_small.png}
   \caption{Estimated posteriors for the salience of \lc- and
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{pics/post_salience.pdf}
+  \includegraphics[width=0.8\textwidth]{pics/post_salience_small.png}
   \caption{Posteriors over relative salience of target readings in
@@
 prosodic effects on quantifier interpretation by employing a new
-experimental paradigm, the incremental verification
-task. Based on a current debate in the literature, we were
+experimental paradigm, the incremental verification task. We were
 specifically interested in whether ``local readings'' of sentences
@@
 In sum, the present findings cannot be explained in terms of the
-austere and stylized versions of traditionalism and grammaticalism
-that we have set up so far. But we should ask what plausible
-additional assumptions or alternative auxiliary assumptions would
+versions of traditionalism and grammaticalism that we have considered
+so far, i.e., with the particular auxiliary assumptions adopted in
+Section~\ref{sec:theories-predictions}. But we should ask what
+plausible amendements or alternative auxiliary assumptions would
 enable either core theory to accommodate the data \emph{ex post}. This
@@
 
-\section{Critical reflection}
+\section{Reflection}
 \label{sec:critical-reflection}
 
-\paragraph{Alternative explanations based on traditionalism and
-  grammaticalism.} Section~\ref{sec:theories-predictions} introduced
+\subsection{Alternative explanations within the core theories}
+
+Section~\ref{sec:theories-predictions} introduced
 traditionalism and grammaticalism as two competing core theories,
-whose ability to make empirical prediction depends on additional
-auxiliary assumptions. We choose, in part for practical reasons,
-particular auxiliary assumptions, but we should also ask more
-generally: on the supposition that our design and the offered
-interpretation of our data are sound, what would it take to
-accommodate the observed data under the core theories that we
-considered?
-
-Consider grammaticalism first. Our data contradicts the notion that
-preferences follow logical strength. But, as noted in
-Section~\ref{sec:theories-predictions}, grammaticalism could be
-supplemented by a conceptually different disambiguation
+whose concrete empirical predictions depend on additional auxiliary
+assumptions. We chose, in part for practical reasons, particular
+auxiliary assumptions, but we should also ask more generally: on the
+supposition that our design and the offered interpretation of our data
+are sound, what would it take to accommodate the observed data under
+the core theories?
+
+\paragraph{Grammaticalism.} Consider grammaticalism first. Our data
+contradicts the notion that preferences follow logical strength. But,
+as noted in Section~\ref{sec:theories-predictions}, grammaticalism
+could be supplemented by a conceptually different disambiguation
 criterion. Selecting readings in terms of how well they answer the
@@
 an option. But it is quite unclear what the question under discussion
-should be that guided judgements in our particular task. Similarly, it
-is not impossible that \citeauthor{Magri2011:Another-Argumen}'s
-(\citeyear{Magri2011:Another-Argumen}) proposal involving obligatory
-exhaustification and variable alternatives that feed into it can
-accommodate the observed data. \todo{look at reviewer comment and
-  acknowledge duly.}
-
-However, looking at the qualitative pattern in
-(\ref{bsp:observed-preferences}), a \emph{prima facie} plausible
-disambiguation criterion is ready at hand: if we assume that each
-insertion of the $\exh(\cdot)$ operator is \emph{costly}
-anti-proportional to the depth of its embedding under other logical
-operators, then we derive a preference of literal readings over local
-ones over global ones. Whether such an \emph{economy principle} is
-sound and in line with further empirical data would then be an
-interesting matter of further investigation. What this economy
-principle does not explain yet is the quantitative differences in the
-preference orders between \as- and \es-sentences. Still, if combined
-with further information about the global properties of the sentences
-in question, this might be an interesting alternative disambiguation
-criterion for an empirically testable grammaticalism.
-
-Traditionalism, on the other hand, has to explain the possibility of
-local readings of prosodically unmarked \es-sentences, and, perhaps,
-also the large number of local readings in accented \es-sentences
-compared to the much lower number in accented \as-sentences. To do so
-within a strict traditionalist framework seems difficult. A first
-option might be to account for alleged local readings as the result of
-some other phenomenon, such as typicality or contrast
+should be that guided judgements in our particular task. To make this
+approach yield \emph{ex ante} predictions, we would need to determine
+before the data is available which implicit QUDs our particular task
+should give rise to, so as to derive a preference ordering over
+readings. This may well be possible, but we do not presently see how.
+
+Another possibility of explaining our data within a grammaticalist
+core theory is to adopt \citeauthor{Magri2011:Another-Argumen}'s
+(\citeyear{Magri2011:Another-Argumen}) proposal that exhaustification
+operators occur at every relevant scope site while alternative sets as
+their input may also be empty.\footnote{This interesting line of
+  alternative \emph{post hoc} explanation was first suggest by a
+  reviewer, but worked out slightly differently here to strengthen the
+  reviewer's case.} For \as- and \es-sentences, we would have to
+consider the parses in (\ref{Magri-Parses}) (in simplified notation).
+
+\begin{exe}
+  \ex \label{Magri-Parses}
+    \begin{xlist}
+    \ex \label{Magri-Parse-AS} \mymark{$\exh_{Alt_1}$}(\mymark{All} $x$ are such that \mymark{$\exh_{Alt_2}$}( $x$ is connected to
+      \mymark{some}  \dots.))
+    \ex \label{Magri-Parse-ES} \mymark{$\exh_{Alt_1}$}(\mymark{Exactly
+        one} $x$  is such that \mymark{$\exh_{Alt_2}$}( $x$ is connected to \mymark{some}  \dots.))
+    \end{xlist}
+\end{exe}
+
+\noindent The alternative sets $Alt_{1,2}$ are plausibly either both
+empty or both non-empty. In the former case, we get the literal
+reading. In the latter case, we should assume that alternatives are
+just the standard ones that asymmetrically entail the literal reading:
+
+\begin{exe}
+  \ex \label{Magri-Alternatives} 
+    \begin{xlist}
+    \ex \label{Magri-Alternatives-AS} For \as-sentences: \\
+      $Alt_1 = \set{\text{``All } x
+          \dots x \text{ is connected to all } \dots \text{''}}$ \\
+        $Alt_2 = \set{\text{``}x \text{ is connected to all } \dots
+          \text{''}}$
+    \ex \label{Magri-Alternatives-AS} For \es-sentences: \\
+      % $Alt_1 = \set{\text{``Exactly 1 } x
+      %     \dots x \text{ is connected to all } \dots \text{''}}$ \\
+      $Alt_1 = \emptyset$ \\
+        $Alt_2 = \set{\text{``}x \text{ is connected to all } \dots \text{''}}$
+    \end{xlist}
+\end{exe}
+
+\noindent Notice that $Alt_1$ is empty for \es-sentences if we
+restrict attention to the ``global alternatives'' that asymmetrically
+entail the to-be-interpreted sentence. Interestingly, the readings
+that this approach derives are exactly the literal readings (under
+empty alternatives) and the local readings (under non-empty
+alternatives). What is left to explain is the preference relation over
+these readings. Here, the Magri-style approach could resort to
+considerations of \emph{parsing economy}: reasoning with fever
+alternatives is easier than reasoning with more alternatives. This
+would explain the preference for literal readings and also why local
+readings are more strongly attested for \es-sentences.
+
+On conceptual grounds we are very much in favor of a disambiguation
+criterion in terms of economy considerations, but whether the
+particular account sketched here is empirically successful in other
+cases as well, must remain to be seen. Two things are worth
+emphasizing here nonetheless. Firstly, the sketched Magri-style
+account is a plausible alternative \emph{post hoc} explanation. It was
+not, at least to our knowledge, a salient possibility before seeing
+our data set: other specifications of $Alt_1$ and $Alt_2$ could have
+been made equally plausible \emph{ex ante}. Secondly, what our data
+refutes is that preferences for readings follow logical
+strength. This, therefore, does not jeopardize grammaticalism as a
+core theory, but calls for theory-internal revision of its
+disambiguation criterion. Taken together, we argue that the data
+presented here points to a dire need of refining grammaticalism,
+perhaps along the lines suggested here, but ideally alongside more
+empirical data like the one we presented.
+
+\paragraph{Traditionalism.} Traditionalism, as we described it in
+Section~\ref{sec:theories-predictions}, is also uncomfortable with our
+data. It has to explain the possibility of local readings of
+prosodically unmarked \es-sentences, and, perhaps, also the large
+number of local readings in accented \es-sentences compared to the
+much lower number in accented \as-sentences. To do so within a strict
+traditionalist framework seems difficult. A first option might be to
+account for alleged local readings as the result of some other
+phenomenon, such as typicality or contrast
 \citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter}.
@@
 however, that our data provides interesting challenges to both
-traditionalism and grammaticalism.
-
-% \paragraph{Critique.} There are a number of conceivable objections to
-% our design and our interpretation of the presented results. We will
-% consider the most pressing ones in the following.
+traditionalism and grammaticalism, without necessarily refuting either
+core theory as such.
+
+\subsection{Critique}
+
+The foregoing interpretation and discussion presupposed that the
+interpretation of our data, given in Section~\ref{sec:discussion-1},
+was sound. But there are a number of conceivable objections to our
+design and our interpretation of the presented results. We will
+consider the most pressing ones in the following.
 

### 2015-02-04 text/paper/revision_01/paper.tex
K2 revision reflection finished

@@
 to adopt. Therefore, we will distinguish different varieties of either
-core theory. While there are certainly other varieties conceivable,
-they are, in our perception, the most prominent ones, but, more
-importantly, also the most practical ones in that they give us precise
-and testable \emph{ex ante} predictions about expected behavioral data
-(as opposed to \emph{ex post} explanations after inspecting the
-data). The predictions of the considere core theories plus their
-auxiliary assumptions are summarized in Table~\ref{tab:predictions} on
-page~\pageref{tab:predictions}. Below, in the discussion section
-(section~\ref{sec:discussion-1}), further conceivable varieties of
-traditionalism and grammaticalism will be discussed \emph{after}
-inspecting the relevant data.
+``core theory.'' While there are certainly other varieties
+conceivable, they are, in our perception, the most prominent ones,
+but, more importantly, also the most practical ones in that they give
+us precise and testable \emph{ex ante} predictions about expected
+behavioral data (as opposed to \emph{ex post} explanations after
+inspecting the data). The predictions of the considered core theories
+plus their auxiliary assumptions are summarized in
+Table~\ref{tab:predictions} on page~\pageref{tab:predictions}. Below,
+in Section~\ref{sec:critical-reflection}), further conceivable
+varieties of traditionalism and grammaticalism will be discussed
+\emph{after} inspecting the relevant data.
 
@@
 was sound. But there are a number of conceivable objections to our
-design and our interpretation of the presented results. We will
-consider the most pressing ones in the following.
-
-% To begin with, it could be questioned whether our design reliably
-% indicates the preference relations in
-% (\ref{bsp:observed-preferences}). One could object that it is not
-% feasible to compare results from the preference-related controls to
-% results from our target conditions, because the source of different
-% readings is fundamentally different. In the former we have a syntactic
-% ambiguity, in the latter a set of putative pragmatic enrichments. The
-% former is a case of perceived ambiguity (some of our subjects reported
-% this), the latter arguably is not
-% \citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
-% if the distribution of responses is indicative of the known preference
-% patterns in preference-related controls, this would not necessarily
-% mean that the distribution of responses in target conditions is
-% indicative of preference relations. Although we cannot rule out that
-% the incremental verification task detects preferences among multiple
-% readings only for some sources of variability in readings and not
-% others, it is by no means clear why this should be so. The burden of
-% argument is on the sceptic. But even if we assume that the incremental
-% verification task is incapable of reliably indicating preferences
-% among candidate pragmatic enrichments of the relevant kind, then it
-% should at least be able to indicate availability of readings. So if we
-% deny the observed response patterns the power to indicate preference,
-% what should the information about availability of readings be that we
-% may safely infer from it? It should be that local readings are
-% available in \es-sentences and that global readings are unattested in
-% \as- and \es-sentences. But that alone is not predicted by either
-% traditionalism or grammaticalism. The former cannot explain the
-% substantial number of local responses in \es-sentences, the latter
-% does not explain the absence of total global responses.
-
-% Another line of criticism that challenges the validity of
-% (\ref{bsp:observed-preferences}) targets the Bayesian
-% salience-competition model that we used to derive it. We readily admit
-% that our model is highly simplistic. Several aspects are especially
-% noteworthy here. Firstly, we did not distinguish different types of
-% errors, and did not take into account that when errors occurred
-% earlier in the sequence, later decision points could no longer be
-% reached. This way the model may actually have unduly de-emphasized the
-% salience of readings that can be judged later in a sequence. Another,
-% more complicated model of the likelihood of answer patterns, might
-% therefore have given support to different conclusions. Unfortunately,
-% it is not clear how exactly such a more complex generating model
-% should be set-up. Eventually, a full processing model, designed for
-% data from incremental verification tasks, would be needed. We cannot
-% offer such a model here, but can only the offer a first step in that
-% direction. More importantly, though, the only part of
-% (\ref{bsp:observed-preferences}) that might plausibly change for a
-% more encompassing model along the lines sketched above is that the 3
-% \emph{false} answers in the \as-conditions with neutral intonation
-% might support the conclusion that the local reading is attested. But
-% this hypothetical effect will certainly be no bigger than marginal,
-% and so no genuinely different conclusions of theoretical relevance
-% should be expected.
+design and our interpretation of the presented results, which
+essentially all cast into doubt that our data suggests the preference
+relation in (\ref{bsp:observed-preferences}). We will consider the
+most pressing ones in the following.
+
+\paragraph{The ``choose first match'' argument.} It is tempting to
+think that participants generally tended to choose the first exit
+possible. They might, after all, have simply wanted to save time and
+be done with the experiment. We considered this a possible confound
+and it is therefore that we included the preference-related
+controls. But the objection is already clearly refuted by the data
+itself. For it would entail that we should see many more global
+readings for \es-sentences, which could be judged before the literal
+readings, and also that we should have seen the reverse pattern in the
+preference-related controls, where we did observe that the reading
+that could be judged \emph{later} attracted comparatively more
+responses.
+
+\paragraph{Incomparability of target conditions and preference-related
+  controls.} One could object that it is not feasible to compare
+results from the preference-related controls to results from our
+target conditions, because the source of different readings is
+fundamentally different. In the former we have a syntactic ambiguity,
+in the latter a set of putative pragmatic enrichments. The former is a
+case of perceived ambiguity (some of our subjects reported this), the
+latter arguably is not
+\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
+if the distribution of responses is indicative of the known preference
+patterns in preference-related controls, this would not necessarily
+mean that the distribution of responses in target conditions is
+indicative of preference relations in the same way.
+
+This objection is very serious. It is amplified by an even more
+general worry, raised as a challenge by a reviewer, who intuits that
+the incremental verification might altogether be insensitive to scalar
+implicatures. According to the reviewer, it is to be expected that
+since \emph{some} is typically strengthened in non-embedded
+conditions, virtually all of our participants would exit at an early
+position corresponding to the literal reading in a suitable version of
+our \ivt.
+
+To address this worry we ran another stripped-down version of the
+\ivt. We recruited 50 subjects via Amazon's Mechanical Turk and paid
+them 1 US\$ compensation. Similar to our main experiment, the
+post-experiment started with two training trials with unambiguous
+sentences, familiarizing our subjects with the task. In the
+browser-based version, alert boxes pointed out subjects' mistakes when
+they tried to exit to early, chose the wrong response or tried to
+unravel the sequence further than strictly necessary. The main part of
+the experiment consisted of six trials, two of which were critical and
+four of which were controls. On critical trials, each subject saw
+different version of sentences like (\ref{bsp:Item-PostExp}), in
+connection with sequences like in Figure~\ref{fig:Trial-PostExp}.
+
+\begin{exe}
+  \ex \label{bsp:Item-PostExp} The scissors are connected to some of the circles.
+\end{exe}
+
+\begin{figure}[t]
+	\centering
+	\subfloat[][Step 2  (\lit true)]{ 
+		\fbox{\includegraphics[width=3.5cm]{pictures/PostExp_2.pdf}}
+	    \label{fig:exseqES1}
+	}
+	\subfloat[][Step 3]{
+		\fbox{\includegraphics[width=3.5cm]{pictures/PostExp_3.pdf}}
+	    \label{fig:exseqES2}
+	}
+	\subfloat[][Step 4 (\acro{prag} false)]{ 
+		\fbox{\includegraphics[width=3.5cm]{pictures/PostExp_4.pdf}}
+	    \label{fig:exseqES3}
+	}
+	\caption{Example sequence for critical trial in
+          post-experiment.}
+	\label{fig:Trial-PostExp}
+\end{figure}
+
+\noindent The first step in the sequence had all potential connections
+covered, as before. On step 2, the critical sentence could be judged
+true under a literal reading. On the last step 4, it could be judged
+false under a pragmatically strengthened implicature reading. Control
+conditions had unambiguous sentences and served to filter out subjects
+with insufficient performance. From the total of 100 critical trials
+(50 subjects times 2 trials each), 66 were literal answers, 27 were
+pragmatic answers and 7 were `errors'. If we restrict attention to
+only those participants that had at least two of the four control
+conditions correct, we are left with 39 subjects. With these, we find
+55 literal, 21 pragmatic and 2 `error' answers. In sum, this strongly
+suggests that the \ivt is not generally insensitive to scalar
+implicature and does give substantial counts also for implicature
+readings if these can be judged later than a literal reading.
+
+If we accept that the \ivt is not insensitive to implicature-based
+ambiguities, what is left to worry about is that information about
+response biases (early vs.~late) do not carry over from the
+preference-related control conditions to the target conditions in the
+main experiment. It could be, after all, that the task triggers
+subjects to exit late for perceived syntactic ambiguities and to exit
+early for ``pragmatic ambiguities'' involving implicature
+readings. This might also possibly explain why there are more `error'
+responses on the last position in the preference-related controls. But
+none of this has any serious impact on the suggested preference
+relation in (\ref{bsp:observed-preferences}). For even if, as possibly
+the post-experiment suggests as well, there is a sequential bias in
+the target conditions to exit early, the main effect of such a bias would
+merely be that we should consider local readings more salient than we
+do now. In the light of the data from main and post-experiments, it
+would be far-fetched to uphold that our data indicates that local
+readings are at least as salient as literal ones. But that means that
+the suggested interpretation in (\ref{bsp:observed-preferences}) still
+holds, and all the problems that we identified for (the considered
+versions of) traditionalism and grammaticalism apply.
+
+To strengthen this case further, let us assume that the \ivt is
+entirely incapable of reliably indicating preferences among candidate
+pragmatic enrichments of the relevant kind. Can we still draw any
+conclusions about mere availability (non-negligible salience) of
+readings? At a minimum, we would like to uphold that local readings
+are available in \es-sentences and that global readings are unattested
+in \as- and \es-sentences. But that alone is not predicted by either
+traditionalism or grammaticalism in the guises that we considered. The
+former cannot explain the substantial number of local responses in
+\es-sentences, the latter does not explain the total absence of global
+responses.
+
+\paragraph{Interpretation of ``salience'' \& the Bayesian model.}
+Another line of criticism that challenges the validity of
+(\ref{bsp:observed-preferences}) targets the Bayesian
+salience-competition model that we used to derive it. To avoid a
+potential misunderstanding pointed out by a reviewer, it is not the
+case the our interpretation of the \ivt assumes that each subject
+fixes an interpretation at the beginning of the sequence and applies
+it, unswayed by anything that is encountered along the sequence of
+revealed pictures. The Bayesian model is compatible with this
+interpretation, but it is also compatible with a another one that we
+think is more plausible, namely that at each choice point during the
+sequence of pictures, subjects' aggregate probabilistic behavior is
+described as a function that compares the relative salience of the
+readings available, together with potential response biases and
+uniform error rates.
+
+Still, we readily admit that our model is highly simplistic. Several
+aspects are especially noteworthy here. Firstly, we did not
+distinguish different types of errors, and did not take into account
+that when errors occurred earlier in the sequence, later decision
+points could no longer be reached. This way the model may actually
+have unduly de-emphasized the salience of readings that can be judged
+later in a sequence. Another, more complicated model of the likelihood
+of answer patterns, might therefore have given support to
+quantitatively different conclusions. Unfortunately, it is not clear
+how exactly such a more complex generating model should be
+set-up. Eventually, a full processing model, designed for data from
+incremental verification tasks, would be needed. We cannot offer such
+a model here, but can only the offer a first step in that
+direction. More importantly, though, the only part of
+(\ref{bsp:observed-preferences}) that might plausibly change for a
+more encompassing model along the lines sketched above is that the 3
+\emph{false} answers in the \as-conditions with neutral intonation
+might support the conclusion that the local reading is attested. But
+this hypothetical effect will certainly be no bigger than marginal,
+and so no genuinely different conclusions of theoretical relevance
+should be expected.
 
@@
 
-We tested experimentally the predictions of traditionalism and
-grammaticalism with respect to the availability of and preferences
-over three types of conceivable pragmatic enrichments of two types of
-sentences, in which scalar \emph{some} occurred in the scope of either
-a monotonic quantifier \emph{all} or the non-monotonic quantifier
-\emph{exactly one}. To avoid potential confounds of the pictorial
-material, such as through typicality or contrast
+We tested experimentally the predictions of suitably constrained
+versions of traditionalism and grammaticalism with respect to the
+availability of and preferences over three types of conceivable
+pragmatic enrichments of two types of sentences, in which scalar
+\emph{some} occurred in the scope of either a monotonic quantifier
+\emph{all} or the non-monotonic quantifier \emph{exactly one}. To
+avoid potential confounds of the pictorial material, such as through
+typicality or contrast
 \citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar},
@@
 Backed up by our analyses, we concluded that both traditionalism and
-grammaticalism do not predict our data well. Traditionalism fails to
+grammaticalism do not predict our under the set of auxiliary
+assumptions that we provided them with in
+Section~\ref{sec:theories-predictions}. Traditionalism fails to
 account for high numbers of responses indicating local readings even
-for prosodically unmarked \es-sentences. Grammaticalism, insofar as
-it builds on disambiguation by logical strength, fails to predict the
+for prosodically unmarked \es-sentences. Grammaticalism, insofar as it
+builds on disambiguation by logical strength, fails to predict the
 absence of answers indicative of global readings and the relative
@@
 strength-based meaning selection does not seem to be a good
-disambiguation criterion for grammaticalism. We tentatively suggested
-an alternative selection principle for grammaticalism in terms of
-``parsing economy.'' Another important conclusion from our data is
-that \es-sentences, using non-monotonic quantifier \emph{exactly one},
-appeared to be prone to receive a ``shallow interpretation.'' This may
-be used by traditionalism to explain answers indicative of local
-readings for \es-sentences. But the point is relevant in general. The
-possibility of ``shallow interpretation'' of non-monotonic quantifiers
-should be considered also when interpreting the results of other
-experimental designs \citep[e.g.][]{CliftonDube2010:Embedded-Implic,
+disambiguation criterion for grammaticalism. This point is also
+relevant in general, because disambiguation based on logical strength
+has been suggested in other domains as well
+\citep[e.g.][]{DalrympleKanazawa1998:Reciprocal-Expr,CobrerosEgre2012:Tolerant-Classi}.
+We tentatively suggested an alternative selection principle for
+grammaticalism in terms of ``parsing economy,'' but it remains to be
+seen whether this is empirically successful in other domains as well.
+
+Another important conclusion from our data is that \es-sentences,
+using non-monotonic quantifier \emph{exactly one}, appeared to be
+prone to receive an unexpected interpretation. This may be used by
+traditionalism to explain answers indicative of local readings for
+\es-sentences. But the point is relevant in general. The possibility
+of unexpected interpretations of non-monotonic quantifiers should be
+considered also when interpreting the results of other experimental
+designs \citep[e.g.][]{CliftonDube2010:Embedded-Implic,
   ChemlaSpector2010:Experimental-Ev}.
@@
 testable predictions about reading preferences where different
-potential readings are allowed (contra a grammaticalism without
-commitment to any testable disambiguation principle). We should then
-try to obtain information about actual preference patterns by explicit
-comparison with structures whose preference structures are
-well-studied, ideally with some model of the data generating process
-for optimal data analysis.
+potential readings are allowed. We should then try to obtain
+information about actual preference patterns by explicit comparison
+with structures whose preference structures are well-studied, ideally
+with some model of the data generating process for optimal data
+analysis.
 

### 2015-02-06 text/paper/revision_01/paper.tex
K2 reworked section 3 traditionalism

@@
 Given this plurality of hypothesized readings, the question arises:
-how salient are these theoretically conceivable readings
-compared to each other (if they are detectable by empirical means at
-all)?  Addressing this question empirically is relevant because it
-lies at the heart of a current debate about the nature of quantity
-inferences. %  and the demarkation between grammar (i.e. syntax/semantics)
-% and domain-general reasoning procedures (i.e. pragmatics).
+how salient are these theoretically conceivable readings compared to
+each other (if they are detectable by empirical means at all)?
+Addressing this question empirically is relevant because it lies at
+the heart of a current debate about the nature of quantity inferences.
 The controversy is usually seen as one between two main competing
-theoretical positions \citep[see][for a detailed comparison of the
-two]{ChemlaSingh2014:Remarks-on-the-}.  Simplifying things for now,
-these two types of theories make clearly different predictions about
-how salient the local readings, in particular, should be.  The first
-position which we refer to as \mymark{traditionalism} (similar to, but
-not identical to Chemla \& Singh’s ``Gricean approach'') holds that
-local readings should not be salient at all. The second one which we
-call \mymark{grammaticalism} (Chemla \& Singh’s ``grammatical
-approach'') holds that local readings are unproblematically available
-and maybe even at least as salient as the literal ones (see Section
-\ref{sec:theories-predictions} for a more thorough exposition of the
-theories and their predictions).
-
-That matters actually are not as simple as just described is reflected
-by lively discussions about which conclusions are permitted by previous
-experimental research \citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,BenzGotzner2014:Embedded-implic}.
-The results of these studies
-were discussed controversially because of several specific reasons. Firstly,
-and most importantly, previous studies presented target sentences visually.
-However, traditionalists often acknowledge the availability of local readings for
-prosodically marked utterances, albeit not as the result of
-a standard scalar implicature but of a different pragmatic process triggered by
-prosodic markedness \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
-Under this view, evidence for the availability of local readings \citep[see][]{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev} may be
-an effect of “silent prosody”  \citep[see e.g.][]{Bader98,Fodor98}. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and \citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue,
-the alleged evidence for the availability of local readings of \as-sentences, might well be
-confounded with “typicality effects”  (see Section~\ref{sec:previous-studies} for discussion).
-Finally, previous studies have only accumulated limited evidence pertaining to the relative
-salience of candidate readings of sentences like (\ref{bsp:AE}) and (\ref{bsp:GE}) (see
+theoretical positions, which we call \mymark{traditionalism} and
+\mymark{grammaticalism} and take to be general ideas behind large
+classes of approach to quantity implicatures \citep[c.f.][for related
+discussion with a focus on deriving processing
+theories]{ChemlaSingh2014:Remarks-on-the-}. Unfortunately, it is
+rather difficult to empirically test either ``core theory'' (
+terminology from \citeauthor{ChemlaSingh2014:Remarks-on-the-})
+directly because additional ``auxiliary assumptions'' are needed in
+both cases to derive falsifiable \emph{ex ante} predictions about
+to-be-expected observations in a concrete behavioral experiment, even
+irrespective of processing accounts. We therefore try to carefully set
+up plausible instantiations of either core theory with particular
+auxiliary assumptions that give testable predictions at the outset in
+Section~\ref{sec:theories-predictions}, then evaluate the obtained
+predictions against our data, and finally broaden our perspective to
+reflect in Section~\ref{sec:critical-reflection} on the impact of our
+data on the more general tenability of the core theories.
+
+But even with crisp theoretical predictions at hand, matters are still
+very complex, as reflected by lively discussions about which
+conclusions are permitted by previous experimental research
+\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,BenzGotzner2014:Embedded-implic}. The
+results of these studies were discussed controversially because of
+several specific reasons. Firstly, and most importantly, previous
+studies presented target sentences visually.  However, traditionalists
+often acknowledge the availability of local readings for prosodically
+marked utterances, albeit not as the result of a standard scalar
+implicature but of a different pragmatic process triggered by prosodic
+markedness
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
+Under
+this view, evidence for the availability of local readings
+\citep[see][]{CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}
+may be an effect of “silent prosody” \citep[see
+e.g.][]{Bader98,Fodor98}. We will therefore address this extant
+position as the \mymark{prosodic markedness hypothesis} and argue
+that, if prosody is hypothesized to play a central role, it is vital
+to present target sentences auditorily or to control for effects of
+“silent prosody” that subjects may apply when reading a
+sentence. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
+\citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue, the alleged
+evidence for the availability of local readings of \as-sentences,
+might well be confounded with, in particular, “typicality effects”
+(see Section~\ref{sec:previous-studies} for discussion).  Finally,
+previous studies have only accumulated limited evidence pertaining to
+the relative salience of candidate readings of sentences like
+(\ref{bsp:AE}) and (\ref{bsp:GE}) (see
 Section~\ref{sec:previous-studies} for discussion).
 
-More generally, two prerequisites have to be met in order to make use
-of experimental data to decide between theoretical positions regarding
-the computation of quantity inferences. Firstly, both traditionalism
-and grammaticalism have to be augmented with additional assumptions to
-derive testable predictions about the relative salience of candidate
-readings. For example, hypothezised effects of prosodic marking have
-to be taken into account before we can test traditionalism empirically
-using sentences (\ref{bsp:AE}) and (\ref{bsp:GE}).  We will address
-this extant position as the \mymark{prosodic markedness hypothesis}
-and argue that, if prosody is hypothesized to play a central role, it
-is vital to present target sentences auditorily or to control for
-effects of “silent prosody” that subjects may apply when reading a
-sentence. Secondly, the relative salience of candidate readings has to
-be operationalized properly, i.e., we have to devise methods to
-measure relative salience. For example, typicality effects and logical
-dependencies between readings have to be controlled for when
-evaluating speaker judgments in terms of the salience of candidate
-readings.  Both of these prerequisites are related to formulating what
-\citet{ChemlaSingh2014:Remarks-on-the-} call ``auxiliary assumptions''
-that are necessary to enable theoretical accounts to make predictions
-about processing. Our emphasis here is not on processing accounts, but
-on predictions of behavioral data --- what is sometimes, perhaps
-misleadingly, called a computational-level perspective. But even so,
-traditionalism and grammaticalism have to summon auxiliary assumptions
-which connect the core theories to the dependent variables of a
-behavioral experiment. Without proper auxiliary assumptions it is hard
-(or impossible) to test traditionalism or grammaticalism empirically.
-
-This paper presents results form an experimental study designed to
-deal with the mentioned problems. The focus is on testing certain
-formulations of traditionalism and grammaticalsim that are explicit
-enough to derive testable predictions about the relative salience of
-candidate readings. For practical reasons, we must choose auxiliary
-assumptions that actually deliver \emph{ex ante} predictions, even
-though this may not exhaust the space of variations on either core
-theory that have been floated in the recent literature (see
-Section~\ref{sec:theories-predictions} for discussion). In order to
-address the prosodic markedness hypothesis, we presented sentence
-materials auditorily and explicitly manipulated contrastive stress on
-embedded scalar items. In order operationalize the relative salience
-of candidate readings, we employed an \mymark{incremental verification
-  task} in which parts of a to-be-evaluated picture were hidden and
-only revealed piece-wise at the participants’ request until they felt
-able to give a binary truth-value judgement
-\citep[see][]{Conroy2008}. To analyze the obtained data in terms of
-relative salience of candidate readings, we furthermore employed a
-statistical model of how the salience of readings guided participants
-judgments in the incremental verification task. We validated this
-method by including control conditions testing ambiguous sentences
-with a well-known preference on available readings. We argue that this
-method provides categorical behavioral data that is both clearly
-indicative of the reading preferences among participants and largely
-independent of potential pictorial confounds, such as the mentioned
-typicality effects.
-
-The data obtained by this method is \emph{prima facie} problematic for
-both traditionalism and grammaticalism, at least if augmented by the
-auxiliary assumptions which we adopted here. However, we want to
-stress from the outset that, while the experimental results allow us
-to derive restrictions on which auxiliary assumptions are conceivable
-for traditionalism and grammaticalism, definite conclusions about the
-general validity of the two core theories will be limited
-\citep[cf.][]{ChemlaSingh2014:Remarks-on-the-}. Bearing this in mind,
-we can summarize our main findings crudely as follows. Contrary to the
-predictions of common versions of traditionalism, we observed many
-answers indicative of local readings of \es-sentences, irrespective of
-prosodic markedness. But also prominent versions of grammaticalism are
-incongruent with the observed data.  Backed up by the
-\mymark{strongest meaning hypothesis}
-\citep{DalrympleKanazawa1998:Reciprocal-Expr} as a disambiguation
-criterion \citep[as suggested by][]{ChierchiaFox2008:The-Grammatical},
-grammaticalism predicts local readings to be much more salient than we
-found evidence for in our data. More strongly even, the preference
-order among putative readings suggested by our data cannot even in
-principle be explained by comparisons of logical strength among
-putative readings. This finding is independently relevant in the light
-of the fact that the strongest meaning hypothesis is frequently
-summoned as a disambiguation criterion also in other domains, such as
-the interpretation of reciprocals
-\citep{DalrympleKanazawa1998:Reciprocal-Expr} or vague predicates
-\citep{CobrerosEgre2012:Tolerant-Classi}. In sum, our data shed doubt
-on both traditionalism and grammaticalism under prominent auxiliary
-assumptions. We conclude the paper by some thoughts on how either
-position could be amended in the light of our data.
-
-The remainder of the paper is structured as
-follows. Section~\ref{sec:get-know-your} elaborates on the three kinds
-of relevant readings for our target
-sentences. Section~\ref{sec:theories-predictions} works out the
-predictions of traditionalism and grammaticalism (plus prominent auxiliary assumptions) 
-about availability and relative salience of readings for these
+% More generally, two prerequisites have to be met in order to make use
+% of experimental data to decide between theoretical positions regarding
+% the computation of quantity inferences. Firstly, both traditionalism
+% and grammaticalism have to be augmented with additional assumptions to
+% derive testable predictions about the relative salience of candidate
+% readings. For example, hypothezised effects of prosodic marking have
+% to be taken into account before we can test traditionalism empirically
+% using sentences (\ref{bsp:AE}) and (\ref{bsp:GE}).  We will address
+% this extant position as the \mymark{prosodic markedness hypothesis}
+% and argue that, if prosody is hypothesized to play a central role, it
+% is vital to present target sentences auditorily or to control for
+% effects of “silent prosody” that subjects may apply when reading a
+% sentence. Secondly, the relative salience of candidate readings has to
+% be operationalized properly, i.e., we have to devise methods to
+% measure relative salience. For example, typicality effects and logical
+% dependencies between readings have to be controlled for when
+% evaluating speaker judgments in terms of the salience of candidate
+% readings.  Both of these prerequisites are related to formulating what
+% \citet{ChemlaSingh2014:Remarks-on-the-} call ``auxiliary assumptions''
+% that are necessary to enable theoretical accounts to make predictions
+% about processing. Our emphasis here is not on processing accounts, but
+% on predictions of behavioral data --- what is sometimes, perhaps
+% misleadingly, called a computational-level perspective. But even so,
+% traditionalism and grammaticalism have to summon auxiliary assumptions
+% which connect the core theories to the dependent variables of a
+% behavioral experiment. Without proper auxiliary assumptions it is hard
+% (or impossible) to test traditionalism or grammaticalism empirically.
+
+To deal with these methodological problems, this paper presents
+results form an experimental study which presented sentence materials
+auditorily and explicitly manipulated contrastive stress on embedded
+scalar items. We employed an \mymark{incremental verification task} in
+which parts of a to-be-evaluated picture were hidden and only revealed
+piece-wise at the participants’ request until they felt able to give a
+binary truth-value judgement \citep[see][]{Conroy2008}. We use both a
+classical regression analysis and a Bayesian statistical model to
+analyze the data from this novel task, and validate this method by
+including control conditions testing ambiguous sentences with a
+well-known preference on available readings. We argue that this method
+provides categorical behavioral data that is both clearly indicative
+of the reading preferences among participants and largely independent
+of potential pictorial confounds, such as the mentioned typicality
+effects.
+
+% The data obtained by this method is \emph{prima facie} problematic for
+% both traditionalism and grammaticalism, at least if augmented by the
+% auxiliary assumptions which we adopted here. However, we want to
+% stress from the outset that, while the experimental results allow us
+% to derive restrictions on which auxiliary assumptions are conceivable
+% for traditionalism and grammaticalism, definite conclusions about the
+% general validity of the two core theories will be limited
+% \citep[cf.][]{ChemlaSingh2014:Remarks-on-the-}. Bearing this in mind,
+% we can summarize our main findings crudely as follows. Contrary to the
+% predictions of common versions of traditionalism, we observed many
+% answers indicative of local readings of \es-sentences, irrespective of
+% prosodic markedness. But also prominent versions of grammaticalism are
+% incongruent with the observed data.  Backed up by the
+% \mymark{strongest meaning hypothesis}
+% \citep{DalrympleKanazawa1998:Reciprocal-Expr} as a disambiguation
+% criterion \citep[as suggested by][]{ChierchiaFox2008:The-Grammatical},
+% grammaticalism predicts local readings to be much more salient than we
+% found evidence for in our data. More strongly even, the preference
+% order among putative readings suggested by our data cannot even in
+% principle be explained by comparisons of logical strength among
+% putative readings. This finding is independently relevant in the light
+% of the fact that the strongest meaning hypothesis is frequently
+% summoned as a disambiguation criterion also in other domains, such as
+% the interpretation of reciprocals
+% \citep{DalrympleKanazawa1998:Reciprocal-Expr} or vague predicates
+% \citep{CobrerosEgre2012:Tolerant-Classi}. In sum, our data shed doubt
+% on both traditionalism and grammaticalism under prominent auxiliary
+% assumptions. We conclude the paper by some thoughts on how either
+% position could be amended in the light of our data.
+
+The paper is structured as follows. Section~\ref{sec:get-know-your}
+elaborates on the three kinds of relevant readings for our target
+sentences. Section~\ref{sec:theories-predictions} works out plausible
+\emph{ex ante} predictions of the core theories traditionalism and
+grammaticalism (for some practically relevant auxiliary assumptions)
+about availability and relative salience of readings for our target
 sentences. Section~\ref{sec:previous-studies} reviews related
@@
 approach. Section~\ref{sec:exp} eventually contributes our
-experimental design, analyses and results.
+experimental design, analyses and results. Finally,
+Section~\ref{sec:critical-reflection} discusses our method and
+interpretation of the results in a broader theoretical context.
 
@@
 
-There are two main theoretical positions which make different
-predictions about the readings of \as- and \es-sentences
+There are two main theoretical positions which appear to make
+different predictions about the readings of \as- and \es-sentences
 \citep[see][for
@@
 will refer to these as \mymark{traditionalism} and
-\mymark{grammaticalism} and treat each one in turn.  As already
-mentioned in the introduction, there is some leeway in assessing the
-predictions for each approach depending on which auxiliary assumptions
-to adopt. Therefore, we will distinguish different varieties of either
-``core theory.'' While there are certainly other varieties
-conceivable, they are, in our perception, the most prominent ones,
-but, more importantly, also the most practical ones in that they give
-us precise and testable \emph{ex ante} predictions about expected
-behavioral data (as opposed to \emph{ex post} explanations after
-inspecting the data). The predictions of the considered core theories
-plus their auxiliary assumptions are summarized in
-Table~\ref{tab:predictions} on page~\pageref{tab:predictions}. Below,
-in Section~\ref{sec:critical-reflection}), further conceivable
-varieties of traditionalism and grammaticalism will be discussed
-\emph{after} inspecting the relevant data.
+\mymark{grammaticalism} and treat each in turn. Both approaches are
+addressed here as ``core theories'': two main ideas behind several
+approaches to quantity implicatures. To determine concrete predictions
+from these, additional ``auxiliary assumptions'' are necessary. Here,
+we spell a set of such auxiliary assumptions for each core theory. Our
+motivation for the particular choices we make is partly guided by
+practical concerns, so as to have a concrete set of predictions for
+each core theory to formulate expectations and compare our data to. We
+therefore introduce some prominent or otherwise relevant variants of
+either core theory, the predictions of which are summarized in
+Table\ref{tab:predictions} on page~\pageref{tab:predictions}. How
+other potential instantiations of either core theory fare in light of
+our data will be discussed in Section~\ref{sec:critical-reflection}.
 
@@
 
-Traditionalism gets its name from its conservative stance towards
-Grice's original theory of conversational implicatures
-\citep{Grice1975:Logic-and-Conve}. Many authors have defended
-traditionalist positions in this sense. Of the more recent literature,
-we would consider as traditionalist, among others, contributions by
+We use ``traditionalism'' as a vague umbrella term for approaches that
+build on \citeauthor{Grice1975:Logic-and-Conve}'s
+(\citeyear{Grice1975:Logic-and-Conve}) original notion that
+conversational implicatures, of which quantity implicatures are a
+special case, are to be thought of as rationalizations of speaker
+behavior. Central in this reasoning is the assumption that the
+speaker's behavior is efficient (if not optimal) and
+goal-oriented. Usually, the assumed goal of conversation is the
+cooperative exchange of relevant information from speaker to
+hearer.\footnote{Of the more recent literature, we would consider as
+  traditionalist, among many others, contributions by
   \citet{Spector2006:Scalar-Implicat},
@@
   \citet{Geurts2010:Quantity-Implic},
-\citet{Franke2011:Quantity-Implic}, or \citet{GoodmanStuhlmuller2013:Knowledge-and-I}.
-
-According to Grice, conversational implicatures, of which quantity
-implicatures are a special case, are to be thought of as
-rationalizations of speaker behavior. Central in this reasoning is the
-assumption that the speaker's behavior is efficient (if not optimal)
-and goal-oriented. Usually, the assumed goal of conversation is the
-cooperative exchange of relevant information from speaker to
-hearer.\footnote{Our conception of ``traditionalism'' is less
-  stringent that \citeauthor{ChemlaSingh2014:Remarks-on-the-}'s
-  ``Gricean approach.'' We allow our traditionalism to violate the
-  constraint that all considered alternatives must be stronger than
-  the one to be interpreted, so as to allow, for instance, global
-  readings of \es-sentences where the alternative
-  (\ref{bsp:GE-Alternative}) does not asymmetrically entail the
-  to-be-interpreted (\ref{bsp:GE}) (see more below). We would even
-  subsume under traditionalism abductive reasoning to the best
-  explanation of what lexical meaning a speaker had intended to convey
-  on an occasion of use in an embedded context, if such an account
-  could be formulated consistently and in such a manner that it makes
-  testable predictions.}
-
-Consequently, the \mymark{Gricean recipe}
-\citep[see][]{Geurts2010:Quantity-Implic} for deriving a simple scalar
-inference like that in (\ref{bsp:Plain-SI-Implicature}) from an
-utterance of (\ref{bsp:Plain-SI-Target}) is as follows: if the issue
-whether Hans solved only some or all of the problems is relevant, then
-a cooperative and knowledgable speaker would utter
+  \citet{Franke2011:Quantity-Implic}, or
+  \citet{GoodmanStuhlmuller2013:Knowledge-and-I}.}
+
+The traditionalist view gives rise to what
+\citet{Geurts2010:Quantity-Implic} calls the \mymark{Gricean recipe}
+for deriving a scalar inference (\ref{bsp:Plain-SI-Implicature}) from
+an utterance of (\ref{bsp:Plain-SI-Target}): if the issue whether Hans
+solved only some or all of the problems is relevant, then a
+cooperative and knowledgable speaker would utter
 (\ref{bsp:Plain-SI-Alternative}) if in a position to do so; hence, one
@@
   derivation of implicatures targeting the speaker's epistemic state
-  \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit}. Section~\ref{sec:discussion-1}
-  will come back to this in more detail.}
+  \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit}. More
+  on this below.}
 
@@
 
-As for \as- and \es-sentences, the Gricean recipe derives global
-readings in a straightforward way. Consequently, traditionalism
-predicts that both literal and global readings are available:  literal
-readings, because these are the result of semantic interpretation
-and form the starting point of pragmatic reasoning; global readings
-because these may be arrived at by the Gricean recipe.
-
-Traditionalism's predictions about relative salience of literal and
-global readings depend on whether certain auxiliary assumptions
-necessary to derive global readings by the Gricean recipe are
-plausibly met. These auxiliary assumptions include relevance of the
-extra information provided by the global reading, mutual awareness
-that the stronger alternative has been a speaker option, the speaker's
-competence about the issue, etc. Normally, traditionalist accounts
-would assume that these extra assumptions are met. In that case,
-traditionalism would predict that global readings should be preferred
-over literal readings. On the other hand, if these extra assumptions
-are implausible, traditionalism would predict that literal readings
-are preferred over global ones \citep[see][for experimental evidence
-indicating that manipulation of speaker knowledgeability indeed
-affects the rate of quantity implicatures drawn by the listener
-for unembedded occurrences of \emph{some}]{GoodmanStuhlmuller2013:Knowledge-and-I}.
-
-Consequently, there are at least two varieties of traditionalism that
-yield slightly different predictions, depending on which extra
-assumptions we make about the relevant context of interpretation. If
-the context (e.g., our experimental design) makes the extra
-assumptions of the Gricean recipe needed to derive non-epistemic
-global readings sufficiently salient, then we get the prediction that
-global readings should be preferred over literal ones; otherwise the
-prediction is that literal readings are preferred over global ones. We
-call the former position \mymark{the strong variety of traditionalism}
-and the latter the \mymark{the weak variety of traditionalism}.\fn{We
-  mention for clarity that although weak traditionalism does not
-  predict literal readings to be more salient than non-epistemic
-  global readings, it might still predict an \emph{epistemically weak
-    implicature}, similar to the global reading, that the speaker is
-  uncertain whether the stronger alternative is true. (See also the
-  discussion in Section~\ref{sec:discussion-1})} It is of course an
-empirical task to determine when a context would favor either variety
-of traditionalism. For our purposes, however, it suffices to note that
-the core theory is plausibly compatible with either preference
-relation: literal over global or the other way around (see also
-Table\ref{tab:predictions}).
-
-Does traditionalism also predict local readings to be available? The
-answer is slightly different for \as- and the \es-sentences. For
-\es-sentences, traditionalism does not predict that a local reading is
-available, at least not as a quantity implicature by conjoining the
-literal meaning with a suitable set of negated alternatives
-\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. The
-literal and the local reading of \es-sentences are logically
-independent. But if $X$ and $Y$ are logically independent
-propositions, then there is no proposition $Z$ such that $X$ would be
-equivalent to $Y \wedge \neg Z$.
-
-On the other hand, as for \as-sentences, there is a traditionalist way
-of deriving the local reading, namely by assuming that not only
-(\ref{bsp:AE-Alternative}) is an alternative to (\ref{bsp:AE}), but
-also the sentence in (\ref{bsp:AE-Alternatives-Extended}) \citep[e.g.][]{Sauerland2004:Scalar-Implicat}.
-
-\begin{exer}{bsp:AE}
-  \ex \mymark{All} of the students solved \mymark{some} of the problems.
-\end{exer}
-
-\begin{exer}{bsp:AE-Alternative}
-  \ex \label{bsp:AE-Alternatives-Standard}\mymark{All} of the students solved \mymark{all} of the problems.
-\end{exer}
+Traditionalism's predictions about availability and relative salience
+of readings of \as- and \es-sentences depend on further auxiliary
+assumptions. To have handy labels, we distinguish between strong and
+weak variants, and between restricted and unrestricted
+variants.
+
+Strong and weak traditionalism differ with respect to whether the
+assumptions needed to derive non-epistemic implicatures are prominent
+or not in the given context of utterance (or some experiment or
+other). These assumptions include relevance of the information in
+question, mutual awareness that the stronger alternative has been a
+speaker option, the speaker's competence about the issue,
+etc. \emph{Strong traditionalism} assumes that the additional
+assumptions needed to derive a non-epistemic implicatures are
+sufficiently salient to prefer the non-epistemic implicature over the
+literal reading; \emph{weak traditionalism} assumes the reverse
+preference order. In other words, in the context of a given
+experiment, it is compatible with a traditionalist position to expect
+literal or implicature readings to be more prominent. Or, put yet
+differently, a traditionalist could be uncertain as to whether a given
+experiment is more likely to trigger more implicature readings or
+literal readings. Without more information about the experiment or
+context of interpretation, traditionalism is compatible with either
+salience ordering.
+
+Orthogonal to this, we distinguish restricted and unrestricted
+variants of traditionalism. For our purposes, restricted
+traditionalism considers only alternative expressions that are
+stronger than the to-be-interpreted utterance. Unrestricted
+traditionalism is more relaxed and also allows alternatives that are
+derived from replacing \emph{some} with \emph{all} and vice versa, if
+necessary multiple times, even if the resulting alternative is not
+logically stronger. Restricted traditionalism considers only
+\as-sentences to have a relevant alternative, namely
+(\ref{bsp:AE-Alternative}). It then predicts the availability of a
+global reading for \as-sentences on top of the literal. Restricted
+traditionalism predicts only literal readings of \es-sentences,
+because the alternative (\ref{bsp:GE-Alternative}) does not entail the
+literal reading of (\ref{bsp:GE}). Every implicature reading available
+to restricted traditionalism is also available to unrestricted
+traditionalism, but the latter's predictions are even richer. For
+\as-sentences, the potential alternative
+(\ref{bsp:AE-Alternatives-Extended}) also makes local readings
+available \citep[e.g.][]{Sauerland2004:Scalar-Implicat}: conjoining a
+literal reading of (\ref{bsp:AE}) with the negation of
+(\ref{bsp:AE-Alternatives-Extended}) gives a local reading.
 
@@
 
-\noindent Clearly, if we conjoin a literal reading of (\ref{bsp:AE})
-with the negation of (\ref{bsp:AE-Alternatives-Extended}) we obtain
-exactly the local reading. (Notice that the negation of
-(\ref{bsp:AE-Alternatives-Extended}) entails the negation of
-(\ref{bsp:AE-Alternative}), so it makes no difference (not) to add it
-in this case.) Consequently, traditionalism does predict that the
-local reading of \as-sentences is available if
-(\ref{bsp:AE-Alternatives-Extended}) is an available alternative. We
-therefore introduce another distinction: \mymark{restricted
-  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
-not available and therefore predicts that the local reading for
-\as-sentences is not available; in contrast, \mymark{unrestricted
-  traditionalism} assumes that (\ref{bsp:AE-Alternatives-Extended}) is
-available and so is the local reading.\fn{The term traditionalism may
-  be misleading here because traditionalists usually assume that
-  scalar implicatures should only be computed when a sentence is
-  uttered in a context in which a logically stronger alternative is
-  relevant \cite{ChemlaSingh2014:Remarks-on-the-}. However, the
-  alternative in (\ref{bsp:AE-Alternatives-Extended}) is not stronger
-  than (\ref{bsp:AE}). For completeness sake, we still decided to
-  subsume “unrestricted traditionalism” under traditionalism because,
-  once alternatives like (\ref{bsp:AE-Alternatives-Extended}) are
-  acknowledged, the local reading of \as-sentences can be derived in a
-  straightforward traditionalist manner \citep[see also][who call this
-  type of theory ``unrestricted
-  globalism'']{ChemlaSpector2010:Experimental-Ev}.}
-
-As far as preferences over readings of \as-sentences are concerned,
-even unrestricted traditionalism would not predict that the local
-reading is preferred over the global reading. This is because the
-derivation of the local reading via
-(\ref{bsp:AE-Alternatives-Extended}) hinges on yet another auxiliary
-assumption, namely the availability of the alternative in
-(\ref{bsp:AE-Alternatives-Extended}), which seems, by comparing
-numbers of replacements, much less obvious and therefore presumably is
-less readily available than the alternative in
-(\ref{bsp:AE-Alternative}). Consequently, we derive the following
-predictions about preferences for unrestricted traditionalism: weak
-unrestricted traditionalism prefers the literal over the global over
-the local reading, while strong unrestricted traditionalism prefers
-the global over the local over the literal reading (see also
-Table~\ref{tab:predictions}).
+\noindent For \es-sentences, we derive a global reading via the
+negation of alternative (\ref{bsp:GE-Alternative}).
+
+In sum, a traditionalist core theory is compatible with a range of
+observations about the availability and relative salience of
+implicature readings. These are summarized in
+Table\ref{tab:predictions}. Most importantly for the subsequent
+discussion, traditionalism does not predict local readings for
+\es-sentences and can favor implicature readings over literal ones or
+vice versa.
 
@@
     & \lit > \glb 
-    & \lit > \glb
+    & \lit 
     \\
     \ \ \ \ weak unrestricted
-    & \lit > \glb > \loc 
+    & \lit > \glb , \loc 
     & \lit > \glb
@@
     & \glb > \lit 
-    & \glb > \lit
+    & \lit 
     \\
     \ \ \ \ strong unrestricted
-    & \glb > \loc > \lit 
+    & \glb , \loc > \lit 
     & \glb > \lit
@@
     are the predicted preference relations. If a reading is not
-    listed, it is predicted to be unavailable.}
+    listed, it is predicted to be unavailable. Comma-separated
+    readings are not ranked, i.e., not predicted to differ as opposed
+    to being predicted to be equally ranked.}
   \label{tab:predictions}

### 2015-02-06 text/paper/revision_01/paper.tex
K2 reworked section 3 traditionalism

@@
 
-Recently, a lot of evidence based on intuitive judgements and more
-theoretical considerations has been discussed in favor of
-\mymark{grammaticalism}
-\citep[see][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical}. % When
-% it comes to the predictions of available readings of \as- and
-% \es-sentences, grammaticalism appears like the conjunction of
-% traditionalism and conventionalism. But conceptually speaking,
-% grammaticalism goes down a road of its own.
-Grammaticalism approaches quantity implicatures by postulating a
-silent operator that can be variably applied during compositional
-computation of a sentence's truth-value
-\citep{Chierchia2006:Broaden-Your-Vi}, if necessary multiple times
-\citep{Fox2007:Free-Choice-and}. This silent operator is referred to
-as $\mathrm{O}(\cdot)$ or $\exh(\cdot)$, because it is assumed to be
-similar in effect to the meaning of particle \emph{only} or of the
-mechanism of \emph{exhaustive interpretation}
-\citep{GroenendijkStokhofThesis1984,Stechowvon-StechowZimmermann1984:Term-Answers-an,Rooijvan-RooijSchulz2013:Exhaustive-Inte,vanRooijSchulz:ExhaustiveInterpretation,Fox2007:Free-Choice-and}. For
-our purposes, it is enough to note that $\exh(\cdot)$ is a poly-typed
+The central idea behind grammaticalist approaches is that quantity
+implicatures are derived by application of exhaustivity operators at
+varying scope-sites during compositional computation of a sentence's
+truth-value, if necessary multiple times
+\citep[see][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical}. For
+our purposes, it is enough to assume that $\exh(\cdot)$ is a poly-typed
 function that enriches an expression $X$, which need not be a full
@@
   have been proposed
-  \citep[e.g.][]{Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}.}
+  \citep[e.g.][]{GroenendijkStokhofThesis1984,Stechowvon-StechowZimmermann1984:Term-Answers-an,Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}.}
 \begin{exe}
@@
 \end{exe}
-
-As this operator can apply at various scope sites, the grammatical
-approach predicts that all three readings of \as- and \es-sentences
-are available: literal readings arise if no exhaustification operator
-is applied; global readings arise if the exhaustification operator
-takes sentence-wide scope as in (\ref{Grammar-Global}); and local
-readings arise if the exhaustification operator takes scope under the
-respective quantifiers as in (\ref{Grammar-Local}).
+%
+A grammaticalist core theory predicts that all three readings of \as-
+and \es-sentences are in principle available: literal readings arise
+if no exhaustification operator is applied; global readings arise if
+the exhaustification operator takes sentence-wide scope as in
+(\ref{Grammar-Global}); and local readings arise if the
+exhaustification operator takes scope under the respective quantifiers
+as in (\ref{Grammar-Local}).
 
@@
 
-The grammatical approach, as described so far, does not yet make
-falsifiable predictions about the relative salience of our three
-candidate readings. In order to derive predictions about reading
-preferences, a selection principle is needed that determines which of
-the many readings made available by the grammar actually obtain or are
-preferred. Proponents of grammaticalism are aware of this and have
-suggested some tentative disambiguation
-strategies. \citet{Magri2011:Another-Argumen}, for example, opts for
-obligatory presence of $\exh$ with variability in the set of relevant
-alternatives.  In the approach of \citet{Magri2011:Another-Argumen},
-alternatives may be pruned entirely in the extreme case. In that case,
-all occurrences of $\exh$ become vacuous resulting in a literal
-reading. However, \citet{Magri2011:Another-Argumen} does not formulate
-an explicit theory about which alternatives enter into the computation
-of sentence meaning under what circumstances. Therefore, it is not
-clear what his approach predicts about the relative salience of the
-candidate readings.
-
-Other proponents of grammaticalism assume that insertion of $\exh$ is
-optional.  These approaches treat the ambiguity between our candidate
-readings as a structural one which resembles syntactic ambiguities. In
-order to derive predictions about reading preferences a mechanism of
-ambiguity resolution is needed in these approaches. One proposal is
-that readings are the more preferred the better they answer the
-contextually given question under discussion
-\citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}.
-Another proposal is to select readings by comparison of logical
-strengths, as suggested by the \mymark{strongest meaning hypothesis}
-of \citet{DalrympleKanazawa1998:Reciprocal-Expr}
-\citep[see][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. For
-now, we focus exclusively on this latter selection principle, because
-it seems to be the most prominent in the literature and because it
-makes the clearest predictions. In the discussion section
-(section~\ref{sec:discussion-1}) alternative selection principles will
-be reconsidered.
+It is a topic of active current debate as to how a grammaticalist
+approach should be supplemented with a principled \emph{disambiguation
+  mechanism} so as to rule out unattested readings obtainable by
+embedded exhaustification and to make concrete predictions about
+preferences over readings made available. % Grammaticalists therefore
+% acknowledge that \emph{some} disambiguation principle must be
+% specified, for otherwise grammaticalism would hardly make any
+% commitment and would overpredict readings in cases where they are
+% unattested, i.e., when scalar items appear in downward-entailing
+% contexts \citep[c.f.][for explicit
+% discussion]{FoxSpector:Economy-and-Emb}.
+Three kinds of approaches have been suggested in the literature
+\citep[c.f.][]{ChemlaSingh2014:Remarks-on-the-}. We briefly touch upon
+each, but focus on the one that is least controversially applicable to
+our experimental case, and that has theoretical significance beyond
+the debate about embedded implicatures.
+
+To start with,
+\citet{Magri2009:A-Theory-of-Ind,Magri2011:Another-Argumen} opts for
+obligatory presence of $\exh(\cdot)$ with variability in the set of relevant
+alternatives.  Under this approach, alternatives may be pruned
+entirely, so that all occurrences of $\exh(\cdot)$ become vacuous resulting
+in a literal reading. Whether alternatives apply or not is a matter of
+their relevance. It is not clear what his approach predicts \emph{ex
+  ante} about the relative salience of the candidate readings in our
+experiment, but we will show in Section~\ref{sec:critical-reflection}
+that this approach can be brought to accommodate the data well after
+the fact.
+
+Other proponents of grammaticalism assume that insertion of $\exh(\cdot)$ is
+optional. Under one proposal for disambiguation, readings are the more
+preferred the better they answer the contextually given question under
+discussion (QUD)
+\citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. This
+is a plausible suggestion, but does not give clear predictions for a
+case like our experiment without fixed QUD. Subjects could in
+principle accommodate any QUD, so that this approach would not
+restrict the space of reading preferences either.
+
+Luckily, the last kind of disambiguation approach does yield a clear
+and non-trivial restriction of reading preferences off-the-shelf. It
+is to select readings by comparison of logical strengths, as suggested
+by the \mymark{strongest meaning hypothesis} of
+\citet{DalrympleKanazawa1998:Reciprocal-Expr}. Supplementing
+grammaticalism with a strength-based selection criterion has been
+suggested, in one form or another, in many contributions to this
+paradigm
+\citep[e.g.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. At
+the same time, the strongest meaning hypothesis has been frequently
+called upon for disambiguation purposes in other domains as well,
+including reciprocals \citep{DalrympleKanazawa1998:Reciprocal-Expr},
+plural predication \citep{Winter2001:Plural-Predicat} or vagueness
+\citep{CobrerosEgre2012:Tolerant-Classi}. For these reasons, we focus
+from now on this latter type of selection principle. In the discussion
+section (section~\ref{sec:discussion-1}) alternative selection
+principles will be reconsidered.
 
 \citet{ChierchiaFox2008:The-Grammatical} discuss two concrete variants
-of strength-based disambiguation: fix a sentence with propositional
-content $S$ and candidate readings $C(S)$, where $C(S)$ contains $S$
-and all readings derivable from inserting $\exh(\cdot)$ at suitable
-scope sites;\fn{Strictly speaking, we should compare \emph{parses} of
-  sentences with $\exh(\cdot)$ at various scope sites with respect to
-  the readings that these parses give rise to
-  \citep[see][]{ChierchiaFox2008:The-Grammatical}, but we may ignore
-  this detail here for ease of exposition.} then define for $X,Y \in
-C(S)$ either
+of strength-based disambiguation that make non-trivial predications
+about preferred readings of \as- and \es-sentences (unlike, say, the
+more detailed variants of \cite{FoxSpector:Economy-and-Emb}): fix a
+sentence with propositional content $S$ and candidate readings $C(S)$,
+where $C(S)$ contains $S$ and all readings derivable from inserting
+$\exh(\cdot)$ at suitable scope sites;\fn{Strictly speaking, we should
+  compare \emph{parses} of sentences with $\exh(\cdot)$ at various
+  scope sites with respect to the readings that these parses give rise
+  to \citep[see][]{ChierchiaFox2008:The-Grammatical}, but we may
+  ignore this detail here for ease of exposition.} then define for
+$X,Y \in C(S)$ either
 \begin{exe}
@@
 
-Taking stock, under the auxiliary assumptions adopted here,
-traditionalism and grammaticalism make different predictions about the
-relative salience (and thus preference) of our candidate
-readings. Most notably, traditionalism does not predict local readings
-for \es-sentences to be available at all while grammaticalism does.
-Grammaticalism predicts that all candidate readings are available and,
-employing the strongest meaning hypothesis as disambiguation
-principle, also comes with a clear prediction about preference:
-literal meanings are dispreferred.  All predictions are summarized in
+Taking stock, traditionalism and grammaticalism have been introduced
+as fairly general core theories that need backup from particular
+auxiliary assumptions to make concrete predictions about availability
+and readings preferences for our target sentences. Most notably, under
+the assumptions made here, traditionalism does not predict local
+readings for \es-sentences to be available while grammaticalism does.
+Grammaticalism, when supplemented with the the strongest meaning
+hypothesis as disambiguation principle, predicts that all candidate
+readings are available and that literal readings are dispreferred in
+all cases. All predictions are summarized in
 Table~\ref{tab:predictions}.

### 2015-02-06 text/paper/revision_01/paper.tex
finalized edits sections 1-3 K2 revision 01

@@
   experiment sheds light on the relative preferences or salience of
-  candidate readings. The presented data turn out to be problematic
-  for both a traditional Gricean view of scalar implicature
-  calculation, as well as the more recent grammatical approach.
+  candidate readings. The presented data turn out to be unexpected
+  under a traditional Gricean view, but also suggest refinement of the
+  more recent grammatical approach.
 \end{abstract}
@@
 The controversy is usually seen as one between two main competing
-theoretical positions, which we call \mymark{traditionalism} and
-\mymark{grammaticalism} and take to be general ideas behind large
+theoretical positions, which we call \emph{traditionalism} and
+\emph{grammaticalism} and take to be general ideas behind large
 classes of approach to quantity implicatures \citep[c.f.][for related
@@
 theories]{ChemlaSingh2014:Remarks-on-the-}. Unfortunately, it is
-rather difficult to empirically test either ``core theory'' (
-terminology from \citeauthor{ChemlaSingh2014:Remarks-on-the-})
-directly because additional ``auxiliary assumptions'' are needed in
-both cases to derive falsifiable \emph{ex ante} predictions about
-to-be-expected observations in a concrete behavioral experiment, even
-irrespective of processing accounts. We therefore try to carefully set
-up plausible instantiations of either core theory with particular
-auxiliary assumptions that give testable predictions at the outset in
+rather difficult to empirically test either ``core theory''
+(terminology from \citeauthor{ChemlaSingh2014:Remarks-on-the-})
+directly because additional ``auxiliary assumptions'' are needed to
+derive falsifiable \emph{ex ante} predictions about to-be-expected
+observations in a concrete behavioral experiment, even irrespective of
+processing accounts. We therefore try to carefully set up plausible
+instantiations of either core theory with particular auxiliary
+assumptions that give testable predictions at the outset in
 Section~\ref{sec:theories-predictions}, then evaluate the obtained
@@
 often acknowledge the availability of local readings for prosodically
-marked utterances, albeit not as the result of a standard scalar
-implicature but of a different pragmatic process triggered by prosodic
-markedness
+marked utterances
 \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
@@
 may be an effect of “silent prosody” \citep[see
-e.g.][]{Bader98,Fodor98}. We will therefore address this extant
-position as the \mymark{prosodic markedness hypothesis} and argue
-that, if prosody is hypothesized to play a central role, it is vital
-to present target sentences auditorily or to control for effects of
-“silent prosody” that subjects may apply when reading a
-sentence. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
+e.g.][]{Bader98,Fodor98}. We therefore address this position as the
+\emph{prosodic markedness hypothesis} explicitly. Secondly, as
+\citet{Tielvan-Tiel2012:Embedded-Scalar} and
 \citet{GeurtsTielvan-Tiel2013:Embedded-Scalar} argue, the alleged
@@
 
-% More generally, two prerequisites have to be met in order to make use
-% of experimental data to decide between theoretical positions regarding
-% the computation of quantity inferences. Firstly, both traditionalism
-% and grammaticalism have to be augmented with additional assumptions to
-% derive testable predictions about the relative salience of candidate
-% readings. For example, hypothezised effects of prosodic marking have
-% to be taken into account before we can test traditionalism empirically
-% using sentences (\ref{bsp:AE}) and (\ref{bsp:GE}).  We will address
-% this extant position as the \mymark{prosodic markedness hypothesis}
-% and argue that, if prosody is hypothesized to play a central role, it
-% is vital to present target sentences auditorily or to control for
-% effects of “silent prosody” that subjects may apply when reading a
-% sentence. Secondly, the relative salience of candidate readings has to
-% be operationalized properly, i.e., we have to devise methods to
-% measure relative salience. For example, typicality effects and logical
+% More generally, two prerequisites have to be met in order to make
+% use of experimental data to decide between theoretical positions
+% regarding the computation of quantity inferences. Firstly, both
+% traditionalism and grammaticalism have to be augmented with
+% additional assumptions to derive testable predictions about the
+% relative salience of candidate readings. For example, hypothezised
+% effects of prosodic marking have to be taken into account before we
+% can test traditionalism empirically using sentences (\ref{bsp:AE})
+% and (\ref{bsp:GE}).  We will address this position as the
+% \mymark{prosodic markedness hypothesis} and argue that, if prosody
+% is hypothesized to play a central role, it is vital to present
+% target sentences auditorily or to control for effects of “silent
+% prosody” that subjects may apply when reading a sentence. Secondly,
+% the relative salience of candidate readings has to be
+% operationalized properly, i.e., we have to devise methods to measure
+% relative salience. For example, typicality effects and logical
 % dependencies between readings have to be controlled for when
 % evaluating speaker judgments in terms of the salience of candidate
-% readings.  Both of these prerequisites are related to formulating what
-% \citet{ChemlaSingh2014:Remarks-on-the-} call ``auxiliary assumptions''
-% that are necessary to enable theoretical accounts to make predictions
-% about processing. Our emphasis here is not on processing accounts, but
-% on predictions of behavioral data --- what is sometimes, perhaps
-% misleadingly, called a computational-level perspective. But even so,
-% traditionalism and grammaticalism have to summon auxiliary assumptions
-% which connect the core theories to the dependent variables of a
-% behavioral experiment. Without proper auxiliary assumptions it is hard
-% (or impossible) to test traditionalism or grammaticalism empirically.
+% readings.  Both of these prerequisites are related to formulating
+% what \citet{ChemlaSingh2014:Remarks-on-the-} call ``auxiliary
+% assumptions'' that are necessary to enable theoretical accounts to
+% make predictions about processing. Our emphasis here is not on
+% processing accounts, but on predictions of behavioral data --- what
+% is sometimes, perhaps misleadingly, called a computational-level
+% perspective. But even so, traditionalism and grammaticalism have to
+% summon auxiliary assumptions which connect the core theories to the
+% dependent variables of a behavioral experiment. Without proper
+% auxiliary assumptions it is hard (or impossible) to test
+% traditionalism or grammaticalism empirically.
 
@@
 sentences. Section~\ref{sec:theories-predictions} works out plausible
-\emph{ex ante} predictions of the core theories traditionalism and
-grammaticalism (for some practically relevant auxiliary assumptions)
-about availability and relative salience of readings for our target
-sentences. Section~\ref{sec:previous-studies} reviews related
+\emph{ex ante} predictions of the competing core
+theories. Section~\ref{sec:previous-studies} reviews related
 experimental studies to the extent necessary to motivate our own
-approach. Section~\ref{sec:exp} eventually contributes our
-experimental design, analyses and results. Finally,
-Section~\ref{sec:critical-reflection} discusses our method and
-interpretation of the results in a broader theoretical context.
+approach. Section~\ref{sec:exp} describes our experimental design,
+analyses and results. Finally, Section~\ref{sec:critical-reflection}
+discusses our method and interpretation of the results in a broader
+theoretical context.
 
@@
 overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation,ChemlaSingh2014:Remarks-on-the-}. We
-will refer to these as \mymark{traditionalism} and
-\mymark{grammaticalism} and treat each in turn. Both approaches are
-addressed here as ``core theories'': two main ideas behind several
-approaches to quantity implicatures. To determine concrete predictions
-from these, additional ``auxiliary assumptions'' are necessary. Here,
-we spell a set of such auxiliary assumptions for each core theory. Our
-motivation for the particular choices we make is partly guided by
-practical concerns, so as to have a concrete set of predictions for
-each core theory to formulate expectations and compare our data to. We
-therefore introduce some prominent or otherwise relevant variants of
-either core theory, the predictions of which are summarized in
-Table\ref{tab:predictions} on page~\pageref{tab:predictions}. How
-other potential instantiations of either core theory fare in light of
-our data will be discussed in Section~\ref{sec:critical-reflection}.
-
-Although strictly speaking not a part of a Gricean theory of scalar
-implicature calculation, traditionalists frequently concede that local
-readings are in principle available, albeit not as a standard scalar
-implicature, but as a different pragmatic process triggered by
-prosodic markedness. We address this \emph{prosodic markedness
+will refer to these as \emph{traditionalism} and \emph{grammaticalism}
+and treat each in turn. Both approaches are addressed here as ``core
+theories'': two main ideas behind several approaches to quantity
+implicatures. To determine concrete predictions from these, additional
+``auxiliary assumptions'' are necessary. Here, we spell a set of such
+auxiliary assumptions for each core theory. Our motivation for the
+particular choices we make is partly guided by practical concerns, so
+as to have a concrete set of predictions for each core theory to
+formulate expectations and compare our data to. We therefore introduce
+some prominent or otherwise relevant variants of either core theory,
+the predictions of which are summarized in Table~\ref{tab:predictions}
+on page~\pageref{tab:predictions}. How other potential instantiations
+of either core theory fare in light of our data will be discussed in
+Section~\ref{sec:critical-reflection}.
+
+Traditionalists frequently concede that local readings are licensed if
+prosodically marked. We address this \emph{prosodic markedness
   hypothesis} separately in Section~\ref{sec:inton-mark-hypoth},
@@
 The traditionalist view gives rise to what
-\citet{Geurts2010:Quantity-Implic} calls the \mymark{Gricean recipe}
-for deriving a scalar inference (\ref{bsp:Plain-SI-Implicature}) from
-an utterance of (\ref{bsp:Plain-SI-Target}): if the issue whether Hans
-solved only some or all of the problems is relevant, then a
-cooperative and knowledgable speaker would utter
-(\ref{bsp:Plain-SI-Alternative}) if in a position to do so; hence, one
-of the most natural explanations of why such a speaker has not uttered
-(\ref{bsp:Plain-SI-Alternative}), but only (\ref{bsp:Plain-SI-Target})
-is that she is uncertain of whether (\ref{bsp:Plain-SI-Alternative})
-is true; but on the assumption that she is knowledgeable (competent,
-opinionated, informed \dots) it follows that
-(\ref{bsp:Plain-SI-Implicature}) should in fact be true.\fn{We are
-  glossing here somewhat swiftly over the more nuanced details of the
-  derivation of implicatures targeting the speaker's epistemic state
+\citet{Geurts2010:Quantity-Implic} calls the \emph{Gricean recipe} for
+deriving (\ref{bsp:Plain-SI-Implicature}) from
+(\ref{bsp:Plain-SI-Target}): if the issue whether Hans solved only
+some or all of the problems is relevant, then a cooperative and
+knowledgable speaker would utter (\ref{bsp:Plain-SI-Alternative}) if
+in a position to do so; hence, one of the most natural explanations of
+why such a speaker has not uttered (\ref{bsp:Plain-SI-Alternative}),
+but only (\ref{bsp:Plain-SI-Target}) is that she is uncertain of
+whether (\ref{bsp:Plain-SI-Alternative}) is true; but on the
+assumption that she is knowledgeable (competent, opinionated, informed
+\dots) it follows that (\ref{bsp:Plain-SI-Implicature}) should in fact
+be true.\fn{We are glossing here somewhat swiftly over the more
+  nuanced details of the derivation of implicatures targeting the
+  speaker's epistemic state
   \citep[e.g.][]{Gazdar1979:Pragmatics:-Imp,Soames1982:How-Presupposit}. More
@@
 assumptions. To have handy labels, we distinguish between strong and
-weak variants, and between restricted and unrestricted
-variants.
+weak, and between restricted and unrestricted variants.
 
@@
 assumptions needed to derive non-epistemic implicatures are prominent
-or not in the given context of utterance (or some experiment or
-other). These assumptions include relevance of the information in
-question, mutual awareness that the stronger alternative has been a
-speaker option, the speaker's competence about the issue,
-etc. \emph{Strong traditionalism} assumes that the additional
-assumptions needed to derive a non-epistemic implicatures are
-sufficiently salient to prefer the non-epistemic implicature over the
-literal reading; \emph{weak traditionalism} assumes the reverse
-preference order. In other words, in the context of a given
-experiment, it is compatible with a traditionalist position to expect
-literal or implicature readings to be more prominent. Or, put yet
-differently, a traditionalist could be uncertain as to whether a given
-experiment is more likely to trigger more implicature readings or
-literal readings. Without more information about the experiment or
-context of interpretation, traditionalism is compatible with either
-salience ordering.
+in the given context of utterance (or some experiment or other). These
+assumptions include relevance of the information in question, mutual
+awareness that the stronger alternative has been a speaker option, the
+speaker's competence about the issue, etc. \emph{Strong
+  traditionalism} assumes that the additional assumptions needed to
+derive non-epistemic implicatures are sufficiently salient to prefer
+an implicature reading over a literal reading; \emph{weak
+  traditionalism} assumes the reverse preference order. In other
+words, in the context of a given experiment, it is compatible with a
+traditionalist position to expect literal or implicature readings to
+be more prominent. Or, put yet differently, a traditionalist could be
+uncertain as to whether a given experiment is more likely to trigger
+more implicature readings or literal readings. Without more
+information about the experiment or context of interpretation,
+traditionalism is compatible with either salience ordering.
 
@@
 stronger than the to-be-interpreted utterance. Unrestricted
-traditionalism is more relaxed and also allows alternatives that are
-derived from replacing \emph{some} with \emph{all} and vice versa, if
-necessary multiple times, even if the resulting alternative is not
-logically stronger. Restricted traditionalism considers only
-\as-sentences to have a relevant alternative, namely
-(\ref{bsp:AE-Alternative}). It then predicts the availability of a
-global reading for \as-sentences on top of the literal. Restricted
-traditionalism predicts only literal readings of \es-sentences,
-because the alternative (\ref{bsp:GE-Alternative}) does not entail the
-literal reading of (\ref{bsp:GE}). Every implicature reading available
-to restricted traditionalism is also available to unrestricted
-traditionalism, but the latter's predictions are even richer. For
-\as-sentences, the potential alternative
-(\ref{bsp:AE-Alternatives-Extended}) also makes local readings
-available \citep[e.g.][]{Sauerland2004:Scalar-Implicat}: conjoining a
-literal reading of (\ref{bsp:AE}) with the negation of
+traditionalism also allows alternatives that are derived from
+replacing \emph{some} with \emph{all} and vice versa, if necessary
+multiple times, even if the resulting alternative is not logically
+stronger. Restricted traditionalism considers only \as-sentences to
+have a relevant alternative, namely (\ref{bsp:AE-Alternative}). It
+then predicts the availability of a global reading for \as-sentences
+on top of the literal. Restricted traditionalism predicts only literal
+readings of \es-sentences, because the alternative
+(\ref{bsp:GE-Alternative}) does not entail the literal reading of
+(\ref{bsp:GE}). Every implicature reading available to restricted
+traditionalism is also available to unrestricted traditionalism, but
+the latter's predictions are even richer. For \as-sentences, the
+potential alternative (\ref{bsp:AE-Alternatives-Extended}) also makes
+local readings available
+\citep[e.g.][]{Sauerland2004:Scalar-Implicat}: conjoining a literal
+reading of (\ref{bsp:AE}) with the negation of
 (\ref{bsp:AE-Alternatives-Extended}) gives a local reading.
@@
 \noindent For \es-sentences, we derive a global reading via the
-negation of alternative (\ref{bsp:GE-Alternative}).
+negation of alternative (\ref{bsp:GE-Alternative}), but not local
+readings.
 
@@
 implicature readings. These are summarized in
-Table\ref{tab:predictions}. Most importantly for the subsequent
+Table~\ref{tab:predictions}. Most importantly for the subsequent
 discussion, traditionalism does not predict local readings for
@@
 varying scope-sites during compositional computation of a sentence's
-truth-value, if necessary multiple times
-\citep[see][]{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical}. For
-our purposes, it is enough to assume that $\exh(\cdot)$ is a poly-typed
-function that enriches an expression $X$, which need not be a full
-proposition, based on a set $\alt(X)$ of (suitable, relevant)
+truth-value
+\citep[see][]{Chierchia2006:Broaden-Your-Vi,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical}. For
+our purposes, it is enough to assume that $\exh(\cdot)$ is a
+poly-typed function that enriches an expression $X$, which need not be
+a full proposition, based on a set $\alt(X)$ of (suitable, relevant)
 alternatives to $X$ that yields an enriched meaning of the
-form:\fn{More sophisticated formulations of exhaustive interpretation
-  have been proposed
-  \citep[e.g.][]{GroenendijkStokhofThesis1984,Stechowvon-StechowZimmermann1984:Term-Answers-an,Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}.}
+form:% \fn{More sophisticated formulations of exhaustive interpretation
+  % have been proposed
+  % \citep[e.g.][]{GroenendijkStokhofThesis1984,Stechowvon-StechowZimmermann1984:Term-Answers-an,Schulz2005:A-Pragmatic-Sol,vanRooijSchulz:ExhaustiveInterpretation,Spector2006:Scalar-Implicat,Fox2007:Free-Choice-and}.}
 \begin{exe}
@@
 It is a topic of active current debate as to how a grammaticalist
-approach should be supplemented with a principled \emph{disambiguation
-  mechanism} so as to rule out unattested readings obtainable by
-embedded exhaustification and to make concrete predictions about
-preferences over readings made available. % Grammaticalists therefore
+approach should be supplemented with a general and well-motivated
+\emph{disambiguation criterion} so as to rule out unattested readings
+obtainable by embedded exhaustification and to make concrete
+predictions about preferences over readings made
+available. % Grammaticalists therefore
 % acknowledge that \emph{some} disambiguation principle must be
@@
 \citet{Magri2009:A-Theory-of-Ind,Magri2011:Another-Argumen} opts for
-obligatory presence of $\exh(\cdot)$ with variability in the set of relevant
-alternatives.  Under this approach, alternatives may be pruned
-entirely, so that all occurrences of $\exh(\cdot)$ become vacuous resulting
-in a literal reading. Whether alternatives apply or not is a matter of
-their relevance. It is not clear what his approach predicts \emph{ex
-  ante} about the relative salience of the candidate readings in our
-experiment, but we will show in Section~\ref{sec:critical-reflection}
-that this approach can be brought to accommodate the data well after
-the fact.
+obligatory presence of $\exh(\cdot)$ with variability in the set of
+alternatives to feed into each $\exh(\cdot)$. Under this approach,
+alternatives may be pruned entirely, so that all occurrences of
+$\exh(\cdot)$ become vacuous, resulting in a literal reading. Whether
+alternatives apply or not is a matter of their relevance. It is not
+clear what his approach predicts \emph{ex ante} about the relative
+salience of candidate readings in a neutral experiment that does not
+explicitly provide information about which alternatives are relevant
+(for whatever purpose). However, we will show in
+Section~\ref{sec:critical-reflection} that Magri's approach can be
+brought to accommodate the data very well after the fact.
 
@@
 and non-trivial restriction of reading preferences off-the-shelf. It
-is to select readings by comparison of logical strengths, as suggested
-by the \mymark{strongest meaning hypothesis} of
+selects readings by comparison of logical strengths, as suggested by
+the \emph{strongest meaning hypothesis} of
 \citet{DalrympleKanazawa1998:Reciprocal-Expr}. Supplementing
@@
 \citep{CobrerosEgre2012:Tolerant-Classi}. For these reasons, we focus
-from now on this latter type of selection principle. In the discussion
-section (section~\ref{sec:discussion-1}) alternative selection
-principles will be reconsidered.
+from now on this latter type of selection
+principle. Section~\ref{sec:critical-reflection} reconsiders
+alternative selection principles.
 
@@
 Since the former is entailed by the latter, we will speak of
-\mymark{weak grammaticalism} and \mymark{strong grammaticalism},
+\emph{weak grammaticalism} and \emph{strong grammaticalism},
 depending on whether (\ref{bsp:SMH-Total}) or (\ref{bsp:SMH-Partial})
@@
 auxiliary assumptions to make concrete predictions about availability
-and readings preferences for our target sentences. Most notably, under
+and reading preferences for our target sentences. Most notably, under
 the assumptions made here, traditionalism does not predict local
 readings for \es-sentences to be available while grammaticalism does.
-Grammaticalism, when supplemented with the the strongest meaning
-hypothesis as disambiguation principle, predicts that all candidate
+Grammaticalism, in the form proposed by
+\citet{ChierchiaFox2008:The-Grammatical}, predicts that all candidate
 readings are available and that literal readings are dispreferred in
@@
     listed, it is predicted to be unavailable. Comma-separated
-    readings are not ranked, i.e., not predicted to differ as opposed
-    to being predicted to be equally ranked.}
+    readings are not ranked, i.e., not predicted to differ and not
+    predicted to be equally salient.}
   \label{tab:predictions}
@@
 
-Although restricted traditionalism does not of itself predict local readings to be
-available at all and even unrestricted traditionalism does not predict local
-readings for \es-sentences,  many authors who adhere to a traditionalist position
-propose that local readings are available if the embedded scalar item
-is prosodically marked by contrastive stress \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
-is taken to be continuous with other cases where pragmatic enrichments can
-take scope under logical operators if the relevant focal accent is present (\ref{bsp:Stress}).
+Although restricted traditionalism does not of itself predict local
+readings to be available at all and even unrestricted traditionalism
+does not predict local readings for \es-sentences, many authors who
+adhere to a traditionalist position propose that local readings can be
+available if the embedded scalar item is prosodically marked by
+contrastive stress
+\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
+is taken to be continuous with other cases where pragmatic enrichments
+can take scope under logical operators if the relevant focal accent is
+present (\ref{bsp:Stress}).
 

### 2015-02-09 text/paper/revision_01/paper.tex
K2 cover letter; sigh...

@@
 picture with respect to some meaning may affect graded truth-value
-judgments: a sentence like \emph{Some of the 10 marbles are white} is
-more typical, intuitively speaking, in a situation with 4 white
-marbles than in a situation with 8 or 9 white marbles \citep[for more
-on the controversial interpretation of ``typicality'' in this context
-see][]{Tielvan-Tiel2014:Quantity-Matter,Cummins2014:Typicality-made,
-  ,Franke2014:Typical-use-of-}. \citeauthor{ChemlaSpector2010:Experimental-Ev}
-show that graded judgments of \as-sentences differ significantly for
-different pictures that agree on the truth value of relevant readings
-but differ with respect to the amount of connections between
+judgments. \citeauthor{ChemlaSpector2010:Experimental-Ev} show that
+graded judgments of \as-sentences differ significantly for different
+pictures that agree on the truth value of relevant readings but differ
+with respect to the amount of connections between
 icons. \citeauthor{ChemlaSpector2010:Experimental-Ev} suggest that
@@
 differences, but submit that this does not explain away the high
-acceptance of pictures like Figure \ref{fig:weak}.
+acceptance of pictures like Figure \ref{fig:weak}.\footnote{It is a
+  matter of controversy what ``typicality'' actually is. Intuitively,
+  a sentence like \emph{Some of the 10 marbles are white} is more
+  ``typical'' or ``natural'' in a situation with 4 white marbles than
+  in a situation with 8 or 9 white marbles. These intuitions have been
+  tested and reported as ``typicality'' or ``naturalness'' data for a
+  number of quantifiers
+  \citep{DegenTanenhaus2011:Making-Inferenc,Tielvan-Tiel2012:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter,DegenTanenhaus2012:Processing-Scal}. It
+  remains controversial, however, what exactly it is that is measured
+  and labelled ``typicality'' in these tasks
+  \citep[c.f.][]{Cummins2014:Typicality-made,Franke2014:Typical-use-of-}.}
 

### 2015-02-09 text/paper/revision_01/paper.tex
K2 more cover letter writing ... sigh sigh

@@
 \begin{abstract}
-  The scalar item \emph{some} is widely assumed to receive a pragmatic
-  meaning enrichment to \emph{some but not all} if it occurs in matrix
+  The scalar item \emph{some} is widely assumed to receive a meaning
+  enrichment to \emph{some but not all} if it occurs in matrix
   position. The question under which circumstances this enrichment can
@@
 cases.  In \as-sentences (mnemonic for \textit{all \dots some \dots})
-as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded the under
+as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded under the
 universal quantifier \emph{all}. In \es-sentences (mnemonic for
@@
 takes scope under the non-monotonic quantifier \emph{exactly one}.
-Current theories, have proposed at least three candidate readings
-for \as- and \es-sentences: (i) a \emph{literal reading} like in (\ref{bsp:AE-Literal}) and
-(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
-(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
-(\ref{bsp:GE-Global}) where the meaning of (\ref{bsp:AE}) and
-(\ref{bsp:GE}) is enriched with the negation of the corresponding
-sentences (\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative})
-respectively; and also (iii) a \emph{local reading} like in
-(\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where \emph{some} is
-interpreted as \emph{some but not all} in the scope of the embedding
-quantifier.
+Current theories, have proposed at least three candidate readings for
+\as- and \es-sentences: (i) a \emph{literal reading} like in
+(\ref{bsp:AE-Literal}) and (\ref{bsp:GE-Literal}) where \emph{some}
+has only its literal meaning; (ii) a \emph{global reading} like in
+(\ref{bsp:AE-Global}) and (\ref{bsp:GE-Global}) where the meaning of
+(\ref{bsp:AE}) and (\ref{bsp:GE}) is enriched with the negation of the
+corresponding sentences (\ref{bsp:AE-Alternative}) and
+(\ref{bsp:GE-Alternative}) respectively; and also (iii) a \emph{local
+  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
+\emph{some} is interpreted as \emph{some but not all} in the scope of
+the embedding quantifier.
 
@@
 To deal with these methodological problems, this paper presents
-results form an experimental study which presented sentence materials
+results from an experimental study which presented sentence materials
 auditorily and explicitly manipulated contrastive stress on embedded
@@
 
-Forty native speakers of German took part in our study, none of which
+Forty native speakers of German took part in our study, none of whom
 had any prior exposure to logic or formal semantics. We excluded two
@@
 indicated by a \emph{false} response. It appears that subjects read
-\es-sentences as if the upward-monotonic quantifier \emph{exactly one}
+\es-sentences as if the non-monotonic quantifier \emph{exactly one}
 was a monotonic \emph{at least one}, without pragmatic enrichment of

### 2015-02-19 text/paper/revision_01/paper.tex
final edits together

@@
 Given this plurality of hypothesized readings, the question arises:
-how salient are these theoretically conceivable readings compared to
-each other (if they are detectable by empirical means at all)?
+how \emph{salient} are these theoretically conceivable readings compared to
+each other, or, put differently, what is the \emph{preference order} on
+hypothesized readings (if they are detectable by empirical means at all)?
 Addressing this question empirically is relevant because it lies at
@@
 \emph{grammaticalism} and take to be general ideas behind large
-classes of approach to quantity implicatures \citep[c.f.][for related
+classes of approaches to quantity implicatures \citep[c.f.][for related
 discussion with a focus on deriving processing
-theories]{ChemlaSingh2014:Remarks-on-the-}. Unfortunately, it is
-rather difficult to empirically test either ``core theory''
-(terminology from \citeauthor{ChemlaSingh2014:Remarks-on-the-})
-directly because additional ``auxiliary assumptions'' are needed to
-derive falsifiable \emph{ex ante} predictions about to-be-expected
-observations in a concrete behavioral experiment, even irrespective of
-processing accounts. We therefore try to carefully set up plausible
-instantiations of either core theory with particular auxiliary
-assumptions that give testable predictions at the outset in
-Section~\ref{sec:theories-predictions}, then evaluate the obtained
-predictions against our data, and finally broaden our perspective to
-reflect in Section~\ref{sec:critical-reflection} on the impact of our
-data on the more general tenability of the core theories.
-
-But even with crisp theoretical predictions at hand, matters are still
-very complex, as reflected by lively discussions about which
-conclusions are permitted by previous experimental research
-\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,BenzGotzner2014:Embedded-implic}. The
-results of these studies were discussed controversially because of
-several specific reasons. Firstly, and most importantly, previous
+theories]{ChemlaSingh2014:Remarks-on-the-}. % Unfortunately, it is
+% rather difficult to empirically test either ``core theory''
+% (terminology from \citeauthor{ChemlaSingh2014:Remarks-on-the-})
+% directly because additional ``auxiliary assumptions'' are needed to
+% derive falsifiable \emph{ex ante} predictions about to-be-expected
+% observations in a concrete behavioral experiment, even irrespective of
+% processing accounts. We therefore try to carefully set up plausible
+% instantiations of either core theory with particular auxiliary
+% assumptions that give testable predictions at the outset in
+% Section~\ref{sec:theories-predictions}, then evaluate the obtained
+% predictions against our data, and finally broaden our perspective to
+% reflect in Section~\ref{sec:critical-reflection} on the impact of our
+% data on the more general tenability of the core theories.
+
+Results from previous empirical studies have been discussed
+controversially
+\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev,BenzGotzner2014:Embedded-implic}. This
+is because of several reasons. Firstly, and most importantly, previous
 studies presented target sentences visually.  However, traditionalists
@@
 sentences. Section~\ref{sec:theories-predictions} works out plausible
-\emph{ex ante} predictions of the competing core
-theories. Section~\ref{sec:previous-studies} reviews related
-experimental studies to the extent necessary to motivate our own
-approach. Section~\ref{sec:exp} describes our experimental design,
+\emph{ex ante} predictions of \emph{traditionalism} and
+\emph{grammaticalism}. Section~\ref{sec:previous-studies} reviews
+related experimental studies to the extent necessary to motivate our
+own approach. Section~\ref{sec:exp} describes our experimental design,
 analyses and results. Finally, Section~\ref{sec:critical-reflection}
@@
 and treat each in turn. Both approaches are addressed here as ``core
-theories'': two main ideas behind several approaches to quantity
-implicatures. To determine concrete predictions from these, additional
-``auxiliary assumptions'' are necessary. Here, we spell a set of such
+theories'' (terminology from
+\citeauthor{ChemlaSingh2014:Remarks-on-the-}): two main ideas behind
+several approaches to quantity implicatures. To determine concrete
+predictions from these, additional ``auxiliary assumptions'' are
+necessary to derive \emph{ex ante} falsifiable predictions about
+to-be-expected observations in a concrete behavioral experiment, even
+irrespective of processing accounts. Here, we spell out a set of such
 auxiliary assumptions for each core theory. Our motivation for the
@@
 formulate expectations and compare our data to. We therefore introduce
-some prominent or otherwise relevant variants of either core theory,
-the predictions of which are summarized in Table~\ref{tab:predictions}
-on page~\pageref{tab:predictions}. How other potential instantiations
-of either core theory fare in light of our data will be discussed in
+certain relevant variants of either core theory, the predictions of
+which are summarized in Table~\ref{tab:predictions} on
+page~\pageref{tab:predictions}. How other potential instantiations of
+either core theory fare in light of our data will be discussed in
 Section~\ref{sec:critical-reflection}.
@@
   hypothesis} separately in Section~\ref{sec:inton-mark-hypoth},
-alongside a brief revision of the relevant experimental data.
+alongside a brief recap of the relevant experimental data.
 
@@
 Strong and weak traditionalism differ with respect to whether the
-assumptions needed to derive non-epistemic implicatures are prominent
-in the given context of utterance (or some experiment or other). These
-assumptions include relevance of the information in question, mutual
-awareness that the stronger alternative has been a speaker option, the
-speaker's competence about the issue, etc. \emph{Strong
-  traditionalism} assumes that the additional assumptions needed to
-derive non-epistemic implicatures are sufficiently salient to prefer
-an implicature reading over a literal reading; \emph{weak
-  traditionalism} assumes the reverse preference order. In other
-words, in the context of a given experiment, it is compatible with a
-traditionalist position to expect literal or implicature readings to
-be more prominent. Or, put yet differently, a traditionalist could be
-uncertain as to whether a given experiment is more likely to trigger
-more implicature readings or literal readings. Without more
-information about the experiment or context of interpretation,
-traditionalism is compatible with either salience ordering.
+assumptions needed to derive (non-epistemic) implicatures are
+plausibly warranted in the given context of utterance (or some
+experiment or other). These assumptions include relevance of the
+information in question, mutual awareness that the stronger
+alternative has been a speaker option, the speaker's competence about
+the issue, etc. \emph{Strong traditionalism} assumes that the
+additional assumptions needed to derive (non-epistemic) implicatures
+are sufficiently salient to prefer an implicature reading over a
+literal reading; \emph{weak traditionalism} assumes the reverse
+preference order. In other words, in the context of a given
+experiment, it is compatible with a traditionalist position to expect
+literal or implicature readings to be more prominent. Or, put yet
+differently, a traditionalist could be uncertain as to whether a given
+experiment is more likely to trigger more implicature readings or
+literal readings. Without more information about the experiment or
+context of interpretation, traditionalism is compatible with either
+salience ordering.
 
@@
 
-Luckily, the last kind of disambiguation approach does yield a clear
-and non-trivial restriction of reading preferences off-the-shelf. It
-selects readings by comparison of logical strengths, as suggested by
-the \emph{strongest meaning hypothesis} of
+The last kind of disambiguation approach does yield a clear
+restriction of reading preferences for the case at hand. It selects
+readings by comparison of logical strengths, as suggested by the
+\emph{strongest meaning hypothesis} of
 \citet{DalrympleKanazawa1998:Reciprocal-Expr}. Supplementing
@@
 \citet{ChierchiaFox2008:The-Grammatical} discuss two concrete variants
-of strength-based disambiguation that make non-trivial predications
+of strength-based disambiguation that make non-trivial predictions
 about preferred readings of \as- and \es-sentences (unlike, say, the
@@
 readings are available for \as- and \es-sentences, but only if
-prosodicly marked by contrastive stress.
+prosodically marked by contrastive stress.
 
@@
 may have been present at least in a subset of the items (see
-footnote~1 in \citet{Frazier08}, p.~330).
+Footnote~1 in \citet{Frazier08}, p.~330).
 
@@
 To sum up so far, though an effect of contrastive accentuation has
-been claimed to be essential for triggering local implicatures,
-experimental evidence is currently mixed, suggesting potential effects
-of presentation mode (visual vs.~auditory), item-specific
-characteristics, as well as the specific construction under
-investigation (e.g., embedded cases vs.~non-embedded cases such as in
-\citet{SchwarzClifton2008:Strengthening-o}). It is for these reasons
-that an experimental investigation into the availability of readings
-of \as- and \es-sentences should present sentential material
-auditorily and explicitly address the prosodic markedness
-hypothesis.
+been claimed to be essential for traditionalism for triggering local
+implicatures, experimental evidence is currently mixed, suggesting
+potential effects of presentation mode (visual vs.~auditory),
+item-specific characteristics, as well as the specific construction
+under investigation (e.g., embedded cases vs.~non-embedded cases such
+as in \citet{SchwarzClifton2008:Strengthening-o}). It is for these
+reasons that an experimental investigation into the availability of
+readings of \as- and \es-sentences should present sentential material
+auditorily and explicitly address the prosodic markedness hypothesis.
 
@@
   informative about the latter. We will address this worry in
-  Section~\textcolor{red}{XYZ}, where we argue that this does not
-  affect the main conclusion that we would like to draw from our data
-  eventually.}
+  Section~\ref{sec:critical-reflection}, where we argue that this does
+  not affect the main conclusion that we would like to draw from our
+  data eventually.}
 
@@
 \as-accented: 86.8\%, \es-neutral: 68.4\%, \es-accented: 68.4\%). Only
-two answers across all critical conditions fall into the category
+two answers (0.4\%) across all critical conditions fall into the category
 indicative of global readings. Judgements indicative of local
@@
 the critical position to reveal a global reading, the latter would be
-indicated by a \emph{false} response. It appears that subjects read
-\es-sentences as if the non-monotonic quantifier \emph{exactly one}
-was a monotonic \emph{at least one}, without pragmatic enrichment of
-\emph{some}. 16 out of the total 21 answers in this category come from
-5 subjects, while the remaining 5 were single answers by 5 different
-subjects.
+indicated by a \emph{false} response. Given the low number of possible
+mistakes resulting from confusion buttons for \emph{true} and
+\emph{false} elsewhere, this seems to be a more systematic pattern. It
+appears as if subjects read \es-sentences as if the non-monotonic
+quantifier \emph{exactly one} was a monotonic \emph{at least one},
+without pragmatic enrichment of \emph{some}. 16 out of the total 21
+answers in this category come from 5 subjects, while the remaining 5
+were single answers by 5 different subjects.
 % subjects 1, 9, 12, 21, 84
@@
 late. But on top of that, a substantial number of `error' answers
-occurs on critical positions. For example, in the \lc-sequence there
-are 23 \emph{true} answers at step 6 where \emph{false} answers would
-be taken as indicative of \ec-readings. In the \ec-sequence there are
-28 \emph{false} answers at step 5 where \emph{true} answers would be
-taken as indicative of \lc-readings. Finally, prosodic cues for
-dispreferred \ec-readings seem to have led to more mistakes than
+occurs on the critical positions. For example, in the \lc-sequence
+there are 23 \emph{true} answers at step 6 where \emph{false} answers
+would be taken as indicative of \ec-readings. In the \ec-sequence
+there are 28 \emph{false} answers at step 5 where \emph{true} answers
+would be taken as indicative of \lc-readings. Finally, prosodic cues
+for dispreferred \ec-readings seem to have led to more mistakes than
 other prosodic patterns.
@@
 judged later in the sequence. Also, the incremental verification task
-was generally sensitive to prosody. However, significant prosodic
-effects were restricted to preference-related controls. Contrastively
-accenting scalar \emph{some} generally led to more local readings, but
-that effect was not significant. Local readings occurred in
-\es-sentences, independently of prosody, but required prosodic marking
-in \as-sentences. Our analyses support the impression that inspection
-of the raw data gives, namely that the general qualitative pattern of
-reading preferences is the same for \as- and \es-conditions: literal
-readings are preferred over local readings which are preferred over
-global readings. More concretely, our analyses suggest the following
-preference patterns (bracketed readings are not supported by our data
-and the previous analyses):
+was generally sensitive to prosody. However, our regression analysis
+showed that significant prosodic effects were restricted to
+preference-related controls. Contrastively, the Bayesian analysis
+showed that accenting scalar \emph{some} generally led to more local
+readings, but that effect was not significant. Local readings occurred
+in \es-sentences, independently of prosody, but required prosodic
+marking in \as-sentences. Our analyses support the impression that
+inspection of the raw data gives, namely that the general qualitative
+pattern of reading preferences is the same for \as- and
+\es-conditions: literal readings are preferred over local readings
+which are preferred over global readings. More concretely, our
+analyses suggest the following preference patterns (bracketed readings
+are not supported by our data and the previous analyses):
 
@@
 load negatively affects the number of scalar implicature responses in
-sentence verification tasks. The small number of local readings in
+sentence verification tasks. The finding of local readings in
 \as-sentences with contrastive stress is easily explained by adopting
@@
 these readings. Here, the Magri-style approach could resort to
-considerations of \emph{parsing economy}: reasoning with fever
-alternatives is easier than reasoning with more alternatives. This
-would explain the preference for literal readings and also why local
-readings are more strongly attested for \es-sentences.
+considerations of \emph{economy}: reasoning with fever alternatives is
+easier than reasoning with more alternatives. This would explain the
+preference for literal readings and also why local readings are more
+strongly attested for \es-sentences.
 
@@
 \paragraph{Traditionalism.} Traditionalism, as we described it in
-Section~\ref{sec:theories-predictions}, is also uncomfortable with our
-data. It has to explain the possibility of local readings of
-prosodically unmarked \es-sentences, and, perhaps, also the large
-number of local readings in accented \es-sentences compared to the
-much lower number in accented \as-sentences. To do so within a strict
-traditionalist framework seems difficult. A first option might be to
-account for alleged local readings as the result of some other
-phenomenon, such as typicality or contrast
+Section~\ref{sec:theories-predictions}, can also not account for the
+observed pattern of results. It has to explain the possibility of
+local readings of prosodically unmarked \es-sentences, and, perhaps,
+also the large number of local readings in accented \es-sentences
+compared to the much lower number in accented \as-sentences. To do so
+within a strict traditionalist framework seems difficult. A first
+option might be to account for alleged local readings as the result of
+some other phenomenon, such as typicality or contrast
 \citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter}.
@@
 design and our interpretation of the presented results, which
-essentially all cast into doubt that our data suggests the preference
+essentially cast into doubt that our data suggests the preference
 relation in (\ref{bsp:observed-preferences}). We will consider the
@@
 the incremental verification might altogether be insensitive to scalar
-implicatures. According to the reviewer, it is to be expected that
-since \emph{some} is typically strengthened in non-embedded
-conditions, virtually all of our participants would exit at an early
-position corresponding to the literal reading in a suitable version of
-our \ivt.
+implicatures. According to such a view, it could be that since
+\emph{some} is typically strengthened in non-embedded conditions,
+virtually all of our participants would exit at an early position
+corresponding to the literal reading in a suitable version of our
+\ivt.
 
@@
 
-If we accept that the \ivt is not insensitive to implicature-based
+If we accept that the \ivt is sensitive to implicature-based
 ambiguities, what is left to worry about is that information about
@@
 the post-experiment suggests as well, there is a sequential bias in
-the target conditions to exit early, the main effect of such a bias would
-merely be that we should consider local readings more salient than we
-do now. In the light of the data from main and post-experiments, it
-would be far-fetched to uphold that our data indicates that local
-readings are at least as salient as literal ones. But that means that
-the suggested interpretation in (\ref{bsp:observed-preferences}) still
-holds, and all the problems that we identified for (the considered
-versions of) traditionalism and grammaticalism apply.
+the target conditions to exit early, the main effect of such a bias
+would merely be that we should consider local readings more salient
+than we do now. In the light of the data from main and
+post-experiments, it would be far-fetched to uphold that our data
+indicates that local readings are at least as salient as literal
+ones. But that means that the suggested interpretation in
+(\ref{bsp:observed-preferences}) still holds, and all the problems
+that we identified for (the considered versions of) traditionalism and
+grammaticalism apply.
 
@@
 \es-sentences, the latter does not explain the total absence of global
-responses.
+responses.\todo{skip this paragraph?}
 
@@
 Backed up by our analyses, we concluded that both traditionalism and
-grammaticalism do not predict our under the set of auxiliary
+grammaticalism do not predict our data under the set of auxiliary
 assumptions that we provided them with in

### 2015-02-21 text/paper/revision_01/paper.tex
Petra edits
final edits K2 revision 01 MF

@@
 auditorily and explicitly manipulated contrastive stress on embedded
-scalar items. We employed an \mymark{incremental verification task} in
+scalar items. We employed an \emph{incremental verification task} in
 which parts of a to-be-evaluated picture were hidden and only revealed
@@
 well-known preference on available readings. We argue that this method
-provides categorical behavioral data that is both clearly indicative
-of the reading preferences among participants and largely independent
-of potential pictorial confounds, such as the mentioned typicality
+provides categorical behavioral data that is both indicative of the
+reading preferences among participants and largely independent of
+potential pictorial confounds, such as the mentioned typicality
 effects.
@@
 elaborates on the three kinds of relevant readings for our target
-sentences. Section~\ref{sec:theories-predictions} works out plausible
+sentences. Section~\ref{sec:theories-predictions} works out testable
 \emph{ex ante} predictions of \emph{traditionalism} and
@@
 Section~\ref{sec:discussion-1} for discussion), we used an
-\mymark{incremental verification task} (\acro{ivt}), which is a
+\emph{incremental verification task} (\acro{ivt}), which is a
 modified version of picture verification
@@
 the critical position to reveal a global reading, the latter would be
-indicated by a \emph{false} response. Given the low number of possible
-mistakes resulting from confusion buttons for \emph{true} and
-\emph{false} elsewhere, this seems to be a more systematic pattern. It
-appears as if subjects read \es-sentences as if the non-monotonic
-quantifier \emph{exactly one} was a monotonic \emph{at least one},
-without pragmatic enrichment of \emph{some}. 16 out of the total 21
-answers in this category come from 5 subjects, while the remaining 5
-were single answers by 5 different subjects.
+indicated by a \emph{false} response. Given the low number of mistakes
+attributable to confusion of buttons for \emph{true} and \emph{false}
+elsewhere, this seems to be a more systematic pattern. It appears as
+if subjects read \es-sentences as if the non-monotonic quantifier
+\emph{exactly one} was a monotonic \emph{at least one}, without
+pragmatic enrichment of \emph{some}. 16 out of the total 21 answers in
+this category come from 5 subjects, while the remaining 5 were single
+answers by 5 different subjects.
 % subjects 1, 9, 12, 21, 84
@@
 
-\paragraph{Summary \& Interpretation.} The present study investigated
-prosodic effects on quantifier interpretation by employing a new
-experimental paradigm, the incremental verification task. We were
-specifically interested in whether ``local readings'' of sentences
-where \emph{some} is embedded under another quantifier can be found,
-and how salient these readings are under varying prosody of auditorily
-presented sentence material, in particular the presence or absence of
-contrastive stress on embedded \emph{some}.
-
+\paragraph{Summary \& Interpretation.} % The present study investigated
+% prosodic effects on quantifier interpretation by employing a new
+% experimental paradigm, the incremental verification task. We were
+% specifically interested in whether ``local readings'' of sentences
+% where \emph{some} is embedded under another quantifier can be found,
+% and how salient these readings are under varying prosody of auditorily
+% presented sentence material, in particular the presence or absence of
+% contrastive stress on embedded \emph{some}.
+%
 High scores of success in control conditions show that participants
@@
 does not help, because local readings were observed for accented as
-well as for unaccented \es-sentences. It would also remain unclear why
-prosodic cues should have such differential effects on \as- and
-\es-sentences.
+well as for unaccented \es-sentences.%  It would also remain unclear why
+% prosodic cues should have such differential effects on \as- and
+% \es-sentences.
 
@@
 perhaps along the lines suggested here, but ideally alongside more
-empirical data like the one we presented.
+experimental data.
 
@@
 also the large number of local readings in accented \es-sentences
-compared to the much lower number in accented \as-sentences. To do so
-within a strict traditionalist framework seems difficult. A first
+compared to the much lower number in accented \as-sentences. A first
 option might be to account for alleged local readings as the result of
@@
 
-The foregoing interpretation and discussion presupposed that the
-interpretation of our data, given in Section~\ref{sec:discussion-1},
-was sound. But there are a number of conceivable objections to our
-design and our interpretation of the presented results, which
-essentially cast into doubt that our data suggests the preference
-relation in (\ref{bsp:observed-preferences}). We will consider the
-most pressing ones in the following.
+The foregoing discussion presupposed that the interpretation of our
+data, given in Section~\ref{sec:discussion-1}, was sound. But there
+are a number of conceivable objections that cast into doubt that our
+data suggests the preference relation in
+(\ref{bsp:observed-preferences}). We will consider the most pressing
+ones in the following.
 
@@
 \citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
-if the distribution of responses is indicative of the known preference
+if the distribution of responses is indicative of the true preference
 patterns in preference-related controls, this would not necessarily
@@
 browser-based version, alert boxes pointed out subjects' mistakes when
-they tried to exit to early, chose the wrong response or tried to
+they tried to exit too early, chose the wrong response or tried to
 unravel the sequence further than strictly necessary. The main part of
@@
 early for ``pragmatic ambiguities'' involving implicature
-readings. This might also possibly explain why there are more `error'
-responses on the last position in the preference-related controls. But
-none of this has any serious impact on the suggested preference
-relation in (\ref{bsp:observed-preferences}). For even if, as possibly
-the post-experiment suggests as well, there is a sequential bias in
-the target conditions to exit early, the main effect of such a bias
-would merely be that we should consider local readings more salient
-than we do now. In the light of the data from main and
-post-experiments, it would be far-fetched to uphold that our data
-indicates that local readings are at least as salient as literal
-ones. But that means that the suggested interpretation in
+readings. But none of this has any serious impact on the suggested
+preference relation in (\ref{bsp:observed-preferences}). For even if
+there is a sequential bias in the target conditions to exit early, the
+main effect of such a bias would merely be that we should consider
+local readings more salient than we do now. In the light of the data
+from main and post-experiments, it would be far-fetched to uphold that
+our data indicates that local readings are at least as salient as
+literal ones. But that means that the suggested interpretation in
 (\ref{bsp:observed-preferences}) still holds, and all the problems
@@
 
-To strengthen this case further, let us assume that the \ivt is
-entirely incapable of reliably indicating preferences among candidate
-pragmatic enrichments of the relevant kind. Can we still draw any
-conclusions about mere availability (non-negligible salience) of
-readings? At a minimum, we would like to uphold that local readings
-are available in \es-sentences and that global readings are unattested
-in \as- and \es-sentences. But that alone is not predicted by either
-traditionalism or grammaticalism in the guises that we considered. The
-former cannot explain the substantial number of local responses in
-\es-sentences, the latter does not explain the total absence of global
-responses.\todo{skip this paragraph?}
+% To strengthen this case further, let us assume that the \ivt is
+% entirely incapable of reliably indicating preferences among candidate
+% pragmatic enrichments of the relevant kind. Can we still draw any
+% conclusions about mere availability (non-negligible salience) of
+% readings? At a minimum, we would like to uphold that local readings
+% are available in \es-sentences and that global readings are unattested
+% in \as- and \es-sentences. But that alone is not predicted by either
+% traditionalism or grammaticalism in the guises that we considered. The
+% former cannot explain the substantial number of local responses in
+% \es-sentences, the latter does not explain the total absence of global
+% responses.
 
@@
 more encompassing model along the lines sketched above is that the 3
-\emph{false} answers in the \as-conditions with neutral intonation
+\emph{false} answers in the \as-conditions with neutral prosody
 might support the conclusion that the local reading is attested. But
@@
 has been suggested in other domains as well
-\citep[e.g.][]{DalrympleKanazawa1998:Reciprocal-Expr,CobrerosEgre2012:Tolerant-Classi}.
+\citep[e.g.][]{DalrympleKanazawa1998:Reciprocal-Expr,Winter2001:Plural-Predicat,CobrerosEgre2012:Tolerant-Classi}.
 We tentatively suggested an alternative selection principle for

### 2015-02-22 text/paper/revision_01/paper.tex
K2 revision 01 this version sent

@@
 \citeauthor{ChemlaSingh2014:Remarks-on-the-}): two main ideas behind
-several approaches to quantity implicatures. To determine concrete
-predictions from these, additional ``auxiliary assumptions'' are
-necessary to derive \emph{ex ante} falsifiable predictions about
-to-be-expected observations in a concrete behavioral experiment, even
+several approaches to quantity implicatures. To derive from these core theories
+\emph{ex ante} falsifiable predictions about
+to-be-expected observations in a concrete behavioral experiment,
+additional ``auxiliary assumptions'' are necessary, even
 irrespective of processing accounts. Here, we spell out a set of such
@@
 
-The last kind of disambiguation approach does yield a clear
-restriction of reading preferences for the case at hand. It selects
+The last kind of disambiguation approach does yield clear predictions
+of reading preferences for the case at hand. It selects
 readings by comparison of logical strengths, as suggested by the
@@
 \citet{ChierchiaFox2008:The-Grammatical}, predicts that all candidate
-readings are available and that literal readings are dispreferred in
-all cases. All predictions are summarized in
+readings are available and that literal readings are never preferred. All predictions are summarized in
 Table~\ref{tab:predictions}.
@@
 \citet{GeurtsPouscoulous2009:Embedded-Implic} conducted a
-picture-verification task (their Experiment~3) to find out whether
+picture-verification task experiment (their Experiment~3) to find out whether
 local readings of \as- and \es-sentences are available.\fn{We will
@@
 In a reply to \citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s
-study. \citet{CliftonDube2010:Embedded-Implic} raised the question
+study, \citet{CliftonDube2010:Embedded-Implic} raised the question
 whether the use of a picture-verification paradigm might have been
@@
 we were looking for a way to unambiguously map responses from a
-picture verification task to specific readings. We were particularly
+picture-verification task to specific readings. We were particularly
 interested in the question whether local readings would be observed at
@@
 	}
-	\subfloat[][Step 5 (\lc true)]{
+  	\subfloat[][Step 5]{
 		\fbox{\includegraphics[width=5cm]{pictures/lc_01_5.pdf}}
@@
 	}
-	\subfloat[][Step 7 (\lc true)]{
+	\subfloat[][Step 7]{
 		\fbox{\includegraphics[width=5cm]{pictures/lc_01_7.pdf}}
@@
 the incremental verification might altogether be insensitive to scalar
-implicatures. According to such a view, it could be that since
+implicatures. According to such a view, it could be that, although
 \emph{some} is typically strengthened in non-embedded conditions,
@@
 incremental verification tasks, would be needed. We cannot offer such
-a model here, but can only the offer a first step in that
+a model here, but can only offer a first step in that
 direction. More importantly, though, the only part of
@@
 pragmatic enrichments of two types of sentences, in which scalar
-\emph{some} occurred in the scope of either a monotonic quantifier
+\emph{some} occurred in the scope of either the monotonic quantifier
 \emph{all} or the non-monotonic quantifier \emph{exactly one}. To
@@
 
-We have argued that auditory presentation of sentence material should
-be controlled for if prosodic information is hypothesized to influence
+We have argued that auditory presentation of sentence material is crucial if
+prosodic information is hypothesized to influence
 availability and preferences of readings. We also argued that
@@
 information about actual preference patterns by explicit comparison
-with structures whose preference structures are well-studied, ideally
+with constructions whose preference structures are well-studied, ideally
 with some model of the data generating process for optimal data

### 2015-09-24 text/paper/reviews_2/response_letter.md
response draft

# Response to editor and reviewer comments

The main changes from the previous version are:

1. shortened section 3 to remove unnecessary detail in predictions of "core theories"
2. careful reformulation of conclusions to be drawn from our data in line with reviewer 2's suggestions; concretely:
	a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
	b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsisten with any possible outcome of our experiment; 
	c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.

## Editor comments

> I would like to ask two things of you: 
>
> (1) have a good think about the balanced conclusion you draw (the data are hard for both sides of the theoretical divide --- reviewer 2: the data clearly favours grammaticalism) and address the reviewer's worry as good as you can (s/he can't be the only one interpreting your paper like that);

We agree that our previous version has not been ideally clear on this. It is not our attention to polarize by misleading rhetorics. We have tried to make very clear in the current version that our main conclusions from our data are (as already stated above):

a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsisten with any possible outcome of our experiment; 
c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.

> (2) rethink the value of the fine-grained description of the landscape of theoretical options (section 3.1/3.2).

Although we had thought that it would be good for the readers to see the full space of possible predictions about preference patterns that relevant "core theories" + "auxiliary hypotheses" give, we agree that it is not strictly necessary to introduce all of these distinctions. We have therefore removed those chunks of Section 3 which introduced terms for these distinctions (including Table 2, which summarized the predictions), and have focused the exposition of "core theories" to the bare essentials necessary.

Some particular "auxiliary assumptions" are taken up in the discussion section 6, but only those that are relevant for the overall discussion, like Magri's appeal to obligatory exhaustification, which is an example for how grammaticalism could predict our data.

## Reviewer 1

Reviewer 1 had only minor remarks.

> Perhaps I am persistently misreading something, but on page 4, should it say that the dots on the right of each diagram (of Figure 1) are papers, and the dots on the left represent students?

Yes, this is right: our oversight. We added this to the Figure caption for clarity.

> It would help, in describing Figure 3, to mention that the sentences about them referred to letters and circles.

This was added to the text.

> Page 20, the Clifton et al. 2002 reference isn't really very relevant to the point being made. If the authors want to cite counterevidence, they would do better with Gilboy, E., Sopena, J., Clifton, C. Jr., & Frazier, L. (1995). Argument structure and association preferences in Spanish and English Compound NPs. Cognition, 54(131-167). But it's not necessary. The citation of Konieczny and  Hemforth says what needs to be said.

PETRA?! -> take out reference to Clifton et al?

> Page 41, bottom, the references to Figure 16c doesn't seem to be correct.

Corrected!

## Reviewer 2

Reviewer 2 actually raises many points, not all of which are fully clear to us. We tried our very best to address all of the issues raised (insofar as we understood what was asked of us), but paid particular attention to those issues flagged as most important by the reviewer herself/himself or the editor.

[In the following, we reproduce the full review and use boldface to indicate the aspects that subsequent comments target.]

>The authors have done a good job responding to the first round of feedback. As in the previous round of review, I believe the paper makes a valuable contribution to the literature on scalar strengthening, and that the paper should be published. However, I continue to believe there is room for improvement. Specifically, **I believe the paper can be streamlined by taking fuller advantage of previous results**, which I hope will also clarify the contributions that the paper makes. 
>
>My most important comment, which I'll try to spell out in Section 1 below, is that the question-answer structure of the paper does not come across as cleanly as it should. **To my mind, the paper aims to answer two questions: (i) Are embedded strengthenings licensed only under marked prosody, i.e., is the Prosodic Marking Hypothesis true? (ii) Are there preferences for the different readings predicted by theories of strengthening? If so, what are they, and how are they determined?**

We feel that this description of what the paper is about is unfortunately not entirely correct. This could lead to certain misunderstandings, so we clarify our position here. We have also added to the text (especially the relevant Section 4.4) a few words to strengthen our view of and motivation for what we are doing. (It is our fault, of course, that this has not been sufficiently clear in the previous version.)

One of our main goals in this paper is, indeed, to address the effects of prosody, but with a particular motivation, namely to rule out rule out effects of silent prosody as confounds in the interpretation of earlier data. This is important because all previous results about the availability of local readings and the salience of readings that depend on visual presentation of sentences could, in principle, be subject to doubt if we hypothesize (like many do) that prosody plays a role in this domain. This also includes the results of Chemla & Spector. This is why we want to be more careful in this paper and not take for granted the conclusions of Chemla & Spector contrary to what the reviewer suggests we should do.

Our reluctance to accept Chemla & Spector's conclusions also comes from the recent critique of, in particular, Bart Geurts and Bob van Tiel, who argue that the Chemla & Spector's results could be influenced unduly by pictorial effects. This is the main motivation for our incremental verification task, as argued in Section 4.4 and followed up in the reflection section 6: to minimize potential pictorial effects.

In effect, the main point of our paradigm is that we would not want to take "full advantage of previous results" but (given the published criticism of these) take a careful reassessment and a novel experimental approach.

> I believe the paper answers (i) quite nicely, but it burdens the reader with too much irrelevant information in setting up and addressing the question (much of section 3 of the paper up to but not including section 3.3 on the Prosodic Marking Hypothesis). **Concerning question (ii), the paper leaves it unresolved, which would be fine had the authors not mischaracterized the question by invoking the Strongest Meaning Hypothesis in the way that they did (as I hope to clarify below).** If these issues could be resolved in a revised version, I would have no serious objection to publication.

Unfortunately, we do not understand in what sense the paper leaves question (ii) unresolved, according to the reviewer. To be clear on this, we wanted to get experimental evidence for preferences among putative readings, and we did. We also discuss whether these are predicted by the competing theories. We have adjusted the formulation of these conclusions according to the reviewer's well-taken suggestions in the new version (see below). We never meant to address the question how preferences are determined (and are not clear on what this should mean).

>Section 1: The question-answer structure of the paper
>
>It will help me to discuss the paper's contributions by taking Chemla & Spector (2011, hf. CS) as relevant background, as they also aimed to detect embedded readings in AS and ES sentences and found results that are sometimes supported but sometimes challenged by the present authors. I focus here on ES sentences, in part because AS sentences are not ideal for teasing apart "grammaticalism" from "unrestricted traditionalism", for reasons discussed in CS and elsewhere. My aim here is to identify some of the important empirical results from the current paper, and to relate them to questions (i) and (ii) above:
>
>Empirical Result (1): Like CS, but using a different method, the present authors find that embedded strengthenings are available.
>
>Consequences of (1): This result supports two of CS's claims. First, it provides further evidence for embedded strengthening (and hence, on the face of it, against Traditionalism -- pending further clarification of "typicality"), though of course it leaves open the question in (i) above. Second, **(1) provides further support for CS's claim that the Strongest Meaning Hypothesis is probably *not* the right disambiguation principle (see note 6 of CS, and CS's section 5.5.2)**.

We are very grateful for drawing our attention to the fact that we should mention that Chemla & Spector have already discussed their data as countering the Strongest Meaning Hypothesis. Our position to this is that, yes, we provide further evidence, but also further evidence that is relevant, given the doubts that were brought forth against Chemla & Spector's design and interpretation.

> Empirical Result (2): The present authors find that embedded strengthenings are available independent of prosodic marking. **This result is totally new, and is made possible by their new method (their Incremental Verification Task).**

There must be some misunderstanding here (see also above): the incremental verification task is motivated by worries about potential pictorial effects. This is orthogonal to the issue of "silent prosody".

> Consequences of (2): This result argues against the Prosodic Marking Hypothesis (cf. question (i) above).
> 
> (3) Empirical Result (3): The present authors find that the literal reading is preferred to the local reading, which is in stark opposition with what CS found. 
>
>Consequences of (3): Given the discussion in (1) above, an obvious challenge is to explain what might have led to different preferences in CS's sample and the one in the present paper (cf. question (ii) above).
>
> If my reading of the paper is correct, then several changes to the paper are in order. 
>
>   - First, I believe **much of the discussion in section 3 concerning auxiliary assumptions should be shortened or even deleted entirely.** To begin with, much of the discussion about Traditionalism seems irrelevant to me. The really important assumption here is the Prosodic Marking Hypothesis, which can be simply stated without bothering with the distinction between weak/strong and restricted/unrestricted traditionalism. In fact, so far as I can tell, nothing that the authors say later in the paper bears on these differences, in part because traditionalism qua core theory is inconsistent with the authors' results. Turning to grammaticalism, in light of the fact that **the Strongest Meaning Hypothesis was already argued in CS to be inoperative (or at least, not dominant) in ES sentences, the authors' decision to take that as the most promising example of a disambiguation criterion seems unjustified.** In sum, the authors introduce many discourse referents in section 3 corresponding to possible combinations of core theory + auxiliary assumptions (all the variants of traditionalism and the conjunction of grammaticalism and the SMH), and at the end of the paper we are reminded that CS already gave us reason to reject them all. This is not very cooperative.   
>   **My concrete suggestion is to considerably shorten Section 3 by not getting into all the choice points concerning Traditionalism (weak/strong, restricted/unrestricted) or Grammaticalism (Magri/QUD/SMH). All of these are irrelevant to the Prosodic Marking Hypothesis, and in any event nothing new is discovered by paper's end about the right auxiliary assumptions**, other than that the answer is unlikely to be straightforward (cf. the conflict with CS's results alluded to above).

We have taken up the suggestion to shorten Section 3 in the way that the reviewer describes.

On the other hand, for the very reasons described above, we are reluctant to accept the results and conclusions of Chemla & Spector as given. Since our design was motivated by catering to the very problems raised for Chemla & Spector, we do believe that our data gives new and interesting information about preference of readings. This is also because, as we argue in Section 4.4, we explicitly compare data from embedded scalars with other ambiguous constructions in the very same experiment (same method, same subject pool).

### 2015-09-25 text/paper/reviews_2/response_letter.md
response letter draft

@@
 
-1. shortened section 3 to remove unnecessary detail in predictions of "core theories"
-2. careful reformulation of conclusions to be drawn from our data in line with reviewer 2's suggestions; concretely:
+1. careful reformulation of conclusions to be drawn from our data in line with reviewer 2's suggestions; concretely:
 	a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
-	b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsisten with any possible outcome of our experiment; 
+	b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment; 
 	c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.
+2. shortening of section 3 to remove unnecessary detail in predictions of "core theories"
+3.
+addition of a few elements of emphasis in introduction, Section 4 and reflection section 6, in response to reviewer 2's comments, which made clear that the previous version may not have made the motivation of our design sufficiently clear
 
@@
 We agree that our previous version has not been ideally clear on this.
-It is not our attention to polarize by misleading rhetorics.
+It is not our intention to polarize by misleading rhetorics.
 We have tried to make very clear in the current version that our main conclusions from our data are (as already stated above):
@@
 a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
-b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsisten with any possible outcome of our experiment; 
+b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment; 
 c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.
@@
 Although we had thought that it would be good for the readers to see the full space of possible predictions about preference patterns that relevant "core theories" + "auxiliary hypotheses" give, we agree that it is not strictly necessary to introduce all of these distinctions.
-We have therefore removed those chunks of Section 3 which introduced terms for these distinctions (including Table 2, which summarized the predictions), and have focused the exposition of "core theories" to the bare essentials necessary.
-
+We have therefore removed those chunks of Section 3 which are not strictly relevant for late discussions (including Table 2, which summarized the predictions).
 Some particular "auxiliary assumptions" are taken up in the discussion section 6, but only those that are relevant for the overall discussion, like Magri's appeal to obligatory exhaustification, which is an example for how grammaticalism could predict our data.
@@
 If so, what are they, and how are they determined?**
+>
+> I believe the paper answers (i) quite nicely, but it burdens the reader with too much irrelevant information in setting up and addressing the question (much of section 3 of the paper up to but not including section 3.3 on the Prosodic Marking Hypothesis).
+Concerning question (ii), the paper leaves it unresolved, which would be fine had the authors not mischaracterized the question by invoking the Strongest Meaning Hypothesis in the way that they did (as I hope to clarify below).
+If these issues could be resolved in a revised version, I would have no serious objection to publication.
 
@@
 This could lead to certain misunderstandings, so we clarify our position here.
-We have also added to the text (especially the relevant Section 4.4) a few words to strengthen our view of and motivation for what we are doing.
+We have also added to the text (introduction, especially the relevant Section 4.4, section 6) to strengthen our view of and motivation for what we are doing.
 (It is our fault, of course, that this has not been sufficiently clear in the previous version.)
 
-One of our main goals in this paper is, indeed, to address the effects of prosody, but with a particular motivation, namely to rule out rule out effects of silent prosody as confounds in the interpretation of earlier data.
-This is important because all previous results about the availability of local readings and the salience of readings that depend on visual presentation of sentences could, in principle, be subject to doubt if we hypothesize (like many do) that prosody plays a role in this domain.
+One of our main goals in this paper is, indeed, to address the effects of prosody, but with a particular motivation, namely to rule out effects of "silent prosody" as confounds in the interpretation of earlier data.
+This is important because all previous experimental results that depend on visual presentation of sentences could, in principle, be subject to doubt if we hypothesize (like many do) that prosody plays a role in this domain.
 This also includes the results of Chemla & Spector.
@@
 
-Our reluctance to accept Chemla & Spector's conclusions also comes from the recent critique of, in particular, Bart Geurts and Bob van Tiel, who argue that the Chemla & Spector's results could be influenced unduly by pictorial effects.
-This is the main motivation for our incremental verification task, as argued in Section 4.4 and followed up in the reflection section 6: to minimize potential pictorial effects.
+Our reluctance to accept Chemla & Spector's conclusions also comes from the recent critique of, in particular, Bart Geurts and Bob van Tiel, who argue that Chemla & Spector's results could be influenced unduly by pictorial effects.
+This is the main motivation for our incremental verification task, as argued in Section 4.4 and followed up in the reflection section 6.
 
 In effect, the main point of our paradigm is that we would not want to take "full advantage of previous results" but (given the published criticism of these) take a careful reassessment and a novel experimental approach.
+We hope that by adding few strategically placed elements of emphasis and explanation (introduction, sections 4 & 6) this will become more transparent.
 
-> I believe the paper answers (i) quite nicely, but it burdens the reader with too much irrelevant information in setting up and addressing the question (much of section 3 of the paper up to but not including section 3.3 on the Prosodic Marking Hypothesis).
-**Concerning question (ii), the paper leaves it unresolved, which would be fine had the authors not mischaracterized the question by invoking the Strongest Meaning Hypothesis in the way that they did (as I hope to clarify below).** If these issues could be resolved in a revised version, I would have no serious objection to publication.
-
-Unfortunately, we do not understand in what sense the paper leaves question (ii) unresolved, according to the reviewer.
+<!---Unfortunately, we do not understand in what sense the paper leaves question (ii) unresolved, according to the reviewer.
 To be clear on this, we wanted to get experimental evidence for preferences among putative readings, and we did.
@@
 We have adjusted the formulation of these conclusions according to the reviewer's well-taken suggestions in the new version (see below).
-We never meant to address the question how preferences are determined (and are not clear on what this should mean).
+We never meant to address the question how preferences are determined (and are not clear on what this should mean).-->
 
+>
+>
 >Section 1: The question-answer structure of the paper
@@
 We are very grateful for drawing our attention to the fact that we should mention that Chemla & Spector have already discussed their data as countering the Strongest Meaning Hypothesis.
-Our position to this is that, yes, we provide further evidence, but also further evidence that is relevant, given the doubts that were brought forth against Chemla & Spector's design and interpretation.
+Our position to this is that, yes, we provide further evidence, but also further evidence that is relevant, given the doubts that were brought forth against Chemla & Spector's design and interpretation and the additional doubts that arise from issues with "silent prosody".
+
+<!--There must be some misunderstanding here (see also above): the incremental verification task is motivated by worries about potential pictorial effects.
+This is orthogonal to the issue of "silent prosody".-->
 
 > Empirical Result (2): The present authors find that embedded strengthenings are available independent of prosodic marking.
-**This result is totally new, and is made possible by their new method (their Incremental Verification Task).**
-
-There must be some misunderstanding here (see also above): the incremental verification task is motivated by worries about potential pictorial effects.
-This is orthogonal to the issue of "silent prosody".
-
+This result is totally new, and is made possible by their new method (their Incremental Verification Task).
+>
 > Consequences of (2): This result argues against the Prosodic Marking Hypothesis (cf. question (i) above).
@@
 This is also because, as we argue in Section 4.4, we explicitly compare data from embedded scalars with other ambiguous constructions in the very same experiment (same method, same subject pool).
+
+> - Second, the authors' abstract and the discussion in the paper make it clear that there are challenges for both traditionalism and grammaticalism.
+This is very important, but **the authors' discussion makes it seem as though the challenges for the two approaches are more on a par than they actually are.
+Traditionalism (as a core theory) is inconsistent with the authors' data, and grammaticalism (as a core theory) is consistent with their data**.
+Of course, grammaticalism is still in need of auxiliary assumptions to account for the data about preferences, but this should occasion no surprise.
+For example, last I checked the psycholinguistics community was still trying to figure out, say, how PP-attachment ambiguities are resolved; just because we don't know how, this does not lead anyone to suggest that syntactic theories that generate PP-attachment ambiguities are in need of "refinement", does it?
+>   My concrete suggestion is to **rephrase the abstract and other relevant passages in the paper so that it does not misleadingly suggest that grammaticalism qua core theory faces any particular difficulty with the authors' results**; what is missing here is a theory of preference, but this is needed for any theoretical approach to strengthening.
+For note that the discrepancy between CS's findings and the present authors' findings concerning preferences need to be accounted for one way or another; since this is a problem for everyone, I don't think it is fair to single out grammaticalism as being in need of refinement, at least not until it is shown that some other approach predicts the discrepancy between CS and the present authors' data on preferences.
+
+We agree that our previous version did not make this clear enough. We reformulated relevant locations to make clear what our position is, namely (same as above):
+
+	a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
+	b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment; 
+	c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.
+
+> Section 2: Minor comments/thoughts (feel free to ignore)
+>
+> A: "Exactly one" as monotonic: **The authors suggest, based on the "true" responses at Step 2, that some of their participants might have re-interpreted "exactly one" as "at least one." I'm wondering if there is a less radical way to make sense of their participants' behaviour: for what it's worth, my intuition is that there might be domain-restriction effects here.** There is exactly one uncovered bell at Step 2; thus, the sentence is literally true under a reading in which the domain of the quantifier is restricted to this one individual.
+I'm not exactly sure how to dissociate this suggestion from the authors', and I of course wouldn't insist that the authors do this.
+I raise the idea here simply for their consideration.
+With this in mind, in future work perhaps the authors might consider examining what would happen if Step 1 were followed instead by what is currently Step 3.
+The domain-restriction proposal would predict less "true" responses here because now there are two bells that are salient in the domain, but an "at least one" reading would still easily permit a "true" response here.
+(Note that getting rid of the current Step 2 is largely harmless, since global readings were basically absent in this paradigm.)
+
+This is a good and interesting suggestion. We cannot follow up on this in the paper, but acknowledge the point in a footnote.
+
+> B: The Strongest Meaning Hypothesis, Again: **As I noted earlier, it does not seem appropriate to assume the SMH for this paradigm in light of CS's results and discussion.** However, I should like to add that one has to be careful about what the SMH actually states when we consider exhaustification, and here perhaps CS themselves could have been more careful.
+When we compare the strength of various sentences that differ in the placement of EXH, we have to be careful about what the alternatives to EXH are.
+So far as I can tell, the SMH may well still be in the running as a disambiguation criterion, if only we could be sure what the alternatives are in any given experimental setup.
+Since we don't know this, we can't really be sure whether the SMH has been properly tested.
+
+As mentioned above, we are grateful for reminding us to take into consideration Chemla & Spector's discussion of the SMH in this case.
+Their footnote 6 makes a similar point to the reviewer's.
+We acknowledge that Chemla & Spector believe that logical strength may still play a role despite their findings and that this may also extend to our findings in the reflection section 6.
+However, like Chemla & Spector and the reviewer, we have no strong vision of how this idea could be realized and so must leave it for future work.
+
+> Having said this, **it's still not clear to me that there is any motivation to appeal to the SMH the way the authors do.** Putting aside the issues raised earlier, it is important to note that **the works that the authors cite were all very careful to limit the immediate applicability of the SMH to either reciprocals (Dalrymple et al.) or to plural predication more generally (Winter).
+One is of course welcome to try extending its applicability, but my reading of the literature is that the SMH was not intended as a general disambiguation principle** (lest it run into well-known issues in other areas, e.g., preferences in scope-ambiguities).
+
+It seems that we have reach rock bottom here, where the reviewer's view differs irresolvably from ours.
+We consider Chierchia, Fox and Spector (2012) "The Grammatical View of Scalar Implicatures and the Relationship between Semantics and Pragmatics" a great and inspiring paper by great and inspiring minds.
+This paper suggests to use the SMH for disambiguating parses.
+Taking great and inspiring papers and minds seriously, we therefore do not think that it is whimsical to pay attention to the SMH, especially, as we stress, our emphasis on it is because it is the only fully spelled out proposal for enriching grammaticalism that applies to our abstract experimental setting.
+
+> C: "Ex ante" predictions: **The authors in many places write that certain proposals are not formulated as "ex ante" predictions.
+But the predictions of all the theories the authors discuss are all fully predictive: given a sentence and a context, just about every theory of strengthening I know clearly predicts how a scalar sentence will be interpreted.** Of course, in experimental settings many relevant features of the context are left open, and hence participants have to guess what context they're in (see e.g., Crain & Steedman, 1985).
+This is certainly the case for the author's experiment, in which many of the contextual features that are important for strengthening are unspecified (e.g., relevance, assumptions about the speaker's mental state, etc).
+But this is a general feature of psycholinguistic studies, is it not?
+If you leave open crucial contextual features, participants have to guess those values.
+Does this make the theories any less predictive?
+Is the difficulty in pinning down a context a difficulty for the theory or for the experimenter?
+
+We are grateful for this comment, because it shows that we have been insufficiently clear on our intended meaning of *ex ante* predictions.
+We have clarified this in footnote XXX.
+We are interested in *ex ante* predictions FOR OUR EXPERIMENT, not general predictions *given a set of contextual parameters*.

### 2015-09-25 text/paper/reviews_2/response_letter.md
response to reviewers and email to Rick drafts

@@
 3.
-addition of a few elements of emphasis in introduction, Section 4 and reflection section 6, in response to reviewer 2's comments, which made clear that the previous version may not have made the motivation of our design sufficiently clear
+addition of a few elements of emphasis in introduction, Section 4 and reflection section 6, in response to reviewer 2's comments showing that the previous version may not have made the motivation of our design sufficiently clear
 
@@
 
-> I would like to ask two things of you: 
+>I would like to ask two things of you: 
 >
-> (1) have a good think about the balanced conclusion you draw (the data are hard for both sides of the theoretical divide --- reviewer 2: the data clearly favours grammaticalism) and address the reviewer's worry as good as you can (s/he can't be the only one interpreting your paper like that);
+>(1) have a good think about the balanced conclusion you draw (the data are hard for both sides of the theoretical divide --- reviewer 2: the data clearly favours grammaticalism) and address the reviewer's worry as good as you can (s/he can't be the only one interpreting your paper like that);
 
@@
 
-> (2) rethink the value of the fine-grained description of the landscape of theoretical options (section 3.1/3.2).
+>(2) rethink the value of the fine-grained description of the landscape of theoretical options (section 3.1/3.2).
 
@@
 
-> It would help, in describing Figure 3, to mention that the sentences about them referred to letters and circles.
+>It would help, in describing Figure 3, to mention that the sentences about them referred to letters and circles.
 
@@
 >
-> I believe the paper answers (i) quite nicely, but it burdens the reader with too much irrelevant information in setting up and addressing the question (much of section 3 of the paper up to but not including section 3.3 on the Prosodic Marking Hypothesis).
+>I believe the paper answers (i) quite nicely, but it burdens the reader with too much irrelevant information in setting up and addressing the question (much of section 3 of the paper up to but not including section 3.3 on the Prosodic Marking Hypothesis).
 Concerning question (ii), the paper leaves it unresolved, which would be fine had the authors not mischaracterized the question by invoking the Strongest Meaning Hypothesis in the way that they did (as I hope to clarify below).
@@
 
->
->
 >Section 1: The question-answer structure of the paper
@@
 First, it provides further evidence for embedded strengthening (and hence, on the face of it, against Traditionalism -- pending further clarification of "typicality"), though of course it leaves open the question in (i) above.
-Second, **(1) provides further support for CS's claim that the Strongest Meaning Hypothesis is probably *not* the right disambiguation principle (see note 6 of CS, and CS's section 5.5.2)**.
+Second, ** (1) provides further support for CS's claim that the Strongest Meaning Hypothesis is probably *not* the right disambiguation principle (see note 6 of CS, and CS's section 5.5.2)**.
 
@@
 
-> Empirical Result (2): The present authors find that embedded strengthenings are available independent of prosodic marking.
+>Empirical Result (2): The present authors find that embedded strengthenings are available independent of prosodic marking.
 This result is totally new, and is made possible by their new method (their Incremental Verification Task).
 >
-> Consequences of (2): This result argues against the Prosodic Marking Hypothesis (cf. question (i) above).
+>Consequences of (2): This result argues against the Prosodic Marking Hypothesis (cf. question (i) above).
 >
-> (3) Empirical Result (3): The present authors find that the literal reading is preferred to the local reading, which is in stark opposition with what CS found. 
+>(3) Empirical Result (3): The present authors find that the literal reading is preferred to the local reading, which is in stark opposition with what CS found. 
 >
@@
 >
-> If my reading of the paper is correct, then several changes to the paper are in order. 
+>If my reading of the paper is correct, then several changes to the paper are in order. 
 >
@@
 We acknowledge that Chemla & Spector believe that logical strength may still play a role despite their findings and that this may also extend to our findings in the reflection section 6.
-However, like Chemla & Spector and the reviewer, we have no strong vision of how this idea could be realized and so must leave it for future work.
+But we have no strong vision of how this idea could be realized and so must leave it for future work without too much speculation from our side here.
 
@@
 This paper suggests to use the SMH for disambiguating parses.
-Taking great and inspiring papers and minds seriously, we therefore do not think that it is whimsical to pay attention to the SMH, especially, as we stress, our emphasis on it is because it is the only fully spelled out proposal for enriching grammaticalism that applies to our abstract experimental setting.
+Taking great and inspiring papers and minds seriously, we therefore think that it is appropriate to pay attention to the SMH, especially, as we stress, our emphasis on it is because it is the only fully spelled out proposal for enriching grammaticalism that applies to our abstract experimental setting.
+(This also relates to the following point about *ex ante* predictions; we take full blame for misunderstandings due to lack of careful enough explanation of what we mean by this term.)
 
@@
 We have clarified this in footnote XXX.
-We are interested in *ex ante* predictions FOR OUR EXPERIMENT, not general predictions *given a set of contextual parameters*.
+We are interested in *ex ante* predictions *for our experiment*, not general predictions *given a set of contextual parameters*.
+We fully agree with the reviewer that abstract experimental setting underspeficy relevant contextual parameters.
+We also therefore agree that our data does not speak against grammaticalism as a "core theory".
+We hope to have amended all relevant formulations in line with the reviewer's comments, so as not to give rise to misleading readings of our intended interpretation of our results.

### 2015-09-28 text/paper/reviews_2/response_letter.md
Editor letter final

@@
 
-PETRA?! -> take out reference to Clifton et al?
+References updated accordingly.
 
@@
 It seems that we have reach rock bottom here, where the reviewer's view differs irresolvably from ours.
-We consider Chierchia, Fox and Spector (2012) "The Grammatical View of Scalar Implicatures and the Relationship between Semantics and Pragmatics" a great and inspiring paper by great and inspiring minds.
-This paper suggests to use the SMH for disambiguating parses.
-Taking great and inspiring papers and minds seriously, we therefore think that it is appropriate to pay attention to the SMH, especially, as we stress, our emphasis on it is because it is the only fully spelled out proposal for enriching grammaticalism that applies to our abstract experimental setting.
+Chierchia, Fox and Spector (2012, "The Grammatical View of Scalar Implicatures and the Relationship between Semantics and Pragmatics") suggest to use the SMH for disambiguating parses.
+We therefore think that it is appropriate to pay attention to the SMH, especially, as we stress, our emphasis on it is because it is the only fully spelled out proposal for enriching grammaticalism that applies to our abstract experimental setting.
 (This also relates to the following point about *ex ante* predictions; we take full blame for misunderstandings due to lack of careful enough explanation of what we mean by this term.)

### 2015-10-16 text/paper/revision_02/paper.tex
revised up to sec 3.3

--- 2015-02-22 text/paper/revision_01/paper.tex
@@
   % freely.
-  We present new experimental data that bear on this theoretical
-  issue. In distinction to previous experimental approaches, we
-  presented sentence material auditorily in order to explicitly
-  control prosodic markedness of the scalar item. Moreover, our
-  experiment sheds light on the relative preferences or salience of
-  candidate readings. The presented data turn out to be unexpected
-  under a traditional Gricean view, but also suggest refinement of the
-  more recent grammatical approach.
+  We present new experimental data that bear on this theoretical issue. In distinction to
+  previous experimental approaches, we presented sentence material auditorily in order to
+  explicitly control prosodic markedness of the scalar item. Moreover, our experiment sheds
+  light on the relative preferences or salience of candidate readings. The presented data turn
+  out to be unexpected under a traditional Gricean view, but also challenge the idea that of
+  disambiguation by logical strength in grammaticalist approaches.
 \end{abstract}
@@
 
-To deal with these methodological problems, this paper presents
-results from an experimental study which presented sentence materials
-auditorily and explicitly manipulated contrastive stress on embedded
-scalar items. We employed an \emph{incremental verification task} in
-which parts of a to-be-evaluated picture were hidden and only revealed
-piece-wise at the participants’ request until they felt able to give a
-binary truth-value judgement \citep[see][]{Conroy2008}. We use both a
-classical regression analysis and a Bayesian statistical model to
-analyze the data from this novel task, and validate this method by
-including control conditions testing ambiguous sentences with a
-well-known preference on available readings. We argue that this method
-provides categorical behavioral data that is both indicative of the
-reading preferences among participants and largely independent of
-potential pictorial confounds, such as the mentioned typicality
-effects.
+To deal with the problem of ``silent intonation,'' this paper presents results from an
+experimental study which presented sentence materials auditorily and explicitly manipulated
+contrastive stress on embedded scalar items. To address worries about pictorial ``typicality
+effects,'' we employed an \emph{incremental verification task} in which parts of a
+to-be-evaluated picture were hidden and only revealed piece-wise at the participants’ request
+until they felt able to give a binary truth-value judgement \citep[see][]{Conroy2008}. In order
+to obtain information about salience of readings, we use both a classical regression analysis
+and a Bayesian statistical model to analyze the data from this novel task, and validate this
+method by including control conditions testing ambiguous sentences with a well-known preference
+on available readings. % We argue that this method provides categorical behavioral data that is
+% both indicative of the reading preferences among participants and largely independent of
+% potential pictorial confounds, such as the mentioned typicality effects.
 
@@
 
-\caption{Examples of distinguishing situations for \as-sentences}
+\caption{Examples of distinguishing situations for \as-sentences. The dots on the left
+  represent students, the dots on the right papers. An arrow from left to right represents that
+  a student has read a paper.}
   \label{fig:AS-distinguishing-pics}
@@
 
-There are two main theoretical positions which appear to make
-different predictions about the readings of \as- and \es-sentences
-\citep[see][for
+There are two main theoretical positions which appear to make different predictions about the
+readings of \as- and \es-sentences \citep[see][for
 overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation,ChemlaSingh2014:Remarks-on-the-}. We
-will refer to these as \emph{traditionalism} and \emph{grammaticalism}
-and treat each in turn. Both approaches are addressed here as ``core
-theories'' (terminology from
-\citeauthor{ChemlaSingh2014:Remarks-on-the-}): two main ideas behind
-several approaches to quantity implicatures. To derive from these core theories
-\emph{ex ante} falsifiable predictions about
-to-be-expected observations in a concrete behavioral experiment,
-additional ``auxiliary assumptions'' are necessary, even
-irrespective of processing accounts. Here, we spell out a set of such
-auxiliary assumptions for each core theory. Our motivation for the
-particular choices we make is partly guided by practical concerns, so
-as to have a concrete set of predictions for each core theory to
-formulate expectations and compare our data to. We therefore introduce
-certain relevant variants of either core theory, the predictions of
-which are summarized in Table~\ref{tab:predictions} on
-page~\pageref{tab:predictions}. How other potential instantiations of
-either core theory fare in light of our data will be discussed in
-Section~\ref{sec:critical-reflection}.
+will refer to these as \emph{traditionalism} and \emph{grammaticalism} and treat each in
+turn. Both approaches are addressed here as ``core theories'' (terminology from
+\citeauthor{ChemlaSingh2014:Remarks-on-the-}): two main ideas behind several approaches to
+quantity implicatures. While traditionalism qua ``core theory'' makes some non-trivial
+predictions about salience of readings of \as- and \es-sentences, grammaticalism does not. To
+derive from grammaticalism a set of falsifiable predictions about outcomes of a concrete
+behavioral experiment like ours \emph{ex ante}, i.e., before having seen any data from that
+particular experiment, additional ``auxiliary assumptions'' are necessary. Here, we focus on
+one such ``auxiliary assumption,'' for reasons to be spelled out
+below. Section~\ref{sec:critical-reflection} will revisit grammaticalism as a ``core theory''
+\emph{ex post}, i.e., in the light of our data.
 
@@
 
-Traditionalism's predictions about availability and relative salience
-of readings of \as- and \es-sentences depend on further auxiliary
-assumptions. To have handy labels, we distinguish between strong and
-weak, and between restricted and unrestricted variants.
-
-Strong and weak traditionalism differ with respect to whether the
-assumptions needed to derive (non-epistemic) implicatures are
-plausibly warranted in the given context of utterance (or some
-experiment or other). These assumptions include relevance of the
-information in question, mutual awareness that the stronger
-alternative has been a speaker option, the speaker's competence about
-the issue, etc. \emph{Strong traditionalism} assumes that the
-additional assumptions needed to derive (non-epistemic) implicatures
-are sufficiently salient to prefer an implicature reading over a
-literal reading; \emph{weak traditionalism} assumes the reverse
-preference order. In other words, in the context of a given
-experiment, it is compatible with a traditionalist position to expect
-literal or implicature readings to be more prominent. Or, put yet
-differently, a traditionalist could be uncertain as to whether a given
-experiment is more likely to trigger more implicature readings or
-literal readings. Without more information about the experiment or
-context of interpretation, traditionalism is compatible with either
-salience ordering.
-
-Orthogonal to this, we distinguish restricted and unrestricted
-variants of traditionalism. For our purposes, restricted
-traditionalism considers only alternative expressions that are
-stronger than the to-be-interpreted utterance. Unrestricted
-traditionalism also allows alternatives that are derived from
-replacing \emph{some} with \emph{all} and vice versa, if necessary
-multiple times, even if the resulting alternative is not logically
-stronger. Restricted traditionalism considers only \as-sentences to
-have a relevant alternative, namely (\ref{bsp:AE-Alternative}). It
-then predicts the availability of a global reading for \as-sentences
-on top of the literal. Restricted traditionalism predicts only literal
-readings of \es-sentences, because the alternative
-(\ref{bsp:GE-Alternative}) does not entail the literal reading of
-(\ref{bsp:GE}). Every implicature reading available to restricted
-traditionalism is also available to unrestricted traditionalism, but
-the latter's predictions are even richer. For \as-sentences, the
-potential alternative (\ref{bsp:AE-Alternatives-Extended}) also makes
-local readings available
-\citep[e.g.][]{Sauerland2004:Scalar-Implicat}: conjoining a literal
-reading of (\ref{bsp:AE}) with the negation of
-(\ref{bsp:AE-Alternatives-Extended}) gives a local reading.
+Traditionalism's predictions about general availability of reading depend on which alternative
+utterances we consider. For \as-sentences, traditionalism can derive the global reading by
+assuming (uncontroversially) that (\ref{bsp:AE-Alternative}) is an alternative. It can derive
+the local reading by assuming (more controversially) that (\ref{bsp:AE-Alternatives-Extended})
+is a relevant alternative \citep[e.g.][]{Sauerland2004:Scalar-Implicat}.\footnote{It is more
+  controversial that (\ref{bsp:AE-Alternatives-Extended}) is an alternative to (\ref{bsp:AE}),
+  because the former does not entail the latter.}
 
@@
 
-\noindent For \es-sentences, we derive a global reading via the
-negation of alternative (\ref{bsp:GE-Alternative}), but not local
-readings.
-
-In sum, a traditionalist core theory is compatible with a range of
-observations about the availability and relative salience of
-implicature readings. These are summarized in
-Table~\ref{tab:predictions}. Most importantly for the subsequent
-discussion, traditionalism does not predict local readings for
-\es-sentences and can favor implicature readings over literal ones or
-vice versa.
+\noindent For \es-sentences, traditionalism can derive the global reading if we assume
+(controversially) that (\ref{bsp:GE-Alternative}) is a relevant alternative. Since local
+readings are logically independent of literal readings, there is no way that traditionalism can
+derive them from the Gricean recipe, no matter what alternatives we consider.
+
+Traditionalism's predictions about preferences among available readings depend whether the
+speaker is (most likely) knowledgeable in the relevant sense. We predict a strong non-epistemic
+implicature that a given alternative is false if the speaker is assumed to be competent;
+otherwise the preferred reading would be a literal reading or a weak epistemic implicature
+(that the speaker does not know whether the alternative is true). In the context of a given
+abstract experiment that does not manipulate speaker expertise (like ours), it is then
+\emph{prima facie} compatible with a traditionalist position to expect literal or implicature
+readings to be more prominent.
+
+In sum, a traditionalist core theory is compatible with a range of observations about the
+availability and relative salience of implicature readings. Most importantly for the subsequent
+discussion, traditionalism does not predict local readings for \es-sentences and can favor
+implicature readings over literal ones or vice versa.
 
@@
 % discussion]{FoxSpector:Economy-and-Emb}.
-Three kinds of approaches have been suggested in the literature
-\citep[c.f.][]{ChemlaSingh2014:Remarks-on-the-}. We briefly touch upon
-each, but focus on the one that is least controversially applicable to
-our experimental case, and that has theoretical significance beyond
-the debate about embedded implicatures.
-
-To start with,
-\citet{Magri2009:A-Theory-of-Ind,Magri2011:Another-Argumen} opts for
-obligatory presence of $\exh(\cdot)$ with variability in the set of
-alternatives to feed into each $\exh(\cdot)$. Under this approach,
-alternatives may be pruned entirely, so that all occurrences of
-$\exh(\cdot)$ become vacuous, resulting in a literal reading. Whether
-alternatives apply or not is a matter of their relevance. It is not
-clear what his approach predicts \emph{ex ante} about the relative
-salience of candidate readings in a neutral experiment that does not
-explicitly provide information about which alternatives are relevant
-(for whatever purpose). However, we will show in
-Section~\ref{sec:critical-reflection} that Magri's approach can be
-brought to accommodate the data very well after the fact.
-
-Other proponents of grammaticalism assume that insertion of $\exh(\cdot)$ is
-optional. Under one proposal for disambiguation, readings are the more
-preferred the better they answer the contextually given question under
-discussion (QUD)
-\citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. This
-is a plausible suggestion, but does not give clear predictions for a
-case like our experiment without fixed QUD. Subjects could in
-principle accommodate any QUD, so that this approach would not
-restrict the space of reading preferences either.
-
-The last kind of disambiguation approach does yield clear predictions
-of reading preferences for the case at hand. It selects
-readings by comparison of logical strengths, as suggested by the
-\emph{strongest meaning hypothesis} of
-\citet{DalrympleKanazawa1998:Reciprocal-Expr}. Supplementing
-grammaticalism with a strength-based selection criterion has been
-suggested, in one form or another, in many contributions to this
-paradigm
+Several approaches have been suggested in the literature
+\citep[c.f.][]{ChemlaSingh2014:Remarks-on-the-}. We focus here on the one that is least
+controversially applicable to our experimental case, and that has theoretical significance
+beyond the debate about embedded implicatures: disambiguation by comparison of logical
+strengths, as suggested by the \emph{strongest meaning hypothesis} of
+\citet{DalrympleKanazawa1998:Reciprocal-Expr}.\footnote{We will come back to other
+  implementations of grammaticalism in Section~\ref{sec:critical-reflection}.}
+
+% To start with,
+% \citet{Magri2009:A-Theory-of-Ind,Magri2011:Another-Argumen} opts for
+% obligatory presence of $\exh(\cdot)$ with variability in the set of
+% alternatives to feed into each $\exh(\cdot)$. Under this approach,
+% alternatives may be pruned entirely, so that all occurrences of
+% $\exh(\cdot)$ become vacuous, resulting in a literal reading. Whether
+% alternatives apply or not is a matter of their relevance. It is not
+% clear what his approach predicts \emph{ex ante} about the relative
+% salience of candidate readings in a neutral experiment that does not
+% explicitly provide information about which alternatives are relevant
+% (for whatever purpose). However, we will show in
+% Section~\ref{sec:critical-reflection} that Magri's approach can be
+% brought to accommodate the data very well after the fact.
+
+% Other proponents of grammaticalism assume that insertion of $\exh(\cdot)$ is
+% optional. Under one proposal for disambiguation, readings are the more
+% preferred the better they answer the contextually given question under
+% discussion (QUD)
+% \citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. This
+% is a plausible suggestion, but does not give clear predictions for a
+% case like our experiment without fixed QUD. Subjects could in
+% principle accommodate any QUD, so that this approach would not
+% restrict the space of reading preferences either.
+
+Supplementing grammaticalism with a strength-based selection criterion has been suggested, in
+one form or another, in many contributions to this paradigm
 \citep[e.g.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. At
-the same time, the strongest meaning hypothesis has been frequently
-called upon for disambiguation purposes in other domains as well,
-including reciprocals \citep{DalrympleKanazawa1998:Reciprocal-Expr},
-plural predication \citep{Winter2001:Plural-Predicat} or vagueness
-\citep{CobrerosEgre2012:Tolerant-Classi}. For these reasons, we focus
-from now on this latter type of selection
-principle. Section~\ref{sec:critical-reflection} reconsiders
-alternative selection principles.
-
-\citet{ChierchiaFox2008:The-Grammatical} discuss two concrete variants
-of strength-based disambiguation that make non-trivial predictions
-about preferred readings of \as- and \es-sentences (unlike, say, the
-more detailed variants of \cite{FoxSpector:Economy-and-Emb}): fix a
-sentence with propositional content $S$ and candidate readings $C(S)$,
-where $C(S)$ contains $S$ and all readings derivable from inserting
-$\exh(\cdot)$ at suitable scope sites;\fn{Strictly speaking, we should
-  compare \emph{parses} of sentences with $\exh(\cdot)$ at various
-  scope sites with respect to the readings that these parses give rise
-  to \citep[see][]{ChierchiaFox2008:The-Grammatical}, but we may
-  ignore this detail here for ease of exposition.} then define for
-$X,Y \in C(S)$ either
-\begin{exe}
-\ex \label{bsp:SMH-Total} 
-  $X$ is preferred to $Y$ iff $X \subset Y$ 
-  \attrib{\citep[(104)]{ChierchiaFox2008:The-Grammatical}}
-\end{exe}
-or
-\begin{exe}
-\ex \label{bsp:SMH-Partial}  $X$ is preferred to $Y$ iff $X \subset Y$
-  and $X$ and $Y$ are readings obtained from applications of
-  $\exh(\cdot)$ at exactly the same scope sites, except for
-  one. \attrib{\citep[(105)]{ChierchiaFox2008:The-Grammatical}} 
-\end{exe}
-Since the former is entailed by the latter, we will speak of
-\emph{weak grammaticalism} and \emph{strong grammaticalism},
-depending on whether (\ref{bsp:SMH-Total}) or (\ref{bsp:SMH-Partial})
-is used.
-
-These two varieties of grammaticalism give rise to different
-predictions about preferred readings. The preference for readings that
-weak grammaticalism predicts mirrors the entailment relations in
-(\ref{bsp:Entailments-AS}) and (\ref{bsp:Entailments-GE}): for
-\as-sentences, weak grammaticalism predicts that local readings are
-preferred over global readings which in turn are preferred over
-literal readings; for \es-sentences weak grammaticalism predicts that
-global readings are most preferred, while literal and local readings
-are not ranked with respect to preference. Strong grammaticalism, on
-the other hand, predicts that \as-sentences preferably get either a
-local or a global reading rather than a literal reading, but does not
-rank these former two with respect to each other because they differ
-in more than one application of the $\exh(\cdot)$ operator. For
-\es-sentences, then, strong grammaticalism does not predict \emph{any}
-preference relations between candidate readings at all.
-
-\medskip
-
-Taking stock, traditionalism and grammaticalism have been introduced
-as fairly general core theories that need backup from particular
-auxiliary assumptions to make concrete predictions about availability
-and reading preferences for our target sentences. Most notably, under
-the assumptions made here, traditionalism does not predict local
-readings for \es-sentences to be available while grammaticalism does.
-Grammaticalism, in the form proposed by
-\citet{ChierchiaFox2008:The-Grammatical}, predicts that all candidate
-readings are available and that literal readings are never preferred. All predictions are summarized in
-Table~\ref{tab:predictions}.
-
-\begin{table}[t]
-  \centering
-  \begin{tabular}{lcc}
-    & \multicolumn{2}{c}{preference \& availability}
-    \\ \cmidrule(r){2-3}
-    theoretical position
-    & \as
-    & \es
-    \\ \midrule
-    traditionalism
-    \\
-    \ \ \ \ weak restricted 
-    & \lit > \glb 
-    & \lit 
-    \\
-    \ \ \ \ weak unrestricted
-    & \lit > \glb , \loc 
-    & \lit > \glb
-    \\
-    \ \ \ \ strong restricted
-    & \glb > \lit 
-    & \lit 
-    \\
-    \ \ \ \ strong unrestricted
-    & \glb , \loc > \lit 
-    & \glb > \lit
-    \\
-    % conventionalism
-    % \\
-    % \ \ defaultism
-    % & \loc >  \lit 
-    % & \loc >  \lit
-    % \\
-    % \ \ literalism
-    % & \lit >  \loc 
-    % & \lit >  \loc
-    % \\
-    grammaticalism
-    \\
-    \ \ \ \ weak
-    & \loc > \glb > \lit 
-    & \glb > \lit, \loc
-    \\
-    \ \ \ \ strong
-    & \glb, \loc > \lit 
-    & \glb, \loc , \lit
-    \\
-  \end{tabular}
-  \caption{Predictions of the relevant theoretical positions. Listed
-    are the predicted preference relations. If a reading is not
-    listed, it is predicted to be unavailable. Comma-separated
-    readings are not ranked, i.e., not predicted to differ and not
-    predicted to be equally salient.}
-  \label{tab:predictions}
-\end{table}
-
-% \begin{table}[t]
-%   \centering
-%   \begin{tabular}{lcccccc}
-%     & \multicolumn{4}{c}{availability} 
-%     & \multicolumn{2}{c}{preference}
-%     \\ \cmidrule(r){2-5}  \cmidrule(r){6-7}
-%     theoretical position
-%     & \as-\glb
-%     & \as-\loc
-%     & \es-\glb
-%     & \es-\loc
-%     & \as
-%     & \es
-%     \\ \midrule
-%     traditionalism
-%     \\
-%     \ \ weak restricted 
-%     & $\checkmark$
-%     & $-$
-%     & $\checkmark$
-%     & $-$
-%     & \lit > \glb 
-%     & \lit > \glb
-%     \\
-%     \ \ weak unrestricted
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $-$
-%     & \lit > \glb > \loc 
-%     & \lit > \glb
-%     \\
-%     \ \ strong restricted
-%     & $\checkmark$
-%     & $-$
-%     & $\checkmark$
-%     & $-$
-%     & \glb > \lit 
-%     & \glb > \lit
-%     \\
-%     \ \ strong unrestricted
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $-$
-%     & \glb > \loc > \lit 
-%     & \glb > \lit
-%     \\
-%     conventionalism
-%     \\
-%     \ \ defaultism
-%     & $-$
-%     & $\checkmark$
-%     & $-$
-%     & $\checkmark$
-%     & \loc >  \lit 
-%     & \loc >  \lit
-%     \\
-%     \ \ literalism
-%     & $-$
-%     & $\checkmark$
-%     & $-$
-%     & $\checkmark$
-%     & \lit >  \loc 
-%     & \lit >  \loc
-%     \\
-%     grammaticalism
-%     \\
-%     \ \ weak
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & \loc > \glb > \lit 
-%     & \glb > \lit, \loc
-%     \\
-%     \ \ strong
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & $\checkmark$
-%     & \glb, \loc > \lit 
-%     & \glb, \loc >  \lit
-%     \\
-%   \end{tabular}
-%   \caption{Predictions of the relevant theoretical positions}
-%   \label{tab:predictions}
-% \end{table}
+the same time, the strongest meaning hypothesis has been frequently called upon for
+disambiguation purposes in other domains as well, including reciprocals
+\citep{DalrympleKanazawa1998:Reciprocal-Expr}, plural predication
+\citep{Winter2001:Plural-Predicat} or vagueness \citep{CobrerosEgre2012:Tolerant-Classi}. The
+main reason, however, why we focus on strength based disambiguation is because it is, as far as
+we can say, the only disambiguation mechanism for grammaticalism suggested in the literature
+that gives predictions about potential outcomes of our experiment \emph{ex ante}, i.e., before
+having seen any data of that experiment.\footnote{See also
+  \citet{ChemlaSpector2010:Experimental-Ev} for insightful discussion of strength-based
+  disambiguation in the light of their experimental results.}
+
+Most straightforwardly, disambiguation by logical strength predicts that preferences for
+readings would just mirro mirror the entailment relations in (\ref{bsp:Entailments-AS}) and
+(\ref{bsp:Entailments-GE}): for \as-sentences, weak grammaticalism predicts that local readings
+are preferred over global readings which in turn are preferred over literal readings; for
+\es-sentences weak grammaticalism predicts that global readings are most preferred, while
+literal and local readings are not ranked with respect to
+preference.\footnote{\citet{ChierchiaFox2008:The-Grammatical} consider another, more elaborate
+  variant of disambiguation based on strongest meanings, but it is not necessary for purposes
+  to discuss these details here.}
 

### 2015-10-17 text/paper/revision_02/paper.tex
K2 rev edits

@@
 
-Although restricted traditionalism does not of itself predict local
-readings to be available at all and even unrestricted traditionalism
-does not predict local readings for \es-sentences, many authors who
-adhere to a traditionalist position propose that local readings can be
-available if the embedded scalar item is prosodically marked by
-contrastive stress
+Although traditionalism does not predict local readings for \es-sentences, many authors who
+adhere to a traditionalist position propose that local readings can be available if the
+embedded scalar item is prosodically marked
 \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,GeurtsTielvan-Tiel2013:Embedded-Scalar}. This
-is taken to be continuous with other cases where pragmatic enrichments
-can take scope under logical operators if the relevant focal accent is
-present (\ref{bsp:Stress}).
+is taken to be continuous with other cases where pragmatic enrichments can take scope under
+logical operators if the relevant focal accent is present (\ref{bsp:Stress}).
 
@@
 hypothesis, traditionalists would therefore predict that local
-readings are available for \as- and \es-sentences, but only if
+readings are available for \es-sentences, but only if
 prosodically marked by contrastive stress.

### 2015-10-17 text/paper/revision_02/paper.tex
K2 rev edits
sec 4.4 edits

--- 2015-10-16 text/paper/revision_02/paper.tex
@@
    \end{minipage}
-        \caption{Example trial and results of
-          \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
-          (\citeyear{ChemlaSpector2010:Experimental-Ev}) study.}
+   \caption{Example trial and results of \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
+     (\citeyear{ChemlaSpector2010:Experimental-Ev}) study. Test sentences for pictures like on
+     the left where: ``Every letter is connected to some of its circles.''}
 \end{figure}
@@
 % found putative evidence in support of local readings.
-Differences in results are likely due to differences in experimental
-design, in particular due to (i) the type of elicited judgement and
-(ii) the possibility of conflating pictorial effects.
+Differences in results might be due to differences in experimental design, in particular due to
+the type of elicited judgement and the possibility of conflating pictorial effects. Also, we
+should reflect on the effects of ``silent prosody.''
 
@@
 
-We are generally sympathetic towards
-\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
-reinterpretation of the data, but note, as
-\citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
-typicality-based explanation does not extend to \es-sentences in an
-obvious way. Moreover, typicality itself is not a satisfactory
-primitive in a putative explanation of the use of quantifiers, but
-rather something that needs explanation itself \citep[c.f.][for
-critical reflection on typicality-based
-explanations]{Cummins2014:Typicality-made}. Indeed, it is possible to
-explain typicality judgements as the outcome of Gricean speaker
-preferences for informative descriptions, just like those that
-rationalize quantity implicatures \citep{Franke2014:Typical-use-of-}.
-For these reasons, we believe that typicality and other pictorial
-effects need to be taken seriously in the experimental design, but do
-not necessarily give a satisfactory account of the observed variation
-all by themselves.
-
-\paragraph{Upshot.} Taken together, we would ideally like a design
-that evokes categorical truth value judgments in a way that is as
-independent as possible of potentially conflating properties of the
-pictorial material and that is nonetheless sensitive enough to detect
-local readings even if they are dispreferred. The sensitivity to
-dispreferred readings should be controlled for. On top of this, it
-would be desirable to obtain further information about the relative
-preferences among all putative readings, so as to be able to decide
-between theoretical positions, as outlined in
-Section~\ref{sec:theories-predictions}. % Neither of the previous
-% studies gives us that, either because they simply have not
-% investigated all the relevant comparisons
-% (\citet{GeurtsPouscoulous2009:Embedded-Implic},
-% \citet{CliftonDube2010:Embedded-Implic}), or because they cannot
-% safely derive the required information for danger of conflating
-% preferences for readings with preferences for pictures
-% (\citet{ChemlaSpector2010:Experimental-Ev}).
-
-Finally, we need to control for ``silent prosody.'' Several studies
-suggest that numerous factors might influence accent placement and
-prosodic phrasing even while reading, amongst them default
-accentuation, constituent length, rhythmic phenomena, and individual
-variation
+We are generally sympathetic towards \citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative
+line of reinterpretation of the data, but note, as \citet{ChemlaSpector2010:Experimental-Ev}
+already observed, that his typicality-based explanation does not extend to \es-sentences in an
+obvious way. Moreover, typicality itself is not a satisfactory primitive in a putative
+explanation of the use of quantifiers, but rather something that needs explanation itself
+\citep[c.f.][for critical reflection on typicality-based
+explanations]{Cummins2014:Typicality-made}. Indeed, it is possible to explain typicality
+judgements as the outcome of Gricean speaker preferences for informative descriptions, just
+like those that rationalize quantity implicatures \citep{Franke2014:Typical-use-of-}.  For
+these reasons, we believe that typicality and other pictorial effects need to be taken
+seriously in the experimental design, but do not necessarily give a satisfactory account of the
+observed variation all by themselves. In other words, if we take worries about pictorial
+effects seriously, we need to reconsider conclusions from previous studies in the light of data
+from a task that minimizes pictorial effects as much as possible.
+
+\paragraph{``Silent prosody.''} Several studies suggest that numerous factors might influence
+accent placement and prosodic phrasing even while reading, amongst them default accentuation,
+constituent length, rhythmic phenomena, and individual variation
 \citep[e.g.][]{Bader98,Fodor98,Steinhauer01,Fodor02,Augurzky08,BreenWatson2011:Intonational-ph,Kentner12}. If
-we adopt the prosodic markedness hypothesis described in
-Section~\ref{sec:inton-mark-hypoth}, as many traditionalists do, we
-predict that the availability of a local reading hinges on the
+we adopt the prosodic markedness hypothesis described in Section~\ref{sec:inton-mark-hypoth},
+as many traditionalists do, we predict that the availability of a local reading hinges on the
 realization of contrastive stress on the scalar item
 \citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar}.
-But if prosody can have this role, it is necessary to control for
-silent accent placement. Ideally, therefore, we should present
-sentences auditorily and systematically manipulate contrastive stress.
+But if prosody can have this role, it is necessary to control for silent accent
+placement. Ideally, therefore, we should present sentences auditorily and systematically
+manipulate contrastive stress.
+
+\paragraph{Upshot.} This leaves us with the following desiderata. (i) In order to test the
+availability and preferences of different readings of \as- and \es-sentences, we need a way to
+unambiguously map responses, ideally categorical, to specific readings. (ii) We should try to
+avoid issues of ``silent prosody'' and actively explore the role of prosodic markedness. (iii)
+We would like to obtain information about the relative preferences of the different readings,
+ideally by comparison to some other, ``base-line'' condition. Finally (iv) we want to minimize
+potential picture typicality effects.
 
@@
 
-\paragraph{General Idea.} In order to test the availability and
-preferences of different readings of \as- and \es-sentences in German,
-we were looking for a way to unambiguously map responses from a
-picture-verification task to specific readings. We were particularly
-interested in the question whether local readings would be observed at
-all, and whether their presence or absence would be modulated by a
-contrastive accent on the scalar item. Moreover, we were interested in
-obtaining information about the relative preferences of the different
-readings. In addition, we wanted to minimize potential picture
-typicality effects. To achieve this (see
-Section~\ref{sec:discussion-1} for discussion), we used an
-\emph{incremental verification task} (\acro{ivt}), which is a
-modified version of picture verification
-\citep[see][]{Conroy2008}. The general idea is that subjects are
-requested to judge sentence material with respect to pictures that do
-not necessarily contain all the information relevant for judging a
-certain reading true or false. In that case, participants can demand
-that more information be revealed. Participants are instructed to make
-a truth-value judgment as soon as they are able to. When they do, the
-trial ends.
+\paragraph{General Idea.} To deal with these desiderata, we used an \emph{incremental
+  verification task} (\acro{ivt}), which is a modified version of picture verification
+\citep[see][]{Conroy2008}. The general idea is that subjects are requested to judge sentence
+material with respect to pictures that do not necessarily contain all the information relevant
+for judging a certain reading true or false. In that case, participants can demand that more
+information be revealed. Participants are instructed to make a truth-value judgment as soon as
+they are able to. When they do, the trial ends.
 

### 2015-10-17 text/paper/reviews_2/response_letter.md

@@
 1. careful reformulation of conclusions to be drawn from our data in line with reviewer 2's suggestions; concretely:
+
 	a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not;
+
 	b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment;
+
 	c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.
+
 2. shortening of section 3 to remove unnecessary detail in predictions of "core theories"
@@
 a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not;
+
 b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment;
+
 c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.
@@
 Although we had thought that it would be good for the readers to see the full space of possible predictions about preference patterns that relevant "core theories" + "auxiliary hypotheses" give, we agree that it is not strictly necessary to introduce all of these distinctions.
-We have therefore removed those chunks of Section 3 which are not strictly relevant for late discussions (including Table 2, which summarized the predictions).
+We have therefore removed those chunks of Section 3 which are not strictly relevant for later discussions (including Table 2, which summarized the predictions).
 Some particular "auxiliary assumptions" are taken up in the discussion section 6, but only those that are relevant for the overall discussion, like Magri's appeal to obligatory exhaustification, which is an example for how grammaticalism could predict our data.

### 2015-10-17 text/paper/revision_02/paper.tex

@@
 
-\noindent The \emph{prosodic markedness hypothesis}, as we will call
-it here, is then an addition to the traditionalist's explanatory
-repertoire. Under this extra assumption, local readings are a marked
-phenomenon, and not the product of the same process as run-of-the-mill
-scalar implicatures. If supplemented with the prosodic markedness
-hypothesis, traditionalists would therefore predict that local
-readings are available for \as- and \es-sentences, but only if
+\noindent The \emph{prosodic markedness hypothesis}, as we will call it here, is then an
+addition to the traditionalist's explanatory repertoire. Under this extra assumption, local
+readings are a marked phenomenon, and not the product of the same process as run-of-the-mill
+scalar implicatures. If supplemented with the prosodic markedness hypothesis, traditionalists
+would therefore predict that local readings are available for \es-sentences, but only if
 prosodically marked by contrastive stress.

### 2015-10-17 text/paper/revision_02/paper.tex
micha final edits version 2

@@
 the type of elicited judgement and the possibility of conflating pictorial effects. Also, we
-should reflect on the effects of ``silent prosody.''
+should consider potential effects of ``silent prosody.''
 
@@
 availability and preferences of different readings of \as- and \es-sentences, we need a way to
-unambiguously map responses, ideally categorical, to specific readings. (ii) We should try to
-avoid issues of ``silent prosody'' and actively explore the role of prosodic markedness. (iii)
-We would like to obtain information about the relative preferences of the different readings,
-ideally by comparison to some other, ``base-line'' condition. Finally (iv) we want to minimize
-potential picture typicality effects.
+unambiguously map responses, ideally categorical, to specific readings. (ii) We want to
+minimize possible pictorial effects. (iii) We would like to obtain information about the
+relative preferences of the different readings, ideally by comparison to some other,
+``base-line'' condition. (iv) We should try to avoid issues of ``silent prosody'' and actively
+explore the role of prosodic markedness.
 
@@
 
-\paragraph{General Idea.} To deal with these desiderata, we used an \emph{incremental
-  verification task} (\acro{ivt}), which is a modified version of picture verification
-\citep[see][]{Conroy2008}. The general idea is that subjects are requested to judge sentence
-material with respect to pictures that do not necessarily contain all the information relevant
-for judging a certain reading true or false. In that case, participants can demand that more
-information be revealed. Participants are instructed to make a truth-value judgment as soon as
-they are able to. When they do, the trial ends.
+\paragraph{General motivation.} To deal with desiderata (i) and (ii), we used an
+\emph{incremental verification task} (\acro{ivt}), which is a modified version of picture
+verification \citep[see][]{Conroy2008}. The general idea is that subjects are requested to
+judge sentence material with respect to pictures that do not necessarily contain all the
+information relevant for judging a certain reading true or false. In that case, participants
+can demand that more information be revealed. Participants are instructed to make a truth-value
+judgment as soon as they are able to. When they do, the trial ends. Motivated by desideratum
+(iii), we include ``preference-related control'' conditions. Sentence material was presented
+auditorily and we manipulated prosodic realization to cater for desideratum (iv).
 
@@
 
-\noindent If we compare (\ref{bsp:observed-preferences}) with
-Table~\ref{tab:predictions}, we quickly see that these findings are
-not predicted by either traditionalism or grammaticalism under the
-auxiliary assumptions that we considered so far. We address each
-position separately in the following.
-
-Traditionalism easily explains the absence of global readings. Weak
-traditionalism, introduced in Section~\ref{sec:traditionalism}, for
-instance, would hold that the extra assumptions needed to derive
-global readings (e.g., a speaker competence assumption) are not
-available or only allow for epistemically weak implicatures that would
-show as responses indicative of literal readings in our task. In
-support of this view, traditionalists could argue that the task's
-rather high processing demands lead to a suppression of global
-readings, in line with the findings of
-\citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
-load negatively affects the number of scalar implicature responses in
-sentence verification tasks. The finding of local readings in
-\as-sentences with contrastive stress is easily explained by adopting
-the prosodic markedness hypothesis. What traditionalism does not
-predict is the high number of answers indicative of local readings in
-the \es-conditions. Resorting to the prosodic markedness hypothesis
-does not help, because local readings were observed for accented as
-well as for unaccented \es-sentences.%  It would also remain unclear why
-% prosodic cues should have such differential effects on \as- and
-% \es-sentences.
+\noindent Let's consider whether traditionalism or grammaticalism are comfortable with these
+preference relations.
+
+Traditionalism easily explains the absence of global readings by holding that the extra
+assumptions needed to derive global readings (e.g., a speaker competence assumption) are not
+available or only allow for epistemically weak implicatures that would show as responses
+indicative of literal readings in our task. In support of this view, traditionalists could
+argue that the task's rather high processing demands lead to a suppression of global readings,
+in line with the findings of \citet{NeysDe-NeysSchaeken2007:When-People-Are} that working
+memory load negatively affects the number of scalar implicature responses in sentence
+verification tasks. The finding of local readings in \as-sentences with contrastive stress is
+easily explained by adopting the prosodic markedness hypothesis. What traditionalism does not
+predict is the high number of answers indicative of local readings in the
+\es-conditions. Resorting to the prosodic markedness hypothesis does not help, because local
+readings were observed for accented as well as for unaccented \es-sentences.
 
 Grammaticalism, on the other hand, fails to predict the pattern in
-(\ref{bsp:observed-preferences}) entirely if it equates preference for
-readings with logical strength. Grammaticalism predicts that literal
-readings of \as-sentences are the least preferred, contrary to
-(\ref{bsp:observed-preferences}). Again, we need to bear the caveat of
-Section~\ref{sec:grammaticalism} in mind that we are only evaluating
-grammaticalism with respect to a particular disambiguation criterion
-here. The verdict, however, seems to be clear. If
-(\ref{bsp:observed-preferences}) shows the actual preference orders
-over readings, then meaning disambiguation in terms of logical
-strength is generally on the wrong track, because no account that
-merely looks at the logical strengths of readings can plausibly
-predict the preference pattern in (\ref{bsp:observed-preferences}) for
-both \as- and \es-sentences at the same time.
-
-In sum, the present findings cannot be explained in terms of the
-versions of traditionalism and grammaticalism that we have considered
-so far, i.e., with the particular auxiliary assumptions adopted in
-Section~\ref{sec:theories-predictions}. But we should ask what
-plausible amendements or alternative auxiliary assumptions would
-enable either core theory to accommodate the data \emph{ex post}. This
-is what we do in the next section, where we also reflect critically on
-our design and our interpretation of the data.
+(\ref{bsp:observed-preferences}) entirely if it equates preference for readings with logical
+strength. Strength-based disambiguation predicts that literal readings of \as-sentences are the
+least preferred, contrary to (\ref{bsp:observed-preferences}). Again, we need to bear the
+caveat of Section~\ref{sec:grammaticalism} in mind that we are only evaluating grammaticalism
+with respect to a particular disambiguation criterion here. The verdict, however, seems to be
+clear. If (\ref{bsp:observed-preferences}) shows the actual preference orders over readings,
+then meaning disambiguation in terms of logical strength is generally on the wrong track,
+because no account that merely looks at the logical strengths of readings can plausibly predict
+the preference pattern in (\ref{bsp:observed-preferences}) for both \as- and \es-sentences at
+the same time.
+
+In sum, the present findings appear to challenge traditionalism as a ``core theory'', and to
+challenge grammaticalism under the ``auxiliary assumption'' that reading preferences mirror
+logical strength. Given this, we should ask what plausible amendements or alternative auxiliary
+assumptions would enable either position to accommodate the data \emph{ex post}. This is what
+we do in the next section, where we also reflect critically on our design and our
+interpretation of the data.
 
@@
 
-Section~\ref{sec:theories-predictions} introduced
-traditionalism and grammaticalism as two competing core theories,
-whose concrete empirical predictions depend on additional auxiliary
-assumptions. We chose, in part for practical reasons, particular
-auxiliary assumptions, but we should also ask more generally: on the
-supposition that our design and the offered interpretation of our data
-are sound, what would it take to accommodate the observed data under
-the core theories?
-
-\paragraph{Grammaticalism.} Consider grammaticalism first. Our data
-contradicts the notion that preferences follow logical strength. But,
-as noted in Section~\ref{sec:theories-predictions}, grammaticalism
-could be supplemented by a conceptually different disambiguation
-criterion. Selecting readings in terms of how well they answer the
-contextually given question under discussion, as suggested by
-\citet{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}, is
-an option. But it is quite unclear what the question under discussion
-should be that guided judgements in our particular task. To make this
-approach yield \emph{ex ante} predictions, we would need to determine
-before the data is available which implicit QUDs our particular task
-should give rise to, so as to derive a preference ordering over
-readings. This may well be possible, but we do not presently see how.
-
-Another possibility of explaining our data within a grammaticalist
-core theory is to adopt \citeauthor{Magri2011:Another-Argumen}'s
-(\citeyear{Magri2011:Another-Argumen}) proposal that exhaustification
-operators occur at every relevant scope site while alternative sets as
-their input may also be empty.\footnote{This interesting line of
-  alternative \emph{post hoc} explanation was first suggest by a
-  reviewer, but worked out slightly differently here to strengthen the
-  reviewer's case.} For \as- and \es-sentences, we would have to
-consider the parses in (\ref{Magri-Parses}) (in simplified notation).
+Section~\ref{sec:theories-predictions} introduced traditionalism and grammaticalism as two
+competing core theories, whose concrete empirical predictions depend on additional
+assumptions. Here, we should finally ask more generally: on the supposition that our design and
+the offered interpretation of our data are sound, what would it take to accommodate the
+observed data under the core theories?
+
+\paragraph{Grammaticalism.} Consider grammaticalism first. Our data contradicts the notion that
+preferences follow logical strength. But, as noted in Section~\ref{sec:theories-predictions},
+grammaticalism could be supplemented by a conceptually different disambiguation
+criterion.\footnote{See also the discussion by \citet{ChemlaSpector2010:Experimental-Ev} on the
+  prospects of pushing strength-based disambiguation in the light of their data, which they
+  also take to imply contradicting evidence on reading preferences.} Selecting readings in
+terms of how well they answer the contextually given question under discussion, as suggested by
+\citet{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}, is an option. But it is
+quite unclear what the question under discussion should be that guided judgements in our
+particular task.
+
+Another possibility of explaining our data within a grammaticalist core theory
+is to adopt \citeauthor{Magri2011:Another-Argumen}'s (\citeyear{Magri2011:Another-Argumen})
+proposal that exhaustification operators occur at every relevant scope site while alternative
+sets as their input may also be empty.\footnote{This interesting line of alternative \emph{post
+    hoc} explanation was first suggest by a reviewer, but worked out slightly differently here
+  to strengthen the reviewer's case.} For \as- and \es-sentences, we would have to consider the
+parses in (\ref{Magri-Parses}) (in simplified notation).
 
@@
 
-On conceptual grounds we are very much in favor of a disambiguation
-criterion in terms of economy considerations, but whether the
-particular account sketched here is empirically successful in other
-cases as well, must remain to be seen. Two things are worth
-emphasizing here nonetheless. Firstly, the sketched Magri-style
-account is a plausible alternative \emph{post hoc} explanation. It was
-not, at least to our knowledge, a salient possibility before seeing
-our data set: other specifications of $Alt_1$ and $Alt_2$ could have
-been made equally plausible \emph{ex ante}. Secondly, what our data
-refutes is that preferences for readings follow logical
-strength. This, therefore, does not jeopardize grammaticalism as a
-core theory, but calls for theory-internal revision of its
-disambiguation criterion. Taken together, we argue that the data
-presented here points to a dire need of refining grammaticalism,
-perhaps along the lines suggested here, but ideally alongside more
+On conceptual grounds we are very much in favor of a disambiguation criterion in terms of
+economy considerations, but whether the particular account sketched here is empirically
+successful in other cases as well, must remain to be seen. Two things are worth emphasizing
+here nonetheless. Firstly, the sketched account is a plausible \emph{post hoc} explanation. It
+was not, at least to our knowledge, a salient possibility before seeing our data set: other
+specifications of $Alt_1$ and $Alt_2$ could have been made equally plausible \emph{ex
+  ante}. Secondly, what our data refutes is that preferences for readings follow logical
+strength. This, therefore, does not jeopardize grammaticalism as a core theory, but merely
+calls for theory-internal revision of its disambiguation criterion, ideally alongside more
 experimental data.
@@
 		\fbox{\includegraphics[width=3.5cm]{pictures/PostExp_2.pdf}}
-	    \label{fig:exseqES1}
+	    \label{fig:exseqPost1}
 	}
@@
 		\fbox{\includegraphics[width=3.5cm]{pictures/PostExp_3.pdf}}
-	    \label{fig:exseqES2}
+	    \label{fig:exseqPost2}
 	}
@@
 		\fbox{\includegraphics[width=3.5cm]{pictures/PostExp_4.pdf}}
-	    \label{fig:exseqES3}
+	    \label{fig:exseqPost3}
 	}
@@
 
-Backed up by our analyses, we concluded that both traditionalism and
-grammaticalism do not predict our data under the set of auxiliary
-assumptions that we provided them with in
-Section~\ref{sec:theories-predictions}. Traditionalism fails to
-account for high numbers of responses indicating local readings even
-for prosodically unmarked \es-sentences. Grammaticalism, insofar as it
-builds on disambiguation by logical strength, fails to predict the
-absence of answers indicative of global readings and the relative
-abundance of answers indicative of literal readings.
-
-The clearest upshot of theoretical importance of this study is that
-strength-based meaning selection does not seem to be a good
-disambiguation criterion for grammaticalism. This point is also
-relevant in general, because disambiguation based on logical strength
-has been suggested in other domains as well
+Backed up by our analyses, we concluded that both traditionalism and grammaticalism do not
+predict our data under the set of auxiliary assumptions that we provided them with in
+Section~\ref{sec:theories-predictions}. Traditionalism fails, as a core theory, to account for
+high numbers of responses indicating local readings even for prosodically unmarked
+\es-sentences. Grammaticalism as a core theory is trivially compatible with our data, because
+it would be compatible with any observed preference order. But insofar as it builds on
+disambiguation by logical strength, grammaticalism fails to predict the absence of answers
+indicative of global readings and the relative abundance of answers indicative of literal
+readings.
+
+The clearest upshot of theoretical importance of this study is that strength-based meaning
+selection does not seem to be a good disambiguation criterion for grammaticalism
+\citep[c.f.][]{ChemlaSpector2010:Experimental-Ev}. This point is also relevant in general,
+because disambiguation based on logical strength has been suggested in other domains as well
 \citep[e.g.][]{DalrympleKanazawa1998:Reciprocal-Expr,Winter2001:Plural-Predicat,CobrerosEgre2012:Tolerant-Classi}.
-We tentatively suggested an alternative selection principle for
-grammaticalism in terms of ``parsing economy,'' but it remains to be
-seen whether this is empirically successful in other domains as well.
+We tentatively suggested an alternative selection principle for grammaticalism in terms of
+``parsing economy,'' but it remains to be seen whether this is empirically successful in other
+domains as well.
 
@@
 
-We have argued that auditory presentation of sentence material is crucial if
-prosodic information is hypothesized to influence
-availability and preferences of readings. We also argued that
-theoretical positions must be formulated in such a way that they make
-testable predictions about reading preferences where different
-potential readings are allowed. We should then try to obtain
-information about actual preference patterns by explicit comparison
-with constructions whose preference structures are well-studied, ideally
-with some model of the data generating process for optimal data
-analysis.
+We have argued that auditory presentation of sentence material is crucial if prosodic
+information is hypothesized to influence availability and preferences of readings. We also
+argued in passing that theoretical positions must be formulated in such a way that they make
+testable predictions about reading preferences where different potential readings are
+allowed. We should then try to obtain information about actual preference patterns by explicit
+comparison with constructions whose preference structures are well-studied, ideally with some
+model of the data generating process for optimal data analysis.
 

### 2015-11-01 text/paper/reviews_2/response_letter.md
rev 2 final edits

--- 2015-09-28 text/paper/reviews_2/response_letter.md
@@
 # Response to editor and reviewer comments
+
+First of all, we would like to thank the editor and the reviewers for their comments and suggestions and for carefully reading our manuscript.
+We addressed each of the points raised to the best of our abilities and think that the reviews substantially improved this work.
 
@@
 
-1. careful reformulation of conclusions to be drawn from our data in line with reviewer 2's suggestions; concretely:
-	a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
-	b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment; 
-	c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.
-2. shortening of section 3 to remove unnecessary detail in predictions of "core theories"
+1. careful reformulation of conclusions to be drawn from our data in line with reviewer 2's suggestions;
+
+2. shortening of section 3 to remove unnecessary detail in predictions of "core theories";
+
 3.
-addition of a few elements of emphasis in introduction, Section 4 and reflection section 6, in response to reviewer 2's comments showing that the previous version may not have made the motivation of our design sufficiently clear
+addition of a few elements of emphasis in introduction, Section 4 and reflection section 6, in response to reviewer 2's comments showing that the previous version may not have made the motivation of our design sufficiently clear.
+
+In the following we will give detailed responses to the comments.
 
@@
 It is not our intention to polarize by misleading rhetorics.
-We have tried to make very clear in the current version that our main conclusions from our data are (as already stated above):
+We have tried to clarify in the current version what our main conclusions from our data are, namely:
 
 a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not;
-b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment; 
+
+b. we further specify why we believe that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment;
+
 c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.
@@
 
-Although we had thought that it would be good for the readers to see the full space of possible predictions about preference patterns that relevant "core theories" + "auxiliary hypotheses" give, we agree that it is not strictly necessary to introduce all of these distinctions.
-We have therefore removed those chunks of Section 3 which are not strictly relevant for late discussions (including Table 2, which summarized the predictions).
+Although we had thought that it would be good for the readers to see the full space of possible predictions about preference patterns that relevant "core theories" + "auxiliary hypotheses" give, we agree that it is not strictly necessary to introduce all of these fine-grained distinctions.
+We have therefore removed those chunks of Section 3 which are not strictly relevant for our overall discussions (including Table 2, which summarized the predictions).
 Some particular "auxiliary assumptions" are taken up in the discussion section 6, but only those that are relevant for the overall discussion, like Magri's appeal to obligatory exhaustification, which is an example for how grammaticalism could predict our data.
@@
 
-Reviewer 1 had only minor remarks.
+Reviewer 1 had only minor remarks, which we will address below.
 
@@
 
-References updated accordingly.
+Good point. We simply removed the reference to Clifton et al. 2002. Citing counterevidence here is not very important, so we leave it at that.
 
@@
 
-Reviewer 2 actually raises many points, not all of which are fully clear to us.
-We tried our very best to address all of the issues raised (insofar as we understood what was asked of us), but paid particular attention to those issues flagged as most important by the reviewer herself/himself or the editor.
+We tried our very best to address all of the issues raised by reviewer 2, and
+paid particular attention to those issues flagged as most important by the
+reviewer herself/himself or the editor.
 
@@
 
-We feel that this description of what the paper is about is unfortunately not entirely correct.
-This could lead to certain misunderstandings, so we clarify our position here.
-We have also added to the text (introduction, especially the relevant Section 4.4, section 6) to strengthen our view of and motivation for what we are doing.
-(It is our fault, of course, that this has not been sufficiently clear in the previous version.)
+We are sorry that we didn't specify these points clearly enough in our previous manuscript.
+We feel that this description of what the paper is about is unfortunately not entirely as we intended.
+This could lead to certain misunderstandings, so we clarify our position in the present manuscript.
+We have also added to the text (introduction, especially the relevant Section 4.4, section 6) to strengthen our view of and the motivation for out study.
 
@@
 This also includes the results of Chemla & Spector.
-This is why we want to be more careful in this paper and not take for granted the conclusions of Chemla & Spector contrary to what the reviewer suggests we should do.
+This is why we want to be more careful in this paper and not take for granted the conclusions of Chemla & Spector.
 
-Our reluctance to accept Chemla & Spector's conclusions also comes from the recent critique of, in particular, Bart Geurts and Bob van Tiel, who argue that Chemla & Spector's results could be influenced unduly by pictorial effects.
+Our reluctance to accept Chemla & Spector's conclusions also comes from the recent critique of, in particular, Geurts & van Tiel, who argue that Chemla & Spector's results could be influenced unduly by pictorial effects.
 This is the main motivation for our incremental verification task, as argued in Section 4.4 and followed up in the reflection section 6.
@@
 We are very grateful for drawing our attention to the fact that we should mention that Chemla & Spector have already discussed their data as countering the Strongest Meaning Hypothesis.
-Our position to this is that, yes, we provide further evidence, but also further evidence that is relevant, given the doubts that were brought forth against Chemla & Spector's design and interpretation and the additional doubts that arise from issues with "silent prosody".
+We agree with this point but we believe that are providing further evidence that is relevant for this discussion, given the doubts that were brought forth against Chemla & Spector's design and interpretation and the additional doubts that arise from issues with "silent prosody".
 
@@
 
-On the other hand, for the very reasons described above, we are reluctant to accept the results and conclusions of Chemla & Spector as given.
+Considering the results and conclusions of Chemla & Spector, we are reluctant to accept these as given.
 Since our design was motivated by catering to the very problems raised for Chemla & Spector, we do believe that our data gives new and interesting information about preference of readings.
-This is also because, as we argue in Section 4.4, we explicitly compare data from embedded scalars with other ambiguous constructions in the very same experiment (same method, same subject pool).
+This is also because, as we argue in Section 4.4, we explicitly compare data from embedded scalars with other ambiguous constructions in the same experiment (same method, same subject pool).
 
@@
 
-This is a good and interesting suggestion. We cannot follow up on this in the paper, but acknowledge the point in a footnote.
+This is a good and interesting suggestion. But we see potential problems with this idea, but feel that discussing this would lead us too far away from our main concerns.
 
@@
 
-It seems that we have reach rock bottom here, where the reviewer's view differs irresolvably from ours.
+It seems that we have reached rock bottom here, where the reviewer's view differs irresolvably from ours.
 Chierchia, Fox and Spector (2012, "The Grammatical View of Scalar Implicatures and the Relationship between Semantics and Pragmatics") suggest to use the SMH for disambiguating parses.
@@
 We are grateful for this comment, because it shows that we have been insufficiently clear on our intended meaning of *ex ante* predictions.
-We have clarified this in footnote XXX.
+We have clarified this more in the text (Section 3).
 We are interested in *ex ante* predictions *for our experiment*, not general predictions *given a set of contextual parameters*.
-We fully agree with the reviewer that abstract experimental setting underspeficy relevant contextual parameters.
+We fully agree that abstract experimental setting underspecify relevant contextual parameters.
 We also therefore agree that our data does not speak against grammaticalism as a "core theory".

### 2015-11-01 text/paper/revision_02/paper.tex
rev 2 final edits

@@
   light on the relative preferences or salience of candidate readings. The presented data turn
-  out to be unexpected under a traditional Gricean view, but also challenge the idea that of
+  out to be unexpected under a traditional Gricean view, but also challenge the idea of
   disambiguation by logical strength in grammaticalist approaches.
@@
 
-To deal with the problem of ``silent intonation,'' this paper presents results from an
-experimental study which presented sentence materials auditorily and explicitly manipulated
-contrastive stress on embedded scalar items. To address worries about pictorial ``typicality
-effects,'' we employed an \emph{incremental verification task} in which parts of a
-to-be-evaluated picture were hidden and only revealed piece-wise at the participants’ request
-until they felt able to give a binary truth-value judgement \citep[see][]{Conroy2008}. In order
-to obtain information about salience of readings, we use both a classical regression analysis
-and a Bayesian statistical model to analyze the data from this novel task, and validate this
-method by including control conditions testing ambiguous sentences with a well-known preference
-on available readings. % We argue that this method provides categorical behavioral data that is
-% both indicative of the reading preferences among participants and largely independent of
-% potential pictorial confounds, such as the mentioned typicality effects.
+To deal with these methodological concerns, this paper presents results from an
+\emph{incremental verification task}. In order to address the problem of silent prosody, we
+presented sentence materials auditorily and explicitly manipulated contrastive stress on
+embedded scalar items. Moreover, to address worries about pictorial “typicality effects,” parts
+of a to-be-evaluated picture were hidden and only revealed piece-wise at the participants’
+request until they felt able to give a binary truth-value judgement
+\citep[see][]{Conroy2008}. In order to obtain information about salience of readings, we use
+both a classical regression analysis and a Bayesian statistical model to analyze the data from
+this novel task, and validate this method by including control conditions testing ambiguous
+sentences with a well-known preference on available readings.
 
@@
 
-Traditionalism's predictions about preferences among available readings depend whether the
-speaker is (most likely) knowledgeable in the relevant sense. We predict a strong non-epistemic
-implicature that a given alternative is false if the speaker is assumed to be competent;
-otherwise the preferred reading would be a literal reading or a weak epistemic implicature
-(that the speaker does not know whether the alternative is true). In the context of a given
-abstract experiment that does not manipulate speaker expertise (like ours), it is then
-\emph{prima facie} compatible with a traditionalist position to expect literal or implicature
-readings to be more prominent.
+Traditionalism’s predictions about preferences among available readings depend on the
+reliability of contextual information, such as speaker knowledgeability. Specifically,
+considering a speaker knowledgeable results in a strong non-epistemic implicature that a given
+alternative is false. By contrast, considering a speaker as ignorant results in a literal
+reading or a weak epistemic implicature (that the speaker does not know whether the alternative
+is true). In the context of a given abstract experiment that does not manipulate speaker
+expertise (like ours), it is then \emph{prima facie} compatible with a traditionalist position
+to expect literal or implicature readings to be more prominent \citep[see][for experimental
+data on this]{GoodmanStuhlmuller2013:Knowledge-and-I}.
 
@@
 Several approaches have been suggested in the literature
-\citep[c.f.][]{ChemlaSingh2014:Remarks-on-the-}. We focus here on the one that is least
-controversially applicable to our experimental case, and that has theoretical significance
-beyond the debate about embedded implicatures: disambiguation by comparison of logical
-strengths, as suggested by the \emph{strongest meaning hypothesis} of
-\citet{DalrympleKanazawa1998:Reciprocal-Expr}.\footnote{We will come back to other
-  implementations of grammaticalism in Section~\ref{sec:critical-reflection}.}
-
-% To start with,
-% \citet{Magri2009:A-Theory-of-Ind,Magri2011:Another-Argumen} opts for
-% obligatory presence of $\exh(\cdot)$ with variability in the set of
-% alternatives to feed into each $\exh(\cdot)$. Under this approach,
-% alternatives may be pruned entirely, so that all occurrences of
-% $\exh(\cdot)$ become vacuous, resulting in a literal reading. Whether
-% alternatives apply or not is a matter of their relevance. It is not
-% clear what his approach predicts \emph{ex ante} about the relative
-% salience of candidate readings in a neutral experiment that does not
-% explicitly provide information about which alternatives are relevant
-% (for whatever purpose). However, we will show in
-% Section~\ref{sec:critical-reflection} that Magri's approach can be
-% brought to accommodate the data very well after the fact.
-
-% Other proponents of grammaticalism assume that insertion of $\exh(\cdot)$ is
-% optional. Under one proposal for disambiguation, readings are the more
-% preferred the better they answer the contextually given question under
-% discussion (QUD)
-% \citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. This
-% is a plausible suggestion, but does not give clear predictions for a
-% case like our experiment without fixed QUD. Subjects could in
-% principle accommodate any QUD, so that this approach would not
-% restrict the space of reading preferences either.
-
-Supplementing grammaticalism with a strength-based selection criterion has been suggested, in
-one form or another, in many contributions to this paradigm
+\citep[c.f.][]{Fox2007:Free-Choice-and,Magri2009:A-Theory-of-Ind,ChemlaSingh2014:Remarks-on-the-}.
+
+To our knowledge, only one of these proposed disambiguation mechanisms is principally able to
+give predictions about potential outcomes of our experiment \emph{ex ante}, i.e., before having
+seen any data of that experiment. The \emph{strongest meaning hypothesis} of
+\citet{DalrympleKanazawa1998:Reciprocal-Expr} involves a disambiguation mechanism by comparison
+of logical strengths. Supplementing grammaticalism with a strength-based selection criterion
+has been suggested, in one form or another, in many contributions to this paradigm
 \citep[e.g.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. At
-the same time, the strongest meaning hypothesis has been frequently called upon for
-disambiguation purposes in other domains as well, including reciprocals
-\citep{DalrympleKanazawa1998:Reciprocal-Expr}, plural predication
-\citep{Winter2001:Plural-Predicat} or vagueness \citep{CobrerosEgre2012:Tolerant-Classi}. The
-main reason, however, why we focus on strength based disambiguation is because it is, as far as
-we can say, the only disambiguation mechanism for grammaticalism suggested in the literature
-that gives predictions about potential outcomes of our experiment \emph{ex ante}, i.e., before
-having seen any data of that experiment.\footnote{See also
-  \citet{ChemlaSpector2010:Experimental-Ev} for insightful discussion of strength-based
-  disambiguation in the light of their experimental results.}
+the same time, the strongest meaning hypothesis has theoretical significance beyond the debate
+about embedded implicatures and has been frequently called upon for disambiguation purposes in
+other domains, including reciprocals \citep{DalrympleKanazawa1998:Reciprocal-Expr}, plural
+predication \citep{Winter2001:Plural-Predicat} or vagueness
+\citep{CobrerosEgre2012:Tolerant-Classi}.
 
 Most straightforwardly, disambiguation by logical strength predicts that preferences for
-readings would just mirro mirror the entailment relations in (\ref{bsp:Entailments-AS}) and
+readings would just mirror the entailment relations in (\ref{bsp:Entailments-AS}) and
 (\ref{bsp:Entailments-GE}): for \as-sentences, weak grammaticalism predicts that local readings
@@
 scalar implicatures. If supplemented with the prosodic markedness hypothesis, traditionalists
-would therefore predict that local readings are available for \es-sentences, but only if
+would therefore predict that local readings are available forK \es-sentences, but only if
 prosodically marked by contrastive stress.
@@
 information relevant for judging a certain reading true or false. In that case, participants
-can demand that more information be revealed. Participants are instructed to make a truth-value
-judgment as soon as they are able to. When they do, the trial ends. Motivated by desideratum
-(iii), we include ``preference-related control'' conditions. Sentence material was presented
-auditorily and we manipulated prosodic realization to cater for desideratum (iv).
+could demand that more information be revealed. Participants were instructed to make a
+truth-value judgment as soon as they were able to do so. When they did, the trial
+ended. Motivated by desideratum (iii), we included ``preference-related control''
+conditions. The sentence materials were presented auditorily and we manipulated the prosodic
+realization to cater for desideratum (iv).
 
@@
 observed to be preferred over \ec-readings (e.g., \cite{Fodor98} for
-an overview of different languages, but see also
-\cite{CliftonCarlsonFrazier2002} for counterevidence). Crucially, an
+an overview of different languages). Crucially, an
 \lc-preference for \acro{pp}-attachment structures has also been
@@
 We fitted generalized linear models to the count data in
-Table~\ref{tab:count_data_CC}, using factors \textsc{Condition} with
+Table~\ref{tab:count_data_CC}, using factors \textsc{SentenceType} with
 levels \as and \es, \textsc{Accent} with levels \emph{neutral} and
@@
 terms of AICs, starting from the saturated model. The best model takes
-main factors \textsc{Reading} and \textsc{Condition} into account, as
+main factors \textsc{Reading} and \textsc{SentenceType} into account, as
 well as the interaction term \textsc{Reading:Condition} ($\chi^2 =
@@
     0.435 \\
-    \textsc{Condition}.\es & 1.030 &  0.301 & 3.423 &  < 0.001 \\
-    \textsc{Reading}.\emph{literal}:\textsc{Condition}.\es & -1.288 &
+    \textsc{SentenceType}.\es & 1.030 &  0.301 & 3.423 &  < 0.001 \\
+    \textsc{Reading}.\emph{literal}:\textsc{SentenceType}.\es & -1.288 &
     0.319 & -4.036 &  < 0.001 \\
-    \textsc{Reading}.\emph{local}:\textsc{Condition}.\es & -0.026 &
+    \textsc{Reading}.\emph{local}:\textsc{SentenceType}.\es & -0.026 &
     0.463 &  -0.0579 &  0.955
@@
 \emph{\lc-cue} and \emph{\ec-cue}, \textsc{Trial} with levels 1 to
-3, and \textsc{Condition} with levels \lc and \ec for the picture
+3, and \textsc{Picture} with levels \lc and \ec for the picture
 sequences. Starting search from the saturated model along a gradient
 of decreasing AICs, we find that the ``best'' model relies on main
-effects of \textsc{Reading}, \textsc{Accent} and \textsc{Condition}
-and two two-way interactions \textsc{Reading:Condition} and
+effects of \textsc{Reading}, \textsc{Accent} and \textsc{Picture}
+and two two-way interactions \textsc{Reading:Picture} and
 \textsc{Reading:Accent} ($\chi^2=18.34$, $df=42$, $p=0.99$,
@@
     \textsc{Reading}.\lc & 0.526 &  0.202 & 2.607 & < 0.01 \\
-    \textsc{Condition}.\lc & 0.497 &  0.170  & 2.929 & < 0.01 \\
+    \textsc{Picture}.\lc & 0.497 &  0.170  & 2.929 & < 0.01 \\
     \textsc{Accent}.\lc & -1.054 & 0.242 & -4.354 & < 0.001 \\
@@
     \\
-    \textsc{Reading}.\emph{error}:\textsc{Condition}.\lc & -0.521 &
+    \textsc{Reading}.\emph{error}:\textsc{Picture}.\lc & -0.521 &
     0.280 & -1.87 & 0.062 \\
-    \textsc{Reading}.\lc:\textsc{Condition}.\lc & -0.583 & 0.195 &
+    \textsc{Reading}.\lc:\textsc{Picture}.\lc & -0.583 & 0.195 &
     -2.997 &  < 0.01 \\
@@
 baseline of \ec-readings in the interaction coefficient for
-\textsc{Reading}.\lc:\textsc{Condition}.\lc. The log-linear model
+\textsc{Reading}.\lc:\textsc{Picture}.\lc. The log-linear model
 therefore indicates that there is a bias for late responses in a
@@
 
-\noindent Let's consider whether traditionalism or grammaticalism are comfortable with these
+\noindent Let's consider whether traditionalism or grammaticalism are compatible with these
 preference relations.
@@
 these readings. Here, the Magri-style approach could resort to
-considerations of \emph{economy}: reasoning with fever alternatives is
+considerations of \emph{economy}: reasoning with fewer alternatives is
 easier than reasoning with more alternatives. This would explain the
@@
 \paragraph{Traditionalism.} Traditionalism, as we described it in
-Section~\ref{sec:theories-predictions}, can also not account for the
-observed pattern of results. It has to explain the possibility of
-local readings of prosodically unmarked \es-sentences, and, perhaps,
-also the large number of local readings in accented \es-sentences
-compared to the much lower number in accented \as-sentences. A first
-option might be to account for alleged local readings as the result of
-some other phenomenon, such as typicality or contrast
+Section~\ref{sec:theories-predictions}, cannot account for the possibility of local readings of
+prosodically unmarked \es-sentences, and, perhaps, also the large number of local readings in
+accented \es-sentences compared to the much lower number in accented \as-sentences. A first
+option might be to account for alleged local readings as the result of some other phenomenon,
+such as typicality or contrast
 \citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter}.
-Since this ties into a critical reflection on our design, we will
-enlarge on the possibility of typicality- and contrast-based effects
-in our setting. Eventually, we argue that contrast-effects alone are
-unlikely to explain the observed high number of local answers in
-\es-sentences, but that a ``modern traditionalist'' explanation of the
-answer pattern might be available if we allow for the possibility that
-\emph{exactly one} gets an unexpected ``referential interpretation.''
+Since this ties into a critical reflection on our design, we will enlarge on the possibility of
+typicality- and contrast-based effects in our setting. Eventually, we argue that
+contrast-effects alone are unlikely to explain the observed high number of local answers in
+\es-sentences, but that a ``modern traditionalist'' explanation of the answer pattern might be
+available if we allow for the possibility that \emph{exactly one} gets an unexpected
+``referential interpretation.''
 
@@
 
-The clearest upshot of theoretical importance of this study is that strength-based meaning
-selection does not seem to be a good disambiguation criterion for grammaticalism
+With regard to grammaticalism, the clearest upshot of theoretical importance of this study is
+that strength-based meaning selection does not seem to be a good disambiguation criterion
 \citep[c.f.][]{ChemlaSpector2010:Experimental-Ev}. This point is also relevant in general,

### 2015-11-03 text/paper/reviews_2/response_letter.md
more final edits petra

@@
 We are very grateful for drawing our attention to the fact that we should mention that Chemla & Spector have already discussed their data as countering the Strongest Meaning Hypothesis.
-We agree with this point but we believe that are providing further evidence that is relevant for this discussion, given the doubts that were brought forth against Chemla & Spector's design and interpretation and the additional doubts that arise from issues with "silent prosody".
+We agree with this point but we believe that we are providing further evidence that is relevant for this discussion, given the doubts that were brought forth against Chemla & Spector's design and interpretation and the additional doubts that arise from issues with "silent prosody".
 
@@
 
-This is a good and interesting suggestion. But we see potential problems with this idea, but feel that discussing this would lead us too far away from our main concerns.
+This is a good and interesting suggestion, but we feel that discussing this would lead us too far away from our main concerns.
 

### 2015-11-03 text/paper/revision_02/paper.tex
more final edits petra

@@
 readings would just mirror the entailment relations in (\ref{bsp:Entailments-AS}) and
-(\ref{bsp:Entailments-GE}): for \as-sentences, weak grammaticalism predicts that local readings
-are preferred over global readings which in turn are preferred over literal readings; for
-\es-sentences weak grammaticalism predicts that global readings are most preferred, while
-literal and local readings are not ranked with respect to
-preference.\footnote{\citet{ChierchiaFox2008:The-Grammatical} consider another, more elaborate
-  variant of disambiguation based on strongest meanings, but it is not necessary for purposes
-  to discuss these details here.}
+(\ref{bsp:Entailments-GE}): for \as-sentences, grammaticalism predicts that local readings are
+preferred over global readings which in turn are preferred over literal readings; for
+\es-sentences grammaticalism predicts that global readings are most preferred, while literal
+and local readings are not ranked with respect to
+preference.\footnote{\citet{ChierchiaFox2008:The-Grammatical} consider another variant of
+  disambiguation based on strongest meanings in which parses that differ in more than one
+  absence/presence of silent exhaustification are incomparable. We ignore this for simplicity,
+ because it matters little for the conclusions drawn from our experimental data.}
 

### 2015-11-04 text/paper/reviews_2/response_letter.md
this version second revision sent

@@
 addition of a few elements of emphasis in introduction, Section 4 and reflection section 6, in response to reviewer 2's comments showing that the previous version may not have made the motivation of our design sufficiently clear.
+
+All significant changes from the previous to this version are highlighted in a separately attached PDF.
 
@@
 This could lead to certain misunderstandings, so we clarify our position in the present manuscript.
-We have also added to the text (introduction, especially the relevant Section 4.4, section 6) to strengthen our view of and the motivation for out study.
+We have also modified the text (introduction, especially the relevant Section 4.4, section 6) to strengthen our view of and the motivation for out study.
 

### 2015-11-04 text/paper/revision_02/title_page/titlePage.tex
this version second revision sent

@@
 \begin{abstract}
-  The scalar item \emph{some} is widely assumed to receive a meaning
-  enrichment to \emph{some but not all} if it occurs in matrix
-  position. The question under which circumstances this enrichment can
-  occur in certain embedded positions plays an important role in
-  deciding how to delineate semantics and pragmatics. % Some claim
-  % that it requires marked intonation for the relevant pragmatic
-  % enrichment to occur in embedded position; others allow for it more
-  % freely.
-  We present new experimental data that bear on this theoretical
-  issue. In distinction to previous experimental approaches, we
-  presented sentence material auditorily in order to explicitly
-  control prosodic markedness of the scalar item. Moreover, our
-  experiment sheds light on the relative preferences or salience of
-  candidate readings. The presented data turn out to be unexpected
-  under a traditional Gricean view, but also suggest refinement of the
-  more recent grammatical approach.
+  The scalar item \emph{some} is widely assumed to receive a meaning enrichment to \emph{some
+    but not all} if it occurs in matrix position. The question under which circumstances this
+  enrichment can occur in certain embedded positions plays an important role in deciding how to
+  delineate semantics and pragmatics.  We present new experimental data that bear on this
+  theoretical issue. In distinction to previous experimental approaches, we presented sentence
+  material auditorily in order to explicitly control prosodic markedness of the scalar
+  item. Moreover, our experiment sheds light on the relative preferences or salience of
+  candidate readings. The presented data turn out to be unexpected under a traditional Gricean
+  view, but also challenge the idea of disambiguation by logical strength in grammaticalist
+  approaches.
 \end{abstract}

### 2016-03-10 text/paper/revision_02/paper.tex
this version second revision sent
proof editor corrections

@@
   Experimental Revisit} 
-\author{% Michael Franke, Fabian Schlotterbeck and Petra Augurzky
+\author{Michael Franke, Fabian Schlotterbeck \& Petra Augurzky \\
+  \normalsize{Seminar f\"{u}r Sprachwissenschaft \& SFB 833} \\ 
+  \normalsize{Eberhard Karls Universit\"{a}t T\"{u}bingen}
 } 
@@
 \begin{abstract}
-  The scalar item \emph{some} is widely assumed to receive a meaning
-  enrichment to \emph{some but not all} if it occurs in matrix
-  position. The question under which circumstances this enrichment can
-  occur in certain embedded positions plays an important role in
-  deciding how to delineate semantics and pragmatics. % Some claim
-  % that it requires marked intonation for the relevant pragmatic
-  % enrichment to occur in embedded position; others allow for it more
-  % freely.
-  We present new experimental data that bear on this theoretical issue. In distinction to
-  previous experimental approaches, we presented sentence material auditorily in order to
-  explicitly control prosodic markedness of the scalar item. Moreover, our experiment sheds
-  light on the relative preferences or salience of candidate readings. The presented data turn
-  out to be unexpected under a traditional Gricean view, but also challenge the idea of
-  disambiguation by logical strength in grammaticalist approaches.
+  The scalar item \emph{some} is widely assumed to receive a meaning enrichment to \emph{some
+    but not all} if it occurs in matrix position. The question under which circumstances this
+  enrichment can occur in certain embedded positions plays an important role in deciding how to
+  delineate semantics and pragmatics.  We present new experimental data that bear on this
+  theoretical issue. In distinction to previous experimental approaches, we presented sentence
+  material auditorily in order to explicitly control prosodic markedness of the scalar
+  item. Moreover, our experiment sheds light on the relative preferences or salience of
+  candidate readings. The presented data turn out to be unexpected under a traditional Gricean
+  view, but also challenge the idea of disambiguation by logical strength in grammaticalist
+  approaches.
 \end{abstract}
@@
 scalar implicatures. If supplemented with the prosodic markedness hypothesis, traditionalists
-would therefore predict that local readings are available forK \es-sentences, but only if
+would therefore predict that local readings are available for \es-sentences, but only if
 prosodically marked by contrastive stress.
@@
 restriction to a categorial choice (whether the sentence fits the
-picture of not) may induce a bias against non-preferred readings in
+picture or not) may induce a bias against non-preferred readings in
 cases where candidate readings stand in entailment relations
@@
 so-called \emph{late-closure} (\lc) reading
-((\ref{bsp:target-related-LC}). Alternatively, the \acro{pp} can be
+(\ref{bsp:target-related-LC}). Alternatively, the \acro{pp} can be
 attached to the whole conjunctive \acro{np} \emph{circles and

### 2016-03-15 text/paper/final/paper.tex
final version submitted

--- 2016-03-10 text/paper/revision_02/paper.tex
@@
 
+\usepackage{etex}
 \usepackage[natbib=true,
@@
             url=false]{biblatex}
-\bibliography{MyRefGlobal}
-% \bibliography{paper}
+\bibliography{extracted-bib}
 
@@
 \author{Michael Franke, Fabian Schlotterbeck \& Petra Augurzky \\
-  \normalsize{Seminar f\"{u}r Sprachwissenschaft \& SFB 833} \\ 
-  \normalsize{Eberhard Karls Universit\"{a}t T\"{u}bingen}
+  \normalsize{University of T\"{u}bingen}
 } 
@@
     \begin{center}
-      \includegraphics[scale=0.25]{pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
-      \includegraphics[scale=0.25]{pictures/paper/Chemla_Spector_2010_RatingBar.png}
+      \includegraphics[scale=0.25]{Chemla_Spector_2010_Critical_AE.png}\\
+      \includegraphics[scale=0.25]{Chemla_Spector_2010_RatingBar.png}
     \end{center}
@@
     \label{fig:CS-Results-as}
-        \includegraphics[width=5.5cm]{pictures/paper/Chemla_Spector_2010_Results_AE.png}
+        \includegraphics[width=5.5cm]{Chemla_Spector_2010_Results_AE.png}
   }
@@
     \label{fig:CS-Results-es}
-    \includegraphics[width=5.5cm]{pictures/paper/Chemla_Spector_2010_Results_GE.png}
+    \includegraphics[width=5.5cm]{Chemla_Spector_2010_Results_GE.png}
   }  
@@
 
-% \begin{figure}[t]
-%   \centering
-%       \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
-%       \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
-%         \caption{Example of critical trial for \as-condition by
-%           \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
-%           (\citeyear{ChemlaSpector2010:Experimental-Ev})}
-%   \label{fig:Chemla-Spector}
-% \end{figure}
-
-\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the
-degree to which a sentence is rated acceptable is proportional to the
-number of available true readings. Observed averaged clicking
-positions are shown in Figures~\ref{fig:CS-Results-as} and
-\ref{fig:CS-Results-es}.
-%
-% \begin{figure}
-%   \centering
-%   \subfloat[][\as-condition]{
-%     \label{fig:CS-Results-as}
-%         \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
-%   }
-%   \subfloat[test][\es-condition]{
-%     \label{fig:CS-Results-es}
-%     \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
-%   }
-%   \caption{Results from
-%     \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
-%     (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
-%   \label{fig:Chemla-Spector-Results}
-% \end{figure}
-%
-According to \citeauthor{ChemlaSpector2010:Experimental-Ev}, the
-crucial piece of evidence for the availability of local readings for
-\as-sentences is that these sentences yielded higher graded
-acceptability scores for the strong situation than for the weak
-situation (although these differ only with respect to the truth value
-of the local reading). Evidence for the availability
-of the local reading for \es-sentences comes from the difference
-between the local and the literal situation. Strikingly, \es-sentences
-received an average 73\% degree of acceptability in the local
-situation although the literal and global readings are false in this
-case.
+\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the degree to which a sentence
+is rated acceptable is proportional to the number of available true readings. Observed averaged
+clicking positions are shown in Figures~\ref{fig:CS-Results-as} and
+\ref{fig:CS-Results-es}. According to \citeauthor{ChemlaSpector2010:Experimental-Ev}, the
+crucial piece of evidence for the availability of local readings for \as-sentences is that
+these sentences yielded higher graded acceptability scores for the strong situation than for
+the weak situation (although these differ only with respect to the truth value of the local
+reading). Evidence for the availability of the local reading for \es-sentences comes from the
+difference between the local and the literal situation. Strikingly, \es-sentences received an
+average 73\% degree of acceptability in the local situation although the literal and global
+readings are false in this case.
 
@@
 
-Summing up, three experimental studies have presented diverging pieces
-of evidence. % \citet{GeurtsPouscoulous2009:Embedded-Implic} did not
-% observe any truth value-judgments that would indicate local readings
-% in a picture verification task and thus conclude that these readings
-% are unavailable. \citet{CliftonDube2010:Embedded-Implic} and
-% \citet{ChemlaSpector2010:Experimental-Ev} employed different designs
-% intended to be sensitive enough to reveal local readings. Both studies
-% found putative evidence in support of local readings.
-Differences in results might be due to differences in experimental design, in particular due to
-the type of elicited judgement and the possibility of conflating pictorial effects. Also, we
-should consider potential effects of ``silent prosody.''
+Summing up, three experimental studies have presented diverging pieces of evidence. Differences
+in results might be due to differences in experimental design, in particular due to the type of
+elicited judgement and the possibility of conflating pictorial effects. Also, we should
+consider potential effects of ``silent prosody.''
 
@@
 	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_1.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ae_01_1.pdf}}
 	    \label{fig:exseqAS1}
@@
 	\subfloat[][Step 2]{
-		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_2.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ae_01_2.pdf}}
 	    \label{fig:exseqAS2}
@@
 	\subfloat[][Step 3 (\lit true)]{ 
-		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_3.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ae_01_3.pdf}}
 	    \label{fig:exseqAS3}
@@
 	\subfloat[][Step 4]{ 
-		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_4.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ae_01_4.pdf}}
 	    \label{fig:exseqAS4}
@@
 	\subfloat[][Step 5 (\glb true)]{
-		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_5.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ae_01_5.pdf}}
 	    \label{fig:exseqAS5}
@@
 	\subfloat[][Step 6]{ 
-		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_6.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ae_01_6.pdf}}
 	    \label{fig:exseqAS6}
@@
 	\subfloat[][Step 7 (\loc false)]{ 
-		\fbox{\includegraphics[width=3.5cm]{pictures/ae_01_7.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ae_01_7.pdf}}
 	    \label{fig:exseqAS7}
@@
 	\subfloat[][Step 1]{ 
-		\fbox{\includegraphics[width=3.5cm]{pictures/ge_01_1.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ge_01_1.pdf}}
 	    \label{fig:exseqES1}
@@
 	\subfloat[][Step 2 (\glb false)]{
-		\fbox{\includegraphics[width=3.5cm]{pictures/ge_01_2.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ge_01_2.pdf}}
 	    \label{fig:exseqES2}
@@
 	\subfloat[][Step 3 (\lit false)]{ 
-		\fbox{\includegraphics[width=3.5cm]{pictures/ge_01_3.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ge_01_3.pdf}}
 	    \label{fig:exseqES3}
@@
 	\subfloat[][Step 4]{ 
-		\fbox{\includegraphics[width=3.5cm]{pictures/ge_01_4.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ge_01_4.pdf}}
 	    \label{fig:exseqES4}
@@
 	\subfloat[][Step 5 (\loc true)]{
-		\fbox{\includegraphics[width=3.5cm]{pictures/ge_01_5.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{ge_01_5.pdf}}
 	    \label{fig:exseqES5}
@@
 	\subfloat[][Step 2]{ 
-		\fbox{\includegraphics[width=5cm]{pictures/lc_01_2.pdf}}
+		\fbox{\includegraphics[width=5cm]{lc_01_2.pdf}}
 	    \label{fig:exlc2}
@@
 	\subfloat[][Step 3 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{pictures/lc_01_3.pdf}}
+		\fbox{\includegraphics[width=5cm]{lc_01_3.pdf}}
 	    \label{fig:exlc3}
@@
 	\subfloat[][Step 4]{
-		\fbox{\includegraphics[width=5cm]{pictures/lc_01_4.pdf}}
+		\fbox{\includegraphics[width=5cm]{lc_01_4.pdf}}
 	    \label{fig:exlc4}
@@
   	\subfloat[][Step 5]{
-		\fbox{\includegraphics[width=5cm]{pictures/lc_01_5.pdf}}
+		\fbox{\includegraphics[width=5cm]{lc_01_5.pdf}}
 	    \label{fig:exlc5}
@@
 	\subfloat[][Step 6 (\ec false)]{
-		\fbox{\includegraphics[width=5cm]{pictures/lc_01_6.pdf}}
+		\fbox{\includegraphics[width=5cm]{lc_01_6.pdf}}
 	    \label{fig:exlc6}
@@
 	\subfloat[][Step 7]{
-		\fbox{\includegraphics[width=5cm]{pictures/lc_01_7.pdf}}
+		\fbox{\includegraphics[width=5cm]{lc_01_7.pdf}}
 	    \label{fig:exlc7}
@@
 	\subfloat[][Step 2]{ 
-		\fbox{\includegraphics[width=5cm]{pictures/ec_01_2.pdf}}
+		\fbox{\includegraphics[width=5cm]{ec_01_2.pdf}}
 	    \label{fig:exec1}
@@
 	\subfloat[][Step 3 (\ec false)]{
-		\fbox{\includegraphics[width=5cm]{pictures/ec_01_3.pdf}}
+		\fbox{\includegraphics[width=5cm]{ec_01_3.pdf}}
 	    \label{fig:exec2}
@@
 	\subfloat[][Step 4]{
-		\fbox{\includegraphics[width=5cm]{pictures/ec_01_4.pdf}}
+		\fbox{\includegraphics[width=5cm]{ec_01_4.pdf}}
 	    \label{fig:exec2}
@@
 	\subfloat[][Step 5 (\lc true)]{
-		\fbox{\includegraphics[width=5cm]{pictures/ec_01_5.pdf}}
+		\fbox{\includegraphics[width=5cm]{ec_01_5.pdf}}
 	    \label{fig:exec2}
@@
 
-Preference-related controls also differed prosodically. Modifier
-attachment ambiguities have been shown to be sensitive to differences
-in prosodic phrasing. Though there has been discussion as to whether
-speakers reliably \textit{produce} disambiguating cues in such
-constructions
-\citep[e.g.][]{Allbritton96,Schafer00,Snedeker03,Kraljik05}, overt
-prosodic boundaries are generally acknowledged to guide interpretive
-processes of attachment ambiguities in \textit{comprehension}
+Preference-related controls also differed prosodically. Modifier attachment ambiguities have
+been shown to be sensitive to differences in prosodic phrasing. Though there has been
+discussion as to whether speakers reliably \textit{produce} disambiguating cues in such
+constructions \citep[e.g.][]{Allbritton96,Schafer00,Snedeker03,Kraljik05}, overt prosodic
+boundaries are generally acknowledged to guide interpretive processes of attachment ambiguities
+in \textit{comprehension}
 \citep[e.g.][]{Beach1991,KjelgaardSpeer1999,Steinhauer99,SchaferSpeerWarrenWhite2000,CliftonCarlsonFrazier2002,Augurzky06}.
-Specifically, it has been shown that prosodically separating a
-modifier from the directly preceding material supports an \ec-reading,
-whereas separating the two potential attachment sites is supportive of
-an \lc-reading
-\citep[e.g.][]{CliftonCarlsonFrazier2002,Fodor02,Jun2003}.  Thus, a
-phrase boundary between {\it squares} and {\it with} in
-(\ref{bsp:target-related}) supports an \ec-reading, whereas a prosodic
-phrase boundary following {\it circles} supports an \lc-reading.
+Specifically, it has been shown that prosodically separating a modifier from the directly
+preceding material supports an \ec-reading, whereas separating the two potential attachment
+sites is supportive of an \lc-reading
+\citep[e.g.][]{CliftonCarlsonFrazier2002,Fodor02,Jun2003}.  Thus, a phrase boundary between
+{\it squares} and {\it with} in (\ref{bsp:target-related}) supports an \ec-reading, whereas a
+prosodic phrase boundary following {\it circles} supports an \lc-reading.
 
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{pics/post_salience_TF_small.png}
+  \includegraphics[width=0.8\textwidth]{post_salience_TF_small.png}
   \caption{Estimated posteriors for the salience of \lc- and
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{pics/post_salience_small.png}
+  \includegraphics[width=0.8\textwidth]{post_salience_small.png}
   \caption{Posteriors over relative salience of target readings in
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{pics/post_q.pdf}
+  \includegraphics[width=0.5\textwidth]{post_q.pdf}
   \caption{Estimated Posteriors over global sequential bias parameter
@@
   \subfloat[][neutral]{
-      \includegraphics[width=0.45\textwidth]{pics/PostDiffT_ASntr.pdf}
+      \includegraphics[width=0.45\textwidth]{PostDiffT_ASntr.pdf}
   }
@@
   \subfloat[][accented]{
-      \includegraphics[width=0.45\textwidth]{pics/PostDiffT_ASacc.pdf}
+      \includegraphics[width=0.45\textwidth]{PostDiffT_ASacc.pdf}
   }
@@
 	\subfloat[][Step 2  (\lit true)]{ 
-		\fbox{\includegraphics[width=3.5cm]{pictures/PostExp_2.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{PostExp_2.pdf}}
 	    \label{fig:exseqPost1}
@@
 	\subfloat[][Step 3]{
-		\fbox{\includegraphics[width=3.5cm]{pictures/PostExp_3.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{PostExp_3.pdf}}
 	    \label{fig:exseqPost2}
@@
 	\subfloat[][Step 4 (\acro{prag} false)]{ 
-		\fbox{\includegraphics[width=3.5cm]{pictures/PostExp_4.pdf}}
+		\fbox{\includegraphics[width=3.5cm]{PostExp_4.pdf}}
 	    \label{fig:exseqPost3}
@@
 
-  \includegraphics[width=\textwidth]{pictures/Acoustics/Table-B.png}
+  \includegraphics[width=\textwidth]{Table-B.png}
 
@@
 
-  \includegraphics[width=\textwidth]{pictures/Acoustics/Table-A.png}
+  \includegraphics[width=\textwidth]{Table-A.png}
 
@@
 
-  \includegraphics[width=\textwidth]{pictures/Acoustics/Table-D.png}
+  \includegraphics[width=\textwidth]{Table-D.png}
 
@@
 
-  \includegraphics[width=\textwidth]{pictures/Acoustics/Table-C.png}
+  \includegraphics[width=\textwidth]{Table-C.png}
 
@@
 
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+
+We would like to thank Oliver Bott, Emmanuel Chemla, Judith Degen, Bart Geurts, Phillipe
+Schlenker and Bob van Tiel for helpful comments and discussion at various stages of this
+work. We are also indebted to three anonymous reviewers and Rick Nouwen for very insightful and
+helpful comments, suggestions and advice. Thanks to Fabian Dablander for help with the
+follow-up experiment, and to Helena Schütze for help with data acquisition for the main
+experiment.
+
+MF gratefully acknowledges support by the Institutional Strategy of the University of Tübingen
+(Deutsche Forschungsgemeinschaft, ZUK 63) and the Priority Program XPrag.de (DFG
+Schwerpunktprogramm 1727). All authors gratefully acknowledge financial support by the
+\emph{Tübingen Center of Linguistics} (T\"uZLI), and project B1 of the Collaborative Research
+Center \emph{Construction of Meaning} (SFB833) funded by the German Research Foundation (DFG).
+
+\medskip
+
+\begin{minipage}{0.45\linewidth}
+  Michael Franke\\
+  Department of Linguistics \\
+  University of T\"{u}bingen \\
+  Wilhelmstra\ss e 19 \\
+  72074 T\"ubingen \\
+  Germany
+\end{minipage}
+\begin{minipage}{0.45\linewidth}
+  Fabian Schlotterbeck\\
+  Collaborative Research Center 833\\
+  University of Tübingen\\ 
+  Nauklerstraße 35\\
+  72074 Tübingen\\
+  Germany
+\end{minipage}
+
+\medskip
+
+\begin{minipage}{0.45\linewidth}
+  Petra Augurzky\\
+  Department of Linguistics \\
+  Collaborative Research Center 833\\
+  University of T\"{u}bingen \\
+  Wilhelmstra\ss e 19 \\
+  72074 T\"ubingen \\
+  Germany
+\end{minipage}
+
 \printbibliography[heading=bibintoc]
